# beh :: expectation ~ cue {#beh-expect-cue}


## What is the purpose of this notebook? {.unlisted .unnumbered}

Here, I plot the expectation ratings as a function of cue.

- Main model: `lmer(expect_rating ~ cue)`
- Main question: do expectations ratings differ as a function of cue type?
- If there is a main effect of cue on expectation ratings, does this cue effect differ depending on task type?
- IV: cue (high / low)
- DV: expectation rating

Also, Do those who have larger IQRs for expectation ratings also show greater cue effects?
Steps:
calculate cue effects per pariticpant (high vs. low cue average)
calculate IQR per participant
check correlation

```{r load_libraries_1, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(psych)
library(car)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(knitr)
library(ggpubr)
library(gridExtra)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(readr)
library(rmarkdown)
library(stringr)
library(gghalves)
library(ggpubr)
library(cueR)
library(Rmisc)
```

```{r parameters, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
print(main_dir)
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model02_iv-cue_dv-expect", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```



### extract random effects from lmer model
```{r}
library(dplyr)
library(tidyr)
library(broom)

compute_randomeffects <- function(lmer_model, rand_savefname, taskname, 
                                  new_rand_names = c("rand_intercept", "rand_cue"), 
                                  new_fix_names =  c("fix_intercept", "fix_cue")) {
  
    # Extract fixed effects and random effects _________________________________
    fixEffect <- as.data.frame(fixef(lmer_model))
    randEffect <- as.data.frame(ranef(lmer_model))
    
    
    # New mapping of fix effect terms _______________________________________
    fix_names <- rownames(fixEffect)
    fix_mapping <- setNames(new_fix_names, fix_names)
    rownames(fixEffect) <- fix_mapping[rownames(fixEffect)]

    
    # New mapping of random effect terms _______________________________________
    unique_terms <- levels(randEffect$term)
    mapping <- setNames(new_rand_names, unique_terms)
    randEffect$newcoef <- mapping[randEffect$term]

    
    # Processing the random effects ____________________________________________
    rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
    wide_rand <- spread(rand_subset, key = newcoef, value = condval)

    
    # Processing the fixed effects _____________________________________________
    wide_fix <- do.call(
        "rbind",
        replicate(nrow(wide_rand),
            as.data.frame(t(as.matrix(fixEffect))),
            simplify = FALSE
        )
    )
    
    # Combining and finalizing the dataframe ___________________________________
    total <- cbind(wide_rand, wide_fix)
    total$task <- taskname
    rownames(total) <- NULL
    new_total <- total %>% dplyr::select(task, everything())
    new_total <- dplyr::rename(total, subj = grp)
    

    # Saving the file
    #write.csv(new_total, rand_savefname, row.names = FALSE)
    return(invisible(new_total))
    
}

```




### Load data across tasks and designate common plot variables {.unlisted .unnumbered}
```{r}
# 1. load data and rename columns ______________________________________________
pvc <- cueR::df_load_pvc_beh(datadir, subject_varkey = "src_subject_id", iv = "param_cue_type", dv = "event02_expect_angle", exclude = "sub-0001")
pvc <- cueR::simple_contrast_beh(pvc)

column_mapping <- c("event04_actual_angle" = "OUTCOME", 
                    "event02_expect_angle" = "EXPECT", 
                    "src_subject_id" = "sub")
pvc <- cueR::df_rename_columns(pvc, column_mapping)
```


## Pain

### For the pain task, what is the effect of cue on expectation ratings? {.unlisted .unnumbered}

> Cue effects are signficiant in Expectation ratings (b = 34.37, p < 001). This is most likely an anchoring effect, because the cue and the expectation rating period is close, but we want to operate this manipulation check that there are expectation differences for high and low cues. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
taskname <- 'pain'


# 0. Summary and plot related keywords _________________________________________
subject <- "sub";
iv <- "cue_ordered";              dv <- "EXPECT"
sub_mean <- "mean_per_sub";       group_mean <- "mean_per_sub_norm_mean"
se <- "se"
iv_keyword <- "cue";              dv_keyword <- "expect"
ggtitle_phrase <- " - Expectation Rating"
ggtitle <- paste0(tools::toTitleCase(taskname), ggtitle_phrase, " (N = ", length(unique(data$sub)), ")");
title <- paste0(tools::toTitleCase(taskname), " - ", tools::toTitleCase(dv_keyword))
xlab <- "Cue type";               ylab <- "Expectation Ratings (degree)"
ylim <- c(-10,190);               w = 5; h = 3;
plot_savefname <- file.path(analysis_dir,
                            paste0("raincloud_task-", taskname,"_iv-", iv_keyword, 
                                   "_dv-rating-", dv_keyword,"_", as.character(Sys.Date()), ".png")
                            )
color <- c("lightgreen", "orange")


data <- pvc[pvc$task==taskname, ]


# 1. summary stats _____________________________________________________________
expect_subjectwise <- meanSummary(data, c(subject, iv), dv)
expect_groupwise <- cueR::summarySEwithin(
    data = expect_subjectwise,
    measurevar = sub_mean, # variable created from above
    withinvars = c(iv), # iv
    idvar = subject
)


# 2. plot parameters _____________________________________________________________
g <- cueR::plot_cueexpectancy_onefactor(
        expect_subjectwise, expect_groupwise, iv,
        sub_mean, group_mean, se, subject, ggtitle, title, 
        xlab="", ylab, taskname, 
        w, h, dv_keyword, color, plot_savefname,
        expand_x = TRUE,
        xlim = c(NA, 3), ylim = c(-20, 200),
        x_scale_expansion = c(0, 0.5),
        x_hline_position = 2.5,
        x_hline_linetype = "dashed",
        x_hline_nudge_x = 0.1,
        x_hline_textsize = 3,
        legend_factor_levels = c("High cue", "Low cue"),
        legend_factor_colors = c("orange", "lightgreen"),
        legend_geom_point_size = 4,
        legend_position = c(-0.1, 0.7),
        legend_widths = c(3, 1)
      )
grid::grid.draw(g)


# 3. mixed effects model _______________________________________________________
model.painexpect <- lmer(EXPECT ~ cue_ordered + (cue_ordered|sub), data = data)
sjPlot::tab_model(model.painexpect,
              title = paste0(tools::toTitleCase(taskname), ": \nlmer(EXPECT ~ CUE + (1| sub), data = pvc)"),
              CSS = list(css.table = '+font-size: 12;'))


# 4. compute random effects and save for compiling across PVC tasks ____________
rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",
        as.character(Sys.Date()), ".csv",
        sep = ""
    ))
randeffect.P <- compute_randomeffects(model.painexpect, rand_savefname = rand_savefname, taskname,
                                      new_rand_names = c("rand_intercept", "rand_cue"),
                                      new_fix_names =  c("fix_intercept", "fix_cue"))
```



## Vicarious

### For the vicarious task, what is the effect of cue on expectation ratings? {.unlisted .unnumbered}

> Cue effects are signficiant in Expectation ratings. This is most likely an anchoring effect, because the cue and the expectation rating period is close, but we want to operate this manipulation check that there are expectation differences for high and low cues. Note that the range is truncated than that of the pain task. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
taskname <- 'vicarious'

# 0. Summary and plot related keywords _________________________________________
subject <- "sub";
iv <- "cue_ordered";              dv <- "EXPECT"
sub_mean <- "mean_per_sub";       group_mean <- "mean_per_sub_norm_mean"
se <- "se"
iv_keyword <- "cue";              dv_keyword <- "expect"
ggtitle_phrase <- " - Expectation Rating"
ggtitle <- paste0(tools::toTitleCase(taskname), ggtitle_phrase, " (N = ", length(unique(data$sub)), ")");
title <- paste0(tools::toTitleCase(taskname), " - ", tools::toTitleCase(dv_keyword))
xlab <- "Cue type";               ylab <- "Expectation Ratings (degree)"
ylim <- c(-10,190);               w = 5; h = 3;
plot_savefname <- file.path(analysis_dir,
                            paste0("raincloud_task-", taskname,"_iv-", iv_keyword, 
                                   "_dv-rating-", dv_keyword,"_", as.character(Sys.Date()), ".png")
                            )
color <- c("lightgreen", "orange")


data <- pvc[pvc$task==taskname, ]


# 1. summary stats _____________________________________________________________
expect_subjectwise <- meanSummary(data, c(subject, iv), dv)
expect_groupwise <- cueR::summarySEwithin(
    data = expect_subjectwise,
    measurevar = sub_mean, # variable created from above
    withinvars = c(iv), # iv
    idvar = subject
)


# 2. plot parameters _____________________________________________________________
g <- cueR::plot_cueexpectancy_onefactor(
        expect_subjectwise, expect_groupwise, iv,
        sub_mean, group_mean, se, subject, ggtitle, title, 
        xlab="", ylab, taskname, 
        w, h, dv_keyword, color, plot_savefname,
        expand_x = TRUE,
        xlim = c(NA, 3), ylim = c(-20, 200),
        x_scale_expansion = c(0, 0.5),
        x_hline_position = 2.5,
        x_hline_linetype = "dashed",
        x_hline_nudge_x = 0.1,
        x_hline_textsize = 3,
        legend_factor_levels = c("High cue", "Low cue"),
        legend_factor_colors = c("orange", "lightgreen"),
        legend_geom_point_size = 4,
        legend_position = c(-0.1, 0.7),
        legend_widths = c(3, 1)
      )
grid::grid.draw(g)


# 3. mixed effects model _______________________________________________________
model.vicexpect <- lmer(EXPECT ~ cue_ordered + (cue_ordered|sub),data = data)
sjPlot::tab_model(model.vicexpect,
              title = paste0(tools::toTitleCase(taskname), ": \nlmer(EXPECT ~ CUE + (1| sub), data = pvc)"),
              CSS = list(css.table = '+font-size: 12;'))


# 4. compute random effects and save for compiling across PVC tasks ____________
rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",
        as.character(Sys.Date()), ".csv",
        sep = ""
    ))
randeffect.V <- compute_randomeffects(model.vicexpect, rand_savefname = rand_savefname, taskname,
                                      new_rand_names = c("rand_intercept", "rand_cue"),
                                      new_fix_names =  c("fix_intercept", "fix_cue"))
```

## Cognitive

### For the cognitive task, what is the effect of cue on expectation ratings? {.unlisted .unnumbered}

> Cue effects are signficiant in Expectation ratings. This is most likely an anchoring effect, because the cue and the expectation rating period is close, but we want to operate this manipulation check that there are expectation differences for high and low cues. Note that the range is truncated than that of the pain task. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
taskname <- 'cognitive'

# 0. Summary and plot related keywords _________________________________________
subject <- "sub";
iv <- "cue_ordered";              dv <- "EXPECT"
sub_mean <- "mean_per_sub";       group_mean <- "mean_per_sub_norm_mean"
se <- "se"
iv_keyword <- "cue";              dv_keyword <- "expect"
ggtitle_phrase <- " - Expectation Rating"
ggtitle <- paste0(tools::toTitleCase(taskname), ggtitle_phrase, " (N = ", length(unique(data$sub)), ")");
title <- paste0(tools::toTitleCase(taskname), " - ", tools::toTitleCase(dv_keyword))
xlab <- "Cue type";               ylab <- "Expectation Ratings (degree)"
ylim <- c(-10,190);               w = 5; h = 3;
plot_savefname <- file.path(analysis_dir,
                            paste0("raincloud_task-", taskname,"_iv-", iv_keyword, 
                                   "_dv-rating-", dv_keyword,"_", as.character(Sys.Date()), ".png")
                            )
color <- c("lightgreen", "orange")


data <- pvc[pvc$task==taskname, ]


# 1. summary stats _____________________________________________________________
expect_subjectwise <- meanSummary(data, c(subject, iv), dv)
expect_groupwise <- cueR::summarySEwithin(
    data = expect_subjectwise,
    measurevar = sub_mean, # variable created from above
    withinvars = c(iv), # iv
    idvar = subject
)


# 2. plot parameters _____________________________________________________________
g <- cueR::plot_cueexpectancy_onefactor(
        expect_subjectwise, expect_groupwise, iv,
        sub_mean, group_mean, se, subject, ggtitle, title, 
        xlab="", ylab, taskname, 
        w, h, dv_keyword, color, plot_savefname,
        expand_x = TRUE,
        xlim = c(NA, 3), ylim = c(-20, 200),
        x_scale_expansion = c(0, 0.5),
        x_hline_position = 2.5,
        x_hline_linetype = "dashed",
        x_hline_nudge_x = 0.1,
        x_hline_textsize = 3,
        legend_factor_levels = c("High cue", "Low cue"),
        legend_factor_colors = c("orange", "lightgreen"),
        legend_geom_point_size = 4,
        legend_position = c(-0.1, 0.7),
        legend_widths = c(3, 1)
      )
grid::grid.draw(g)


# 3. mixed effects model _______________________________________________________
model.cogexpect <- lmer(EXPECT ~ cue_ordered + (cue_ordered|sub),data = data)
sjPlot::tab_model(model.cogexpect,
              title = paste0(tools::toTitleCase(taskname), ": \nlmer(EXPECT ~ CUE + (1| sub), data = pvc)"),
              CSS = list(css.table = '+font-size: 12;'))


# 4. compute random effects and save for compiling across PVC tasks ____________
rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",
        as.character(Sys.Date()), ".csv",
        sep = ""
    ))
randeffect.C <- compute_randomeffects(model.cogexpect, rand_savefname = rand_savefname, taskname,
                                      new_rand_names = c("rand_intercept", "rand_cue"),
                                      new_fix_names =  c("fix_intercept", "fix_cue"))
```



## Individual difference analysis

### Are cue effects (on expectation ratings) similar across tasks? {.unlisted .unnumbered}

> Using the random slopes of cue effects, here we plot them side by side
> with all three tasks of pain, cognitive, vicarious. As we can see, there
> is a high correlation across the random effects of cue across
> pain-cognitive, pain-vicarious, and cognitive-vicarious. These plots
> suggest a universal mechansim in the cue-expectancy effect, although
> some may critic that the cues were identical across tasks, thereby the
> cue effects are identical due to the stimuli itself, not necessarily a
> domain-general expectation process.

```{r random effects scatter plot, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# # load random effects data____________________________________________________
# rand_dir <- file.path(main_dir, "analysis", "mixedeffect", "model01_iv-cue_dv-expect", as.character(Sys.Date()))
# dir.create(rand_dir, showWarnings = FALSE, recursive = TRUE)
# dfP <- read.csv(file.path(
#     rand_dir,
#     paste("randeffect_task-pain", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
# ))
# dfV <- read.csv(file.path(
#     rand_dir,
#     paste("randeffect_task-vicarious", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
# ))
# dfC <- read.csv(file.path(
#     rand_dir,
#     paste("randeffect_task-cognitive", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
# ))


# combined random effects ______________________________________________________
pvc.randeffect <- rbind(randeffect.P, randeffect.V, randeffect.C)
pvc_rand_cue_subset <- subset(pvc.randeffect, select = c(task, subj, rand_cue))
pvc_rand_cue <- spread(pvc_rand_cue_subset, key = task, value = rand_cue)


# plot individually ____________________________________________________________
pv <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'vicarious', y = 'pain', p_acc = 0.001, r_acc = 0.01, limit_min = -60, limit_max = 60, label_position = 50)
vc <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'cognitive', y = 'vicarious', p_acc = 0.001, r_acc = 0.01, limit_min = -60, limit_max = 60, label_position = 50)
cp <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'pain', y = 'cognitive', p_acc = 0.001, r_acc = 0.01, limit_min = -60, limit_max = 60, label_position = 50)


# combine plots and add title __________________________________________________
plots <- ggpubr::ggarrange(pv, vc, cp, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob("individual differences\n - cue effects from expectation ratings", color = "black", face = "bold", size = 15))
plots

# save plot ____________________________________________________________________
# save_plotname <- file.path(
#     analysis_dir,
#     paste("randeffect_scatterplot_task-all_",
#         as.character(Sys.Date()), ".png",
#         sep = ""
#     )
# )
# ggsave(save_plotname, width = 10, height = 3)
```
