# [beh] outcome ~ cue {#ch03_cue}

## What is the purpose of this notebook? {.unlisted .unnumbered}

Here, I plot the outcome ratings as a function of cue. 

* Main model: `lmer(outcome_rating ~ cue)` 
* Main question: do outcome ratings differ as a function of cue type? 
* If there is a main effect of cue on outcome ratings, does this cue effect differ depending on task type?
* IV: cue (high / low)
* DV: outcome rating

FIX: plot statistics in random effect plot - what is broken?

```{r load_libraries_2, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(psych)
library(car)
library(lme4)
library(lmerTest)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(rmarkdown)
library(stringr)
library(ICC)
library(gghalves)
## library(extraoperators)
##library(JWileymisc)
##library(multilevelTools)
library(ggpubr)

source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
main_dir = dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, "scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

```{r parameters_2, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
print(main_dir)
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
```

```{r common_parameters_2, message=FALSE, warning=FALSE, paged.print=FALSE}
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"; iv_keyword <- "cue"; dv <- "event04_actual_angle"; dv_keyword <- "outcome"
xlab <- ""; ylim = c(0,180); ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
subjectwise_mean <- "mean_per_sub"; group_mean <- "mean_per_sub_norm_mean"; se <- "se"
color_scheme <-     if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color_scheme <- c("#1B9E77", "#D95F02")
    } else {
        color_scheme <- c("#4575B4", "#D73027")
    }
print_lmer_output <- FALSE
ggtitle_phrase <- " - Outcome Rating (degree)"
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model02_iv-cue_dv-outcome", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```

```{r ggplotfunction_2, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
ggplot_onefactor_pertask <- function(taskname, subject_varkey, subject, exclude,
                                     analysis_dir, iv, iv_keyword, dv, dv_keyword, 
                                     subjectwise_mean, group_mean, se,
                                     xlab, ylim, ylab, ggtitle_phrase, print_lmer_output) {
    ## designate where the lmer output lives
    model_savefname <- file.path(
        analysis_dir,paste("lmer_task-", taskname,"_iv-", iv_keyword, "_dv-rating-", dv_keyword,"_", as.character(Sys.Date()), ".txt",
            sep = ""))
      
    ## load data, run model, and exclude outliers
    data <- load_task_social_df(datadir, taskname, subject_varkey, iv, dv, exclude)
    data$subject = factor(data$src_subject_id)
    data = data[!is.na(data[, dv] ),] # removing NA values
    #print(length(unique(data$subject)))

    cooksd <- lmer_onefactor_cooksd(data, taskname, iv, dv, subject, dv_keyword, model_savefname, print_lmer_output) # run lmer
    influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data$subject)))))])
    data_screen <- data[-influential, ]
    
    ## summary statistics
    subjectwise <- meanSummary(data_screen, c(subject, iv), dv)
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = subjectwise_mean, # variable created from above
        withinvars = c(iv), # iv
        idvar = "subject"
    )
    
    ## designate plot save location
    ggtitle <- paste0(str_to_title(taskname), ggtitle_phrase, " N = (", length(unique(data$subject)), ")");  
    title <- paste0(str_to_title(taskname), " - ", str_to_title(dv_keyword))
    w = 5; h = 3; 
    plot_savefname <- file.path(analysis_dir,
                                paste0("raincloud_task", taskname,"iv-", iv_keyword, "_dv-rating-", dv_keyword,"_", as.character(Sys.Date()), ".png")
                                )
    
    # plot_rainclouds_onefactor
    p1 <- plot_halfrainclouds_onefactor(
        subjectwise, groupwise,
        iv, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name,ylim,
        w, h, dv_keyword, color_scheme, plot_savefname
    )
randEffect$newcoef <- mapvalues(randEffect$term,
    from = c(as.character(unique(randEffect$term)[1]),
             as.character(unique(randEffect$term)[2])
             ),
    to = c("rand_intercept", "rand_cue")
)

rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = colnames(wide_fix)[1],
    fix_cue = colnames(wide_fix)[2],
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",
        as.character(Sys.Date()), "_outlier-cooksd.csv",
        sep = ""
    )
)
write.csv(new_total, rand_savefname, row.names = FALSE)
return(p1)
}
```

## Pain
### For the vicarious task, what is the effect of cue on outcome ratings? {.unlisted .unnumbered}
[ INSERT DESCRIPTION ]
```{r pain_iv-cue_dv-outcome, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
taskname = 'pain'
ggplot_onefactor_pertask(taskname, subject_varkey, subject, exclude,
                                     analysis_dir, iv, iv_keyword, dv, dv_keyword, 
                                     subjectwise_mean, group_mean, se,
                                     xlab, ylim, ylab, ggtitle_phrase, print_lmer_output)
```

## Vicarious
### For the vicarious task, what is the effect of cue on outcome ratings? {.unlisted .unnumbered}
[ INSERT DESCRIPTION ]
```{r vicarious_iv-cue_dv-outcome, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
taskname = 'vicarious'
ggplot_onefactor_pertask(taskname, subject_varkey, subject, exclude,
                                     analysis_dir, iv, iv_keyword, dv, dv_keyword, 
                                     subjectwise_mean, group_mean, se,
                                     xlab, ylim, ylab, ggtitle_phrase, print_lmer_output)
```

## Cognitive
### For the cognitive task, what is the effect of cue on outcome ratings? {.unlisted .unnumbered}
[ INSERT DESCRIPTION ]
```{r cognitive_iv-cue_dv-outcome, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
taskname = 'cognitive'
ggplot_onefactor_pertask(taskname, subject_varkey, subject, exclude,
                                     analysis_dir, iv, iv_keyword, dv, dv_keyword, 
                                     subjectwise_mean, group_mean, se,
                                     xlab, ylim, ylab, ggtitle_phrase, print_lmer_output)
```

```{r random_effects_2, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# test function
rand_dir <- analysis_dir
dir.create(rand_dir, showWarnings = FALSE, recursive = TRUE)
dfP <- read.csv(file.path(
    rand_dir,
    paste("randeffect_task-pain", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
))
dfV <- read.csv(file.path(
    rand_dir,
    paste("randeffect_task-vicarious", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
))
dfC <- read.csv(file.path(
    rand_dir,
    paste("randeffect_task-cognitive", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
))

pvc <- merge_recurse(list(dfP, dfV, dfC))

save_fname <- file.path(
    analysis_dir,
    paste("randeffect_task-all_",
        as.character(Sys.Date()), ".csv",
        sep = ""
    )
)
write.csv(pvc, save_fname, row.names = FALSE)
```


## Individual differences analysis: random cue effects
Using the random effects from the mixed effects model, I'm plotting the random effect of cue types per task. 



[ INSERT DESCRIPTION ]
```{r random_cue_scatter_plot_2, echo=FALSE, message=FALSE, warning=FALSE}
pvc_rand_cue_subset <- subset(pvc, select = c(task, subj, rand_cue))
pvc_rand_cue <- spread(pvc_rand_cue_subset, key = task, value = rand_cue)
# plot individually
# limit_min = -40, limit_max = 40,
pv <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'vicarious', y = 'pain', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 20, label_position = 38)
vc <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'cognitive', y = 'vicarious', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 20,  label_position = 38)
cp <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'pain', y = 'cognitive', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 20, label_position = 38)
# combine plots and add title
plots <- ggpubr::ggarrange(pv, vc, cp, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob("individual differences\n - cue effects from outcome ratings", color = "black", face = "bold", size = 15))

save_plotname <- file.path(
    analysis_dir,
    paste("randcueonly_scatterplot_task-all_", 
        as.character(Sys.Date()), ".png",
        sep = ""
    )
)
ggsave(save_plotname, width = 10, height = 3)
plots

```

Note:
* Pain: Warning: Removed 2 rows containing non-finite values (`stat_cor()`).
* Vicarious: Warning: Removed 1 rows containing non-finite values (`stat_cor()`).
* Cognitive: Warning: Removed 2 rows containing non-finite values (`stat_cor()`).


## Individual differences analysis 2: random intercept + random slopes of cue effect
based on Tor's suggestion, plotting the random efects with the random intercepts as well. not just the cue effects
```{r random_effects_scatter_plot_2, echo=FALSE, message=FALSE, warning=FALSE}
pvc$rand = pvc$rand_intercept + pvc$rand_cue
pvc_rand_cue_subset <- subset(pvc, select = c(task, subj, rand))
pvc_rand_cue <- spread(pvc_rand_cue_subset, key = task, value = rand)
# plot individually
# limit_min = -40, limit_max = 40,
pv <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'vicarious', y = 'pain', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 20, label_position = 38)
vc <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'cognitive', y = 'vicarious', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 20,  label_position = 38)
cp <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'pain', y = 'cognitive', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 20, label_position = 38)
# combine plots and add title
plots <- ggpubr::ggarrange(pv, vc, cp, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob("individual differences\n - cue effects from outcome ratings", color = "black", face = "bold", size = 15))

save_plotname <- file.path(
    analysis_dir,
    paste("randeffect_scatterplot_task-all_", 
        as.character(Sys.Date()), ".png",
        sep = ""
    )
)
ggsave(save_plotname, width = 10, height = 3)
plots

```

Note:
* Pain: Warning: Removed 49 rows containing non-finite values (`stat_cor()`).
* Vicarious: Removed 8 rows containing non-finite values (`stat_cor()`).
* Cognitive: Removed 52 rows containing non-finite values (`stat_cor()`).
