# beh :: outcome ~ cue {#beh-outcome-cue}

## What is the purpose of this notebook? {.unlisted .unnumbered}

Here, I plot the outcome ratings as a function of cue.

- Main model: `lmer(outcome_rating ~ cue)`
- Main question: do outcome ratings differ as a function of cue type?
- If there is a main effect of cue on outcome ratings, does this cue effect differ depending on task type?
- IV: cue (high / low)
- DV: outcome rating

FIX: plot statistics in random effect plot - what is broken?

```{r load_libraries_2, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(psych)
library(car)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
# library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
# library(RCurl)
# library(rstanarm)
library(reshape)
# library(boot)
# library(afex)
# library(cowplot)
library(readr)
library(rmarkdown)
library(stringr)
library(ICC)
library(gghalves)
## library(extraoperators)
##library(JWileymisc)
##library(multilevelTools)
library(ggpubr)
library(cueR)
```

```{r parameters_2, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
print(main_dir)
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model03_iv-cue_dv-outcome", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```


### Load data across tasks and designate common plot variables {.unlisted .unnumbered}
```{r}
# 1. load data and rename columns ______________________________________________
pvc <- cueR::df_load_pvc_beh(datadir, subject_varkey = "src_subject_id", iv = "param_cue_type", dv = "event02_expect_angle", exclude = "sub-0001")
pvc <- cueR::simple_contrast_beh(pvc)

column_mapping <- c("event04_actual_angle" = "OUTCOME", 
                    "event02_expect_angle" = "EXPECT", 
                    "src_subject_id" = "sub")
pvc <- cueR::df_rename_columns(pvc, column_mapping)
```



## Pain

### For the vicarious task, what is the effect of cue on outcome ratings? {.unlisted .unnumbered}

> There is a signficiant effect of cue on outcome ratings. High cues lead to greater outcome ratings on average. 

```{r pain_iv-cue_dv-outcome, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# taskname = 'pain'
# ggplot_onefactor_pertask(taskname, subject_varkey, subject, exclude,
#                                      analysis_dir, iv, iv_keyword, dv, dv_keyword,
#                                      subjectwise_mean, group_mean, se,
#                                      xlab, ylim, ylab, ggtitle_phrase, print_lmer_output)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
taskname <- 'pain'


# 0. Summary and plot related keywords _________________________________________
subject <- "sub";
iv <- "cue_ordered";              dv <- "OUTCOME"
sub_mean <- "mean_per_sub";       group_mean <- "mean_per_sub_norm_mean"
se <- "se"
iv_keyword <- "cue";              dv_keyword <- "outcome"
ggtitle_phrase <- " - Outcome Rating"
ggtitle <- paste0(tools::toTitleCase(taskname), ggtitle_phrase, " (N = ", length(unique(data$sub)), ")");
title <- paste0(tools::toTitleCase(taskname), " - ", tools::toTitleCase(dv_keyword))
xlab <- "Cue type";               ylab <- "Outcome Ratings (degree)"
ylim <- c(-10,190);               w = 5; h = 3;
plot_savefname <- file.path(analysis_dir,
                            paste0("raincloud_task-", taskname,"_iv-", iv_keyword, 
                                   "_dv-rating-", dv_keyword,"_", as.character(Sys.Date()), ".png")
                            )
color <- c("#4575B4", "#D73027")


data <- pvc[pvc$task==taskname, ]


# 1. summary stats _____________________________________________________________
outcome_subjectwise <- meanSummary(data, c(subject, iv), dv)
outcome_groupwise <- cueR::summarySEwithin(
    data = outcome_subjectwise,
    measurevar = sub_mean, # variable created from above
    withinvars = c(iv), # iv
    idvar = subject
)


# 2. plot parameters _____________________________________________________________
g <- cueR::plot_cueexpectancy_onefactor(
        outcome_subjectwise, outcome_groupwise, iv,
        sub_mean, group_mean, se, subject, ggtitle, title, 
        xlab="", ylab, taskname, 
        w, h, dv_keyword, color, plot_savefname,
        expand_x = TRUE,
        xlim = c(NA, 3), ylim = c(-20, 200),
        x_scale_expansion = c(0, 0.5),
        x_hline_position = 2.5,
        x_hline_linetype = "dashed",
        x_hline_nudge_x = 0.1,
        x_hline_textsize = 3,
        legend_factor_levels = c("High cue", "Low cue"),
        legend_factor_colors = c("#D73027", "#4575B4" ),
        legend_geom_point_size = 4,
        legend_position = c(-0.1, 0.7),
        legend_widths = c(3, 1)
      )
grid::grid.draw(g)


# 3. mixed effects model _______________________________________________________
model.painexpect <- lmer(OUTCOME ~ cue_ordered + (cue_ordered|sub), data = data)
sjPlot::tab_model(model.painexpect,
              title = paste0(tools::toTitleCase(taskname), ": \nlmer(OUTCOME ~ CUE + (1| sub), data = pvc)"),
              CSS = list(css.table = '+font-size: 12;'))


# 4. compute random effects and save for compiling across PVC tasks ____________
rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",
        as.character(Sys.Date()), ".csv",
        sep = ""
    ))
randeffect.P <- compute_randomeffects(model.painexpect, rand_savefname = rand_savefname, taskname,
                                      new_rand_names = c("rand_intercept", "rand_cue"),
                                      new_fix_names =  c("fix_intercept", "fix_cue"))
```


## Vicarious

### For the vicarious task, what is the effect of cue on outcome ratings? {.unlisted .unnumbered}

> Cue effects are significant even in the outcome rating domain. Note that the outcome ratings are measured after the stimulus delivery, and the cue-related data points are no longer visible on screen. 

```{r vicarious_iv-cue_dv-outcome, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# taskname = 'vicarious'
# ggplot_onefactor_pertask(taskname, subject_varkey, subject, exclude,
#                                      analysis_dir, iv, iv_keyword, dv, dv_keyword,
#                                      subjectwise_mean, group_mean, se,
#                                      xlab, ylim, ylab, ggtitle_phrase, print_lmer_output)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
taskname <- 'vicarious'


# 0. Summary and plot related keywords _________________________________________
subject <- "sub";
iv <- "cue_ordered";              dv <- "OUTCOME"
sub_mean <- "mean_per_sub";       group_mean <- "mean_per_sub_norm_mean"
se <- "se"
iv_keyword <- "cue";              dv_keyword <- "outcome"
ggtitle_phrase <- " - Outcome Rating"
ggtitle <- paste0(tools::toTitleCase(taskname), ggtitle_phrase, " (N = ", length(unique(data$sub)), ")");
title <- paste0(tools::toTitleCase(taskname), " - ", tools::toTitleCase(dv_keyword))
xlab <- "Cue type";               ylab <- "Outcome Ratings (degree)"
ylim <- c(-10,190);               w = 5; h = 3;
plot_savefname <- file.path(analysis_dir,
                            paste0("raincloud_task-", taskname,"_iv-", iv_keyword, 
                                   "_dv-rating-", dv_keyword,"_", as.character(Sys.Date()), ".png")
                            )
color <- c("#4575B4", "#D73027")


data <- pvc[pvc$task==taskname, ]


# 1. summary stats _____________________________________________________________
outcome_subjectwise <- meanSummary(data, c(subject, iv), dv)
outcome_groupwise <- cueR::summarySEwithin(
    data = outcome_subjectwise,
    measurevar = sub_mean, # variable created from above
    withinvars = c(iv), # iv
    idvar = subject
)


# 2. plot parameters _____________________________________________________________
g <- cueR::plot_cueexpectancy_onefactor(
        outcome_subjectwise, outcome_groupwise, iv,
        sub_mean, group_mean, se, subject, ggtitle, title, 
        xlab="", ylab, taskname, 
        w, h, dv_keyword, color, plot_savefname,
        expand_x = TRUE,
        xlim = c(NA, 3), ylim = c(-20, 200),
        x_scale_expansion = c(0, 0.5),
        x_hline_position = 2.5,
        x_hline_linetype = "dashed",
        x_hline_nudge_x = 0.1,
        x_hline_textsize = 3,
        legend_factor_levels = c("High cue", "Low cue"),
        legend_factor_colors = c("#D73027", "#4575B4" ),
        legend_geom_point_size = 4,
        legend_position = c(-0.1, 0.7),
        legend_widths = c(3, 1)
      )
grid::grid.draw(g)


# 3. mixed effects model _______________________________________________________
model.vicexpect <- lmer(OUTCOME ~ cue_ordered + (cue_ordered|sub), data = data)
sjPlot::tab_model(model.vicexpect,
              title = paste0(tools::toTitleCase(taskname), ": \nlmer(OUTCOME ~ CUE + (1| sub), data = pvc)"),
              CSS = list(css.table = '+font-size: 12;'))


# 4. compute random effects and save for compiling across PVC tasks ____________
rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",
        as.character(Sys.Date()), ".csv",
        sep = ""
    ))
randeffect.V <- compute_randomeffects(model.vicexpect, rand_savefname = rand_savefname, taskname,
                                      new_rand_names = c("rand_intercept", "rand_cue"),
                                      new_fix_names =  c("fix_intercept", "fix_cue"))
```

## Cognitive

### For the cognitive task, what is the effect of cue on outcome ratings? {.unlisted .unnumbered}

> Cue effects are significant even in the outcome rating domain. Note that the outcome ratings are measured after the stimulus delivery, and the cue-related data points are no longer visible on screen. 

```{r cognitive_iv-cue_dv-outcome, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# taskname = 'cognitive'
# ggplot_onefactor_pertask(taskname, subject_varkey, subject, exclude,
#                                      analysis_dir, iv, iv_keyword, dv, dv_keyword,
#                                      subjectwise_mean, group_mean, se,
#                                      xlab, ylim, ylab, ggtitle_phrase, print_lmer_output)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
taskname <- 'cognitive'


# 0. Summary and plot related keywords _________________________________________
subject <- "sub";
iv <- "cue_ordered";              dv <- "OUTCOME"
sub_mean <- "mean_per_sub";       group_mean <- "mean_per_sub_norm_mean"
se <- "se"
iv_keyword <- "cue";              dv_keyword <- "outcome"
ggtitle_phrase <- " - Outcome Rating"
ggtitle <- paste0(tools::toTitleCase(taskname), ggtitle_phrase, " (N = ", length(unique(data$sub)), ")");
title <- paste0(tools::toTitleCase(taskname), " - ", tools::toTitleCase(dv_keyword))
xlab <- "Cue type";               ylab <- "Outcome Ratings (degree)"
ylim <- c(-10,190);               w = 5; h = 3;
plot_savefname <- file.path(analysis_dir,
                            paste0("raincloud_task-", taskname,"_iv-", iv_keyword, 
                                   "_dv-rating-", dv_keyword,"_", as.character(Sys.Date()), ".png")
                            )
color <- c("#4575B4", "#D73027")


data <- pvc[pvc$task==taskname, ]


# 1. summary stats _____________________________________________________________
outcome_subjectwise <- meanSummary(data, c(subject, iv), dv)
outcome_groupwise <- cueR::summarySEwithin(
    data = outcome_subjectwise,
    measurevar = sub_mean, # variable created from above
    withinvars = c(iv), # iv
    idvar = subject
)


# 2. plot parameters _____________________________________________________________
g <- cueR::plot_cueexpectancy_onefactor(
        outcome_subjectwise, outcome_groupwise, iv,
        sub_mean, group_mean, se, subject, ggtitle, title, 
        xlab="", ylab, taskname, 
        w, h, dv_keyword, color, plot_savefname,
        expand_x = TRUE,
        xlim = c(NA, 3), ylim = c(-20, 200),
        x_scale_expansion = c(0, 0.5),
        x_hline_position = 2.5,
        x_hline_linetype = "dashed",
        x_hline_nudge_x = 0.1,
        x_hline_textsize = 3,
        legend_factor_levels = c("High cue", "Low cue"),
        legend_factor_colors = c("#D73027", "#4575B4" ),
        legend_geom_point_size = 4,
        legend_position = c(-0.1, 0.7),
        legend_widths = c(3, 1)
      )
grid::grid.draw(g)


# 3. mixed effects model _______________________________________________________
model.cogexpect <- lmer(OUTCOME ~ cue_ordered + (cue_ordered|sub), data = data)
sjPlot::tab_model(model.cogexpect,
              title = paste0(tools::toTitleCase(taskname), ": \nlmer(OUTCOME ~ CUE + (1| sub), data = pvc)"),
              CSS = list(css.table = '+font-size: 12;'))


# 4. compute random effects and save for compiling across PVC tasks ____________
rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",
        as.character(Sys.Date()), ".csv",
        sep = ""
    ))
randeffect.C <- compute_randomeffects(model.cogexpect, rand_savefname = rand_savefname, taskname,
                                      new_rand_names = c("rand_intercept", "rand_cue"),
                                      new_fix_names =  c("fix_intercept", "fix_cue"))
```




```{r random_effects_2, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# # test function
# rand_dir <- analysis_dir
# dir.create(rand_dir, showWarnings = FALSE, recursive = TRUE)
# dfP <- read.csv(file.path(
#     rand_dir,
#     paste("randeffect_task-pain", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
# ))
# dfV <- read.csv(file.path(
#     rand_dir,
#     paste("randeffect_task-vicarious", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
# ))
# dfC <- read.csv(file.path(
#     rand_dir,
#     paste("randeffect_task-cognitive", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
# ))
# 
# pvc <- merge_recurse(list(dfP, dfV, dfC))
# 
# save_fname <- file.path(
#     analysis_dir,
#     paste("randeffect_task-all_",
#         as.character(Sys.Date()), ".csv",
#         sep = ""
#     )
# )
# write.csv(pvc, save_fname, row.names = FALSE)
```


## Individual differences analysis: random cue effects

Using the random effects from the mixed effects model, I'm plotting the random effect of cue types per task.

> There is a linear relationship between random effects of cue across task domains. A participant with a greater cue effect in one task is likely to exhibit a large cue effect in another.

```{r random effects scatter plot, echo=FALSE, paged.print=FALSE}
# # load random effects data____________________________________________________
# rand_dir <- file.path(main_dir, "analysis", "mixedeffect", "model01_iv-cue_dv-expect", as.character(Sys.Date()))
# dir.create(rand_dir, showWarnings = FALSE, recursive = TRUE)
# dfP <- read.csv(file.path(
#     rand_dir,
#     paste("randeffect_task-pain", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
# ))
# dfV <- read.csv(file.path(
#     rand_dir,
#     paste("randeffect_task-vicarious", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
# ))
# dfC <- read.csv(file.path(
#     rand_dir,
#     paste("randeffect_task-cognitive", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
# ))


# combined random effects ______________________________________________________
pvc.randeffect <- rbind(randeffect.P, randeffect.V, randeffect.C)
pvc_rand_cue_subset <- subset(pvc.randeffect, select = c(task, subj, rand_cue))
pvc_rand_cue <- spread(pvc_rand_cue_subset, key = task, value = rand_cue)


# plot individually ____________________________________________________________
pv <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'vicarious', y = 'pain', p_acc = 0.001, r_acc = 0.01, limit_min = -15, limit_max = 15, label_position = 12)
vc <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'cognitive', y = 'vicarious', p_acc = 0.001, r_acc = 0.01, limit_min = -15, limit_max = 15, label_position = 12)
cp <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'pain', y = 'cognitive', p_acc = 0.001, r_acc = 0.01, limit_min = -15, limit_max = 15, label_position = 12)


# combine plots and add title __________________________________________________
plots <- ggpubr::ggarrange(pv, vc, cp, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob("individual differences\n - cue effects from expectation ratings", color = "black", face = "bold", size = 15))
plots

# save plot ____________________________________________________________________
# save_plotname <- file.path(
#     analysis_dir,
#     paste("randeffect_scatterplot_task-all_",
#         as.character(Sys.Date()), ".png",
#         sep = ""
#     )
# )
# ggsave(save_plotname, width = 10, height = 3)
```


