# [ beh ] outcome ~ stimulus_intensity {#ch04_outcome-stim}

## What is the purpose of this notebook? {.unlisted .unnumbered}
Here, I plot the outcome ratings as a function of stimulus intensity 
* Main model: `lmer(outcome_rating ~ stim)` 
* Main question: do outcome ratings differ as a function of stimulus intensity? We should expect to see a linear effect of stimulus intensity.
* If there is a main effect of cue on expectation ratings, does this cue effect differ depending on task type?
* IV: stim (high / med / low)
* DV: outcome rating

FIX: plot statistics in random effect plot - what is broken?

```{r load_libraries_3, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(psych)
library(car)
library(lme4)
library(lmerTest)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(rmarkdown)
library(stringr)
library(ICC)
library(gghalves)
## library(extraoperators)
##library(JWileymisc)
##library(multilevelTools)
library(ggpubr)
library(PupillometryR) # geom_flat_violin
#source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summaryse.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulatedata.R")
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

```{r parameters_3, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
print(main_dir)
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
```

```{r common_parameters_3, message=FALSE, warning=FALSE, paged.print=FALSE}
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_stimulus_type"; iv_keyword <- "stim"; dv <- "event04_actual_angle"; dv_keyword <- "outcome"
xlab <- ""; ylim = c(0,180); ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
subjectwise_mean <- "mean_per_sub"; group_mean <- "mean_per_sub_norm_mean"; se <- "se"
color_scheme <-     if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color_scheme <- c("#1B9E77", "#D95F02")
    } else {
        color_scheme <- c("#4575B4", "#D73027")
    }
print_lmer_output <- FALSE
ggtitle_phrase <- " - Outcome Rating (degree)"
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", paste0("model03_iv-",iv_keyword,"_dv-",dv_keyword), as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```

```{r ggplotfunction_3, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
ggplot_onefactor_pertask <- function(taskname, subject_varkey, subject, exclude,
                                     analysis_dir, iv, iv_keyword, dv, dv_keyword, 
                                     subjectwise_mean, group_mean, se,color_scheme,
                                     xlab, ylim, ylab, ggtitle_phrase, print_lmer_output) {
    ## designate where the lmer output lives
    model_savefname <- file.path(
        analysis_dir,paste("lmer_task-", taskname,"_iv-", iv_keyword, "_dv-rating-", dv_keyword,"_", as.character(Sys.Date()), ".txt",
            sep = ""))
      
    ## load data, run model, and exclude outliers
    data <- load_task_social_df(datadir, taskname, subject_varkey, iv, dv, exclude)
    data$subject = factor(data$src_subject_id)
    data = data[!is.na(data[, dv] ),] # removing NA values
    #print(length(unique(data$subject)))
    data <- data %>%
    mutate(ordered_iv = fct_relevel(.data[[iv]], 
            "low_stim", "med_stim", "high_stim"))
    cooksd <- lmer_onefactor_cooksd(data, taskname, "ordered_iv", dv, subject, dv_keyword, model_savefname, print_lmer_output) # run lmer
    influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data$subject)))))])
    data_screen <- data[-influential, ]
    
    ## summary statistics
    subjectwise <- meanSummary(data_screen, c(subject, "ordered_iv"), dv)
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = subjectwise_mean, # variable created from above
        withinvars = c("ordered_iv"), # iv
        idvar = "subject"
    )
    
    ## designate plot save location
    ggtitle <- paste0(str_to_title(taskname), ggtitle_phrase, " N = (", length(unique(data$subject)), ")");  
    title <- paste0(str_to_title(taskname), " - ", str_to_title(dv_keyword))
    w = 5; h = 3; 
    plot_savefname <- file.path(analysis_dir,
                                paste0("raincloud_task", taskname,"_iv-", iv_keyword, "_dv-rating-", dv_keyword,"_", as.character(Sys.Date()), ".png")
                                )

    
    # plot_rainclouds_onefactor
    p1 <- plot_halfrainclouds_onefactor(
        subjectwise, groupwise,
        "ordered_iv", subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name,ylim,
        w, h, dv_keyword, color_scheme, plot_savefname
    )
    
    p1 <-   p1 + 
      geom_hline(yintercept = 0, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 0, label = c("no sensation"), hjust = 0, nudge_x = 0.1, size = 3) +
      geom_hline(yintercept = 3, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 3, label = c("barely detectable"), hjust = 0, nudge_x = 0.1, size = 3) +
      geom_hline(yintercept = 10, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 10, label = c("weak"), hjust = 0, nudge_x = 0.1, size = 3) +
      geom_hline(yintercept = 30, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 30, label = c("moderate"), hjust = 0, nudge_x = 0.1, size = 3) +
      geom_hline(yintercept = 65, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 65, label = c("strong"), hjust = 0, nudge_x = 0.1, size = 3) +
      geom_hline(yintercept = 95, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 95, label = c("very strong"), hjust = 0, nudge_x = 0.1, size = 3) +
      geom_hline(yintercept = 180, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 180, label = c("strongest imaginable"), hjust = 0, nudge_x = 0.1, size = 3) +
      coord_cartesian(clip = 'off')+
      theme_classic() + 
      theme(legend.position = "none") 
    
    return(p1)
# randEffect$newcoef <- mapvalues(randEffect$term,
#     from = c(as.character(unique(randEffect$term)[1]),
#              as.character(unique(randEffect$term)[2])
#              ),
#     to = c("rand_intercept", paste0("rand_", iv_keyword))
# )
# 
# rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
# wide_rand <- spread(rand_subset, key = newcoef, value = condval)
# 
# wide_fix <- do.call(
#     "rbind",
#     replicate(nrow(wide_rand),
#         as.data.frame(t(as.matrix(fixEffect))),
#         simplify = FALSE
#     )
# )
# rownames(wide_fix) <- NULL
# new_wide_fix <- dplyr::rename(wide_fix,
#     fix_intercept = colnames(wide_fix)[1],
#     fix_reg = colnames(wide_fix)[2],
# )
# 
# total <- cbind(wide_rand, new_wide_fix)
# total$task <- taskname
# new_total <- total %>% dplyr::select(task, everything())
# new_total <- dplyr::rename(total, subj = grp)
# 
# rand_savefname <- file.path(
#     analysis_dir,
#     paste("randeffect_task-", taskname, "_",
#         as.character(Sys.Date()), "_outlier-cooksd.csv",
#         sep = ""
#     )
# )
# write.csv(new_total, rand_savefname, row.names = FALSE)

}
```

## Pain

### For the pain task, what is the effect of stimulus intensity on outcome ratings? {.unlisted .unnumbered}
[ INSERT DESCRIPTION ]
```{r pain_iv-stim_dv-outcome, echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
taskname = 'pain'
color_scheme = c("#FFA79A", "#CA5C4D", "#941100")
ggplot_onefactor_pertask(taskname, subject_varkey, subject, exclude,
                                     analysis_dir, iv, iv_keyword, dv, dv_keyword, 
                                     subjectwise_mean, group_mean, se, color_scheme,
                                     xlab, ylim, ylab, ggtitle_phrase, print_lmer_output)
```

## Vicarious
### For the vicarious task, what is the effect of stimulus intensity on outcome ratings? {.unlisted .unnumbered}
[ INSERT DESCRIPTION ]
```{r vicarious_iv-stim_dv-outcome, echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
taskname = 'vicarious'
color_scheme = c("#C6FF8A", "#63C76E", "#008F51")
ggplot_onefactor_pertask(taskname, subject_varkey, subject, exclude,
                                     analysis_dir, iv, iv_keyword, dv, dv_keyword, 
                                     subjectwise_mean, group_mean, se, color_scheme,
                                     xlab, ylim, ylab, ggtitle_phrase, print_lmer_output)
```

## Cognitive
### For the cognitive task, what is the effect of stimulus intensity on outcome ratings? {.unlisted .unnumbered}
[ INSERT DESCRIPTION ]
```{r cognitive_iv-stim_dv-outcome, echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
taskname = 'cognitive'
color_scheme = c("#8EA1FF", "#485DC8", "#011891")
ggplot_onefactor_pertask(taskname, subject_varkey, subject, exclude,
                                     analysis_dir, iv, iv_keyword, dv, dv_keyword, 
                                     subjectwise_mean, group_mean, se, color_scheme,
                                     xlab, ylim, ylab, ggtitle_phrase, print_lmer_output)
```

```{r random_effects_3, eval=FALSE, message=FALSE, warning=TRUE, include=FALSE, paged.print=FALSE}
# test function
rand_dir <- analysis_dir
dir.create(rand_dir, showWarnings = FALSE, recursive = TRUE)
dfP <- read.csv(file.path(
    rand_dir,
    paste("randeffect_task-pain", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
))
dfV <- read.csv(file.path(
    rand_dir,
    paste("randeffect_task-vicarious", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
))
dfC <- read.csv(file.path(
    rand_dir,
    paste("randeffect_task-cognitive", "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = "")
))

pvc <- merge_recurse(list(dfP, dfV, dfC))

save_fname <- file.path(
    analysis_dir,
    paste("randeffect_task-all_",
        as.character(Sys.Date()), ".csv",
        sep = ""
    )
)
write.csv(pvc, save_fname, row.names = FALSE)
```

## for loop
```{r}
combined_se_calc_cooksd <- data.frame()
analysis_dir <- file.path(
        main_dir,
        "analysis", "mixedeffect", "model04_iv-stim_dv-actual",as.character(Sys.Date())
    )
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)

# 1. [ PARAMETERS ]  __________________________________________________ # nolint
dv_keyword <- "actual"
xlab <- ""
ylab <- "judgment (degree)"
for (taskname in c("pain", "vicarious", "cognitive")) {
    ggtitle <- paste(taskname, " - actual judgment (degree)")
    title <- paste(taskname, " - actual")
    subject <- "src_subject_id"
    subject_varkey <- "src_subject_id"
    data <- load_task_social_df(datadir, 
        taskname = taskname,
        subject_varkey = "src_subject_id",
        
        iv = "param_cue_type",
        dv = "event04_actual_angle",
        exclude = "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
    )

    w <- 10
    h <- 6

    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
    # contrast code ________________________________________
    data$stim[data$event03_stimulus_type == "low_stim"] <- -0.5 # social influence task
    data$stim[data$event03_stimulus_type == "med_stim"] <- 0 # no influence task
    data$stim[data$event03_stimulus_type == "high_stim"] <- 0.5 # no influence task

    data$stim_factor <- factor(data$event03_stimulus_type)

    # contrast code 1 linear
    data$stim_con_linear[data$event03_stimulus_type == "low_stim"] <- -0.5
    data$stim_con_linear[data$event03_stimulus_type == "med_stim"] <- 0
    data$stim_con_linear[data$event03_stimulus_type == "high_stim"] <- 0.5

    # contrast code 2 quadratic
    data$stim_con_quad[data$event03_stimulus_type == "low_stim"] <- -0.33
    data$stim_con_quad[data$event03_stimulus_type == "med_stim"] <- 0.66
    data$stim_con_quad[data$event03_stimulus_type == "high_stim"] <- -0.33

    # social cude contrast
    data$social_cue[data$param_cue_type == "low_cue"] <- -0.5 # social influence task
    data$social_cue[data$param_cue_type == "high_cue"] <- 0.5 # no influence task

    stim_con1 <- "stim_con_linear"
    stim_con2 <- "stim_con_quad"
    iv1 <- "param_cue_type"
    #iv1 <- "social_cue"
    dv <- "event04_actual_angle"

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )
    cooksd <- lmer_onefactor_cooksd(
        data, taskname, iv, dv,
        subject, dv_keyword, model_savefname, print_lmer_output = TRUE
    )
    influential <- as.numeric(names(cooksd)[
        (cooksd > (4 / as.numeric(length(unique(data$src_subject_id)))))
    ])
    data_screen <- data[-influential, ]
    # [ PLOT ] reordering for plots _________________________ # nolint
    data_screen$stim_name[data_screen$param_stimulus_type == "high_stim"] <- "high"
    data_screen$stim_name[data_screen$param_stimulus_type == "med_stim"] <- "med"
    data_screen$stim_name[data_screen$param_stimulus_type == "low_stim"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data_screen$stim_ordered <- factor(
        data_screen$stim_name,
        levels = c("low", "med", "high")
    )
    model_iv1 <- "stim_ordered"
    #model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data_screen,
        c("src_subject_id", model_iv1), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1), idvar = "src_subject_id"
    )
    actual_groupwise$task <- taskname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402
    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)

    #  [ PLOT ] calculate mean and se  ----------------------------------------------------------------------------
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "src_subject_id"
    ggtitle <- paste(taskname, " - Actual Rating (degree) Cooksd removed")
    title <- paste(taskname, " - Actual")
    xlab <- ""
    ylab <- "ratings (degree)"
    ylim <- c(-10,190)
    dv_keyword <- "actual"
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027", "#D95F02" )
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_halfrainclouds_onefactor(
        actual_subjectwise, actual_groupwise, model_iv1,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )

    g <- g + 
      geom_hline(yintercept = 0, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 0, label = c("no sensation"), hjust = 0, nudge_x = 0.1, size = 3) +
      geom_hline(yintercept = 3, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 3, label = c("barely detectable"), hjust = 0, nudge_x = 0.1, size = 3) +
      geom_hline(yintercept = 10, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 10, label = c("weak"), hjust = 0, nudge_x = 0.1, size = 3) +
      geom_hline(yintercept = 30, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 30, label = c("moderate"), hjust = 0, nudge_x = 0.1, size = 3) +
      geom_hline(yintercept = 65, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 65, label = c("strong"), hjust = 0, nudge_x = 0.1, size = 3) +
      geom_hline(yintercept = 95, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 95, label = c("very strong"), hjust = 0, nudge_x = 0.1, size = 3) +
      geom_hline(yintercept = 180, size = 0.1, linetype = "dashed") + 
      geom_label(x = 3.5, y = 180, label = c("strongest imaginable"), hjust = 0, nudge_x = 0.1, size = 3) +
      coord_cartesian(clip = 'off')+
      theme_classic() + 
      theme(legend.position = "none") 
    
    ggsave(plot_savefname, width = w, height = h)
    
  g  

    # save fixed random effects _______________________________
#     randEffect$newcoef <- mapvalues(randEffect$term,
#         from = c("(Intercept)", "data[, iv]", 
#                  "data[, stim_con1]", "data[, stim_con2]", 
#                  "data[, iv]:data[, stim_con1]", 
#                  "data[, iv]:data[, stim_con2]"),
#         to = c("rand_intercept", "rand_cue", "rand_stimlin", 
#                "rand_stimquad", "rand_int_cue_stimlin", #"rand_int_cue_stimquad")
#     )
# 
#     #
#     # # The arguments to spread():
#     # # - data: Data object
#     # # - key: Name of column containing the new column names
#     # # - value: Name of column containing values
#     #
#     # # TODO: add fixed effects
#     #
#     rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
#     wide_rand <- spread(rand_subset, key = newcoef, value = condval)
#     wide_fix <- do.call(
#         "rbind",
#         replicate(nrow(wide_rand), #as.data.frame(t(as.matrix(fixEffect))),
#             simplify = FALSE
#         )
#     )
#     rownames(wide_fix) <- NULL
#     new_wide_fix <- dplyr::rename(wide_fix,
#         fix_intercept = `(Intercept)`, 
#         fix_cue = `social_cue`, # `data[, iv]`,
#         fix_stimulus_linear = `stim_con_linear`, # `data[, stim_con1]`,
#         fix_stimulus_quad = `stim_con_quad`, #`data[, stim_con2]`, 
#         fix_int_cue_stimlin = `social_cue:stim_con_linear`, #`data[, iv]:data[, stim_con1]`,
#         fix_int_cue_stimquad = `social_cue:stim_con_quad` #`data[, iv]:data[, stim_con2]`
#     )
# 
#     total <- cbind(wide_rand, new_wide_fix)
#     total$task <- taskname
#     new_total <- total %>% dplyr::select(task, everything())
#     new_total <- dplyr::rename(total, subj = grp)
# 
#     plot_savefname <- file.path(analysis_dir, 
#                                 paste("randeffect_task-", taskname, 
#                                       "_", as.character(Sys.Date()), #"_outlier-cooksd.csv", sep = ""))
#     write.csv(new_total, plot_savefname, row.names = FALSE)
# 
}

```

## Lineplot
```{r}
library(ggpubr)
DATA = as.data.frame(combined_se_calc_cooksd)
color = c( "#4575B4", "#D73027")
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "se"
dv_keyword = "actual"
p1 = plot_lineplot_onefactor(DATA, 'pain', 
               LINEIV1, MEAN, ERROR, color, xlab = "Stimulus intensity" , ylab= "Outcome rating", ggtitle = 'pain' )
p2 = plot_lineplot_onefactor(DATA,'vicarious', 
               LINEIV1, MEAN, ERROR, color,xlab = "Stimulus intensity" , ylab= "Outcome rating",ggtitle = 'vicarious')
p3 = plot_lineplot_onefactor(DATA, 'cognitive', 
               LINEIV1, MEAN, ERROR, color,xlab = "Stimulus intensity" , ylab= "Outcome rating",ggtitle = 'cognitive')
#grid.arrange(p1, p2, p3, ncol=3 , common.legend = TRUE)
ggpubr::ggarrange(p1,p2,p3,ncol = 3, nrow = 1, common.legend = TRUE,legend = "bottom")
plot_filename = file.path(analysis_dir,
                          paste('lineplot_task-all_rating-',dv_keyword,'.png', sep = ""))
ggsave(plot_filename, width = 15, height = 6)
```

## individual differences in outcome rating cue effect 
[ INSERT DESCRIPTION ]
```{r random_effects_scatter_plot_3, eval=FALSE, message=FALSE, warning=TRUE, include=FALSE}
pvc_rand_subset <- subset(pvc, select = c(task, subj, rand_stim))
pvc_rand <- spread(pvc_rand_subset, key = task, value = rand_stim)
# plot individually
# limit_min = -40, limit_max = 40,
pv <- plot_ggplot_correlation(data = pvc_rand, x = 'vicarious', y = 'pain', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 20, label_position = 38)
vc <- plot_ggplot_correlation(data = pvc_rand, x = 'cognitive', y = 'vicarious', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 20,  label_position = 38)
cp <- plot_ggplot_correlation(data = pvc_rand, x = 'pain', y = 'cognitive', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 20, label_position = 38)
# combine plots and add title
plots <- ggpubr::ggarrange(pv, vc, cp, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste0("individual differences\n - ", iv_keyword, " effects from ",dv_keyword" ratings"), color = "black", face = "bold", size = 15))
print(plots)
save_plotname <- file.path(
    analysis_dir,
    paste("randeffect_scatterplot_task-all_", 
        as.character(Sys.Date()), ".png",
        sep = ""
    )
)
ggsave(save_plotname, width = 10, height = 3)

```

