# [beh] outcome_rating ~ cue * stim {#ch05_outcome-cueXstim}

## What is the purpose of this notebook? {.unlisted .unnumbered}

Here, we want to test whether lmer is the equivalent of repeated measures anova

I plot the outcome ratings as a function of cue and stimulus intensity. 

* Main model: `lmer(outcome_rating ~ cue * stim)` 
* Main question: do outcome ratings differ as a function of cue type and stimulus intensity? 
* If there is a main effect of cue on outcome ratings, does this cue effect differ depending on task type?
* Is there an interaction between the two factors?
* IV: 
  - cue (high / low)
  - stim (high / med / low)
* DV: outcome rating

## load data

```{r load_libraries_4, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(psych)
library(car)
library(lme4)
library(lmerTest)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(rmarkdown)
library(stringr)
library(ICC)
library(gghalves)

library(ggpubr)
library(PupillometryR) # geom_flat_violin

# source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
# source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summaryse.R")
# source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulatedata.R")
# source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
file.sources = list.files(c("/Users/h/Documents/projects_local/cue_expectancy/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

```{r parameters_4, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
print(main_dir)
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
```

## lmer
```{r}
analysis_dir <- file.path(
    main_dir, "analysis",
    "mixedeffect", "model04_iv-cuecontrast_dv-outcome", as.character(Sys.Date()))
dir.create(analysis_dir, recursive = TRUE, showWarnings = FALSE)
taskname <- "pain"

    subject_varkey <- "src_subject_id"
    iv <- "param_cue_type"; iv_keyword <- "cue"
    dv <- "event04_actual_angle"
    dv_keyword <- "actual"
    subject <- "subject"
    xlab <- ""
    ylab <- "ratings (degree)"
    exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
    w <- 10
    h <- 6
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname, "_cue_on_rating-", dv_keyword, "_",
            as.character(Sys.Date()), ".txt",
            sep = ""
        )
    )
    # ___ 1) load data _______________________________________________________________ # nolint
    data <- load_task_social_df(datadir, taskname, subject_varkey, iv, dv, exclude)
    unique(data$src_subject_id)
    data$subject <- factor(data$src_subject_id)

    
    w <- 10
    h <- 6

    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
    # contrast code ________________________________________
    data$stim[data$event03_stimulus_type == "low_stim"] <- -0.5 # social influence task
    data$stim[data$event03_stimulus_type == "med_stim"] <- 0 # no influence task
    data$stim[data$event03_stimulus_type == "high_stim"] <- 0.5 # no influence task

    data$stim_factor <- factor(data$event03_stimulus_type)

    # contrast code 1 linear
    data$stim_con_linear[data$event03_stimulus_type == "low_stim"] <- -0.5
    data$stim_con_linear[data$event03_stimulus_type == "med_stim"] <- 0
    data$stim_con_linear[data$event03_stimulus_type == "high_stim"] <- 0.5

    # contrast code 2 quadratic
    data$stim_con_quad[data$event03_stimulus_type == "low_stim"] <- -0.33
    data$stim_con_quad[data$event03_stimulus_type == "med_stim"] <- 0.66
    data$stim_con_quad[data$event03_stimulus_type == "high_stim"] <- -0.33

    # social cude contrast
    data$social_cue[data$param_cue_type == "low_cue"] <- -0.5 # social influence task
    data$social_cue[data$param_cue_type == "high_cue"] <- 0.5 # no influence task


    stim_con1 <- "stim_con_linear"
    stim_con2 <- "stim_con_quad"
    iv1 <- "social_cue"
    dv <- "event04_actual_angle"
```


```{r}
fullmodel <- lmer(event04_actual_angle ~ 1+ social_cue + stim_con_linear + stim_con_quad + social_cue:stim_con_linear + social_cue:stim_con_quad
     + (1+ social_cue + stim_con_linear + stim_con_quad+ social_cue:stim_con_linear  + social_cue:stim_con_quad| src_subject_id), data=data)
summary(fullmodel)
```

## repeated measures
```{r}
################################################################################

data <- data %>%
  group_by(src_subject_id) %>%
  mutate(trial = row_number())

df <- data %>%
  group_by(src_subject_id,session_id, param_run_num, param_cond_type) %>%
  mutate(repeat_order = row_number()) %>%
  ungroup()

# long to wide
wide.df = df[c("src_subject_id","session_id","param_run_num", "param_cue_type", "param_stimulus_type", "repeat_order","event04_actual_angle" )] %>% 
   pivot_wider(names_from = c(param_cue_type, param_stimulus_type), values_from = event04_actual_angle) 

################################################################################
# average within subject


wide.ave <- wide.df %>%
  dplyr::group_by(src_subject_id) %>%
  dplyr::summarize(
    across(c(high_cue_high_stim, high_cue_med_stim, high_cue_low_stim, low_cue_high_stim, low_cue_med_stim, low_cue_low_stim), mean, na.rm = TRUE)
  )

################################################################################
# contrast coding
# modeling the average performance (intercept)
wide.ave$ave = (+1/6) * wide.ave$high_cue_high_stim + 
  (+1/6) * wide.ave$high_cue_med_stim + 
  (+1/6) * wide.ave$high_cue_low_stim + 
  (+1/6) * wide.ave$low_cue_high_stim + 
  (+1/6) * wide.ave$low_cue_med_stim + 
  (+1/6) * wide.ave$low_cue_low_stim 
t.ave = lm(wide.ave$ave ~ 1)
summary(t.ave)

# model :: cue effect
wide.ave$cue_effect = (+1/2) * wide.ave$high_cue_high_stim + 
  (+1/2) * wide.ave$high_cue_med_stim + 
  (+1/2) * wide.ave$high_cue_low_stim + 
  (-1/2) * wide.ave$low_cue_high_stim + 
  (-1/2) * wide.ave$low_cue_med_stim + 
  (-1/2) * wide.ave$low_cue_low_stim 
t.cue = lm(wide.ave$cue_effect ~ 1)
summary(t.cue)

# model :: stim effect
wide.ave$stim_effect = 
  (+1/2) * wide.ave$high_cue_high_stim + 
  (0) * wide.ave$high_cue_med_stim + 
  (-1/2) * wide.ave$high_cue_low_stim + 
  (+1/2) * wide.ave$low_cue_high_stim + 
  (0) * wide.ave$low_cue_med_stim + 
  (-1/2) * wide.ave$low_cue_low_stim 
t.stim = lm(wide.ave$stim_effect ~ 1)
summary(t.stim)

# model :: interaction
wide.ave$interaction = 
  (+1/4) * wide.ave$high_cue_high_stim + 
  (0) * wide.ave$high_cue_med_stim + 
  (-1/4) * wide.ave$high_cue_low_stim + 
  (-1/4) * wide.ave$low_cue_high_stim + 
  (0) * wide.ave$low_cue_med_stim + 
  (+1/4) * wide.ave$low_cue_low_stim 
t.int = lm(wide.ave$interaction ~ 1)
summary(t.int)


```


## converges with more than 36 observations?

```{r}
################################################################################
# filter subject with more than 36 trials
data
data <- data %>%
  group_by(src_subject_id) %>%
  mutate(trial = row_number())

df_filtered <- data %>%
  group_by(src_subject_id) %>%
  filter(n() > 36) %>%
  ungroup()


frequency_df <- df_filtered %>%
  dplyr::group_by(src_subject_id) %>%
  dplyr::summarize(frequency = n(), .groups = 'drop')

################################################################################
# run null model
# library(performance)
# model.null <- lmer(event04_actual_angle ~ 1+ social_cue + stim_con_linear + stim_con_quad + social_cue:stim_con_linear + social_cue:stim_con_quad
#      + (1| src_subject_id), data=df_filtered, REML = TRUE)
# performance::icc(model.null)

################################################################################
# model.36 <- lmer(event04_actual_angle ~ 1+ social_cue + stim_con_linear + stim_con_quad + social_cue:stim_con_linear + social_cue:stim_con_quad
#      + (1+ social_cue + stim_con_linear| src_subject_id), data=df_filtered, REML = TRUE)
# summary(model.36)

################################################################################
model.36full <- lmer(event04_actual_angle ~ 1+ social_cue + stim_con_linear + stim_con_quad + social_cue:stim_con_linear + social_cue:stim_con_quad
     + (1+ social_cue + stim_con_linear + stim_con_quad + social_cue:stim_con_linear + social_cue:stim_con_quad | src_subject_id), data=df_filtered, REML = TRUE)
summary(model.36full)
################################################################################
# deviance
# anova(model.36, model.36full, refit = FALSE)
```

```{r}
# random_intercepts <- getME(model.36full, "Z")
# random_intercepts
fixed_effects_matrix <- model.matrix(~ 1+ social_cue + stim_con_linear + stim_con_quad + social_cue:stim_con_linear + social_cue:stim_con_quad, data = df_filtered)
fixed_effects_matrix
# heatmap(fixed_effects_matrix, col=heat.colors(256), scale="column")
# Convert matrix to data frame
mat_df <- melt(t(fixed_effects_matrix))

ggplot(mat_df, aes(x=Var1, y=Var2, fill=value)) + 
    geom_tile()
```

```{r}
# Compute the covariance matrix
cov_matrix <- cov(fixed_effects_matrix)
# Base R image plot
image(cov_matrix, main = "Covariance Matrix of Fixed Effects")

# Alternatively, use the `heatmap()` function for a more detailed plot
heatmap(cov_matrix, main = "Covariance Matrix of Fixed Effects")
library(ggplot2)
library(reshape2)

# Ensure your matrix has proper row and column names
rownames(cov_matrix) <- colnames(fixed_effects_matrix)
colnames(cov_matrix) <- colnames(fixed_effects_matrix)

# Reshape the matrix to long format
long_cor_matrix <- melt(cov_matrix)

# Plot using ggplot2
ggplot(long_cor_matrix, aes(Var1, Var2, fill = value)) +
  geom_tile() +
  scale_fill_gradient2() +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  labs(x = "Regressors", y = "Regressors", fill = "Correlation", title = "Correlation Matrix of Fixed Effects")
# corrplot(long_cor_matrix)

# M<-cor(fixed_effects_matrix)
# corrplot(M, method="circle")
```


```{r}
library(lme4)
# For random intercepts
random_intercepts <- getME(model.36full, "Z")
# For random slopes
random_slopes <- getME(model.36full, "Zt")
dim(random_slopes)
library(Matrix)
par(mar = c(5, 4, 4, 2) + 0.1)
image(random_slopes, ylab = "Rows", xlab = "Columns", main = "Sparse Matrix Plot")
image(t(random_intercepts), ylab = "Rows", xlab = "Columns", main = "Sparse Matrix Plot")

```








