# beh :: per trial {#jepma}

## Overview

The purpose of this markdown is to benchmark the plots from Jepma et al. (2018).
Here, we plot the expectancy ratings and the actual ratings, with the high and low cues -- in one panel.

### Some thoughts, TODOs {.unlisted .unnumbered}

- plot 2. some runs were repeated or omitted for the subjects that have more than 72 trials. I need to identify that list and work on the behavioral data.
- I need to check whether the counterbalancing was done correctly.

```{r load_libraries_5, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
# library(lmSupport)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(stats)
library(ggpubr)
library(sjPlot)
library(sjmisc)
# library(sjlabelled)
library(lme4)
library(effectsize)
library(brms)
library(devtools)
library(visibly) #
library(plotly) #plot
library(scico) # plot

library(r2mlm)
library(cueR)
# main_dir = dirname(dirname(getwd()))
# file.sources = list.files(file.path(main_dir, "scripts/step02_R/utils"),
#                           pattern="*.R",
#                           full.names=TRUE,
#                           ignore.case=TRUE)
# sapply(file.sources,source,.GlobalEnv)
```



SANDBOX turn into function
```{r}

plot_per_trial <-
  function(subjectwise = trialorder_subjectwise_p2,
           iv = "trial_index", color_grp = "cue_ordered",
           dv = "rating_type", sub_mean = "mean_per_sub",
           se = "se", subject = "sub", ggtitle, title,
           xlabel = "No. of trials", ylabel = "Outcome Rating",
           taskname, ylim, w, h, dv_keyword = "rating",
           color_manual = c("high cue" = "#941100", "low cue" = "#5d5d5d"),
           save_fname, shape_manual = c("high cue" = 21, "low cue" = 16),
           total_n = NA) {
    
    standard_error <- function(data, mean_col, total_n) {
      se <- sd(data[[mean_col]], na.rm = TRUE) / sqrt(as.numeric(total_n))
      return(se)
    }
    # Pre-calculate ymin and ymax for error bars
    # subjectwise <- subjectwise %>%
    #   dplyr::mutate(
    #     ymin = .data[[sub_mean]] - standard_error(subjectwise, sub_mean, total_n),
    #     ymax = .data[[sub_mean]] + standard_error(subjectwise, sub_mean, total_n)
    #   )
    subjectwise$ymin <- subjectwise[[sub_mean]] - standard_error(subjectwise, sub_mean, subject)
    subjectwise$ymax <- subjectwise[[sub_mean]] + standard_error(subjectwise, sub_mean, subject)

    g <- ggplot(data = subjectwise,
                aes_string(
                  x = iv,
                  y = sub_mean,
                  color = color_grp,
                  group = dv
                )) +
      geom_point(
        data = subjectwise,
        aes(
          shape = as.character(dv),
          x = iv,
          y = sub_mean,
          group = dv,
          #color = cue_ordered
        ),
        
        size = 2.5
      ) +
      scale_shape_manual(values = c(16, 21)) +
      
      # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
      geom_errorbar(aes(ymin = ymin, ymax = ymax), width = 0.1, size = 0.5) +
      # geom_errorbar(
      #   data = subjectwise,
      #   aes(
      #     x = as.numeric(iv),
      #     y = sub_mean,
      #     group = dv,
      #     colour = color_grp,
      #     ymin = ymin,
      #     #sub_mean - sd/sqrt(as.numeric(total_n)),
      #     ymax = ymax #sub_mean + sd/sqrt(as.numeric(total_n))
      #   ),
      #   width = .1,
      #   size = 0.5
      # ) +
      scale_color_manual(values = color_manual) +
      xlab(xlabel) +
      ylab(ylabel) +
      labs(title = paste(taskname, "(N = ", as.numeric(total_n), ")")) +
      ylim(0, 120) +
      theme_classic2() +
      theme(aspect.ratio = .7) +
      theme(
        axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 15),
        axis.title.y = element_text(size = 15)
      )
    return(g)
  }
```

load data and combine participant data

```{r load_data_and_exclude_m1}
# main_dir = dirname(dirname(getwd()))
# datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model06_iv-cue-trial_dv-expect-actual", as.character(Sys.Date()))
# dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
# subject_varkey <- "src_subject_id"
# iv <- "param_cue_type"
# taskname <- "pain"
# exclude <- "sub-0001"
# data <- cueR::df_load_beh(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
# data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
```




```{r}
# 1. load data and rename columns ______________________________________________
df <- cueR::df_load_beh(datadir, taskname = taskname, subject_varkey = "src_subject_id", iv = "param_cue_type", dv = "event02_expect_angle", exclude = "sub-0001")
df <- cueR::simple_contrast_beh(df)

column_mapping <- c("event04_actual_angle" = "OUTCOME", 
                    "event02_expect_angle" = "EXPECT", 
                    "event02_expect_RT" = "EXPECT_RT", 
                    "event04_actual_RT" = "OUTCOME_RT", 
                    "src_subject_id" = "sub",
                    "session_id" = "ses")
df <- cueR::df_rename_columns(df, column_mapping)
# dropping NA values
df <- df[!is.na(df$OUTCOME), ]

```


## What's the corrleation across expectation, outcome ratings and Reaction time?
There could be a correlation between higher outcome ratings and faster reaction times, or not. Let's check what the pattern looks like
```{r}
# df(df, package = 'visibly')

myvars <- names(df) %in%
  c( "EXPECT", "EXPECT_RT", "OUTCOME", "OUTCOME_RT", "event01_cue_onset")
newdata <- data[myvars]
data_naomit <- na.omit(newdata)
cor_matrix = cor(data_naomit)
visibly::corr_heat(cor_matrix)
```


## Are the fixation durations somewhat orthogonal?
There are four jittered fixations in this experiment. We want to make sure that the distribution of these jitters are NOT correlated
* ITI: intertrial interval
* ISI01: presented after cue, prior to expectation rating, 
* ISI02: presented after expectation rating, prior to stimulus delivery
* ISI03: presented after stimulus delivery, prior to outcome rating
```{r}
ISIvars <- names(df) %in%
  c(  "ITI_duration", "ISI01_duration", "ISI02_duration", "ISI03_duration")
ISIdata <- df[ISIvars]
summary(ISIdata)
ISIdata_naomit <- na.omit(ISIdata)
ISIcor_matrix = cor(ISIdata_naomit)
corr_heat(ISIcor_matrix)
```


## What is the VIF of expectation ratings, expectation reaction time and outcome rating reaction time?
```{r}
car::vif(lm(OUTCOME ~  EXPECT + EXPECT_RT + OUTCOME_RT, dat = data_naomit))

```

## Per run, what is the average rating pattern across trials?
plot 1 - one run, average across participants

> Expectation ratings have a larger range than outcome ratings. Luckly, 

The script (hidden) processes experimental data from a study involving trials, cues, and stimuli. It calculates and visualizes how ratings (EXPECT and OUTCOME) vary across trials, taking into account the type of cue (high or low) and differences between subjects. The final plot shows these relationships, with clear visual distinctions between different categories of data.

```{r transform data to longform, echo=FALSE}

# subject # run # param_cue # param_stim # rating_type # rating_value

data_trial= df %>%
  arrange(sub, ses, param_run_num) %>%
  group_by(sub) %>%
  mutate(trial_index = rep_len(1:12, length.out = n()))
# convert to long dataframe ____________________________________________________
data_long = data_trial %>%
  pivot_longer(cols = c('EXPECT', 'OUTCOME'),
               names_to = "rating_type",
               values_to = "rating_value")

# rename variables and labels __________________________________________________
data_long$stim_name <- NA
data_long$rating_type <- factor(data_long$rating_type)
data_long$trial_index <- factor(data_long$trial_index)

data_long$cue_name[data_long$param_cue_type == "high_cue"] <- "high cue"
data_long$cue_name[data_long$param_cue_type == "low_cue"] <- "low cue"

data_long$stim_name[data_long$param_stimulus_type == "high_stim"] <- "high"
data_long$stim_name[data_long$param_stimulus_type == "med_stim"] <- "med"
data_long$stim_name[data_long$param_stimulus_type == "low_stim"] <- "low"

data_long$stim_ordered <- factor(
    data_long$stim_name,
    levels = c("low", "med", "high")
)
data_long$cue_ordered <- factor(
    data_long$cue_name,
    levels = c("low cue", "high cue")
)
subject <- "sub"
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"
rating <- "rating_type"
dv <- "rating_value"
    
# summary statistics ___________________________________________________________
trialorder_subjectwise <- meanSummary(
    data_long,
    c(subject, model_iv2, rating, "trial_index"), dv
)

subjectwise_naomit <- na.omit(trialorder_subjectwise)

trialorder_groupwise <- summarySEwithin(
    data = subjectwise_naomit,
    measurevar = "mean_per_sub",
    withinvars = c("cue_ordered", "rating_type",  "trial_index"), idvar = subject
)

# subset summary statistics ___________________________________________________________
trialorder_subjectwise$rating_type_key <- trialorder_subjectwise$rating_type
trialorder_groupwise$rating_type_key <- trialorder_groupwise$rating_type
actual_trialorder_groupwise <- trialorder_groupwise[which(trialorder_groupwise$rating_type_key == "OUTCOME"),]
expect_trialorder_groupwise <-trialorder_groupwise[which(trialorder_groupwise$rating_type_key == "EXPECT"),]
actual_trialorder_subjectwise <- trialorder_subjectwise[which(trialorder_subjectwise$rating_type_key == "OUTCOME"),]
expect_trialorder_subjectwise <-trialorder_subjectwise[which(trialorder_subjectwise$rating_type_key == "EXPECT"),]

# plot  ________________________________________________________________________
# * dataset: trialorder_groupwise
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"

g <- ggplot(
  data = trialorder_groupwise,
  aes(
    x = trial_index,
    y = mean_per_sub_norm_mean,
    color = cue_ordered,
    group = rating_type_key
  )
) +
  geom_point(
    data = trialorder_groupwise,
    aes(
      shape = as.character(rating_type_key),
      x = trial_index,
      y = mean_per_sub_norm_mean,
      group = rating_type_key,
    ),
    size = 3
  ) +
  scale_shape_manual(values = c("OUTCOME" = 16, "EXPECT" = 21)) +
  
  geom_errorbar(
    data = trialorder_groupwise,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      group = rating_type_key,
      colour = cue_ordered,
      ymin = mean_per_sub_norm_mean - se,
      ymax = mean_per_sub_norm_mean + se
    ),
    width = .01,
    linewidth = 0.5
  ) +
  scale_color_manual(values = c("high cue" = "red",
                                "low cue" = "blue")) +
  xlab("No. of trials") +
  ylab("Rating") +
  ylim(0, 100) +
  theme_classic() +
  theme(
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 15),
    axis.title.y = element_text(size = 15)
  )
g
```


## What is the distribution across all runs, i.e. 72 trials? 
plot 2 - average across participant, but spread all 6 runs in one x axis

load data and combine participant data
1) check the number of trials per participant
2) flag participants with 72 trials
I'm plotting all of the trials per participant. In this case, there is no trialwise variability, because we're plotting all 72 trials.
Averaging across participants will be the only source of variability, reflected in the error bars

>  What is the pattern for outcome and expectation ratings?
> How is does this pattern differ depending on high vs low cues?
> 1) As a sanity check, high cues leads to higher outcome ratings, compared to lower outcome ratings. 
> 2) Within high cues, expectations ratings are higher than outcome ratings -- i.e. compensating for the high expectations 
> 3) Within low cues, expectation ratings are lower than outcome ratings -- i.e. compenstation for more painful than expected experience, thus restuling in higher outcome ratings 
> 4) the difference between expectation and outcome rating is smaller in the low cue condition than the high cue condition. ")
        
```{r p2 check number of trials per participant}

# 1. count trial numbers across all runs _______________________________________
data_p2= df %>%
  arrange(sub) %>%
  group_by(sub) %>%
  mutate(trial_index = row_number())
# df_clean <- data_p2[complete.cases(data_p2$event02_expect_angle), ]
df_clean <- data_p2[complete.cases(data_p2$OUTCOME), ]

# 2. Check number of features related to trials  _____________________________
# check if every participant has maximum of 72 trials. Anything beyond that is erroneous

# ___ 1) Calculate the maximum row number for each participant
max_rows <- aggregate(trial_index ~ src_subject_id, data_p2, max)

# ___ 2) Check if any participant's maximum row number is not 72
count_trial <- df_clean %>% count("src_subject_id")
morethan72trials <- count_trial[count_trial$freq > 72,]$src_subject_id
output_html <- paste0("<strong>Participants with more than 72 trials (error check):</strong><br/>",
                      paste(morethan72trials, collapse = ", "))
htmltools::HTML(output_html)

# ___ 3) Check partiicpants with more than 60 trials
morethan60trials <- count_trial[count_trial$freq > 60,]$src_subject_id
output_html <- paste0("<strong>Participants with more than 60 trials:</strong><br/>",
                      paste(morethan60trials, collapse = ", "))
htmltools::HTML(output_html)


# 3. convert subset of participants to long form _______________________________
data_p2_long = df_clean %>%
  pivot_longer(cols = c('EXPECT', 'OUTCOME'),
               names_to = "rating_type",
               values_to = "rating_value")


# 4. convert column names ______________________________________________________
data_p2_long$cue_name <- NA
data_p2_long$stim_name <- NA
data_p2_long$cue_name[data_p2_long$param_cue_type == "high_cue"] <- "high cue"
data_p2_long$cue_name[data_p2_long$param_cue_type == "low_cue"] <- "low cue"

data_p2_long$stim_name[data_p2_long$param_stimulus_type == "high_stim"] <- "high"
data_p2_long$stim_name[data_p2_long$param_stimulus_type == "med_stim"] <- "med"
data_p2_long$stim_name[data_p2_long$param_stimulus_type == "low_stim"] <- "low"

data_p2_long$stim_ordered <- factor(
    data_p2_long$stim_name,
    levels = c("low", "med", "high")
)
data_p2_long$cue_ordered <- factor(
    data_p2_long$cue_name,
    levels = c("low cue", "high cue")
)
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"
rating <- "rating_type"
dv <- "rating_value"


# 5. summary statistics ________________________________________________________
trialorder_subjectwise_p2 <- meanSummary(
    data_p2_long,
    c(model_iv2, rating, "trial_index"), dv
)

subjectwise_naomit_p2 <- na.omit(trialorder_subjectwise_p2)
# NOTE: we can have group wise summary statistics, given that the trial numbers. 1 ~ 72 happen only once for a given pariticpant
# in other words, there are no within subject statistics for 72 trials

# 6. plot ______________________________________________________________________
# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 <- "trial_index"
iv2 <- "cue_ordered"

library(ggrepel)

g <- ggplot(
  data = trialorder_subjectwise_p2,
  aes(x = trial_index,
      y = mean_per_sub,
      color = cue_ordered,
      group = rating_type
      )
  ) +

    geom_point(
    data = trialorder_subjectwise_p2,
    aes(
      shape = as.character(rating_type),
      x = trial_index,
      y = mean_per_sub,
      group = rating_type
      ),

    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  geom_errorbar(
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub,
      group = rating_type,
      colour = cue_ordered,
      ymin = mean_per_sub - sd/sqrt(length(unique(data_p2_long$src_subject_id))),
      ymax = mean_per_sub + sd/sqrt(length(unique(data_p2_long$src_subject_id)))
      ), width = .1, size = 0.5
    ) +
  scale_color_manual(values = c("high cue" = "red",
                                "low cue" = "blue")) +
  xlab("No. of trials") +
  ylab("Outcome Rating") +
  labs(title = paste(taskname, "- What is the pattern for outcome and expectation ratings?\nHow is does this pattern differ depending on high vs low cues?"),
        subtitle = "1) As a sanity check, high cues leads to higher outcome ratings, compared to lower outcome ratings. 2) Within high cues, expectations ratings are higher than outcome ratings -- i.e. compensating for the high expectations 3) Within low cues, expectation ratings are lower than outcome ratings -- i.e. compenstation for more painful than expected experience, thus restuling in higher outcome ratings 4) the difference between expectation and outcome rating is smaller in the low cue condition than the high cue condition. ")+
  ylim(0,120) +
  theme_classic2() +

  theme(aspect.ratio = .7) +
    theme(    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 15),
    axis.title.y = element_text(size = 15))
g
```


## What are the patterns of trials PER TASK?

### pain
```{r echo=FALSE}
taskname <- "pain"

# 1. load data _________________________________________________________________
df <- cueR::df_load_beh(datadir, taskname = taskname, subject_varkey = "src_subject_id", iv = "param_cue_type", dv = "event02_expect_angle", exclude = "sub-0001")
df <- cueR::simple_contrast_beh(df)

column_mapping <- c("event04_actual_angle" = "OUTCOME", 
                    "event02_expect_angle" = "EXPECT", 
                    "event02_expect_RT" = "EXPECT_RT", 
                    "event04_actual_RT" = "OUTCOME_RT", 
                    "src_subject_id" = "sub",
                    "session_id" = "ses")
df <- cueR::df_rename_columns(df, column_mapping)


# 2. dropping NA values ________________________________________________________
data_p2 <- df %>%
  arrange(sub) %>%
  group_by(sub) %>%
  mutate(trial_index = row_number())

df_clean <- data_p2[complete.cases(data_p2$OUTCOME), ]


# 3. Find participants with a column maximum value greater than 60 _____________
max_values <- aggregate(df_clean$trial_index, by = list(df_clean$sub), FUN = max) # Calculate the maximum value for each participant
included_ids <- max_values[(max_values$x > 59) & (max_values$x < 73), "Group.1"] # Get IDs with maximum value greater than 60
df_included <- df_clean[df_clean$src_subject_id %in% included_ids, ] # Subset the dataframe

# Subset the data frame to include only the listed IDs
data_p2_long = df_clean %>%
  pivot_longer(cols = c('EXPECT', 'OUTCOME'),
               names_to = "rating_type",
               values_to = "rating_value")


# 4. rename columns ____________________________________________________________
data_p2_long$stim_name <- NA
data_p2_long <- data_p2_long[data_p2_long$src_subject_id %in% included_ids, ]

data_p2_long$cue_name[data_p2_long$param_cue_type == "high_cue"] <- "high cue"
data_p2_long$cue_name[data_p2_long$param_cue_type == "low_cue"] <- "low cue"

data_p2_long$stim_name[data_p2_long$param_stimulus_type == "high_stim"] <- "high"
data_p2_long$stim_name[data_p2_long$param_stimulus_type == "med_stim"] <- "med"
data_p2_long$stim_name[data_p2_long$param_stimulus_type == "low_stim"] <- "low"

data_p2_long$stim_ordered <- factor(data_p2_long$stim_name,
                                    levels = c("low", "med", "high"))
data_p2_long$cue_ordered <- factor(data_p2_long$cue_name,
                                   levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"
rating <- "rating_type"
dv <- "rating_value"

    
# 5. summary statistic _________________________________________________________
trialorder_subjectwise_p2 <- meanSummary(
    data_p2_long,
    c( model_iv2, rating, "trial_index"), dv
)
subjectwise_naomit_p2 <- na.omit(trialorder_subjectwise_p2)

# 6. plot ______________________________________________________________________
# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

g <- ggplot(
  data = trialorder_subjectwise_p2,
  aes(x = trial_index,
      y = mean_per_sub,
      color = cue_ordered,
      group = rating_type
      )
  ) +
    geom_point(
    data = trialorder_subjectwise_p2,
    aes(
      shape = as.character(rating_type),
      x =trial_index,
      y = mean_per_sub,
      group = rating_type
      ),

    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  geom_errorbar(
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub,
      group = rating_type,
      colour = cue_ordered,
      ymin = mean_per_sub - sd/sqrt(length(unique(data_p2_long$src_subject_id))),
      ymax = mean_per_sub + sd/sqrt(length(unique(data_p2_long$src_subject_id)))
      ), width = .1, size = 0.5
    ) +
  scale_color_manual(values = c("high cue" = "#941100",
                                "low cue" = "#5D5C5C")) +
  xlab("No. of trials") +
  ylab("Rating") +
  labs(title = paste(tools::toTitleCase(taskname), "(N = ", length(unique(data_p2_long$src_subject_id)), ")"))+
  ylim(0,120) +
  theme_classic2() +
  theme(aspect.ratio = .7) +
  theme(
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 15),
    axis.title.y = element_text(size = 15)
  )
g

```

### vicarious

```{r echo=FALSE}

taskname <- "vicarious"

# 1. load data _________________________________________________________________
df <- cueR::df_load_beh(datadir, taskname = taskname, subject_varkey = "src_subject_id", iv = "param_cue_type", dv = "event02_expect_angle", exclude = "sub-0001")
df <- cueR::simple_contrast_beh(df)

column_mapping <- c("event04_actual_angle" = "OUTCOME", 
                    "event02_expect_angle" = "EXPECT", 
                    "event02_expect_RT" = "EXPECT_RT", 
                    "event04_actual_RT" = "OUTCOME_RT", 
                    "src_subject_id" = "sub",
                    "session_id" = "ses")
df <- cueR::df_rename_columns(df, column_mapping)


# 2. dropping NA values ________________________________________________________
data_p2 <- df %>%
  arrange(sub) %>%
  group_by(sub) %>%
  mutate(trial_index = row_number())

df_clean <- data_p2[complete.cases(data_p2$OUTCOME), ]


# 3. Find participants with a column maximum value greater than 60 _____________
max_values <- aggregate(df_clean$trial_index, by = list(df_clean$sub), FUN = max) # Calculate the maximum value for each participant
included_ids <- max_values[(max_values$x > 59) & (max_values$x < 73), "Group.1"] # Get IDs with maximum value greater than 60
df_included <- df_clean[df_clean$src_subject_id %in% included_ids, ] # Subset the dataframe

# Subset the data frame to include only the listed IDs
data_p2_long = df_clean %>%
  pivot_longer(cols = c('EXPECT', 'OUTCOME'),
               names_to = "rating_type",
               values_to = "rating_value")


# 4. rename columns ____________________________________________________________
data_p2_long$stim_name <- NA
data_p2_long <- data_p2_long[data_p2_long$src_subject_id %in% included_ids, ]

data_p2_long$cue_name[data_p2_long$param_cue_type == "high_cue"] <- "high cue"
data_p2_long$cue_name[data_p2_long$param_cue_type == "low_cue"] <- "low cue"

data_p2_long$stim_name[data_p2_long$param_stimulus_type == "high_stim"] <- "high"
data_p2_long$stim_name[data_p2_long$param_stimulus_type == "med_stim"] <- "med"
data_p2_long$stim_name[data_p2_long$param_stimulus_type == "low_stim"] <- "low"

data_p2_long$stim_ordered <- factor(data_p2_long$stim_name,
                                    levels = c("low", "med", "high"))
data_p2_long$cue_ordered <- factor(data_p2_long$cue_name,
                                   levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"
rating <- "rating_type"
dv <- "rating_value"

    
# 5. summary statistic _________________________________________________________
trialorder_subjectwise_p2 <- meanSummary(
    data_p2_long,
    c( model_iv2, rating, "trial_index"), dv
)
subjectwise_naomit_p2 <- na.omit(trialorder_subjectwise_p2)

# 6. plot ______________________________________________________________________
# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

g <- ggplot(
  data = trialorder_subjectwise_p2,
  aes(x = trial_index,
      y = mean_per_sub,
      color = cue_ordered,
      group = rating_type
      )
  ) +
    geom_point(
    data = trialorder_subjectwise_p2,
    aes(
      shape = as.character(rating_type),
      x =trial_index,
      y = mean_per_sub,
      group = rating_type,
      #color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub,
      group = rating_type,
      colour = cue_ordered,
      ymin = mean_per_sub - sd/sqrt(length(unique(data_p2_long$src_subject_id))),
      ymax = mean_per_sub + sd/sqrt(length(unique(data_p2_long$src_subject_id)))
      ), width = .1, size = 0.5
    ) +
  scale_color_manual(values = c("high cue" = "#009411",
                                "low cue" = "#5D5C5C")) +
  xlab("No. of trials") +
  ylab("Rating") +
  labs(title = paste(tools::toTitleCase(taskname), "(N = ", length(unique(data_p2_long$src_subject_id)), ")"))+
  ylim(0,120) +
  theme_classic2() +
  theme(aspect.ratio = .7) +
  theme(
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 15),
    axis.title.y = element_text(size = 15)
  )
g
```

### cognitive

```{r echo=FALSE}
taskname <- "cognitive"

# 1. load data _________________________________________________________________
df <- cueR::df_load_beh(datadir, taskname = taskname, subject_varkey = "src_subject_id", iv = "param_cue_type", dv = "event02_expect_angle", exclude = "sub-0001")
df <- cueR::simple_contrast_beh(df)

column_mapping <- c("event04_actual_angle" = "OUTCOME", 
                    "event02_expect_angle" = "EXPECT", 
                    "event02_expect_RT" = "EXPECT_RT", 
                    "event04_actual_RT" = "OUTCOME_RT", 
                    "src_subject_id" = "sub",
                    "session_id" = "ses")
df <- cueR::df_rename_columns(df, column_mapping)


# 2. dropping NA values ________________________________________________________
data_p2 <- df %>%
  arrange(sub) %>%
  group_by(sub) %>%
  mutate(trial_index = row_number())

df_clean <- data_p2[complete.cases(data_p2$OUTCOME), ]


# 3. Find participants with a column maximum value greater than 60 _____________
max_values <- aggregate(df_clean$trial_index, by = list(df_clean$sub), FUN = max) # Calculate the maximum value for each participant
included_ids <- max_values[(max_values$x > 59) & (max_values$x < 73), "Group.1"] # Get IDs with maximum value greater than 60
df_included <- df_clean[df_clean$src_subject_id %in% included_ids, ] # Subset the dataframe

# Subset the data frame to include only the listed IDs
data_p2_long = df_clean %>%
  pivot_longer(cols = c('EXPECT', 'OUTCOME'),
               names_to = "rating_type",
               values_to = "rating_value")


# 4. rename columns ____________________________________________________________
data_p2_long$stim_name <- NA
data_p2_long <- data_p2_long[data_p2_long$src_subject_id %in% included_ids, ]

data_p2_long$cue_name[data_p2_long$param_cue_type == "high_cue"] <- "high cue"
data_p2_long$cue_name[data_p2_long$param_cue_type == "low_cue"] <- "low cue"

data_p2_long$stim_name[data_p2_long$param_stimulus_type == "high_stim"] <- "high"
data_p2_long$stim_name[data_p2_long$param_stimulus_type == "med_stim"] <- "med"
data_p2_long$stim_name[data_p2_long$param_stimulus_type == "low_stim"] <- "low"

data_p2_long$stim_ordered <- factor(data_p2_long$stim_name,
                                    levels = c("low", "med", "high"))
data_p2_long$cue_ordered <- factor(data_p2_long$cue_name,
                                   levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"
rating <- "rating_type"
dv <- "rating_value"

    
# 5. summary statistic _________________________________________________________
trialorder_subjectwise_p2 <- meanSummary(
    data_p2_long,
    c( model_iv2, rating, "trial_index"), dv
)
subjectwise_naomit_p2 <- na.omit(trialorder_subjectwise_p2)

# 6. plot ______________________________________________________________________
# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

g <- ggplot(
  data = trialorder_subjectwise_p2,
  aes(x = trial_index,
      y = mean_per_sub,
      color = cue_ordered,
      group = rating_type
      )
  ) +
    geom_point(
    data = trialorder_subjectwise_p2,
    aes(
      shape = as.character(rating_type),
      x =trial_index,
      y = mean_per_sub,
      group = rating_type
      ),

    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  geom_errorbar(
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub,
      group = rating_type,
      colour = cue_ordered,
      ymin = mean_per_sub - sd/sqrt(length(unique(data_p2_long$src_subject_id))),
      ymax = mean_per_sub + sd/sqrt(length(unique(data_p2_long$src_subject_id)))
      ), width = .1, size = 0.5
    ) +
  scale_color_manual(values = c("high cue" = "navy",
                                "low cue" = "#5D5C5C")) +
  xlab("No. of trials") +
  ylab("Rating") +
  labs(title = paste(tools::toTitleCase(taskname), "(N = ", length(unique(data_p2_long$src_subject_id)), ")"))+
  ylim(0,120) +
  theme_classic2() +
  theme(aspect.ratio = .7) +
  theme(
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 15),
    axis.title.y = element_text(size = 15)
  )
g

```

## within subject vicarious

```{r echo=FALSE}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "vicarious"

ylab <- "Outcome Ratings (degree)"
subject <- "subject"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999" #/ "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"
data <- data.frame()
# load data _____________________________________
data <- df_load_beh(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
data_p2= data %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())

df_clean <- data_p2[complete.cases(data_p2$event02_expect_angle), ]

count_trial <- df_clean %>% count("src_subject_id")
# included_ids <- count_trial[(count_trial$freq > 60) & (count_trial$freq < 73),]$src_subject_id

# Subset the data frame to include only the listed IDs

data_p2_long = df_clean %>%
  pivot_longer(cols = c('event02_expect_angle', 'event04_actual_angle'),
               names_to = "rating_type",
               values_to = "rating_value")
# data_p2_long <- data_p2_long[data_p2_long$src_subject_id %in% included_ids, ]

    data_p2_long$cue_name[data_p2_long$param_cue_type == "high_cue"] <- "high cue"
    data_p2_long$cue_name[data_p2_long$param_cue_type == "low_cue"] <- "low cue"

    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "high_stim"] <- "high"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "med_stim"] <- "med"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "low_stim"] <- "low"

    data_p2_long$stim_ordered <- factor(
        data_p2_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_p2_long$cue_ordered <- factor(
        data_p2_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    rating <- "rating_type"
    dv <- "rating_value"
    subject = "trial_index"
    trialorder_subjectwise_p2 <- meanSummary(
        data_p2_long,
        c( model_iv2, rating, model_iv1, "trial_index"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
    # subjectwise_naomit_p2$c
    # subjectwise_naomit_p2 <- na.omit(trialorder_subjectwise_p2)
    trialorder_groupwise_p2 <- summarySEwithin(
        data = trialorder_subjectwise_p2,
        measurevar = "mean_per_sub",
        withinvars = c("cue_ordered", "trial_index", "rating_type"),
    )

# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_groupwise_p2,
  aes(x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      color = cue_ordered,
      # group = rating_type
      linetype = as.factor(rating_type)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_groupwise_p2,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      color = cue_ordered,
      linetype = as.factor(rating_type)
      )) +
    geom_point(
    data = trialorder_groupwise_p2,
    aes(
      shape = as.character(rating_type),
      x =as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      linetype = as.factor(rating_type),
      color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub_mean,
      # group = rating_type,
      colour = cue_ordered,
      linetype = as.factor(rating_type),
      ymin = mean_per_sub_norm_mean - se,
      ymax = mean_per_sub_norm_mean + se), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high cue" = "red", #"#009411",
                                "low cue" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("Outcome Rating") +
  labs(title = paste(taskname, "(N = ", length(unique(data_p2_long$src_subject_id)), ")"))+
  ylim(0,120) +
  theme_classic2() +
theme(aspect.ratio = .7) +
        theme(    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 15),
    axis.title.y = element_text(size = 15))
g
```

## Tor request -- only outcome ratings. 3 tasks

### pain

```{r echo=FALSE}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "pain"

ylab <- "Outcome Ratings (degree)"
subject <- "subject"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999" #/ "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"
data <- data.frame()
# load data _____________________________________
data <- df_load_beh(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
data_p2= data %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())

df_clean <- data_p2[complete.cases(data_p2$event02_expect_angle), ]

count_trial <- df_clean %>% count("src_subject_id")
# included_ids <- count_trial[(count_trial$freq > 60) & (count_trial$freq < 73),]$src_subject_id

# Subset the data frame to include only the listed IDs

data_p2_long = df_clean %>%
  pivot_longer(cols = c( 'event04_actual_angle'),
               names_to = "rating_type",
               values_to = "rating_value")
# data_p2_long <- data_p2_long[data_p2_long$src_subject_id %in% included_ids, ]

    data_p2_long$cue_name[data_p2_long$param_cue_type == "high_cue"] <- "high cue"
    data_p2_long$cue_name[data_p2_long$param_cue_type == "low_cue"] <- "low cue"

    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "high_stim"] <- "high"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "med_stim"] <- "med"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "low_stim"] <- "low"

    data_p2_long$stim_ordered <- factor(
        data_p2_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_p2_long$cue_ordered <- factor(
        data_p2_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    # rating <- "rating_type"
    dv <- "rating_value"
    subject = "trial_index"
    trialorder_subjectwise_p2 <- meanSummary(
        data_p2_long,
        c( model_iv2,  model_iv1, "trial_index"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
    trialorder_subjectwise_p2 <- subset(trialorder_subjectwise_p2, trial_index < 73)
    # subjectwise_naomit_p2$c
    # subjectwise_naomit_p2 <- na.omit(trialorder_subjectwise_p2)
    trialorder_groupwise_p2 <- summarySEwithin(
        data = trialorder_subjectwise_p2,
        measurevar = "mean_per_sub",
        withinvars = c("cue_ordered", "trial_index" ),
    )
trialorder_subjectwise_p2 <- subset(trialorder_subjectwise_p2, trial_index < 73)
# trialorder_subjectwise_p2 <- trialorder_subjectwise_p2[trialorder_subjectwise_p2$trial_index< 73,]
# trialorder_groupwise_p2 <- trialorder_groupwise_p2[trialorder_groupwise_p2$trial_index< 73,]
# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_groupwise_p2,
  aes(x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(cue_ordered)
      )
  ) +
  geom_smooth(
    method = "lm",
    data = trialorder_groupwise_p2,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      color = cue_ordered,
      # linetype = as.factor(cue_ordered)
      )) +
    geom_point(
    data = trialorder_groupwise_p2,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      # linetype = as.factor(rating_type),
      color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub_mean,
      # group = rating_type,
      colour = cue_ordered,
      # linetype = as.factor(cue_ordered),
      ymin = mean_per_sub_norm_mean - se,
      ymax = mean_per_sub_norm_mean + se), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high cue" = "red", #"#009411",
                                "low cue" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("Outcome Rating") +
  labs(title = paste0(taskname, " (N = ", length(unique(data_p2_long$src_subject_id)), ")"))+
  # ylim(0,120) +
  theme_classic2() +
theme(aspect.ratio = .7) +
        theme(    axis.text.x = element_text(size = 20),
    axis.text.y = element_text(size = 20),
    axis.title.x = element_text(size = 25),
    axis.title.y = element_text(size = 25),
    axis.title = element_text(size = 40))
g
```

### vicarious

```{r echo=FALSE}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "vicarious"

ylab <- "Outcome Ratings (degree)"
subject <- "subject"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999" #/ "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"
data <- data.frame()
# load data _____________________________________
data <- df_load_beh(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
data_p2= data %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())

df_clean <- data_p2[complete.cases(data_p2$event02_expect_angle), ]

count_trial <- df_clean %>% count("src_subject_id")
# included_ids <- count_trial[(count_trial$freq > 60) & (count_trial$freq < 73),]$src_subject_id

# Subset the data frame to include only the listed IDs

data_p2_long = df_clean %>%
  pivot_longer(cols = c( 'event04_actual_angle'),
               names_to = "rating_type",
               values_to = "rating_value")
# data_p2_long <- data_p2_long[data_p2_long$src_subject_id %in% included_ids, ]

    data_p2_long$cue_name[data_p2_long$param_cue_type == "high_cue"] <- "high cue"
    data_p2_long$cue_name[data_p2_long$param_cue_type == "low_cue"] <- "low cue"

    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "high_stim"] <- "high"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "med_stim"] <- "med"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "low_stim"] <- "low"

    data_p2_long$stim_ordered <- factor(
        data_p2_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_p2_long$cue_ordered <- factor(
        data_p2_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    # rating <- "rating_type"
    dv <- "rating_value"
    subject = "trial_index"
    trialorder_subjectwise_p2 <- meanSummary(
        data_p2_long,
        c( model_iv2,  model_iv1, "trial_index"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
    # subjectwise_naomit_p2$c
    # subjectwise_naomit_p2 <- na.omit(trialorder_subjectwise_p2)
    trialorder_groupwise_p2 <- summarySEwithin(
        data = trialorder_subjectwise_p2,
        measurevar = "mean_per_sub",
        withinvars = c("cue_ordered", "trial_index" ),
    )

# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_groupwise_p2,
  aes(x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(cue_ordered)
      )
  ) +
  geom_smooth(
    method = "lm",
    data = trialorder_groupwise_p2,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      color = cue_ordered,
      # linetype = as.factor(cue_ordered)
      )) +
    geom_point(
    data = trialorder_groupwise_p2,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      # linetype = as.factor(rating_type),
      color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub_mean,
      # group = rating_type,
      colour = cue_ordered,
      # linetype = as.factor(cue_ordered),
      ymin = mean_per_sub_norm_mean - se,
      ymax = mean_per_sub_norm_mean + se), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high cue" = "red", #"#009411",
                                "low cue" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("Outcome Rating") +
  labs(title = paste0(taskname, " (N = ", length(unique(data_p2_long$src_subject_id)), ")"))+
  ylim(0,120) +
  theme_classic2() +
theme(aspect.ratio = .7) +
        theme(    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20))
g
```

### cognitive

```{r echo=FALSE}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "cognitive"

ylab <- "Outcome Ratings (degree)"
subject <- "subject"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999" #/ "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"
data <- data.frame()
# load data _____________________________________
data <- df_load_beh(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
data_p2= data %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())

df_clean <- data_p2[complete.cases(data_p2$event02_expect_angle), ]

count_trial <- df_clean %>% count("src_subject_id")
# included_ids <- count_trial[(count_trial$freq > 60) & (count_trial$freq < 73),]$src_subject_id

# Subset the data frame to include only the listed IDs

data_p2_long = df_clean %>%
  pivot_longer(cols = c( 'event04_actual_angle'),
               names_to = "rating_type",
               values_to = "rating_value")
# data_p2_long <- data_p2_long[data_p2_long$src_subject_id %in% included_ids, ]

    data_p2_long$cue_name[data_p2_long$param_cue_type == "high_cue"] <- "high cue"
    data_p2_long$cue_name[data_p2_long$param_cue_type == "low_cue"] <- "low cue"

    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "high_stim"] <- "high"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "med_stim"] <- "med"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "low_stim"] <- "low"

    data_p2_long$stim_ordered <- factor(
        data_p2_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_p2_long$cue_ordered <- factor(
        data_p2_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    # rating <- "rating_type"
    dv <- "rating_value"
    subject = "trial_index"
    trialorder_subjectwise_p2 <- meanSummary(
        data_p2_long,
        c( model_iv2,  model_iv1, "trial_index"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
    trialorder_subjectwise_p2 <- subset(trialorder_subjectwise_p2, trial_index < 73)
    # subjectwise_naomit_p2$c
    # subjectwise_naomit_p2 <- na.omit(trialorder_subjectwise_p2)
    trialorder_groupwise_p2 <- summarySEwithin(
        data = trialorder_subjectwise_p2,
        measurevar = "mean_per_sub",
        withinvars = c("cue_ordered", "trial_index" ),
    )

# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_groupwise_p2,
  aes(x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(cue_ordered)
      )
  ) +
  geom_smooth(
    method = "lm",
    data = trialorder_groupwise_p2,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      color = cue_ordered,
      # linetype = as.factor(cue_ordered)
      )) +
    geom_point(
    data = trialorder_groupwise_p2,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      # linetype = as.factor(rating_type),
      color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub_mean,
      # group = rating_type,
      colour = cue_ordered,
      # linetype = as.factor(cue_ordered),
      ymin = mean_per_sub_norm_mean - se,
      ymax = mean_per_sub_norm_mean + se), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high cue" = "red", #"#009411",
                                "low cue" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("Outcome Rating") +
  labs(title = paste0(taskname, " (N = ", length(unique(data_p2_long$src_subject_id)), ")"))+
  ylim(0,120) +
  theme_classic2() +
theme(aspect.ratio = .7) +
          theme(    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20))
g
```

## Tor request -- only expect ratings. 3 tasks

### pain

```{r echo=FALSE}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "pain"

ylab <- "Expectation Ratings (degree)"
subject <- "subject"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999" #/ "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"
data <- data.frame()
# load data _____________________________________
data <- df_load_beh(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
data_p2= data %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())

df_clean <- data_p2[complete.cases(data_p2$event02_expect_angle), ]

count_trial <- df_clean %>% count("src_subject_id")
# included_ids <- count_trial[(count_trial$freq > 60) & (count_trial$freq < 73),]$src_subject_id

# Subset the data frame to include only the listed IDs

model_cuetrial <- lmer(event04_actual_angle ~ trial_index*param_cue_type + (param_cue_type|src_subject_id), data = df_clean)
summary(model_cuetrial)
anova(model_cuetrial)
random_slopes <- ranef(model_cuetrial)$src_subject_id$param_cue_typelow_cue
group_ids <- c(rownames(ranef(model_cuetrial)$src_subject_id))
df <- data.frame(sub = group_ids, cue_randomslope = random_slopes)
write.csv(df, file.path(main_dir,"data","RL", "cue_trial_ranef_pain.csv"), row.names = FALSE)


data_p2_long = df_clean %>%
  pivot_longer(cols = c( 'event02_expect_angle'),
               names_to = "rating_type",
               values_to = "rating_value")
# data_p2_long <- data_p2_long[data_p2_long$src_subject_id %in% included_ids, ]

    data_p2_long$cue_name[data_p2_long$param_cue_type == "high_cue"] <- "high cue"
    data_p2_long$cue_name[data_p2_long$param_cue_type == "low_cue"] <- "low cue"

    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "high_stim"] <- "high"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "med_stim"] <- "med"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "low_stim"] <- "low"

    data_p2_long$stim_ordered <- factor(
        data_p2_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_p2_long$cue_ordered <- factor(
        data_p2_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    # rating <- "rating_type"
    dv <- "rating_value"
    subject = "trial_index"
    trialorder_subjectwise_p2 <- meanSummary(
        data_p2_long,
        c( model_iv2,  model_iv1, "trial_index"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
    trialorder_subjectwise_p2 <- subset(trialorder_subjectwise_p2, trial_index < 73)
    # subjectwise_naomit_p2$c
    # subjectwise_naomit_p2 <- na.omit(trialorder_subjectwise_p2)
    trialorder_groupwise_p2 <- summarySEwithin(
        data = trialorder_subjectwise_p2,
        measurevar = "mean_per_sub",
        withinvars = c("cue_ordered", "trial_index" ),
    )
trialorder_subjectwise_p2 <- subset(trialorder_subjectwise_p2, trial_index < 73)
# trialorder_subjectwise_p2 <- trialorder_subjectwise_p2[trialorder_subjectwise_p2$trial_index< 73,]
# trialorder_groupwise_p2 <- trialorder_groupwise_p2[trialorder_groupwise_p2$trial_index< 73,]
# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_groupwise_p2,
  aes(x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(cue_ordered)
      )
  ) +
  geom_smooth(
    method = "lm",
    data = trialorder_groupwise_p2,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      color = cue_ordered,
      # linetype = as.factor(cue_ordered)
      )) +
    geom_point(
    data = trialorder_groupwise_p2,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      # linetype = as.factor(rating_type),
      color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub_mean,
      # group = rating_type,
      colour = cue_ordered,
      # linetype = as.factor(cue_ordered),
      ymin = mean_per_sub_norm_mean - se,
      ymax = mean_per_sub_norm_mean + se), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high cue" = "red", #"#009411",
                                "low cue" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("Expectation Rating") +
  labs(title = paste0(taskname, " (N = ", length(unique(data_p2_long$src_subject_id)), ")"))+
  ylim(0,120) +
  theme_classic2() +
theme(aspect.ratio = .7) +
    theme(    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20))
g
```

### vicarious

```{r echo=FALSE}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "vicarious"

ylab <- "Outcome Ratings (degree)"
subject <- "subject"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999" #/ "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"
data <- data.frame()
# load data _____________________________________
data <- df_load_beh(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
data_p2= data %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())

df_clean <- data_p2[complete.cases(data_p2$event02_expect_angle), ]

# random slopes
model_cuetrial <- lmer(event04_actual_angle ~ trial_index*param_cue_type + (param_cue_type|src_subject_id), data = df_clean)
summary(model_cuetrial)
anova(model_cuetrial)
random_slopes <- ranef(model_cuetrial)$src_subject_id$param_cue_typelow_cue
group_ids <- c(rownames(ranef(model_cuetrial)$src_subject_id))
df <- data.frame(sub = group_ids, cue_randomslope = random_slopes)
write.csv(df, file.path(main_dir,"data","RL", "cue_trial_ranef_vicarious.csv"), row.names = FALSE)
# random slopes
count_trial <- df_clean %>% count("src_subject_id")
# included_ids <- count_trial[(count_trial$freq > 60) & (count_trial$freq < 73),]$src_subject_id

# Subset the data frame to include only the listed IDs

data_p2_long = df_clean %>%
  pivot_longer(cols = c( 'event04_actual_angle'),
               names_to = "rating_type",
               values_to = "rating_value")
# data_p2_long <- data_p2_long[data_p2_long$src_subject_id %in% included_ids, ]

    data_p2_long$cue_name[data_p2_long$param_cue_type == "high_cue"] <- "high cue"
    data_p2_long$cue_name[data_p2_long$param_cue_type == "low_cue"] <- "low cue"

    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "high_stim"] <- "high"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "med_stim"] <- "med"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "low_stim"] <- "low"

    data_p2_long$stim_ordered <- factor(
        data_p2_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_p2_long$cue_ordered <- factor(
        data_p2_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    # rating <- "rating_type"
    dv <- "rating_value"
    subject = "trial_index"
    trialorder_subjectwise_p2 <- meanSummary(
        data_p2_long,
        c( model_iv2,  model_iv1, "trial_index"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
    # subjectwise_naomit_p2$c
    # subjectwise_naomit_p2 <- na.omit(trialorder_subjectwise_p2)
    trialorder_groupwise_p2 <- summarySEwithin(
        data = trialorder_subjectwise_p2,
        measurevar = "mean_per_sub",
        withinvars = c("cue_ordered", "trial_index" ),
    )

# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_groupwise_p2,
  aes(x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(cue_ordered)
      )
  ) +
  geom_smooth(
    method = "lm",
    data = trialorder_groupwise_p2,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      color = cue_ordered,
      # linetype = as.factor(cue_ordered)
      )) +
    geom_point(
    data = trialorder_groupwise_p2,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      # linetype = as.factor(rating_type),
      color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub_mean,
      # group = rating_type,
      colour = cue_ordered,
      # linetype = as.factor(cue_ordered),
      ymin = mean_per_sub_norm_mean - se,
      ymax = mean_per_sub_norm_mean + se), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high cue" = "red", #"#009411",
                                "low cue" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("Outcome Rating") +
  labs(title = paste0(taskname, " (N = ", length(unique(data_p2_long$src_subject_id)), ")"))+
  ylim(0,120) +
  theme_classic2() +
theme(aspect.ratio = .7) +
        theme(    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20))
g
```

### cognitive

```{r echo=FALSE}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "cognitive"

ylab <- "Expectation Ratings (degree)"
subject <- "subject"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999" #/ "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"
data <- data.frame()
# load data _____________________________________
data <- df_load_beh(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
data_p2= data %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())

df_clean <- data_p2[complete.cases(data_p2$event02_expect_angle), ]

# random slopes
model_cuetrial <- lmer(event04_actual_angle ~ trial_index*param_cue_type + (param_cue_type|src_subject_id), data = df_clean)
summary(model_cuetrial)
anova(model_cuetrial)
random_slopes <- ranef(model_cuetrial)$src_subject_id$param_cue_typelow_cue
group_ids <- c(rownames(ranef(model_cuetrial)$src_subject_id))
df <- data.frame(sub = group_ids, cue_randomslope = random_slopes)
write.csv(df, file.path(main_dir,"data","RL", "cue_trial_ranef_cognitive.csv"), row.names = FALSE)

# random slopes
count_trial <- df_clean %>% count("src_subject_id")
# included_ids <- count_trial[(count_trial$freq > 60) & (count_trial$freq < 73),]$src_subject_id

# Subset the data frame to include only the listed IDs

data_p2_long = df_clean %>%
  pivot_longer(cols = c( 'event02_expect_angle'),
               names_to = "rating_type",
               values_to = "rating_value")
# data_p2_long <- data_p2_long[data_p2_long$src_subject_id %in% included_ids, ]

    data_p2_long$cue_name[data_p2_long$param_cue_type == "high_cue"] <- "high cue"
    data_p2_long$cue_name[data_p2_long$param_cue_type == "low_cue"] <- "low cue"

    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "high_stim"] <- "high"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "med_stim"] <- "med"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "low_stim"] <- "low"

    data_p2_long$stim_ordered <- factor(
        data_p2_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_p2_long$cue_ordered <- factor(
        data_p2_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    # rating <- "rating_type"
    dv <- "rating_value"
    subject = "trial_index"
    trialorder_subjectwise_p2 <- meanSummary(
        data_p2_long,
        c( model_iv2,  model_iv1, "trial_index"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
    trialorder_subjectwise_p2 <- subset(trialorder_subjectwise_p2, trial_index < 73)
    # subjectwise_naomit_p2$c
    # subjectwise_naomit_p2 <- na.omit(trialorder_subjectwise_p2)
    trialorder_groupwise_p2 <- summarySEwithin(
        data = trialorder_subjectwise_p2,
        measurevar = "mean_per_sub",
        withinvars = c("cue_ordered", "trial_index" ),
    )

# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_groupwise_p2,
  aes(x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(cue_ordered)
      )
  ) +
  geom_smooth(
    method = "lm",
    data = trialorder_groupwise_p2,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      color = cue_ordered,
      # linetype = as.factor(cue_ordered)
      )) +
    geom_point(
    data = trialorder_groupwise_p2,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      # group = rating_type,
      # linetype = as.factor(rating_type),
      color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub_mean,
      # group = rating_type,
      colour = cue_ordered,
      # linetype = as.factor(cue_ordered),
      ymin = mean_per_sub_norm_mean - se,
      ymax = mean_per_sub_norm_mean + se), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high cue" = "red", #"#009411",
                                "low cue" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("Expectation Rating") +
  labs(title = paste0(taskname, " (N = ", length(unique(data_p2_long$src_subject_id)), ")"))+
  ylim(0,120) +
  theme_classic2() +
theme(aspect.ratio = .7) +
          theme(    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20))
g
```

## lmer

```{r echo=FALSE}
model_cuetrial <- lmer(event04_actual_angle ~ trial_index*param_cue_type + (param_cue_type|src_subject_id), data = df_clean)
summary(model_cuetrial)
anova(model_cuetrial)
random_slopes <- ranef(model_cuetrial)$src_subject_id$param_cue_typelow_cue
group_ids <- c(rownames(ranef(model_cuetrial)$src_subject_id))
df <- data.frame(sub = group_ids, cue_randomslope = random_slopes)
write.csv(df, file.path(main_dir,"data","RL", "cue_trial_ranef_{taskname}.csv"), row.names = FALSE)
```

### lmer histogram

```{r}
hist(random_slopes)
```

```{r}
df <- data.frame(sub = group_ids, cue_randomslope = random_slopes)
write.csv(df, file.path(main_dir,"data","RL", "cue_trial_ranef_{taskname}.csv"), row.names = FALSE)
# TODO: create a json file that also keeps track of which participants are include hree, using what model
# comment
```

## Do current expectation ratings predict outcome ratings?

### Additional analyse 01/18/2023 {.unlisted .unnumbered}

- see if current expectation ratings predict outcome ratings
- see if prior stimulus experience (N-1) predicts current expectation ratings
- see if current expectation ratings are explained as a function of prior outcome rating and current expectation rating

when loading the dataset, I need to add in trial index per dataframe.
Then, for the shift the rating?

```{r}
data_a3 <- data_p2 %>%
  group_by(src_subject_id, session_id, param_run_num) %>%
  mutate(trial_index = row_number(param_run_num))

data_a3lag <-
    data_a3 %>%
    group_by(src_subject_id, session_id, param_run_num) %>%
    mutate(lag.04outcomeangle = dplyr::lag(event04_actual_angle, n = 1, default = NA))
data_a3lag_omit <- data_a3lag[complete.cases(data_a3lag$lag.04outcomeangle),]
```

```{r}
    trialorder_subjectwise_lagoutcome <- meanSummary(
        data_a3lag_omit,
        c("src_subject_id", "session_id", "param_run_num"), "lag.04outcomeangle" )
    trialorder_subjectwise_lagoutcome <- meanSummary(
        data_a3lag_omit,
        c("src_subject_id", "session_id", "param_run_num"), "lag.04outcomeangle" )

    # subjectwise_naomit <- na.omit(trialorder_subjectwise)
    # trialorder_groupwise <- summarySEwithin(
    #     data = subjectwise_naomit,
    #     measurevar = "mean_per_sub",
    #     withinvars = c("cue_ordered", "rating_type",  "trial_index"), idvar = subject
    # )
```

```{r}
model.lagoutcome = lmer(event02_expect_angle ~ lag.04outcomeangle + (1 | src_subject_id) + (1|session_id) , data = data_a3lag_omit)
summary(model.lagoutcome)
```

```{r}
meanSummary_2continuous <- function(DATA, GROUP, DV1, DV2) {
    z <- ddply(DATA, GROUP, .fun = function(xx) {
        c(
            DV1_mean_per_sub = mean(xx[, DV1], na.rm = TRUE),
            DV1_sd = sd(xx[, DV1], na.rm = TRUE),
            DV2_mean_per_sub = mean(xx[, DV2], na.rm = TRUE),
            DV2_sd = sd(xx[, DV1], na.rm = TRUE)
        )
    })
    return(z)
}
```

```{r}
subjectwise_2dv = meanSummary_2continuous(data_a3lag_omit,
        c("src_subject_id", "trial_index"),
        "lag.04outcomeangle", "event02_expect_angle")
```

```{r}
subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
```

```{r}
sp <- ggplot(data=subjectwise_naomit_2dv,
             aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color="green",
                 linetype="dashed", size=0.5) +
  theme(aspect.ratio=1) +
  xlab("n-1 outcome rating") +
  ylab("n expectation rating")
sp
# plot(subjectwise_naomit_2dv$DV1_mean_per_sub, subjectwise_naomit_2dv$DV2_mean_per_sub) + lines(x = c(0,200), y = c(0,200))
```

```{r}
    trialorder_groupwise <- summarySEwithin(
        data = subjectwise_naomit_2dv,
        measurevar = "DV1_mean_per_sub",
        # betweenvars = "src_subject_id",
        withinvars = factor( "trial_index"),
         idvar = "src_subject_id"
    )
```

```{r}
    trialorder_groupwise <- summarySEwithin(
        data = subset(subjectwise_naomit_2dv, select = -c(src_subject_id)),
        measurevar = "DV1_mean_per_sub",
        # betweenvars = "src_subject_id",
        withinvars = as.factor( "trial_index")
         #idvar = "trial_index"
    )
```

```{r}
data_a3lag_omit$src_subject_id <- as.factor(data_a3lag_omit$src_subject_id)

lag.raw <- ggplot(aes(x=lag.04outcomeangle, y=event02_expect_angle), data=data_a3lag_omit) +
  geom_smooth(method='lm', se=F, size=0.75) +
  geom_point(size=0.1) +
    geom_abline(intercept = 0, slope = 1, color="green",
                 linetype="dashed", size=0.5) +
  facet_wrap(~src_subject_id) +
  theme(legend.position='none') +
  xlim(0,180) + ylim(0,180) +
  xlab("raw data from each participant: n-1 lagged outcome angle") +
  ylab("n current expectation rating")
lag.raw +
  labs(title = paste(taskname, "- Is there a linear relationship between current expectation ratings and the previous outcome ratings?"),
       subtitle = "Plotting the raw data - with all of the datapoints ignoring run differences",
       caption = "Blue = fitted linear slope per participant; Green: 1:1 slope")
```

```{r}
subjectwise_naomit_2dv$src_subject_id <- as.factor(subjectwise_naomit_2dv$src_subject_id)

lag.avg <- ggplot(aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub), data=subjectwise_naomit_2dv) +
  geom_smooth(method='lm', se=F, size=0.75) +
  geom_point(size=0.1) +
    geom_abline(intercept = 0, slope = 1, color="green",
                 linetype="dashed", size=0.5) +
  facet_wrap(~src_subject_id) +
  theme(legend.position='none') +
  xlim(0,180) + ylim(0,180) +
  xlab("raw data from each participant: n-1 lagged outcome angle") +
  ylab("n current expectation rating")

lag.avg +
  labs(title = paste(taskname, "- Is there a linear relationship between current expectation ratings and the previous outcome ratings?"),
       subtitle = "Observation notes: 1) The relationship is more of an attenuated one, where the higher outcome ratings lead to a slightly lower expectation rating, and a low outcome leads to a higher expectation rating, when considering a 1:1 relationship. This pattern could be explained by regression to the mean type mechanism, where participants are accounting for the fact that their previous experience was extreme on either ends and that this current trial will be under/over estimated. It probably will make sense to also see the relationship between current expectation ratings influencing current outcome ratings. ",
       caption = "Blue = fitted linear slope per participant; Green: 1:1 slope")

```

```{r}
# https://gist.github.com/even4void/5074855
```

```{r}
ggplot(data_a3lag_omit, aes(y = event02_expect_angle,
                       x = lag.04outcomeangle,
                       colour = subject), size = .3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .3) +
  theme_bw()
```

## Additional analysis

01/23/2023

```{r}
model.lag_cue = lmer(event02_expect_angle ~ lag.04outcomeangle*param_cue_type + (1 | src_subject_id) + (1|session_id) , data = data_a3lag_omit)
summary(model.lag_cue)
```

```{r}
meanSummary_2continuous <- function(DATA, GROUP, DV1, DV2) {
    z <- ddply(DATA, GROUP, .fun = function(xx) {
        c(
            DV1_mean_per_sub = mean(xx[, DV1], na.rm = TRUE),
            DV1_sd = sd(xx[, DV1], na.rm = TRUE),
            DV2_mean_per_sub = mean(xx[, DV2], na.rm = TRUE),
            DV2_sd = sd(xx[, DV1], na.rm = TRUE)
        )
    })
    return(z)
}
```

```{r}
subjectwise_cuetype = meanSummary_2continuous(data_a3lag_omit,
        c("src_subject_id", "trial_index", "param_cue_type"),
        "lag.04outcomeangle", "event02_expect_angle")
```

```{r}
# subjectwise_cuetype_2dv <- na.omit(subjectwise_cuetype)
```

```{r}
subjectwise_cuetype$param_cue_type <- as.factor(subjectwise_cuetype$param_cue_type)
sp <- ggplot(data=subjectwise_cuetype,
             aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub,
             color = param_cue_type)) +
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color="green",
                 linetype="dashed", size=0.5) +
  geom_smooth(method = 'lm') +
  theme(aspect.ratio=1) +
  xlab("n-1 outcome rating") +
  ylab("n expectation rating")
sp +
    labs(title = paste(taskname, "- Does the linear relationship between current expectation ratings and the previous outcome ratings differ as a function of cue?"),
       subtitle = "Plotting the raw data - with all of the datapoints averaged across runs per 12 trials",
       caption = "high cue vs low cue. The slope is significant, theree is not interaction; Green: 1:1 slope")
# plot(subjectwise_naomit_2dv$DV1_mean_per_sub, subjectwise_naomit_2dv$DV2_mean_per_sub) + lines(x = c(0,200), y = c(0,200))
```
