# [beh] RT ~ cue {#ch07_RT-cue}

## What is the purpose of this notebook? {.unlisted .unnumbered}

Here, I test the cue effect (high vs. low) on Reaction time and performance in the cogntive, mental-rotation tasks

- left = diff, right = same
- model 1: Does RT differ as a function of cue type?
- model 1-1: Does RT differ as a function of cue, ONLY for the correct trials?
- model 1-2: Does RT differ as a function of cue, ONLY for the incorrect trials?
- model 2: would log-transforming help? Do we see a cue effect on the log-transformmed RTs?

```{r load_libraries_6, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
library(lme4)
library(lmerTest)
library(plyr)
#library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
#library(Hmisc)
#library(Rmisc)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(gghalves)
## library(extraoperators)
##library(JWileymisc)
##library(multilevelTools)
library(ggpubr)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

library(r2mlm)
main_dir = dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, "scripts/step02_R/utils"),
                          pattern="*.R",
                          full.names=TRUE,
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

### parameters

```{r main_directory_6, include=FALSE}
main_dir = dirname(dirname(getwd()))
print(main_dir)
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
```

### 1) plot RT data

```{r load_data_6, echo=TRUE}
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "cognitive"
ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"

data <- df_load_beh(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv,  exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
```

### plot RT distribution per participant

- the purpose is to identify whether RTs are distributed from 0-5 sec or not

```{r plot_RT_distribution_6, echo=TRUE, fig.width=10, fig.height=12}
ggplot(data, aes(x = event03_RT, group = subject)) +
  geom_histogram(
    color = "darkblue",
    fill = "lightblue",
    binwidth = 0.25,
    bins = 20
  ) +
  facet_wrap( ~ subject, ncol = 10) +
  theme(axis.text = element_text(size = 7), text = element_text(size = 12))
```

- some participants may not have responded within time limit
- the button may not have registered the correct onset
- I may have to remove the RTs with 5 sec.

---

### exclude participants with RT of 5 seconds {.unlisted .unnumbered}

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "cognitive"

ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"

# load data _____________________________________
data <- df_load_beh(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset

analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model07_iv-cue_dv-RT", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)

data$event03_response_samediff <- mapvalues(data$event03_stimulusC_response,
                                                from = c(1, 2),
                                                to = c("diff", "same"))

data$event03_correct <- ifelse(data$event03_C_stim_match == data$event03_response_samediff, 1, ifelse(data$event03_C_stim_match != data$event03_response_samediff, 0, "NA"))
```

## model 1:

- plotting all of the code
- Does RT differ as a function of high vs. low cue?
- conclusion: No. RT does not differ as a function of cue

```{r m1_cue_effect_on_RT_6, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# parameters ________________________________
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "cognitive"
ylim = c(0,5)

# lmer filename ________________________________
model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), ".txt",
            sep = ""
        )
    )

# removing NA values ________________________________
data_clean = data[!is.na(data$event03_correct),]
data_clean$subject = factor(data_clean$src_subject_id)

# lmer model ________________________________
sink(model_savefname)
model_onefactor <- lmer(event03_RT ~ param_cue_type + (1 | subject), data = data_clean)
summary(model_onefactor)
sink()


fixEffect <- as.data.frame(fixef(model_onefactor))
randEffect <- as.data.frame(ranef(model_onefactor))
cooksd <- cooks.distance(model_onefactor)
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data_clean$subject)))))])
data_screen <- data_clean[-influential, ]

# summary statistics for plots ________________________________
subjectwise <- meanSummary(data_screen, c(subject, iv), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(iv), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    group_mean <- "mean_per_sub_norm_mean"
se <- "se";    subject <- "subject"
ggtitle <- paste(taskname, " - Reaction Time (s)");    title <- paste(taskname, " - RT")
xlab <- "";    ylab <- "Reaction Time (s)";
w = 5; h = 3; dv_keyword <- "RT"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4274AD", "#C5263A")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_dv-", dv_keyword,
            "_", as.character(Sys.Date()), ".png",
            sep = ""
        )
    )
plot_halfrainclouds_onefactor(
        subjectwise, groupwise,
        iv, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

# random effects ________________________________
randEffect <- as.data.frame(ranef(model_onefactor))
fixEffect <- as.data.frame(fixef(model_onefactor))
randEffect$newcoef <- mapvalues(randEffect$term,
    from = c("(Intercept)",
             "param_cue_typelow_cue"
             ),
    to = c("rand_intercept", "rand_cue")
)

rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = `(Intercept)`,
    fix_cue = `param_cue_typelow_cue`,
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",
        as.character(Sys.Date()), "_outlier-cooksd.csv",
        sep = ""
    )
)
write.csv(new_total, rand_savefname, row.names = FALSE)
```

## model 1-1

- omitting code (identical to model 1, except for subsetting correct trials)
- Only using correct trials, does RT differ as a function of high vs. low cue?
- conclusion 1-1: No. Even within the subset of correct trials, RT does not differ as a function of cue

```{r model_1-1_correct_trials_only_6, echo=FALSE}
# parameters ________________________________
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT-correct"
xlab <- ""
taskname <- "cognitive"
ylim = c(0,5)

# lmer filename ________________________________
model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), ".txt",
            sep = ""
        )
    )

# removing NA values ________________________________

data_clean = data[!is.na(data$event03_correct),]
data_c = data[data_clean$event03_correct == 1,]
data_c$subject = factor(data_c$src_subject_id)

# lmer model ________________________________
sink(model_savefname)
model_onefactor_correct <- lmer(event03_RT ~ param_cue_type + (1 | subject), data = data_c)
summary(model_onefactor_correct)
sink()



cooksd <- cooks.distance(model_onefactor_correct)
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data_c$subject)))))])
data_screen <- data_c[-influential, ]

# summary statistics for plots ________________________________
subjectwise <- meanSummary(data_screen, c(subject, iv), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(iv), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    group_mean <- "mean_per_sub_norm_mean"
se <- "se";    subject <- "subject"
ggtitle <- paste(taskname, dv_keyword);    title <- paste(taskname, " - RT")
xlab <- "";    ylab <- "Reaction Time (s)";
w = 5; h = 3;
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4274AD", "#C5263A")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_dv-", dv_keyword,
            "_", as.character(Sys.Date()), ".png",
            sep = ""
        )
    )
plot_halfrainclouds_onefactor(
        subjectwise, groupwise,
        iv, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

# random effects ________________________________
fixEffect_correct <- as.data.frame(fixef(model_onefactor_correct))
randEffect_correct <- as.data.frame(ranef(model_onefactor_correct))
randEffect_correct$newcoef <- mapvalues(randEffect_correct$term,
    from = c("(Intercept)",
             "param_cue_typelow_cue"
             ),
    to = c("rand_intercept", "rand_cue")
)

rand_subset <- subset(randEffect_correct, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = `(Intercept)`,
    fix_cue = `param_cue_typelow_cue`,
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",dv_keyword,
            "_",
        as.character(Sys.Date()), "_outlier-cooksd.csv",
        sep = ""
    )
)
write.csv(new_total, rand_savefname, row.names = FALSE)
```

## model 1-2:

- omitting code (identical to model 1, except for subsetting incorrect trials)
- Only using incorrect trials, does RT differ as a function of high vs. low cue?
- conclusion 1-2: no. Even within the subset of incorrect trials, RT does not differ as a function of cue

```{r model_1-2_incorrect_trials_only_6, echo=FALSE}
# parameters ________________________________
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT-incorrect"
xlab <- ""
taskname <- "cognitive"
ylim = c(0,5)

# lmer filename ________________________________
model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), ".txt",
            sep = ""
        )
    )

# removing NA values ________________________________

data_clean = data[!is.na(data$event03_correct),]
data_i = data[data_clean$event03_correct == 0,]
data_i$subject = factor(data_i$src_subject_id)

# lmer model ________________________________
sink(model_savefname)
model_onefactor_incorrect <- lmer(event03_RT ~ param_cue_type + (1 | subject), data = data_i)
summary(model_onefactor_incorrect)
sink()



cooksd <- cooks.distance(model_onefactor_incorrect)
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data_i$subject)))))])
data_screen <- data_i[-influential, ]

# summary statistics for plots ________________________________
subjectwise <- meanSummary(data_screen, c(subject, iv), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(iv), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    group_mean <- "mean_per_sub_norm_mean"
se <- "se";    subject <- "subject"
ggtitle <- paste(taskname, dv_keyword);    title <- paste(taskname, " - RT")
xlab <- "";    ylab <- "Reaction Time (s)";
w = 5; h = 3;
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4274AD", "#C5263A")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_dv-", dv_keyword,
            "_", as.character(Sys.Date()), ".png",
            sep = ""
        )
    )
plot_halfrainclouds_onefactor(
        subjectwise, groupwise,
        iv, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

# random effects ________________________________
fixEffect_incorrect <- as.data.frame(fixef(model_onefactor_incorrect))
randEffect_incorrect <- as.data.frame(ranef(model_onefactor_incorrect))
randEffect_incorrect$newcoef <- mapvalues(randEffect_incorrect$term,
    from = c("(Intercept)",
             "param_cue_typelow_cue"
             ),
    to = c("rand_intercept", "rand_cue")
)

rand_subset <- subset(randEffect_incorrect, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = `(Intercept)`,
    fix_cue = `param_cue_typelow_cue`,
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",dv_keyword,
            "_",
        as.character(Sys.Date()), "_outlier-cooksd.csv",
        sep = ""
    )
)
write.csv(new_total, rand_savefname, row.names = FALSE)
```

## model 2:

- omitting code (identical to model 1, except for log-transformming RT)
- Does log transformming help? After log-transformming RT, does RT differ as a function of high vs. low cue?
- conclusion 2: No, log transformmed or not, there is no significant cue effect on RT

```{r m2_cue_effect_on_log-RT_6, echo=FALSE}
# parameters ________________________________
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "log_RT"
dv_keyword <- "RT-log"
xlab <- ""
taskname <- "cognitive"
ylim = c(0,5)

# lmer filename ________________________________
model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "-log_", as.character(Sys.Date()), ".txt",
            sep = ""
        )
    )

# removing NA values ________________________________
data_clean = data[!is.na(data$event03_correct),]
data_clean$log_RT = log(data_clean$event03_RT)
data_clean$subject = factor(data_clean$src_subject_id)

# lmer model ________________________________
sink(model_savefname)
model_onefactor_log <- lmer(log_RT ~ param_cue_type + (1 | subject), data = data_clean)
summary(model_onefactor_log)
sink()


fixEffect <- as.data.frame(fixef(model_onefactor_log))
randEffect <- as.data.frame(ranef(model_onefactor_log))
cooksd <- cooks.distance(model_onefactor_log)
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data_clean$subject)))))])
data_screen_log <- data_clean[-influential, ]

# summary statistics for plots ________________________________
subjectwise <- meanSummary(data_screen_log, c(subject, iv), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(iv), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    group_mean <- "mean_per_sub_norm_mean"
se <- "se";
ggtitle <- paste(taskname, dv_keyword);    title <- paste(taskname, " - RT")
xlab <- "";    ylab <- "Reaction Time (s)";
w = 5; h = 3;
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4274AD", "#C5263A")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_dv-", dv_keyword,
            "-log_", as.character(Sys.Date()), ".png",
            sep = ""
        )
    )
plot_halfrainclouds_onefactor(
        subjectwise, groupwise,
        iv, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

# random effects ________________________________
fixEffect <- as.data.frame(fixef(model_onefactor_log))
randEffect <- as.data.frame(ranef(model_onefactor_log))
randEffect$newcoef <- mapvalues(randEffect$term,
    from = c("(Intercept)",
             "param_cue_typelow_cue"
             ),
    to = c("rand_intercept", "rand_cue")
)

rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = `(Intercept)`,
    fix_cue = `param_cue_typelow_cue`,
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",
        as.character(Sys.Date()), "_outlier-cooksd.csv",
        sep = ""
    )
)
write.csv(new_total, rand_savefname, row.names = FALSE)
```
