# beh :: within / between subject effect {#scaling}

## What is the purpose of this notebook? {.unlisted .unnumbered}

cue effect with raw score, conflated with scale artifact and also common domain general expectation mechanisms.
Q. what about task-specific components?

Here, we want to examine the between and within subject effects of subjective ratings. 
There are scale usage differences across individuals. It's evident in our behavioral data. 
These scale usage differences do not really reflecting the underlying experience, but compresses the scale.
This is one of the reasons why including the between subject term improves the performance of the mediation model. 
It's also in line with Enders and Tofighi's illustration of centering in multilevel models. 

The logic is that there are multiple components that go into subjective ratings
the way that an individual uses a scale ("between-subject effect")
and the fact that the rating does reflect the subjective experience ("within-subject effect")
We want to rid of the between subject effect and focus on the subjective experience. 

One way to resolve this is by z-scoring.

Hypothesis: After z-scoring, if we see a high correlation across tasks in terms of their cue effects, then we can safely conclude that the way that people think of expectations are highly domain general

Some thoughts:
* if scaling artifact is a big driving factor, that pain to brain is going to lead to a weak signal.
* within person pain effects. only weakly tracks individual differences.


* Main model: `lmer( OUTCOME ~ EXPECT)` vs. `lmer( OUTCOME ~ zscoreEXPECT)`
* Main question: {{ INSERT YOUR QUESTION }}? 
* {{ HYPOTHESES/EXPECTED OUTCOME }}
* 
* IV: 
  - {{ FACTOR NAME }} ( {{ LEVELS}} )
* DV: {{ DV }}


::::{.refbox}
* [Enders, C. K., & Tofighi, D. (2007). Centering predictor variables in cross-sectional multilevel models: A new look at an old issue. Psychological Methods, 12(2), 121–138.](https://doi.org/10.1037/1082-989X.12.2.121)
::::


### TODO: 
```
zscore the ratings (ignore sessions)
predict outcome ratings
model compare zscore vs just raw score
include between subject level scores as covariates. AS ALWAYS
```


### load libraries {.unlisted .unnumbered}
```{r message=FALSE, warning=FALSE, include=FALSE}
library(car)
library(psych)
library(lme4)
library(plyr); library(dplyr)
library(cueR)
library(ggplot2)
```

```{r}
# parameters ___________________________________________________________________
main_dir <- dirname(dirname(getwd()))
datadir <- file.path(main_dir, 'data', 'beh', 'beh02_preproc')
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model09_scaling", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "pain"
ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
# 1. load data _________________________________________________________________
data <- cueR::df_load_beh(datadir,
                            taskname = taskname,
                            subject_varkey = subject_varkey,
                            iv = iv,
                            exclude = exclude)
# processed_data <- cueR::compute_enderstofighi(data, sub="src_subject_id",
#                                     outcome = "event04_actual_angle",expect= "event02_expect_angle",
#                                     ses = "session_id", run = "param_run_num")
```

```{r}
  maindata <- data %>%
    group_by(!!sym("src_subject_id")) %>%
    mutate(OUTCOME = as.numeric(!!sym("event04_actual_angle"))) %>%
    mutate(EXPECT = as.numeric(!!sym("event02_expect_angle"))) %>%
    mutate(OUTCOME_avg = mean(OUTCOME, na.rm = TRUE)) %>%
    mutate(OUTCOME_demean = OUTCOME - OUTCOME_avg) %>%
    mutate(EXPECT_avg = mean(EXPECT, na.rm = TRUE)) %>%
    mutate(EXPECT_demean = EXPECT - EXPECT_avg)
  
  data_p2 <- maindata %>%
    arrange(!!sym("src_subject_id")) %>%
    group_by(!!sym("src_subject_id")) %>%
    mutate(trial_index = row_number())
  
  data_a3 <- data_p2 %>%
    group_by(!!sym("src_subject_id"), !!sym("session_id"), !!sym("param_run_num")) %>%
    mutate(trial_index = row_number(!!sym("param_run_num")))
  
  data_a3lag <- data_a3 %>%
    group_by(!!sym("src_subject_id"), !!sym("session_id"), !!sym("param_run_num")) %>%
    mutate(lag.OUTCOME_demean = dplyr::lag(OUTCOME_demean, n = 1, default = NA))
  
  data_a3lag <- data_a3lag %>%
    mutate(EXPECT_cmc = EXPECT_avg - mean(EXPECT_avg))
  
  data_centered <- data_a3lag[complete.cases(data_a3lag$lag.OUTCOME_demean),]
  
```


```{r}
data_centered
```


### display distribution of data
Let's look at the distribution of the data. X axis: Y axis: 
```{r paged.print=TRUE, fig.width=10, fig.height=5}
# remove NA values first
data_centered_NA <- data_centered %>% filter(!is.na(OUTCOME))  # Remove NA values

g<- ggplot(data_centered_NA, aes(x = subject, y = OUTCOME, fill = subject)) +
  geom_boxplot() +  
  theme_classic() +
  labs(x = "Subject", y = "Outcome Rating") +
  theme(legend.position = "none",
        aspect.ratio = 0.5) 

g <- ggplot_largetext(g)
g

```
> Summary: 

### plot {.unlisted .unnumbered}
We'll plot Y as a function of A and B
X axis: 
Y axis:
Each data point indicates ... 
```{r fig.height=10, fig.width=10}

```
> Conclusion:


:::: {.infobox}
Include the actual content here. here are my thoughts
::::

:::: {.refbox}
Include the actual content here. here are my thoughts
::::

