# within / between subject effect and Scaling {#scaling}

## What is the purpose of this notebook? {.unlisted .unnumbered}

> Here, we want to examine the between and within subject effects of subjective ratings. 
There are scale usage differences across individuals. It's evident in our behavioral data. 
These scale usage differences do not really reflecting the underlying experience, but compresses the scale.
This is one of the reasons why including the between-subject term improves the performance of the mediation model. 
It's also in line with Enders and Tofighi's illustration of centering in multilevel models. 
\n
The logic is that there are multiple components that go into subjective ratings
the way that an individual uses a scale ("between-subject effect")
and the fact that the rating does reflect the subjective experience ("within-subject effect")
We want to rid of the between subject effect and focus on the subjective experience. 
\n
One way to resolve this is by z-scoring.
\n
Hypothesis: After z-scoring, if we see a high correlation across tasks in terms of their cue effects, then we can safely conclude that the way that people think of expectations are highly domain general
\n
The cue effect from raw scores can be conflated with scale artifact and also common domain general expectation mechanisms.
Q. what about task-specific components?
\n
Some thoughts:
* if scaling artifact is a big driving factor, that pain to brain is going to lead to a weak signal.
* within person pain effects. only weakly tracks individual differences.
/n
* Main model: `lmer( OUTCOME ~ EXPECT)` vs. `lmer( OUTCOME ~ zscoreEXPECT)`
* Main question: Does Z-scoring lead to an improvement in predicting pain? Does the effect shrink, indicating that most pain ratings are a byproduct of participants using the scale differently? 
* {{ HYPOTHESES/EXPECTED OUTCOME }}
* If slopes increase after z-scoring, effects
* IV: 
  - {{ Zscore }} ( {{ LEVELS}} )
* DV: {{ Outcome }}


---
title: "Your Document Title"
author: "Your Name"
output: 
  bookdown::html_document2:
    toc: true
    toc_depth: 2
    number_sections: true
    theme: united
---


::::{.refbox}
* [Enders, C. K., & Tofighi, D. (2007). Centering predictor variables in cross-sectional multilevel models: A new look at an old issue. Psychological Methods, 12(2), 121–138.](https://doi.org/10.1037/1082-989X.12.2.121)
* https://philippmasur.de/2018/05/23/how-to-center-in-multilevel-models/
* displaying lmer in html tables: https://strengejacke.github.io/sjPlot/articles/tab_mixed.html
::::


## TODO: 
```
- [x] zscore the ratings (ignore sessions)
- [x] predict outcome ratings
- [x] model compare zscore vs just raw score
- [x] include between subject level scores as covariates. AS ALWAYS
- [ ]identify why model doesn't converge for OUTCOME ~ EXPECT + (EXPECT|SUB)
It might be the zero ratings 
- [ ] Drop trials with ratings of 0. 
- [ ] raw cue effect, raw stim effect, raw cue/stimeffect, raw cue/stim + 1 effect
```

### load libraries {.unlisted .unnumbered}
```{r message=FALSE, warning=FALSE, include=FALSE}
library(car)
library(psych)
library(lme4); library(lmerTest)
library(glmmTMB)
library(plyr)
library(dplyr)
library(cueR)
library(ggplot2)
library(plotly)
library(gridExtra)
library(broom.mixed)
library(knitr)
library(grid)
library(ggpubr)

library(dplyr)
library(broom.mixed)
library(effectsize)
```

## computed_enderstofighi
```{r}
compute_enderstofighi <- function(data, sub, outcome, expect, ses, run) {
  maindata <- data %>%
    group_by(!!sym(sub)) %>%
    mutate(OUTCOME = as.numeric(!!sym(outcome))) %>%
    mutate(EXPECT = as.numeric(!!sym(expect))) %>%
    mutate(OUTCOME_cm = mean(OUTCOME, na.rm = TRUE)) %>%
    mutate(OUTCOME_demean = OUTCOME - OUTCOME_cm) %>%
    mutate(EXPECT_cm = mean(EXPECT, na.rm = TRUE)) %>%
    mutate(EXPECT_demean = EXPECT - EXPECT_cm) %>%
    #mutate(OUTCOME_zscore = as.numeric(scale(OUTCOME, center = TRUE, scale = TRUE)[, 1])) %>%
    #mutate(EXPECT_zscore = as.numeric(scale(EXPECT, center = TRUE, scale = TRUE)[, 1])) 
    mutate(OUTCOME_zscore = (OUTCOME - mean(OUTCOME, na.rm = TRUE))/sd(OUTCOME, na.rm = TRUE)) %>% #as.numeric(scale(OUTCOME, center = TRUE, scale = TRUE)[, 1])) %>%
    mutate(EXPECT_zscore = (EXPECT - mean(EXPECT, na.rm = TRUE))/sd(EXPECT, na.rm = TRUE)) #as.numeric(scale(EXPECT, center = TRUE, scale = TRUE)[, 1])) 
  
  data_p2 <- maindata %>%
    arrange(!!sym(sub)) %>%
    group_by(!!sym(sub)) %>%
    mutate(trial_index = row_number())
  
  data_a3 <- data_p2 %>%
    group_by(!!sym(sub), !!sym(ses), !!sym(run)) %>%
    mutate(trial_index = row_number(!!sym(run)))
  
  data_a3lag <- data_a3 %>%
    group_by(!!sym(sub), !!sym(ses), !!sym(run)) %>%
    mutate(lag.OUTCOME_demean = dplyr::lag(OUTCOME_demean, n = 1, default = NA))
  
  # Create Subjectwise Mean, centered in relation to the group mean
  data_a3cmc <- data_a3lag %>%
    ungroup %>%
    mutate(EXPECT_cmc = EXPECT_cm - mean(EXPECT_cm, na.rm=TRUE)) %>%
    mutate(OUTCOME_cmc = OUTCOME_cm - mean(OUTCOME_cm, na.rm=TRUE))
  
  
  # Remove NA values ___________________________________________________________
  data_centered_NA <- data_a3cmc %>% 
    filter(!is.na(OUTCOME)) %>% # Remove NA values
    filter(!is.na(EXPECT))

  return(data_centered_NA)
  
}

```


```{r include=FALSE}
# parameters ___________________________________________________________________
main_dir <- dirname(dirname(getwd()))
datadir <- file.path(main_dir, 'data', 'beh', 'beh02_preproc')
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model09_var", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "pain"
ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0001"
# 1. load data _________________________________________________________________
data <- cueR::df_load_beh(datadir,
                            taskname = taskname,
                            subject_varkey = subject_varkey,
                            iv = iv,
                            exclude = exclude)

column_mapping <- c("src_subject_id" = "subject", 
                    "session_id" = "ses", 
                    "param_run_num" = "run", 
                    "param_task_name" = "runtype",
                    "param_cue_type" = "cue", 
                    "param_stimulus_type" = "stimintensity")

data <- df_rename_columns(data, column_mapping)
data_centered <- cueR::compute_enderstofighi(data, sub="subject",
                                    outcome = "event04_actual_angle",expect= "event02_expect_angle",
                                    ses = "ses", run = "run")

```






## Analysis 1: Pain display distribution of data
Let's look at the distribution of the data. X axis: Y axis: 
Here's the loaded dataset, filtered if Outcome Ratings have NA
```{r fig.width=10, paged.print=TRUE}
# remove NA values first
df.centered_NA <- data_centered %>% filter(!is.na(OUTCOME))  # Remove NA values
head(df.centered_NA)
```


### Plot Outcome rating distribution
Ratings are sorted based on Median values of Outcome rating
```{r include=FALSE}
# Sort the data by median "outcome" in ascending order
sorted_data <- df.centered_NA %>%
  group_by(subject) %>%
  summarize(median_outcome = median(OUTCOME, na.rm = TRUE)) %>%
  arrange(median_outcome) %>%
  select(subject)

# Reorder the "subject" factor based on the sorted order
df.centered_NA$subject <- factor(df.centered_NA$subject, levels = sorted_data$subject)

# Create the ggplot
g <- ggplot(df.centered_NA, aes(x = subject, y = OUTCOME, fill = subject)) +
  geom_boxplot(outlier.shape = NA, width = 1.2, position = position_dodge(2)) +  
  geom_jitter(width = .1, alpha = 0, size = 1) +
  labs(x = "Subject", y = "Pain Outcome Rating") +
  theme_classic() +
  theme(legend.position = "none") +
  scale_x_discrete(breaks = NULL) 

# Convert ggplot object to a plotly object with hover information
g_plotly <- ggplotly(ggplot_largetext(g), tooltip = c("x", "y"))
g_plotly

```

### Identify subjects with narrow IQR
I plan to use this to filter out participants
```{r}
library(dplyr)

# Assuming df.centered_NA is your dataframe and it's already loaded

# Task 1: Top and Bottom 5% Subjects
sorted_data <- df.centered_NA %>%
  group_by(subject) %>%
  summarize(median_outcome = median(OUTCOME, na.rm = TRUE)) %>%
  arrange(median_outcome)

num_subjects <- nrow(sorted_data)
top_bottom_count <- ceiling(num_subjects * 0.05)

top_5_percent_subjects <- head(sorted_data, top_bottom_count)$subject
bottom_5_percent_subjects <- tail(sorted_data, top_bottom_count)$subject

# Task 2: Narrow IQR Subjects
iqr_data <- df.centered_NA %>%
  group_by(subject) %>%
  summarize(IQR = IQR(OUTCOME, na.rm = TRUE)) %>%
  arrange(IQR)

# Output the subjects
cat("Top 5% Subjects based on Median Outcome:\n", toString(as.character(top_5_percent_subjects)), "\n")
cat("Bottom 5% Subjects based on Median Outcome:\n", toString(as.character(bottom_5_percent_subjects)), "\n")

# If you want to see the subjects with the narrowest IQRs
# cat("Subjects with the Narrowest IQRs:\n", head(iqr_data)$subject, "\n")
cat("Subjects with the Narrowest IQRs:\n", toString(as.character(head(iqr_data)$subject)), "\n")
narrowest_iqr_string <- paste0('"', as.character(head(iqr_data)$subject), '"', collapse = ", ")
cat("Subjects with the Narrowest IQRs:\n", narrowest_iqr_string, "\n")

# head(iqr_data)$subject

# Create filter string based on narrow variability
subject_ids <- as.character(head(iqr_data)$subject)
formatted_subjects <- paste0("sub-", sprintf("%04d", as.numeric(subject_ids)))
filter_string <- paste(formatted_subjects, collapse = "|")
filter_string <- paste0("sub-0001|", filter_string)
# Output the filter string
cat("Filter String: ", filter_string, "\n")

```

## Analysis 2: Z score vs. not model comparison
### lmer model compare z score vs nonzscore {-}

Q. how do the coefficients change as a function of Z scoring vs not? 
```{r}
model.z <- lmer(OUTCOME ~ EXPECT_zscore + (EXPECT_zscore|subject), df.centered_NA)
model.nonz <- lmer(OUTCOME ~ EXPECT + (EXPECT|subject), df.centered_NA)
model.cmc <- lmer(OUTCOME ~ EXPECT_demean + EXPECT_cmc + (1|subject), df.centered_NA)

print_dash("model with Z scores")
summary(model.z)

print_dash("model with raw scores, i.e. non Zscores")
summary(model.nonz)

print_dash("model with raw scores CMC and CWC")
summary(model.cmc)

print_dash("model comparison")
anova(model.z, model.nonz)
```




### plot :: subjectwise slopes of Zscore and nonZscore
TODO: change color scheme and increase figure size
```{r include=FALSE}

g.rawscore <- ggplot(df.centered_NA, aes(y = OUTCOME,
                       x = EXPECT,
                       colour = subject, 
                       group = subject), size = .3, colour = 'gray') +
  geom_point(size = .1, alpha = .5) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .3, alpha = .8) +
  theme_classic() +
  theme(legend.position = "none") + 
  coord_fixed(ratio = 1)
g.rawscore <- ggplot_largetext(g.rawscore)

g.zscore <- ggplot(df.centered_NA, aes(y = OUTCOME,
                       x = EXPECT_zscore,
                       colour = subject,
                       group = subject), size = .3, color = 'gray') +
  geom_point(size = .1, alpha = .5) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .3, alpha = 1) +
  theme_classic() + 
  theme(legend.position = "none") + 
  coord_fixed(ratio = 1)
g.zscore <- ggplot_largetext(g.zscore)

gridExtra::grid.arrange(g.rawscore, g.zscore, ncol = 2,
                        widths = c(1, 1.3), heights = c(1, 1))
```


## Analysis 3: across PVC, Are these expectation effects domain-general or domain-specific?
### load entire data of pain,vicarious,cognitive {.unlisted .unnumbered}
```{r include=FALSE}
dataPVC <- cueR::df_load_pvc_beh(datadir,
                              subject_varkey = "src_subject_id",
                            iv = iv,
                            dv = "event04_actual_angle",
                            exclude = filter_string)
# center data
df.PVC_center <- compute_enderstofighi(dataPVC, sub="sub",
                                    outcome = "event04_actual_angle",expect= "event02_expect_angle",
                                    ses = "ses", run = "run")
```

##  Validate: correlation matrix across centered variables

::::{.todolist}The zscores do not seem to be scaled within participant. 
Let's check what's going on.
The mean value should be 0 for all participants
::::

```{r}
library(dplyr)
head(df.PVC_center)
# Assuming df is your dataframe, and 'participant', 'col1', 'col2', 'col3' are your column names
df.PVC_center$subject <- factor(df.PVC_center$sub)
df.PVC_center$OUTCOME <- as.numeric(df.PVC_center$OUTCOME)
df.PVC_center$EXPECT_cmc <- as.numeric(df.PVC_center$EXPECT_cmc)
df.PVC_center$EXPECT_demean <- as.numeric(df.PVC_center$EXPECT_demean)
correlation_matrix_per_participant <- df.PVC_center %>%
  group_by(sub) %>%
  summarize(
    cor_matrix = list(cor(.[, c("OUTCOME", "EXPECT_cmc", "EXPECT_demean", "EXPECT_zscore")], 
                        use = "complete.obs"))
  )
# To view the correlation matrix for the first participant
# correlation_matrix_per_participant$cor_matrix[[1]]

# plot correlatin matrix _______________________________________________________
library(ggplot2)
library(reshape2)
library(dplyr)

# Assuming correlation_matrix_per_participant is the result from the previous step
for(i in 1:nrow(correlation_matrix_per_participant)) {
  participant_id <- correlation_matrix_per_participant$sub[i]
  cor_matrix <- correlation_matrix_per_participant$cor_matrix[[i]]

  # Convert the correlation matrix to long format
  long_cor_matrix <- melt(cor_matrix)
  names(long_cor_matrix) <- c("Var1", "Var2", "value")

  # Plotting
  p <- ggplot(long_cor_matrix, aes(Var1, Var2, fill = value)) +
    geom_tile() +
    scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                         midpoint = 0, limit = c(-1, 1), space = "Lab", 
                         name="Correlation") +
    theme_minimal() +
    ggtitle(paste("Correlation Matrix for Participant", participant_id))

  print(p)
}

```


### plot per participant. Outcome, Expect, demean
```{r}
pain.df <- df.PVC_center[df.PVC_center$runtype == "runtype-pain", ]
sub_0063pain.df <- pain.df[pain.df$sub == "sub-0060",]
head(sub_0063pain.df)
# hist(sub_0063pain.df$EXPECT)
# hist(sub_0063pain.df$EXPECT_zscore)
# hist(sub_0063pain.df$EXPECT_cm)
# hist(sub_0063pain.df$EXPECT_demean)

plot(sub_0063pain.df$EXPECT_demean, sub_0063pain.df$OUTCOME)
plot(sub_0063pain.df$EXPECT_zscore, sub_0063pain.df$OUTCOME)

r <- ggplot(sub_0063pain.df, aes(x = EXPECT)) + 
  geom_histogram(bins = 30, fill = "blue", alpha = 0.7) +
  labs(title = "Histogram of Variable", x = "Expect (Raw)", y = "Outcome")+
  theme_classic()

z <- ggplot(sub_0063pain.df, aes(x = EXPECT_zscore)) + 
  geom_histogram(bins = 30, fill = "blue", alpha = 0.7) +
  labs(title = "Histogram of Variable", x = "Expect (Z)", y = "Outcome")+
  theme_classic()

cmc <- ggplot(sub_0063pain.df, aes(x = EXPECT_cm)) + 
  geom_histogram(bins = 30, fill = "blue", alpha = 0.7) +
  labs(title = "Histogram of Variable", x = "Expect (CMC)", y = "Outcome") +
  theme_classic()
arranged_plots <- (ggpubr::ggarrange(
        r, z, cmc,
        common.legend = FALSE,
        legend = "none",
        ncol = 3,
        nrow = 1,
        widths = c(1,1,1),
        heights = c(1),
        align = "v"
      ))
grid.draw(arranged_plots)
```


## Analysis 3


### lmer model compare z score vs nonzscore
```{r}
pain.df <- df.PVC_center[df.PVC_center$runtype == "runtype-pain", ]
vic.df <- df.PVC_center[df.PVC_center$runtype == "runtype-vicarious", ]
cog.df <- df.PVC_center[df.PVC_center$runtype == "runtype-cognitive", ]
model.pain_z <- lmer(OUTCOME ~ EXPECT_zscore + (EXPECT_zscore|sub), pain.df)
model.vic_z <- lmer(OUTCOME ~ EXPECT_zscore + (EXPECT_zscore|sub), vic.df)
model.cog_z <- lmer(OUTCOME ~ EXPECT_zscore + (EXPECT_zscore|sub), cog.df)
model.pain_raw <- lmer(OUTCOME ~ EXPECT + (EXPECT|sub), pain.df)
model.vic_raw <- lmer(OUTCOME ~ EXPECT + (EXPECT|sub),  vic.df)
model.cog_raw <- lmer(OUTCOME ~ EXPECT + (EXPECT|sub), cog.df)
model.pain_cmc <- lmer(OUTCOME ~ EXPECT_demean + EXPECT_cmc + (1|sub), pain.df)
model.vic_cmc <- lmer(OUTCOME ~ EXPECT_demean + EXPECT_cmc + (1|sub),  vic.df)
model.cog_cmc <- lmer(OUTCOME ~ EXPECT_demean + EXPECT_cmc + (1|sub), cog.df)


model.pain_z <- lmer(OUTCOME ~ EXPECT_zscore + (EXPECT_zscore|sub), pain.df)
model.pain_bothz <- lmer(OUTCOME_zscore ~ EXPECT_zscore + (EXPECT_zscore|sub), pain.df)
model.pain_bothCM <- lmer(OUTCOME_demean ~ EXPECT_demean + (EXPECT_demean|sub), pain.df)
model.pain_CM <- lmer(OUTCOME ~ EXPECT_demean + (EXPECT_demean|sub), pain.df)

print_dash("model with Z scores :: Pain")
summary(model.pain_z)

print_dash("model with Z scores :: Vicarious")
summary(model.vic_z)

print_dash("model with Z scores :: Cognitive")
summary(model.cog_z)

print_dash("model with raw scores, i.e. non Zscores :: Pain")
summary(model.pain_raw)

print_dash("model with raw scores, i.e. non Zscores :: Vicarious")
summary(model.vic_raw)

print_dash("model with raw scores, i.e. non Zscores :: Cognitive")
summary(model.cog_raw)

print_dash("model with raw Pain scores CMC and CWC")
# summary(model.pain_cmc)
sjPlot::tab_model(model.pain_cmc, p.val = "kr", show.df = TRUE)
print_dash("model comparison")
anova(model.pain_z, model.pain_raw)

# _______________________________________________________
# # Example using broom to get a tidied summary
# library(broom)
# 
# tidy_model_pain_z <- tidy(model.pain_z)
# tidy_model_vic_z <- tidy(model.vic_z)
# # ... and so on for the other models
# 
# # Combine tidied summaries into one data frame
# all_tidy_effects <- bind_rows(
#   tidy_model_pain_z %>% mutate(model = "Pain Z"),
#   tidy_model_vic_z %>% mutate(model = "Vicarious Z"),
#   # ... and so on for the other models
# )
# 
# # Print the combined tidied model summaries
# print(all_tidy_effects)
```

### check lmer CMC model
```{r}
sjPlot::tab_model(model.pain_cmc, p.val = "kr", show.df = TRUE)
```


### lmer combined coefficients into table
Since there are multiple models, I combine the coefficients (within subject expectation effects) into one table
```{r include=FALSE}

library(dplyr)
library(broom.mixed)
library(effectsize)

tidy_model_with_name <- function(model, model_name) {
  
  # Standardize parameters _____________________________________________________
  X <- effectsize::standardize_parameters(model, method = "pseudo")

  # Exclude the intercept and grab all other standardized coefficients _________
  beta_stds <- X$Std_Coefficient[X$Parameter != "(Intercept)"]

  # Tidy the model, filter out intercept, and add standardized coefficients ____
  tidy_data <- broom.mixed::tidy(model) %>%
    filter(effect == "fixed", term != "(Intercept)") %>%
    select(term, estimate, p.value) %>%
    mutate(model = model_name)

  # Add the standardized coefficients to the tidy data _________________________
  # Assuming the order of terms in tidy_data matches the order in X
  tidy_data$beta_std <- beta_stds
  tidy_data$task <- strsplit(model_name, " ")[[1]][1]
  
  # Reorder columns as desired _________________________________________________
  tidy_data <- tidy_data %>%
    select(task, model, term, estimate, beta_std, p.value)

  return(tidy_data)
}

# 
tidy_model.pain_z <- tidy_model_with_name(model.pain_z, "Pain Outcome ~ ExpectZ")
tidy_model.vic_z <- tidy_model_with_name(model.vic_z, "Vicarious Outcome ~ ExpectZ")
tidy_model.cog_z <- tidy_model_with_name(model.cog_z, "Cognitive Outcome ~ ExpectZ")

tidy_model.pain_raw <- tidy_model_with_name(model.pain_raw, "Pain Outcome ~ Expect")
tidy_model.vic_raw <- tidy_model_with_name(model.vic_raw, "Vicarious Outcome ~ Expect")
tidy_model.cog_raw <- tidy_model_with_name(model.cog_raw, "Cognitive Outcome ~ Expect")

tidy_model.pain_cmc <- tidy_model_with_name(model.pain_cmc, "Pain Outcome ~ demean + CMC")
tidy_model.vic_cmc <- tidy_model_with_name(model.vic_cmc, "Vicarious Outcome ~ demean + CMC")
tidy_model.cog_cmc <- tidy_model_with_name(model.cog_cmc, "Cognitive Outcome ~ demean + CMC")

tidy_model.pain_z <- tidy_model_with_name(model.pain_z, "Pain Outcome ~ ExpectZ")
tidy_model.pain_bothz <- tidy_model_with_name(model.pain_bothz, "Pain OutcomeZ ~ ExpectZ")
tidy_model.pain_bothCM <- tidy_model_with_name(model.pain_bothCM, "Pain Outcome_demean ~ Expect_demean")
tidy_model.pain_CM <- tidy_model_with_name(model.pain_CM, "Pain Outcome ~ Expect_demean")


# bind all extracted values ____________________________________________________
all_fixed_effects <- bind_rows(
  tidy_model.pain_z,
  tidy_model.vic_z,
  tidy_model.cog_z,
  tidy_model.pain_raw,
  tidy_model.vic_raw,
  tidy_model.cog_raw,
  tidy_model.pain_cmc,
  tidy_model.vic_cmc,
  tidy_model.cog_cmc,
  tidy_model.pain_z,
  tidy_model.pain_bothz,
  tidy_model.pain_bothCM, 
  tidy_model.pain_CM
)
```


```{r}
library(DT)
# Print or use kable/DT for a nicer table in R Markdown ________________________
DT::datatable(all_fixed_effects,
                            options = list(
                              pageLength = 25,
                columnDefs = list(
                  list(targets = c(4,5,6),  # Assuming 2nd and 3rd columns are numeric
                       render = JS(
                         "function(data, type, row, meta) {",
                         "return type === 'display' || type === 'filter' ?",
                         "parseFloat(data).toFixed(3) : data;",
                         "}"
                       )
                  )
                )
              ),
             caption = "Summary of Non-Intercept Fixed Effects across Models")

```

### plot how much of the CMCs predict outcome ratings
### plot how much of the demeans predict outcome ratings
```{r}
library(ggplot2)
library(gridExtra)
library(grid)

plot_endertofighi <- function(data, taskname, color_low="gray", color_high="black") {
  runtype_filter <- paste0("runtype-", taskname)
  data$sub_numeric <- as.numeric(as.factor(data$sub))
  # Plot for demean ____________________________________________________________
  g.Odemean <- ggplot(data, 
                     aes(y = OUTCOME_demean, x = EXPECT_demean, colour = sub_numeric, group = sub), size = .3, color = 'gray') +
    #geom_point(size = .1) +
    geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = .3) +
    theme_classic() +
    scale_colour_gradient(low = color_low, high = color_high) +
    # theme(legend.position = "none") + 
        theme(legend.position = "none",
          plot.margin = margin(t = .3, r = .1, b = .1, l = .1, unit = "pt")) + 
    coord_fixed(ratio = 1) 
    # ylim(0,200)
  g.Odemean <- ggplot_largetext(g.Odemean)  # Assuming ggplot_largetext is a defined function
  

  # Plot for demean ____________________________________________________________
  g.demean <- ggplot(data, 
                     aes(y = OUTCOME, x = EXPECT_demean, colour = sub_numeric, group = sub), size = .3, color = 'gray') +
    geom_point(size = .1, alpha = .1) +
    geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = .3) +
    theme_classic() +
    scale_colour_gradient(low = color_low, high = color_high) +
    # theme(legend.position = "none") + 
        theme(legend.position = "none",
          plot.margin = margin(t = .3, r = .1, b = .1, l = .1, unit = "pt")) + 
    coord_fixed(ratio = 1) +
    ylim(0,200)
  g.demean <- ggplot_largetext(g.demean)  # Assuming ggplot_largetext is a defined function
  
    # Plot for Cluster-wise means ________________________________________________
  g.Ocm <- ggplot(data, 
                 aes(y = OUTCOME, x = EXPECT_cm, colour = sub_numeric, group = sub), size = .3, color = 'gray') +
    #geom_point(size = .1, alpha = .1) +
  stat_summary(
    fun = mean, geom = "point",
    aes(group = sub), # Group by subject
    size = 1
  ) +
    scale_colour_gradient(low = color_low, high = color_high) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = color_low) +  # Add the identity line
    geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = 1) + #size = .3) +
    theme_classic() + 
        theme(legend.position = "none",
              plot.margin = margin(t = .3, r = .1, b = .1, l = .1, unit = "pt")) + 
    coord_fixed(ratio = 1) +
    ylim(0,200)
  g.Ocm <- ggplot_largetext(g.Ocm)  # Assuming ggplot_largetext is a defined function
  
  
  
  
  # Plot for Cluster-wise means ________________________________________________
  g.cm <- ggplot(data, 
                 aes(y = OUTCOME_cm, x = EXPECT_cm, colour = sub_numeric, group = sub), size = .3, color = 'gray') +
      stat_summary(
    fun.y = mean, geom = "point",
    aes(group =sub_numeric), #EXPECT_cm),
    size = 1
  ) +
   geom_point(size = .1, alpha = .1) +
    scale_colour_gradient(low = color_low, high = color_high) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = color_low) +  # Add the identity line
    geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = 1) + #size = .3) +
    theme_classic() + 
        theme(legend.position = "none",
              plot.margin = margin(t = .3, r = .1, b = .1, l = .1, unit = "pt")) + 
    coord_fixed(ratio = 1) +
    ylim(-10,200)
  g.cm <- ggplot_largetext(g.cm)  # Assuming ggplot_largetext is a defined function
  
  
  # Plot for Zscore ____________________________________________________________
  g.z <- ggplot(data, 
                 aes(y = OUTCOME, x = EXPECT_zscore, colour = sub_numeric, group = sub), size = .3, color = 'gray') +
    #geom_point(size = .1) +
    scale_colour_gradient(low = color_low, high = color_high) +
    geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = .3) +
    theme_classic() + 
        theme(legend.position = "none", plot.margin = margin(t = .3, r = .1, b = .1, l = .1, unit = "pt")) + 

    coord_fixed(ratio = 1)
  g.z <- ggplot_largetext(g.z)  # Assuming ggplot_largetext is a defined function
  
  
    # Plot for Zscore ____________________________________________________________
  g.z2 <- ggplot(data, 
                 aes(y = OUTCOME_zscore, x = EXPECT_zscore, colour = sub_numeric, group = sub), size = .3, color = 'gray') +
    #geom_point(size = .1) +
    scale_colour_gradient(low = color_low, high = color_high) +
    geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = .3) +
    theme_classic() + 
        theme(legend.position = "none", plot.margin = margin(t = .3, r = .1, b = .1, l = .1, unit = "pt")) + 

    coord_fixed(ratio = 1)
  g.z2 <- ggplot_largetext(g.z2)  # Assuming ggplot_largetext is a defined function
  
  # Combine plots
  title_text <- paste(tools::toTitleCase(taskname), "task: within-subject centered vs. subject-cluster means\n")
  title_grob <- grid::textGrob(title_text, gp = gpar(fontsize = 18), vjust = 1)

  # grid.draw(gridExtra::grid.arrange(g.demean, g.cm, g.z, ncol = 3,
  #                         widths = c(1,  1, 1), heights = c(1, 1, 1), 
  #                         top = title_grob
  # ))
  
  
    # Plot for Cluster-wise means ________________________________________________
  g.cmc <- ggplot(data, 
                 aes(y = OUTCOME_cmc, x = EXPECT_cmc, colour = sub_numeric, group = sub), size = .3, color = 'gray') +
      stat_summary(
    fun.y = mean, geom = "point",
    aes(group =sub_numeric), #EXPECT_cm),
    size = 1
  ) +
   geom_point(size = .1, alpha = .1) +
    scale_colour_gradient(low = color_low, high = color_high) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = color_low) +  # Add the identity line
    geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = 1) + #size = .3) +
    theme_classic() + 
        theme(legend.position = "none",
              plot.margin = margin(t = .3, r = .1, b = .1, l = .1, unit = "pt")) + 
    coord_fixed(ratio = 1) +
    ylim(-10,200)
  g.cmc <- ggplot_largetext(g.cmc)  # Assuming ggplot_largetext is a defined function
  
      # Plot for raw means ________________________________________________
  g.raw <- ggplot(data, 
                 aes(y = OUTCOME, x = EXPECT, colour = sub_numeric, group = sub), size = .3, color = 'gray') +
  #     stat_summary(
  #   fun.y = mean, geom = "point",
  #   aes(group =sub_numeric), #EXPECT_cm),
  #   size = .1, alpha = .1
  # ) +
   geom_point(size = .1, alpha = .1) +
    scale_colour_gradient(low = color_low, high = color_high) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = color_low) +  # Add the identity line
    geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = .3) + #size = .3) +
    theme_classic() + 
        theme(legend.position = "none",
              plot.margin = margin(t = .3, r = .1, b = .1, l = .1, unit = "pt")) + 
    coord_fixed(ratio = 1) +
    ylim(-10,200)
  g.raw <- ggplot_largetext(g.raw)  # Assuming ggplot_largetext is a defined function
  
  
  arranged_plots <- (ggpubr::ggarrange(
        g.demean, g.Ocm, g.cm, g.z, g.z2, g.Odemean, g.cmc, g.raw,
        common.legend = FALSE,
        legend = "none",
        ncol = 4,
        nrow = 2,
        widths = c(1,1,1),
        heights = c(1,1),
        align = "v"
      ))
  #return(wbeffect)
  
  annotated_plots <- ggpubr::annotate_figure(arranged_plots,
                                   top = title_grob)
  grid.draw(annotated_plots)

  
}

#plot_endertofighi(df.PVC_center[df.PVC_center$runtype == "runtype-pain", ], "pain")
```

```{r echo=FALSE, fig.height=5, fig.width=10}
cueR::plot_endertofighi(df.PVC_center[df.PVC_center$runtype == "runtype-pain", ], "pain", color_low = "red", color_high = "darkred")

cueR::plot_endertofighi(df.PVC_center[df.PVC_center$runtype == "runtype-vicarious", ], "vicarious",color_low = "#5bba6f", color_high = "#054a29" )

cueR::plot_endertofighi(df.PVC_center[df.PVC_center$runtype == "runtype-cognitive", ], "cognitive", color_low = "#caf0f8", color_high = "#03045e")
```


```{r}
subjectwise <- meanSummary_2continuous(df.PVC_center[df.PVC_center$runtype == "runtype-pain", ], 
                                            c("sub"),"OUTCOME", "EXPECT")
subjectwise$EXPECT_cm <- subjectwise$DV2_mean_per_sub
subjectwise$OUTCOME_cm <- subjectwise$DV1_mean_per_sub
color_low = "red"; color_high = "darkred"
    # Plot for Cluster-wise means ________________________________________________
# cueR::plot_ggplot_correlation(subjectwise, y = DV1_mean_per_sub, x = DV2_mean_per_sub,
#                         p_acc = 0.001, r_acc = 0.001, limit_min = 0, limit_max = 200, label_position = 180)
subjectwise$sub_numeric <- as.numeric((subjectwise$sub))
g.manualOcm <- ggplot(subjectwise,
                 aes(y = OUTCOME_cm, x = EXPECT_cm, colour = sub_numeric, group = sub), size = .3, color = ) +
    geom_point(size = 2, alpha = 1, color = "red") +
  # stat_summary(
  #   fun.y = mean, geom = "point",
  #   aes(group = sub), # Group by subject
  #   size = 1
  # ) +
    scale_colour_gradient(low = color_low, high = color_high) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = color_low) +  # Add the identity line
    #geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = 1) + #size = .3) +
    theme_classic() +
        theme(legend.position = "none",
              plot.margin = margin(t = .3, r = .1, b = .1, l = .1, unit = "pt")) +
    coord_fixed(ratio = 1) +
    ylim(0,200)
  g.manualOcm <- ggplot_largetext(g.manualOcm)  # Assuming ggplot_largetext is a defined function
  g.manualOcm

#### TODO: DEBUG WHY?
  mean_xy <- function(x, y) {
  data.frame(x = mean(x, na.rm = TRUE), y = mean(y, na.rm = TRUE))
}
df.PVC_center$sub_numeric <- as.numeric(df.PVC_center$sub)
    g.Ocm <- ggplot(df.PVC_center[df.PVC_center$runtype == "runtype-pain", ],
                 aes(y = OUTCOME, x = EXPECT_cm, colour = sub_numeric, group = as.factor(sub)), size = .3, color = 'gray') +
    #geom_point(size = .1, alpha = .1) +
  stat_summary(
    fun.data = mean_xy, geom = "point",
    aes(group = as.factor(sub)), # Group by subject
    size = 1
  ) +
    scale_colour_gradient(low = color_low, high = color_high) +
    geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = color_low) +  # Add the identity line
    geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = 1) + #size = .3) +
    theme_classic() +
        theme(legend.position = "none",
              plot.margin = margin(t = .3, r = .1, b = .1, l = .1, unit = "pt")) +
    coord_fixed(ratio = 1) +
    ylim(0,200)
  g.Ocm <- ggplot_largetext(g.Ocm)  # Assuming ggplot_largetext is a defined function
  g.Ocm

  
# Checks
library(dplyr)
group_counts <- df.PVC_center %>% count(sub)
print(group_counts)

# plot
ggplot(df.PVC_center, aes(x = EXPECT_cm, y = OUTCOME, color = as.factor(sub))) +
  geom_point() + theme(legend.position = "none")

```


> Demeaning has a similar efect as zscoring, the only difference is that the mean is forced to 0 and the standard deviation 1 for the zscore. 
in a sense, both are removing the between subject effects and homing in onthe within subject effects. 


## Analysis 4: Random effects of Expectation. extract subjectwise coefficients. see if they are similar across tasks. 
#### function; extract random effect of expectation
```{r}
extract_fix_rand_effect <- function(model, taskname){
fixEffect <<- as.data.frame(fixef(model))
randEffect <<- as.data.frame(ranef(model))


randEffect$newcoef <- mapvalues(randEffect$term,
    from = c(as.character(unique(randEffect$term)[1]),
             as.character(unique(randEffect$term)[2])
             ),
    to = c("rand_intercept", "rand_withinexpect" )
)

rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
wide_rand <- tidyr::spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = colnames(wide_fix)[1],
    fix_withinexpect = colnames(wide_fix)[2],
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)
return(new_total)
}
```

```{r}
range(df.PVC_center[df.PVC_center$runtype == "runtype-pain", "EXPECT_cmc"])
range(df.PVC_center[df.PVC_center$runtype == "runtype-pain", "EXPECT_demean"])
cueR::print_dash("Correlation Pain")
cor(df.PVC_center[df.PVC_center$runtype == "runtype-pain", c("OUTCOME", "EXPECT_demean","EXPECT_cm", "EXPECT_cmc")])
cueR::print_dash("Correlation Vicarious")
cor(df.PVC_center[df.PVC_center$runtype == "runtype-vicarious", c("OUTCOME", "EXPECT_demean","EXPECT_cm", "EXPECT_cmc")])
cueR::print_dash("Correlation Cognitive")
cor(df.PVC_center[df.PVC_center$runtype == "runtype-cognitive", c("OUTCOME", "EXPECT_demean","EXPECT_cm", "EXPECT_cmc")])

model.pain_cmc <- lmer(OUTCOME ~ EXPECT_demean + EXPECT_cmc + (EXPECT_demean|sub), df.PVC_center[df.PVC_center$runtype == "runtype-pain", ], )
model.vic_cmc <- lmer(OUTCOME ~ EXPECT_demean + EXPECT_cmc + (EXPECT_demean|sub), df.PVC_center[df.PVC_center$runtype == "runtype-vicarious", ])
model.cog_cmc <- lmer(OUTCOME ~ EXPECT_demean + EXPECT_cmc + (EXPECT_demean|sub), df.PVC_center[df.PVC_center$runtype == "runtype-cognitive", ])
cueR::print_dash("lmer Pain")
summary(model.pain_cmc)
cueR::print_dash("lmer Vicarious")
summary(model.vic_cmc)
cueR::print_dash("lmer Cognitive")
summary(model.cog_cmc)
```

```{r}
# stack random effects across pain, vicarious, cognitive task __________________
dfP <- extract_fix_rand_effect(model.pain_cmc, "pain")
dfV <- extract_fix_rand_effect(model.vic_cmc, "vicarious")
dfC <- extract_fix_rand_effect(model.cog_cmc, "cognitive")
pvc_rand <- reshape::merge_recurse(list(dfP, dfV, dfC))
colnames(pvc_rand)


# subset data with just the random slopes ______________________________________
pvc_rand_within_subset <- subset(pvc_rand, select = c(task, subj, rand_withinexpect))
pvc_rand_cue <- tidyr::spread(pvc_rand_within_subset, key = task, value = rand_withinexpect)


# plot per task and aggregate __________________________________________________
pv <- cueR::plot_ggplot_correlation(data = pvc_rand_cue, x = 'vicarious', y = 'pain', 
                                    p_acc = 0.001, r_acc = 0.01, 
                                    limit_min = -.75, limit_max = .75, label_position = .6)
vc <- cueR::plot_ggplot_correlation(data = pvc_rand_cue, x = 'cognitive', y = 'vicarious', 
                                    p_acc = 0.001, r_acc = 0.01, 
                                    limit_min = -.75, limit_max = .75, label_position = .6)
cp <- cueR::plot_ggplot_correlation(data = pvc_rand_cue, x = 'pain', y = 'cognitive', 
                                    p_acc = 0.001, r_acc = 0.01, 
                                    limit_min = -.75, limit_max = .75, label_position = .6)

plots <- ggpubr::ggarrange(pv, vc, cp, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
title_text <- paste(tools::toTitleCase("individual differences\n - expectation effects on outcome ratings"))
title_grob <- grid::textGrob(title_text, gp = gpar(fontsize = 18), vjust = 1)
plots_title <- annotate_figure(plots, top = title_grob)


# save plots ___________________________________________________________________
# save_plotname <- file.path(
#     analysis_dir,
#     paste("randeffect_scatterplot_task-all_",
#         as.character(Sys.Date()), ".png",
#         sep = ""
#     )
# )
# ggsave(save_plotname, width = 10, height = 3)
plots_title
```

## Random effect distribution
```{r}
library(tidyr)
library(ggplot2)

# Reshape the data to long format ______________________________________________
long_data <- pivot_longer(pvc_rand_cue, cols = c(pain, vicarious, cognitive), names_to = "task", values_to = "expectation_randomeffects")
long_data$task <- factor(long_data$task, levels = c("pain", "vicarious", "cognitive"))
custom_colors <- c("pain" = "#941100", "vicarious" = "#008F51", "cognitive" = "#011891")

# Plotting all three distributions in one plot ______________________________________________
ggplot(long_data, aes(x = expectation_randomeffects, fill = task)) +
    geom_histogram(position = "identity", alpha = 0.5, bins = 30) +
    scale_fill_manual(values = custom_colors) +
  scale_color_manual(values = custom_colors) +
    geom_density(aes(color = task), size = 1.2, alpha = 1, fill = NA) +
    facet_wrap(~ task) +
    theme_classic() +
    ggtitle("Random effects of Expectation ratings - distributions of Pain, Vicarious, and Cognitive")

# overlay at once ______________________________________________
# Plotting all three distributions overlaid in one plot
ggplot(long_data, aes(x = expectation_randomeffects, fill = task)) +
    geom_histogram(position = "identity", alpha = 0.5, bins = 50, aes(y = ..density..)) +
    #geom_density(alpha = 0.5, size = .5) +
    geom_density(aes(color = task), size = 1.2, alpha = 1, fill = NA) +
    scale_fill_manual(values = custom_colors) +
    scale_color_manual(values = custom_colors) +
    theme_classic() +
    ggtitle("Random effects of Expectation ratings - distributions of Pain, Vicarious, and Cognitive")
```


```{r}
# Random effect ________________________________________________________________
# fixEffect <<- as.data.frame(fixef(model.pain_cmc))
# randEffect <<- as.data.frame(ranef(model.pain_cmc))
# 
# 
# randEffect$newcoef <- mapvalues(randEffect$term,
#     from = c(as.character(unique(randEffect$term)[1]),
#              as.character(unique(randEffect$term)[2])
#              ),
#     to = c("rand_intercept", "rand_withinexpect" )
# )
# 
# rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
# wide_rand <- tidyr::spread(rand_subset, key = newcoef, value = condval)
# 
# wide_fix <- do.call(
#     "rbind",
#     replicate(nrow(wide_rand),
#         as.data.frame(t(as.matrix(fixEffect))),
#         simplify = FALSE
#     )
# )
# rownames(wide_fix) <- NULL
# new_wide_fix <- dplyr::rename(wide_fix,
#     fix_intercept = colnames(wide_fix)[1],
#     fix_withinexpect = colnames(wide_fix)[2],
# )
# 
# total <- cbind(wide_rand, new_wide_fix)
# total$task <- taskname
# new_total <- total %>% dplyr::select(task, everything())
# new_total <- dplyr::rename(total, subj = grp)
# 
# rand_savefname <- file.path(
#     analysis_dir,
#     paste("randeffect_task-", taskname, "_",
#         as.character(Sys.Date()), "_outlier-cooksd.csv",
#         sep = ""
#     )
# )
# write.csv(new_total, rand_savefname, row.names = FALSE)

###################################### reference
    cooksd <- lmer_onefactor_cooksd(data, taskname, iv, dv, subject, dv_keyword, model_savefname, print_lmer_output) # run lmer
    influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data$subject)))))])
    data_screen <- data[-influential, ]

    ## summary statistics
    subjectwise <- meanSummary(data_screen, c(subject, iv), dv)
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = subjectwise_mean, # variable created from above
        withinvars = c(iv), # iv
        idvar = "subject"
    )

    ## designate plot save location
    ggtitle <- paste0(str_to_title(taskname), ggtitle_phrase, " N = (", length(unique(data$subject)), ")");
    title <- paste0(str_to_title(taskname), " - ", str_to_title(dv_keyword))
    w = 5; h = 3;
    plot_savefname <- file.path(analysis_dir,
                                paste0("raincloud_task", taskname,"iv-", iv_keyword, "_dv-rating-", dv_keyword,"_", as.character(Sys.Date()), ".png")
                                )

    # plot_rainclouds_onefactor
    p1 <- plot_halfrainclouds_onefactor(
        subjectwise, groupwise,
        iv, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name,ylim,
        w, h, dv_keyword, color_scheme, plot_savefname
    )
randEffect$newcoef <- mapvalues(randEffect$term,
    from = c(as.character(unique(randEffect$term)[1]),
             as.character(unique(randEffect$term)[2])
             ),
    to = c("rand_intercept", "rand_cue")
)

rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = colnames(wide_fix)[1],
    fix_cue = colnames(wide_fix)[2],
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",
        as.character(Sys.Date()), "_outlier-cooksd.csv",
        sep = ""
    )
)
write.csv(new_total, rand_savefname, row.names = FALSE)
```


## Analysis 5: Buchel. plot the distribution of stimulus intensity as a function of pain sensitivity people


## Analysis 6: create raw/zscore cue effect
TODO: create new Rmd

```{r}
head(df.PVC_center)
```

```{r}

dv <- "OUTCOME"

# 3. calculate difference scores and summarize _____________________________
sub_diff <- subset(df.PVC_center,
                   select = c("sub", "ses", "run", "task", "stimintensity", "cuetype", dv))
head(sub_diff)
sub_diff_NA <- sub_diff %>% filter(!is.na(dv))  # drop NA
# ___ 1) first, summarize each condition _______________________________________
subjectwise <- meanSummary(sub_diff_NA, c(
    "sub", "ses", "run",
    "task", "cuetype",
    "stimintensity"), dv)
# ___ 2) spread out high and low cue columns ___________________________________
mean_outcome <- subjectwise[1:(length(subjectwise) - 1)]
wide <- mean_outcome %>%
    tidyr::spread(cuetype, mean_per_sub)
# ___ 3) calculate difference score "cue effect" _______________________________
wide$diff <- wide$`cuetype-high` - wide$`cuetype-low`
subjectwise_diff <- meanSummary(wide, c("sub", "task"), "diff")
subjectwise_NA <- subjectwise_diff %>% filter(!is.na(sd)) # drop na values
# ___ 4) calculate group wise contrast  _______________________________________
groupwise_diff <- Rmisc::summarySEwithin(
    data = subjectwise_NA,
    measurevar = "mean_per_sub", # variable created from above
    withinvars = "task", # iv
    idvar = "sub"
)
head(groupwise_diff)
# save dataframe _______________________________________________________________
sorted_df <- subjectwise_diff %>%
  dplyr::arrange(task) %>%
  dplyr::rename(cue_contrast_high_gt_low = mean_per_sub)
# write.csv(sorted_df, file = file.path(main_dir,"analysis", "mixedeffect", "dataframes", "beh_cueeffect_rawoutcome.csv"), row.names = FALSE)

# TODO: create json file for describing file metadata. BIDS format please
# column_metadata <- list(
#   sub = list(
# description = "subject id in BIDS formats"
# labels = "sub-%04d"
# ),
#   task = list(
#     description = "Task performed by the subject in cue expectancy task",
#     generation_info = "counter balanced across runs. However number of runs performed are included in computations. Subjects may have different frequencies of tasks performed. Some may have completed 6 pain runs, whereas other may have completed 2 pain runs, depending on how many sessions they attended. ",
#     labels = c("pain", "vicarious", "cognitive")
#   ),
#   cue_contrast_high_gt_low = list(
#     description = "Mean cue difference (high vs. low cue) per subject",
#     generation_info = "Calculated as the mean of cue effects across participants, per task ",
#   ),
#   sd = list(
#     description = "Standard deviasion",
#     generation_info = "How column3 was generated",
#     labels = c("Label1", "Label2", "Label3")
#   )
# )

```


> Summary: 

### plot {.unlisted .unnumbered}
We'll plot Y as a function of A and B
X axis: 
Y axis:
Each data point indicates ... 
```{r fig.height=10, fig.width=10}

```
> Conclusion:


:::: {.infobox}
Include the actual content here. here are my thoughts
::::

:::: {.refbox}
Include the actual content here. here are my thoughts
::::

