# beh ::  Different scaling methods ~  Cue effects {#cueeffects}

## What is the purpose of this notebook? {.unlisted .unnumbered}

Here, we extract the cue effects across different types of ratings
* cue effects of raw outcome rating ("cue_raw_outcome")
* cue effects of z-scored outcome rating ("cue_z_outcome")
* stim effects of raw outcome rating ("stim_raw_outcome")
* stim effects of z-scored outcome rating ("stim_z_outcome")
* cue effects / stim effect using raw outcome rating ("cuestim_raw_outcome")
* cue effects / stim effects using z score ratings  ("cuestim_z_outcome")
* regularized cue effects +1 / stim effect +1 using raw outcome rating ("cuestim_raw_outcome_reg")
* regularized cue effects / stim effects using z score ratings ("cuestim_z_outcome_reg")


### load libraries {.unlisted .unnumbered}
```{r message=FALSE, warning=FALSE}
library(car)
library(psych)
library(lme4); library(lmerTest)
library(glmmTMB)
library(plyr)
library(dplyr)
library(cueR)
library(ggplot2)
library(plotly)
library(gridExtra)
library(broom.mixed)
library(knitr)
library(grid)
library(ggpubr)

library(dplyr)
library(broom.mixed)
library(effectsize)
library(corrplot)
```


```{r}
compute_enderstofighi <- function(data, sub, outcome, expect, ses, run) {
  maindata <- data %>%
    group_by(!!sym(sub)) %>%
    mutate(OUTCOME = as.numeric(!!sym(outcome))) %>%
    mutate(EXPECT = as.numeric(!!sym(expect))) %>%
    mutate(OUTCOME_cm = mean(OUTCOME, na.rm = TRUE)) %>%
    mutate(OUTCOME_demean = OUTCOME - OUTCOME_cm) %>%
    mutate(EXPECT_cm = mean(EXPECT, na.rm = TRUE)) %>%
    mutate(EXPECT_demean = EXPECT - EXPECT_cm) %>%
    #mutate(OUTCOME_zscore = as.numeric(scale(OUTCOME, center = TRUE, scale = TRUE)[, 1])) %>%
    #mutate(EXPECT_zscore = as.numeric(scale(EXPECT, center = TRUE, scale = TRUE)[, 1])) 
    mutate(OUTCOME_zscore = (OUTCOME - mean(OUTCOME, na.rm = TRUE))/sd(OUTCOME, na.rm = TRUE)) %>% #as.numeric(scale(OUTCOME, center = TRUE, scale = TRUE)[, 1])) %>%
    mutate(EXPECT_zscore = (EXPECT - mean(EXPECT, na.rm = TRUE))/sd(EXPECT, na.rm = TRUE)) #as.numeric(scale(EXPECT, center = TRUE, scale = TRUE)[, 1])) 
  
  data_p2 <- maindata %>%
    arrange(!!sym(sub)) %>%
    group_by(!!sym(sub)) %>%
    mutate(trial_index = row_number())
  
  data_a3 <- data_p2 %>%
    group_by(!!sym(sub), !!sym(ses), !!sym(run)) %>%
    mutate(trial_index = row_number(!!sym(run)))
  
  data_a3lag <- data_a3 %>%
    group_by(!!sym(sub), !!sym(ses), !!sym(run)) %>%
    mutate(lag.OUTCOME_demean = dplyr::lag(OUTCOME_demean, n = 1, default = NA))
  
  # Create Subjectwise Mean, centered in relation to the group mean
  data_a3cmc <- data_a3lag %>%
    ungroup %>%
    mutate(EXPECT_cmc = EXPECT_cm - mean(EXPECT_cm, na.rm=TRUE)) %>%
    mutate(OUTCOME_cmc = OUTCOME_cm - mean(OUTCOME_cm, na.rm=TRUE))
  
  
  # Remove NA values ___________________________________________________________
  data_centered_NA <- data_a3cmc %>% 
    filter(!is.na(OUTCOME)) %>% # Remove NA values
    filter(!is.na(EXPECT))

  return(data_centered_NA)
  
}
```

```{r include=FALSE}
main_dir <- dirname(dirname(getwd()))
datadir <- file.path(main_dir, 'data', 'beh', 'beh02_preproc')
filter_string = "sub-0001"
dataPVC <- cueR::df_load_pvc_beh(datadir,
                              subject_varkey = "src_subject_id",
                            iv = iv,
                            dv = "event04_actual_angle",
                            exclude = filter_string)
# center data
df.PVC_center <- compute_enderstofighi(dataPVC, sub="sub",
                                    outcome = "event04_actual_angle",expect= "event02_expect_angle",
                                    ses = "ses", run = "run")
```

### display distribution of data
Let's look at the distribution of the data. X axis: Y axis: 
```{r paged.print=TRUE}
head(df.PVC_center)
#colnames(df.PVC_center)
```
> Summary: 


## function: compute cue effects
```{r}
#' Compute Cue Effect
#'
#' This function processes a dataframe to compute the cue effect. It involves 
#' subsetting and filtering the data, summarizing conditions, calculating 
#' difference scores, and calculating group-wise contrast. The function also 
#' allows renaming of the resultant columns.
#'
#' @param df A dataframe containing the relevant data.
#' @param dv The name of the dependent variable in the dataframe.
#' @param new_col_name The new name for the column that will be created as a result 
#'        of computing the cue effect.
#' @return A dataframe with the computed cue effect, sorted by task, with a new 
#'         column for the cue effect and its standard deviation, renamed as specified.
#' @import dplyr
#' @import tidyr
#' @import Rmisc
#' @export
#' @examples
#' # Assuming df is a dataframe with the necessary structure and "OUTCOME" is your dependent variable:
#' result <- compute_cueeffect(df, "OUTCOME", "new_cue_effect")
compute_cueeffect <- function(df, dv, new_col_name) {
  library(dplyr)
  library(tidyr)
  library(Rmisc)

  # 1) Subset and filter data __________________________________________________
  df$task <- factor(df$task)
  sub_diff <- subset(df, select = c("sub", "ses", "run", "task", "stimintensity", "cuetype", dv))
  sub_diff_NA <- sub_diff %>% filter(!is.na(dv))

  # 2) Summarize each condition and spread out columns _________________________
  subjectwise <- meanSummary(sub_diff_NA, c("sub", "ses", "run", "task", "cuetype", "stimintensity"), dv)
  mean_outcome <- subjectwise[1:(length(subjectwise) - 1)]
  wide <- mean_outcome %>% tidyr::spread(cuetype, mean_per_sub)

  # 3) Calculate difference score ______________________________________________
  wide$diff <- wide$`cuetype-high` - wide$`cuetype-low`
  subjectwise_diff <- meanSummary(wide, c("sub", "task"), "diff")
  subjectwise_NA <- subjectwise_diff %>% filter(!is.na(sd))

  # 4) Calculate group wise contrast ___________________________________________
  groupwise_diff <- summarySEwithin(data = subjectwise_NA, measurevar = "mean_per_sub", withinvars = "task", idvar = "sub")
  sd_col <- paste0(new_col_name, "_sd")
  # sort data based on task and rename _________________________________________
  sorted_df <- subjectwise_diff %>%
    arrange(task) %>%
    rename(!!new_col_name := mean_per_sub, 
           !!sd_col := sd
           )

  return(sorted_df)
}

```

## function: compute stim effects
```{r}
#' Compute Stimulus Effect
#'
#' This function calculates the stimulus effect based on the provided dataframe.
#' It filters the data, computes summary statistics, calculates difference scores,
#' and optionally renames the resulting columns.
#'
#' @param df Dataframe containing the data to be analyzed.
#' @param dv Name of the dependent variable column in `df`.
#' @param new_col_name New column name for the renamed mean_per_sub column.
#' @return A dataframe with the computed stimulus effect, sorted by task, 
#'         and with columns optionally renamed.
#' @import dplyr
#' @import tidyr
#' @import Rmisc
#' @export
#' @examples
#' # Assuming df is your dataframe and "OUTCOME" is your dependent variable:
#' result <- compute_stimeffect(df, "OUTCOME", "new_mean_outcome")
compute_stimeffect <- function(df, dv, new_col_name) {
  # 1) Subset and filter data __________________________________________________
  df$task <- factor(df$task)
  sub_diff <- subset(df, select = c("sub", "ses", "run", "task", "stimintensity", "cuetype", dv))
  sub_diff_NA <- sub_diff %>% filter(!is.na(dv))

 
  # 2) Summarize each condition and spread out columns _________________________
  subjectwise <- meanSummary(sub_diff_NA, c("sub", "ses", "run", "task", "cuetype", "stimintensity"), dv)
  mean_outcome <- subjectwise[1:(length(subjectwise) - 1)]
  wide <- mean_outcome %>% tidyr::spread(stimintensity, mean_per_sub)

  # 3) Calculate difference score ______________________________________________
  wide$diff <- wide$high - wide$low
  subjectwise_diff <- meanSummary(wide, c("sub", "task"), "diff")
  subjectwise_NA <- subjectwise_diff %>% filter(!is.na(sd))
  # 
  # # 4) Calculate group wise contrast _________________________________________
  groupwise_diff <- Rmisc::summarySEwithin(data = subjectwise_NA, 
                                           measurevar = "mean_per_sub", 
                                           withinvars = "task", 
                                           idvar = "sub")
  # 
  sd_col <- paste0(new_col_name, "_sd")
  # sort data based on task and rename _________________________________________
  sorted_df <- subjectwise_diff %>%
    arrange(task) %>%
    rename(!!new_col_name := mean_per_sub, 
           !!sd_col := sd
           )
  return(sorted_df)
} 
```


## compute the cue and stim effects for further analysis {.unlisted .unnumbered}


```{r}
# calculate cue & stim effects per participant and rename column _______________
cue_raw_outcome <- compute_cueeffect(df.PVC_center, dv = "OUTCOME", new_col_name = "cue_raw_outcome")
cue_z_outcome <- compute_cueeffect(df.PVC_center, dv = "OUTCOME_zscore", new_col_name = "cue_z_outcome")
cue_raw_expect <- compute_cueeffect(df.PVC_center, dv = "EXPECT", new_col_name = "cue_raw_expect")
cue_z_expect <- compute_cueeffect(df.PVC_center, dv = "EXPECT_zscore", new_col_name = "cue_z_expect")

rawstim_outcome <- compute_stimeffect(df.PVC_center, dv = "OUTCOME", new_col_name = "stim_raw_outcome")
zstim_outcome <- compute_stimeffect(df.PVC_center, dv = "OUTCOME_zscore", new_col_name = "stim_z_outcome")
rawstim_expect <- compute_stimeffect(df.PVC_center, dv = "EXPECT", new_col_name = "stim_raw_expect")
zstim_expect <- compute_stimeffect(df.PVC_center, dv = "EXPECT_zscore", new_col_name = "stim_z_expect")


# Merging all dataframes _______________________________________________________
merged_df <- cue_raw_outcome %>%
  full_join(cue_z_outcome, by = c("sub", "task")) %>%
  full_join(cue_raw_expect, by = c("sub", "task")) %>%
  full_join(cue_z_expect, by = c("sub", "task")) %>%
  full_join(rawstim_outcome, by = c("sub", "task")) %>%
  full_join(zstim_outcome, by = c("sub", "task")) %>%
  full_join(rawstim_expect, by = c("sub", "task")) %>%
  full_join(zstim_expect, by = c("sub", "task"))

# calculate cue vs stim effect ratio ___________________________________________
merged_df$cuestim_raw_outcome <- merged_df$cue_raw_outcome/merged_df$stim_raw_outcome
merged_df$cuestim_raw_outcome_reg <- (merged_df$cue_raw_outcome+1)/(merged_df$stim_raw_outcome+1)

merged_df$cuestim_z_outcome <- merged_df$cue_z_outcome/merged_df$stim_z_outcome
merged_df$cuestim_z_outcome_reg <- (merged_df$cue_z_outcome+1)/(merged_df$stim_z_outcome+1)


write.csv(merged_df, file.path(main_dir, "data", "hlm", "cue_stim_effects_scaling.csv"), row.names = FALSE)
```
```{r}
# Let's check what the cue & stim effects look like ____________________________
head(merged_df)
```


```{r, fig.height=6}
pain.df <-merged_df[merged_df$task == 'pain', ]
cor(pain.df$cue_raw_outcome, pain.df$cue_z_outcome, use = "complete.obs")

# Reshape the dataframe to a long format _______________________________________
pain.long_df <- pivot_longer(pain.df, 
                        cols = c("cue_raw_outcome", "cue_z_outcome", 
                                 "cue_raw_expect", "cue_z_expect", 
                                 "stim_raw_outcome", "stim_z_outcome", 
                                 "stim_raw_expect", "stim_z_expect",
                                 
                                 "cuestim_raw_outcome", "cuestim_raw_outcome_reg",
                                 "cuestim_z_outcome", "cuestim_z_outcome_reg"
                                 ), 
                        names_to = "variable", 
                        values_to = "value")

pain_heatmap <- pain.long_df[, c("sub", "variable", "value")]
# Create the heatmap ___________________________________________________________
ggplotly(ggplot(pain_heatmap, aes(x = variable, y = sub, fill = value)) +
  geom_tile() +
  scale_fill_gradient(low = "blue", high = "red") +
  #facet_grid(rows = vars(sub)) +
  theme_minimal() +
  coord_fixed(ratio = .1) +
  labs(x = "Variable", y = "Subject", fill = "Value") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(angle = 45, vjust = 1)))

# correlation matrix ___________________________________________________________
pain.df.subset <- pain.df[, c("cue_raw_outcome", "cue_z_outcome", 
                                 "cue_raw_expect", "cue_z_expect", 
                                 "stim_raw_outcome", "stim_z_outcome", 
                                 "stim_raw_expect", "stim_z_expect",
                                 
                                 "cuestim_raw_outcome", "cuestim_raw_outcome_reg",
                                 "cuestim_z_outcome", "cuestim_z_outcome_reg")]
                                 #"cuestim_raw_expect", "cuestim_raw_expect_reg",
                                 #"cuestim_z_expect", "cuestim_z_expect_reg")]

M <- cor(as.matrix(pain.df.subset), use ="complete.obs")
#round(M, 2)
testRes = cor.mtest(M, conf.level = 0.95)
corrplot(M, p.mat = testRes$p, method = 'color', diag = TRUE, 
         sig.level = c( 0.05), pch.cex = 0.7,
         tl.cex = 0.6,
         insig = 'label_sig', pch.col = 'grey20')#, order = 'AOE')
```
## Illustration of the plot labels
The variable names indicate `{effect}_{raw/z}_{ratings}`

* `effect` illustrates which contrasts we compute, cue effects or stim effects
    - `cue`: high cue vs. low cue average values per participant
    - `stim`: high stim vs. low stim average values per participant
* `raw/z`: 
    - `raw`: use the raw behavioral ratings (per participant) to compute the aforementioned effects, or 
    - `z`: use the z scores (per participant) to compute the aforementioned effects
* `ratings`
    - `outcome`: outcome ratings
    - `expect`: expectation ratings
    
* example: `cue_raw_outcome` illustrate the cue effect, calculated based on raw outcome ratings. It is the average outcome rating difference between high vs. low cues, calculated per participant.
    
 
## Summary:
* Given that these cue-effect scores are between subject measures, the Z scored version and the raw scored version will have the same variance structure across participants. 
* Taking a look at the correlation matrix,
* 1) we know what raw and z scores of the same effects will have a significant correlation.
* Validation: 
    * 2) expectation ratings as a function of cue ("cue_raw_expect") are highly correlated with outcome ratings as a function of cue ("cue_raw_outcome"). 
    * 3) Stimulus effects have no correlation with the cue effects (i.e. there is no significant corerlation of "stim_raw_outcome" & "cue_raw_outcome" ). 
* 4) Question: cue effect proportional to the stim effect ("cuestim_raw_outcome") is correlated with the stim effect, but not the cue effect. why?

```{r}
rand_norms_100 <- rnorm(n = 100, mean = 100, sd = 25)
rand_norms_100.Z <- (rand_norms_100-mean(rand_norms_100))/sd(rand_norms_100)
cor(rand_norms_100, rand_norms_100.Z)
rand_norms_100.demean <- (rand_norms_100-mean(rand_norms_100))
cor(rand_norms_100, rand_norms_100.demean)
```

