# [beh] N-1 outcome rating ~ N expectation rating {#ch11_n-1outcome}

```
date: '2022-09-13'
updated: '2023-01-18'
```


### DONE {.unlisted .unnumbered}
* plot individual ratings (check distribution)
* afterwards, normalize the ratings and bin them

### Overview  {.unlisted .unnumbered}
* My hypothesis is that the cue-expectancy follows a Bayesian mechanism, akin to what's listed in Jayazeri (2019)
* Here, I plot the expectation ratings (N) and outcome ratings (N-1) and see if the pattern is akin to a sigmoidal curve. 
* If so, I plan to dive deeper and potentially take a Bayesian approach. Jayazeri (2018)


```{r load_libraries_11, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
# library(lmSupport)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(bbmle)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(stats)
library(ggpubr)
library(equatiomatic)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lme4)
library(effectsize)
library(brms)
library(devtools)
library(gghalves)
library(visibly) # 
library(plotly) #plot
library(scico) # plot

source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
# source("https://gist.github.com/benmarwick/2a1bb0133ff568cbe28d/geom_flat_violin.R")

library(r2mlm)
main_dir = dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, "scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```



```{r load_data_and_exclude_11, include=FALSE}
#load data and combine participant data
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "pain"

ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"

# load data _____________________________________
data <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
# data['event03_RT'], data.event03_RT - pandas
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model08_iv-cue-trial_dv-expect-actual", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```


## expectation_rating ~ N-1_outcome_rating 
### Additional analyse 01/18/2023: Q. Do previous outcome ratings predict current expectation ratings? {.unlisted .unnumbered}

* see if current expectation ratings predict outcome ratings
* see if prior stimulus experience (N-1) predicts current expectation ratings
* see if current expectation ratings are explained as a function of prior outcome rating and current expectation rating

when loading the dataset, I need to add in trial index per dataframe.
Then, for the shift the rating? 
```{r include=FALSE}
data_p2= data %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_a3 <- data_p2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

data_a3lag <- 
    data_a3 %>%
    group_by(src_subject_id, session_id, param_run_num) %>%
    mutate(lag.04outcomeangle = dplyr::lag(event04_actual_angle, n = 1, default = NA))
data_a3lag_omit <- data_a3lag[complete.cases(data_a3lag$lag.04outcomeangle),]
```


```{r include=FALSE}
    trialorder_subjectwise_lagoutcome <- meanSummary(
        data_a3lag_omit,
        c("src_subject_id", "session_id", "param_run_num"), "lag.04outcomeangle" )
```

```{r echo=TRUE}
model.lagoutcome = lmer(event02_expect_angle ~ lag.04outcomeangle + (1 | src_subject_id) + (1|session_id) , data = data_a3lag_omit,REML = FALSE)
# summary(model.lagoutcome)
sjPlot::tab_model(model.lagoutcome)
```


### Not sure whether this is accurate {.unlisted .unnumbered}
```{r}
startvec <- c(Asym =10, xmid = 0, scal = 350)
nm1 <- nlmer(event02_expect_angle ~ SSlogis(lag.04outcomeangle,Asym, xmid, scal) ~ Asym|src_subject_id, 
             data_a3lag_omit, start = startvec)
```
```{r}
nform <- ~Asym/(1+exp((xmid-input)/scal))
## b. Use deriv() to construct function:
nfun <- deriv(nform,namevec=c("Asym","xmid","scal"),
              function.arg=c("input","Asym","xmid","scal"))
nm1b <- update(nm1,event02_expect_angle ~ nfun(lag.04outcomeangle, Asym, xmid, scal)  ~ Asym | src_subject_id)
sjPlot::tab_model(nm1b)
```

```{r echo=TRUE}

bbmle::AICtab(model.lagoutcome, nm1b)
```



```{r include=FALSE}
meanSummary_2dv <- function(DATA, GROUP, DV1, DV2) {
    z <- ddply(DATA, GROUP, .fun = function(xx) {
        c(
            DV1_mean_per_sub = mean(xx[, DV1], na.rm = TRUE),
            DV1_sd = sd(xx[, DV1], na.rm = TRUE),
            DV2_mean_per_sub = mean(xx[, DV2], na.rm = TRUE),
            DV2_sd = sd(xx[, DV1], na.rm = TRUE)
        )
    })
    return(z)
}
```

```{r include=FALSE}
subjectwise_2dv = meanSummary_2dv(data_a3lag_omit,
        c("src_subject_id", "trial_index"), 
        "lag.04outcomeangle", "event02_expect_angle")

subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
sp <- ggplot(data=subjectwise_naomit_2dv, 
             aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", linewidth=0.5) +
  theme(aspect.ratio=1) +
  theme_classic() +
  xlab("n-1 outcome rating") +
  ylab("n expectation rating")
sp
# plot(subjectwise_naomit_2dv$DV1_mean_per_sub, subjectwise_naomit_2dv$DV2_mean_per_sub) + lines(x = c(0,200), y = c(0,200))
```


```{r include=FALSE}
    # trialorder_groupwise <- summarySEwithin(
    #     data = subjectwise_naomit_2dv,
    #     measurevar = "DV1_mean_per_sub",
    #     # betweenvars = "src_subject_id",
    #     withinvars = factor( "trial_index"),
    #      idvar = "src_subject_id"
    # )
```


```{r include=FALSE}
    trialorder_groupwise <- summarySEwithin(
        data = subset(subjectwise_naomit_2dv, select = -c(src_subject_id)),
        measurevar = "DV1_mean_per_sub",
        # betweenvars = "src_subject_id",
        withinvars = as.factor( "trial_index")
         #idvar = "trial_index"
    )
```

```{r echo=FALSE}
data_a3lag_omit$src_subject_id <- as.factor(data_a3lag_omit$src_subject_id)

lag.raw <- ggplot(aes(x=lag.04outcomeangle, y=event02_expect_angle), data=data_a3lag_omit) +
  geom_smooth(method='lm', se=F, size=0.75) +
  geom_point(size=0.1) + 
    geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", size=0.5) +
  facet_wrap(~src_subject_id) + 
  theme(legend.position='none') + 
  xlim(0,180) + ylim(0,180) +
  xlab("raw data from each participant: n-1 lagged outcome angle") + 
  ylab("n current expectation rating")
lag.raw +
  labs(title = paste(taskname, "- Is there a linear relationship between current expectation ratings and the previous outcome ratings?"),
       subtitle = "Plotting the raw data - with all of the datapoints ignoring run differences", 
       caption = "Blue = fitted linear slope per participant; Green: 1:1 slope")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
subjectwise_naomit_2dv$src_subject_id <- as.factor(subjectwise_naomit_2dv$src_subject_id)

lag.avg <- ggplot(aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub), data=subjectwise_naomit_2dv) +
  geom_smooth(method='lm', se=F, size=0.75) +
  geom_point(size=0.1) + 
    geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", size=0.5) +
  facet_wrap(~src_subject_id) + 
  theme(legend.position='none') + 
  xlim(0,180) + ylim(0,180) +
  xlab("raw data from each participant: n-1 lagged outcome angle") + 
  ylab("n current expectation rating") 

lag.avg +
  labs(title = paste(taskname, "- Is there a linear relationship between current expectation ratings and the previous outcome ratings?"),
       subtitle = "Observation notes: 1) The relationship is more of an attenuated one, where the higher outcome ratings lead to a slightly lower expectation rating, and a low outcome leads to a higher expectation rating, when considering a 1:1 relationship. This pattern could be explained by regression to the mean type mechanism, where participants are accounting for the fact that their previous experience was extreme on either ends and that this current trial will be under/over estimated. It probably will make sense to also see the relationship between current expectation ratings influencing current outcome ratings. ", 
       caption = "Blue = fitted linear slope per participant; Green: 1:1 slope")

```

```{r}
# https://gist.github.com/even4void/5074855
```

```{r echo=FALSE}
ggplot(data_a3lag_omit, aes(y = event02_expect_angle, 
                       x = lag.04outcomeangle, 
                       shape = subject), size = .3, color = 'gray') + 
  geom_point(size = .1) + 
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .3) +
  theme_classic()
```


## Current expectation_rating ~ N-1_outcomerating * cue

### Additional analysis 01/23/2023 Q. Do these models differ as a function of cue? {.unlisted .unnumbered}

```{r echo=TRUE}
model.lag_cue = lmer(event02_expect_angle ~ lag.04outcomeangle*param_cue_type + (1 | src_subject_id) + (1|session_id) , data = data_a3lag_omit)
sjPlot::tab_model(model.lag_cue)
```

```{r include=FALSE}
meanSummary_2dv <- function(DATA, GROUP, DV1, DV2) {
    z <- ddply(DATA, GROUP, .fun = function(xx) {
        c(
            DV1_mean_per_sub = mean(xx[, DV1], na.rm = TRUE),
            DV1_sd = sd(xx[, DV1], na.rm = TRUE),
            DV2_mean_per_sub = mean(xx[, DV2], na.rm = TRUE),
            DV2_sd = sd(xx[, DV1], na.rm = TRUE)
        )
    })
    return(z)
}
```

```{r include=FALSE}
subjectwise_cuetype = meanSummary_2dv(data_a3lag_omit,
        c("src_subject_id", "trial_index", "param_cue_type"), 
        "lag.04outcomeangle", "event02_expect_angle")

subjectwise_cuetype_2dv <- na.omit(subjectwise_cuetype)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

subjectwise_cuetype$param_cue_type <- as.factor(subjectwise_cuetype$param_cue_type)
sp <- ggplot(data=subjectwise_cuetype, 
             aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub,
             color = param_cue_type)) + 
  geom_point(alpha = .8) +
  geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", size=0.5) +
  scale_color_manual(values = c("#941100", "#BBBBBB"), ) +
  geom_smooth(method = 'lm') +
  theme(aspect.ratio=1) +
  xlab("n-1 outcome rating") +
  ylab("n expectation rating")
sp + theme_classic() +
    labs(title = paste(taskname, "- Does the linear relationship between current expectation ratings and the previous outcome ratings differ as a function of cue?"),
       subtitle = "Plotting the raw data - with all of the datapoints averaged across runs per 12 trials", 
       caption = "high cue vs low cue. The slope is significant, theree is not interaction; Green: 1:1 slope")
# plot(subjectwise_naomit_2dv$DV1_mean_per_sub, subjectwise_naomit_2dv$DV2_mean_per_sub) + lines(x = c(0,200), y = c(0,200))
```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
ggplot(data_a3lag_omit, aes(y = event02_expect_angle, 
                       x = lag.04outcomeangle, 
                       colour = param_cue_type, shape = subject), size = .3, color = 'gray') + 
  geom_point(size = .1) + 
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .3) +
  scale_color_manual(values = c("#941100", "#BBBBBB"), ) +
  theme_classic()
```


## Let's demean the ratings.

* Bin ratings
* Check if the bins do their jobs? by plotting one run
* then check the min, max and see if the quantization is done properly.

> YES, it is

```{r include=FALSE}
# per subject, session, run
#das$wt_2 <- as.numeric(cut_number(das$wt,3))
df_subset = subset(data_a3lag_omit, src_subject_id == 18 )
#df_subset$lag.04outcomeangle
min(df_subset$lag.04outcomeangle)
max(df_subset$lag.04outcomeangle)
range(df_subset$lag.04outcomeangle)
cut_interval(range(df_subset$lag.04outcomeangle), n = 5)
hist(df_subset$lag.04outcomeangle)
# hist(c(121.39691, 102.30392,  89.30972,  92.07837, 121.51694, 148.16579, 122.95297 ,126.36490 ,123.69007 , 51.34019,  36.86990))
df_subset$bin = cut_interval(df_subset$lag.04outcomeangle, n = 5)
df_subset$bin_num = as.numeric(cut_interval(df_subset$lag.04outcomeangle, n = 5))
# cut_interval(df_subset$lag.04outcomeangle, n = 6)
# as.numeric(cut_interval(df_subset$lag.04outcomeangle, n = 6))
# https://stackoverflow.com/questions/21714457/is-cut-style-binning-available-in-dplyr

  # mutate(lagoutcomebin = as.numeric(ggplot2::cut_interval(data_a3lag_omit$lag.04outcomeangle,5)))
  #group_by(src_subject_id, session_id, ) %>%
```

```{r include=FALSE}
df_discrete = data_a3lag_omit %>%
  group_by(src_subject_id) %>%
  mutate(bin = cut_interval(lag.04outcomeangle, n = 5),
         n_1outcomelevels = as.numeric(cut_interval(lag.04outcomeangle, n = 5)))

```

confirm that df discrete has 5 levels per participant
the number of counts per frequency can differ 
```{r include=FALSE}
res <- df_discrete %>% 
  group_by(src_subject_id,n_1outcomelevels) %>% 
  tally()
```

```{r echo=FALSE}
as_tibble(res)
```


```{r echo=FALSE}
pain_df  = df_discrete[df_discrete$param_task_name == "pain",]
ggplot(pain_df, aes(y = event02_expect_angle, 
                       x = n_1outcomelevels, 
                       colour = subject), size = .3, color = 'gray') + 
  geom_point(size = .1) + 
  # geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  geom_smooth(method = "gam") +
  theme_bw()
```


## DEMEAN AND THEN DISCRETIZE


```{r include=FALSE}

df_discrete = data_a3lag_omit %>%
  group_by(src_subject_id) %>%
  mutate(lag.04outcomeangle_demean = lag.04outcomeangle-mean(lag.04outcomeangle),
         event02_expect_angle_demean = event02_expect_angle-mean(event02_expect_angle)) %>%
  mutate(bin = cut_interval(lag.04outcomeangle_demean, n = 5),
         n_1outcomelevels = as.numeric(cut_interval(lag.04outcomeangle_demean, n = 5)))
```

```{r echo=TRUE}
res <- df_discrete %>% 
  group_by(src_subject_id,n_1outcomelevels) %>% 
  tally()
res
```

```{r echo=FALSE}
pain_df  = df_discrete[df_discrete$param_task_name == "pain",]
ggplot(pain_df, aes(y = event02_expect_angle_demean, 
                       x = n_1outcomelevels, 
                       colour = subject), size = .3, color = 'gray') + 
  geom_point(size = .1) + 
  # geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  geom_smooth(method = "gam") +
  theme_classic()
```

```{r include=FALSE}
df_discrete$n_1outcomelevels_newlev = df_discrete$n_1outcomelevels -3
    subjectwise_bin_demean <- meanSummary(df_discrete, c(
        "subject","param_task_name","n_1outcomelevels" 
    ), "event02_expect_angle_demean")
subjectwise_bin_demean_naomit <- na.omit(subjectwise_bin_demean)
    groupwise_bin_demean <- summarySEwithin(
        data = subjectwise_bin_demean_naomit,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("n_1outcomelevels"), # iv
       idvar = "subject"
    )
subjectwise_bin_demean_naomit$n_1outcomelevels_newlev = as.numeric(subjectwise_bin_demean_naomit$n_1outcomelevels) -3
groupwise_bin_demean$n_1outcomelevels_newlev = as.numeric(groupwise_bin_demean$n_1outcomelevels) -3
```


```{r include=FALSE}
plot_halfrainclouds_sig <- function(subjectwise, groupwise, iv,sub_iv,
                                      subjectwise_mean, group_mean, se, subject,
                                      ggtitle, title, xlab, ylab, taskname, ylim,
                                      w, h, dv_keyword, color, save_fname) {
  g <- ggplot(
    data = subjectwise,
    aes(
      y = .data[[subjectwise_mean]],
      x = factor(.data[[iv]]),
      fill = factor(.data[[iv]])
    )
  ) +
    coord_cartesian(ylim = ylim, expand = TRUE) +

    geom_half_violin(
      aes(fill = factor(.data[[iv]])),
      side = 'r',
      #position = 'dodge',
      adjust = 0.5,
      trim = FALSE,
      alpha = .5,
      colour = NA
    ) +


    # geom_point(
    #   aes(
    #     x = as.numeric(.data[[iv]]) - .15,
    #     y = .data[[subjectwise_mean]],
    #     color = factor(.data[[iv]])
    #   ),
    #   position = position_jitter(width = .05),
    #   size = 1, alpha = 0.8, shape = 20
    # ) +

  # geom_line(data = subjectwise,
  #   aes(
  #     group = .data[[subject]],
  #     x = as.numeric(as.factor(.data[[iv]])) - .1 ,
  #     y = .data[[subjectwise_mean]],
  #     fill = factor(.data[[iv]])
  #     ),
  #   linetype = "solid",
  #   color = "grey",
  #   alpha = .3) +

  geom_point(
    aes(
      # group = .data[[subject]],
      x = as.numeric(as.factor(.data[[iv]])) - .1 ,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.7,
  ) + 
    # geom_boxplot(
    #   aes(
    #     x = .data[[iv]],
    #     y = .data[[subjectwise_mean]],
    #     fill = .data[[iv]]
    #   ),
    #   outlier.shape = NA, alpha = 0.8, width = .1, colour = "black"
    # ) +

    # geom_half_boxplot(
    #   data = subjectwise,
    #   aes(x = .data[[iv]],
    #       y = .data[[subjectwise_mean]],
    #       fill = .data[[iv]]),
    #   side = "r",
    #   outlier.shape = NA,
    #   alpha = 0.8,
    #   width = .05,
    #   notch = FALSE,
    #   notchwidth = 0,
    #   varwidth = FALSE,
    #   colour = "black",
    #   errorbar.draw = FALSE
    # ) +

    geom_errorbar(
      data = groupwise,
      aes(
        x = as.numeric(.data[[sub_iv]]) + .1 ,
        y = as.numeric(.data[[group_mean]]),
        color = factor(.data[[iv]]),
        ymin = .data[[group_mean]] - .data[[se]],
        ymax = .data[[group_mean]] + .data[[se]]
      ),
      position = position_dodge(width=0.1), width=0.1 ,   # position = 'dodge',
      alpha = 1
    ) +
geom_line(
  data = groupwise,
  aes(
    #group = .data[[subject]],
    group = 1,
    y = as.numeric(.data[[group_mean]]),
    x = as.numeric(.data[[sub_iv]]) + .1 ,
    # fill = factor(.data[[iv]])
  ),
  linetype = "solid", color = "#C97482", alpha = 1
) +

    # legend stuff ________________________________________________________ # nolint
    #expand_limits(x = 2.8) +
    #guides(fill = "none") +
    guides(color = "none") +
    guides(fill = guide_legend(title = title)) +
    scale_fill_manual(values = color) +
    scale_color_manual(values = color) +
    ggtitle(ggtitle) +
    xlab(xlab) +
    ylab(ylab) +
    theme_classic()
  ggsave(save_fname, width = w, height = h)
  return(g)
}

```

```{r echo=FALSE}
df_discrete$n_1outcomelevels_newlev = as.factor(df_discrete$n_1outcomelevels_newlev)
g <-
  plot_halfrainclouds_sig(
    subjectwise_bin_demean_naomit,
    groupwise_bin_demean,
    iv = "n_1outcomelevels_newlev",
    sub_iv = "n_1outcomelevels",
    subjectwise_mean = "mean_per_sub",
    group_mean = "mean_per_sub_norm_mean",
    se = "se",
    subject = "subject",
    ggtitle = "Do we see a sigmoidal pattern in the pain task?\nPrevious outcome ratings predict expectation ratings",
    title = "levels of (N-1) outcome ratings",
    xlab = "outcome ratings (N-1)",
    ylab = "expectation ratings (N)",
    taskname = "pain",
    ylim = c(-40, 40),
    w = 3,
    h = 5,
    dv_keyword = "sigmoidal",
    color = c(
      '#ad2831',
      "#800e13",
      "#640d14",
      "#38040e",
      "#250902",
      "#250902"
    ),
    save_fname = "~/Download/TEST.png"
  )
g
```
https://groups.google.com/g/ggplot2/c/csPNfSLKkco



