# outcome ~ expect Jayazeri (2018) {#ch13_outcome-expect}

```
date: '2022-09-13'
updated: '2023-02-07'
```


### TODO  {.unlisted .unnumbered}
* plot individual ratings (check distribution)
* afterwards, normalize the ratings and bin them
* 0207 future explore sigmoid fitting https://stackoverflow.com/questions/63568848/fitting-a-sigmoidal-curve-to-points-with-ggplot

## Overview 
* My hypothesis is that the cue-expectancy follows a Bayesian mechanism, akin to what's listed in Jayazeri (2019)
* Here, I plot the expectation ratings (N) and outcome ratings (N) and see if the pattern is akin to a sigmoidal curve. 
* If so, I plan to dive deeper and potentially take a Bayesian approach. 
* Instead of (N-1), we'll be using the cue and the expectation ratings to explain the outcome ratings


```{r load_libraries_13, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
# library(lmSupport)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(stats)
library(ggpubr)
library(equatiomatic)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lme4)
library(effectsize)
library(brms)
library(devtools)
library(gghalves)
library(visibly) # 
library(ggtext)
library(plotly) #plot
library(scico) # plot
source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
# source("https://gist.github.com/benmarwick/2a1bb0133ff568cbe28d/geom_flat_violin.R")

library(r2mlm)
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

```{r function::plot_errorbar_13, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
plot_errorbar <- function(subjectwise, groupwise, iv,sub_iv, group_by,
                                      subjectwise_mean, group_mean, se, subject,
                                      ggtitle, title, xlab, ylab, taskname, ylim,
                                      w, h, dv_keyword, color, level_num, save_fname) {
  g <- ggplot(
    data = subjectwise,
    aes(
      y = .data[[subjectwise_mean]],
      x = factor(.data[[iv]]),
      fill = factor(.data[[group_by]])
    )
  ) +
    coord_cartesian(ylim = ylim, expand = TRUE) +

  geom_point(
    aes(
      # group = .data[[subject]],
      x = as.numeric(factor(.data[[iv]])) - (level_num/2)-0.1,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[group_by]])
    ),
    position = position_jitter(width = .1),
    size = 1,
    alpha = 0.3,
  ) + 

    geom_errorbar(
      data = groupwise,
      aes(
        #x = as.numeric(.data[[sub_iv]]) + .1 ,
        x = as.numeric(.data[[iv]]) + .1 ,
        y = as.numeric(.data[[group_mean]]),
        group = .data[[group_by]],
        color = factor(.data[[group_by]]),
        ymin = .data[[group_mean]] - .data[[se]],
        ymax = .data[[group_mean]] + .data[[se]]
      ),
      position = position_dodge(width=0.3), width=0.3 ,   # position = 'dodge',
      alpha = 1, lwd=.7
    ) +
geom_line(
  data = groupwise,
  aes(
    group = .data[[group_by]],
    y = as.numeric(.data[[group_mean]]),
    # x = as.numeric(.data[[sub_iv]]) + .1 ,
    x = as.numeric(.data[[iv]]) + .1 ,
    color = factor(.data[[group_by]]),
  ),
  position = position_dodge(width=0.2),
  linetype = "solid",  alpha = 1, 
  # color = "#C97482",
) +

    # legend stuff ________________________________________________________ # nolint
    #expand_limits(x = 2.8) +
    #guides(fill = "none") +
    #guides(color = "none") +
    #scale_x_discrete(sort(unique(subjectwise_mean[,iv]))) +
    guides(fill = guide_legend(title = title)) +
    scale_fill_manual(values = color) +
    scale_color_manual(values = color) +
    ggtitle(ggtitle) +
    xlab(xlab) +
    ylab(ylab) +
    theme_bw() +
      theme(axis.line = element_line(colour = "grey50"), 
      panel.background = element_blank(),
      plot.subtitle = ggtext::element_textbox_simple(size= 11))
  ggsave(save_fname, width = w, height = h)
  return(g)
}
```

```{r include=FALSE}
plot_halfrainclouds_sig <- function(subjectwise, groupwise, iv,sub_iv,
                                      subjectwise_mean, group_mean, se, subject,
                                      ggtitle, title, xlab, ylab, taskname, ylim,
                                      w, h, dv_keyword, color, save_fname) {
  g <- ggplot(
    data = subjectwise,
    aes(
      y = .data[[subjectwise_mean]],
      x = factor(.data[[iv]]),
      fill = factor(.data[[iv]])
    )
  ) +
    coord_cartesian(ylim = ylim, expand = TRUE) +

    geom_half_violin(
      aes(fill = factor(.data[[iv]])),
      side = 'r',
      #position = 'dodge',
      adjust = 0.5,
      trim = FALSE,
      alpha = .5,
      colour = NA
    ) +


    # geom_point(
    #   aes(
    #     x = as.numeric(.data[[iv]]) - .15,
    #     y = .data[[subjectwise_mean]],
    #     color = factor(.data[[iv]])
    #   ),
    #   position = position_jitter(width = .05),
    #   size = 1, alpha = 0.8, shape = 20
    # ) +

  # geom_line(data = subjectwise,
  #   aes(
  #     group = .data[[subject]],
  #     x = as.numeric(factor(.data[[iv]])) - .1 ,
  #     y = .data[[subjectwise_mean]],
  #     fill = factor(.data[[iv]])
  #     ),
  #   linetype = "solid",
  #   color = "grey",
  #   alpha = .3) +

  geom_point(
    aes(
      # group = .data[[subject]],
      x = as.numeric(factor(.data[[iv]])) - .1 ,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.7,
  ) + 
    # geom_boxplot(
    #   aes(
    #     x = .data[[iv]],
    #     y = .data[[subjectwise_mean]],
    #     fill = .data[[iv]]
    #   ),
    #   outlier.shape = NA, alpha = 0.8, width = .1, colour = "black"
    # ) +

    # geom_half_boxplot(
    #   data = subjectwise,
    #   aes(x = .data[[iv]],
    #       y = .data[[subjectwise_mean]],
    #       fill = .data[[iv]]),
    #   side = "r",
    #   outlier.shape = NA,
    #   alpha = 0.8,
    #   width = .05,
    #   notch = FALSE,
    #   notchwidth = 0,
    #   varwidth = FALSE,
    #   colour = "black",
    #   errorbar.draw = FALSE
    # ) +

    geom_errorbar(
      data = groupwise,
      aes(
        x = as.numeric(.data[[sub_iv]]) + .1 ,
        y = as.numeric(.data[[group_mean]]),
        color = factor(.data[[iv]]),
        ymin = .data[[group_mean]] - .data[[se]],
        ymax = .data[[group_mean]] + .data[[se]]
      ),
      position = position_dodge(width=0.1), width=0.1 ,   # position = 'dodge',
      alpha = 1
    ) +
geom_line(
  data = groupwise,
  aes(
    #group = .data[[subject]],
    group = 1,
    y = as.numeric(.data[[group_mean]]),
    x = as.numeric(.data[[sub_iv]]) + .1 ,
    # fill = factor(.data[[iv]])
  ),
  linetype = "solid", color = "#C97482", alpha = 1
) +

    # legend stuff ________________________________________________________ # nolint
    #expand_limits(x = 2.8) +
    #guides(fill = "none") +
    guides(color = "none") +
    guides(fill = guide_legend(title = title)) +
    scale_fill_manual(values = color) +
    scale_color_manual(values = color) +
    ggtitle(ggtitle) +
    xlab(xlab) +
    ylab(ylab) +
    theme_bw()
  ggsave(save_fname, width = w, height = h)
  return(g)
}

```

```{r include=FALSE}
plot_halfrainclouds_try <- function(subjectwise, groupwise, iv,sub_iv, group_by,
                                      subjectwise_mean, group_mean, se, subject,
                                      ggtitle, title, xlab, ylab, taskname, ylim,
                                      w, h, dv_keyword, color, save_fname) {
  g <- ggplot(
    data = subjectwise,
    aes(
      y = .data[[subjectwise_mean]],
      x = factor(.data[[iv]]),
      fill = factor(.data[[group_by]])
    )
  ) +
    coord_cartesian(ylim = ylim, expand = TRUE) +

    geom_half_violin(
      aes(fill = factor(.data[[group_by]])),
      side = 'r',
      position = position_nudge(x = .1, y = 0),
      # position = 'dodge',
      adjust = 1.5,
      trim = FALSE,
      alpha = .5,
      colour = NA
    ) +


    # geom_point(
    #   aes(
    #     x = as.numeric(.data[[iv]]) - .15,
    #     y = .data[[subjectwise_mean]],
    #     color = factor(.data[[iv]])
    #   ),
    #   position = position_jitter(width = .05),
    #   size = 1, alpha = 0.8, shape = 20
    # ) +

  # geom_line(data = subjectwise,
  #   aes(
  #     group = .data[[subject]],
  #     x = as.numeric(factor(.data[[iv]])) - .1 ,
  #     y = .data[[subjectwise_mean]],
  #     fill = factor(.data[[iv]])
  #     ),
  #   linetype = "solid",
  #   color = "grey",
  #   alpha = .3) +

  geom_point(
    aes(
      # group = .data[[subject]],
      x = as.numeric(factor(.data[[iv]])) - .1 ,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[group_by]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.7,
  ) + 
    # geom_boxplot(
    #   aes(
    #     x = .data[[iv]],
    #     y = .data[[subjectwise_mean]],
    #     fill = .data[[iv]]
    #   ),
    #   outlier.shape = NA, alpha = 0.8, width = .1, colour = "black"
    # ) +

    # geom_half_boxplot(
    #   data = subjectwise,
    #   aes(x = .data[[iv]],
    #       y = .data[[subjectwise_mean]],
    #       fill = .data[[iv]]),
    #   side = "r",
    #   outlier.shape = NA,
    #   alpha = 0.8,
    #   width = .05,
    #   notch = FALSE,
    #   notchwidth = 0,
    #   varwidth = FALSE,
    #   colour = "black",
    #   errorbar.draw = FALSE
    # ) +

    geom_errorbar(
      data = groupwise,
      aes(
        x = as.numeric(.data[[sub_iv]]) + .1 ,
        y = as.numeric(.data[[group_mean]]),
        group = .data[[group_by]],
        color = factor(.data[[group_by]]),
        ymin = .data[[group_mean]] - .data[[se]],
        ymax = .data[[group_mean]] + .data[[se]]
      ),
      position = position_dodge(width=0.1), width=0.1 ,   # position = 'dodge',
      alpha = 1
    ) +
geom_line(
  data = groupwise,
  aes(
    #group = .data[[subject]],
    group = 1,
    y = as.numeric(.data[[group_mean]]),
    x = as.numeric(.data[[sub_iv]]) + .1 ,
    # fill = factor(.data[[iv]])
  ),
  linetype = "solid", color = "#C97482", alpha = 1
) +

    # legend stuff ________________________________________________________ # nolint
    #expand_limits(x = 2.8) +
    #guides(fill = "none") +
    guides(color = "none") +
    guides(fill = guide_legend(title = title)) +
    scale_fill_manual(values = color) +
    scale_color_manual(values = color) +
    ggtitle(ggtitle) +
    xlab(xlab) +
    ylab(ylab) +
    theme_bw()
  ggsave(save_fname, width = w, height = h)
  return(g)
}

```

load data and combine participant data
```{r load_data_and_exclude_13}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event04_actual_angle"
dv_keyword <- "outcome_rating"
xlab <- ""
ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"

analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model13_iv-cue-expect_dv-outcome", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```


## Do expectation ratings predict current outcome ratings? Does this differ as a function of cue?
* see if current expectation ratings predict outcome ratings
* ~~see if prior stimulus experience (N-1) predicts current expectation ratings~~
* ~~see if current expectation ratings are explained as a function of prior outcome rating and current expectation rating~~


```{r eval=FALSE, include=FALSE}
# TRIAL ORDER WITHIN PARTICIPANT
  #arrange(src_subject_id ) %>%
# df= data %>%
#   group_by(src_subject_id) %>%
#   mutate(trial_index = row_number())

# TRIAL ORDER WITHIN RUN
# data_a3 <- data_p2 %>% 
#   group_by(src_subject_id, session_id, param_run_num) %>% 
#   mutate(trial_index = row_number(param_run_num))

```

## task-pain, HLM modeling
``lmer(outcome ~ cue * expectation + (1|participant))``
```{r echo=FALSE}
taskname = "pain"
df <- load_task_social_df(datadir,taskname = taskname,subject_varkey = subject_varkey,iv = iv,exclude = exclude  )
df_dropna <- df[!is.na(df$event02_expect_angle) & !is.na(df$event04_actual_angle),]
model.expectoutcome = lmer(event04_actual_angle ~ param_cue_type*event02_expect_angle + (1 | src_subject_id)  , data = df_dropna)
summary(model.expectoutcome)
```
## Fig. Expectation ratings predict outcome ratings 
**Purpose of this section: **
* Before binning the data, I want to check if expectation ratings explain outcome ratings.

**Observation: **
* 1. expectation ratings after a high cue reflect an overestimation, that is compensated for a lower outcome rating. 
* 2. expectation ratings after a low cue reflects an overestimating, which is compensated with a higher outcome rating
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# summarize dataframe __________________________________________________________
iv1 = "event02_expect_angle"; iv2 = "event04_actual_angle"
df_dropna <- df[!is.na(df[, iv1]) & !is.na(df[, iv2]), ]
subjectwise_2dv = meanSummary_2dv(df_dropna,
        c("src_subject_id", "param_cue_type"), 
          "event02_expect_angle", "event04_actual_angle")
subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
subjectwise_naomit_2dv$param_cue_type <- as.factor(subjectwise_naomit_2dv$param_cue_type)
# plot _________________________________________________________________________
sp <- ggplot(data=subjectwise_naomit_2dv, 
             aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub,
             color = param_cue_type)) + 
  geom_point(aes(shape = param_cue_type, color = param_cue_type), size = 2, alpha = .8) + 
  geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", linewidth=0.5) +
  theme(aspect.ratio=1) +
  scale_color_manual(values = c("high_cue" = "#000000", 
                                "low_cue" = "#BBBBBB")) +
  scale_shape_manual(values = c(16, 17)) +
  xlab("expect rating") +
  ylab("outcome rating") + ylim(0,180) + xlim(0,180) +
  theme(axis.line = element_line(colour = "grey50"), 
      panel.background = element_blank(),
      plot.subtitle = ggtext::element_textbox_simple(size= 11))

# Add description ______________________________________________________________
sp +  labs(title =paste0("task-",taskname, "- What is the pattern for outcome and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )

# ,
#         subtitle = "1) expectation ratings after a high cue reflect an overestimation, that is compensated for a lower outcome rating. 2) expectation ratings after a low cue reflects an overestimating, which is compensated with a higher outcome rating ")

```

## TODO: PLOT participant rating  {.unlisted .unnumbered}
* purpose: to see the raw data distribution. Are there any alarming participants to remove?
x axis participant
y axis histogram of actual ratings

## Check bin process {.unlisted .unnumbered}

### Let's demean the ratings for one participant  {.unlisted .unnumbered}
1. bin ratings
Do the bins do their jobs?
plot one run
then check the min, max and see if the quantization is done properly.
YES, it is
```{r eval=FALSE, include=FALSE}
# per subject, session, run
df_subset = subset(df_dropna, src_subject_id == 117 )
min(df_subset$event04_actual_angle)
max(df_subset$event04_actual_angle)
range(df_subset$event04_actual_angle)
cut_interval(range(df_subset$event04_actual_angle), n = 10)
hist(df_subset$event04_actual_angle)
df_subset$bin = cut_interval(df_subset$event04_actual_angle, n = 10)
df_subset$bin_num = as.numeric(cut_interval(df_subset$event04_actual_angle, n = 10))
```
* confirm that df discrete has 10 levels per participant
* the number of counts per frequency can differ 
```{r}
k <-df_dropna %>% group_by(src_subject_id) %>% filter(n()>= 5) %>% ungroup()

df_discrete = k %>%
  group_by(src_subject_id) %>%
  mutate(bin = cut_interval(event04_actual_angle, n = 10),
         outcomelevels = as.numeric(cut_interval(event04_actual_angle, n = 10)))

res <- df_discrete %>% 
  group_by(src_subject_id,outcomelevels) %>% 
  tally()

dset1 <- head(res)
knitr::kable(dset1, format = "html")
```


### subjectwise plot {.unlisted .unnumbered}
What is the pattern of expectation rating and outcome rating, per participant? 
Do we see a linear effect? We should also plot the data as a sigmoidal fit
```{r echo=FALSE}
df <- load_task_social_df(datadir,taskname = taskname,subject_varkey = subject_varkey,iv = iv,exclude = exclude  )
iv1 = "event02_expect_angle"; iv2 = "event04_actual_angle"; levels = 10
df_dropna <- df[!is.na(df[, iv1]) & !is.na(df[, iv2]), ]
k <-df_dropna %>% group_by(src_subject_id) %>% filter(n()>= 5) %>% ungroup()
#pain_df  = df_discrete[df_discrete$param_task_name == "pain",]
df_discrete <- k %>%
  dplyr::group_by(.data[["src_subject_id"]]) %>%
  select(everything())  %>%
  mutate(outcome_demean = .data[[iv2]] - mean(.data[[iv2]]),
         iv1_demean = .data[[iv1]] - mean(.data[[iv1]])) %>%
  mutate(
    bin = ggplot2::cut_interval(.data[["iv1_demean"]], n = levels),
    expectlevels = as.numeric(cut_interval(.data[["iv1_demean"]], n = levels))
  )

swp <- ggplot(
  df_discrete,
  aes(y = outcome_demean,
      x = expectlevels,
      colour = subject),
  size = .01,
  color = 'gray'
) +
  geom_point(position = position_jitter(width = .1),size = .1, alpha = .3) +
  # geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  geom_smooth(method = 'rlm', se = F, linewidth = .1, alpha = .5) +
  theme(axis.line = element_line(colour = "grey50"), 
      panel.background = element_blank(),
      plot.subtitle = ggtext::element_textbox_simple(size= 11))

# ADD description
swp +  labs(title =paste0("task-",taskname, "- Subjectwise pattern for outcome and expect ratings? \n\n"),
        subtitle = "participants indeed have a linear relationship betwen ")
```


## binned expectation ratings per task


### Pain: binned expectation ratings
* checked warnings: None

```{r pain_discrete_10bin_cue_13, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
taskname = "pain"
df <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
plot_binned_rating(df, taskname, iv1 = "event02_expect_angle", iv2 = "event04_actual_angle", xlab = "expectation ratings",
                               ylab = "outcome ratings", levels = 10) 
```


#### Pain: low and high cues separately

```{r pain_discrete_10bin_lowcue_13, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
taskname = "pain"
df <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
subsetdf <- df[df$param_cue_type == 'low_cue',]
pain_low <- plot_binned_rating(subsetdf, taskname, iv1 = "event02_expect_angle", iv2 = "event04_actual_angle", xlab = "expectation ratings",
                               ylab = "outcome ratings", levels = 10) 
```

```{r pain_discrete_10bin_highcue_13, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
taskname = "pain"
df <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
subsetdf <- df[df$param_cue_type == 'high_cue',]
pain_high <- plot_binned_rating(subsetdf, taskname, iv1 = "event02_expect_angle", iv2 = "event04_actual_angle", xlab = "expectation ratings",
                               ylab = "outcome ratings", levels = 10) 
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
plots <- ggpubr::ggarrange(pain_low, pain_high, ncol = 2, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob("", color = "black", face = "bold", size = 15))
plots_title
```

### Vicarious: binned expectation ratings
* checked warnings: None
```{r vicarious_discrete_10bin_cue_13, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
taskname = "vicarious"
df <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
plot_binned_rating(df, taskname, iv1 = "event02_expect_angle", iv2 = "event04_actual_angle", xlab = "expectation ratings",
                               ylab = "outcome ratings", levels = 10) 
```

### Cognitive: binned expectation ratings
```{r cognitive_discrete_10bin_cue_13, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
taskname = "cognitive"
df <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
plot_binned_rating(df, taskname, iv1 = "event02_expect_angle", iv2 = "event04_actual_angle", xlab = "expectation ratings",
                               ylab = "outcome ratings", levels = 10) 
```

Warnings: due to mere empty trials in high or low cue groups in the expectation ratings
```
Warning in qt(conf.interval/2 + 0.5, datac$N - 1): NaNs produced
```

## not splitting into cue groups
* checked warnings: None
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
taskname = "pain"; levels = 10
df <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
df_dropna <- df[!is.na(df$event02_expect_angle) & !is.na(df$event04_actual_angle),]
k <-df_dropna %>% group_by(src_subject_id) %>% filter(n()>= 5) %>% ungroup()
df_discrete = k %>%
  group_by(src_subject_id) %>%
  mutate(event04_actual_angle_demean = event04_actual_angle-mean(event04_actual_angle),
         event02_expect_angle_demean = event02_expect_angle-mean(event02_expect_angle)) %>%
  mutate(bin = cut_interval(event02_expect_angle_demean, n = 10),
         expectlevels = as.numeric(cut_interval(event02_expect_angle_demean, n = 10)))

df_discrete$expectlevels_newlev = df_discrete$expectlevels -5

# subjectwise_bin_demean <- meanSummary(df_discrete, c(
#         "subject","param_task_name","expectlevels",
#     ), "event04_actual_angle_demean")

subjectwise_bin_demean_cue <- meanSummary(df_discrete, c(
        "subject","param_task_name","expectlevels"
    ), "event04_actual_angle_demean")
subjectwise_bin_demean_naomit <- na.omit(subjectwise_bin_demean_cue)
    groupwise_bin_demean <- summarySEwithin(
        data = subjectwise_bin_demean_naomit,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("expectlevels"), # iv
       idvar = "subject"
    )
    
    
subjectwise_bin_demean_naomit$expectlevels_newlev <- as.numeric(subjectwise_bin_demean_naomit$expectlevels) - (levels/2)
groupwise_bin_demean$expectlevels_newlev <- as.numeric(groupwise_bin_demean$expectlevels) - (levels/2)
g <-
  plot_halfrainclouds_sigmoid(
    subjectwise_bin_demean_naomit,
    groupwise_bin_demean,
    iv = "expectlevels_newlev",
    sub_iv = "expectlevels",
    subjectwise_mean = "mean_per_sub",
    group_mean = "mean_per_sub_norm_mean",
    se = "se",
    subject = "subject",
    ggtitle = "Do we see a sigmoidal pattern in the pain task?\nexpectation predict outcome ratings",
    title = "levels of expectation ratings",
    xlab = "expectation ratings",
    ylab = "outcome ratings",
    taskname = "pain",
    ylim = c(-40, 40),
    w = 3,
    h = 5,
    dv_keyword = "sigmoidal",
    color = c(
      '#641220',
      "#6e1423",
      "#85182a",
      "#a11d33",
      "#a71e34",
      
      "#b21e35",
      "#bd1f36",
      "#c71f37",
      "#da1e37",
      "#e01e37",
      "#e01e37"
    ),
    save_fname = "~/Download/TEST.png"
  )
g
```
https://groups.google.com/g/ggplot2/c/csPNfSLKkco


```{r archive_plot_full_code, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# taskname = "vicarious"
# df <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
# 
# df_dropna <- df[!is.na(df$event02_expect_angle) & !is.na(df$event04_actual_angle),]
# 
# k <-df_dropna %>% group_by(src_subject_id) %>% filter(n()>= 5) %>% ungroup()
# df_discrete = k %>%
#   group_by(src_subject_id) %>%
#   mutate(event04_actual_angle_demean = event04_actual_angle-mean(event04_actual_angle),
#          event02_expect_angle_demean = event02_expect_angle-mean(event02_expect_angle)) %>%
#   mutate(bin = cut_interval(event02_expect_angle_demean, n = 10),
#          expectlevels = as.numeric(cut_interval(event02_expect_angle_demean, n = 10)))
# 
# vic_df  = df_discrete[df_discrete$param_task_name == taskname,]
# vic_df$expectlevels_newlev = vic_df$expectlevels -5
# 
# subjectwise_bin_demean_cue <- meanSummary(vic_df, c(
#         "subject","param_task_name","expectlevels", "param_cue_type" 
#     ), "event04_actual_angle_demean")
# subjectwise_bin_demean_naomit <- na.omit(subjectwise_bin_demean_cue)
#     groupwise_bin_demean <- summarySEwithin(
#         data = subjectwise_bin_demean_naomit,
#         measurevar = "mean_per_sub", # variable created from above
#         withinvars = c("expectlevels", "param_cue_type"), # iv
#        idvar = "subject"
#     )
# subjectwise_bin_demean_naomit$expectlevels_newlev = as.numeric(subjectwise_bin_demean_naomit$expectlevels) -5
# groupwise_bin_demean$expectlevels_newlev = as.numeric(groupwise_bin_demean$expectlevels) -5
# vic_df$expectlevels_newlev = as.factor(vic_df$expectlevels_newlev)
# g <-
#   plot_errorbar(
#     subjectwise_bin_demean_naomit,
#     groupwise_bin_demean,
#     iv = "expectlevels_newlev",
#     sub_iv = "expectlevels",
#     group_by = "param_cue_type",
#     subjectwise_mean = "mean_per_sub",
#     group_mean = "mean_per_sub_norm_mean",
#     se = "se",
#     subject = "subject",
#     ggtitle = paste0("Do we see a sigmoidal pattern in the pain task?\ntask-", taskname, ": expectation predict outcome ratings"),
#     title = "levels of expectation ratings",
#     xlab = "expectation ratings",
#     ylab = "outcome ratings",
#     taskname = "pain",
#     ylim = c(-40, 40),
#     w = 3,
#     h = 5,
#     dv_keyword = "sigmoidal",
#     color = c("#941100","#6E6E6E"),
#     save_fname = "~/Download/TEST.png"
#   )
# g
```

