# [beh] outcome ~ cue * stim * expectrating * n-1outcomerating  {#ch14_factorize}


## What is the purpose of this notebook? {.unlisted .unnumbered}

1. Linear relationship between expectation and outcome ratings, as a function of stimulus intensity and cues
* Here, I model the outcome ratings as a function of cue, stimulus intensity, expectation ratings, N-1 outcome rating. 
* From this, I see that the linear relationship of expectation ratings and outcome ratings are split across a 1:1 slope, depending on high or low cues. In other words, when exposed to a high cue, participants tend to rate higher on expectations but report lower outcome ratings, and viceversa for low cues. 
Based on these results, I ask the following:

2.Are participants who are overestimating for high cues also underestimators for low cues?
* Here, I calculate Orthogonal distance from the 1:1 slope. 
* Based on that, I test whether the absolute ODR distance is equivalent across cues. If a participant equally overestimates for a high cue and underestimates a stimuli for a low cue, their ODR distance should be the same. This is reflected in the subject-level slopes, which are parallel.

### Some thoughts, TODOs {.unlisted .unnumbered}

* Standardized coefficients
* Slope difference? Intercept difference? ( cue and expectantion rating)
* Correct for the range (within participant)
hypothesis:
1. Larger expectation leads to prediction error
2. Individual differences in ratings
3. Outcome experience, based on behavioral experience
What are the brain maps associated with each component.  


```{r load_libraries_5, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
# library(lmSupport)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(stats)
library(ggpubr)
library(equatiomatic)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lme4)
library(effectsize)
library(brms)
library(devtools)
library(gghalves)
library(visibly) # 
library(plotly) #plot
library(scico) # plot
source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
# source("https://gist.github.com/benmarwick/2a1bb0133ff568cbe28d/geom_flat_violin.R")

library(r2mlm)
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

### load data and combine participant data {.unlisted .unnumbered}

```{r load_data_and_exclude_m1}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "pain"

ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"

# load data _____________________________________
data <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
# data['event03_RT'], data.event03_RT - pandas
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model14_iv-cue-stim-N1outcome-expect_dv-outcome", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```

### summarize data {.unlisted .unnumbered}
```{r echo=FALSE}
summary(data[, c("event02_expect_RT", "event04_actual_RT", "event02_expect_angle", "event04_actual_angle")])
```

### Covariance matrix: ratings and RT {.unlisted .unnumbered}
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# data(data, package = 'visibly')

myvars <- names(data) %in% 
  c( "event02_expect_angle", "event02_expect_RT", "event04_actual_angle", "event04_actual_RT", "event01_cue_onset")
newdata <- data[myvars]
# numdata  <- unlist(lapply(data, is.numeric), use.names = FALSE) 
data_naomit <- na.omit(newdata)
cor_matrix = cor(data_naomit)
corr_heat(cor_matrix)
```

### Covariance matrix: fixation durations (e.g. ISIs) {.unlisted .unnumbered}
```{r}
ISIvars <- names(data) %in% 
  c( "ISI01_duration", "ISI02_duration", "ISI03_duration")
ISIdata <- data[ISIvars]
# numdata  <- unlist(lapply(data, is.numeric), use.names = FALSE) 
ISIdata_naomit <- na.omit(ISIdata)
ISIcor_matrix = cor(ISIdata_naomit)
corr_heat(ISIcor_matrix)
```

```{r function::simple_contrasts_beh, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
simple_contrasts_beh <- function(df) {
# [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
df$stim_factor <- factor(df$param_stimulus_type)

# contrast code 1 linear
df$stim_con_linear[df$param_stimulus_type == "low_stim"] <-  -0.5
df$stim_con_linear[df$param_stimulus_type == "med_stim"] <-  0
df$stim_con_linear[df$param_stimulus_type == "high_stim"] <-  0.5

# contrast code 2 quadratic
df$stim_con_quad[df$param_stimulus_type == "low_stim"] <-  -0.33
df$stim_con_quad[df$param_stimulus_type == "med_stim"] <-  0.66
df$stim_con_quad[df$param_stimulus_type == "high_stim"] <-  -0.33

# cue contrast
df$CUE_high_gt_low[df$param_cue_type == "low_cue"] <-  -0.5 # social influence task
df$CUE_high_gt_low[df$param_cue_type == "high_cue"] <-  0.5 # no influence task

df$stim_ordered <- factor(
        df$param_stimulus_type,
        levels = c("low_stim", "med_stim", "high_stim")
    )

df$cue_name[df$param_cue_type == "low_cue"] <- "low"
df$cue_name[df$param_cue_type == "high_cue"] <- "high"

df$cue_ordered <- factor(
        df$cue_name,
        levels = c("low", "high")
    )
return(df)
}
```



```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
maindata <- data %>%
group_by(src_subject_id) %>%
mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
mutate(demean_outcome = event04_actual_angle - avg_outcome) %>%
mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
mutate(demean_expect = event02_expect_angle - avg_expect)
```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
data_p2= data %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_a3 <- data_p2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

data_a3lag <- 
    data_a3 %>%
    group_by(src_subject_id, session_id, param_run_num) %>%
    mutate(lag.04outcomeangle = dplyr::lag(event04_actual_angle, n = 1, default = NA))
data_a3lag_omit <- data_a3lag[complete.cases(data_a3lag$lag.04outcomeangle),]
```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
df <- data_a3lag_omit
pvc <- simple_contrasts_beh(df)
```

## Original motivation: 
Plot pain outcome rating as a function of expectation rating and cue {.unlisted .unnumbered}
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# summarize dataframe __________________________________________________________
iv1 = "event02_expect_angle"; iv2 = "event04_actual_angle"
df_dropna <- pvc[!is.na(pvc[, iv1]) & !is.na(pvc[, iv2]), ]
subjectwise_2dv = meanSummary_2dv(df_dropna,
        c("src_subject_id", "param_cue_type"), 
          "event02_expect_angle", "event04_actual_angle")
subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
subjectwise_naomit_2dv$param_cue_type <- as.factor(subjectwise_naomit_2dv$param_cue_type)
# plot _________________________________________________________________________
sp <- ggplot(data=subjectwise_naomit_2dv, 
             aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub,
             color = param_cue_type)) + 
  geom_point(aes(shape = param_cue_type, color = param_cue_type), size = 2, alpha = .8) + 
  geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", linewidth=0.5) +
  theme(aspect.ratio=1) +
  scale_color_manual(values = c("high_cue" = "#000000", 
                                "low_cue" = "#BBBBBB")) +
  scale_shape_manual(values = c(16, 17)) +
  xlab("expect rating") +
  ylab("outcome rating") + ylim(0,180) + xlim(0,180) +
  theme(axis.line = element_line(colour = "grey50"), 
      panel.background = element_blank(),
      plot.subtitle = ggtext::element_textbox_simple(size= 11))

# Add description ______________________________________________________________
sp +  labs(title =paste0("task-",taskname, "- What is the pattern for outcome and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )

```

## Pain

### linear model {.unlisted .unnumbered}
* **CUE_high_gt_low** : high cue: 0.5, low cue: -0.5
* **stim_con_linear** : high intensity: 0.5, med intensity: 0, low intensity: -0.5
* **stim_con_quad** : high intensity: -0.33, med intensity: 0.66, low intensity: -0.33

```{r echo=FALSE, message=TRUE, warning=TRUE}
model.factorize = lmer(event04_actual_angle ~ CUE_high_gt_low*stim_con_linear*event02_expect_angle + CUE_high_gt_low*stim_con_quad*event02_expect_angle + lag.04outcomeangle + (CUE_high_gt_low|src_subject_id), data = pvc)
#summary(model.factorize)
sjPlot::tab_model(model.factorize, p.val = "kr", show.df = TRUE)
```


### pain plot parameters
```{r}
iv1 = "event02_expect_angle"; iv2 = "event04_actual_angle";
group = "param_cue_type"; subject = "src_subject_id"; 
xlab = "expectation rating"; ylab = "outcome rating"
min = 0; max = 180
```

### Pain run, collapsed across stimulus intensity {.unlisted .unnumbered}
```{r rawoutcome_pain, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv1 = "event02_expect_angle"; iv2 = "event04_actual_angle"
df_dropna <-
  pvc[!is.na(pvc$event02_expect_angle) & !is.na(pvc$event04_actual_angle),]
total <-
  plot_twovariable(
    df_dropna, iv1, iv2, group, subject, xmin=0, xmax=180, ymin=0,ymax=180, xlab, ylab,
    ggtitle = "all stimulus intensity", 
    color_scheme = c("high_cue" ="#941100","low_cue" =  "#BBBBBB"), 
    alpha = .8, fit_lm = FALSE, lm_method = "lm"
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for outcome and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )
  # geom_line(method="lm", alpha=0.3, size=1, span=0.5) # geom_smooth(method=lm, se = TRUE) 
# +geom_smooth(method = "lm", alpha=0.1, size=0, span=0.5)
```
```{r rawoutcome_pain_stimuluswise, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv1 = "event02_expect_angle"; iv2 = "event04_actual_angle"
# low stimulus intensity
df_low = df_dropna[df_dropna$param_stimulus_type == "low_stim", ]
low <-
  plot_twovariable(
    df_low, iv1, iv2, group, subject, xmin=0, xmax=180, ymin=0,ymax=180, xlab, ylab,
    ggtitle = "Low intensity",
    color_scheme = c("high_cue" ="#FF8800","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )

# med stimulus intensity
df_med = df_dropna[df_dropna$param_stimulus_type == "med_stim", ]
med <-
  plot_twovariable(
    df_med, iv1, iv2, group, subject, xmin=0, xmax=180, ymin=0,ymax=180, xlab, ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("high_cue" ="#DB6000","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )

# high stimulus intensity
df_high = df_dropna[df_dropna$param_stimulus_type == "high_stim", ]
high <-
  plot_twovariable(
    df_high, iv1, iv2, group, subject, xmin=0, xmax=180, ymin=0,ymax=180, xlab, ylab,
    ggtitle = "High intensity",
    color_scheme = c("high_cue" ="#941100","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n Expect/Outcome linear relationship differs as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```

### loess
```{r rawoutcome_pain_stimuluswise_loess, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv1 = "event02_expect_angle"; iv2 = "event04_actual_angle"
# low stimulus intensity
df_low = df_dropna[df_dropna$param_stimulus_type == "low_stim", ]
low <-
  plot_twovariable(
    df_low, iv1, iv2, group, subject, xmin=0, xmax=180, ymin=0,ymax=180, xlab, ylab,
    ggtitle = "Low intensity",
    color_scheme = c("high_cue" ="#FF8800","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "loess"
  )

# med stimulus intensity
df_med = df_dropna[df_dropna$param_stimulus_type == "med_stim", ]
med <-
  plot_twovariable(
    df_med, iv1, iv2, group, subject, xmin=0, xmax=180, ymin=0,ymax=180, xlab, ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("high_cue" ="#DB6000","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )

# high stimulus intensity
df_high = df_dropna[df_dropna$param_stimulus_type == "high_stim", ]
high <-
  plot_twovariable(
    df_high, iv1, iv2, group, subject, xmin=0, xmax=180, ymin=0,ymax=180, xlab, ylab,
    ggtitle = "High intensity",
    color_scheme = c("high_cue" ="#941100","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n Expect/Outcome linear relationship differs as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```

### ODR distance: Q. Are those overestimating for high cues also underestimators for low cues?  {.unlisted .unnumbered}
Note: Warning: Removed 1 rows containing non-finite values (`stat_half_ydensity()`).

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
iv1 = "event02_expect_angle"; iv2 = "event04_actual_angle"
pvc$odr_expectoutcome = abs(pvc$event02_expect_angle + pvc$event04_actual_angle) / sqrt(2)

cooksd <- lmer_onefactor_cooksd(pvc, "pain", iv = "cue_name", dv= "odr_expectoutcome", subject_keyword = "src_subject_id",
                                  dv_keyword = "distance from 1:1", model_savefname = "/Users/h/Desktop/TEST.txt", print_lmer_output = TRUE) 
```
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
subject_keyword = "src_subject_id"
model_iv1 = "cue_name"
dv = "odr_expectoutcome"
groupwise_measurevar = "mean_per_sub"

iv <- "cue_name"; iv_keyword <- "cue"; dv <- "odr_expectoutcome"; dv_keyword <- "odr_expectoutcome"
xlab <- ""; ylim = c(-10,180); ylab <- "Distance from 1:1 baseline"
subject <- "src_subject_id"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
subjectwise_mean <- "mean_per_sub"; group_mean <- "mean_per_sub_norm_mean"; se <- "se"
subjectwise <- meanSummary(
        pvc,
        c(subject_keyword, model_iv1), dv 
    )
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = groupwise_measurevar,
        withinvars = c(model_iv1), idvar = subject_keyword
    )
ggtitle = paste(taskname, "ODR distance of expect-outcome rating from 1:1")
title = "cue"

  color_scheme <-     if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color_scheme <- c("#1B9E77", "#D95F02")
    } else {
        # color_scheme <- c("#4575B4", "#D73027")
        color_scheme <- c("#941100","#5D5C5C")
    }

save_fname = "/Users/h/Desktop/TEST.png"
p <- plot_halfrainclouds_onefactor(subjectwise, groupwise, iv,
                                      subjectwise_mean, group_mean, se, subject,
                                      ggtitle, title, xlab, ylab, taskname, ylim,
                                      w = 10, h = 10, dv_keyword, color =color_scheme, save_fname)
p
```


## Vicarious
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
xlab <- ""
taskname <- "vicarious"
ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"
data <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model15_iv-cue-stim-N1outcome-expect_dv-outcome-demean", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)

maindata <- data %>%
group_by(src_subject_id) %>%
mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
mutate(demean_outcome = event04_actual_angle - avg_outcome) %>%
mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
mutate(demean_expect = event02_expect_angle - avg_expect)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
data_p2= maindata %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_a3 <- data_p2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

data_a3lag <- 
    data_a3 %>%
    group_by(src_subject_id, session_id, param_run_num) %>%
    mutate(lag.04outcomeangle = dplyr::lag(event04_actual_angle, n = 1, default = NA))
data_a3lag_omit <- data_a3lag[complete.cases(data_a3lag$lag.04outcomeangle),]

df <- data_a3lag_omit
pvc <- simple_contrasts_beh(df)


```

### Vicarious linear model {.unlisted .unnumbered}
```{r echo=FALSE, message=TRUE, warning=TRUE}
model.factorize = lmer(event04_actual_angle~ CUE_high_gt_low*stim_con_linear*event02_expect_angle + CUE_high_gt_low*stim_con_quad*event02_expect_angle +lag.04outcomeangle+ (1|src_subject_id), data = pvc)
# summary(model.factorize)
tab_model(model.factorize, p.val = "kr", show.df = TRUE)
```

### Vicarious run, collapsed across stimulus intensity {.unlisted .unnumbered}
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
df_dropna <-
  pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
total <-
  plot_twovariable(
    df_dropna,
    iv1 = "event02_expect_angle", iv2 = "event04_actual_angle",
    group = "param_cue_type",
    subject = "src_subject_id",
    xmin=0, xmax=180, ymin=0,ymax=180,
    xlab = "expectation rating",
    ylab = "outcome rating", 
    ggtitle = paste(taskname, "all stimulus intensity"),
    color_scheme = c("high_cue" ="#009411","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = FALSE, lm_method = "lm"
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for outcome and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n"))
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
iv1 = "event02_expect_angle"; iv2 = "event04_actual_angle"
# low stimulus intensity
df_low = df_dropna[df_dropna$param_stimulus_type == "low_stim", ]
low <-
  plot_twovariable(
    df_low, iv1, iv2,
    group = "param_cue_type", subject = "src_subject_id",
    xmin=0, xmax=180, ymin=0,ymax=180,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "Low stimulus",
    color_scheme = c("high_cue" ="#9CDB06","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )

# med stimulus intensity
df_med = df_dropna[df_dropna$param_stimulus_type == "med_stim", ]
med <-
  plot_twovariable(
    df_med, iv1, iv2,
    group = "param_cue_type", subject = "src_subject_id",
    xmin=0, xmax=180, ymin=0,ymax=180,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "Medium stimulus",
    color_scheme = c("high_cue" ="#4EB80B","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )

# high stimulus intensity
df_high = df_dropna[df_dropna$param_stimulus_type == "high_stim", ]
high <-
  plot_twovariable(
    df_high, iv1, iv2,
    group = "param_cue_type", subject = "src_subject_id",
    xmin=0, xmax=180, ymin=0,ymax=180,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "High stimulus",
    color_scheme = c("high_cue" ="#009411","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )
vic_plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(vic_plots, top = text_grob(paste(str_to_title(taskname), "\n Expect/Outcome linear relationship differs as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```


### ODR distance: Q. Are those overestimating for high cues also underestimators for low cues?  {.unlisted .unnumbered}
Note: Warning: Removed 1 rows containing non-finite values (`stat_half_ydensity()`).

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
pvc$odr_expectoutcome = abs(pvc$event02_expect_angle + pvc$event04_actual_angle) / sqrt(2)

cooksd <- lmer_onefactor_cooksd(pvc, "pain", iv = "cue_name", dv= "odr_expectoutcome", subject_keyword = "src_subject_id",
                                  dv_keyword = "distance from 1:1", model_savefname = "/Users/h/Desktop/TEST.txt", print_lmer_output = TRUE) 
```
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
subject_keyword = "src_subject_id"
model_iv1 = "cue_name"
dv = "odr_expectoutcome"
groupwise_measurevar = "mean_per_sub"

iv <- "cue_name"; iv_keyword <- "cue"; dv <- "odr_expectoutcome"; dv_keyword <- "odr_expectoutcome"
xlab <- ""; ylim = c(-10,180); ylab <- "Distance from 1:1 baseline"
subject <- "src_subject_id"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
subjectwise_mean <- "mean_per_sub"; group_mean <- "mean_per_sub_norm_mean"; se <- "se"
subjectwise <- meanSummary(
        pvc,
        c(subject_keyword, model_iv1), dv 
    )
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = groupwise_measurevar,
        withinvars = c(model_iv1), idvar = subject_keyword
    )
ggtitle = "ODR distance of expect-outcome rating from 1:1"
title = "cue"

  color_scheme <-     if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color_scheme <- c("#1B9E77", "#D95F02")
    } else {
        # color_scheme <- c("#4575B4", "#D73027")
        color_scheme <- c("#009411","#5D5C5C")
    }

save_fname = "/Users/h/Desktop/TEST.png"
p <- plot_halfrainclouds_onefactor(subjectwise, groupwise, iv,
                                      subjectwise_mean, group_mean, se, subject,
                                      ggtitle, title, xlab, ylab, taskname, ylim,
                                      w = 10, h = 10, dv_keyword, color =color_scheme, save_fname)
p
```

## Cognitive
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
xlab <- ""
taskname <- "cognitive"
ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"
data <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model15_iv-cue-stim-N1outcome-expect_dv-outcome-demean", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)

maindata <- data %>%
group_by(src_subject_id) %>%
mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
mutate(demean_outcome = event04_actual_angle - avg_outcome) %>%
mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
mutate(demean_expect = event02_expect_angle - avg_expect)

data_p2= maindata %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_a3 <- data_p2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

data_a3lag <- 
    data_a3 %>%
    group_by(src_subject_id, session_id, param_run_num) %>%
    mutate(lag.04outcomeangle = dplyr::lag(event04_actual_angle, n = 1, default = NA))
data_a3lag_omit <- data_a3lag[complete.cases(data_a3lag$lag.04outcomeangle),]

df <- data_a3lag_omit
pvc <- simple_contrasts_beh(df)

```

### Cognitive linear model {.unlisted .unnumbered}
```{r echo=FALSE, message=TRUE, warning=TRUE}
model.factorize = lmer(event04_actual_angle~ CUE_high_gt_low*stim_con_linear*event02_expect_angle + CUE_high_gt_low*stim_con_quad*event02_expect_angle +lag.04outcomeangle+ (1|src_subject_id), data = pvc)
# summary(model.factorize)
tab_model(model.factorize, p.val = "kr", show.df = TRUE)
```

### cognitive parameters
```{r}
iv1 = "event02_expect_angle"; iv2 = "event04_actual_angle";
group = "param_cue_type"; subject = "src_subject_id"; 
xlab = "expectation rating"; ylab = "outcome rating"
min = 0; max = 180
```

### Cognitive run, collapsed across stimulus intensity {.unlisted .unnumbered}
Warning: Warning: Removed 2 rows containing missing values (`geom_line()`).
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
df_dropna <-
  pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
total <-
  plot_twovariable(
    df_dropna, iv1, iv2, group, subject,
    xmin=0, xmax=180, ymin=0,ymax=180, xlab, ylab, 
    ggtitle = "all stimulus intensity",
    color_scheme = c("high_cue" ="#110094","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = FALSE, lm_method = "lm"
  )
title =paste0("task-",taskname, "- What is the pattern for outcome and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
plots_title <- annotate_figure(total, top = text_grob(title, color = "black", face = "bold", size = 12))
plots_title
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv1 = "event02_expect_angle"; iv2 = "event04_actual_angle"
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_low = df_dropna[df_dropna$param_stimulus_type == "low_stim", ]
low <-
  plot_twovariable(
    df_low, iv1, iv2, group, subject,
    xmin=0, xmax=180, ymin=0,ymax=180, xlab, ylab, 
    ggtitle = "Low intensity",
    color_scheme = c("high_cue" ="#9400DB","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_med = df_dropna[df_dropna$param_stimulus_type == "med_stim", ]
med <-
  plot_twovariable(
    df_med, iv1, iv2, group, subject,
    xmin=0, xmax=180, ymin=0,ymax=180, xlab, ylab, 
    ggtitle = "Medium intensity",
    color_scheme = c("high_cue" ="#5200B8","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_high = df_dropna[df_dropna$param_stimulus_type == "high_stim", ]
high <-
  plot_twovariable(
    df_high, iv1, iv2, group, subject,
    xmin=0, xmax=180, ymin=0,ymax=180, xlab, ylab, 
    ggtitle = "High intensity",
    color_scheme = c("high_cue" ="#110094","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )
cog_plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(cog_plots, top = text_grob(paste(str_to_title(taskname), "\n Expect/Outcome linear relationship differs as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```


### ODR distance: Q. Are those overestimating for high cues also underestimators for low cues?  {.unlisted .unnumbered}
Note: Warning: Removed 1 rows containing non-finite values (`stat_half_ydensity()`).
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
pvc$odr_expectoutcome = abs(pvc$event02_expect_angle + pvc$event04_actual_angle) / sqrt(2)

cooksd = lmer_onefactor_cooksd(pvc, "pain", iv = "cue_name", dv= "odr_expectoutcome", subject_keyword = "src_subject_id",
                                  dv_keyword = "distance from 1:1", model_savefname = "/Users/h/Desktop/TEST.txt", print_lmer_output = TRUE) 
```
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
subject_keyword = "src_subject_id"
model_iv1 = "cue_name"
dv = "odr_expectoutcome"
groupwise_measurevar = "mean_per_sub"

iv <- "cue_name"; iv_keyword <- "cue"; dv <- "odr_expectoutcome"; dv_keyword <- "odr_expectoutcome"
xlab <- ""; ylim = c(-10,180); ylab <- "Distance from 1:1 baseline"
subject <- "src_subject_id"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
subjectwise_mean <- "mean_per_sub"; group_mean <- "mean_per_sub_norm_mean"; se <- "se"
subjectwise <- meanSummary(
        pvc,
        c(subject_keyword, model_iv1), dv 
    )
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = groupwise_measurevar,
        withinvars = c(model_iv1), idvar = subject_keyword
    )
ggtitle = "ODR distance of expect-outcome rating from 1:1"
title = "cue"

  color_scheme <-     if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color_scheme <- c("#1B9E77", "#D95F02")
    } else {
        # color_scheme <- c("#4575B4", "#D73027")
        color_scheme <- c("#110094","#5D5C5C")
    }

save_fname = "/Users/h/Desktop/TEST.png"
p <- plot_halfrainclouds_onefactor(subjectwise, groupwise, iv,
                                      subjectwise_mean, group_mean, se, subject,
                                      ggtitle, title, xlab, ylab, taskname, ylim,
                                      w = 10, h = 10, dv_keyword, color =color_scheme, save_fname)
p
```
```{r}
library(plotly)
plot_ly(x=subjectwise_naomit_2dv$param_cue_type, y=subjectwise_naomit_2dv$DV1_mean_per_sub, z=subjectwise_naomit_2dv$DV2_mean_per_sub, type="scatter3d", mode="markers", color=subjectwise_naomit_2dv$param_cue_type)
```

