# [ beh ] outcome_demean ~ cue * stim * expectrating * n-1outcomerating  {#ch15_demean_per_sub}

## What is the purpose of this notebook? {.unlisted .unnumbered}
Here, I model the outcome ratings as a function of cue, stimulus intensity, expectation ratings, N-1 outcome rating.
* As opposed to notebook 14, I demean the ratings within participants
* In other words, calculate the average within subjects and subtract ratings 
* Main model: `lmer(outcome_rating ~ cue * stim * expectation rating + N-1 outcomerating)` 
* Main question: What constitutes a reported outcome rating? 
* Sub questions:
  - If there is a linear relationship between expectation rating and outcome rating, does this differ as a function of cue?
  - How does a N-1 outcome rating affect current expectation ratings? 
  - Later, is this effect different across tasks or are they similar?

* IV: 
  stim (high / med / low)
  cue (high / low)
  expectation rating (continuous)
  N-1 outcome rating (continuous)
* DV: outcome rating

### Some thoughts, TODOs {.unlisted .unnumbered}

* Standardized coefficients
* Slope difference? Intercept difference? ( cue and expectation rating)
* Correct for the range (within participant)
hypothesis:
1. Larger expectation leads to prediction error
2. Individual differences in ratings
3. Outcome experience, based on behavioral experience
What are the brain maps associated with each component.  


```{r load_libraries_15, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
# library(lmSupport)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(tidyverse)
library(GGally)
library(lme4)
library(gghalves)
library(effectsize)
library(devtools)
library(visibly) # 
library(plotly) #plot
library(scico) # plot
library(emmeans) # v. 1.7.0
library(magrittr) # v. 2.0.1
source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
# source("https://gist.github.com/benmarwick/2a1bb0133ff568cbe28d/geom_flat_violin.R")

library(r2mlm)
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

load data and combine participant data

```{r load_data_and_exclude_m1, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "pain"

ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"

# load data _____________________________________
data <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
# data['event03_RT'], data.event03_RT - pandas
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model15_iv-cue-stim-N1outcome-expect_dv-outcome", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```

```{r outcomerating_descriptivestats, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
summary(data[, c("event02_expect_RT", "event04_actual_RT", "event02_expect_angle", "event04_actual_angle")])
```
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# data(data, package = 'visibly')

myvars <- names(data) %in% 
  c( "event02_expect_angle", "event02_expect_RT", "event04_actual_angle", "event04_actual_RT", "event01_cue_onset")
newdata <- data[myvars]
# numdata  <- unlist(lapply(data, is.numeric), use.names = FALSE) 
data_naomit <- na.omit(newdata)
cor_matrix = cor(data_naomit)
corr_heat(cor_matrix)
```
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

ISIvars <- names(data) %in% 
  c( "ISI01_duration", "ISI02_duration", "ISI03_duration")
ISIdata <- data[ISIvars]
# numdata  <- unlist(lapply(data, is.numeric), use.names = FALSE) 
ISIdata_naomit <- na.omit(ISIdata)
ISIcor_matrix = cor(ISIdata_naomit)
corr_heat(ISIcor_matrix)
```

```{r function::simple_contrasts_beh, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
simple_contrasts_beh <- function(df) {
# [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
df$stim_factor <- factor(df$param_stimulus_type)

# contrast code 1 linear
df$stim_con_linear[df$param_stimulus_type == "low_stim"] <-  -0.5
df$stim_con_linear[df$param_stimulus_type == "med_stim"] <-  0
df$stim_con_linear[df$param_stimulus_type == "high_stim"] <-  0.5

# contrast code 2 quadratic
df$stim_con_quad[df$param_stimulus_type == "low_stim"] <-  -0.33
df$stim_con_quad[df$param_stimulus_type == "med_stim"] <-  0.66
df$stim_con_quad[df$param_stimulus_type == "high_stim"] <-  -0.33

# cue contrast
df$cue_con[df$param_cue_type == "low_cue"] <-  -0.5 # social influence task
df$cue_con[df$param_cue_type == "high_cue"] <-  0.5 # no influence task

df$stim_ordered <- factor(
        df$param_stimulus_type,
        levels = c("low_stim", "med_stim", "high_stim")
    )

df$cue_name[df$param_cue_type == "low_cue"] <- "low"
df$cue_name[df$param_cue_type == "high_cue"] <- "high"

df$cue_ordered <- factor(
        df$cue_name,
        levels = c("low", "high")
    )
return(df)
}
```

### groupby subject and average
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
maindata <- data %>%
group_by(src_subject_id) %>%
mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
mutate(demean_outcome = event04_actual_angle - avg_outcome) %>%
mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
mutate(demean_expect = event02_expect_angle - avg_expect)

data_p2= maindata %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_a3 <- data_p2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

data_a3lag <- 
    data_a3 %>%
    group_by(src_subject_id, session_id, param_run_num) %>%
    mutate(lag.demean_outcome = dplyr::lag(demean_outcome, n = 1, default = NA))
data_a3lag_omit <- data_a3lag[complete.cases(data_a3lag$lag.demean_outcome),]

df <- data_a3lag_omit
pvc <- simple_contrasts_beh(df)
```

## linear model
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
model.factorize_demean = lmer(demean_outcome~ cue_con*stim_factor*demean_expect +lag.demean_outcome+ (1|src_subject_id), data = pvc)
summary(model.factorize_demean)


```

## Q. Are those overestimating for high cues also underestimators for low cues?
y axis: oiutcome rating
x axis: high cue

distance from 1:1 line
```{r echo=FALSE, warning=TRUE}

pvc$odr_expectoutcome = abs(pvc$demean_expect + pvc$demean_outcome) / sqrt(2)

cooksd = lmer_onefactor_cooksd(pvc, "pain", iv = "cue_name", dv= "odr_expectoutcome", subject_keyword = "src_subject_id",
                                  dv_keyword = "distance from 1:1", model_savefname = "/Users/h/Desktop/TEST.txt", print_lmer_output = TRUE) 
```
Can you test if the slopes are the same? That might tell us something about whether, expectancies translate into outcomes with the same efficacy across all three tasks. 



```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
pvc$odr_expectoutcome = abs(pvc$demean_expect + pvc$demean_outcome) / sqrt(2)

cooksd = lmer_onefactor_cooksd(pvc, "pain", iv = "cue_name", dv= "odr_expectoutcome", subject_keyword = "src_subject_id",
                                  dv_keyword = "distance from 1:1", model_savefname = "/Users/h/Desktop/TEST.txt", print_lmer_output = TRUE) 

subject_keyword = "src_subject_id"
model_iv1 = "cue_name"
dv = "odr_expectoutcome"
groupwise_measurevar = "mean_per_sub"

iv <- "cue_name"; iv_keyword <- "cue"; dv <- "odr_expectoutcome"; dv_keyword <- "odr_expectoutcome"
xlab <- ""; ylim = c(-90,90); ylab <- "Distance from 1:1 baseline"
subject <- "src_subject_id"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
subjectwise_mean <- "mean_per_sub"; group_mean <- "mean_per_sub_norm_mean"; se <- "se"
subjectwise <- meanSummary(
        pvc,
        c(subject_keyword, model_iv1), dv 
    )
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = groupwise_measurevar,
        withinvars = c(model_iv1), idvar = subject_keyword
    )
ggtitle = "ODR distance of expect-outcome rating from 1:1"
title = "cue"

  color_scheme <-     if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color_scheme <- c("#1B9E77", "#D95F02")
    } else {
        # color_scheme <- c("#4575B4", "#D73027")
        color_scheme <- c("#941100","#5D5C5C")
    }

save_fname = "/Users/h/Desktop/TEST.png"
p <- plot_halfrainclouds_onefactor(subjectwise, groupwise, iv,
                                      subjectwise_mean, group_mean, se, subject,
                                      ggtitle, title, xlab, ylab, taskname, ylim,
                                      w = 10, h = 10, dv_keyword, color =color_scheme, save_fname)
p
```




## pain run, collapsed across stimulus intensity
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
df_dropna <-
  pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
total <-
  plot_twovariable(
    df_dropna,
    iv1 = "demean_expect",
    iv2 = "demean_outcome",
    group = "param_cue_type",
    subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating",
    ylab = "outcome rating", 
    ggtitle = "all stimulus intensity", 
    color_scheme = c("high_cue" ="#941100","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE
  )
total
```
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_low = df_dropna[df_dropna$param_stimulus_type == "low_stim", ]
low <-
  plot_twovariable(
    df_low, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "Low intensity",
    color_scheme = c("high_cue" ="#FF8800","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE
  )
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_med = df_dropna[df_dropna$param_stimulus_type == "med_stim", ]
med <-
  plot_twovariable(
    df_med, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "Medium intensity",
    color_scheme = c("high_cue" ="#DB6000","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE
  )
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_high = df_dropna[df_dropna$param_stimulus_type == "high_stim", ]
high <-
  plot_twovariable(
    df_high, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "High intensity",
    color_scheme = c("high_cue" ="#941100","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob("individual differences\n - cue effects from outcome ratings", color = "black", face = "bold", size = 15))
plots
```

## vicarious
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
xlab <- ""
taskname <- "vicarious"
ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"
data <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model15_iv-cue-stim-N1outcome-expect_dv-outcome-demean", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)

maindata <- data %>%
group_by(src_subject_id) %>%
mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
mutate(demean_outcome = event04_actual_angle - avg_outcome) %>%
mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
mutate(demean_expect = event02_expect_angle - avg_expect)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
data_p2= maindata %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_a3 <- data_p2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

data_a3lag <- 
    data_a3 %>%
    group_by(src_subject_id, session_id, param_run_num) %>%
    mutate(lag.demean_outcome = dplyr::lag(demean_outcome, n = 1, default = NA))
data_a3lag_omit <- data_a3lag[complete.cases(data_a3lag$lag.demean_outcome),]

df <- data_a3lag_omit
pvc <- simple_contrasts_beh(df)


```
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
df_dropna <-
  pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
total <-
  plot_twovariable(
    df_dropna,
    iv1 = "demean_expect",
    iv2 = "demean_outcome",
    group = "param_cue_type",
    subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating",
    ylab = "outcome rating", 
    ggtitle = paste(taskname, "all stimulus intensity"),
    color_scheme = c("high_cue" ="#009411","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE
  )
total
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_low = df_dropna[df_dropna$param_stimulus_type == "low_stim", ]
low <-
  plot_twovariable(
    df_low, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "Low intensity",
    color_scheme = c("high_cue" ="#9CDB06","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE
  )
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_med = df_dropna[df_dropna$param_stimulus_type == "med_stim", ]
med <-
  plot_twovariable(
    df_med, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "Medium intensity",
    color_scheme = c("high_cue" ="#4EB80B","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE
  )
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_high = df_dropna[df_dropna$param_stimulus_type == "high_stim", ]
high <-
  plot_twovariable(
    df_high, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "High intensity",
    color_scheme = c("high_cue" ="#009411","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE
  )
vic_plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(vic_plots, top = text_grob("individual differences\n - cue effects from outcome ratings", color = "black", face = "bold", size = 15))
vic_plots
```
```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
pvc$odr_expectoutcome = abs(pvc$demean_expect + pvc$demean_outcome) / sqrt(2)

cooksd <- lmer_onefactor_cooksd(pvc, "pain", iv = "cue_name", dv= "odr_expectoutcome", subject_keyword = "src_subject_id",
                                  dv_keyword = "distance from 1:1", model_savefname = "/Users/h/Desktop/TEST.txt", print_lmer_output = TRUE) 

subject_keyword = "src_subject_id"
model_iv1 = "cue_name"
dv = "odr_expectoutcome"
groupwise_measurevar = "mean_per_sub"

iv <- "cue_name"; iv_keyword <- "cue"; dv <- "odr_expectoutcome"; dv_keyword <- "odr_expectoutcome"
xlab <- ""; ylim = c(-90,90); ylab <- "Distance from 1:1 baseline"
subject <- "src_subject_id"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
subjectwise_mean <- "mean_per_sub"; group_mean <- "mean_per_sub_norm_mean"; se <- "se"
subjectwise <- meanSummary(
        pvc,
        c(subject_keyword, model_iv1), dv 
    )
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = groupwise_measurevar,
        withinvars = c(model_iv1), idvar = subject_keyword
    )
ggtitle = "ODR distance of expect-outcome rating from 1:1"
title = "cue"

  color_scheme <-     if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color_scheme <- c("#1B9E77", "#D95F02")
    } else {
        # color_scheme <- c("#4575B4", "#D73027")
        color_scheme <- c("#009411","#5D5C5C")
    }

save_fname = "/Users/h/Desktop/TEST.png"
p <- plot_halfrainclouds_onefactor(subjectwise, groupwise, iv,
                                      subjectwise_mean, group_mean, se, subject,
                                      ggtitle, title, xlab, ylab, taskname, ylim,
                                      w = 10, h = 10, dv_keyword, color =color_scheme, save_fname)
p
```

## cognitive
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
xlab <- ""
taskname <- "cognitive"
ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"
data <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model15_iv-cue-stim-N1outcome-expect_dv-outcome-demean", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)

maindata <- data %>%
group_by(src_subject_id) %>%
mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
mutate(demean_outcome = event04_actual_angle - avg_outcome) %>%
mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
mutate(demean_expect = event02_expect_angle - avg_expect)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
data_p2= maindata %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_a3 <- data_p2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

data_a3lag <- 
    data_a3 %>%
    group_by(src_subject_id, session_id, param_run_num) %>%
    mutate(lag.demean_outcome = dplyr::lag(demean_outcome, n = 1, default = NA))
data_a3lag_omit <- data_a3lag[complete.cases(data_a3lag$lag.demean_outcome),]

df <- data_a3lag_omit
pvc <- simple_contrasts_beh(df)
```
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
df_dropna <-
  pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
total <-
  plot_twovariable(
    df_dropna,
    iv1 = "demean_expect",
    iv2 = "demean_outcome",
    group = "param_cue_type",
    subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating",
    ylab = "outcome rating", 
    ggtitle = "all stimulus intensity",
    color_scheme = c("high_cue" ="#110094","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE
  )
total
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_low = df_dropna[df_dropna$param_stimulus_type == "low_stim", ]
low <-
  plot_twovariable(
    df_low, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "Low intensity",
    color_scheme = c("high_cue" ="#9400DB","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE
  )
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_med = df_dropna[df_dropna$param_stimulus_type == "med_stim", ]
med <-
  plot_twovariable(
    df_med, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "Medium intensity",
    color_scheme = c("high_cue" ="#5200B8","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE
  )
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_high = df_dropna[df_dropna$param_stimulus_type == "high_stim", ]
high <-
  plot_twovariable(
    df_high, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "High intensity",
    color_scheme = c("high_cue" ="#110094","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE
  )
vic_plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(vic_plots, top = text_grob("individual differences\n - cue effects from outcome ratings", color = "black", face = "bold", size = 15))
vic_plots
```


```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
pvc$odr_expectoutcome = abs(pvc$demean_expect + pvc$demean_outcome) / sqrt(2)

cooksd = lmer_onefactor_cooksd(pvc, "pain", iv = "cue_name", dv= "odr_expectoutcome", subject_keyword = "src_subject_id",
                                  dv_keyword = "distance from 1:1", model_savefname = "/Users/h/Desktop/TEST.txt", print_lmer_output = TRUE) 

subject_keyword = "src_subject_id"
model_iv1 = "cue_name"
dv = "odr_expectoutcome"
groupwise_measurevar = "mean_per_sub"

iv <- "cue_name"; iv_keyword <- "cue"; dv <- "odr_expectoutcome"; dv_keyword <- "odr_expectoutcome"
xlab <- ""; ylim = c(-90,90); ylab <- "Distance from 1:1 baseline"
subject <- "src_subject_id"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
subjectwise_mean <- "mean_per_sub"; group_mean <- "mean_per_sub_norm_mean"; se <- "se"
subjectwise <- meanSummary(
        pvc,
        c(subject_keyword, model_iv1), dv 
    )
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = groupwise_measurevar,
        withinvars = c(model_iv1), idvar = subject_keyword
    )
ggtitle = "ODR distance of expect-outcome rating from 1:1"
title = "cue"

  color_scheme <-     if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color_scheme <- c("#1B9E77", "#D95F02")
    } else {
        # color_scheme <- c("#4575B4", "#D73027")
        color_scheme <- c("#110094","#5D5C5C")
    }

save_fname = "/Users/h/Desktop/TEST.png"
p <- plot_halfrainclouds_onefactor(subjectwise, groupwise, iv,
                                      subjectwise_mean, group_mean, se, subject,
                                      ggtitle, title, xlab, ylab, taskname, ylim,
                                      w = 10, h = 10, dv_keyword, color =color_scheme, save_fname)
p
```
```{r}
# library(plotly)
# plot_ly(x=subjectwise_naomit_2dv$param_cue_type, y=subjectwise_naomit_2dv$DV1_mean_per_sub, z=subjectwise_naomit_2dv$DV2_mean_per_sub, type="scatter3d", mode="markers", color=subjectwise_naomit_2dv$param_cue_type)
```

## across tasks (PVC), is the  slope for (highvslow cue) the same?Tor question
* Adding "participant" as random effects leads to a singular boundary issue. The reason is because there is no random effects variance across participants. 
1) If I add task as a random effect, in other words, allowing for differences across tasks, I get the following results: 
* expectancy-outcome relationship differs across tasks, taskname_lin:demean_expect, t(14130) = 4.317, p < .001
* expectancy-outcome relationship differs across cue and tasks, "taskname_lin:cue_con:demean_expect", t(14130) = 5.758, p < .001
taskname_lin:cue_con                -3.790e+00  1.448e+00  1.413e+04  -2.618  0.00886 ** 
++ taskname_lin:demean_expect           9.854e-02  2.283e-02  1.413e+04   4.317 1.59e-05 ***
cue_con:demean_expect               -9.077e-02  1.987e-02  1.413e+04  -4.569 4.95e-06 ***
cue_con:taskname_quad                5.352e+00  1.334e+00  1.413e+04   4.012 6.04e-05 ***
demean_expect:taskname_quad         -1.596e-01  2.253e-02  1.413e+04  -7.084 1.47e-12 ***
taskname_lin:cue_con:demean_expect   2.629e-01  4.565e-02  1.413e+04   5.758 8.67e-09 ***
cue_con:demean_expect:taskname_quad -1.021e-01  4.505e-02  1.413e+04  -2.266  0.02348 *  

2) If I add sub as random effect and ignore singular. Plus, if I remove the cue contrast...
* expectancy-outcome relationship differs across tasks, factor(param_task_name):demean_expect, F(2, 14136) = 54.765, p < .001
 
```{r}
p <- load_task_social_df(datadir, taskname = 'pain', subject_varkey = subject_varkey, iv = iv, exclude = exclude)
v <- load_task_social_df(datadir, taskname = 'vicarious', subject_varkey = subject_varkey, iv = iv, exclude = exclude)
c <- load_task_social_df(datadir, taskname = 'cognitive', subject_varkey = subject_varkey, iv = iv, exclude = exclude)
p_sub <- p[, c("param_task_name", "param_cue_type", "src_subject_id","session_id", "param_run_num", "param_stimulus_type", "event04_actual_angle", "event02_expect_angle")]
v_sub <- v[, c("param_task_name", "param_cue_type", "src_subject_id","session_id", "param_run_num", "param_stimulus_type", "event04_actual_angle", "event02_expect_angle")]
c_sub <- c[, c("param_task_name", "param_cue_type", "src_subject_id", "session_id", "param_run_num","param_stimulus_type", "event04_actual_angle", "event02_expect_angle")]
pvc_sub <- do.call("rbind", list(p_sub, v_sub, c_sub))
```
```{r}
maindata <- pvc_sub %>%
group_by(src_subject_id) %>%
mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
mutate(demean_outcome = event04_actual_angle - avg_outcome) %>%
mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
mutate(demean_expect = event02_expect_angle - avg_expect)

data_p2= maindata %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_a3 <- data_p2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

data_a3lag <- 
    data_a3 %>%
    group_by(src_subject_id, session_id, param_run_num) %>%
    mutate(lag.demean_outcome = dplyr::lag(demean_outcome, n = 1, default = NA))
data_a3lag_omit <- data_a3lag[complete.cases(data_a3lag$lag.demean_outcome),]

df <- data_a3lag_omit
pvc_sub <- simple_contrasts_beh(df)
```

```{r}
# contrast code 1 linear
pvc_sub$taskname_lin[pvc_sub$param_task_name == "pain"] <-  0.5
pvc_sub$taskname_lin[pvc_sub$param_task_name == "vicarious"] <-  0
pvc_sub$taskname_lin[pvc_sub$param_task_name == "cognitive"] <-  -0.5

# contrast code 2 quadratic
pvc_sub$taskname_quad[pvc_sub$param_task_name == "pain"] <-  -0.33
pvc_sub$taskname_quad[pvc_sub$param_task_name == "vicarious"] <-  0.66
pvc_sub$taskname_quad[pvc_sub$param_task_name == "cognitive"] <-  -0.33

pvc_sub$sub = factor(pvc_sub$src_subject_id)
# model_test = lm(pvc_sub$demean_outcome~ pvc_sub$demean_expect)
model_task = lmer(demean_outcome~ taskname_lin*cue_con*demean_expect + taskname_quad*cue_con*demean_expect +  (1 | sub), data = pvc_sub)
model_wotask = lmer(demean_outcome~ cue_con*demean_expect +(1 | sub), data = pvc_sub)
summary(model_task)
anova(model_task)
anova(model_wotask, model_task)
# summary(model_test)
```

```{r}
model_task1 = lmer(demean_outcome~ factor(param_task_name)*demean_expect  +  (1 | sub), data = pvc_sub)
model_wotask1 = lmer(demean_outcome~ demean_expect+ (1 | sub), data = pvc_sub)
summary(model_task1)
anova(model_task1)
anova(model_wotask1)
anova(model_wotask1, model_task1)

```

```{r}
library(emmeans)
# emm1 = emmeans(model_task, specs = pairwise ~ stimintensity:task)
# emm1
```

