#  (N-1) shifted outcome ratings ~ (N) expectation ratings; {#ch18_linear_vs_sigmoidal}

```
title: "model12_jayazeri_N-2"
date: '2023-01-31'
updated: '2023-01-31'
```



## Overview 

Here, we want to test whether the relationship between N-1 and expectation is sigmoidal or not. 
1) fit a cubic: sigmoidal
2) fit a quadratic and see if there's an interaction


https://www.statology.org/curve-fitting-in-r/

```{r}
psych::mediate(event04_actual_angle ~ cue_con*stim_con_linear+ event02_expect_angle + lag.04outcomeangle, data = pvc, n.iter = 1000) %>% print(short = FALSE) 
```

### need to calculate participant level average score for 
```{r}
iv1 = "lag.04outcomeangle"
iv2 = "event02_expect_angle"
group = "param_cue_type"
df_dropna <- pvc[!is.na(pvc[, iv1]) & !is.na(df[, iv2]), ]
    subjectwise_2dv <- meanSummary_2dv(
        pvc,
        c("src_subject_id", "param_cue_type"),
        iv1, iv2
    )
subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
subjectwise_naomit_2dv[ , group] <- as.factor(subjectwise_naomit_2dv[, group])
```

# WORK ON THIS PART. FITTING POLYNOMIALS
```{r}
fit1 <- lm(DV2_mean_per_sub ~ DV1_mean_per_sub*param_cue_type, data=subjectwise_naomit_2dv)
fit2 <- lm(DV2_mean_per_sub ~ poly(param_cue_type+DV1_mean_per_sub,degree = 2,raw=TRUE), data=subjectwise_naomit_2dv)
# fit3 <- lm(DV2_mean_per_sub~poly(param_cue_type*DV1_mean_per_sub,3,raw=TRUE), data=subjectwise_naomit_2dv)
# fit4 <- lm(DV2_mean_per_sub~poly(param_cue_type*DV1_mean_per_sub,4,raw=TRUE), data=subjectwise_naomit_2dv)
# fit5 <- lm(DV2_mean_per_sub~poly(param_cue_type*DV1_mean_per_sub,5,raw=TRUE), data=subjectwise_naomit_2dv)

summary(fit1)$adj.r.squared
summary(fit2)$adj.r.squared
# summary(fit3)$adj.r.squared
# summary(fit4)$adj.r.squared
# summary(fit5)$adj.r.squared

plot(subjectwise_naomit_2dv$DV1_mean_per_sub, subjectwise_naomit_2dv$DV2_mean_per_sub,pch=19, xlab='x', ylab='y', asp=1)
x_axis <- seq(0,180, length=15)


lines(x_axis, predict(fit3, data.frame( cue_con = 0.5, DV1_mean_per_sub = x_axis)), col='purple')
lines(x_axis, predict(fit3, data.frame( cue_con = -0.5, DV1_mean_per_sub = x_axis)), col='pink')
```

# WORK ON THIS PART. FITTING POLYNOMIALS
```{r}
fit1 <- lm(event02_expect_angle ~ lag.04outcomeangle*cue_con, data=pvc)
fit2 <- lm(event02_expect_angle~poly(cue_con*lag.04outcomeangle,2,raw=TRUE), data=pvc)
fit3 <- lm(event02_expect_angle~poly(cue_con*lag.04outcomeangle,3,raw=TRUE), data=pvc)
fit4 <- lm(event02_expect_angle~poly(cue_con*lag.04outcomeangle,4,raw=TRUE), data=pvc)
fit5 <- lm(event02_expect_angle~poly(cue_con*lag.04outcomeangle,5,raw=TRUE), data=pvc)

summary(fit1)$adj.r.squared
summary(fit2)$adj.r.squared
summary(fit3)$adj.r.squared
summary(fit4)$adj.r.squared
summary(fit5)$adj.r.squared

plot(pvc$lag.04outcomeangle, pvc$event02_expect_angle,pch=19, xlab='x', ylab='y', asp=1)
x_axis <- seq(0,180, length=15)


lines(x_axis, predict(fit3, data.frame( cue_con = 0.5, lag.04outcomeangle = x_axis)), col='purple')
lines(x_axis, predict(fit3, data.frame( cue_con = -0.5, lag.04outcomeangle = x_axis)), col='pink')
```

```{r}
model.sig <- glm(event04_actual_angle ~ event02_expect_angle*cue_con+lag.04outcomeangle, family=binomial, data=pvc)
```


# WORK ON THIS PART. FITTING POLYNOMIALS
```{r}
fit1 <- lm(event04_actual_angle ~ event02_expect_angle*cue_con, data=pvc)
fit2 <- lm(event04_actual_angle~poly(cue_con*event02_expect_angle ,2,raw=TRUE), data=pvc)
fit3 <- lm(event04_actual_angle~poly(cue_con*event02_expect_angle,3,raw=TRUE), data=pvc)
fit4 <- lm(event04_actual_angle~poly(cue_con*event02_expect_angle,4,raw=TRUE), data=pvc)
fit5 <- lm(event04_actual_angle~poly(cue_con*event02_expect_angle,5,raw=TRUE), data=pvc)
# fit <- nls(grad ~ theta1/(1 + exp(-(theta2 + theta3*event02_expect_angle))), 
#            start=list(theta1 = 4, theta2 = 0.09, theta3 = 0.31), trace=TRUE)
summary(fit1)$adj.r.squared
summary(fit2)$adj.r.squared
summary(fit3)$adj.r.squared
summary(fit4)$adj.r.squared
summary(fit5)$adj.r.squared

plot(pvc$event02_expect_angle, pvc$event04_actual_angle,pch=19, xlab='x', ylab='y', asp=1)
x_axis <- seq(0,180, length=180)


lines(x_axis, predict(fit2, data.frame( cue_con = 0.5, event02_expect_angle = x_axis )), col='purple')
lines(x_axis, predict(fit2, data.frame( cue_con = -0.5,  event02_expect_angle = x_axis )), col='blue')
```

```{r}
# summarize dataframe __________________________________________________________
plot_twovariable <- function(df, iv1, iv2, group, subject, min, max, xlab, ylab, ggtitle, color_scheme, alpha, fit_lm) {
    # x: iv1 e.g. expect rating
    # y: iv2 e.g. outcome rating
    # group: param_cue_type
    # subject: src_subject_id
    # xlab("expect rating") +
    # ylab("outcome rating") +
    # color_scheme = c("high_cue" = "#000000",low_cue" = "#BBBBBB"        )
    library(ggplot2)

    df_dropna <- df[!is.na(df[, iv1]) & !is.na(df[, iv2]), ]
    subjectwise_2dv <- meanSummary_2dv(
        df_dropna,
        c(subject, group),
        iv1, iv2
    )
    subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
    subjectwise_naomit_2dv[ , group] <- as.factor(subjectwise_naomit_2dv[, group])
    # plot _________________________________________________________________________ #nolint

    g <- ggplot(
        data = subjectwise_naomit_2dv,
        aes(
            x = .data[["DV1_mean_per_sub"]],
            y = .data[["DV2_mean_per_sub"]],
            color = .data[[group]]
        )
    ) +
        geom_point(
            aes(shape = .data[[group]],
            color = .data[[group]]),
            size = 2,
            alpha = alpha) +
        geom_abline(
            intercept = 0, slope = 1, color = "green",
            linetype = "dashed", linewidth = 0.5
        ) +
        theme(aspect.ratio = 1) +
        scale_color_manual(values = color_scheme) +
        scale_shape_manual(values = c(16, 17)) +
        xlab(xlab) +
        ylab(ylab) +
        ylim(min,max) +
        xlim(min,max) +
        ggtitle(ggtitle) +
        theme(
            axis.line = element_line(colour = "grey50"),
            panel.background = element_blank(),
            plot.subtitle = ggtext::element_textbox_simple(size = 11)
        )


    if (isTRUE(fit_lm)) {
        g <- g +
        geom_ribbon(stat = "smooth", method = "gam", se = TRUE, alpha = 0.1,
              aes(color = NULL, group = factor(group))) +
        geom_line(stat = "smooth", method = "gam", alpha = 0.8, size = 1.5)
    } else {
        g
    }
    return(g)
}

```

```{r}
plot(pvc$event02_expect_angle, pvc$event04_actual_angle,pch=19, xlab='x', ylab='y', asp=1)
x_axis <- seq(0,180, length=180)


plot_twovariable(pvc, iv1 = "event02_expect_angle", 
                 iv2 = "event04_actual_angle", 
                 group = "cue_name", 
                 subject = "src_subject_id", min = 0, max =180, xlab = "expect", ylab = "outcome",
                 ggtitle = "loess", color_scheme =  c("high" ="#009411","low" =  "#5D5C5C"), alpha = 0.5, fit_lm = TRUE)
```


```{r}
fit1 <- lm(y~x, data=df)
fit2 <- lm(y~poly(x,2,raw=TRUE), data=df)
fit3 <- lm(y~poly(x,3,raw=TRUE), data=df)
fit4 <- lm(y~poly(x,4,raw=TRUE), data=df)

```

library
```{r load libraries, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(stats)
library(ggpubr)
library(equatiomatic)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lme4)
library(effectsize)
library(brms)
library(devtools)
library(gghalves)
library(visibly) # 
library(plotly) #plot
library(scico) # plot
#source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
# source("https://gist.github.com/benmarwick/2a1bb0133ff568cbe28d/geom_flat_violin.R")

library(r2mlm)
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

load data and combine participant data

```{r load data and exclude}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "pain"

ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"

# load data _____________________________________
data <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
# data['event03_RT'], data.event03_RT - pandas
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model12_iv-cue-trial_dv-expectjayazer_N-2", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```


## Do previous outcome ratings predict current expectation ratings?
### Additional analyse 01/18/2023 {.unlisted .unnumbered}
* examine if prior stimulus experience (N-2) predicts current expectation ratings
* see if current expectation ratings are explained as a function of prior outcome rating and current expectation rating

when loading the dataset, I need to add in trial index per dataframe.
Then, for the shift the rating? 
```{r}
data_p2= data %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_a3 <- data_p2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

data_a3lag <- 
    data_a3 %>%
    group_by(src_subject_id, session_id, param_run_num) %>%
    mutate(lag.04outcomeangle = dplyr::lag(event04_actual_angle, n = 2, default = NA))
data_a3lag_omit <- data_a3lag[complete.cases(data_a3lag$lag.04outcomeangle),]
```


```{r}
    trialorder_subjectwise_lagoutcome <- meanSummary(
        data_a3lag_omit,
        c("src_subject_id", "session_id", "param_run_num"), "lag.04outcomeangle" )
    trialorder_subjectwise_lagoutcome <- meanSummary(
        data_a3lag_omit,
        c("src_subject_id", "session_id", "param_run_num"), "lag.04outcomeangle" )

```
```{r}
model.lagoutcome = lmer(event02_expect_angle ~ lag.04outcomeangle + (1 | src_subject_id) + (1|session_id) , data = data_a3lag_omit)
summary(model.lagoutcome)
```

```{r}
meanSummary_2dv <- function(DATA, GROUP, DV1, DV2) {
    z <- ddply(DATA, GROUP, .fun = function(xx) {
        c(
            DV1_mean_per_sub = mean(xx[, DV1], na.rm = TRUE),
            DV1_sd = sd(xx[, DV1], na.rm = TRUE),
            DV2_mean_per_sub = mean(xx[, DV2], na.rm = TRUE),
            DV2_sd = sd(xx[, DV1], na.rm = TRUE)
        )
    })
    return(z)
}
```

```{r}
subjectwise_2dv = meanSummary_2dv(data_a3lag_omit,
        c("src_subject_id", "trial_index"), 
        "lag.04outcomeangle", "event02_expect_angle")
```

```{r}
subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
```

```{r}
sp <- ggplot(data=subjectwise_naomit_2dv, 
             aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", size=0.5) +
  theme(aspect.ratio=1) +
  xlab("n-2 outcome rating") +
  ylab("n expectation rating")
sp
```


```{r}
    trialorder_groupwise <- summarySEwithin(
        data = subjectwise_naomit_2dv,
        measurevar = "DV1_mean_per_sub",
        # betweenvars = "src_subject_id",
        withinvars = factor( "trial_index"),
         idvar = "src_subject_id"
    )
```


```{r}
    trialorder_groupwise <- summarySEwithin(
        data = subset(subjectwise_naomit_2dv, select = -c(src_subject_id)),
        measurevar = "DV1_mean_per_sub",
        # betweenvars = "src_subject_id",
        withinvars = as.factor( "trial_index")
         #idvar = "trial_index"
    )
```
```{r}
data_a3lag_omit$src_subject_id <- as.factor(data_a3lag_omit$src_subject_id)

lag.raw <- ggplot(aes(x=lag.04outcomeangle, y=event02_expect_angle), data=data_a3lag_omit) +
  geom_smooth(method='lm', se=F, size=0.75) +
  geom_point(size=0.1) + 
    geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", size=0.5) +
  facet_wrap(~src_subject_id) + 
  theme(legend.position='none') + 
  xlim(0,180) + ylim(0,180) +
  xlab("raw data from each participant: n-2 lagged outcome angle") + 
  ylab("n current expectation rating")
lag.raw +
  labs(title = paste(taskname, "- Is there a linear relationship between current expectation ratings and the previous outcome ratings?"),
       subtitle = "Plotting the raw data - with all of the datapoints ignoring run differences", 
       caption = "Blue = fitted linear slope per participant; Green: 1:1 slope")
lag.raw
```

```{r}
subjectwise_naomit_2dv$src_subject_id <- as.factor(subjectwise_naomit_2dv$src_subject_id)

lag.avg <- ggplot(aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub), data=subjectwise_naomit_2dv) +
  geom_smooth(method='lm', se=F, size=0.75) +
  geom_point(size=0.1) + 
    geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", size=0.5) +
  facet_wrap(~src_subject_id) + 
  theme(legend.position='none') + 
  xlim(0,180) + ylim(0,180) +
  xlab("raw data from each participant: n-2 lagged outcome angle") + 
  ylab("n current expectation rating") 

lag.avg +
  labs(title = paste(taskname, "- Is there a linear relationship between current expectation ratings and the previous outcome ratings?"),
       subtitle = "Observation notes: 1) The relationship is more of an attenuated one, where the higher outcome ratings lead to a slightly lower expectation rating, and a low outcome leads to a higher expectation rating, when considering a 1:1 relationship. This pattern could be explained by regression to the mean type mechanism, where participants are accounting for the fact that their previous experience was extreme on either ends and that this current trial will be under/over estimated. It probably will make sense to also see the relationship between current expectation ratings influencing current outcome ratings. ", 
       caption = "Blue = fitted linear slope per participant; Green: 1:1 slope")

```

```{r}
# https://gist.github.com/even4void/5074855
```

```{r}
ggplot(data_a3lag_omit, aes(y = event02_expect_angle, 
                       x = lag.04outcomeangle, 
                       colour = subject), size = .3, color = 'gray') + 
  geom_point(size = .1) + 
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .3) +
  theme_bw()
```


## Do these models differ as a function of cue?
### Additional analysis 01/23/2023 {.unlisted .unnumbered}
```{r}
model.lag_cue = lmer(event02_expect_angle ~ lag.04outcomeangle*param_cue_type + (1 | src_subject_id) + (1|session_id) , data = data_a3lag_omit)
summary(model.lag_cue)
```
```{r}
meanSummary_2dv <- function(DATA, GROUP, DV1, DV2) {
    z <- ddply(DATA, GROUP, .fun = function(xx) {
        c(
            DV1_mean_per_sub = mean(xx[, DV1], na.rm = TRUE),
            DV1_sd = sd(xx[, DV1], na.rm = TRUE),
            DV2_mean_per_sub = mean(xx[, DV2], na.rm = TRUE),
            DV2_sd = sd(xx[, DV1], na.rm = TRUE)
        )
    })
    return(z)
}
```

```{r}
subjectwise_cuetype = meanSummary_2dv(data_a3lag_omit,
        c("src_subject_id", "trial_index", "param_cue_type"), 
        "lag.04outcomeangle", "event02_expect_angle")
```

```{r}
subjectwise_cuetype_2dv <- na.omit(subjectwise_cuetype)
```

```{r}
subjectwise_cuetype$param_cue_type <- as.factor(subjectwise_cuetype$param_cue_type)
sp <- ggplot(data=subjectwise_cuetype, 
             aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub,
             color = param_cue_type)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", size=0.5) +
  geom_smooth(method = 'lm') +
  theme(aspect.ratio=1) +
  xlab("n-2 outcome rating") +
  ylab("n expectation rating")
sp +
    labs(title = paste(taskname, "- Does the linear relationship between current expectation ratings and the previous outcome ratings differ as a function of cue?"),
       subtitle = "Plotting the raw data - with all of the datapoints averaged across runs per 12 trials", 
       caption = "high cue vs low cue. The slope is significant, theree is not interaction; Green: 1:1 slope")
# plot(subjectwise_naomit_2dv$DV1_mean_per_sub, subjectwise_naomit_2dv$DV2_mean_per_sub) + lines(x = c(0,200), y = c(0,200))
```

## Let's demean the ratings.
bin ratings
Do the bins do their jobs?
plot one run
then check the min, max and see if the quantization is done properly.
YES, it is
```{r test_bin_12}
# per subject, session, run
#das$wt_2 <- as.numeric(cut_number(das$wt,3))
df_subset = subset(data_a3lag_omit, src_subject_id == 18 )
#df_subset$lag.04outcomeangle
min(df_subset$lag.04outcomeangle)
max(df_subset$lag.04outcomeangle)
range(df_subset$lag.04outcomeangle)
cut_interval(range(df_subset$lag.04outcomeangle), n = 5)
hist(df_subset$lag.04outcomeangle)
# hist(c(121.39691, 102.30392,  89.30972,  92.07837, 121.51694, 148.16579, 122.95297 ,126.36490 ,123.69007 , 51.34019,  36.86990))
df_subset$bin = cut_interval(df_subset$lag.04outcomeangle, n = 5)
df_subset$bin_num = as.numeric(cut_interval(df_subset$lag.04outcomeangle, n = 5))
# cut_interval(df_subset$lag.04outcomeangle, n = 6)
# as.numeric(cut_interval(df_subset$lag.04outcomeangle, n = 6))
# https://stackoverflow.com/questions/21714457/is-cut-style-binning-available-in-dplyr

  # mutate(lagoutcomebin = as.numeric(ggplot2::cut_interval(data_a3lag_omit$lag.04outcomeangle,5)))
  #group_by(src_subject_id, session_id, ) %>%
```

```{r}
df_discrete = data_a3lag_omit %>%
  group_by(src_subject_id) %>%
  mutate(bin = cut_interval(lag.04outcomeangle, n = 5),
         n_2outcomelevels = as.numeric(cut_interval(lag.04outcomeangle, n = 5)))

#, "session_id", "param_run_num"
# df_subset$bin = cut_interval(df_subset$lag.04outcomeangle, n = 5)
# df_subset$bin_num = as.numeric(cut_interval(df_subset$lag.04outcomeangle, n = 5))
```

confirm that df discrete has 5 levels per participant
the number of counts per frequency can differ 
```{r}
res <- df_discrete %>% 
  group_by(src_subject_id,n_2outcomelevels) %>% 
  tally()
```

```{r}
res
```


```{r}
pain_df  = df_discrete[df_discrete$param_task_name == "pain",]
ggplot(pain_df, aes(y = event02_expect_angle, 
                       x = n_2outcomelevels, 
                       colour = subject), size = .3, color = 'gray') + 
  geom_point(size = .1) + 
  # geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  geom_smooth(method = "gam") +
  theme_bw()
```


## DEMEAN AND THEN DISCRETIZE


```{r}

df_discrete = data_a3lag_omit %>%
  group_by(src_subject_id) %>%
  mutate(lag.04outcomeangle_demean = lag.04outcomeangle-mean(lag.04outcomeangle),
         event02_expect_angle_demean = event02_expect_angle-mean(event02_expect_angle)) %>%
  mutate(bin = cut_interval(lag.04outcomeangle_demean, n = 5),
         n_2outcomelevels = as.numeric(cut_interval(lag.04outcomeangle_demean, n = 5)))

#, "session_id", "param_run_num"
# df_subset$bin = cut_interval(df_subset$lag.04outcomeangle, n = 5)
# df_subset$bin_num = as.numeric(cut_interval(df_subset$lag.04outcomeangle, n = 5))
```

```{r}
res <- df_discrete %>% 
  group_by(src_subject_id,n_2outcomelevels) %>% 
  tally()
res
```

```{r}
pain_df  = df_discrete[df_discrete$param_task_name == "pain",]
ggplot(pain_df, aes(y = event02_expect_angle_demean, 
                       x = n_2outcomelevels, 
                       colour = subject), size = .3, color = 'gray') + 
  geom_point(size = .1) + 
  # geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  geom_smooth(method = "gam") +
  theme_bw()
```
```{r}
df_discrete$n_2outcomelevels_newlev = df_discrete$n_2outcomelevels -3
    subjectwise_bin_demean <- meanSummary(df_discrete, c(
        "subject","param_task_name","n_2outcomelevels" 
    ), "event02_expect_angle_demean")
subjectwise_bin_demean_naomit <- na.omit(subjectwise_bin_demean)
    groupwise_bin_demean <- summarySEwithin(
        data = subjectwise_bin_demean_naomit,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("n_2outcomelevels"), # iv
       idvar = "subject"
    )
subjectwise_bin_demean_naomit$n_2outcomelevels_newlev = as.numeric(subjectwise_bin_demean_naomit$n_2outcomelevels) -3
groupwise_bin_demean$n_2outcomelevels_newlev = as.numeric(groupwise_bin_demean$n_2outcomelevels) -3
```


```{r}
plot_halfrainclouds_sig <- function(subjectwise, groupwise, iv,sub_iv,
                                      subjectwise_mean, group_mean, se, subject,
                                      ggtitle, title, xlab, ylab, taskname, ylim,
                                      w, h, dv_keyword, color, save_fname) {
  g <- ggplot(
    data = subjectwise,
    aes(
      y = .data[[subjectwise_mean]],
      x = factor(.data[[iv]]),
      fill = factor(.data[[iv]])
    )
  ) +
    coord_cartesian(ylim = ylim, expand = TRUE) +

    geom_half_violin(
      aes(fill = factor(.data[[iv]])),
      side = 'r',
      #position = 'dodge',
      adjust = 0.5,
      trim = FALSE,
      alpha = .5,
      colour = NA
    ) +


    # geom_point(
    #   aes(
    #     x = as.numeric(.data[[iv]]) - .15,
    #     y = .data[[subjectwise_mean]],
    #     color = factor(.data[[iv]])
    #   ),
    #   position = position_jitter(width = .05),
    #   size = 1, alpha = 0.8, shape = 20
    # ) +

  # geom_line(data = subjectwise,
  #   aes(
  #     group = .data[[subject]],
  #     x = as.numeric(factor(.data[[iv]])) - .1 ,
  #     y = .data[[subjectwise_mean]],
  #     fill = factor(.data[[iv]])
  #     ),
  #   linetype = "solid",
  #   color = "grey",
  #   alpha = .3) +

  geom_point(
    aes(
      # group = .data[[subject]],
      x = as.numeric(factor(.data[[iv]])) - .1 ,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.7,
  ) + 
    # geom_boxplot(
    #   aes(
    #     x = .data[[iv]],
    #     y = .data[[subjectwise_mean]],
    #     fill = .data[[iv]]
    #   ),
    #   outlier.shape = NA, alpha = 0.8, width = .1, colour = "black"
    # ) +

    # geom_half_boxplot(
    #   data = subjectwise,
    #   aes(x = .data[[iv]],
    #       y = .data[[subjectwise_mean]],
    #       fill = .data[[iv]]),
    #   side = "r",
    #   outlier.shape = NA,
    #   alpha = 0.8,
    #   width = .05,
    #   notch = FALSE,
    #   notchwidth = 0,
    #   varwidth = FALSE,
    #   colour = "black",
    #   errorbar.draw = FALSE
    # ) +

    geom_errorbar(
      data = groupwise,
      aes(
        x = as.numeric(.data[[sub_iv]]) + .1 ,
        y = as.numeric(.data[[group_mean]]),
        color = factor(.data[[iv]]),
        ymin = .data[[group_mean]] - .data[[se]],
        ymax = .data[[group_mean]] + .data[[se]]
      ),
      position = position_dodge(width=0.1), width=0.1 ,   # position = 'dodge',
      alpha = 1
    ) +
geom_line(
  data = groupwise,
  aes(
    #group = .data[[subject]],
    group = 1,
    y = as.numeric(.data[[group_mean]]),
    x = as.numeric(.data[[sub_iv]]) + .1 ,
    # fill = factor(.data[[iv]])
  ),
  linetype = "solid", color = "#C97482", alpha = 1
) +

    # legend stuff ________________________________________________________ # nolint
    #expand_limits(x = 2.8) +
    #guides(fill = "none") +
    guides(color = "none") +
    guides(fill = guide_legend(title = title)) +
    scale_fill_manual(values = color) +
    scale_color_manual(values = color) +
    ggtitle(ggtitle) +
    xlab(xlab) +
    ylab(ylab) +
    theme_bw()
  ggsave(save_fname, width = w, height = h)
  return(g)
}

```

```{r}
df_discrete$n_2outcomelevels_newlev = as.factor(df_discrete$n_2outcomelevels_newlev)
g <-
  plot_halfrainclouds_sig(
    subjectwise_bin_demean_naomit,
    groupwise_bin_demean,
    iv = "n_2outcomelevels_newlev",
    sub_iv = "n_2outcomelevels",
    subjectwise_mean = "mean_per_sub",
    group_mean = "mean_per_sub_norm_mean",
    se = "se",
    subject = "subject",
    ggtitle = "Do we see a sigmoidal pattern in the pain task?\nPrevious outcome ratings predict expectation ratings",
    title = "levels of (N-2) outcome ratings",
    xlab = "outcome ratings (N-2)",
    ylab = "expectation ratings (N)",
    taskname = "pain",
    ylim = c(-40, 40),
    w = 3,
    h = 5,
    dv_keyword = "sigmoidal",
    color = c(
      '#ad2831',
      "#800e13",
      "#640d14",
      "#38040e",
      "#250902",
      "#250902"
    ),
    save_fname = "~/Download/TEST_n-2.png"
  )
g
```
https://groups.google.com/g/ggplot2/c/csPNfSLKkco

```{r}
g +    geom_errorbar(
      data = groupwise_bin_demean,
      aes(
        x = as.numeric("n_2outcomelevels_newlev")  ,
        y = as.numeric("mean_per_sub_norm_mean"),
        #colour = as.numeric("n_2outcomelevels_newlev"),
        ymin = mean_per_sub_norm_mean - se,
        ymax = mean_per_sub_norm_mean + se
      ), width = .1    ) 
g
```

