# RL :: simulation {#RLsimulation}

## What is the purpose of this notebook? {.unlisted .unnumbered}

- Here, Aryan simulated behavioral outcome ratings using a reinforcement learning model.
- TODO: link this notebook with Aryan's matlab script. In other words, which code generated `data/simulated/0409/table_exp.csv`?

```{r include=FALSE}
library(tidyr)
library(dplyr)
library(plyr)
library(ggpubr)
library(r2mlm)
library(cueR)
```

## function

```{r include=FALSE}
# summarize dataframe __________________________________________________________
plot_twovariable <- function(df, iv1, iv2, group, subject, xmin, xmax, ymin,ymax,
xlab, ylab, ggtitle, color_scheme, alpha, fit_lm, lm_method = NULL, identity_line=TRUE, size=NULL) {
    # x: iv1 e.g. expect rating
    # y: iv2 e.g. outcome rating
    # group: param_cue_type
    # subject: src_subject_id
    # xlab("expect rating") +
    # ylab("outcome rating") +
    # color_scheme = c("high_cue" = "#000000",low_cue" = "#BBBBBB"        )
    library(ggplot2)

    df_dropna <- df[!is.na(df[, iv1]) & !is.na(df[, iv2]), ]
    subjectwise_naomit_2dv <- meanSummary_2continuous(
        df_dropna,
        c(subject, group),
        iv1, iv2
    )
    # subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
    subjectwise_naomit_2dv[ , group] <- as.factor(subjectwise_naomit_2dv[, group])
    # plot _________________________________________________________________________ #nolint

    g <- ggplot(
        data = subjectwise_naomit_2dv,
        aes(
            x = .data[["DV1_mean_per_sub"]],
            y = .data[["DV2_mean_per_sub"]],
            color = .data[[group]],
            size = size
        )
    ) +
        geom_point(
            aes(shape = .data[[group]],
            color = .data[[group]]),
            size = 2,
            alpha = alpha) +

        theme(aspect.ratio = 1) +
        scale_color_manual(values = color_scheme) +
        scale_shape_manual(values = c(16, 3)) +
        xlab(xlab) +
        ylab(ylab) +
        ylim(ymin,ymax) +
        xlim(xmin,xmax) +
        ggtitle(ggtitle) +
        theme(
            axis.line = element_line(colour = "grey50"),
            panel.background = element_blank(),
            plot.subtitle = ggtext::element_textbox_simple(size = 11)
        )


    if (isTRUE(fit_lm)) {
        g <- g +
        # geom_ribbon(stat = "smooth", method = lm_method, se = FALSE, alpha = 0.1,
        #       aes(color = NULL, group = factor(group))) +
        geom_line(stat = "smooth", method = lm_method, se = FALSE, alpha = 0.8, linewidth = 1.5)
    } else {
        g
    }

    if (isTRUE(identity_line)) {
        g <- g + geom_abline(
            intercept = 0, slope = 1, color = "#373737", # color = "green"
            linetype = "dashed",
            linewidth = .5
        )
    } else {
        g
    }
    return(g)
}

```

```{r include=FALSE}
main_dir = dirname(dirname(getwd()))
expect_fname = file.path(main_dir, 'data/simulated/0409/table_exp.csv')
outcome_fname = file.path(main_dir, 'data/simulated/0409/table_pain.csv')
expect = read.csv(expect_fname)
outcome = read.csv(outcome_fname)

head(expect)
head(outcome)
```

```{r include=FALSE}
# tidy the dataframes by renaming "expect" _____________________________________
expect$sub <- rep(1:250, each = 2)
expect_long <- expect %>%
  pivot_longer(
    cols = c("mean_ExpL_Subj_N1", "mean_ExpL_Subj_N2", "mean_ExpL_Subj_N3",
              "mean_ExpH_Subj_N1", "mean_ExpH_Subj_N2", "mean_ExpH_Subj_N3"),
    names_to = c("cue_level", "noxious"),  # split column names into Exp and Subj columns
    names_pattern = "mean_(Exp.*)_Subj_N(.*)"  # use regular expression to extract Exp and Subj values
  )
E.df <- expect_long %>%
  mutate(
    stimulusintensity = case_when(
      noxious == 1 ~ "low_stim",
      noxious == 2 ~ "med_stim",
      noxious == 3 ~ "high_stim",
    ),
    cue = case_when(
      cue_level == "ExpH" ~ "high_cue",
      cue_level == "ExpL" ~ "low_cue"
    )
    )
E.df$expectation <- E.df$value

# outcome ______________________________________________________________________
outcome$sub <- rep(1:250, each = 2) #1:nrow(outcome)
outcome_long <- outcome %>%
  pivot_longer(
    cols = c("mean_PainL_Subj_N1", "mean_PainL_Subj_N2", "mean_PainL_Subj_N3",
              "mean_PainH_Subj_N1", "mean_PainH_Subj_N2", "mean_PainH_Subj_N3"),
    names_to = c("cue_level", "noxious"),  # split column names into Exp and Subj columns
    names_pattern = "mean_(Pain.*)_Subj_N(.*)"  # use regular expression to extract Exp and Subj values
  )
O.df <- outcome_long %>%
  mutate(
    stimulusintensity = case_when(
      noxious == 1 ~ "low_stim",
      noxious == 2 ~ "med_stim",
      noxious == 3 ~ "high_stim",
    ),
    cue = case_when(
      cue_level == "PainH" ~ "high_cue",
      cue_level == "PainL" ~ "low_cue"
    )
    )
O.df$outcome <- O.df$value
```

```{r include=FALSE}
merged_df <- merge(E.df, O.df, by = c("sub", "cue", "stimulusintensity"))
merge.df <- data.frame(merged_df)
```

## plot expectation and outcome ratings per cue X stim {.unlisted .unnumbered}

> Here, I plot the simulated values as a function of expectation and outcome rating
> Different stimulus intensities and cue levels are plotted.
> The simulated data does mimic the behavioral data in terms of the demeaned outcome/expectation ratings.

```{r}
group <- "cue"

iv1 <- "demean_expect"
iv2 <- "demean_outcome"

subject <- "sub"
xmin <- 48;xmax <- 50
ymin <- 48;ymax <- 50
xlab <- "expectation rating"
ylab <- "outcome rating"
ggtitle <- "all stimulus intensity"
color_scheme <- c("high_cue" = "#941100", "low_cue" =  "#5D5C5C")
alpha <- .8
fit_lm <- TRUE
lm_method <- "lm"
identity_line <- TRUE
size <- NULL
g <- ggplot(data = merged_df,
            aes(
              x = .data[["expectation"]],
              y = .data[["outcome"]],
              color = .data[[group]],
              size = size
            )) +
  geom_point(aes(shape = .data[[group]],
                 color = .data[[group]]),
             size = 2,
             alpha = alpha) +
  theme(aspect.ratio = 1) +
  scale_color_manual(values = color_scheme) +
  scale_shape_manual(values = c(16, 3)) +
  xlab(xlab) +
  ylab(ylab) +
  ylim(ymin, ymax) +
  xlim(xmin, xmax) +
  ggtitle(ggtitle) +
  theme(
    axis.line = element_line(colour = "grey50"),
    panel.background = element_blank(),
    plot.subtitle = ggtext::element_textbox_simple(size = 11)
  )


if (isTRUE(fit_lm)) {
  g <- g +
    geom_line(
      stat = "smooth",
      method = lm_method,
      se = FALSE,
      alpha = 0.8,
      linewidth = 1.5
    )
} else {
  g
}

if (isTRUE(identity_line)) {
  g <- g + geom_abline(
    intercept = 0,
    slope = 1,
    color = "#373737",
    # color = "green"
    linetype = "dashed",
    linewidth = .5
  )
} else {
  g
}
g
```

> The curvature resembles the demeaned ratings that we observed.

## plot expectation and outcome, collapsing across all stimulus intesnity

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
clean.df <- merge.df[,c("sub", "cue", "stimulusintensity", "expectation", "outcome")]
total <-
  plot_twovariable(
    clean.df,
    iv1 = "expectation",
    iv2 = "outcome",
    group = "cue",
    subject = "sub",
    xmin=48, xmax=50, ymin=48, ymax=50,
    xlab = "expectation rating",
    ylab = "outcome rating",
    ggtitle = "all stimulus intensity",
    color_scheme = c("high_cue" ="#941100","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE, lm_method = "lm", identity_line=TRUE, size=NULL
  )
total
```

> Given both ratings are demeaned, the intercept is the mean of the intensity ratings (49 C).

## Plot Outcome as a function of stim X cue X Expectation rating

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

iv1 = "expectation";    iv2 = "outcome"
# low stimulus intensity _______________________________________________________
df_low = clean.df[clean.df$stimulusintensity == "low_stim", ]
low <-
  plot_twovariable(
    df_low, iv1, iv2,
    group = "cue", subject = "sub",
    # xmin=47.5, xmax=50.5, ymin=47.5, ymax=50.5,
    xmin=48, xmax=50, ymin=48, ymax=50,
    xlab = "Simulated\nexpectation rating", ylab = "Simulated\noutcome rating",
    ggtitle = "Low intensity",
    color_scheme = c("high_cue" ="#C506FF","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = FALSE, lm_method = "lm", identity_line=FALSE, size=NULL
  )

# med stimulus intensity _______________________________________________________
df_med <- clean.df[clean.df$stimulusintensity == "med_stim", ]
med <-
  plot_twovariable(
    df_med, iv1, iv2,
    group = "cue", subject = "sub",
    # xmin=47.5, xmax=50.5, ymin=47.5, ymax=50.5,
    xmin=48, xmax=50, ymin=48, ymax=50,
    xlab = "Simulated\nexpectation rating", ylab = " \n ",
    ggtitle = "Medium intensity",
    color_scheme = c("high_cue" ="#9118DD","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = FALSE, lm_method = "lm", identity_line=FALSE, size=NULL
  )

# high stimulus intensity _______________________________________________________
df_high = clean.df[clean.df$stimulusintensity == "high_stim", ]
high <-
  plot_twovariable(
    df_high, iv1, iv2,
    group = "cue", subject = "sub",
    # xmin=47.5, xmax=50.5, ymin=47.5, ymax=50.5,
    xmin=48, xmax=50, ymin=48, ymax=50,
    xlab = "Simulated\nexpectation rating", ylab = " \n ",
    ggtitle = "High intensity",
    color_scheme = c("high_cue" ="#5C29BA","low_cue" =  "#5D5C5C"),
    alpha = .5, fit_lm = FALSE, lm_method = "lm", identity_line=FALSE, size=NULL
  )

# combine plots ________________________________________________________________
low <- low + theme(text = element_text(size = 13)) + theme(aspect.ratio=1)+ scale_x_continuous(breaks = seq(48, 50))
med <- med + theme(text = element_text(size = 13)) + theme(aspect.ratio=1) + scale_x_continuous(breaks = seq(48, 50))
high <- high + theme(text = element_text(size = 13)) + theme(aspect.ratio=1) +scale_x_continuous(breaks = seq(48, 50))

plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob("individual differences\n - cue effects from outcome ratings", color = "black", face = "bold", size = 15))
plots

# ggsave(file.path(main_dir, 'analysis/mixedeffect/CCNfigures/figD.png'), plots)
```

### plot cue and stim using line plots

> The cue and stim effects are signficiant, but the mid range is different. The behavioral data shows that the medium intensity has smaller cue effects compared to the high and low cues, whereas the current simulations show the opposite trend. Not sure if we should read too much into this.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
clean.df$stim_name[clean.df$stimulusintensity == "low_stim"] <- "low"
clean.df$stim_name[clean.df$stimulusintensity == "med_stim"] <- "med"
clean.df$stim_name[clean.df$stimulusintensity == "high_stim"] <- "high"

clean.df$stim_ordered <- factor(
        clean.df$stim_name,
        levels = c("low", "med", "high")
    )

clean.df$cue_name[clean.df$cue == "low_cue"] <- "low"
clean.df$cue_name[clean.df$cue == "high_cue"] <- "high"

clean.df$cue_ordered <- factor(
        clean.df$cue_name,
        levels = c("low", "high")
    )
# DATA = as.data.frame(combined_se_calc_cooksd)
color <- c( "#4575B4", "#D73027")
iv1 <- "stim_ordered"
iv2 <- "cue_ordered"
xlab <- "Stimulus Intensity"
ylab <- "Outcome Rating"
dv <- "outcome"
mean <- "mean_per_sub_norm_mean"
error <- "ci"
dv_keyword <- "outcome"

actual_subjectwise <- meanSummary(clean.df,
                                  c(subject, iv1, iv2), dv)
actual_groupwise <- summarySEwithin(
  data = actual_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(iv1, iv2),
  idvar = subject
)

# plot lineplot ________________________________________________________________

DATA = as.data.frame(actual_groupwise)
color = c( "#4575B4", "#D73027")
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "ci"
dv_keyword = "outcome"
actual_groupwise$taskname <- "pain"
p1 <- plot_lineplot_twofactor_subset(actual_groupwise, 'pain',
               LINEIV1, LINEIV2, MEAN, ERROR, color, ggtitle = tools::toTitleCase('pain') )
p1


```

> The cue and stim effects are signficiant, but the mid range is different. The behaviorla data shows that the medium intensity has smaller cue effects compared to the high and low cues, whereas the current simulations show the opposite trend. Not sure if we should read too much into this.
