# [beh] RL simulation Aryan {#ch18_simulation_aryan}



## What is the purpose of this notebook? {.unlisted .unnumbered}
* Here, I model Aryans model fitted results, using the same scheme as my behavioral analysis (15*.Rmd)


```{r load_libraries_5, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
# library(lmSupport)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(stats)
library(ggpubr)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lme4)
library(effectsize)
library(brms)
library(devtools)
library(visibly) # 
library(plotly) #plot
library(scico) # plot
# source("https://gist.github.com/benmarwick/2a1bb0133ff568cbe28d/geom_flat_violin.R")

library(r2mlm)
main_dir = dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, "scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

## load data {.unlisted .unnumbered}

```{r load_data_and_exclude_m1, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "pain"
ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"

# load data _____________________________________
main_dir = dirname(dirname(getwd()))
data <- read.csv(file.path(main_dir, 'data/simulated/model_ver04_0508/table_pain_new.csv'))
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model19_RLsimulationplot", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```




```{r function::simple_contrasts_beh, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
simple_contrasts_beh <- function(df) {
#factorize stimulus type ________________________________________
df$stim_factor <- factor(df$param_stimulus_type)

# contrast code 1 linear
df$stim_con_linear[df$param_stimulus_type == "low_stim"] <-  -0.5
df$stim_con_linear[df$param_stimulus_type == "med_stim"] <-  0
df$stim_con_linear[df$param_stimulus_type == "high_stim"] <-  0.5

# contrast code 2 quadratic
df$stim_con_quad[df$param_stimulus_type == "low_stim"] <-  -0.33
df$stim_con_quad[df$param_stimulus_type == "med_stim"] <-  0.66
df$stim_con_quad[df$param_stimulus_type == "high_stim"] <-  -0.33

# cue contrast
df$CUE_high_gt_low[df$param_cue_type == "low_cue"] <-  -0.5 # social influence task
df$CUE_high_gt_low[df$param_cue_type == "high_cue"] <-  0.5 # no influence task

df$stim_ordered <- factor(
        df$param_stimulus_type,
        levels = c("low_stim", "med_stim", "high_stim")
    )

df$cue_name[df$param_cue_type == "low_cue"] <- "low"
df$cue_name[df$param_cue_type == "high_cue"] <- "high"

df$cue_ordered <- factor(
        df$cue_name,
        levels = c("low", "high")
    )
return(df)
}
```

## Plot the relationship between expectation and outcome rating using model 4 simulations (Jepma)
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# convert column names
data$event04_actual_angle <- data$Pain_mdl4
data$event02_expect_angle <- data$Exp_mdl4

# demean data
maindata <- data %>%
  group_by(src_subject_id) %>%
    mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
    mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
    mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
    mutate(demean_outcome = event04_actual_angle - avg_outcome) %>%
    mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
    mutate(demean_expect = event02_expect_angle - avg_expect)

# assign trial numbers
data_p2 <- maindata %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())

data_a3 <- data_p2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

# calculate lag score (N-1 outcome score_)
data_a3lag <- 
    data_a3 %>%
    group_by(src_subject_id, session_id, param_run_num) %>%
    mutate(lag.demean_outcome = dplyr::lag(demean_outcome, n = 1, default = NA))

# calculate subject level average score
data_a3lag <- data_a3lag %>%
  mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) 
data_a3lag_omit <- data_a3lag[complete.cases(data_a3lag$lag.demean_outcome),]

# compute contrasts
df <- data_a3lag_omit
pvc <- simple_contrasts_beh(df)
```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# plot expectation and outcome rating
df_dropna <-
  pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
total <-
  plot_twovariable(
    df_dropna,
    iv1 = "demean_expect",
    iv2 = "demean_outcome",
    group = "param_cue_type",
    subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating",
    ylab = "outcome rating", 
    ggtitle = "all stimulus intensity", 
    color_scheme = c("high_cue" ="#941100","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE, lm_method = "lm", identity_line = TRUE
  )
total
```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# only keep rows that both have expectation and outcome ratings
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_low = df_dropna[df_dropna$param_stimulus_type == "low_stim", ]
low <-
  plot_twovariable(
    df_low, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "Low intensity",
    color_scheme = c("high_cue" ="#FF8800","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE, lm_method = "lm", identity_line = TRUE
  )
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_med = df_dropna[df_dropna$param_stimulus_type == "med_stim", ]
med <-
  plot_twovariable(
    df_med, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "Medium intensity",
    color_scheme = c("high_cue" ="#DB6000","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE, lm_method = "lm", identity_line = TRUE
  )
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_high = df_dropna[df_dropna$param_stimulus_type == "high_stim", ]
high <-
  plot_twovariable(
    df_high, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "High intensity",
    color_scheme = c("high_cue" ="#941100","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE, lm_method = "lm", identity_line = TRUE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob("model fitted data\n - predicted data from Aryan", color = "black", face = "bold", size = 15))
plots_title
```

## Plot the relationship between expectation and outcome rating using model 2 simulations (Jepma)

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

data$event04_actual_angle <- data$Pain_mdl2
data$event02_expect_angle <- data$Exp_mdl2
maindata <- data %>%
group_by(src_subject_id) %>%
mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
mutate(demean_outcome = event04_actual_angle - avg_outcome) %>%
mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
mutate(demean_expect = event02_expect_angle - avg_expect)

data_p2= maindata %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_a3 <- data_p2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

data_a3lag <- 
    data_a3 %>%
    group_by(src_subject_id, session_id, param_run_num) %>%
    mutate(lag.demean_outcome = dplyr::lag(demean_outcome, n = 1, default = NA))
data_a3lag <- data_a3lag %>%
  mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) 
data_a3lag_omit <- data_a3lag[complete.cases(data_a3lag$lag.demean_outcome),]

df <- data_a3lag_omit
pvc <- simple_contrasts_beh(df)
```


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
df_dropna <-
  pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
total <-
  plot_twovariable(
    df_dropna,
    iv1 = "demean_expect",
    iv2 = "demean_outcome",
    group = "param_cue_type",
    subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating",
    ylab = "outcome rating", 
    ggtitle = "all stimulus intensity", 
    color_scheme = c("high_cue" ="#941100","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE, lm_method = "lm", identity_line = TRUE
  )
total
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_low = df_dropna[df_dropna$param_stimulus_type == "low_stim", ]
low <-
  plot_twovariable(
    df_low, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "Low intensity",
    color_scheme = c("high_cue" ="#FF8800","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE, lm_method = "lm", identity_line = TRUE
  )
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_med = df_dropna[df_dropna$param_stimulus_type == "med_stim", ]
med <-
  plot_twovariable(
    df_med, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "Medium intensity",
    color_scheme = c("high_cue" ="#DB6000","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE, lm_method = "lm", identity_line = TRUE
  )
df_dropna <- pvc[!is.na(pvc$demean_expect) & !is.na(pvc$demean_outcome),]
df_high = df_dropna[df_dropna$param_stimulus_type == "high_stim", ]
high <-
  plot_twovariable(
    df_high, iv1 = "demean_expect", iv2 = "demean_outcome",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "expectation rating", ylab = "outcome rating",
    ggtitle = "High intensity",
    color_scheme = c("high_cue" ="#941100","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE, lm_method = "lm", identity_line = TRUE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob("model fitted data Jepma version\n - predicted data from Aryan", color = "black", face = "bold", size = 15))
plots_title
```


### model fits from model 2. expectation ratings (Jepma model)
```{r}
main_dir = dirname(dirname(getwd()))
data <- read.csv(file.path(main_dir, 'data/simulated/model_ver04_0508/table_pain_new.csv'))
subjectwise_2dv <- meanSummary_2dv(data, c("src_subject_id"), 
                                   "event02_expect_angle", "Exp_mdl2" )
ggplot(data = subjectwise_2dv, 
       aes(x = .data[["DV1_mean_per_sub"]], 
           y = .data[["DV2_mean_per_sub"]],
           size = .5
           )) +
  geom_point(size = 2, alpha = .5  ) + 
  ylim(0,180) + 
  xlim(0,180) +
  coord_fixed() +
  geom_abline(intercept = 0, slope = 1, color = "#373737", linetype = "dashed", linewidth = .5) + 
  xlab("Observed\nexpectation rating") + 
  ylab("Model-fitted \nexpectation rating")+
  theme(
    axis.line = element_line(colour = "grey50"),
    panel.background = element_blank(),
    plot.subtitle = ggtext::element_textbox_simple(size = 1), 
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 15),
    axis.title.y = element_text(size = 15)
      
  )
```

### model fits from model 2. outcome ratings (Jepma model)
```{r}
subjectwise_2dv <- meanSummary_2dv(data, c("src_subject_id"), 
                                   "event04_actual_angle", "Pain_mdl2" )
ggplot(data = subjectwise_2dv, 
       aes(x = .data[["DV1_mean_per_sub"]], 
           y = .data[["DV2_mean_per_sub"]],
           size = .5
           )) +
  geom_point(size = 2, alpha = .5  ) + 
  ylim(0,180) + 
  xlim(0,180) +
  coord_fixed() +
  geom_abline(intercept = 0, slope = 1, color = "#373737", linetype = "dashed", linewidth = .5) + 
  xlab("Observed\noutcome rating") + 
  ylab("Model-fitted \noutcome rating")+
  theme(
    axis.line = element_line(colour = "grey50"),
    panel.background = element_blank(),
    plot.subtitle = ggtext::element_textbox_simple(size = 1), 
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20)
      
  )
```

## correlation betweeen alpha_incongruent and cue trial slope (randome effects of cue)
```{r echo=FALSE}
# load dataframe
cue_trial <- data.frame(read.csv(file.path(main_dir, 'data/RL/cue_trial_ranef_pain.csv')))
# grab alpha_incongruent
model_param <- data.frame(read.csv(file.path(main_dir, "data/RL/modelfit_jepma_0525/par_mdl2_pain.csv")))
# grab cue slope
# Perform inner join merge on common columns
merged_df <- merge(cue_trial, model_param, by.x = "sub", by.y = "subj_num_new_pain", all = FALSE)
# Filter the rows in the first data frame based on the intersection
# plot ggplot
# run lmer
merged_df$alpha_c_gt_i <- merged_df$alpha_c - merged_df$alpha_i
merged_2dv <- meanSummary_2dv(merged_df, c("sub"), 
                                   "cue_randomslope", "pain_err" )
ggplot(data = merged_df, 
       aes(x = .data[["cue_randomslope"]], 
           y = .data[["alpha_c_gt_i"]],
           size = .5
           )) +
  geom_point(size = 2, alpha = .5  ) + 
  ylim(-10,10) + 
  xlim(-10,10) +
  coord_fixed() +
  geom_abline(intercept = 0, slope = 1, color = "#373737", linetype = "dashed", linewidth = .5) + 
  xlab("Cue random slopes") + 
  ylab("Alpha \n(congruent > incongruent)")+
  theme(
    axis.line = element_line(colour = "grey50"),
    panel.background = element_blank(),
    plot.subtitle = ggtext::element_textbox_simple(size = 1), 
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20)
      
  )
```
```{r echo=FALSE}
# load dataframe
cue_trial <- data.frame(read.csv(file.path(main_dir, 'data/RL/cue_trial_ranef_vicarious.csv')))
# grab alpha_incongruent
model_param <- data.frame(read.csv(file.path(main_dir, "data/RL/modelfit_jepma_0525/par_mdl2_vic.csv")))
# grab cue slope
# Perform inner join merge on common columns
merged_df <- merge(cue_trial, model_param, by.x = "sub", by.y = "subj_num_new_vicarious", all = FALSE)
# Filter the rows in the first data frame based on the intersection
# plot ggplot
# run lmer
merged_df$alpha_c_gt_i <- merged_df$alpha_c - merged_df$alpha_i
merged_2dv <- meanSummary_2dv(merged_df, c("sub"), 
                                   "cue_randomslope", "pain_err" )
ggplot(data = merged_df, 
       aes(x = .data[["cue_randomslope"]], 
           y = .data[["alpha_c_gt_i"]],
           size = .5
           )) +
  geom_point(size = 2, alpha = .5  ) + 
  ylim(-10,10) + 
  xlim(-10,10) +
  coord_fixed() +
  geom_abline(intercept = 0, slope = 1, color = "#373737", linetype = "dashed", linewidth = .5) + 
  xlab("Cue random slopes") + 
  ylab("Alpha \n(congruent > incongruent)")+
  theme(
    axis.line = element_line(colour = "grey50"),
    panel.background = element_blank(),
    plot.subtitle = ggtext::element_textbox_simple(size = 1), 
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20)
      
  )
```

```{r echo=FALSE}
# load dataframe
cue_trial <- data.frame(read.csv(file.path(main_dir, 'data/RL/cue_trial_ranef_cognitive.csv')))
# grab alpha_incongruent
model_param <- data.frame(read.csv(file.path(main_dir, "data/RL/modelfit_jepma_0525/par_mdl2_cog.csv")))
# grab cue slope
# Perform inner join merge on common columns
merged_df <- merge(cue_trial, model_param, by.x = "sub", by.y = "subj_num_new_cognitive", all = FALSE)
# Filter the rows in the first data frame based on the intersection
# plot ggplot
# run lmer
merged_df$alpha_c_gt_i <- merged_df$alpha_c - merged_df$alpha_i
merged_2dv <- meanSummary_2dv(merged_df, c("sub"), 
                                   "cue_randomslope", "pain_err" )
ggplot(data = merged_df, 
       aes(x = .data[["cue_randomslope"]], 
           y = .data[["alpha_c_gt_i"]],
           size = .5
           )) +
  geom_point(size = 2, alpha = .5  ) + 
  ylim(-10,10) + 
  xlim(-10,10) +
  coord_fixed() +
  geom_abline(intercept = 0, slope = 1, color = "#373737", linetype = "dashed", linewidth = .5) + 
  xlab("Cue random slopes") + 
  ylab("Alpha \n(congruent > incongruent)")+
  theme(
    axis.line = element_line(colour = "grey50"),
    panel.background = element_blank(),
    plot.subtitle = ggtext::element_textbox_simple(size = 1), 
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20)
      
  )
```


## correlation betweeen alpha_incongruent and NPS
```{r}
# load dataframe
NPS <- data.frame(read.csv(file.path(main_dir, 'data/NPS_curated.csv')))
NPS <- NPS %>%
  mutate(congruency = case_when(
    cuetype == "cuetype-low" & stimintensity == "low" ~ "congruent",
    cuetype == "cuetype-high" & stimintensity == "high" ~ "congruent",
    cuetype == "cuetype-low" & stimintensity == "high" ~ "incongruent",
    cuetype == "cuetype-high" & stimintensity == "low" ~ "incongruent",
    TRUE ~ "other"
  ))
NPS_congru <- NPS %>%
  group_by(sub) %>%
  summarise(avg_diff = mean(NPSpos[congruency == "congruent"]) - mean(NPSpos[congruency == "incongruent"]))

# grab alpha_incongruent
model_param <- data.frame(read.csv(file.path(main_dir, "data/RL/modelfit_jepma_0525/par_mdl2_pain.csv")))

model_param <- model_param %>%
  mutate(sub = sprintf("sub-%04d", subj_num_new_pain))

# Merge the two dataframes based on the "sub" column
merged_NPS <- merge(NPS_congru, model_param, by = "sub")
merged_NPS$alpha_c_gt_i <- merged_NPS$alpha_c - merged_NPS$alpha_i
# grab cue slope
# grab intersection of subject ids
# plot ggplot
ggplot(data = merged_NPS, 
       aes(x = .data[["avg_diff"]], 
           y = .data[["alpha_c_gt_i"]],
           size = .5
           )) +
  geom_point(size = 2, alpha = .5  ) + 
  ylim(-10,10) + 
  xlim(-10,10) +
  coord_fixed() +
  geom_abline(intercept = 0, slope = 1, color = "#373737", linetype = "dashed", linewidth = .5) + 
  xlab("NPS \n(congruent > incongruent)") + 
  ylab("Alpha \n(congruent > incongruent)")+
  theme(
    axis.line = element_line(colour = "grey50"),
    panel.background = element_blank(),
    plot.subtitle = ggtext::element_textbox_simple(size = 1), 
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20)
      
  )
# run lmer

```

## correlation bettween NPS and PE

### test similarity between NPS positive values and PE (11/06/2023)

```{r}
PEdf <- read.csv(file.path(main_dir, 'data/RL/modelfit_jepma_0525/table_pain.csv'))
NPS <- data.frame(read.csv(file.path(main_dir, 'data/NPS_curated.csv')))

PEdf <- PEdf %>%
  mutate(sub = sprintf("sub-%04d", src_subject_id),
         ses = sprintf("ses-%02d", session_id),
         run = sprintf("run-%02d", param_run_num),
         trial = sprintf("trial-%03d", trial_index_runwise-1)
         )
merged_NPSpe <- merge(NPS, PEdf, by = c("sub", "ses", "run", "trial"))


subjectwise_2dv <- meanSummary_2dv(merged_NPSpe, c("src_subject_id","stimintensity", "cuetype"), 
                                   "PE_mdl2", "NPSpos" )
ggplot(data = subjectwise_2dv, 
       aes(x = .data[["DV1_mean_per_sub"]], 
           y = .data[["DV2_mean_per_sub"]],
           color = .data[["cuetype"]],
           # shape = .data[["stimintensity"]],
           # size = .5
           )) +
  geom_point(size = 2, alpha = .5  ) + 
  ylim(-50,50) + 
  xlim(-50,50) +
  coord_fixed() +
  scale_color_manual(values = c("cuetype-high" ="red","cuetype-low" =  "#5D5C5C"))+
  geom_abline(intercept = 0, slope = 1, color = "#373737", linetype = "dashed", linewidth = .5) + 
  xlab("PE") + 
  ylab("NPSpos")+
  theme(
    axis.line = element_line(colour = "grey50"),
    panel.background = element_blank(),
    plot.subtitle = ggtext::element_textbox_simple(size = 1), 
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20)
      
  )
```


```{r}
model.25 <- lmer(merged_NPSpe$NPSpos ~ merged_NPSpe$PE_mdl2 + (1|sub), data = merged_NPSpe)
summary(model.25)
```

### test relationship between PE and cue type and stimintensity (06/16/2023)
```{r}
model.PENPS <- lmer(NPSpos ~ PE_mdl2*cuetype*stimintensity + (1|sub), data = merged_NPSpe)
summary(model.PENPS)
```

### plot the relationship between PE and NPS as a function of cue
```{r}
ggplot(data = merged_NPSpe, 
       aes(x = .data[["PE_mdl2"]], 
           y = .data[["NPSpos"]],
           color = .data[["cuetype"]],
           size = .5
           )) +
  geom_point(size = 2, alpha = .5  ) + 
  ylim(-150,150) + 
  xlim(-150,150) +
  coord_fixed() +
  scale_color_manual(values = c("cuetype-high" ="red","cuetype-low" =  "#5D5C5C"))+
  geom_abline(intercept = 0, slope = 1, color = "#373737", linetype = "dashed", linewidth = .5) + 
  xlab("PE") + 
  ylab("NPSpos")+
  theme(
    axis.line = element_line(colour = "grey50"),
    panel.background = element_blank(),
    plot.subtitle = ggtext::element_textbox_simple(size = 1), 
    axis.text.x = element_text(size = 15),
    axis.text.y = element_text(size = 15),
    axis.title.x = element_text(size = 20),
    axis.title.y = element_text(size = 20)
      
  )
```

### plot the relationship between PE and NPS as a function of cue and stimulus intensity
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

df_low = merged_NPSpe[merged_NPSpe$stimintensity == "low", ]
low <-
  plot_twovariable(
    df_low, iv1 = "PE_mdl2", iv2 = "NPSpos",
    group = "param_cue_type", subject = "sub",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "PE", ylab = "NPSpos",
    ggtitle = "Low intensity",
    color_scheme = c("high_cue" ="#FF8800","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE, lm_method = "lm", identity_line = TRUE
  )

df_med = merged_NPSpe[merged_NPSpe$stimintensity == "med", ]
med <-
  plot_twovariable(
    df_med, iv1 = "PE_mdl2", iv2 = "NPSpos",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "PE", ylab = "NPSpos",
    ggtitle = "Medium intensity",
    color_scheme = c("high_cue" ="#DB6000","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE, lm_method = "lm", identity_line = TRUE
  )
df_high = merged_NPSpe[merged_NPSpe$stimintensity == "high", ]
high <-
  plot_twovariable(
    df_high, iv1 = "PE_mdl2", iv2 = "NPSpos",
    group = "param_cue_type", subject = "src_subject_id",
    xmin=-50, xmax=50, ymin=-50, ymax=50,
    xlab = "PE", ylab = "NPSpos",
    ggtitle = "High intensity",
    color_scheme = c("high_cue" ="#941100","low_cue" =  "#5D5C5C"),
    alpha = .8, fit_lm = TRUE, lm_method = "lm", identity_line = TRUE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob("individual differences\n - cue effects from outcome ratings", color = "black", face = "bold", size = 15))
plots
```
