# [model] NPSsimulation {#ch20_npssimulation}


```{r include=FALSE}
library(car)
library(psych)
library(reshape)
library(dplyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(plyr)
library(ggpubr)
library(r2mlm)
library(effectsize)
library(devtools)
options(es.use_symbols = TRUE) # get nice symbols when printing! (On Windows, requires R >= 4.2.0)
library(EMAtools)
library(emmeans)
library(equatiomatic)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(DT)
library(raincloudplots)
devtools::source_url("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(r2mlm)
main_dir <- dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```

### Function

```{r function::simple_contrasts_singletrial, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
simple_contrasts_singletrial <- function(df) {
# [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
df$STIM <- factor(df$stim)

# contrast code 1 linear
df$STIM_linear[df$stimintensity == "low"] <-  -0.5
df$STIM_linear[df$stimintensity == "med"] <-  0
df$STIM_linear[df$stimintensity == "high"] <-  0.5

# contrast code 2 quadratic
df$STIM_quadratic[df$stimintensity == "low"] <-  -0.33
df$STIM_quadratic[df$stimintensity == "med"] <-  0.66
df$STIM_quadratic[df$stimintensity == "high"] <-  -0.33

# cue contrast
df$CUE_high_gt_low[df$cuetype == "cuetype-low"] <-  -0.5 # social influence task
df$CUE_high_gt_low[df$cuetype == "cuetype-high"] <-  0.5 # no influence task

df$stim_ordered <- factor(
        df$stimintensity,
        levels = c("low", "med", "high")
    )

df$cue_name[df$cuetype == "cuetype-low"] <- "low"
df$cue_name[df$cuetype == "cuetype-high"] <- "high"

df$cue_ordered <- factor(
        df$cue_name,
        levels = c("low", "high")
    )
return(df)
}
```

```{r function::NPS_lineplot_34, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
two_factor_lineplot <-
  function(df, iv1, iv2, mean, error, xlab, ylab) {
    g <- ggplot(
      data = df,
      aes(
        x = .data[[iv1]],
        y = .data[[mean]],
        group = factor(.data[[iv2]]),
        color = factor(.data[[iv2]])
      ),
      cex.lab = 1.5,
      cex.axis = 2,
      cex.main = 1.5,
      cex.sub = 1.5
    ) +
      geom_errorbar(aes(
        ymin = (.data[[mean]] - .data[[error]]),
        ymax = (.data[[mean]] + .data[[error]])
      ), width = .1) +
      geom_line() +
      geom_point() +
      ggtitle(ggtitle) +
      xlab(xlab) +
      ylab(ylab) +
      #scale_color_manual(values = color) +
      theme_classic() +
      
      theme(aspect.ratio = .6) +
      expand_limits(x = 3.25) +
      #guides(fill = "none") +
      #guides(color = TRUE) +
      #guides(fill = guide_legend(title = "title")) +
      #scale_fill_manual(values = color) +
      scale_color_manual("",
                         values =  c(
                           "pain" = "#941100",
                           "vicarious" = "#008F51",
                           "cognitive" = "#011891"
                         )) +
      theme(
        legend.position = c(.99, .99),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      theme(legend.key = element_rect(fill = "white", colour = "white")) +
      theme_bw()
    
    return(g)
  }
```


### NPS data
```{r message=FALSE, warning=FALSE, include=FALSE}

# Step 1: Common parameters
# step 1: load data
for (signature_key in c("NPSpos")) {
     #c("NPS", "NPSpos", "NPSneg", "VPS", #"VPSnooccip", "ThermalPain", "MechPain", "GeneralAversive", "AversiveVisual"
                      #  "ZhouVPS", "PINES",  "GSR", "GeuterPaincPDM")) {
  dv_keyword = signature_key
  signature_name = signature_key
  # step 1: common parameters _______
  main_dir <- dirname(dirname(getwd()))

  analysis_folder  = paste0("model35_iv-task-stim_dv-", signature_key)

  sig_name <-
    Sys.glob(file.path(
      main_dir,
      "analysis/fmri/nilearn/signature_extract",
      paste0(
        "signature-",
        signature_key,
        "_sub-all_runtype-pvc_event-stimulus.tsv"
      )
    )) # nolint
  print(sig_name)
  analysis_dir <-
    file.path(main_dir,
              "analysis",
              "mixedeffect",
              analysis_folder,
              as.character(Sys.Date())) # nolint
  dir.create(analysis_dir,
             showWarnings = FALSE,
             recursive = TRUE)
  savedir <- analysis_dir
  
  # step 2: load data
  df = read.csv(sig_name)
  sig_df = df %>% separate(
    singletrial_fname,
    sep = "_",
    c(
      "sub",
      "ses",
      "run",
      "runtype",
      "event",
      "trial",
      "cuetype",
      "stimintensity"
    )
  )
  sig_df = sig_df %>% separate(
    stimintensity,
    into = c(NA, "stimintensity"),
    extra = "drop",
    fill = "left"
  )
  pvc <- simple_contrasts_singletrial(sig_df)
  pvc$task[pvc$runtype == "runtype-pain"] <- "pain"
  pvc$task[pvc$runtype == "runtype-vicarious"] <- "vicarious"
  pvc$task[pvc$runtype == "runtype-cognitive"] <- "cognitive"
  pvc$task <- factor(pvc$task)
  
  
  # step 3: parameters
  
  taskname = "all"
  plot_keyword = "stimulusintensity"
  ggtitle_phrase =  "(3 tasks x 3 stimulus intensity)"
  
  pvc$task = factor(pvc$task)


}
```

### behavioral data
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# Load behavioral data

main_dir = dirname(dirname(getwd()))
print(main_dir)
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
taskname = '*'
subject_varkey <- "src_subject_id"
iv <- "param_stimulus_type"; 
iv_keyword <- "stim"; 
dv <- "event04_actual_angle"; dv_keyword <- "outcome"
exclude <- "sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0007|sub-0008|sub-0013|sub-0016|sub-0017|sub-0019|sub-0020|sub-0021|sub-0025|sub-0075"
#sub-0074|sub-0085|sub-0118|sub-0117|sub-0103|sub-0063

p.df <- load_task_social_df(datadir, taskname = "pain", subject_varkey, iv, dv, exclude)
v.df <- load_task_social_df(datadir, taskname = "vicarious", subject_varkey, iv, dv, exclude)
c.df <- load_task_social_df(datadir, taskname = "cognitive", subject_varkey, iv, dv, exclude)

p.df2= p.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_p <- p.df2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

v.df2= v.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_v <- v.df2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

c.df2= c.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number()-1)
data_c <- c.df2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num) )
p.sub <- data_p[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
v.sub <- data_v[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
c.sub <- data_c[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
# sub, ses, run, runtype, event, trial, cuetype, stimintensity
# src_subject_id, session_id, param_run_num, param_task_name, event02_expect_angle, param_cue_type, param_stimulus_type, event04_actual_angle
pvc.sub = rbind(p.sub, v.sub, c.sub)

pvc.sub$trial_ind <- pvc.sub$trial_index -1 
pvc.sub$sub <- sprintf("sub-%04d", pvc.sub$src_subject_id)
pvc.sub$ses <- sprintf("ses-%02d", pvc.sub$session_id)
pvc.sub$run <- sprintf("run-%02d", pvc.sub$param_run_num)
pvc.sub$runtype <- sprintf("runtype-%s", pvc.sub$param_task_name)
pvc.sub$trial <- sprintf("trial-%03d", pvc.sub$trial_ind)
pvc.sub[c('cue', 'DEPc')]  <- str_split_fixed(pvc.sub$param_cue_type , '_', 2)
pvc.sub$cuetype <- sprintf("cuetype-%s", pvc.sub$cue)
pvc.sub[c('stimintensity', 'DEP')]  <- str_split_fixed(pvc.sub$param_stimulus_type , '_', 2)

# merge
pvc.beh <- pvc.sub[,c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity","event02_expect_angle", "event04_actual_angle")]
df_merge <- merge(pvc, pvc.beh, 
                  by.x = c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity"),
                  by.y = c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity")
                  )
  
```

### Q. Within pain task, Does stimulus intenisty level and cue level significantly predict NPS dotproducts? {.unlisted .unnumbered}
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
combined_se_calc_cooksd <- data.frame()
taskname = "pain"
ggtitle <- paste(taskname, " - NPS (degree)")
title <- paste(taskname, " - actual")
subject <- "sub"
w <- 10
h <- 6
p.sig <- df_merge[df_merge$runtype == "runtype-pain" ,]
data <- p.sig
#  _______________________________________ 01. Contrast ________________# nolint
data$stim[data$stimintensity == "low"] <- -0.5 # 
data$stim[data$stimintensity == "med"] <- 0 
data$stim[data$stimintensity == "high"] <-  0.5 

data$STIM <- factor(data$stimintensity)

# contrast code 1 linear
data$STIM_linear[data$stimintensity == "low"] <- -0.5
data$STIM_linear[data$stimintensity == "med"] <- 0
data$STIM_linear[data$stimintensity == "high"] <- 0.5

# contrast code 2 quadratic
data$STIM_quadratic[data$stimintensity == "low"] <- -0.33
data$STIM_quadratic[data$stimintensity == "med"] <- 0.66
data$STIM_quadratic[data$stimintensity == "high"] <- -0.33

# social cude contrast
data$CUE_high_gt_low[data$cuetype == "cuetype-low"] <-  -0.5 
data$CUE_high_gt_low[data$cuetype == "cuetype-high"] <-  0.5 

data$EXPECT <- data$event02_expect_angle
stim_con1 <- "STIM_linear"
stim_con2 <- "STIM_quadratic"
iv1 <- "CUE_high_gt_low"
dv <- "NPSpos"

#  ________________________________________ 02. Model _________________ # nolint
model_savefname <- file.path(
  analysis_dir,
  paste(
    "lmer_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), "_cooksd.txt",    sep = ""
  )
)

cooksd <- lmer_twofactor_cooksd_fix(
  data,  taskname,  iv1,  stim_con1,  stim_con2,  dv,  subject,  dv_keyword,  model_savefname,  'random_intercept',
  print_lmer_output = FALSE
)
influential <- as.numeric(names(cooksd)[(cooksd > (4 / as.numeric(length(unique(
  data$sub
)))))])
data_screen <- data[-influential,]

#  ________________________________________ 03. Plot, reordering levels # nolint
data_screen$cue_name[data_screen$cuetype == "cuetype-high"] <-  "high cue"
data_screen$cue_name[data_screen$cuetype == "cuetype-low"] <-  "low cue"

data_screen$stim_name[data_screen$stimintensity == "high"] <-  "high"
data_screen$stim_name[data_screen$stimintensity == "med"] <-  "med"
data_screen$stim_name[data_screen$stimintensity == "low"] <-  "low"

data_screen$stim_ordered <- factor(data_screen$stim_name,
                                   levels = c("low", "med", "high"))
data_screen$cue_ordered <- factor(data_screen$cue_name,
                                  levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"

#  _________________________________________ 04. Plot, calculate mean and se # nolint
NPSstimcue_subjectwise <- meanSummary(data_screen,
                                      c(subject, model_iv1, model_iv2), dv)
NPSstimcue_groupwise <- summarySEwithin(
  data = NPSstimcue_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
NPSstimcue_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402


#  _________________________________________ 05. Plot, parameters _____ # nolint
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
subject <- "sub"
ggtitle <- paste(taskname, " - NPSpos Cooksd removed")
title <- paste(taskname, " - NPSpos")
xlab <- ""
ylab <- "NPSpos (degree)"
ylim <- c(-10, 60)
dv_keyword <- "NPSpos"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#4575B4", "#D73027")
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), "_cooksd.png",
    sep = ""
  )
)
g <- plot_halfrainclouds_twofactor(
  NPSstimcue_subjectwise,  NPSstimcue_groupwise,
  model_iv1,  model_iv2,
  sub_mean,  group_mean,
  se,  subject,
  ggtitle,  title,
  xlab,  ylab,
  taskname,  ylim,
  w,  h,
  dv_keyword,  color,  plot_savefname
)
g
```

```{r include=FALSE}
df <- p.sig %>%
  group_by(sub) %>%
  mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
  mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
  # mutate(E = as.numeric(E)) %>%
  mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
  mutate(OUTCOME_demean = event04_actual_angle - avg_outcome) %>%
  mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
  mutate(EXPECT_demean = event02_expect_angle - avg_expect) %>%
  # mutate(avg_E = mean(E, na.rm = TRUE)) %>%
  # mutate(E_demean = E - avg_E) %>%
  group_by(sub, ses) %>%
  mutate(NPSpos = as.numeric(NPSpos)) %>%
  mutate(avg_NPS = mean(NPSpos, na.rm = TRUE)) %>%
  mutate(NPS_demean = NPSpos - avg_NPS) %>%
  ungroup %>%
  mutate(OUTCOME_cmc = avg_outcome - mean(avg_outcome)) %>%
  mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) %>%
  mutate(NPS_cmc = avg_NPS - mean(avg_NPS))
  # mutate(E_cmc = avg_E - mean(avg_E)) 
```

### get pain relationship, controlling for cue, cuetype, expect
```{r echo=TRUE, message=TRUE, warning=TRUE, paged.print=FALSE}

model.stim <- lmer(event04_actual_angle ~ 
                          STIM_linear + 
                          CUE_high_gt_low + STIM_quadratic+ EXPECT_demean +
                          EXPECT_cmc +
                          ses + 
                          (1|sub), data = df
                    ) 
# CUE_high_gt_low+STIM+EXPECT_demean
sjPlot::tab_model(model.stim,
                  title = "Multilevel-modeling: \nlmer(NPSpos ~ CUE + STIM + EXPECT_demean + SES + (1| sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
# re.beta <- coef(model.stim)$unit[,"x"]
fixEffect_expect <-as.data.frame(fixef(model.stim))
randEffect_expect <-as.data.frame(ranef(model.stim))
```

```{r}
ntrials = 12
lowintens = 48;     
medintens = 49;
highintens = 50;
stim <- 48:50
painmean = 30      # average pain; arbitrary, on a 0 - 100 scale
painslope = fixEffect_expect['STIM_linear',1]     # rise in pain per unit change in stim (per degree)
painslope_stan = 0.33621048	
stdCoef.merMod <- function(object) {
  sdy <- sd(getME(object,"y"))
  sdx <- apply(getME(object,"X"), 2, sd)
  sc <- fixef(object)*sdx/sdy
  se.fixef <- coef(summary(object))[,"Std. Error"]
  se <- se.fixef*sdx/sdy
  return(data.frame(stdcoef=sc, stdse=se))
}
stdCoef.merMod(model.stim)

```

```{r}
# # library(limma)

# S <- rep(stim,times=ntrials) # stim
# C <- rep(rep(c(1,-1), each = 3), times = 6) #cue
# E <- painslope * (C + rnorm(length(C))) + painmean # pseudo nociception
# Szscore <- (S - mean(S)) / sd(S)

df$S <- as.numeric(mapvalues(df$stimintensity, 
                                        from = c("low", "med", "high"), c(48, 49, 50)))
df$C <- as.numeric(mapvalues(df$cuetype, 
                                        from = c("cuetype-low", "cuetype-high"), c(-1, 1)))
df$E <- painslope * (df$C + rnorm(length(df$C))) + painmean

df$Szscore <- (df$S - mean(df$S, na.rm = TRUE)) / sd(df$S)

df$Pcalib = df$Szscore * painslope + painmean + rnorm(length(df$C))

model.stim2pain <- lmer(Pcalib ~ S  + (1|sub), df)

b_stim2pain = fixef(model.stim2pain)[2] #0.4126089 #36.5757

df$Sprime = df$Szscore * b_stim2pain + painmean # subjective pain experience, converted to a scale of 0-180, in order to match expectation ratings
# df$Sprime = df$S * b_stim2pain 

df <- df %>%
  group_by(sub) %>%
  mutate(E = as.numeric(E)) %>%
  mutate(avg_E = mean(E, na.rm = TRUE)) %>%
  mutate(E_demean = E - avg_E) %>%
  mutate(E_cmc = avg_E - mean(avg_E))
```

## simulation **
```{r}
w = 0.7

error = rnorm(length(df$C))

df$P.assim <-  w * df$Sprime + (1 - w) * df$E + error

df$P.pe = df$Sprime - df$E + error

df$P.adapt <- 1

  minimal.diff <- (df$Sprime - df$E)/std(df$Sprime) < b_stim2pain
  large.diff <- (df$Sprime - df$E)/std(df$Sprime) > b_stim2pain
  df$P.adapt[minimal.diff] <- w * df$Sprime[minimal.diff] + (1 - w) * df$E[minimal.diff] + error[minimal.diff]
  df$P.adapt[large.diff] <- w * df$Sprime[large.diff]  + error[large.diff]

```


```{r echo=FALSE}
ggplot(df, aes(x = E, y = P.assim, color = cue_name)) +
   geom_point() + 
  theme_classic()
```

```{r echo=FALSE}
ggplot(df, aes(x = E, y = P.pe, color = cue_name)) +
   geom_point() + 
  theme_classic()
```
```{r echo=FALSE}
ggplot(df, aes(x = E, y = P.adapt, color = cue_name)) +
   geom_point() + 
  #ylim(800,1000) +
  theme_classic()
```

## Lineplots Original {.unlisted .unnumbered}
```{r echo=FALSE}
Out.stim <- meanSummary(df,
                                      c("sub", "stim_ordered", "cue_name"), "event04_actual_angle")
Out.group <- summarySEwithin(
  data = Out.stim,
  measurevar = "mean_per_sub",
  withinvars = c("stim_ordered", "cue_name"),
  idvar = "sub"
)
g <- plot_lineplot_twofactor(Out.group,
                        iv1 = "stim_ordered", iv2 = "cue_name", 
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low" = "#4575B4", "high" = "#D73027"), 
                        ggtitle = "Pain rating - original data", 
                        xlab = "Stimulus intensity", 
                        ylab = "Outcome Rating (Original data)")
g + theme(aspect.ratio=.8)
```


### Lineplots P.assim {.unlisted .unnumbered}
```{r echo=FALSE}
Out.assim <- meanSummary(df,
                                      c("sub", "stim_ordered", "cue_name"), "P.assim")
Out.assim.group <- summarySEwithin(
  data = Out.assim,
  measurevar = "mean_per_sub",
  withinvars = c("stim_ordered", "cue_name"),
  idvar = "sub"
)
g <- plot_lineplot_twofactor(Out.assim.group,
                        iv1 = "stim_ordered", iv2 = "cue_name", 
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low" = "#4575B4", "high" = "#D73027"), ggtitle = "P.assim", 
                        xlab = "Stimulus intensity", ylab = "P.assim Outcome ratings")
g + theme(aspect.ratio=.8)
```
### P.assim ~ demeaned_expect * cue * stim
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv1 = "E_demean"; iv2 = "P.assim" # "NPS_demean"
group = "cuetype"; subject = "sub"
xlab = "Expectation rating \n(subjectwise mean-centered)"
ylab = "P.assim" 
# low stimulus intensity
demean_low = df[df$stimintensity == "low", ]
low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=-50, ymax=150, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab, 
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = df[df$stimintensity == "med", ]
med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=-50, ymax=150, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab, 
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = df[df$stimintensity == "high", ]
high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=-50, ymax=150, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab, 
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n Assimilate"), color = "black", face = "bold", size = 12))
plots_title
```

### Lineplots P.pe {.unlisted .unnumbered}
```{r echo=FALSE}
Out.pe <- meanSummary(df,
                                      c("sub", "stim_ordered", "cue_name"), "P.pe")
Out.pe.group <- summarySEwithin(
  data = Out.pe,
  measurevar = "mean_per_sub",
  withinvars = c("stim_ordered", "cue_name"),
  idvar = "sub"
)
g <- plot_lineplot_twofactor(Out.pe.group,
                        iv1 = "stim_ordered", iv2 = "cue_name", 
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low" = "#4575B4", "high" = "#D73027"), ggtitle = "P.pe", 
                        xlab = "Stimulus intensity", ylab = "P.pe Outcome ratings")
g + theme(aspect.ratio=.8)
```

### P.pe ~ demeaned_expect * cue * stim
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv1 = "E"; iv2 = "P.pe" # "NPS_demean"
group = "cuetype"; subject = "sub"
xlab = "Expectation rating \n(subjectwise mean-centered)"
ylab = "P.pe" 
# low stimulus intensity
demean_low = df[df$stimintensity == "low", ]
low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=-150, ymax=150, xmin=-150, xmax=150,
    xlab = xlab, ylab = ylab, 
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = df[df$stimintensity == "med", ]
med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=-150, ymax=150, xmin=-150, xmax=150,
    xlab = xlab, ylab = ylab, 
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = df[df$stimintensity == "high", ]
high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=-150, ymax=150, xmin=-150, xmax=150,
    xlab = xlab, ylab = ylab, 
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n Prediction error"), color = "black", face = "bold", size = 12))
plots_title
```


### Lineplots P.adapt {.unlisted .unnumbered}
```{r echo=FALSE}
Out.adapt <- meanSummary(df,
                                      c("sub", "stim_ordered", "cue_name"), "P.adapt")
Out.adapt.group <- summarySEwithin(
  data = Out.adapt,
  measurevar = "mean_per_sub",
  withinvars = c("stim_ordered", "cue_name"),
  idvar = "sub"
)
g <- plot_lineplot_twofactor(Out.adapt.group,
                        iv1 = "stim_ordered", iv2 = "cue_name", 
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low" = "#4575B4", "high" = "#D73027"), ggtitle = "P.adapt", 
                        xlab = "Stimulus intensity", ylab = "P.adapt Outcome ratings")
g + theme(aspect.ratio=.8)
```




### P.adapt ~ demeaned_expect * cue * stim

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv1 = "E_demean"; iv2 = "P.adapt" # "NPS_demean"
group = "cuetype"; subject = "sub"
xlab = "Expectation rating \n(demean)"
ylab = "P.adapt" 
# low stimulus intensity
demean_low = df[df$stimintensity == "low", ]
low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=-25, ymax=75, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab, 
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = df[df$stimintensity == "med", ]
med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=-25, ymax=75, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab, 
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = df[df$stimintensity == "high", ]
high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=-25, ymax=75, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab, 
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n P.adapt and demeaned expectation"), color = "black", face = "bold", size = 12))
plots_title
```