# RL simulation Jepma PE {#ch23_jepmaPE}


## Overview
The purpose of this markdown is to benchmark the plots from Jepma et al. (2018). 
Here, we plot the expectancy ratings and the actual ratings, with the high and low cues -- in one panel. 
PE is calculated based on behavioral ratings

### Some thoughts, TODOs {.unlisted .unnumbered}
* plot 2. some runs were repeated or omitted for the subjects that have more than 72 trials. I need to identify that list and work on the behavioral data. 
* I need to check whether the counterbalancing was done correctly. 


```{r message=FALSE, warning=FALSE, include=FALSE}
library(psych)
library(car)
# library(lmSupport)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(bbmle)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(stats)
library(ggpubr)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lme4)
library(effectsize)
library(brms)
library(devtools)
library(gghalves)
library(visibly) # 
library(plotly) #plot
library(scico) # plot


library(r2mlm)
main_dir <- dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```

## load behavioral daata
```{r}
df = read.csv(file.path(main_dir, 'resources', 'references', 'cue_behavioraldata.csv'))
```

```{r}
colnames(df)
```

```{r}
# PE :: prediction error ______________________________________________________
df$PE =   df$RATING_outcome - df$RATING_expectation
# Lag expectation rating ______________________________________________________
# per run/ses/sub
data_a3lag <- df %>%
  group_by(sub,ses,run) %>% 
  mutate(prev_trial.RATING_expectation = lag(RATING_expectation, n = 1, default = NA)) %>% 
  mutate(next_trial.RATING_expectation = lead(RATING_expectation, n = 1, default = NA)) %>%
  mutate(ave.RATING_expectation = mean(RATING_expectation, na.rm = TRUE))
data_a3lag <- data_a3lag[!is.na(data_a3lag$ave.RATING_expectation),]
taskname = 'pain'
data_a3lag$next_trial.RATING_expect_fill = coalesce(data_a3lag$next_trial.RATING_expectation, data_a3lag$ave.RATING_expectation) 
data_a3lag$prev_trial.RATING_expect_fill = coalesce(data_a3lag$prev_trial.RATING_expectation, data_a3lag$ave.RATING_expectation) 

data_a3lag <- data_a3lag[data_a3lag$task == 'pain',]
# EXPECTUPDATE :: expectation (N) - expectation (N-1) ________________________
df_jepma <- data_a3lag %>%
  # group_by(sub,ses,run) %>%
  mutate(EXPECTUPDATE_NEXT =  RATING_expectation- next_trial.RATING_expect_fill)  %>%
  mutate(EXPECTUPDATE_PREV =  RATING_expectation- prev_trial.RATING_expect_fill)  %>%
  mutate(EXPECTUPDATE_PREV_JEPMA =  (RATING_expectation- prev_trial.RATING_expect_fill)/(PE+1))
```

```{r}
df_jepma$PE_type[df_jepma$PE >  0] <- "aversive" # outcome > expect
df_jepma$PE_type[df_jepma$PE <= 0] <- "appetitive" # outcome < expect
df_jepma$PE_con[df_jepma$PE <=  0] <- -1
df_jepma$PE_con[df_jepma$PE > 0] <-  1
df_jepma$cue_con[df_jepma$IV_cuelevel == "low_cue"] <- -1
df_jepma$cue_con[df_jepma$IV_cuelevel == "high_cue"] <- 1
df_jepma <- df_jepma[!is.na(df_jepma$RATING_expectation),]

write.csv(df_jepma, file.path(main_dir, "data", "hlm", "cuerating_0505.csv"))
```

## JEPMA
```{r}
# summary statistics ____________________________________________________________
subject = "sub"
model_iv1 = "PE_type"
model_iv2 =  "IV_cuelevel"

dv <- "EXPECTUPDATE_PREV_JEPMA" #"PE"
    subjectwise <- meanSummary(
        df_jepma,
        c(subject, model_iv1, model_iv2), dv
    )
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    #  calculate mean and se  ----------------------------------------------------------------------------
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(taskname, "Confirmation bias in expectation updating")
    legend_title <- "cue levels"
    title <- paste(taskname, " - Actual")
    xlab <- ""
    ylab <- "Learning Rate"
    ylim <- c(-250,250)
    dv_keyword <- "learning rate"
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c( "#D73027", "#4575B4")
    } # if keyword starts with]
    analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model23_jepmaPE")
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )

plot_halfrainclouds_twofactor(subjectwise, groupwise,
                                      model_iv1, model_iv2, sub_mean, group_mean, se, subject,
                                      ggtitle, legend_title, xlab, ylab, task_name, ylim,
                                      w, h, dv_keyword, color, save_fname)

plot_lineplot_twofactor(groupwise, model_iv1, model_iv2, "mean_per_sub_norm_mean", error = "se",
                      color = c( high_cue = "#D73027", low_cue = "#4575B4"), 
                      ggtitle, 
                      xlab= "Stimulus intensity", 
                      ylab = "Learning rate") 
```

## PREVIOUS TRIAL w/o dividing (PE+1)
```{r}
# summary statistics ____________________________________________________________
subject = "sub"
model_iv1 = "PE_type"
model_iv2 =  "IV_cuelevel"

dv <- "EXPECTUPDATE_PREV" #"PE"
    subjectwise <- meanSummary(
        df_jepma,
        c(subject, model_iv1, model_iv2), dv
    )
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    #  calculate mean and se  ----------------------------------------------------------------------------
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(taskname, "Confirmation bias in expectation updating")
    legend_title <- "cue levels"
    title <- paste(taskname, " - Actual")
    xlab <- ""
    ylab <- "Expectation update on previous trial"
    ylim <- c(-250,250)
    dv_keyword <- "learning rate"
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c( "#D73027", "#4575B4")
    } # if keyword starts with]
    analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model23_jepmaPE")
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )

plot_halfrainclouds_twofactor(subjectwise, groupwise,
                                      model_iv1, model_iv2, sub_mean, group_mean, se, subject,
                                      ggtitle, legend_title, xlab, ylab, task_name, ylim,
                                      w, h, dv_keyword, color, save_fname)

plot_lineplot_twofactor(groupwise, model_iv1, model_iv2, "mean_per_sub_norm_mean", error = "se",
                      color = c( high_cue = "#D73027", low_cue = "#4575B4"), 
                      ggtitle, 
                      xlab= "", 
                      ylab = "Expectation update on next trial") 
```


## NEXT TRIAL WITHOUT DIVIDING (PE+1)
```{r}
# summary statistics ____________________________________________________________
subject = "sub"
model_iv1 = "PE_type"
model_iv2 =  "IV_cuelevel"

dv <- "EXPECTUPDATE_NEXT" #"PE"
    subjectwise <- meanSummary(
        df_jepma,
        c(subject, model_iv1, model_iv2), dv
    )
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    #  calculate mean and se  ----------------------------------------------------------------------------
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(taskname, " - Confirmation bias in expectation updating")
    legend_title <- "cue levels"
    title <- paste(taskname, " - Actual")
    xlab <- ""
    ylab <- "Expectation update on next trial"
    ylim <- c(-250,250)
    dv_keyword <- "learning rate"
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c( "#D73027", "#4575B4")
    } # if keyword starts with]
    analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model23_jepmaPE")
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )

plot_halfrainclouds_twofactor(subjectwise, groupwise,
                                      model_iv1, model_iv2, sub_mean, group_mean, se, subject,
                                      ggtitle, legend_title, xlab, ylab, task_name, ylim,
                                      w, h, dv_keyword, color, save_fname)

plot_lineplot_twofactor(groupwise, model_iv1, model_iv2, "mean_per_sub_norm_mean", error = "se",
                      color = c( high_cue = "#D73027", low_cue = "#4575B4"), 
                      ggtitle, 
                      xlab= "Stimulus intensity", 
                      ylab = "Expectation difference from previous trial") 
```

```{r}
plot_lineplot_twofactor(groupwise, model_iv1, model_iv2, "mean_per_sub_norm_mean", error = "se",
                      color = c( high_cue = "#D73027", low_cue = "#4575B4"), 
                      ggtitle, 
                      xlab= "Stimulus intensity", 
                      ylab = "Learning rate") 
```

```
library(plyr)
subjectwise_cuetype = meanSummary_2dv(DATA=df_jepma,
        GROUP = c("sub", "trialindex", "IV_cuelevel"), DV1 = "PE", DV2 = "EXPECTUPDATE")
plot_twovariable(subjectwise_cuetype, iv1 = "DV1_mean_per_sub", iv2 = "DV2_mean_per_sub", group = "IV_cuelevel", subject = "sub", xmin=-50, xmax=50, ymin=-50,ymax=50,
xlab="PE", ylab="Expectation update", ggtitle="", color_scheme=c( high_cue = "#D73027", low_cue = "#4575B4"), alpha=.8, fit_lm=TRUE, lm_method = "lm", identity_line=TRUE, size=NULL)

```
```{r}
subjectwise_cuetype_groupby = meanSummary_2dv(DATA=df_jepma,
        GROUP = c("sub", "IV_cuelevel"), DV1 = "PE", DV2 = "EXPECTUPDATE_PREV")
plot_twovariable(df_jepma, iv1 = "PE", iv2 = "EXPECTUPDATE_PREV", group = "IV_cuelevel", subject = "sub", xmin=-50, xmax=50, ymin=-50,ymax=50,
xlab="PE", ylab="Expectation update", ggtitle="", color_scheme=c( high_cue = "#D73027", low_cue = "#4575B4"), alpha=.8, fit_lm=TRUE, lm_method = "lm", identity_line=TRUE, size=NULL)

```
```{r}
subjectwise_cuetype_groupby = meanSummary_2dv(DATA=df_jepma,
        GROUP = c("sub", "IV_cuelevel"), DV1 = "PE", DV2 = "EXPECTUPDATE_PREV_JEPMA")
plot_twovariable(df_jepma, iv1 = "PE", iv2 = "EXPECTUPDATE_PREV_JEPMA", group = "IV_cuelevel", subject = "sub", xmin=-50, xmax=50, ymin=-50,ymax=50,
xlab="PE", ylab="Expectation update", ggtitle="", color_scheme=c( high_cue = "#D73027", low_cue = "#4575B4"), alpha=.8, fit_lm=TRUE, lm_method = "lm", identity_line=TRUE, size=NULL)

```

# use sjplot
```{r}

model.l <- lmer(EXPECTUPDATE_PREV_JEPMA ~ 1+ PE*IV_cuelevel + (1+ IV_cuelevel|sub), data = df_jepma, 
                control=lmerControl(check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4)))
summary(model.l)
```
```{r}
library(sjPlot)
plot_model(model.l, type = "pred", terms = c("PE", "IV_cuelevel"))
```



```{r}
# subjectwise_cuetype_groupby = meanSummary_2dv(DATA=df_jepma,
#         GROUP = c("sub", "IV_cuelevel"), DV1 = "PE", DV2 = "EXPECTUPDATE_JEPMA")
# plot_twovariable(df_jepma, iv1 = "PE", iv2 = "EXPECTUPDATE", group = "IV_cuelevel", subject = "sub", xmin=-50, xmax=50, ymin=-50,ymax=50,
# xlab="PE", ylab="Expectation update", ggtitle="", color_scheme=c( high_cue = "#D73027", low_cue = "#4575B4"), alpha=.8, fit_lm=TRUE, lm_method = "lm", identity_line=TRUE, size=NULL)

```



