# PE and NPS {#ch24_RL_PE_NPS}
---
title: "24_RL_iv-PE_dv-NPS"
output: html_document
date: "2023-11-05"
---

## What is the purpose of this notebook? {.unlisted .unnumbered}
Here, I investigate the relationship between prediction errors and NPS extracted values.
The question we ask is, whether the cue-expectancy effects of NPS are driven by prediction errors. 

```{r include=FALSE}
library(car)
library(psych)
library(reshape)
library(dplyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(plyr)
library(ggpubr)
library(r2mlm)
library(effectsize)
library(devtools)
options(es.use_symbols = TRUE) # get nice symbols when printing! (On Windows, requires R >= 4.2.0)
library(EMAtools)
library(emmeans)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(DT)
library(raincloudplots)
devtools::source_url("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(r2mlm)
main_dir <- dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```



```{r}

# load NPS dot product
NPSdf <- read.csv(file.path(main_dir, 'analysis/fmri/nilearn/deriv01_signature/rampupdown/signature-NPSpos_sub-all_runtype-pvc_event-stimulus.tsv' ))

# load RL data
RLdf <- read.csv(file.path(main_dir, "/data/RL/modelfit_jepma_0525/table_pain.csv"))
# grab intersection of data using the sub column
```

some data wrangling: split filenames into columns. This will serve as metadata. NPSsplit
We'll use this to merge NPSsplit and RLdf

```{r}
NPSsplit <- NPSdf %>%
  # Extract the components from the filename column
  extract(col = singletrial_fname, into = c("sub", "ses", "run", "runtype", "event", "trial", "cuetype", "stimintensity"),
          regex = "(sub-\\w+)_+(ses-\\w+)_+(run-\\w+)_+(runtype-\\w+)_+(event-\\w+)_+(trial-\\w+)_+(cuetype-\\w+)_+(stimintensity-\\w+).nii.gz") %>%
  # Extract numbers and keywords as specified
  mutate(
    src_subject_id = as.integer(str_extract(sub, "\\d+")),
    session_id = as.integer(str_extract(ses, "\\d+")),
    param_run_num = as.integer(str_extract(run, "\\d+")),
    trial_index_runwise = as.integer(str_extract(trial, "\\d+")) + 1,
    param_cue_type = case_when(
      str_detect(cuetype, "low") ~ "low_cue",
      str_detect(cuetype, "high") ~ "high_cue"
    ), 
    param_task_name = str_replace(runtype, "runtype-", ""), 
    param_stimulus_type = case_when(
      stimintensity == "stimintensity-low" ~ "low_stim",
      stimintensity == "stimintensity-med" ~ "med_stim",
      stimintensity == "stimintensity-high" ~ "high_stim",
      TRUE ~ stimintensity  # Retain original value if neither "low" nor "high"
    )
  ) %>%
  
  # Select and rename the necessary columns
  select(
    src_subject_id,
    session_id,
    param_run_num,
    param_task_name,
    event,
    trial_index_runwise,
    param_cue_type,
    param_stimulus_type,
    NPSpos
  )
    # stimintensity
```

merge the two dataframes
```{r}

merge_df <- inner_join(NPSsplit, RLdf, by = c("src_subject_id",
    "session_id",
    "param_run_num",
    "param_task_name","param_cue_type", "param_stimulus_type", "trial_index_runwise"))

# result_df will contain rows that have matching values in columns A, B, and C in both df1 and df2.

```

## scatter plot
```{r}
merge_df$sub <- factor(merge_df$src_subject_id)
model.NPSRL = lmer(NPSpos ~ PE_mdl3 + (PE_mdl3 | sub) + (1|session_id), data = merge_df)
summary(model.NPSRL)
```

structure: sub, NPS, PE
subjectwise correlations
```{r}

ggplot(merge_df, aes(y = NPSpos, 
                       x = PE_mdl2, 
                       colour = src_subject_id), size = .3, color = 'gray') + 
  geom_point(size = .1) + 
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .3) +
  theme_bw()
```

```{r}
library(dplyr)
library(ggplot2)
library(broom)

# Assuming you have a dataframe `df` with the variables `subject`, `trial`, `NPS`, `PE`

# Calculate the coefficients for each participant
df <- merge_df
df$subject <- df$src_subject_id
df$NPS <- df$NPSpos
df$PE <- df$PE_mdl2

coefficients <- df %>%
  group_by(subject) %>%
  do(tidy(lm(PE ~ NPS, data = .)))

# Extract slopes and intercepts
slopes_intercepts <- coefficients %>%
  filter(term == "NPS") %>%
  select(subject, slope = estimate)

intercepts <- coefficients %>%
  filter(term == "(Intercept)") %>%
  select(subject, intercept = estimate)

# Merge slopes and intercepts
subject_lines <- full_join(slopes_intercepts, intercepts, by = "subject")

# Calculate the average slope and intercept for the group
avg_slope <- mean(subject_lines$slope)
avg_intercept <- mean(subject_lines$intercept)

# Plot
ggplot(df, aes(x = NPS, y = PE)) +
  geom_point(alpha = 0.4) +  # Plot the raw data points
  geom_abline(data = subject_lines, aes(slope = slope, intercept = intercept, color = as.factor(subject)), size = 1) +
  geom_abline(slope = avg_slope, intercept = avg_intercept, color = "black", size = 1.5, linetype = "dashed") +
  labs(color = "Subject") +
  theme_minimal() +
  theme(legend.position = "none")  # Remove legend if not needed

```


## re-run brain results from `XX.md`
## re-run behavioral results from `XX.Rmd`
