# RL ::  New model ~  cue*stim {#RL_newmodel}

## What is the purpose of this notebook? {.unlisted .unnumbered}

Here, we want to... assess the performance of Aryans new model.
We also want to see what PE best explains
Outcome? Expectation? NPS? Insula? etc

* Main model: `lmer( NPS ~ PE)` 
* Main question: Is NPS best explained by the model PE? And if so, which model best 
* {{ HYPOTHESES/EXPECTED OUTCOME }}
* 
* IV: 
  - {{ FACTOR NAME }} ( {{ LEVELS}} )
* DV: {{ DV }}


### TODO: 
```
load Aryan's dataframe
Predict NPS with different model PEs
load nps
```

### References : Once note book is complete, add at the bottom of Rmd
```
INSERT HERE
```

### load libraries {.unlisted .unnumbered}
```{r message=FALSE, warning=FALSE, include=FALSE}
library(car)
library(psych)
library(cueR)
library(ggplot2)
library(dplyr)
library(plyr)
library(tidyverse)
library(lme4)
library(lmerTest)
library(ggheatmap)
library(ggcorrplot)
```


### display distribution of data
Let's look at the distribution of the data. X axis: Y axis: 
```{r paged.print=TRUE}
main_dir <- dirname(dirname(getwd()))
rldf <- read.csv("/Users/h/Documents/projects_local/cue_expectancy/data/RL/table_pain_8mdls_andZscores_01182024.csv")
NPSdf <- read.csv(file.path(main_dir, 'analysis/fmri/nilearn/deriv01_signature/rampupdown/signature-NPSpos_sub-all_runtype-pvc_event-stimulus.tsv' ))

```


```{r}
NPSsplit <- NPSdf %>%
  # Extract the components from the filename column
  extract(col = singletrial_fname, into = c("sub", "ses", "run", "runtype", "event", "trial", "cuetype", "stimintensity"),
          regex = "(sub-\\w+)_+(ses-\\w+)_+(run-\\w+)_+(runtype-\\w+)_+(event-\\w+)_+(trial-\\w+)_+(cuetype-\\w+)_+(stimintensity-\\w+).nii.gz") %>%
  # Extract numbers and keywords as specified
  mutate(
    src_subject_id = as.integer(str_extract(sub, "\\d+")),
    session_id = as.integer(str_extract(ses, "\\d+")),
    param_run_num = as.integer(str_extract(run, "\\d+")),
    trial_index_runwise = as.integer(str_extract(trial, "\\d+")) + 1,
    param_cue_type = case_when(
      str_detect(cuetype, "low") ~ "low_cue",
      str_detect(cuetype, "high") ~ "high_cue"
    ),
    param_task_name = str_replace(runtype, "runtype-", ""),
    param_stimulus_type = case_when(
      stimintensity == "stimintensity-low" ~ "low_stim",
      stimintensity == "stimintensity-med" ~ "med_stim",
      stimintensity == "stimintensity-high" ~ "high_stim",
      TRUE ~ stimintensity  # Retain original value if neither "low" nor "high"
    )
  ) %>%

  # Select and rename the necessary columns
  select(
    src_subject_id,
    session_id,
    param_run_num,
    param_task_name,
    event,
    trial_index_runwise,
    param_cue_type,
    param_stimulus_type,
    NPSpos
  )
    # stimintensity
```

merge the two dataframes

```{r}

merge_df <- inner_join(NPSsplit, rldf, by = c("src_subject_id",
    "session_id",
    "param_run_num",
    "param_task_name","param_cue_type", "param_stimulus_type", "trial_index_runwise"))

# result_df will contain rows that have matching values in columns A, B, and C in both df1 and df2.

```

```{r}
head(merge_df)
colnames(merge_df)
```
## create heatmap
I want to observe the strcture across different models and how correlated they are with the outcome variable
NPS, event02_expect_angle, event04_actual_angle

```{r}
# g <- ggheatmap::ggheatmap(merge_df[, c("NPSpos", "event02_expect_angle", 
#                                   "event04_actual_angle", 
#                                   "Exp_mdl1", "Exp_mdl2",
#                                   "Exp_mdl3","Exp_mdl4")])
# ggheatmap(merge_df[, c("NPSpos","event04_actual_angle", "zPain_mdl1", "zPain_mdl2", "Pain_mdl1", "Pain_mdl2")])
corr <- cor(merge_df[, c("NPSpos", "event02_expect_angle", 
                                  "event04_actual_angle",
                                  "Exp_mdl1", "Exp_mdl2",
                                  "Exp_mdl3","Exp_mdl4","Exp_mdl7","Exp_mdl14","Exp_mdl15", "zPE_mdl13",
                         "Pain_mdl15")])
p.mat <- ggcorrplot::cor_pmat(corr)
ggcorrplot(corr, hc.order = FALSE,
     p.mat = p.mat, insig = "blank")
```
```{r}
ggcorrplot(cor(merge_df[, c( "zPain_mdl1", "zPain_mdl2", "zPE_mdl13")]))
```

## TODO: need the comparable z scores and raw scores from Aryan
```{r}
ggheatmap(merge_df[, c( "zPain_mdl1", "zPain_mdl2", "zPE_mdl13")])
```


```{r}
model.zpe13 <- lmer(NPSpos ~ zPE_mdl13 + (zPE_mdl13|src_subject_id), data = merge_df)
model.zExp13 <- lmer(NPSpos ~ zExp_mdl13 + (zExp_mdl13|src_subject_id), data = merge_df)
model.zPain13 <- lmer(NPSpos ~ zPain_mdl13 + (zExp_mdl13|src_subject_id), data = merge_df)

# summary(model.zpe13)
# summary(model.zExp13)
# summary(model.zPain13)
# 
# anova(model.zpe13, model.zExp13)
# model.zExp13 <- lmer(NPSpos ~ zExp_mdl13 + (zExp_mdl13|src_subject_id), data = merge_df)
# model.zExp13 <- lmer(NPSpos ~ zExp_mdl13 + (zExp_mdl13|src_subject_id), data = merge_df)

# BAD model ____________________________________________________________________
model.full <- lmer(NPSpos ~ zPE_mdl13 + zExp_mdl13 + zPain_mdl13 + (1|src_subject_id), data = merge_df)
summary(model.full)
vif(model.full)
```



```{r}

ggplot(merge_df, aes(y = NPSpos,
                       x = zPE_mdl13,
                       colour = src_subject_id), size = .3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .3) +
  theme_bw()
```
```{r}
library(dplyr)
library(ggplot2)
library(broom)

# Assuming you have a dataframe `df` with the variables `subject`, `trial`, `NPS`, `PE`

# Calculate the coefficients for each participant
df <- merge_df
df$subject <- df$src_subject_id
df$NPS <- df$NPSpos
df$PE <- df$zPE_mdl13

coefficients <- df %>%
  group_by(subject) %>%
  do(tidy(lm(NPS ~ PE, data = .)))

# Extract slopes and intercepts
slopes_intercepts <- coefficients %>%
  filter(term == "PE") %>%
  select(subject, slope = estimate)

intercepts <- coefficients %>%
  filter(term == "(Intercept)") %>%
  select(subject, intercept = estimate)

# Merge slopes and intercepts
subject_lines <- full_join(slopes_intercepts, intercepts, by = "subject")

# Calculate the average slope and intercept for the group
avg_slope <- mean(subject_lines$slope)
avg_intercept <- mean(subject_lines$intercept)

# Plot
ggplot(df, aes(x = PE, y = NPS)) +
  geom_point(alpha = 0.4) +  # Plot the raw data points
  geom_abline(data = subject_lines, aes(slope = slope, intercept = intercept, color = as.factor(subject)), size = 1) +
  geom_abline(slope = avg_slope, intercept = avg_intercept, color = "black", size = 1.5, linetype = "dashed") +
  labs(color = "Subject") +
  theme_minimal() +
  theme(legend.position = "none")  # Remove legend if not needed

```


> Summary: 

### plot {.unlisted .unnumbered}
We'll plot Y as a function of A and B
X axis: 
Y axis:
Each data point indicates ... 
```{r fig.height=10, fig.width=10}

```
> Conclusion:


:::: {.infobox}
Include the actual content here. here are my thoughts
::::

:::: {.refbox}
Include the actual content here. here are my thoughts
::::

