# [fMRI] VPS ~ singletrial {#ch36_singletrial_V}

```
author: "Heejung Jung
date: "2023-03-23"
```

## What is the purpose of this notebook? {.unlisted .unnumbered}

* Here, I model vPS dot products as a function of cue, stimulus intensity and expectation ratings. 
* One of the findings is that low cues lead to higher VPS dotproducts in the high intensity group, and that this effect becomes non-significant across sessions. 
* 03/23/2023: For now, I'm grabbing participants that have complete data, i.e. 18 runs, all three sessions. N = 65


```{r libraries_vps_stim, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(psych)
library(reshape)
library(PupillometryR)
library(dplyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(plyr)
library(ggpubr)
library(r2mlm)
library(effectsize)
options(es.use_symbols = TRUE) # get nice symbols when printing! (On Windows, requires R >= 4.2.0)
library(EMAtools)
library(emmeans)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
main_dir = dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, "scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```


```{r function::summary_for_plots_pvc, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
summary_for_plots_PVC <- function(df, groupwise_measurevar, subject_keyword, model_iv1, model_iv2, dv) {
    #  [ PLOT ] calculate mean and se  _________________________
    subjectwise <- meanSummary(
        df,
        c(subject_keyword, model_iv1, model_iv2), dv
    )
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = groupwise_measurevar,
        withinvars = c(model_iv1, model_iv2), idvar = subject_keyword
    )

    return(list(subjectwise,groupwise))
}
```

```{r function::simple_contrasts_singletrial, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
simple_contrasts_singletrial <- function(df) {
# [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
df$stim_factor <- factor(df$stim)

# contrast code 1 linear
df$stim_con_linear[df$stimintensity == "low"] <-  -0.5
df$stim_con_linear[df$stimintensity == "med"] <-  0
df$stim_con_linear[df$stimintensity == "high"] <-  0.5

# contrast code 2 quadratic
df$stim_con_quad[df$stimintensity == "low"] <-  -0.33
df$stim_con_quad[df$stimintensity == "med"] <-  0.66
df$stim_con_quad[df$stimintensity == "high"] <-  -0.33

# cue contrast
df$CUE_high_gt_low[df$cuetype == "cuetype-low"] <-  -0.5 # social influence task
df$CUE_high_gt_low[df$cuetype == "cuetype-high"] <-  0.5 # no influence task

df$stim_ordered <- factor(
        df$stimintensity,
        levels = c("low", "med", "high")
    )

df$cue_name[df$cuetype == "cuetype-low"] <- "low"
df$cue_name[df$cuetype == "cuetype-high"] <- "high"

df$cue_ordered <- factor(
        df$cue_name,
        levels = c("low", "high")
    )
return(df)
}
```

```{r function::VPS_lineplot_36, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
two_factor_lineplot <-
  function(df, iv1, iv2, mean, error, xlab, ylab) {
    g <- ggplot(
      data = df,
      aes(
        x = .data[[iv1]],
        y = .data[[mean]],
        group = factor(.data[[iv2]]),
        color = factor(.data[[iv2]])
      ),
      cex.lab = 1.5,
      cex.axis = 2,
      cex.main = 1.5,
      cex.sub = 1.5
    ) +
      geom_errorbar(aes(
        ymin = (.data[[mean]] - .data[[error]]),
        ymax = (.data[[mean]] + .data[[error]])
      ), width = .1) +
      geom_line() +
      geom_point() +
      ggtitle(ggtitle) +
      xlab(xlab) +
      ylab(ylab) +
      #scale_color_manual(values = color) +
      theme_classic() +
      
      theme(aspect.ratio = .6) +
      expand_limits(x = 3.25) +
      #guides(fill = "none") +
      #guides(color = TRUE) +
      #guides(fill = guide_legend(title = "title")) +
      #scale_fill_manual(values = color) +
      scale_color_manual("",
                         values =  c(
                           "pain" = "#941100",
                           "vicarious" = "#008F51",
                           "cognitive" = "#011891"
                         )) +
      theme(
        legend.position = c(.99, .99),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      theme(legend.key = element_rect(fill = "white", colour = "white")) +
      theme_bw()
    
    return(g)
  }
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
# step 1: load data
for (signature_key in c("VPS")) {
     #c("NPS", "NPSpos", "NPSneg", "VPS", #"VPSnooccip", "ThermalPain", "MechPain", "GeneralAversive", "AversiveVisual"
                      #  "ZhouVPS", "PINES",  "GSR", "GeuterPaincPDM")) {
  dv_keyword = signature_key
  signature_name = signature_key
  # step 1: common parameters _______
  main_dir <- dirname(dirname(getwd()))

  analysis_folder  = paste0("model36_iv-task-stim_dv-", signature_key)

  sig_name <-
    Sys.glob(file.path(
      main_dir,
      "analysis/fmri/nilearn/signature_extract",
      paste0(
        "signature-",
        signature_key,
        "_sub-all_runtype-pvc_event-stimulus.tsv"
      )
    )) # nolint
  print(sig_name)
  analysis_dir <-
    file.path(main_dir,
              "analysis",
              "mixedeffect",
              analysis_folder,
              as.character(Sys.Date())) # nolint
  dir.create(analysis_dir,
             showWarnings = FALSE,
             recursive = TRUE)
  savedir <- analysis_dir
  
  # step 2: load data
  df = read.csv(sig_name)
  sig_df = df %>% separate(
    singletrial_fname,
    sep = "_",
    c(
      "sub",
      "ses",
      "run",
      "runtype",
      "event",
      "trial",
      "cuetype",
      "stimintensity"
    )
  )
  sig_df = sig_df %>% separate(
    stimintensity,
    into = c(NA, "stimintensity"),
    extra = "drop",
    fill = "left"
  )
  pvc <- simple_contrasts_singletrial(sig_df)
  pvc$task[pvc$runtype == "runtype-pain"] <- "pain"
  pvc$task[pvc$runtype == "runtype-vicarious"] <- "vicarious"
  pvc$task[pvc$runtype == "runtype-cognitive"] <- "cognitive"
  pvc$task <- factor(pvc$task)
  
  
  # step 3: parameters
  
  taskname = "all"
  plot_keyword = "stimulusintensity"
  ggtitle_phrase =  "(3 tasks x 3 stimulus intensity)"
  
  pvc$task = factor(pvc$task)
  plot_keys <- list(
    sub_mean = "mean_per_sub",
    group_mean = "mean_per_sub_norm_mean",
    legend_keyword = "stimulus intensity",
    se = "se",
    subject = "sub",
    ggtitle = paste0(
      str_to_title(signature_key),
      " dot product: ",
      str_to_title(taskname),
      ' ',
      ggtitle_phrase,
      " (N = ",
      length(unique(pvc$sub)),
      ")"
    ),
    title = paste0(
      str_to_title(signature_key),
      " - ",
      str_to_title(plot_keyword)
    ),
    xlab = "",
    ylab = paste(signature_key, " (dot product)"),
    ylim = c(-250, 500)
  )
  
  # step 4: within between summary
  groupwise <- data.frame()
  subjectwise <- data.frame()
  summary <- summary_for_plots_PVC(
    df = pvc,
    # taskname = taskname,
    groupwise_measurevar = plot_keys$sub_mean,
    # "mean_per_sub",
    subject_keyword = plot_keys$subject,
    # "sub",
    model_iv1 =  "task",
    model_iv2 =  "stim_ordered",
    dv = signature_key #"VPS"
  )
  subjectwise <<- as.data.frame(summary[[1]])
  groupwise <<- as.data.frame(summary[[2]])
  if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
    plot_keys$color <- c("#1B9E77", "#D95F02", "#D95F02")
  } else {
    plot_keys$color <- c("#4575B4", "#FFA500", "#D73027")
  }
  
  # step 5: plot
  
  iv2 = "stim_ordered"
  iv1 = "task"
  taskname = "all"
  if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
    color <- c("#1B9E77", "#D95F02", "#D95F02")
  } else {
    color <- c("#4575B4", "#FFA500", "#D73027")
  }
  subject_mean <- "mean_per_sub"
  sub_mean = subject_mean
  group_mean <- "mean_per_sub_norm_mean"
  se <- "se"
  ylim <- c(-25, 26)
  subject <- "sub"
  ggtitle_phrase <-  "(3 tasks x 3 stimulus intensity)"
  ggtitle <-
    paste0(
      str_to_title(signature_name),
      " dot product: ",
      str_to_title(taskname),
      ' ',
      ggtitle_phrase,
      " (N = ",
      length(unique(pvc$sub)),
      ")"
    )
  
  title <-
    paste0(str_to_title(dv_keyword),
           " - ",
           str_to_title(plot_keys$legend_keyword))
  xlab <- ""
  plot_keyword = "stimintensity"
  ylab <- paste(signature_name, " (dot product)")
  plot2_savefname <- file.path(
    analysis_dir,
    paste(
      "signature_task-",
      taskname,
      "_event-",
      plot_keyword,
      "_dv-",
      signature_key,
      "_",
      as.character(Sys.Date()),
      ".png",
      sep = ""
    )
  )
  p <- plot_halfrainclouds_twofactor(
    subjectwise,
    groupwise,
    iv1,
    iv2,
    subject_mean,
    group_mean,
    se,
    subject,
    ggtitle,
    title,
    xlab,
    ylab,
    taskname,
    ylim,
    w = 10,
    h = 6,
    dv_keyword,
    color,
    plot2_savefname
  )
  p
}
```


```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
print(main_dir)
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
taskname = '*'
subject_varkey <- "src_subject_id"
iv <- "param_stimulus_type"; 
iv_keyword <- "stim"; 
dv <- "event04_actual_angle"; dv_keyword <- "outcome"
exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"

p.df <- load_task_social_df(datadir, taskname = "pain", subject_varkey, iv, dv, exclude)
v.df <- load_task_social_df(datadir, taskname = "vicarious", subject_varkey, iv, dv, exclude)
c.df <- load_task_social_df(datadir, taskname = "cognitive", subject_varkey, iv, dv, exclude)

p.df2= p.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_p <- p.df2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

v.df2= v.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_v <- v.df2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

c.df2= c.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number()-1)
data_c <- c.df2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num) )
p.sub <- data_p[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
v.sub <- data_v[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
c.sub <- data_c[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
# sub, ses, run, runtype, event, trial, cuetype, stimintensity
# src_subject_id, session_id, param_run_num, param_task_name, event02_expect_angle, param_cue_type, param_stimulus_type, event04_actual_angle
pvc.sub = rbind(p.sub, v.sub, c.sub)
```

```{r warning=FALSE, include=FALSE}
pvc.sub$trial_ind <- pvc.sub$trial_index -1 
pvc.sub$sub <- sprintf("sub-%04d", pvc.sub$src_subject_id)
pvc.sub$ses <- sprintf("ses-%02d", pvc.sub$session_id)
pvc.sub$run <- sprintf("run-%02d", pvc.sub$param_run_num)
pvc.sub$runtype <- sprintf("runtype-%s", pvc.sub$param_task_name)
pvc.sub$trial <- sprintf("trial-%03d", pvc.sub$trial_ind)
pvc.sub[c('cue', 'DEPc')]  <- str_split_fixed(pvc.sub$param_cue_type , '_', 2)
pvc.sub$cuetype <- sprintf("cuetype-%s", pvc.sub$cue)
pvc.sub[c('stimintensity', 'DEP')]  <- str_split_fixed(pvc.sub$param_stimulus_type , '_', 2)

# merge
pvc.beh <- pvc.sub[,c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity","event02_expect_angle", "event04_actual_angle")]
df_merge <- merge(pvc, pvc.beh, 
                  by.x = c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity"),
                  by.y = c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity")
                  )
  
```


---

## VPS ~ 3 task * 3 stimulus_intensity
### Q. What does the VPS pattern look like for the three tasks? {.unlisted .unnumbered}

#### Contrast weight table {.unlisted .unnumbered}
```{r echo=FALSE}
tab <- matrix(c(.5, 0, -.5, 
                -.34, -.66, -.34), ncol=3, byrow=TRUE)
colnames(tab) <- c('pain','vicarious','cognitive')
rownames(tab) <- c('task_P_gt_C','task_V_gt_PC')
kableExtra::kable_styling(
  knitr::kable(
    tab, caption = "Contrast weights", "html"), 
  "striped", position = "left", font_size = 15)
```


```{r message=FALSE, warning=FALSE, include=FALSE}
# contrast code 1 linear
pvc$task_P_gt_C[pvc$task == "pain"] <- 0.5
pvc$task_P_gt_C[pvc$task == "vicarious"] <- 0
pvc$task_P_gt_C[pvc$task == "cognitive"] <- -0.5

# contrast code 2 quadratic
pvc$task_V_gt_PC[pvc$task == "pain"] <- -.34
pvc$task_V_gt_PC[pvc$task == "vicarious"] <- .66
pvc$task_V_gt_PC[pvc$task == "cognitive"] <- -.34
```

```{r echo=TRUE, warning=TRUE, class.output="bg-warning"}
model.alltask <-
  lmer(VPS ~ task_P_gt_C*stim_factor + 
         task_V_gt_PC*stim_factor + (task|sub), data = pvc)
sjPlot::tab_model(model.alltask)
```

#### eta-squared {.unlisted .unnumbered}
```{r echo=FALSE, warning=TRUE, class.output="bg-warning"}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.alltask, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

#### Cohen's d {.unlisted .unnumbered}
```{r echo=FALSE, warning=TRUE, class.output="bg-warning"}
kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.alltask, pvc, type = "lme4"), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
plot_halfrainclouds_twofactor(
  subjectwise,  groupwise,
  iv1 = "task",  iv2 = "stim_ordered",
  sub_mean = "mean_per_sub",  group_mean = "mean_per_sub_norm_mean",
  se = "se",  subject = "sub",
  ggtitle = "All tasks",
  legend_title = "task Stim intensity",
  xlab = "Task",  ylab = paste(signature_key, ' (dot product)'),
  task_name = "all",
  ylim = c(-50, 50),
  w = 10,
  h = 6,
  dv_keyword = "stimulusintensity",
  color = c( "#1982c4","#ffca3a", "#9a031e"),
  analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model36_VPS")
  save_fname = file.path(analysis_dir, "plot_35.png")
) 
```


## VPS ~ vicarious task: 2 cue x 3 stimulus_intensity

### Q. Within vicarious task, Does stimulus intenisty level and cue level significantly predict VPS dotproducts? {.unlisted .unnumbered}
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
combined_se_calc_cooksd <- data.frame()
taskname = "vicarious"
    ggtitle <- paste(taskname, " - actual judgment (degree)")
    title <- paste(taskname, " - actual")
    subject <- "sub"
    w <- 10
    h <- 6
p.sig <- df_merge[df_merge$runtype == "runtype-vicarious",]
data <- p.sig
    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
    # contrast code ________________________________________
    data$stim[data$stimintensity == "low"] <- -0.5 # social influence task
    data$stim[data$stimintensity == "med"] <- 0 # no influence task
    data$stim[data$stimintensity == "high"] <- 0.5 # no influence task

    data$stim_factor <- factor(data$stimintensity)

    # contrast code 1 linear
    data$stim_con_linear[data$stimintensity == "low"] <- -0.5
    data$stim_con_linear[data$stimintensity == "med"] <- 0
    data$stim_con_linear[data$stimintensity == "high"] <- 0.5

    # contrast code 2 quadratic
    data$stim_con_quad[data$stimintensity == "low"] <- -0.33
    data$stim_con_quad[data$stimintensity == "med"] <- 0.66
    data$stim_con_quad[data$stimintensity == "high"] <- -0.33

    # social cude contrast
    data$social_cue[data$cuetype == "cuetype-low"] <- -0.5 # social influence task
    data$social_cue[data$cuetype == "cuetype-high"] <- 0.5 # no influence task


    stim_con1 <- "stim_con_linear"
    stim_con2 <- "stim_con_quad"
    iv1 <- "social_cue"
    dv <- "VPS"

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )
    
    cooksd <- lmer_twofactor_cooksd_fix(
        data, taskname, iv1, stim_con1, stim_con2, dv,
        subject, dv_keyword, model_savefname, 'random_intercept', print_lmer_output = FALSE
    )
    influential <- as.numeric(names(cooksd)[
        (cooksd > (4 / as.numeric(length(unique(data$sub)))))
    ])
    data_screen <- data[-influential, ]
    # [ PLOT ] reordering for plots _________________________ # nolint
    data_screen$cue_name[data_screen$cuetype == "cuetype-high"] <- "high cue"
    data_screen$cue_name[data_screen$cuetype == "cuetype-low"] <- "low cue"

    data_screen$stim_name[data_screen$stimintensity == "high"] <- "high"
    data_screen$stim_name[data_screen$stimintensity == "med"] <- "med"
    data_screen$stim_name[data_screen$stimintensity == "low"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data_screen$stim_ordered <- factor(
        data_screen$stim_name,
        levels = c("low", "med", "high")
    )
    data_screen$cue_ordered <- factor(
        data_screen$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data_screen,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402
    
    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
    # if(any(startsWith(dv_keyword, c("expect", "Expect")))){color = c( "#1B9E77", "#D95F02")}else{color=c( "#4575B4", "#D73027")} # if keyword starts with
    # print("groupwisemean")
    #  [ PLOT ] calculate mean and se  ----------------------------------------------------------------------------
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(taskname, " - ", signature_key, " Cooksd removed")
    title <- paste(taskname, " - ", signature_key)
    xlab <- ""
    ylab <- paste(signature_key, " (degree)")
    ylim <- c(-10,60)
    dv_keyword <- signature_key
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_rainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
g
```


### Linear model ver 1: VPS ~ stimulus_intensity
```{r echo=TRUE, message=FALSE, warning=TRUE, paged.print=FALSE}
model.vpsstim <- lmer(VPS ~ stim_con_linear + stim_con_quad +(stim_con_linear + stim_con_quad |sub), data = data_screen)
sjPlot::tab_model(model.vpsstim)
```

#### Linear model ver 1: eta-squared
```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.vpsstim, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)

```

#### Linear model ver 1: Cohen's d VPS stimulus intensity = 0.213 {.unlisted .unnumbered}
```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.vpsstim, data_screen, type = "lme4"), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

### Linear model ver 2: VPS ~ stimulus_intenisy * cue 
```{r echo=TRUE, message=FALSE, warning=TRUE, paged.print=FALSE}
model.vpscuestim <- lmer(VPS ~ CUE_high_gt_low*stim_con_linear + CUE_high_gt_low*stim_con_quad + (CUE_high_gt_low+stim_factor|sub), data = data_screen)
sjPlot::tab_model(model.vpscuestim)
```

#### Linear model ver 2: eta-squared {.unlisted .unnumbered}
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.vpscuestim, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

#### Cohen's d: VPS stimulus intensity d = 0.217, cue level d = 0.013 {.unlisted .unnumbered}
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.vpscuestim, data_screen, type = "lme4"), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```


### Lineplots  {.unlisted .unnumbered}
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
plot_lineplot_twofactor_subset(actual_groupwise, taskname = "vicarious", 
                        iv1 = "stim_ordered", iv2 = "cue_ordered", 
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("#4575B4", "#D73027"), ggtitle = "Within vicarious task: VPS dotproducts as a function of stimulus intensity level and cue", 
                        xlab = "Stimulus intensity", ylab = paste(signature_key, " (dot product)"))
```

### 2 Cue x 3 Stimulus intensity x Expectation rating 
```{r echo=TRUE, message=FALSE, warning=TRUE, paged.print=FALSE}
model.vps3factor <- lmer(VPS ~ CUE_high_gt_low*stim_con_linear*event02_expect_angle + CUE_high_gt_low*stim_con_quad*event02_expect_angle + (CUE_high_gt_low|sub), data = data_screen)
sjPlot::tab_model(model.vps3factor)
```


```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.vps3factor, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)

kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.vps3factor, data_screen, type = "lme4"), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

---

## VPS ~ session * cue * stimulus_intensity
### Q. Is the cue effect on VPS different across sessions? {.unlisted .unnumbered}

> Quick answer: Yes, the cue effect in session 1 (for high intensity group) is significantly different; the dirrection flips in session 3; whereas this different becomes non significant in session 4.


### Session 1: 2 cue * 3 stimulus_intensity  {.unlisted .unnumbered}
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
combined_se_calc_cooksd <- data.frame()
taskname = "vicarious"
    ggtitle <- paste(taskname, " - actual judgment (degree)")
    title <- paste(taskname, " - actual")
    subject <- "sub"
    w <- 10
    h <- 6
s1.sig <- df_merge[df_merge$runtype == "runtype-vicarious" & df_merge$ses == "ses-01",]
data <- s1.sig
    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
data$stim[data$stimintensity == "low"] <- -0.5 # social influence task
data$stim[data$stimintensity == "med"] <- 0 # no influence task
data$stim[data$stimintensity == "high"] <- 0.5 # no influence task

data$stim_factor <- factor(data$stimintensity)

# contrast code 1 linear
data$stim_con_linear[data$stimintensity == "low"] <- -0.5
data$stim_con_linear[data$stimintensity == "med"] <- 0
data$stim_con_linear[data$stimintensity == "high"] <- 0.5

# contrast code 2 quadratic
data$stim_con_quad[data$stimintensity == "low"] <- -0.33
data$stim_con_quad[data$stimintensity == "med"] <- 0.66
data$stim_con_quad[data$stimintensity == "high"] <- -0.33

    # social cude contrast
    data$social_cue[data$cuetype == "cuetype-low"] <- -0.5 # social influence task
    data$social_cue[data$cuetype == "cuetype-high"] <- 0.5 # no influence task


    stim_con1 <- "stim_con_linear"
    stim_con2 <- "stim_con_quad"
    iv1 <- "social_cue"
    dv <- signature_key

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )
    
    cooksd <- lmer_twofactor_cooksd_fix(
        data, taskname, iv1, stim_con1, stim_con2, dv,
        subject, dv_keyword, model_savefname, 'random_intercept', print_lmer_output = FALSE
    )
    influential <- as.numeric(names(cooksd)[
        (cooksd > (4 / as.numeric(length(unique(data$sub)))))
    ])
    data_screen <- data[-influential, ]
    # [ PLOT ] reordering for plots _________________________ # nolint
    data_screen$cue_name[data_screen$cuetype == "cuetype-high"] <- "high cue"
    data_screen$cue_name[data_screen$cuetype == "cuetype-low"] <- "low cue"

    data_screen$stim_name[data_screen$stimintensity == "high"] <- "high"
    data_screen$stim_name[data_screen$stimintensity == "med"] <- "med"
    data_screen$stim_name[data_screen$stimintensity == "low"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data_screen$stim_ordered <- factor(
        data_screen$stim_name,
        levels = c("low", "med", "high")
    )
    data_screen$cue_ordered <- factor(
        data_screen$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data_screen,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402
    
    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
   # calculate mean and se  
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(taskname, " - ",signature_key," Cooksd removed")
    title <- paste(taskname, " - ",signature_key)
    xlab <- ""
    ylab <- paste(signature_key," (degree)")
    ylim <- c(-10,60)
    dv_keyword <- signature_key
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_halfrainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
g
```



### Session 3: 2 cue * 3 stimulus_intensity  {.unlisted .unnumbered}
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
combined_se_calc_cooksd <- data.frame()
taskname = "vicarious"
    ggtitle <- paste(taskname, " - actual judgment (degree)")
    title <- paste(taskname, " - actual")
    subject <- "sub"
    w <- 10
    h <- 6
s1.sig <- df_merge[df_merge$runtype == "runtype-vicarious" & df_merge$ses == "ses-03",]
data <- s1.sig
    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
data$stim[data$stimintensity == "low"] <- -0.5 # social influence task
data$stim[data$stimintensity == "med"] <- 0 # no influence task
data$stim[data$stimintensity == "high"] <- 0.5 # no influence task

data$stim_factor <- factor(data$stimintensity)

# contrast code 1 linear
data$stim_con_linear[data$stimintensity == "low"] <- -0.5
data$stim_con_linear[data$stimintensity == "med"] <- 0
data$stim_con_linear[data$stimintensity == "high"] <- 0.5

# contrast code 2 quadratic
data$stim_con_quad[data$stimintensity == "low"] <- -0.33
data$stim_con_quad[data$stimintensity == "med"] <- 0.66
data$stim_con_quad[data$stimintensity == "high"] <- -0.33

    # social cude contrast
    data$social_cue[data$cuetype == "cuetype-low"] <- -0.5 # social influence task
    data$social_cue[data$cuetype == "cuetype-high"] <- 0.5 # no influence task


    stim_con1 <- "stim_con_linear"
    stim_con2 <- "stim_con_quad"
    iv1 <- "social_cue"
    dv <- signature_key

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )
    
    cooksd <- lmer_twofactor_cooksd_fix(
        data, taskname, iv1, stim_con1, stim_con2, dv,
        subject, dv_keyword, model_savefname, 'random_intercept', print_lmer_output = FALSE
    )
    influential <- as.numeric(names(cooksd)[
        (cooksd > (4 / as.numeric(length(unique(data$sub)))))
    ])
    data_screen <- data[-influential, ]
    # [ PLOT ] reordering for plots _________________________ # nolint
    data_screen$cue_name[data_screen$cuetype == "cuetype-high"] <- "high cue"
    data_screen$cue_name[data_screen$cuetype == "cuetype-low"] <- "low cue"

    data_screen$stim_name[data_screen$stimintensity == "high"] <- "high"
    data_screen$stim_name[data_screen$stimintensity == "med"] <- "med"
    data_screen$stim_name[data_screen$stimintensity == "low"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data_screen$stim_ordered <- factor(
        data_screen$stim_name,
        levels = c("low", "med", "high")
    )
    data_screen$cue_ordered <- factor(
        data_screen$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data_screen,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402
    
    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
   # calculate mean and se  
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(taskname, " - ", signature_key, " Cooksd removed")
    title <- paste(taskname, " - ", signature_key)
    xlab <- ""
    ylab <- paste(signature_key, " (degree)")
    ylim <- c(-10,60)
    dv_keyword <- signature_key
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_halfrainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
g
```


### Session 4: 2 cue * 3 stimulus_intensity  {.unlisted .unnumbered}
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
combined_se_calc_cooksd <- data.frame()
taskname = "vicarious"
    ggtitle <- paste(taskname, " - actual judgment (degree)")
    title <- paste(taskname, " - actual")
    subject <- "sub"
    w <- 10
    h <- 6
s1.sig <- df_merge[df_merge$runtype == "runtype-vicarious" & df_merge$ses == "ses-04",]
data <- s1.sig
    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
data$stim[data$stimintensity == "low"] <- -0.5 # social influence task
data$stim[data$stimintensity == "med"] <- 0 # no influence task
data$stim[data$stimintensity == "high"] <- 0.5 # no influence task

data$stim_factor <- factor(data$stimintensity)

# contrast code 1 linear
data$stim_con_linear[data$stimintensity == "low"] <- -0.5
data$stim_con_linear[data$stimintensity == "med"] <- 0
data$stim_con_linear[data$stimintensity == "high"] <- 0.5

# contrast code 2 quadratic
data$stim_con_quad[data$stimintensity == "low"] <- -0.33
data$stim_con_quad[data$stimintensity == "med"] <- 0.66
data$stim_con_quad[data$stimintensity == "high"] <- -0.33

    # social cude contrast
    data$social_cue[data$cuetype == "cuetype-low"] <- -0.5 # social influence task
    data$social_cue[data$cuetype == "cuetype-high"] <- 0.5 # no influence task


    stim_con1 <- "stim_con_linear"
    stim_con2 <- "stim_con_quad"
    iv1 <- "social_cue"
    dv <- signature_key

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )
    
    cooksd <- lmer_twofactor_cooksd_fix(
        data, taskname, iv1, stim_con1, stim_con2, dv,
        subject, dv_keyword, model_savefname, 'random_intercept', print_lmer_output = FALSE
    )
    influential <- as.numeric(names(cooksd)[
        (cooksd > (4 / as.numeric(length(unique(data$sub)))))
    ])
    data_screen <- data[-influential, ]
    # [ PLOT ] reordering for plots _________________________ # nolint
    data_screen$cue_name[data_screen$cuetype == "cuetype-high"] <- "high cue"
    data_screen$cue_name[data_screen$cuetype == "cuetype-low"] <- "low cue"

    data_screen$stim_name[data_screen$stimintensity == "high"] <- "high"
    data_screen$stim_name[data_screen$stimintensity == "med"] <- "med"
    data_screen$stim_name[data_screen$stimintensity == "low"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data_screen$stim_ordered <- factor(
        data_screen$stim_name,
        levels = c("low", "med", "high")
    )
    data_screen$cue_ordered <- factor(
        data_screen$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data_screen,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402
    
    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
   # calculate mean and se  
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(taskname, " - ", signature_key, " Cooksd removed")
    title <- paste(taskname, " - ", signature_key)
    xlab <- ""
    ylab <- paste(signature_key, " (degree)")
    ylim <- c(-10,60)
    dv_keyword <- signature_key
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_halfrainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
g
```


---

## VPS ~ outcome_rating
### Q. Do higher VPS values indicate higher outcome ratings? (Vicarious task only) {.unlisted .unnumbered}

> Yes, Higher VPS values are associated with higher outcome ratings. The pattern is slightly different from the NPS plots, when separated out into three panels of stimulus intensity levels. Neeed to ponder on these results


```{r echo=FALSE, message=FALSE, warning=FALSE}
# plot parameters
iv1 = signature_key; iv2 = "event04_actual_angle";
subject = "sub"
xlab = signature_key; ylab = "Outcome rating";
ggtitle = "All stimulus intensity"
alpha = 0.8; lm_method = "lm"
p.sig <- df_merge[df_merge$runtype == "runtype-vicarious",]
df_dropna <- p.sig[!is.na(p.sig[, iv1]) & !is.na(p.sig[, iv2]), ]
subjectwise_2dv <- meanSummary_2dv(
        df_dropna,
        c(subject),
        iv1, iv2
    )
    subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
    g <- ggplot(
        data = subjectwise_naomit_2dv,
        aes(
            x = .data[["DV1_mean_per_sub"]],
            y = .data[["DV2_mean_per_sub"]],
        )
    ) +
        geom_point(
          size = 2,
            alpha = alpha) +
        # geom_abline(
        #     intercept = 0, slope = 1, color = "green",
        #     linetype = "dashed", linewidth = 0.5
        # ) +
        theme(aspect.ratio = 1) +
        #scale_color_manual(values = color_scheme) +
        scale_shape_manual(values = c(16, 17)) +
        xlab(xlab) +
        ylab(ylab) +
        xlim(-10, 30) +
        ylim(0,100) +
        ggtitle(ggtitle) +
        theme(
            axis.line = element_line(colour = "grey50"),
            panel.background = element_blank(),
            plot.subtitle = ggtext::element_textbox_simple(size = 11)
        ) +
              geom_ribbon(stat = "smooth", method = lm_method, se = TRUE, alpha = 0.1,
              aes(color = NULL)) +
        geom_line(stat = "smooth", method = lm_method, alpha = 0.8, linewidth = 1.5)
    g
```

### outcome_ratings * cue
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
p.sig <- df_merge[df_merge$runtype == "runtype-vicarious",]
iv2 = "event04_actual_angle"; iv1 = signature_key
df_dropna <-
  p.sig[!is.na(p.sig$event04_actual_angle) & !is.na(p.sig$VPS),]
total <-
  plot_twovariable(
    df_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin =0, ymax = 100, xmin = -10, xmax = 30,
    ylab = "outcome rating",
    xlab = signature_key, 
    ggtitle = "all stimulus intensity", 
    color_scheme = c("cuetype-high" ="#008F51","cuetype-low" =  "#BBBBBB"), 
    alpha = .8, fit_lm = TRUE, lm_method ="lm", identity_line = FALSE
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for VPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )
```


### outcome_ratings * stimulus_intensity * cue

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv2 = "event04_actual_angle"; iv1 = signature_key
group = "cuetype"; subject = "sub"
# low stimulus intensity
df_low = df_dropna[df_dropna$stimintensity == "low", ]
low <-
  plot_twovariable(
    df_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=0, ymax=180, xmin=-10,xmax=30,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#C6FF8A","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
df_med = df_dropna[df_dropna$stimintensity == "med", ]
med <-
  plot_twovariable(
    df_med, iv1, iv2,
    group = group, subject = subject,
    ymin=0, ymax=180, xmin=-10,xmax=30,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#63C76E","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
df_high = df_dropna[df_dropna$stimintensity == "high", ]
high <-
  plot_twovariable(
    df_high, iv1, iv2,
    group = group, subject = subject,
    ymin=0, ymax=180, xmin=-10,xmax=30,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#008F51","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n VPS/Outcome linear relationship differs as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```


---

## VPS ~ expectation_rating
### Q. What is the relationship betweeen expectation ratings & VPS? (Vicarious task only) {.unlisted .unnumbered}
Do we see a linear effect between expectation rating and VPS dot products? Also, does this effect differ as a function of cue and stimulus intensity ratings, as is the case for behavioral ratings?

> Quick answer: Kind of, expectation ratings predict VPS dotproducts; almost only in the low cue conditions across all stimulus intensity levels. 


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
p.sig <- df_merge[df_merge$runtype == "runtype-vicarious",]
iv1 = "event02_expect_angle"; iv2 = signature_key
df_dropna <-
  p.sig[!is.na(p.sig$event02_expect_angle) & !is.na(p.sig$VPS),]
total <-
  plot_twovariable(
    df_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    xmin =0, xmax = 100, ymin = -10, ymax = 20,
    xlab = "expectation rating",
    ylab = signature_key, 
    ggtitle = "all stimulus intensity", 
    color_scheme = c("cuetype-high" ="#008F51","cuetype-low" =  "#BBBBBB"), 
    alpha = .8, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )


total + labs(title =paste0("task-",taskname, "- What is the pattern for VPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n"))
```


```{r rawoutcome_pain_stimuluswise, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv1 = "event02_expect_angle"; iv2 = signature_key
group = "cuetype"; subject = "sub"
# low stimulus intensity
df_low = df_dropna[df_dropna$stimintensity == "low", ]
low <-
  plot_twovariable(
    df_low, iv1 , iv2,
    group = group, subject = subject,
    xmin =0, xmax = 100, ymin = -10, ymax = 20,
    xlab = "expectation rating", ylab = signature_key,
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#C6FF8A","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
df_med = df_dropna[df_dropna$stimintensity == "med", ]
med <-
  plot_twovariable(
    df_med, iv1, iv2,
    group = group, subject = subject,
    xmin =0, xmax = 100, ymin = -10, ymax = 20,
    xlab = "expectation rating", ylab = signature_key,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#63C76E","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
df_high = df_dropna[df_dropna$stimintensity == "high", ]
high <-
  plot_twovariable(
    df_high, iv1, iv2,
    group = group, subject = subject,
    xmin =0, xmax = 100, ymin = -10, ymax = 20,
    xlab = "expectation rating", ylab = signature_key,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#008F51","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n Expect/Outcome linear relationship differs as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```


