# [fMRI] Cognitive signature ~ single trial {#ch37_singletrial_C}

```
author: "Heejung Jung"
date: "2023-03-04"
```


```{r libraries_nps_stim, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(psych)
library(reshape)
library(PupillometryR)
library(dplyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(plyr)
library(ggpubr)
library(r2mlm)
library(plotly)
library(effectsize)
options(es.use_symbols = TRUE) # get nice symbols when printing! (On Windows, requires R >= 4.2.0)
library(EMAtools)
library(emmeans)
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summaryse.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulatedata.R")
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

## Function {.unlisted .unnumbered}
```{r function::summary_for_plots_pvc, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
summary_for_plots_PVC <- function(df, groupwise_measurevar, subject_keyword, model_iv1, model_iv2, dv) {
    #  [ PLOT ] calculate mean and se  _________________________
    subjectwise <- meanSummary(
        df,
        c(subject_keyword, model_iv1, model_iv2), dv
    )
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = groupwise_measurevar,
        withinvars = c(model_iv1, model_iv2), idvar = subject_keyword
    )

    return(list(subjectwise,groupwise))
}
```

```{r function::simple_contrasts_singletrial, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
simple_contrasts_singletrial <- function(df) {
# [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
df$stim_factor <- factor(df$stim)

# contrast code 1 linear
df$stim_con_linear[df$stimintensity == "low"] <-  -0.5
df$stim_con_linear[df$stimintensity == "med"] <-  0
df$stim_con_linear[df$stimintensity == "high"] <-  0.5

# contrast code 2 quadratic
df$stim_con_quad[df$stimintensity == "low"] <-  -0.33
df$stim_con_quad[df$stimintensity == "med"] <-  0.66
df$stim_con_quad[df$stimintensity == "high"] <-  -0.33

# cue contrast
df$cue_con[df$cuetype == "cuetype-low"] <-  -0.5 # social influence task
df$cue_con[df$cuetype == "cuetype-high"] <-  0.5 # no influence task

df$stim_ordered <- factor(
        df$stimintensity,
        levels = c("low", "med", "high")
    )

df$cue_name[df$cuetype == "cuetype-low"] <- "low"
df$cue_name[df$cuetype == "cuetype-high"] <- "high"

df$cue_ordered <- factor(
        df$cue_name,
        levels = c("low", "high")
    )
return(df)
}
```

```{r function::Cog_lineplot_34, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
two_factor_lineplot <-
  function(df, iv1, iv2, mean, error, xlab, ylab) {
    g <- ggplot(
      data = df,
      aes(
        x = .data[[iv1]],
        y = .data[[mean]],
        group = factor(.data[[iv2]]),
        color = factor(.data[[iv2]])
      ),
      cex.lab = 1.5,
      cex.axis = 2,
      cex.main = 1.5,
      cex.sub = 1.5
    ) +
      geom_errorbar(aes(
        ymin = (.data[[mean]] - .data[[error]]),
        ymax = (.data[[mean]] + .data[[error]])
      ), width = .1) +
      geom_line() +
      geom_point() +
      ggtitle(ggtitle) +
      xlab(xlab) +
      ylab(ylab) +
      theme_classic() +
      theme(aspect.ratio = .6) +
      expand_limits(x = 3.25) +
      scale_color_manual("",
                         values =  c(
                           "pain" = "#941100",
                           "vicarious" = "#008F51",
                           "cognitive" = "#011891"
                         )) +
      theme(
        legend.position = c(.99, .99),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      theme(legend.key = element_rect(fill = "white", colour = "white")) +
      theme_bw()
    
    return(g)
  }
```

## Step 1: Common parameters {.unlisted .unnumbered}
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

# step 1: load data
for (signature_key in c("Kragel18CogControl")) {
  dv_keyword = signature_key
  signature_name = signature_key
  # step 1: common parameters _______
  main_dir <- dirname(dirname(getwd()))
  analysis_folder  = paste0("model37_iv-task-stim_dv-", signature_key)
  sig_name <-
    Sys.glob(file.path(
      main_dir, "analysis/fmri/nilearn/signature_extract",
      paste0(
        "signature-", signature_key,"_sub-all_runtype-pvc_event-stimulus.tsv"
      )
    )) # nolint
  print(sig_name)
  analysis_dir <-
    file.path(main_dir, "analysis", "mixedeffect", analysis_folder, as.character(Sys.Date())
              ) # nolint
  dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
  savedir <- analysis_dir
  
  # step 2: load data
  df = read.csv(sig_name)
  sig_df = df %>% separate(
    singletrial_fname,
    sep = "_",
    c(
      "sub", "ses", "run", "runtype", "event", "trial", "cuetype", "stimintensity"
    )
  )
  sig_df = sig_df %>% separate(
    stimintensity,
    into = c(NA, "stimintensity"),
    extra = "drop",
    fill = "left"
  )
  pvc <- simple_contrasts_singletrial(sig_df)
  pvc$task[pvc$runtype == "runtype-pain"] <- "pain"
  pvc$task[pvc$runtype == "runtype-vicarious"] <- "vicarious"
  pvc$task[pvc$runtype == "runtype-cognitive"] <- "cognitive"
  pvc$task <- factor(pvc$task)
  
  
  # step 3: parameters
  
  taskname = "all"
  plot_keyword = "stimulusintensity"
  ggtitle_phrase =  "(3 tasks x 3 stimulus intensity)"
  
  pvc$task = factor(pvc$task)
  plot_keys <- list(
    sub_mean = "mean_per_sub",
    group_mean = "mean_per_sub_norm_mean",
    legend_keyword = "stimulus intensity",
    se = "se",
    subject = "sub",
    ggtitle = paste0(
      str_to_title(signature_key)," dot product: ",str_to_title(taskname),' ',
      ggtitle_phrase," (N = ", length(unique(pvc$sub)), ")"
    ),
    title = paste0(
      str_to_title(signature_key), " - ", str_to_title(plot_keyword)
    ),
    xlab = "",    ylab = paste(signature_key, " (dot product)"),
    ylim = c(-250, 500)
  )
  
  # step 4: within between summary
  groupwise <- data.frame()
  subjectwise <- data.frame()
  summary <- summary_for_plots_PVC(
    df = pvc,
    groupwise_measurevar = plot_keys$sub_mean,
    subject_keyword = plot_keys$subject,
    model_iv1 =  "task",
    model_iv2 =  "stim_ordered",
    dv = signature_key #"Cog"
  )
  subjectwise <<- as.data.frame(summary[[1]])
  groupwise <<- as.data.frame(summary[[2]])
  if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
    plot_keys$color <- c("#1B9E77", "#D95F02", "#D95F02")
  } else {
    plot_keys$color <- c("#4575B4", "#FFA500", "#D73027")
  }
  
  # step 5: plot
  
  iv2 = "stim_ordered"
  iv1 = "task"
  taskname = "all"
  if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
    color <- c("#1B9E77", "#D95F02", "#D95F02")
  } else {
    color <- c("#4575B4", "#FFA500", "#D73027")
  }
  subject_mean <- "mean_per_sub"
  sub_mean = subject_mean
  group_mean <- "mean_per_sub_norm_mean"
  se <- "se"
  ylim <- c(-25, 26)
  subject <- "sub"
  ggtitle_phrase <-  "(3 tasks x 3 stimulus intensity)"
  ggtitle <-
    paste0(
      str_to_title(signature_name),
      " dot product: ", str_to_title(taskname), ' ', ggtitle_phrase,
      " (N = ", length(unique(pvc$sub)), ")"
    )
  
  title <-
    paste0(str_to_title(dv_keyword),
           " - ",
           str_to_title(plot_keys$legend_keyword))
  xlab <- ""
  plot_keyword = "stimintensity"
  ylab <- paste(signature_name, " (dot product)")
  plot2_savefname <- file.path(
    analysis_dir,
    paste(
      "signature_task-",taskname, "_event-",plot_keyword,"_dv-",signature_key,"_",
      as.character(Sys.Date()),".png",
      sep = ""
    )
  )
  p <- plot_halfrainclouds_twofactor(
    subjectwise, groupwise,
    iv1, iv2, subject_mean, group_mean, se, subject,
    ggtitle, title, xlab, ylab, taskname,
    ylim, w = 10, h = 6, dv_keyword, color, plot2_savefname
  )
  p
}
```

### Load behavioral data {.unlisted .unnumbered}
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
print(main_dir)
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
taskname = '*'
subject_varkey <- "src_subject_id"
iv <- "param_stimulus_type"; 
iv_keyword <- "stim"; 
dv <- "event04_actual_angle"; dv_keyword <- "outcome"
exclude <- "sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0007|sub-0008|sub-0011|sub-0013|sub-0014|sub-0016|sub-0017|sub-0019|sub-0020|sub-0021|sub-0023|sub-0024|sub-0025|sub-0026|sub-0035|sub-0040|sub-0041|sub-0059|sub-0064|sub-0066|sub-0069|sub-0070|sub-0074|sub-0075|sub-0076|sub-0077|sub-0079|sub-0083|sub-0084|sub-0088|sub-0089|sub-0103|sub-0111|sub-0112|sub-0131"

p.df <- load_task_social_df(datadir, taskname = "pain", subject_varkey, iv, dv, exclude)
v.df <- load_task_social_df(datadir, taskname = "vicarious", subject_varkey, iv, dv, exclude)
c.df <- load_task_social_df(datadir, taskname = "cognitive", subject_varkey, iv, dv, exclude)

p.df2= p.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_p <- p.df2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

v.df2= v.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_v <- v.df2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

c.df2= c.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number()-1)
data_c <- c.df2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num) )
p.sub <- data_p[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
v.sub <- data_v[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
c.sub <- data_c[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
# sub, ses, run, runtype, event, trial, cuetype, stimintensity
# src_subject_id, session_id, param_run_num, param_task_name, event02_expect_angle, param_cue_type, param_stimulus_type, event04_actual_angle
pvc.sub = rbind(p.sub, v.sub, c.sub)


```

```{r}
pvc.sub$trial_ind <- pvc.sub$trial_index -1 
pvc.sub$sub <- sprintf("sub-%04d", pvc.sub$src_subject_id)
pvc.sub$ses <- sprintf("ses-%02d", pvc.sub$session_id)
pvc.sub$run <- sprintf("run-%02d", pvc.sub$param_run_num)
pvc.sub$runtype <- sprintf("runtype-%s", pvc.sub$param_task_name)
pvc.sub$trial <- sprintf("trial-%03d", pvc.sub$trial_ind)
pvc.sub[c('cue', 'DEPc')]  <- str_split_fixed(pvc.sub$param_cue_type , '_', 2)
pvc.sub$cuetype <- sprintf("cuetype-%s", pvc.sub$cue)
pvc.sub[c('stimintensity', 'DEP')]  <- str_split_fixed(pvc.sub$param_stimulus_type , '_', 2)

# merge
pvc.beh <- pvc.sub[,c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity","event02_expect_angle", "event04_actual_angle")]
df_merge <- merge(pvc, pvc.beh, 
                  by.x = c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity"),
                  by.y = c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity")
                  )
  
```




## PVC all task comparison
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=FALSE}
# contrast code 1 linear
pvc$task_con_linear[pvc$task == "pain"] <- 0.5
pvc$task_con_linear[pvc$task == "vicarious"] <- 0
pvc$task_con_linear[pvc$task == "cognitive"] <- -0.5

# contrast code 2 quadratic
pvc$task_con_quad[pvc$task == "pain"] <- 0.66
pvc$task_con_quad[pvc$task == "vicarious"] <- -.34
pvc$task_con_quad[pvc$task == "cognitive"] <- -.34
```

```{r class.output="bg-warning"}
model.alltask <- lmer(Kragel18CogControl ~ task_con_linear*stim_factor + task_con_quad*stim_factor + (task|sub), data = pvc)
summary(model.alltask)
```

```{r class.output="bg-warning"}
print("eta squared")
eta_squared(model.alltask, partial = TRUE)
```
<!-- parameters::model_parameters(model.alltask) -->

```{r class.output="bg-warning"}
lme.dscore(model.alltask, pvc, type = "lme4")
```

```{r}
plot_halfrainclouds_twofactor(subjectwise, groupwise,
                                      iv1 = "task", iv2 = "stim_ordered", sub_mean = "mean_per_sub", group_mean = "mean_per_sub_norm_mean", se = "se", subject = "sub",
                                      ggtitle = "All tasks", title = "task Stim intensity", xlab = "Task", ylab = paste(signature_key, ' (dot product)'), task_name = "all", 
                              ylim = c(-50, 50),
                                      w=10, h=6, dv_keyword = "stimulusintensity", color = c("red", "yellow", "blue"), save_fname = "/Users/h/Desktop/plot_35.png") 
```


## Cognitive only Stim x cue interaction

### 2x3 stimulus intensity * cue 
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
combined_se_calc_cooksd <- data.frame()
taskname = "cognitive"
ggtitle <- paste(taskname, " - actual judgment (degree)")
title <- paste(taskname, " - actual")
subject <- "sub"
w <- 10;    h <- 6
c.sig <- df_merge[df_merge$runtype == "runtype-cognitive",]
data <- c.sig
    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
    # contrast code ________________________________________
data$stim[data$stimintensity == "low"] <- -0.5 # social influence task
data$stim[data$stimintensity == "med"] <- 0 # no influence task
data$stim[data$stimintensity == "high"] <- 0.5 # no influence task

data$stim_factor <- factor(data$stimintensity)

# contrast code 1 linear
data$stim_con_linear[data$stimintensity == "low"] <- -0.5
data$stim_con_linear[data$stimintensity == "med"] <- 0
data$stim_con_linear[data$stimintensity == "high"] <- 0.5

# contrast code 2 quadratic
data$stim_con_quad[data$stimintensity == "low"] <- -0.33
data$stim_con_quad[data$stimintensity == "med"] <- 0.66
data$stim_con_quad[data$stimintensity == "high"] <- -0.33

# social cude contrast
data$social_cue[data$cuetype == "cuetype-low"] <- -0.5 # social influence task
data$social_cue[data$cuetype == "cuetype-high"] <- 0.5 # no influence task


stim_con1 <- "stim_con_linear"
stim_con2 <- "stim_con_quad"
iv1 <- "social_cue"
dv <- "Kragel18CogControl"

    # [ MODEL ] _________________________________________________ # nolint
model_savefname <- file.path(
    analysis_dir,
    paste("lmer_task-", taskname, "_rating-", dv_keyword, "_",
          as.character(Sys.Date()),"_cooksd.txt", sep = ""
        )
    )
    
    cooksd <- lmer_twofactor_cooksd_fix(
        data, taskname, iv1, stim_con1, stim_con2, dv,
        subject, dv_keyword, model_savefname, 'random_intercept', print_lmer_output = FALSE
    )
    influential <- as.numeric(names(cooksd)[
        (cooksd > (4 / as.numeric(length(unique(data$sub)))))
    ])
    data_screen <- data[-influential, ]
    # [ PLOT ] reordering for plots _________________________ # nolint
    data_screen$cue_name[data_screen$cuetype == "cuetype-high"] <- "high cue"
    data_screen$cue_name[data_screen$cuetype == "cuetype-low"] <- "low cue"

    data_screen$stim_name[data_screen$stimintensity == "high"] <- "high"
    data_screen$stim_name[data_screen$stimintensity == "med"] <- "med"
    data_screen$stim_name[data_screen$stimintensity == "low"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data_screen$stim_ordered <- factor(
        data_screen$stim_name,
        levels = c("low", "med", "high")
    )
    data_screen$cue_ordered <- factor(
        data_screen$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data_screen,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402
    
    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
    # if(any(startsWith(dv_keyword, c("expect", "Expect")))){color = c( "#1B9E77", "#D95F02")}else{color=c( "#4575B4", "#D73027")} # if keyword starts with
    # print("groupwisemean")
    #  [ PLOT ] calculate mean and se  ----------------------------------------------------------------------------
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(taskname, " - ", signature_key, " Cooksd removed")
    title <- paste(taskname, " - ", signature_key)
    xlab <- ""
    ylab <- paste(signature_key, " (dot product)")
    ylim <- c(-.25,.25)
    dv_keyword <- signature_key
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_halfrainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
g
```


### Linear model
```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
cooksd <- lmer_twofactor_cooksd_fix(
        data, taskname, iv1, stim_con1, stim_con2, dv,
        subject, dv_keyword, model_savefname, 'random_slopes', print_lmer_output = TRUE
    )
```

### Cog stimulus intensity Cohen's d = 0.72
```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
model.cogstim <- lmer(Kragel18CogControl ~ stim_con_linear + stim_con_quad +(stim_con_linear + stim_con_quad |sub), data = data_screen)
summary(model.cogstim)
```

```{r class.output="bg-warning"}
eta_squared(model.cogstim, partial = TRUE)

```

```{r class.output="bg-warning"}
lme.dscore(model.cogstim, data_screen, type = "lme4")
emm1 = emmeans(model.cogstim, specs = pairwise ~ stim_con_linear+ stim_con_quad )
```

### Cognitive stimulus & cue effect size: stim_d = 0.73, cue_d = 0.069
```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE, class.output="bg-warning"}
model.cogcuestim <- lmer(Kragel18CogControl ~ cue_con*stim_con_linear + cue_con*stim_con_quad + (cue_con|sub), data = data_screen)
summary(model.cogcuestim)
print("eta squared")
eta_squared(model.cogcuestim, partial = TRUE)
#parameters::model_parameters(model.cogcuestim)
lme.dscore(model.cogcuestim, data_screen, type = "lme4")
```


### Lineplots
```{r echo=FALSE, message=FALSE, warning=FALSE}
plot_lineplot_twofactor(actual_groupwise, taskname = "cognitive", 
                        iv1 = "stim_ordered", iv2 = "cue_ordered", 
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("#4575B4", "#D73027"), ggtitle = "Cognitive Signature as a function of cue and stimulus intensity", 
                        xlab = "Stimulus intensity", ylab = paste(signature_key, " (dot product)"))
```

### Linear model with Stim x Cue x Expectation rating
```{r class.output="bg-warning"}
model.cog3factor <- lmer(Kragel18CogControl ~ cue_con*stim_con_linear*event02_expect_angle + cue_con*stim_con_quad*event02_expect_angle + (cue_con|sub), data = data_screen)
summary(model.cog3factor)
print("eta squared")
eta_squared(model.cog3factor, partial = TRUE)
#parameters::model_parameters(model.cog3factor)
lme.dscore(model.cog3factor, data_screen, type = "lme4")
```

```{r echo=FALSE}
fig <- plot_ly(data_screen, x = ~event02_expect_angle, y = ~Kragel18CogControl, z = ~event04_actual_angle, color = ~cue_con, colors = c('#BF382A', '#0C4B8E'))
fig <- fig %>% add_markers()
fig <- fig %>% layout(scene = list(xaxis = list(title = 'Expectation'),
                     yaxis = list(title = 'Kragel Cognitive'),
                     zaxis = list(title = 'Outcome rating')))

fig
```



### Session 1: 2x3 stimulus intensity * cue 
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
combined_se_calc_cooksd <- data.frame()
taskname = "cognitive"
    ggtitle <- paste(taskname, " - actual judgment (degree)")
    title <- paste(taskname, " - actual")
    subject <- "sub"
    w <- 10
    h <- 6
s1.sig <- df_merge[df_merge$runtype == "runtype-cognitive" & df_merge$ses == "ses-01",]
data <- s1.sig
    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
data$stim[data$stimintensity == "low"] <- -0.5 # social influence task
data$stim[data$stimintensity == "med"] <- 0 # no influence task
data$stim[data$stimintensity == "high"] <- 0.5 # no influence task

data$stim_factor <- factor(data$stimintensity)

# contrast code 1 linear
data$stim_con_linear[data$stimintensity == "low"] <- -0.5
data$stim_con_linear[data$stimintensity == "med"] <- 0
data$stim_con_linear[data$stimintensity == "high"] <- 0.5

# contrast code 2 quadratic
data$stim_con_quad[data$stimintensity == "low"] <- -0.33
data$stim_con_quad[data$stimintensity == "med"] <- 0.66
data$stim_con_quad[data$stimintensity == "high"] <- -0.33

    # social cude contrast
    data$social_cue[data$cuetype == "cuetype-low"] <- -0.5 # social influence task
    data$social_cue[data$cuetype == "cuetype-high"] <- 0.5 # no influence task


    stim_con1 <- "stim_con_linear"
    stim_con2 <- "stim_con_quad"
    iv1 <- "social_cue"
    dv <- signature_key

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )
    
    cooksd <- lmer_twofactor_cooksd_fix(
        data, taskname, iv1, stim_con1, stim_con2, dv,
        subject, dv_keyword, model_savefname, 'random_intercept', print_lmer_output = FALSE
    )
    influential <- as.numeric(names(cooksd)[
        (cooksd > (4 / as.numeric(length(unique(data$sub)))))
    ])
    data_screen <- data[-influential, ]
    # [ PLOT ] reordering for plots _________________________ # nolint
    data_screen$cue_name[data_screen$cuetype == "cuetype-high"] <- "high cue"
    data_screen$cue_name[data_screen$cuetype == "cuetype-low"] <- "low cue"

    data_screen$stim_name[data_screen$stimintensity == "high"] <- "high"
    data_screen$stim_name[data_screen$stimintensity == "med"] <- "med"
    data_screen$stim_name[data_screen$stimintensity == "low"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data_screen$stim_ordered <- factor(
        data_screen$stim_name,
        levels = c("low", "med", "high")
    )
    data_screen$cue_ordered <- factor(
        data_screen$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data_screen,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402
    
    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
   # calculate mean and se  
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(taskname, " - ",signature_key," Cooksd removed")
    title <- paste(taskname, " - ",signature_key)
    xlab <- ""
    ylab <- paste(signature_key," (degree)")
    ylim <- c(-10,60)
    dv_keyword <- signature_key
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_halfrainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
g
```



### Session 3: 2x3 stimulus intensity * cue 
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
combined_se_calc_cooksd <- data.frame()
taskname = "cognitive"
    ggtitle <- paste(taskname, " - actual judgment (degree)")
    title <- paste(taskname, " - actual")
    subject <- "sub"
    w <- 10
    h <- 6
s1.sig <- df_merge[df_merge$runtype == "runtype-cognitive" & df_merge$ses == "ses-03",]
data <- s1.sig
    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
data$stim[data$stimintensity == "low"] <- -0.5 # social influence task
data$stim[data$stimintensity == "med"] <- 0 # no influence task
data$stim[data$stimintensity == "high"] <- 0.5 # no influence task

data$stim_factor <- factor(data$stimintensity)

# contrast code 1 linear
data$stim_con_linear[data$stimintensity == "low"] <- -0.5
data$stim_con_linear[data$stimintensity == "med"] <- 0
data$stim_con_linear[data$stimintensity == "high"] <- 0.5

# contrast code 2 quadratic
data$stim_con_quad[data$stimintensity == "low"] <- -0.33
data$stim_con_quad[data$stimintensity == "med"] <- 0.66
data$stim_con_quad[data$stimintensity == "high"] <- -0.33

    # social cude contrast
    data$social_cue[data$cuetype == "cuetype-low"] <- -0.5 # social influence task
    data$social_cue[data$cuetype == "cuetype-high"] <- 0.5 # no influence task


    stim_con1 <- "stim_con_linear"
    stim_con2 <- "stim_con_quad"
    iv1 <- "social_cue"
    dv <- signature_key

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )
    
    cooksd <- lmer_twofactor_cooksd_fix(
        data, taskname, iv1, stim_con1, stim_con2, dv,
        subject, dv_keyword, model_savefname, 'random_intercept', print_lmer_output = FALSE
    )
    influential <- as.numeric(names(cooksd)[
        (cooksd > (4 / as.numeric(length(unique(data$sub)))))
    ])
    data_screen <- data[-influential, ]
    # [ PLOT ] reordering for plots _________________________ # nolint
    data_screen$cue_name[data_screen$cuetype == "cuetype-high"] <- "high cue"
    data_screen$cue_name[data_screen$cuetype == "cuetype-low"] <- "low cue"

    data_screen$stim_name[data_screen$stimintensity == "high"] <- "high"
    data_screen$stim_name[data_screen$stimintensity == "med"] <- "med"
    data_screen$stim_name[data_screen$stimintensity == "low"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data_screen$stim_ordered <- factor(
        data_screen$stim_name,
        levels = c("low", "med", "high")
    )
    data_screen$cue_ordered <- factor(
        data_screen$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data_screen,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402
    
    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
   # calculate mean and se  
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(taskname, " - ", signature_key, " Cooksd removed")
    title <- paste(taskname, " - ", signature_key)
    xlab <- ""
    ylab <- paste(signature_key, " (degree)")
    ylim <- c(-10,60)
    dv_keyword <- signature_key
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_halfrainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
g
```


### Session 4: 2x3 stimulus intensity * cue 
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
combined_se_calc_cooksd <- data.frame()
taskname = "cognitive"
    ggtitle <- paste(taskname, " - actual judgment (degree)")
    title <- paste(taskname, " - actual")
    subject <- "sub"
    w <- 10
    h <- 6
s1.sig <- df_merge[df_merge$runtype == "runtype-cognitive" & df_merge$ses == "ses-04",]
data <- s1.sig
    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
data$stim[data$stimintensity == "low"] <- -0.5 # social influence task
data$stim[data$stimintensity == "med"] <- 0 # no influence task
data$stim[data$stimintensity == "high"] <- 0.5 # no influence task

data$stim_factor <- factor(data$stimintensity)

# contrast code 1 linear
data$stim_con_linear[data$stimintensity == "low"] <- -0.5
data$stim_con_linear[data$stimintensity == "med"] <- 0
data$stim_con_linear[data$stimintensity == "high"] <- 0.5

# contrast code 2 quadratic
data$stim_con_quad[data$stimintensity == "low"] <- -0.33
data$stim_con_quad[data$stimintensity == "med"] <- 0.66
data$stim_con_quad[data$stimintensity == "high"] <- -0.33

    # social cude contrast
    data$social_cue[data$cuetype == "cuetype-low"] <- -0.5 # social influence task
    data$social_cue[data$cuetype == "cuetype-high"] <- 0.5 # no influence task


    stim_con1 <- "stim_con_linear"
    stim_con2 <- "stim_con_quad"
    iv1 <- "social_cue"
    dv <- signature_key

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )
    
    cooksd <- lmer_twofactor_cooksd_fix(
        data, taskname, iv1, stim_con1, stim_con2, dv,
        subject, dv_keyword, model_savefname, 'random_intercept', print_lmer_output = FALSE
    )
    influential <- as.numeric(names(cooksd)[
        (cooksd > (4 / as.numeric(length(unique(data$sub)))))
    ])
    data_screen <- data[-influential, ]
    # [ PLOT ] reordering for plots _________________________ # nolint
    data_screen$cue_name[data_screen$cuetype == "cuetype-high"] <- "high cue"
    data_screen$cue_name[data_screen$cuetype == "cuetype-low"] <- "low cue"

    data_screen$stim_name[data_screen$stimintensity == "high"] <- "high"
    data_screen$stim_name[data_screen$stimintensity == "med"] <- "med"
    data_screen$stim_name[data_screen$stimintensity == "low"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data_screen$stim_ordered <- factor(
        data_screen$stim_name,
        levels = c("low", "med", "high")
    )
    data_screen$cue_ordered <- factor(
        data_screen$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data_screen,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402
    
    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
   # calculate mean and se  
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(taskname, " - ", signature_key, " Cooksd removed")
    title <- paste(taskname, " - ", signature_key)
    xlab <- ""
    ylab <- paste(signature_key, " (degree)")
    ylim <- c(-10,60)
    dv_keyword <- signature_key
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_halfrainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
g
```




## Cognitive only: Outcome ratings & Kragel 2018
```{r echo=FALSE, message=FALSE, warning=FALSE}
# plot parameters
iv2 = "event04_actual_angle"; iv1 = signature_key
subject = "sub"
ylab = "Outcome rating"; xlab = signature_key
ggtitle = "All stimulus intensity"
alpha = 0.8; lm_method = "lm"
c.sig <- df_merge[df_merge$runtype == "runtype-cognitive",]
df_dropna <- c.sig[!is.na(c.sig[, iv1]) & !is.na(c.sig[, iv2]), ]
subjectwise_2dv <- meanSummary_2dv(
        df_dropna, c(subject), iv1, iv2
        )
    subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
    g <- ggplot(
        data = subjectwise_naomit_2dv,
        aes(
            x = .data[["DV1_mean_per_sub"]],
            y = .data[["DV2_mean_per_sub"]],
        )
    ) +
        geom_point(
          size = 2,
            alpha = alpha) +
        # geom_abline(
        #     intercept = 0, slope = 1, color = "green",
        #     linetype = "dashed", linewidth = 0.5
        # ) +
        theme(aspect.ratio = 1) +
        #scale_color_manual(values = color_scheme) +
        scale_shape_manual(values = c(16, 17)) +
        xlab(xlab) +
        ylab(ylab) +
        xlim(-0.25, 0.25) +
        ylim(0,100) +
        ggtitle(ggtitle) +
        theme(
            axis.line = element_line(colour = "grey50"),
            panel.background = element_blank(),
            plot.subtitle = ggtext::element_textbox_simple(size = 11)
        ) +
              geom_ribbon(stat = "smooth", method = lm_method, se = TRUE, alpha = 0.1,
              aes(color = NULL)) +
        geom_line(stat = "smooth", method = lm_method, alpha = 0.8, linewidth = 1.5)
    g
```

### outcome ratings * cue
```{r echo=FALSE, message=FALSE, warning=FALSE}
c.sig <- df_merge[df_merge$runtype == "runtype-cognitive",]
iv2 = "event04_actual_angle"; iv1 = signature_key
df_dropna <- c.sig[!is.na(c.sig[, iv1]) & !is.na(c.sig[, iv2]), ]
total <-
  plot_twovariable(
    df_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin=0, ymax=100, xmin=-.25, xmax=.25,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "all stimulus intensity", 
    color_scheme = c("cuetype-high" ="#011891","cuetype-low" =  "#BBBBBB"), 
    alpha = .8, fit_lm = TRUE, lm_method ="lm"
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for NPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )
```
### outcome ratings * stim * cue
```{r message=FALSE, warning=FALSE, , echo=FALSE, paged.print=FALSE}
iv2 = "event04_actual_angle"; iv1 = signature_key
group = "cuetype"; subject = "sub"
# low stimulus intensity
df_low = df_dropna[df_dropna$stimintensity == "low", ]
low <-
  plot_twovariable(
    df_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=0, ymax=100, xmin=-.25, xmax=.25,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#8EA1FF","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )

# med stimulus intensity
df_med = df_dropna[df_dropna$stimintensity == "med", ]
med <-
  plot_twovariable(
    df_med, iv1, iv2,
    group = group, subject = subject,
    ymin=0, ymax=100, xmin=-.25, xmax=.25,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#485DC8","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )

# high stimulus intensity
df_high = df_dropna[df_dropna$stimintensity == "high", ]
high <-
  plot_twovariable(
    df_high, iv1, iv2,
    group = group, subject = subject,
    ymin=0, ymax=100, xmin=-.25, xmax=.25,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#011891","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```


## Cognitive only: Expectation ratings & NPS
```{r echo=FALSE, message=FALSE, warning=FALSE}
c.sig <- df_merge[df_merge$runtype == "runtype-cognitive",]
iv1 = "event02_expect_angle"; iv2 = signature_key
df_dropna <- c.sig[!is.na(c.sig[, iv1]) & !is.na(c.sig[, iv2]), ]
total <-
  plot_twovariable(
    df_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    xmin =0, xmax = 100, ymin = -.25, ymax = .25,
    xlab = "expectation rating",
    ylab = signature_key, 
    ggtitle = "all stimulus intensity", 
    color_scheme = c("cuetype-high" ="#011891","cuetype-low" =  "#BBBBBB"), 
    alpha = .8, fit_lm = TRUE, lm_method = "lm"
  )
total + labs(title =paste0("task-",taskname, " - What is the pattern for ", signature_key,"dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n"))
```


```{r , echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv1 = "event02_expect_angle"; iv2 = signature_key
group = "cuetype"; subject = "sub"
xlab = "expectation rating"; ylab = signature_key
xmin =0; xmax = 100; ymin = -.25; ymax = .25
# low stimulus intensity
df_low = df_dropna[df_dropna$stimintensity == "low", ]
low <-
  plot_twovariable(
    df_low, iv1 , iv2,
    group = group, subject = subject,
    xmin, xmax, ymin, ymax,
    xlab,  ylab,
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#8EA1FF","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )

# med stimulus intensity
df_med = df_dropna[df_dropna$stimintensity == "med", ]
med <-
  plot_twovariable(
    df_med, iv1, iv2,
    group = group, subject = subject,
    xmin, xmax, ymin, ymax,
    xlab = "expectation rating", ylab = signature_key,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#485DC8","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )

# high stimulus intensity
df_high = df_dropna[df_dropna$stimintensity == "high", ]
high <-
  plot_twovariable(
    df_high, iv1, iv2,
    group = group, subject = subject,
    xmin, xmax, ymin, ymax,
    xlab = "expectation rating", ylab = signature_key,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#011891","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm"
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n Expect/Outcome linear relationship differs as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```





