# [fMRI] Single trial correlation between cue and stim {#ch38_singletrial_corr}

```
author: "Heejung Jung"
date: "2023-03-04"
```

## What is the purpose of this notebook? {.unlisted .unnumbered}

* Identify the correlation between cue and stimulus phase single trial nifti files
* On discovery, I've calculated the correlation via script: `scripts/step10_nilearn/singletrialLSS/step07_corr_cue_stim.py`


```{r libraries_nps_stim, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(psych)
library(reshape)
library(PupillometryR)
library(dplyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summaryse.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulatedata.R")
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```


```{r function::summary_for_plots_pvc, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
summary_for_plots_PVC <- function(df, groupwise_measurevar, subject_keyword, model_iv1, model_iv2, dv) {
    #  [ PLOT ] calculate mean and se  _________________________
    subjectwise <- meanSummary(
        df,
        c(subject_keyword, model_iv1, model_iv2), dv
    )
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = groupwise_measurevar,
        withinvars = c(model_iv1, model_iv2), idvar = subject_keyword
    )

    return(list(subjectwise,groupwise))
}
```

```{r function::simple_contrasts_singletrial, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
simple_contrasts_singletrial <- function(df) {
# [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
df$stim_factor <- factor(df$stim)

# contrast code 1 linear
df$stim_con_linear[df$stimintensity == "low"] <-  -0.5
df$stim_con_linear[df$stimintensity == "med"] <-  0
df$stim_con_linear[df$stimintensity == "high"] <-  0.5

# contrast code 2 quadratic
df$stim_con_quad[df$stimintensity == "low"] <-  -0.33
df$stim_con_quad[df$stimintensity == "med"] <-  0.66
df$stim_con_quad[df$stimintensity == "high"] <-  -0.33

# cue contrast
df$cue_con[df$cuetype == "cuetype-low"] <-  -0.5 # social influence task
df$cue_con[df$cuetype == "cuetype-high"] <-  0.5 # no influence task

df$stim_ordered <- factor(
        df$stimintensity,
        levels = c("low", "med", "high")
    )

df$cue_name[df$cuetype == "cuetype-low"] <- "low"
df$cue_name[df$cuetype == "cuetype-high"] <- "high"

df$cue_ordered <- factor(
        df$cue_name,
        levels = c("low", "high")
    )
return(df)
}
```

```{r function::NPS_lineplot_34, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
two_factor_lineplot <-
  function(df, iv1, iv2, mean, error, xlab, ylab) {
    g <- ggplot(
      data = df,
      aes(
        x = .data[[iv1]],
        y = .data[[mean]],
        group = factor(.data[[iv2]]),
        color = factor(.data[[iv2]])
      ),
      cex.lab = 1.5,
      cex.axis = 2,
      cex.main = 1.5,
      cex.sub = 1.5
    ) +
      geom_errorbar(aes(
        ymin = (.data[[mean]] - .data[[error]]),
        ymax = (.data[[mean]] + .data[[error]])
      ), width = .1) +
      geom_line() +
      geom_point() +
      ggtitle(ggtitle) +
      xlab(xlab) +
      ylab(ylab) +
      #scale_color_manual(values = color) +
      theme_classic() +
      
      theme(aspect.ratio = .6) +
      expand_limits(x = 3.25) +
      #guides(fill = "none") +
      #guides(color = TRUE) +
      #guides(fill = guide_legend(title = "title")) +
      #scale_fill_manual(values = color) +
      scale_color_manual("",
                         values =  c(
                           "pain" = "#941100",
                           "vicarious" = "#008F51",
                           "cognitive" = "#011891"
                         )) +
      theme(
        legend.position = c(.99, .99),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      theme(legend.key = element_rect(fill = "white", colour = "white")) +
      theme_bw()
    
    return(g)
  }
```

```{r}
main_dir = dirname(dirname(getwd()))
main_dir = "/Users/h/Dropbox/projects_dropbox/social_influence_analysis"
analysis_dir = 
single_trial_dir = file.path(main_dir, 'analysis/fmri/nilearn/deriv04_corrcuestim')
```


```{r include=FALSE}
combined_se_calc_cooksd <- data.frame()
subject_varkey = 'sub'; dv = 'dotprod'
taskname = "vicarious"
for (taskname in c("pain", "vicarious", "cognitive")) {
filename <- paste("*_runtype-", taskname, "_desc-singletrialcorrelation_x-cue_y-stim.tsv", sep = "")
common_path <- Sys.glob(file.path(single_trial_dir, filename
  ))

exclude <- "sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0007|sub-0008|sub-0011|sub-0013|sub-0014|sub-0016|sub-0017|sub-0019|sub-0020|sub-0021|sub-0023|sub-0024|sub-0025|sub-0026|sub-0035|sub-0040|sub-0041|sub-0059|sub-0064|sub-0066|sub-0069|sub-0070|sub-0074|sub-0075|sub-0076|sub-0077|sub-0079|sub-0083|sub-0084|sub-0088|sub-0089|sub-0103|sub-0111|sub-0112|sub-0131"

filter_path <- common_path[!str_detect(common_path, pattern = exclude)]

df <- do.call("rbind", lapply(filter_path, FUN = function(files) {
    as.data.frame(read.table(file = files, sep = '\t', header = TRUE))
  }))

is.nan.data.frame <- function(x) {
    do.call(cbind, lapply(x, is.nan))
  }
df[is.nan(df)] <- NA
df[, "sub"] <- factor(df[, subject_varkey])

# B. plot expect rating NA ___________________________________________________
if (hasArg(dv)){
  df_expect_NA <- aggregate(df[, dv], list(df$subject), function(x) sum(is.na(x)))
  df_remove_NA <- df[!is.na(df[dv]), ]
  df <- as.data.frame(df_remove_NA)}

summary(lmer(corr ~ 1 + (1|sub), data = df))



subject <- "sub"
dv <- "corr"
subjectwise_mean <- "mean_per_sub"
    ## summary statistics
subjectwise <- meanSummary(df, c(subject,"ses", "run"), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = subjectwise_mean, # variable created from above
        withinvars = c("ses", "run"), #NULL,#c(subject), # iv
        idvar = "sub"
    )
groupwise$task <- taskname
combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, groupwise)
}
```

## plot correlation (one-sample-t)


## Lineplot
```{r echo=FALSE}
library(ggpubr)
DATA = as.data.frame(combined_se_calc_cooksd)
color = c( "#4575B4", "#D73027")
LINEIV1 = "run"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "se"
dv_keyword = "actual"
p1 = plot_lineplot_onefactor(DATA, 'pain', 
               LINEIV1, MEAN, ERROR, color, xlab = "Runs" , ylab= "Correlation between \ncue and stimulus", ggtitle = 'pain' )
p2 = plot_lineplot_onefactor(DATA,'vicarious', 
               LINEIV1, MEAN, ERROR, color,xlab = "Runs" , ylab= "Correlation between \ncue and stimulus",ggtitle = 'vicarious')
p3 = plot_lineplot_onefactor(DATA, 'cognitive', 
               LINEIV1, MEAN, ERROR, color,xlab = "Runs" , ylab= "Correlation between \ncue and stimulus",ggtitle = 'cognitive')
ggpubr::ggarrange(p1,p2,p3,ncol = 3, nrow = 1, common.legend = TRUE,legend = "bottom")

```


