# fMRI :: single trial QC {#singletrialqc}

## What is the purpose of this notebook? {.unlisted .unnumbered}

- I started this analysis because the single trial models and the univariate maps seemed different. The NPS extracted values are non-significant for the dummy univariate maps; the single trials are significant. Also, the activation for the pain dummy contrast between high and low stimulus intensity is almost non-significant. ~/social_influence_analysis/scripts/step04_SPM/6conditions/6cond_stimlinear_dummy.html
- Here, I test whether the order of single trials and session order are significantly different in terms of NPS values. If so, this systematic difference may indicate a modeling difference across runs.

:::: {.refbox}

- https://aosmith.rbind.io/2019/04/15/custom-contrasts-emmeans/
- https://aosmith.rbind.io/2019/04/15/custom-contrasts-emmeans#:~:text=Building%20a%20custom%20contrast%20involves,0%20to%20the%20other%20groups.
  ::::

```{r, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(psych)
library(reshape)
library(dplyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(plyr)
library(ggpubr)
library(r2mlm)
library(effectsize)
library(devtools)
options(es.use_symbols = TRUE) # get nice symbols when printing! (On Windows, requires R >= 4.2.0)
library(EMAtools)
library(emmeans)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(DT)
library(raincloudplots)
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/R_rainclouds.R")
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/summarySE.R")

devtools::source_url("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
main_dir = dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, "scripts/step02_R/utils"),
                          pattern="*.R",
                          full.names=TRUE,
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
# file.sources = list.files(c("https://raw.githubusercontent.com/jungheejung/cue_expectancy/main/scripts/step02_R/utils"), pattern="*.R", full.names=TRUE, ignore.case=TRUE)
# sapply(file.sources,source,.GlobalEnv)
```

## functions

```{r function::summary_for_plots_pvc, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
summary_for_plots_PVC <- function(df, groupwise_measurevar, subject_keyword, model_iv1, model_iv2, dv) {
    #  [ PLOT ] calculate mean and se  _________________________
    subjectwise <- meanSummary(
        df,
        c(subject_keyword, model_iv1, model_iv2), dv
    )
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = groupwise_measurevar,
        withinvars = c(model_iv1, model_iv2), idvar = subject_keyword
    )

    return(list(subjectwise,groupwise))
}
```

```{r function::simple_contrasts_singletrial, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
simple_contrasts_singletrial <- function(df) {
# [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
df$STIM <- factor(df$stim)

# contrast code 1 linear
df$STIM_linear[df$stimintensity == "low"] <-  -0.5
df$STIM_linear[df$stimintensity == "med"] <-  0
df$STIM_linear[df$stimintensity == "high"] <-  0.5

# contrast code 2 quadratic
df$STIM_quadratic[df$stimintensity == "low"] <-  -0.33
df$STIM_quadratic[df$stimintensity == "med"] <-  0.66
df$STIM_quadratic[df$stimintensity == "high"] <-  -0.33

# cue contrast
df$CUE_high_gt_low[df$cuetype == "cuetype-low"] <-  -0.5 # social influence task
df$CUE_high_gt_low[df$cuetype == "cuetype-high"] <-  0.5 # no influence task

df$stim_ordered <- factor(
        df$stimintensity,
        levels = c("low", "med", "high")
    )

df$cue_name[df$cuetype == "cuetype-low"] <- "low"
df$cue_name[df$cuetype == "cuetype-high"] <- "high"

df$cue_ordered <- factor(
        df$cue_name,
        levels = c("low", "high")
    )
return(df)
}
```

```{r function::NPS_lineplot_34, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
two_factor_lineplot <-
  function(df, iv1, iv2, mean, error, xlab, ylab) {
    g <- ggplot(
      data = df,
      aes(
        x = .data[[iv1]],
        y = .data[[mean]],
        group = factor(.data[[iv2]]),
        color = factor(.data[[iv2]])
      ),
      cex.lab = 1.5,
      cex.axis = 2,
      cex.main = 1.5,
      cex.sub = 1.5
    ) +
      geom_errorbar(aes(
        ymin = (.data[[mean]] - .data[[error]]),
        ymax = (.data[[mean]] + .data[[error]])
      ), width = .1) +
      geom_line() +
      geom_point() +
      ggtitle(ggtitle) +
      xlab(xlab) +
      ylab(ylab) +
      #scale_color_manual(values = color) +
      theme_classic() +

      theme(aspect.ratio = .6) +
      expand_limits(x = 3.25) +
      #guides(fill = "none") +
      #guides(color = TRUE) +
      #guides(fill = guide_legend(title = "title")) +
      #scale_fill_manual(values = color) +
      scale_color_manual("",
                         values =  c(
                           "pain" = "#941100",
                           "vicarious" = "#008F51",
                           "cognitive" = "#011891"
                         )) +
      theme(
        legend.position = c(.99, .99),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      theme(legend.key = element_rect(fill = "white", colour = "white")) +
      theme_bw()

    return(g)
  }
```

## load data {.unlisted .unnumbered}

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# Load behavioral data
main_dir = dirname(dirname(getwd()))
print(main_dir)
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
taskname = '*'
subject_varkey <- "src_subject_id"
iv <- "param_stimulus_type";
iv_keyword <- "stim";
dv <- "event04_actual_angle"; dv_keyword <- "outcome"
exclude <- "sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0007|sub-0008|sub-0013|sub-0016|sub-0017|sub-0019|sub-0020|sub-0021|sub-0025|sub-0075"

p.df <- df_load_beh(datadir, taskname = "pain", subject_varkey, iv, dv, exclude)
v.df <- df_load_beh(datadir, taskname = "vicarious", subject_varkey, iv, dv, exclude)
c.df <- df_load_beh(datadir, taskname = "cognitive", subject_varkey, iv, dv, exclude)

p.df2= p.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_p <- p.df2 %>%
  group_by(src_subject_id, session_id, param_run_num) %>%
  mutate(trial_index = row_number(param_run_num))

v.df2= v.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_v <- v.df2 %>%
  group_by(src_subject_id, session_id, param_run_num) %>%
  mutate(trial_index = row_number(param_run_num))

c.df2= c.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number()-1)
data_c <- c.df2 %>%
  group_by(src_subject_id, session_id, param_run_num) %>%
  mutate(trial_index = row_number(param_run_num) )

p.sub <- data_p[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
v.sub <- data_v[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
c.sub <- data_c[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
# sub, ses, run, runtype, event, trial, cuetype, stimintensity
# src_subject_id, session_id, param_run_num, param_task_name, event02_expect_angle, param_cue_type, param_stimulus_type, event04_actual_angle
pvc.sub = rbind(p.sub, v.sub, c.sub)

```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
pvc.sub$trial_ind <- pvc.sub$trial_index -1
pvc.sub$sub <- sprintf("sub-%04d", pvc.sub$src_subject_id)
pvc.sub$ses <- sprintf("ses-%02d", pvc.sub$session_id)
pvc.sub$run <- sprintf("run-%02d", pvc.sub$param_run_num)
pvc.sub$runtype <- sprintf("runtype-%s", pvc.sub$param_task_name)
pvc.sub$trial <- sprintf("trial-%03d", pvc.sub$trial_ind)
pvc.sub[c('cue', 'DEPc')]  <- str_split_fixed(pvc.sub$param_cue_type , '_', 2)
pvc.sub$cuetype <- sprintf("cuetype-%s", pvc.sub$cue)
pvc.sub[c('stimintensity', 'DEP')]  <- str_split_fixed(pvc.sub$param_stimulus_type , '_', 2)

# merge
pvc.beh <- pvc.sub[,c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity","event02_expect_angle", "event04_actual_angle")]
df_merge <- merge(pvc.sub, pvc.beh,
                  by.x = c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity"),
                  by.y = c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity")
                  )

```

## trial-order wise {.unlisted .unnumbered}

The purpose is to check whether trial orders have a systematic differences in average BOLD intensity, or more specifically, average NPS responses.
As we can see, the first trials always have higher NPS responses.
TODO: run a stats test to see if there a significant difference

```{r message=FALSE, warning=FALSE, include=FALSE}

# Step 1: Common parameters
# step 1: load data
for (signature_key in c("NPSpos")) {
     #c("NPS", "NPSpos", "NPSneg", "VPS", #"VPSnooccip", "ThermalPain", "MechPain", "GeneralAversive", "AversiveVisual"
                      #  "ZhouVPS", "PINES",  "GSR", "GeuterPaincPDM")) {
  dv_keyword = signature_key
  signature_name = signature_key
  # step 1: common parameters _______
  main_dir <- dirname(dirname(getwd()))

  analysis_folder  = paste0("model39_iv-task-stim_dv-", signature_key)

  sig_name <-
    Sys.glob(file.path(
      main_dir,
      "analysis/fmri/nilearn/signature_extract",
      paste0(
        "signature-",
        signature_key,
        "_sub-all_runtype-pvc_event-stimulus.tsv"
      )
    )) # nolint
  print(sig_name)
  analysis_dir <-
    file.path(main_dir,
              "analysis",
              "mixedeffect",
              analysis_folder,
              as.character(Sys.Date())) # nolint
  dir.create(analysis_dir,
             showWarnings = FALSE,
             recursive = TRUE)
  savedir <- analysis_dir

  # step 2: load data
  df = read.csv(sig_name)
  sig_df = df %>% separate(
    singletrial_fname,
    sep = "_",
    c(
      "sub",
      "ses",
      "run",
      "runtype",
      "event",
      "trial",
      "cuetype",
      "stimintensity"
    )
  )
  sig_df = sig_df %>% separate(
    stimintensity,
    into = c(NA, "stimintensity"),
    extra = "drop",
    fill = "left"
  )
  pvc <- simple_contrasts_singletrial(sig_df)
  pvc$task[pvc$runtype == "runtype-pain"] <- "pain"
  pvc$task[pvc$runtype == "runtype-vicarious"] <- "vicarious"
  pvc$task[pvc$runtype == "runtype-cognitive"] <- "cognitive"
  pvc$task <- factor(pvc$task)


  # step 3: parameters

  taskname = "all"
  plot_keyword = "stimulusintensity"
  ggtitle_phrase =  "(3 tasks x 3 trial order)"

  pvc$task = factor(pvc$task)
  plot_keys <- list(
    sub_mean = "mean_per_sub",
    group_mean = "mean_per_sub_norm_mean",
    legend_keyword = "trial index",
    se = "se",
    subject = "sub",
    ggtitle = paste0(
      str_to_title(signature_key),
      " dot product: ",
      str_to_title(taskname),
      ' ',
      ggtitle_phrase,
      " (N = ",
      length(unique(pvc$sub)),
      ")"
    ),
    title = paste0(
      str_to_title(signature_key),
      " - ",
      str_to_title(plot_keyword)
    ),
    xlab = "",
    ylab = paste(signature_key, " (dot product)"),
    ylim = c(-250, 500)
  )

  # step 4: within between summary
  groupwise <- data.frame()
  subjectwise <- data.frame()
  summary <- summary_for_plots_PVC(
    df = pvc,
    # taskname = taskname,
    groupwise_measurevar = plot_keys$sub_mean,
    # "mean_per_sub",
    subject_keyword = plot_keys$subject,
    # "sub",
    model_iv1 =  "task",
    model_iv2 =  "trial",
    dv = signature_key #"NPSpos"
  )
  subjectwise <<- as.data.frame(summary[[1]])
  groupwise <<- as.data.frame(summary[[2]])
  if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
    plot_keys$color <- c("#1B9E77", "#D95F02", "#D95F02")
  } else {
    plot_keys$color <- c("#FF2A00","#E82817","#D1252E","#B92346","#A2215D","#8B1F74","#741C8B","#5D1AA2","#4618B9","#2E16D1","#1713E8","#0011FF")
  }

  # step 5: plot

  iv2 = "trial"
  iv1 = "task"
  taskname = "all"
  if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
    color <- c("#1B9E77", "#D95F02", "#D95F02")
  } else {
    color <- c("#FF2A00","#E82817","#D1252E","#B92346","#A2215D","#8B1F74","#741C8B","#5D1AA2","#4618B9","#2E16D1","#1713E8","#0011FF")
  }
  subject_mean <- "mean_per_sub"
  sub_mean = subject_mean
  group_mean <- "mean_per_sub_norm_mean"
  se <- "se"
  ylim <- c(-25, 26)
  subject <- "sub"
  ggtitle_phrase <-  "(3 tasks x 12 trial order)"
  ggtitle <-
    paste0(
      str_to_title(signature_name),
      " dot product: ",
      str_to_title(taskname),
      ' ',
      ggtitle_phrase,
      " (N = ",
      length(unique(pvc$sub)),
      ")"
    )

  title <-
    paste0(str_to_title(dv_keyword),
           " - ",
           str_to_title(plot_keys$legend_keyword))
  xlab <- ""
  plot_keyword = "trial"
  ylab <- paste(signature_name, " (dot product)")
  plot2_savefname <- file.path(
    analysis_dir,
    paste(
      "signature_task-",
      taskname,
      "_event-",
      plot_keyword,
      "_dv-",
      signature_key,
      "_",
      as.character(Sys.Date()),
      ".png",
      sep = ""
    )
  )
  p <- plot_halfrainclouds_twofactorthick(
    subjectwise,    groupwise,
    iv1,    iv2,
    subject_mean,    group_mean,
    se,    subject,
    ggtitle,    title,
    xlab,    ylab,
    taskname,
    ylim,    w = 20,    h = 6,
    dv_keyword,    color,    plot2_savefname
  )


  p
}
```

```{r}
p
```

### line plots {.unlisted .unnumbered}

```{r echo=FALSE, warning=FALSE}

g <- plot_lineplot_twofactor(groupwise,
                        iv1 = "trial", iv2 = "task",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c( 'pain' = "#941100", 'cognitive' = "#110094", 'vicarious' = '#009411'), ggtitle = "NPS (positive weights) & single trial dotproduct \nas a function of task and trial order",
                        xlab = "Trial order", ylab = "NPSpos (dot product)")
g +  theme(legend.position = "bottom")
g
```

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
addSmallLegend <- function(myPlot, pointSize = 0.5, textSize = 3, spaceLegend = 0.1) {
    myPlot +
        guides(shape = guide_legend(override.aes = list(size = pointSize)),
               color = guide_legend(override.aes = list(size = pointSize))) +
        theme(legend.title = element_text(size = textSize),
              legend.text  = element_text(size = textSize),
              legend.key.size = unit(spaceLegend, "lines"))
}

# Apply on original plot
addSmallLegend(p)
```

### linear model:

Q. Is this trial effect only prominent in the pain task?
Q. Is this trial effect only present for the first trial of the run?

```{r}
pvc$trial_num <- as.numeric(as.factor(pvc$trial))
model <-  lmer(NPSpos ~ task * trial_num + (1|sub), data = pvc)
Anova(model, type = "III")
```

```{r eval=FALSE, include=FALSE}
# Assuming you have a model object named 'model' resulting from your analysis
# Assuming your categorical variable is named 'your_categorical_variable'

# # Specify the custom contrast
# custom_contrast <- c(11, -1, -1, -1, -1, -1, -1, -1, -1, -1, -1, -1)
# pvc$trial <- as.numeric(as.factor(pvc$trial))
# # Apply the custom contrast using emmeans
# emmeans_results <- emmeans(model, ~ trial_con,
#                            at = list(trial = custom_contrast))
#
# # Print the emmeans results
# print(emmeans_results)

```

```{r echo=TRUE}
pain = pvc[pvc$runtype == 'runtype-pain',]
pain$trialorder = as.numeric(factor(pain$trial))

# helmert_contrasts
pain$trialorder_levels <- factor(pain$trialorder,
                                   levels=c(1,2,3,4,5,6,7,8,9,10,11,12))
pain$trial_con  = factor(pain$trialorder_levels)

# contrasts(pain$trial_con) <- contrast_list
model = lmer(NPSpos ~ trial_con + (trial_con|sub), data = pain) #, contrasts = (trial_con = contrast_list))
summary(model)

```

### trial order emmeans

```{r echo=FALSE}
# https://aosmith.rbind.io/2019/04/15/custom-contrasts-emmeans/
emm_options(pbkrtest.limit = 6024, lmerTest.limit = 6024)
emm <- emmeans(model,specs = ~trial_con, pbkrtest.limit = 4000)
t1 = c(1,0,0,0,0,0,0,0,0,0,0,0)
tother = c(0,1/11,1/11,1/11,1/11,1/11,1/11,1/11,1/11,1/11,1/11,1/11)

early =c(0,1/5,1/5,1/5,1/5,1/5,0,0,0,0,0,0)
late = c(0,0,0,0,0,0,1/6,1/6,1/6,1/6,1/6,1/6)

t2 = c(0,1,0,0,0,0,0,0,0,0,0,0)
tother2 =  c(0,0,1/10,1/10,1/10,1/10,1/10,1/10,1/10,1/10,1/10,1/10)

t3 = c(0,0,1,0,0,0,0,0,0,0,0,0)
tother3 =  c(0,0,0,1/9,1/9,1/9,1/9,1/9,1/9,1/9,1/9,1/9)

t4 = c(0,0,0,1,0,0,0,0,0,0,0,0)
tother4 =  c(0,0,0,0,1/8,1/8,1/8,1/8,1/8,1/8,1/8,1/8)

t5 = c(0,0,0,0,1,0,0,0,0,0,0,0)
tother5 =  c(0,0,0,0,0,1/7,1/7,1/7,1/7,1/7,1/7,1/7)

t6 = c(0,0,0,0,0,1,0,0,0,0,0,0)
tother6 =  c(0,0,0,0,0,0,1/6,1/6,1/6,1/6,1/6,1/6)

t7 = c(0,0,0,0,0,0,1,0,0,0,0,0)
tother7 =  c(0,0,0,0,0,0,0,1/5,1/5,1/5,1/5,1/5)

t8 = c(0,0,0,0,0,0,0,1,0,0,0,0)
tother8 =  c(0,0,0,0,0,0,0,0,1/4,1/4,1/4,1/4)

t9 = c(0,0,0,0,0,0,0,0,1,0,0,0)
tother9 =  c(0,0,0,0,0,0,0,0,0,1/3,1/3,1/3)

t10 = c(0,0,0,0,0,0,0,0,0,1,0,0)
tother10 =  c(0,0,0,0,0,0,0,0,0,0,1/2,1/2)

t11 = c(0,0,0,0,0,0,0,0,0,0,1/2,0)
tother11 =  c(0,0,0,0,0,0,0,0,0,0,0,-1/2)

t12 = c(0,0,0,0,0,0,0,0,0,0,0,1)
tother12 =  c(0,1/10,1/10,1/10,1/10,1/10,1/10,1/10,1/10,1/10,1/10,0)

contrast(emm, method = list("first trial vs others" = t1 - tother,
                            "early 6 trials vs later 6 trials" = early-late,
                            "2nd trial vs others" = t2 - tother2,
                            "3rd trial vs others" = t3 - tother3,
                            "4th trial vs others" = t4 - tother4,
                            "5th trial vs others" = t5 - tother5,
                            "6th trial vs others" = t6 - tother6,
                            "7th trial vs others" = t7 - tother7,
                            "8th trial vs others" = t8 - tother8,
                            "9th trial vs others" = t9 - tother9,
                            "10th trial vs others" = t10 - tother10,
                            "11th trial vs 12th trial" = t11 - tother11,
                            "1st trial vs 2nd trial" = t1 - t2,
                            "12trial vs 2-11th trial" = t12-tother12),
         adjust = "mvt")
# %>%
  # confint()
# contrast(emm, method =  "helmert",  adjust = "bonferroni")
```

```
Discussion:
* 1st trial has high NPS values compared to other consecutive trials, across participants (t(262) = 7.197, p < .0001)
* The next thought was that there would be a linear trend. However, note that 2nd trial is not significantly different from the other trials, t(294) = -0.232, N.S. In other words, there is not linear detrending effect across trials.
* The last and 2nd-to-last trial (11th trial and 12th trial) are significantly different, t(104) = 9.645, p < .0001.
* However, it's not like the last trial is different from all others. 12th trial is not significantly different from the average of 2-11 trials, t(531) = -1.983, N.S.
```

## run wise {.unlisted .unnumbered}

```{r message=FALSE, warning=FALSE, include=FALSE}

# Step 1: Common parameters
# step 1: load data
for (signature_key in c("NPSpos")) {
     #c("NPS", "NPSpos", "NPSneg", "VPS", #"VPSnooccip", "ThermalPain", "MechPain", "GeneralAversive", "AversiveVisual"
                      #  "ZhouVPS", "PINES",  "GSR", "GeuterPaincPDM")) {
  dv_keyword = signature_key
  signature_name = signature_key
  # step 1: common parameters _______
  main_dir <- dirname(dirname(getwd()))

  analysis_folder  = paste0("model35_iv-task-stim_dv-", signature_key)

  sig_name <-
    Sys.glob(file.path(
      main_dir,
      "analysis/fmri/nilearn/signature_extract",
      paste0(
        "signature-",
        signature_key,
        "_sub-all_runtype-pvc_event-stimulus.tsv"
      )
    )) # nolint
  print(sig_name)
  analysis_dir <-
    file.path(main_dir,
              "analysis",
              "mixedeffect",
              analysis_folder,
              as.character(Sys.Date())) # nolint
  dir.create(analysis_dir,
             showWarnings = FALSE,
             recursive = TRUE)
  savedir <- analysis_dir

  # step 2: load data
  df = read.csv(sig_name)
  sig_df = df %>% separate(
    singletrial_fname,
    sep = "_",
    c(
      "sub",
      "ses",
      "run",
      "runtype",
      "event",
      "trial",
      "cuetype",
      "stimintensity"
    )
  )
  sig_df = sig_df %>% separate(
    stimintensity,
    into = c(NA, "stimintensity"),
    extra = "drop",
    fill = "left"
  )
  pvc <- simple_contrasts_singletrial(sig_df)
  pvc$task[pvc$runtype == "runtype-pain"] <- "pain"
  pvc$task[pvc$runtype == "runtype-vicarious"] <- "vicarious"
  pvc$task[pvc$runtype == "runtype-cognitive"] <- "cognitive"
  pvc$task <- factor(pvc$task)
  # ____________________________________________________________________________
  # figure out which run was first vs second
  pvc$run_num = as.numeric(as.factor(pvc$run))
  pvc <- pvc %>%
  dplyr::group_by(sub, ses, runtype) %>%
  dplyr::mutate(mean_run = mean(run_num))
  # compared to mean_run, is the run_num smaller or larger?
  pvc$formerlatter_run <- ifelse(pvc$mean_run >= pvc$run_num , "former", "latter")
  pvc$ses_run <- interaction( pvc$formerlatter_run, pvc$ses,sep = "_")

  # step 3: parameters _________________________________________________________

  taskname = "all"
  plot_keyword = "stimulusintensity"
  ggtitle_phrase =  "(3 tasks x 3 stimulus intensity)"

  pvc$task = factor(pvc$task)
  plot_keys <- list(
    sub_mean = "mean_per_sub", group_mean = "mean_per_sub_norm_mean",
    legend_keyword = "ses_run",
    se = "se", subject = "sub",
    ggtitle = paste0(
      str_to_title(signature_key)," dot product: ",str_to_title(taskname),' ',ggtitle_phrase," (N = ",length(unique(pvc$sub)),")"
    ),
    title = paste0(
      str_to_title(signature_key)," - ",str_to_title(plot_keyword)
    ),
    xlab = "",
    ylab = paste(signature_key, " (dot product)"),
    ylim = c(-250, 500)
  )

  # step 4: within between summary
  groupwise <- data.frame()
  subjectwise <- data.frame()
  summary <- summary_for_plots_PVC(
    df = pvc,
    groupwise_measurevar = plot_keys$sub_mean,
    subject_keyword = plot_keys$subject,
    model_iv1 =  "task",
    model_iv2 =  "ses_run",
    dv = signature_key #"NPSpos"
  )
  subjectwise <<- as.data.frame(summary[[1]])
  groupwise <<- as.data.frame(summary[[2]])
  if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
    plot_keys$color <- c("#1B9E77", "#D95F02", "#D95F02")
  } else {
    plot_keys$color <- c("#FFD500","#D3A33C","#7C02FF","#490098","#D618B4","#A40086")
  }

  # step 5: plot

  iv2 = "ses_run"
  iv1 = "task"
  taskname = "all"
  if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
    color <- c("#1B9E77", "#D95F02", "#D95F02")
  } else {
    color <- c("#FFD500","#D3A33C","#7C02FF","#490098","#D618B4","#A40086")
  }
  subject_mean <- "mean_per_sub"
  sub_mean = subject_mean
  group_mean <- "mean_per_sub_norm_mean"
  se <- "se"
  ylim <- c(-25, 26)
  subject <- "sub"
  ggtitle_phrase <-  "(3 tasks x 6 ses_run)"
  ggtitle <-
    paste0(
      str_to_title(signature_name),
      " dot product: ",str_to_title(taskname),
      ' ',ggtitle_phrase," (N = ",length(unique(pvc$sub)),
      ")"
    )

  title <-
    paste0(str_to_title(dv_keyword),
           " - ",
           str_to_title(plot_keys$legend_keyword))
  xlab <- ""
  plot_keyword = "trial"
  ylab <- paste(signature_name, " (dot product)")
  plot2_savefname <- file.path(
    analysis_dir,
    paste(
      "signature_task-",      taskname,
      "_event-",      plot_keyword,
      "_dv-",      signature_key,
      "_",      as.character(Sys.Date()),
      ".png",
      sep = ""
    )
  )
  s <- plot_halfrainclouds_twofactor(
    subjectwise,
    groupwise,
    iv1,
    iv2,
    subject_mean,
    group_mean,
    se,
    subject,
    ggtitle,
    title,
    xlab,
    ylab,
    taskname,
    ylim,
    w = 30,
    h = 6,
    dv_keyword,
    color,
    plot2_savefname
  )
  s
}
```

```{r echo=FALSE, warning=TRUE}
s
```

```{r echo=FALSE, warning=FALSE}

g <- plot_lineplot_twofactor(groupwise,
                        iv1 = "ses_run", iv2 = "task",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c( 'pain' = "#941100", 'cognitive' = "#110094", 'vicarious' = '#009411'), ggtitle = "NPS (positive weights) & single trial dotproduct \nas a function of task and trial order",
                        xlab = "Session and Run order", ylab = "NPSpos (dot product)")
g +  theme(legend.position = "bottom")
g
```

### linear model: run/ses wise

```
lmer(NPSpos ~ task*ses_run_con + (task|sub), data = pvc)
```

```{r}
pvc$ses_run_con <- as.factor(pvc$ses_run)
contrasts(pvc$ses_run_con) = contr.poly(6)
model_run <-  lmer(NPSpos ~ task*ses_run_con + (task|sub), data = pvc)
Anova(model_run, type = "III")
# summary(model_run)
```

### emmeans run wise

```{r}
# https://aosmith.rbind.io/2019/04/15/custom-contrasts-emmeans/
emm_options(pbkrtest.limit = 12000, lmerTest.limit = 12000)
emm <- emmeans(model_run,specs = ~task:ses_run_con, pbkrtest.limit = 12000)

painLinear = c(0,0,0,0,0,0,-0.5976143,-0.3585686, -0.1195229,0.1195229,0.3585686,0.5976143,0,0,0,0,0,0)

contrast(emm, method = list("painlinear" = painLinear),
         adjust = "mvt")
```
