# [fMRI] NPS \~ singletrial {#ch40_EndersTofighi}

---

title: "[fMRI] NPS ~ singletrial"
output:
html_document:
toc: true
toc_float:
collapsed: false
smooth_scroll: false

---

## What is the purpose of this notebook? {.unlisted .unnumbered}

- Here, I model NPS dot products as a function of cue, stimulus intensity and expectation ratings.
- One of the findings is that low cues lead to higher NPS dotproducts in the high intensity group, and that this effect becomes non-significant across sessions.
- 03/23/2023: For now, I'm grabbing participants that have complete data, i.e. 18 runs, all three sessions.

```{r libraries_nps_stim, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(psych)
library(reshape)
library(dplyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(plyr)
library(ggpubr)
library(r2mlm)
library(effectsize)
library(devtools)
options(es.use_symbols = TRUE) # get nice symbols when printing! (On Windows, requires R >= 4.2.0)
library(EMAtools)
library(emmeans)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(DT)
library(raincloudplots)
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/R_rainclouds.R")
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/summarySE.R")

devtools::source_url("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
main_dir = dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, "scripts/step02_R/utils"),
                          pattern="*.R",
                          full.names=TRUE,
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
# file.sources = list.files(c("https://raw.githubusercontent.com/jungheejung/cue_expectancy/main/scripts/step02_R/utils"), pattern="*.R", full.names=TRUE, ignore.case=TRUE)
# sapply(file.sources,source,.GlobalEnv)
```

```{r function::summary_for_plots_pvc, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
summary_for_plots_PVC <- function(df, groupwise_measurevar, subject_keyword, model_iv1, model_iv2, dv) {
    #  [ PLOT ] calculate mean and se  _________________________
    subjectwise <- meanSummary(
        df,
        c(subject_keyword, model_iv1, model_iv2), dv
    )
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = groupwise_measurevar,
        withinvars = c(model_iv1, model_iv2), idvar = subject_keyword
    )

    return(list(subjectwise,groupwise))
}
```

```{r function::simple_contrasts_singletrial, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
simple_contrasts_singletrial <- function(df) {
# [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
df$STIM <- factor(df$stim)

# contrast code 1 linear
df$STIM_linear[df$stimintensity == "low"] <-  -0.5
df$STIM_linear[df$stimintensity == "med"] <-  0
df$STIM_linear[df$stimintensity == "high"] <-  0.5

# contrast code 2 quadratic
df$STIM_quadratic[df$stimintensity == "low"] <-  -0.33
df$STIM_quadratic[df$stimintensity == "med"] <-  0.66
df$STIM_quadratic[df$stimintensity == "high"] <-  -0.33

# cue contrast
df$CUE_high_gt_low[df$cuetype == "cuetype-low"] <-  -0.5 # social influence task
df$CUE_high_gt_low[df$cuetype == "cuetype-high"] <-  0.5 # no influence task

df$stim_ordered <- factor(
        df$stimintensity,
        levels = c("low", "med", "high")
    )

df$cue_name[df$cuetype == "cuetype-low"] <- "low"
df$cue_name[df$cuetype == "cuetype-high"] <- "high"

df$cue_ordered <- factor(
        df$cue_name,
        levels = c("low", "high")
    )
return(df)
}
```

```{r function::NPS_lineplot_34, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
two_factor_lineplot <-
  function(df, iv1, iv2, mean, error, xlab, ylab) {
    g <- ggplot(
      data = df,
      aes(
        x = .data[[iv1]],
        y = .data[[mean]],
        group = factor(.data[[iv2]]),
        color = factor(.data[[iv2]])
      ),
      cex.lab = 1.5,
      cex.axis = 2,
      cex.main = 1.5,
      cex.sub = 1.5
    ) +
      geom_errorbar(aes(
        ymin = (.data[[mean]] - .data[[error]]),
        ymax = (.data[[mean]] + .data[[error]])
      ), width = .1) +
      geom_line() +
      geom_point() +
      ggtitle(ggtitle) +
      xlab(xlab) +
      ylab(ylab) +
      #scale_color_manual(values = color) +
      theme_classic() +

      theme(aspect.ratio = .6) +
      expand_limits(x = 3.25) +
      #guides(fill = "none") +
      #guides(color = TRUE) +
      #guides(fill = guide_legend(title = "title")) +
      #scale_fill_manual(values = color) +
      scale_color_manual("",
                         values =  c(
                           "pain" = "#941100",
                           "vicarious" = "#008F51",
                           "cognitive" = "#011891"
                         )) +
      theme(
        legend.position = c(.99, .99),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      theme(legend.key = element_rect(fill = "white", colour = "white")) +
      theme_bw()

    return(g)
  }
```

## 1. NPS \~ 3 task x 3 stimulus intensity

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Step 1: Common parameters
# step 1: load data
for (signature_key in c("NPS", "NPSpos", "NPSneg", "VPS", "VPSnooccip", "ThermalPain", "MechPain", "GeneralAversive", "AversiveVisual", "ZhouVPS", "PINES",  "GSR", "GeuterPaincPDM"))  {
     #{
  dv_keyword = signature_key
  signature_name = signature_key
  # step 1: common parameters _______
  main_dir <- dirname(dirname(getwd()))

  analysis_folder  = paste0("model40_iv-task-stim_dv-", signature_key)

  sig_name <-
    Sys.glob(file.path(
      main_dir,
      "analysis/fmri/nilearn/signature_extract",
      paste0(
        "signature-",
        signature_key,
        "_sub-all_runtype-pvc_event-stimulus.tsv"
      )
    )) # nolint
  print(sig_name)
  analysis_dir <-
    file.path(main_dir,
              "analysis",
              "mixedeffect",
              analysis_folder,
              as.character(Sys.Date())) # nolint
  dir.create(analysis_dir,
             showWarnings = FALSE,
             recursive = TRUE)
  savedir <- analysis_dir

  # step 2: load data
  df = read.csv(sig_name)
  sig_df = df %>% separate(
    singletrial_fname,
    sep = "_",
    c(
      "sub",
      "ses",
      "run",
      "runtype",
      "event",
      "trial",
      "cuetype",
      "stimintensity"
    )
  )
  sig_df = sig_df %>% separate(
    stimintensity,
    into = c(NA, "stimintensity"),
    extra = "drop",
    fill = "left"
  )
  pvc <- simple_contrasts_singletrial(sig_df)
  pvc$task[pvc$runtype == "runtype-pain"] <- "pain"
  pvc$task[pvc$runtype == "runtype-vicarious"] <- "vicarious"
  pvc$task[pvc$runtype == "runtype-cognitive"] <- "cognitive"
  pvc$task <- factor(pvc$task)


  # step 3: parameters

  taskname = "all"
  plot_keyword = "stimulusintensity"
  ggtitle_phrase =  "(3 tasks x 3 stimulus intensity)"

  pvc$task = factor(pvc$task)
  plot_keys <- list(
    sub_mean = "mean_per_sub",
    group_mean = "mean_per_sub_norm_mean",
    legend_keyword = "stimulus intensity",
    se = "se",
    subject = "sub",
    ggtitle = paste0(
      str_to_title(signature_key),
      " dot product: ",
      str_to_title(taskname),
      ' ',
      ggtitle_phrase,
      " (N = ",
      length(unique(pvc$sub)),
      ")"
    ),
    title = paste0(
      str_to_title(signature_key),
      " - ",
      str_to_title(plot_keyword)
    ),
    xlab = "",
    ylab = paste(signature_key, " (dot product)"),
    ylim = c(-250, 500)
  )

  # step 4: within between summary
  groupwise <- data.frame()
  subjectwise <- data.frame()
  summary <- summary_for_plots_PVC(
    df = pvc,
    # taskname = taskname,
    groupwise_measurevar = plot_keys$sub_mean,
    # "mean_per_sub",
    subject_keyword = plot_keys$subject,
    # "sub",
    model_iv1 =  "task",
    model_iv2 =  "stim_ordered",
    dv = signature_key #"NPSpos"
  )
  subjectwise <<- as.data.frame(summary[[1]])
  groupwise <<- as.data.frame(summary[[2]])
  if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
    plot_keys$color <- c("#1B9E77", "#D95F02", "#D95F02")
  } else {
    plot_keys$color <- c(
                           "pain" = "#941100",
                           "vicarious" = "#008F51",
                           "cognitive" = "#011891"
                         )
  }

  # step 5: plot

  iv2 = "stim_ordered"
  iv1 = "task"
  taskname = "all"
  if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
    color <- c("#1B9E77", "#D95F02", "#D95F02")
  } else {
    color <- c(
                           "pain" = "#941100",
                           "vicarious" = "#008F51",
                           "cognitive" = "#011891"
                         )
  }
  subject_mean <- "mean_per_sub"
  sub_mean = subject_mean
  group_mean <- "mean_per_sub_norm_mean"
  se <- "se"
  ylim <- c(-25, 26)
  subject <- "sub"
  ggtitle_phrase <-  "(3 tasks x 3 stimulus intensity)"
  ggtitle <-
    paste0(
      str_to_title(signature_name),
      " dot product: ",
      str_to_title(taskname),
      ' ',
      ggtitle_phrase,
      " (N = ",
      length(unique(pvc$sub)),
      ")"
    )

  title <-
    paste0(str_to_title(dv_keyword),
           " - ",
           str_to_title(plot_keys$legend_keyword))
  xlab <- ""
  plot_keyword = "stimintensity"
  ylab <- paste(signature_name, " (dot product)")
  plot2_savefname <- file.path(
    analysis_dir,
    paste(
      "signature_task-",
      taskname,
      "_event-",
      plot_keyword,
      "_dv-",
      signature_key,
      "_",
      as.character(Sys.Date()),
      ".png",
      sep = ""
    )
  )
  p <- plot_halfrainclouds_twofactor(
    subjectwise,
    groupwise,
    iv2,
    iv1,
    subject_mean,
    group_mean,
    se,
    subject,
    ggtitle,
    title,
    xlab,
    ylab,
    taskname,
    ylim,
    w = 10,
    h = 6,
    dv_keyword,
    color,
    plot2_savefname
  )
print(p)

k <- plot_lineplot_twofactor(groupwise,
                        iv1 =iv2, iv2 = iv1,
                        mean = group_mean, error = "se",
                        color=color,
                        ggtitle = title,
                        xlab = xlab, ylab = ylab)
k <- k + theme(aspect.ratio=.8)

print(k)
}
```

```{r echo=FALSE}
p
```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# Load behavioral data

main_dir = dirname(dirname(getwd()))
print(main_dir)
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
taskname = '*'
subject_varkey <- "src_subject_id"
iv <- "param_stimulus_type";
iv_keyword <- "stim";
dv <- "event04_actual_angle"; dv_keyword <- "outcome"
exclude <- "sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0007|sub-0008|sub-0013|sub-0016|sub-0017|sub-0019|sub-0020|sub-0021|sub-0025|sub-0075|sub-0009|sub-0117|sub-0119|sub-0081|sub-0060"
#sub-0074|sub-0085|sub-0118|sub-0117|sub-0103|sub-0063

p.df <- load_task_social_df(datadir, taskname = "pain", subject_varkey, iv, dv, exclude)
v.df <- load_task_social_df(datadir, taskname = "vicarious", subject_varkey, iv, dv, exclude)
c.df <- load_task_social_df(datadir, taskname = "cognitive", subject_varkey, iv, dv, exclude)

p.df2= p.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_p <- p.df2 %>%
  group_by(src_subject_id, session_id, param_run_num) %>%
  mutate(trial_index = row_number(param_run_num))

v.df2= v.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
data_v <- v.df2 %>%
  group_by(src_subject_id, session_id, param_run_num) %>%
  mutate(trial_index = row_number(param_run_num))

c.df2= c.df %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number()-1)
data_c <- c.df2 %>%
  group_by(src_subject_id, session_id, param_run_num) %>%
  mutate(trial_index = row_number(param_run_num) )
p.sub <- data_p[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
v.sub <- data_v[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
c.sub <- data_c[,c("src_subject_id", "session_id", "param_run_num", "param_task_name", "event02_expect_angle", "param_cue_type", "param_stimulus_type", "event04_actual_angle", "trial_index")]
# sub, ses, run, runtype, event, trial, cuetype, stimintensity
# src_subject_id, session_id, param_run_num, param_task_name, event02_expect_angle, param_cue_type, param_stimulus_type, event04_actual_angle
pvc.sub = rbind(p.sub, v.sub, c.sub)

# data_a3lag <-
#     pvc.sub %>%
#     group_by(param_task_name, src_subject_id, session_id, param_run_num) %>%
#     mutate(lag.04outcomeangle = dplyr::lag(event04_actual_angle, n = 1, default = NA))
# pvc.sub <- data_a3lag[complete.cases(data_a3lag$lag.04outcomeangle),]
#

```

```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
pvc.sub$trial_ind <- pvc.sub$trial_index -1
pvc.sub$sub <- sprintf("sub-%04d", pvc.sub$src_subject_id)
pvc.sub$ses <- sprintf("ses-%02d", pvc.sub$session_id)
pvc.sub$run <- sprintf("run-%02d", pvc.sub$param_run_num)
pvc.sub$runtype <- sprintf("runtype-%s", pvc.sub$param_task_name)
pvc.sub$trial <- sprintf("trial-%03d", pvc.sub$trial_ind)
pvc.sub[c('cue', 'DEPc')]  <- str_split_fixed(pvc.sub$param_cue_type , '_', 2)
pvc.sub$cuetype <- sprintf("cuetype-%s", pvc.sub$cue)
pvc.sub[c('stimintensity', 'DEP')]  <- str_split_fixed(pvc.sub$param_stimulus_type , '_', 2)

# merge
pvc.beh <- pvc.sub[,c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity","event02_expect_angle", "event04_actual_angle")]
df_merge <- merge(pvc, pvc.beh,
                  by.x = c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity"),
                  by.y = c("sub", "ses", "run", "runtype", "trial", "cuetype", "stimintensity")
                  )

```

```{r}
# contrast code 1 linear
df_merge$task_V_gt_C[df_merge$task == "pain"] <-  0
df_merge$task_V_gt_C[df_merge$task == "vicarious"] <-  0.5
df_merge$task_V_gt_C[df_merge$task == "cognitive"] <- -0.5

# contrast code 2 quadratic
df_merge$task_P_gt_VC[df_merge$task == "pain"] <-  0.66
df_merge$task_P_gt_VC[df_merge$task == "vicarious"] <-  0.34
df_merge$task_P_gt_VC[df_merge$task == "cognitive"] <-  -0.34


```

#### Contrast weight table {.unlisted .unnumbered}

```{r echo=FALSE}
tab <- matrix(c(0, .5, -.5,
                .66, -.34, -.34), ncol=3, byrow=TRUE)
colnames(tab) <- c('pain','vicarious','cognitive')
rownames(tab) <- c('task_V_gt_C','task_P_gt_VC')
kableExtra::kable_styling(
  knitr::kable(
    tab, caption = "Contrast weights", "html"),
  "striped", position = "left", font_size = 15)
```

### Linear model results (NPS \~ paintask: 2 cue x 3 stimulus_intensity)

```{r echo=TRUE, message=FALSE, warning=TRUE, paged.print=FALSE}

model.task_stim <- lmer(NPSpos ~
                          task_P_gt_VC*STIM_linear + task_P_gt_VC* STIM_quadratic + task_V_gt_C*STIM_linear + task_V_gt_C*STIM_quadratic +
                          (1|sub), data = df_merge
                    )
sjPlot::tab_model(model.task_stim,
                  title = "Multilevel-modeling: \nlmer(DATA ~ TASK * STIM + (1 | sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

```
lmer(NPSpos ~
                          CUE_high_gt_low*STIM_linear +CUE_high_gt_low * STIM_quadratic +
                          (CUE_high_gt_low+STIM|sub), data = data_screen
                    )
```

```{r echo=FALSE}
summary(model.task_stim)
```

#### Linear model eta-squared {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.task_stim, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
#parameters::model_parameters(model.npscuestim)
```

#### Linear model Cohen's d: NPS stimulus_intensity d = 1.16, cue d = 0.45 {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}

kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.task_stim, df_merge, type = "lme4"),
    "html"), "striped", position = "left", font_size = 12)
```

## 2. NPS \~ paintask: 2 cue x 3 stimulus_intensity

### Q. Within pain task, Does stimulus intenisty level and cue level significantly predict NPS dotproducts? {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
combined_se_calc_cooksd <- data.frame()
combined_psig <- data.frame()
taskname = "pain"
ggtitle <- paste(taskname, " - NPS (degree)")
title <- paste(taskname, " - actual")
subject <- "sub"
w <- 10
h <- 6
p.sig <- df_merge[df_merge$runtype == "runtype-pain" ,]
data <- p.sig
combined_psig <-
  rbind(combined_psig, p.sig)
# [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
data$stim[data$stimintensity == "low"] <-  -0.5 # social influence task
data$stim[data$stimintensity == "med"] <- 0 # no influence task
data$stim[data$stimintensity == "high"] <-  0.5 # no influence task

data$STIM <- factor(data$stimintensity)

# contrast code 1 linear
data$STIM_linear[data$stimintensity == "low"] <- -0.5
data$STIM_linear[data$stimintensity == "med"] <- 0
data$STIM_linear[data$stimintensity == "high"] <- 0.5

# contrast code 2 quadratic
data$STIM_quadratic[data$stimintensity == "low"] <- -0.33
data$STIM_quadratic[data$stimintensity == "med"] <- 0.66
data$STIM_quadratic[data$stimintensity == "high"] <- -0.33

# social cude contrast
data$CUE_high_gt_low[data$cuetype == "cuetype-low"] <-  -0.5 # social influence task
data$CUE_high_gt_low[data$cuetype == "cuetype-high"] <-  0.5 # no influence task

data$EXPECT <- data$event02_expect_angle
data <- data %>%
mutate(NPS_gmc = NPSpos - mean(NPSpos))
#######################
stim_con1 <- "STIM_linear"
stim_con2 <- "STIM_quadratic"
iv1 <- "CUE_high_gt_low"
dv <- "NPS_gmc"
#######################

# [ MODEL ] _________________________________________________ # nolint
model_savefname <- file.path(
  analysis_dir,
  paste(
    "lmer_task-",
    taskname,
    "_rating-",
    dv_keyword,
    "_",
    as.character(Sys.Date()),
    "_cooksd.txt",
    sep = ""
  )
)

cooksd <- lmer_twofactor_cooksd(
  data,
  taskname,
  iv1,
  stim_con1,
  stim_con2,
  dv,
  subject,
  dv_keyword,
  model_savefname,
  'random_intercept',
  print_lmer_output = FALSE
)
influential <- as.numeric(names(cooksd)[(cooksd > (4 / as.numeric(length(unique(
  data$sub
)))))])
data_screen <- data[-influential,]

data_screen %>%
  group_by

# [ PLOT ] reordering for plots _________________________ # nolint
data_screen$cue_name[data_screen$cuetype == "cuetype-high"] <-
  "high cue"
data_screen$cue_name[data_screen$cuetype == "cuetype-low"] <-
  "low cue"

data_screen$stim_name[data_screen$stimintensity == "high"] <-
  "high"
data_screen$stim_name[data_screen$stimintensity == "med"] <-
  "med"
data_screen$stim_name[data_screen$stimintensity == "low"] <-
  "low"

# DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

data_screen$stim_ordered <- factor(data_screen$stim_name,
                                   levels = c("low", "med", "high"))
data_screen$cue_ordered <- factor(data_screen$cue_name,
                                  levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"

#  [ PLOT ] calculate mean and se  _________________________
NPSstimcue_subjectwise <- meanSummary(data_screen,
                                      c(subject, model_iv1, model_iv2), dv)
NPSstimcue_groupwise <- summarySEwithin(
  data = NPSstimcue_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
NPSstimcue_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

combined_se_calc_cooksd <-
  rbind(combined_se_calc_cooksd, NPSstimcue_groupwise)
# calculate mean and se
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
subject <- "sub"
ggtitle <- paste(taskname, " - NPSpos Cooksd removed")
title <- paste(taskname, " - NPSpos")
xlab <- ""
ylab <- "NPSpos (degree)"
ylim <- c(-10, 60)
dv_keyword <- "NPSpos"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#4575B4", "#D73027")
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), "_cooksd.png",
    sep = ""
  )
)
g <- plot_halfrainclouds_twofactor(
  NPSstimcue_subjectwise,
  NPSstimcue_groupwise,
  model_iv1,
  model_iv2,
  sub_mean,
  group_mean,
  se,
  subject,
  ggtitle,
  title,
  xlab,
  ylab,
  taskname,
  ylim,
  w,
  h,
  dv_keyword,
  color,
  plot_savefname
)
g
```

### Lineplots with only low cue {.unlisted .unnumbered}

```{r echo=FALSE, warning=FALSE}
subsetNPS <- NPSstimcue_groupwise[NPSstimcue_groupwise$cue_ordered == "low cue",]
g <- plot_lineplot_twofactor_subset(subsetNPS, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#5D5C5C", "#D73027"), ggtitle = "Within pain task: NPS dotproducts as a function of stimulus intensity level and cue",
                        xlab = "Stimulus intensity", ylab = "NPSpos (dot product)")
g + theme(aspect.ratio=.8)
```

### Lineplots {.unlisted .unnumbered}

```{r echo=FALSE, warning=FALSE}
g <- plot_lineplot_twofactor_subset(NPSstimcue_groupwise, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#5D5C5C","high cue" = "#D73027"), ggtitle = "Within pain task: NPS dotproducts as a function of stimulus intensity level and cue",
                        xlab = "Stimulus intensity", ylab = "NPSpos (dot product)")
g + theme(aspect.ratio=.8)
```

```{r}

```

### Lineplots {.unlisted .unnumbered}

```{r echo=FALSE, warning=FALSE}
g <- plot_lineplot_twofactor(NPSstimcue_groupwise,
                        iv2 = "stim_ordered", iv1 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("high" = "red",
                                  "med" = "orange",
                                  "low" = "yellow"),
                        ggtitle = "Within pain task: NPS dotproducts as a function of stimulus intensity level and cue",
                        xlab = "Stimulus intensity", ylab = "NPSpos (dot product)")
g + theme(aspect.ratio=.8)
```

### Linear model results (NPS \~ paintask: 2 cue x 3 stimulus_intensity)

```{r echo=TRUE, message=FALSE, warning=TRUE, paged.print=FALSE}

model.npscuestim <- lmer(NPS_gmc ~
                          CUE_high_gt_low*STIM_linear +CUE_high_gt_low * STIM_quadratic +
                          (1|sub), data = data_screen
                    )
sjPlot::tab_model(model.npscuestim,
                  title = "Multilevel-modeling: \nlmer(NPSpos ~ CUE * STIM + (CUE + STIM | sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

```
lmer(NPSpos ~
                          CUE_high_gt_low*STIM_linear +CUE_high_gt_low * STIM_quadratic +
                          (CUE_high_gt_low+STIM|sub), data = data_screen
                    )
```

```{r echo=FALSE}
summary(model.npscuestim)
```

#### Linear model eta-squared {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.npscuestim, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
#parameters::model_parameters(model.npscuestim)
```

#### Linear model Cohen's d: NPS stimulus_intensity d = 1.16, cue d = 0.45 {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}

kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.npscuestim, data_screen, type = "lme4"),
    "html"), "striped", position = "left", font_size = 12)
```

## 3. NPS \~ SES \* CUE \* STIM

### Q. Is the cue effect on NPS different across sessions? {.unlisted .unnumbered}

> Quick answer: Yes, the cue effect in session 1 (for high intensity group) is significantly different; whereas this different becomes non significant in session 4. To unpack, a participant was informed to experience a low stimulus intensity, when in fact they were delivered a high intensity stimulus. This violation presumably leads to a higher NPS response, given that they were delivered a much painful stimulus than expected. The fact that the cue effect is almost non significant during the last session indicates that the cue effects are not just an anchoring effect.

```{r}

# code session
# contrast code 1 linear
combined_psig$SES_linear[combined_psig$ses == "ses-01"] <- -0.5
combined_psig$SES_linear[combined_psig$ses == "ses-03"] <- 0
combined_psig$SES_linear[combined_psig$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
combined_psig$SES_quadratic[combined_psig$ses == "ses-01"] <- -0.33
combined_psig$SES_quadratic[combined_psig$ses == "ses-03"] <- 0.66
combined_psig$SES_quadratic[combined_psig$ses == "ses-04"] <- -0.33

model.npsses <- lmer(NPSpos ~
                          CUE_high_gt_low*STIM_linear*SES_linear +
                          CUE_high_gt_low*STIM_quadratic*SES_linear +
                          CUE_high_gt_low*STIM_linear*SES_quadratic +
                          CUE_high_gt_low*STIM_quadratic*SES_quadratic +
                          (1|sub), data = combined_psig
                    )
# CUE_high_gt_low+STIM+EXPECT_demean
sjPlot::tab_model(model.npsses,
                  title = "Multilevel-modeling: \nlmer(NPSpos ~ CUE * STIM * SES + (1| sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

#### eta squared {.unlisted .unnumbered}

```{r echo=FALSE, warning=TRUE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.npsses, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

#### Cohen's d {.unlisted .unnumbered}

```{r echo=FALSE, warning=TRUE}
kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.npsses, combined_psig, type = "lme4"), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

#### Session wise plots {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

combined_se_calc_cooksd <- data.frame()
for (sesname in c("ses-01", "ses-03", "ses-04")) {
taskname = "pain"
    ggtitle <- paste(taskname, " - actual judgment (degree)")
    title <- paste(taskname, " - actual")
    subject <- "sub"
    w <- 10
    h <- 6
s1.sig <- df_merge[df_merge$runtype == "runtype-pain" & df_merge$ses == sesname,]
data <- s1.sig
    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
data$stim[data$stimintensity == "low"] <- -0.5 # social influence task
data$stim[data$stimintensity == "med"] <- 0 # no influence task
data$stim[data$stimintensity == "high"] <- 0.5 # no influence task

data$STIM <- factor(data$stimintensity)

# contrast code 1 linear
data$STIM_linear[data$stimintensity == "low"] <- -0.5
data$STIM_linear[data$stimintensity == "med"] <- 0
data$STIM_linear[data$stimintensity == "high"] <- 0.5

# contrast code 2 quadratic
data$STIM_quadratic[data$stimintensity == "low"] <- -0.33
data$STIM_quadratic[data$stimintensity == "med"] <- 0.66
data$STIM_quadratic[data$stimintensity == "high"] <- -0.33

    # social cude contrast
    data$CUE_high_gt_low[data$cuetype == "cuetype-low"] <- -0.5 # social influence task
    data$CUE_high_gt_low[data$cuetype == "cuetype-high"] <- 0.5 # no influence task


    stim_con1 <- "STIM_linear"
    stim_con2 <- "STIM_quadratic"
    iv1 <- "CUE_high_gt_low"
    dv <- "NPSpos"

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )

    cooksd <- lmer_twofactor_cooksd(
        data, taskname, iv1, stim_con1, stim_con2, dv,
        subject, dv_keyword, model_savefname, 'random_intercept', print_lmer_output = FALSE
    )
    influential <- as.numeric(names(cooksd)[
        (cooksd > (4 / as.numeric(length(unique(data$sub)))))
    ])
    data_screen <- data[-influential, ]
    # [ PLOT ] reordering for plots _________________________ # nolint
    data_screen$cue_name[data_screen$cuetype == "cuetype-high"] <- "high cue"
    data_screen$cue_name[data_screen$cuetype == "cuetype-low"] <- "low cue"

    data_screen$stim_name[data_screen$stimintensity == "high"] <- "high"
    data_screen$stim_name[data_screen$stimintensity == "med"] <- "med"
    data_screen$stim_name[data_screen$stimintensity == "low"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data_screen$stim_ordered <- factor(
        data_screen$stim_name,
        levels = c("low", "med", "high")
    )
    data_screen$cue_ordered <- factor(
        data_screen$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data_screen,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    actual_groupwise$ses <- sesname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
   # calculate mean and se
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(str_to_title(taskname), " - NPSpos Cooksd removed ", sesname )
    title <- paste(str_to_title(taskname), " - cue level")
    xlab <- ""
    ylab <- "NPSpos (degree)"
    ylim <- c(-10,60)
    dv_keyword <- "NPSpos"
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_halfrainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
print(g)
}
```

#### session wise line plots {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE}
# lineplot per session

DATA = as.data.frame(combined_se_calc_cooksd)
color = c("#4C77ED", "#ED220D")
model_iv1 <- "stim_ordered"
model_iv2 <- "ses_ordered"
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "se"
dv_keyword = "actual"
p1 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-01",],
               LINEIV1, LINEIV2, MEAN, ERROR, color, ggtitle = 'ses-01',
               ylab = "NPS (dot products)" )
p2 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-03",],
               LINEIV1, LINEIV2, MEAN, ERROR, color, ggtitle = 'ses-03',
               ylab = "NPS (dot products)")
p3 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-04",],
               LINEIV1, LINEIV2, MEAN, ERROR, color,ggtitle = 'ses-04',
               ylab = "NPS (dot products)")

ggpubr::ggarrange(p1,p2,p3,ncol = 3, nrow = 1, common.legend = TRUE,legend = "bottom")
plot_filename = file.path(analysis_dir,
                          paste('lineplot_task-all_rating-',dv_keyword,'.png', sep = ""))
ggsave(plot_filename, width = 8, height = 4)
```

---

## 4. [INCORRECT] no cmc NPS \~ CUE \* STIM \* EXPECT {.unlisted .unnumbered}

- 2 cue \* 3 stimulus_intensity \* expectation_rating

```{r eval=FALSE, warning=TRUE, include=FALSE}

data_screen$EXPECT <- data_screen$event02_expect_angle
model.nps3factor <- lmer(NPSpos ~
                          CUE_high_gt_low*STIM_linear*EXPECT +
                           CUE_high_gt_low*STIM_quadratic*EXPECT +
                          (CUE_high_gt_low  |sub), data = data_screen
                    )
sjPlot::tab_model(model.nps3factor,
                  title = "Multilevel-modeling: \nlmer(NPSpos ~ CUE * STIM * EXPECTATION + (CUE + STIM + EXPECT | sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

#### eta squared {.unlisted .unnumbered}

```{r eval=FALSE, warning=TRUE, include=FALSE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.nps3factor, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

#### Cohen's d {.unlisted .unnumbered}

```{r eval=FALSE, warning=TRUE, include=FALSE}
kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.nps3factor, data_screen, type = "lme4"), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

---

## 6. OUTCOME \~ NPS

### Q. Do higher NPS values indicate higher outcome ratings? (Pain task only) {.unlisted .unnumbered}

> TODO: update. Yes, Higher NPS values are associated with higher outcome ratings. The linear relationship between NPS value and outcome ratings are stronger for conditions where cue level is congruent with stimulus intensity levels. In other words, NPS-outcome rating relationship is stringent in the low cue-low intensity group, as is the case for high cue-ghigh intensity group.

```{r include=FALSE}
remove_sub_list = c("sub-0009")
#, "sub-0117", "sub-0081", "sub-0060", "sub-0063", "sub-0074", "sub-0080", "sub-0085", "sub-0098", "sub-0118", "sub-0129")
df_merge_drop <- subset(df_merge, !(sub %in% remove_sub_list))
freq <- count(df_merge, "sub")
subset_ses <-  df_merge_drop[df_merge_drop$task == 'pain',]
p.demean <- subset_ses %>%
group_by(sub) %>%
mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
mutate(OUTCOME_demean = event04_actual_angle - avg_outcome) %>%
mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
mutate(EXPECT_demean = event02_expect_angle - avg_expect)

p.demean <- p.demean %>%
group_by(sub, ses) %>%
mutate(NPSpos = as.numeric(NPSpos)) %>%
mutate(avg_NPS = mean(NPSpos, na.rm = TRUE)) %>%
mutate(NPS_demean = NPSpos - avg_NPS) %>%
  ungroup %>%
mutate(OUTCOME_cmc = avg_outcome - mean(avg_outcome)) %>%
mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) %>%
mutate(NPS_cmc = avg_NPS - mean(avg_NPS)) %>%
  mutate(NPS_gmc = NPSpos - mean(NPSpos)) %>%
mutate(OUTCOME_gmc = event04_actual_angle - mean(event04_actual_angle)) %>%
  mutate(EXPECT_gmc = event02_expect_angle - mean(event02_expect_angle))
p.demean$EXPECT <- p.demean$event02_expect_angle
p.demean$OUTCOME <- p.demean$event04_actual_angle

demean_dropna <- p.demean[!is.na(p.demean[, iv1]) & !is.na(p.demean[, iv2]),]
demean_dropna$EXPECT <- demean_dropna$event02_expect_angle
```

### Linear model (without CMC subjectwise mean) {.unlisted .unnumbered}

```{r eval=FALSE, message=FALSE, warning=TRUE, include=FALSE, paged.print=FALSE}
# DEPRECATE DEPRECATE DEPRECATE DEPRECATE DEPRECATEDEPRECATEDEPRECATE
# organize variable names
# NPS_demean vs. NPSpos
model.npsoutcome <- lmer(OUTCOME_demean ~
                           CUE_high_gt_low*STIM_linear*NPSpos +
                           CUE_high_gt_low*STIM_quadratic*NPSpos +
                           (CUE_high_gt_low+STIM+NPSpos|sub), data = demean_dropna)
sjPlot::tab_model(model.npsoutcome,
                  title = "Multilevel-modeling: \nlmer(OUTCOME_demean ~ CUE * STIM * NPSpos + (CUE * STIM *NPSpos | sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

```{r echo=TRUE, message=FALSE, warning=TRUE, paged.print=FALSE}
# organize variable names
# NPS_demean vs. NPSpos
model.npsoutcome <- lmer(OUTCOME_gmc ~
                           CUE_high_gt_low*STIM_linear*NPS_demean +
                           CUE_high_gt_low*STIM_quadratic*NPS_demean +
                           NPS_cmc + (1|sub), data = demean_dropna)
sjPlot::tab_model(model.npsoutcome,
                  title = "Multilevel-modeling: \nlmer(OUTCOME_gmc ~ CUE * STIM * NPSpos_demean + NPS_cmc + (1| sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

### 6-0. No transformation {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# plot parameters
iv2 = "event04_actual_angle"
iv1 = "NPSpos"
subject = "sub"
ylab = "Outcome rating"
xlab = "NPSpos" #signature_key
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
p.sig <- df_merge[df_merge$runtype == "runtype-pain",]
df_dropna <- p.sig[!is.na(p.sig[, iv1]) & !is.na(p.sig[, iv2]),]
subjectwise_2dv <- meanSummary_2dv(df_dropna,
                                   c(subject),
                                   iv1, iv2)
subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
g <- ggplot(data = subjectwise_naomit_2dv,
            aes(x = .data[["DV1_mean_per_sub"]],
                y = .data[["DV2_mean_per_sub"]],)) +
  geom_point(size = 2,
             alpha = alpha) +

  theme(aspect.ratio = 1) +
  #scale_color_manual(values = color_scheme) +
  scale_shape_manual(values = c(16, 17)) +
  xlab(xlab) +
  ylab(ylab) +
  xlim(-10, 30) +
  ylim(0, 180) +
  ggtitle(ggtitle) +
  theme(
    axis.line = element_line(colour = "grey50"),
    panel.background = element_blank(),
    plot.subtitle = ggtext::element_textbox_simple(size = 11)
  ) +
  geom_ribbon(
    stat = "smooth",
    method = lm_method,
    se = TRUE,
    alpha = 0.1,
    aes(color = NULL)
  ) +
  geom_line(
    stat = "smooth",
    method = lm_method,
    alpha = 0.8,
    linewidth = 1.5
  )
g
```

### 6-1. outcome_rating \* cue {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
p.sig <- df_merge[df_merge$runtype == "runtype-pain",]
iv2 = "event04_actual_angle"; iv1 = "NPSpos"
df_dropna <-
  p.sig[!is.na(p.sig$event04_actual_angle) & !is.na(p.sig$NPSpos),]
total <-
  plot_twovariable(
    df_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin=0, ymax=180, xmin=-10, xmax=30,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "all stimulus intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#BBBBBB"),
    alpha = .8, fit_lm = TRUE, lm_method ="lm", identity_line = FALSE
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for NPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )
```

### 6-2. outcome_rating \* stimulus_intensity \* cue {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv2 = "event04_actual_angle"; iv1 = "NPSpos"
group = "cuetype"; subject = "sub"
# low stimulus intensity
df_low = df_dropna[df_dropna$stimintensity == "low", ]
low <-
  plot_twovariable(
    df_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=0, ymax=180, xmin=-10, xmax=30,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
df_med = df_dropna[df_dropna$stimintensity == "med", ]
med <-
  plot_twovariable(
    df_med, iv1, iv2,
    group = group, subject = subject,
    ymin=0, ymax=180, xmin=-10, xmax=30,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
df_high = df_dropna[df_dropna$stimintensity == "high", ]
high <-
  plot_twovariable(
    df_high, iv1, iv2,
    group = group, subject = subject,
    ymin=0, ymax=180, xmin=-10, xmax=30,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```

### 6-3. OUTCOMEgmc \~ NPScmc \* cue {.unlisted .unnumbered}

```{r echo=FALSE}
# plot parameters
iv1 = "NPS_cmc"
iv2 = "OUTCOME_gmc"

subject = "sub"
ylab = "Outcome rating \n(grand mean-centered)"
xlab = paste(signature_key, "\n(cluster grand mean-centered; CMC)")
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"

total <-
  plot_twovariable(
    demean_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin=-90, ymax=180, xmin=-15, xmax=20,
    ylab,  xlab = xlab, #, "\n(subjectwise mean-centered)"),
    ggtitle = "all stimulus intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#BBBBBB"),
    alpha = .8, fit_lm = TRUE, lm_method ="lm", identity_line = FALSE
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for NPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )

```

### 6-4. OUTCOMEgmc \~ NPScmc \* cue \* stim

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

# plot parameters
###################
iv1 = "NPS_cmc"
iv2 = "OUTCOME_gmc"
subject = "sub"
ylab = "Outcome rating \n(grand mean-centered)"
xlab = paste(signature_key, "\n(cluster grandmean-centered; CMC)")
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
###################
# iv2 = "OUTCOME_demean"; iv1 = "NPSpos" # "NPSpos"
# ylab = "Outcome rating \n(subjectwise mean-centered)"
# xlab =  paste(signature_key)
group = "cuetype"; subject = "sub"
# low stimulus intensity
demean_low = demean_dropna[demean_dropna$stimintensity == "low", ]
low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=-50, ymax=50, xmin=-10, xmax=30,
    ylab = ylab, xlab =  xlab,
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimintensity == "med", ]
med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=-50, ymax=50, xmin=-20, xmax=30,
    ylab = ylab, xlab =  xlab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimintensity == "high", ]
high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=-50, ymax=50, xmin=-10, xmax=30,
    ylab = ylab, xlab =  xlab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```

### 6-5. OUTCOMEgmc \~ NPSdemean {.unlisted .unnumbered}

```{r echo=FALSE}
remove_sub_list = c("sub-0009")
#, "sub-0117", "sub-0081", "sub-0060", "sub-0063", "sub-0074", "sub-0080", "sub-0085", "sub-0098", "sub-0118", "sub-0129")
df_merge_drop <- subset(df_merge, !(sub %in% remove_sub_list))
freq <- count(df_merge, "sub")
subset_ses <-  df_merge_drop[df_merge_drop$task == 'pain',]
p.demean <- subset_ses %>%
group_by(sub) %>%
mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
mutate(OUTCOME_demean = event04_actual_angle - avg_outcome) %>%
mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
mutate(EXPECT_demean = event02_expect_angle - avg_expect)

p.demean <- p.demean %>%
group_by(sub, ses) %>%
mutate(NPSpos = as.numeric(NPSpos)) %>%
mutate(avg_NPS = mean(NPSpos, na.rm = TRUE)) %>%
mutate(NPS_demean = NPSpos - avg_NPS) %>%
  ungroup %>%
mutate(OUTCOME_cmc = avg_outcome - mean(avg_outcome)) %>%
mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) %>%
mutate(NPS_cmc = avg_NPS - mean(avg_NPS)) %>%
mutate(NPS_gmc = NPSpos - mean(NPSpos)) %>%
mutate(OUTCOME_gmc = event04_actual_angle - mean(event04_actual_angle)) %>%
  mutate(EXPECT_gmc = event02_expect_angle - mean(event02_expect_angle))
p.demean$EXPECT <- p.demean$event02_expect_angle
p.demean$OUTCOME <- p.demean$event04_actual_angle
# plot parameters
###################
iv1 = "NPS_demean"
iv2 = "OUTCOME_gmc"
subject = "sub"
ylab = "Outcome rating \n(grand mean-centered)"
xlab = paste(signature_key, "\n(subjectwise mean-centered; CWC)")
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
###################

demean_dropna <- p.demean[!is.na(p.demean[, iv1]) & !is.na(p.demean[, iv2]),]
demean_dropna$EXPECT <- demean_dropna$event02_expect_angle
total <-
  plot_twovariable(
    demean_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin=-25, ymax=25, xmin=-5, xmax=5,
    ylab,  xlab = xlab, #, "\n(subjectwise mean-centered)"),
    ggtitle = "all stimulus intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#BBBBBB"),
    alpha = .8, fit_lm = TRUE, lm_method ="lm", identity_line = FALSE
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for NPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )

```

### facet wrap {.unlisted .unnumbered}

> same plot as 6-5, but adding subjectwise slopes

```{r echo=FALSE}
# plot parameters
###################
iv1 = "NPS_demean"
iv2 = "OUTCOME_gmc"
subject = "sub"
###################
ggplot(demean_dropna, aes(x = NPS_demean,
                       y = OUTCOME_gmc,
                       col=cuetype,
                       shape = sub), alpha = .3, size = .3, color = 'gray') +
  geom_point(size = .1) +
  # geom_line(aes(col=cuetype)) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1, alpha = .3) +
  theme_classic() + theme(legend.position = "none")
```

### 6-6. OUTCOMEgmc \~ NPSdemean \* cue \* stim {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, paged.print=FALSE}

# plot parameters
###################
iv1 = "NPS_demean"
iv2 = "OUTCOME_gmc"
subject = "sub"
ylab = "Outcome rating \n(grand mean-centered)"
xlab = paste(signature_key, "\n(CWC; subjectwise mean-centered; CWC)")
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
###################
# low stimulus intensity
yminval=-55; ymaxval=120; xminval=-20; xmaxval=20;
ymin=yminval; ymax=ymaxval; xmin=xminval; xmax=xmaxval;

demean_low = demean_dropna[demean_dropna$stimintensity == "low", ]
low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=yminval, ymax=ymaxval, xmin=xminval, xmax=xmaxval,
    ylab = ylab, xlab =  xlab,
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimintensity == "med", ]
med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=yminval, ymax=ymaxval, xmin=xminval, xmax=xmaxval,
    ylab = ylab, xlab =  xlab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimintensity == "high", ]
high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=yminval, ymax=ymaxval, xmin=xminval, xmax=xmaxval,
    ylab = ylab, xlab =  xlab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```

---

## 7. NPS \~ expectation_rating

### Q. What is the relationship betweeen expectation ratings & NPS? (Pain task only) {.unlisted .unnumbered}

Do we see a linear effect between expectation rating and NPS dot products? Also, does this effect differ as a function of cue and stimulus intensity ratings, as is the case for behavioral ratings?

> Quick answer: Yes, expectation ratings predict NPS dotproducts; Also, there tends to be a different relationship depending on cues, just by looking at the figures, although this needs to be tested statistically.

### 7. linear model {.unlisted .unnumbered}

```{r include=FALSE}
remove_sub_list = c("sub-0009") # "sub-0117", "sub-0081", "sub-0060", "sub-0063", "sub-0074", "sub-0085", "sub-0098", "sub-0118")
df_merge_drop <- subset(df_merge, !(sub %in% remove_sub_list))
subset_ses <-  df_merge_drop[df_merge_drop$task == 'pain',]
p.demean <- subset_ses %>%
  group_by(sub) %>%
  mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
  mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
  mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
  mutate(OUTCOME_demean = event04_actual_angle - avg_outcome) %>%
  mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
  mutate(EXPECT_demean = event02_expect_angle - avg_expect) %>%
  group_by(sub, ses) %>%
  mutate(NPSpos = as.numeric(NPSpos)) %>%
  mutate(avg_NPS = mean(NPSpos, na.rm = TRUE)) %>%
  mutate(NPS_demean = NPSpos - avg_NPS) %>%
  ungroup %>%
  mutate(OUTCOME_cmc = avg_outcome - mean(avg_outcome)) %>%
  mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) %>%
  mutate(NPS_cmc = avg_NPS - mean(avg_NPS)) %>%
mutate(NPS_gmc = NPSpos - mean(NPSpos)) %>%
mutate(OUTCOME_gmc = event04_actual_angle - mean(event04_actual_angle)) %>%
  mutate(EXPECT_gmc = event02_expect_angle - mean(event02_expect_angle))
p.demean$EXPECT <- p.demean$event02_expect_angle
p.demean$OUTCOME <- p.demean$event04_actual_angle
```

GEORGE SUGGESTION

```{r echo=TRUE, warning=TRUE, paged.print=FALSE}
model.npsexpectdemean <- lmer(NPS_gmc ~
                          CUE_high_gt_low*STIM_linear*EXPECT_demean +
                          CUE_high_gt_low*STIM_quadratic*EXPECT_demean +
                          EXPECT_cmc +
                          (1 |sub), data = demean_dropna, REML = FALSE
                    )
# CUE_high_gt_low+STIM+EXPECT_demean
sjPlot::tab_model(model.npsexpectdemean,
                  title = "Multilevel-modeling: \nlmer(NPSpos ~ CUE * STIM * EXPECT_demean + (1| sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

### 7-1. [correct] NPSgmc \~ EXPECTdemean \* cue {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# plot parameters
###################
iv1 = "EXPECT_demean"
iv2 = "NPS_gmc"
subject = "sub"
xlab = "Expectation rating \n(CWC; subjectwise mean-centered)"
ylab = paste(signature_key, "\n(grand-mean-centered)") #, " \n(mean-centered)")
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
###################
# plot parameters
demean_dropna <- p.demean[!is.na(p.demean[, iv1]) & !is.na(p.demean[, iv2]),]

total <-
  plot_twovariable(
    demean_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin=-30, ymax=30, xmin=-50, xmax=50,
    xlab ,ylab,
    ggtitle = "all stimulus intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#BBBBBB"),
    alpha = .8, fit_lm = TRUE, lm_method ="lm", identity_line = FALSE
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for NPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )

```

```{r echo=FALSE}
ggplot(demean_dropna, aes(x = event02_expect_angle,
                       y = event04_actual_angle,
                       col = cuetype,
                       shape = sub), size = .3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .3) +
  theme_classic() + theme(legend.position = "none")
```

```{r echo=FALSE}
ggplot(demean_dropna, aes(x = event02_expect_angle,
                       y = event04_actual_angle,
                       col = stim_ordered,
                       shape = sub), size = .3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  theme_classic() + theme(legend.position = "none")
```

```{r echo=FALSE}
ggplot(demean_dropna, aes(x = EXPECT_demean,
                       y = OUTCOME_gmc,
                       col = stim_ordered,
                       shape = sub), size = .3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1, alpha = .2) +
  theme_classic() + theme(legend.position = "none")
```

```{r echo=FALSE}
ggplot(demean_dropna[demean_dropna$stimintensity == 'low',],
       aes(x = NPS_demean,
                       y = OUTCOME_gmc,
                       col = cuetype,
                       shape = sub), size = .3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1, alpha = .2) +
  theme_classic() + theme(legend.position = "none")

ggplot(demean_dropna[demean_dropna$stimintensity == 'high',],
       aes(x = NPS_demean,
                       y = OUTCOME_gmc,
                       col = cuetype,
                       shape = sub), size = 3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1, alpha = .2) +
  theme_classic() + theme(legend.position = "none")
```

```{r echo=FALSE}
ggplot(demean_dropna, aes(x = event02_expect_angle,
                       y = NPS_gmc,
                       col = cuetype,
                       shape = sub), size = .3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .3) +
  theme_classic() + theme(legend.position = "none")
```

```{r echo=FALSE}
ggplot(demean_dropna, aes(x = STIM_linear,
                       y = NPS_gmc,
                       col = cuetype,
                       shape = sub), size = .3, color = c('red', 'gray')) +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  theme_classic() + theme(legend.position = "none")
```

```{r echo=FALSE}
ggplot(demean_dropna, aes(x = NPS_demean,
                       y = OUTCOME_gmc,
                       col = cuetype,
                       shape = sub), size = .3, col = c('red', 'gray')) +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  theme_classic() + theme(legend.position = "none")

```

### 7-2. [correct] NPSgmc \~ EXPECTdemean \* cue \* stim {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}

# plot parameters
###################
iv1 = "EXPECT_demean"
iv2 = "NPS_gmc"
subject = "sub"
xlab = "Expectation rating \n(CWC; subjectwise mean-centered)"
ylab = paste(signature_key, "\n(grand mean-centered")
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
yminval=-30; ymaval=30; xminval=-60; xmaxval=60;
###################

# low stimulus intensity
demean_low = demean_dropna[demean_dropna$stimintensity == "low", ]
low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=yminval, ymax=ymaxval, xmin=xminval, xmax=xmaxval,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimintensity == "med", ]
med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=yminval, ymax=ymaxval, xmin=xminval, xmax=xmaxval,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimintensity == "high", ]
high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=yminval, ymax=ymaxval, xmin=xminval, xmax=xmaxval,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```

### 7-3. [correct] NPSgmc \~ EXPECTcmc {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
remove_sub_list = c("sub-0009") # "sub-0117", "sub-0081", "sub-0060", "sub-0063", "sub-0074", "sub-0085", "sub-0098", "sub-0118")
df_merge_drop <- subset(df_merge, !(sub %in% remove_sub_list))
subset_ses <-  df_merge_drop[df_merge_drop$task == 'pain',]
p.demean <- subset_ses %>%
  group_by(sub) %>%
  mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
  mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
  mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
  mutate(OUTCOME_demean = event04_actual_angle - avg_outcome) %>%
  mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
  mutate(EXPECT_demean = event02_expect_angle - avg_expect) %>%
  group_by(sub, ses) %>%
  mutate(NPSpos = as.numeric(NPSpos)) %>%
  mutate(avg_NPS = mean(NPSpos, na.rm = TRUE)) %>%
  mutate(NPS_demean = NPSpos - avg_NPS) %>%
  ungroup %>%
  mutate(OUTCOME_cmc = avg_outcome - mean(avg_outcome)) %>%
  mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) %>%
  mutate(NPS_cmc = avg_NPS - mean(avg_NPS)) %>%
mutate(NPS_gmc = NPSpos - mean(NPSpos)) %>%
mutate(OUTCOME_gmc = event04_actual_angle - mean(event04_actual_angle)) %>%
  mutate(EXPECT_gmc = event02_expect_angle - mean(event02_expect_angle))
p.demean$EXPECT <- p.demean$event02_expect_angle
p.demean$OUTCOME <- p.demean$event04_actual_angle
# plot parameters
###################
iv1 = "EXPECT_cmc"
iv2 = "NPS_gmc"
subject = "sub"
xlab = "Expectation rating \n(CMC; cluster grand mean-centered)"
ylab = paste(signature_key, "\n(grand-mean-centered)") #, " \n(mean-centered)")
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
###################
# plot parameters
demean_dropna <- p.demean[!is.na(p.demean[, iv1]) & !is.na(p.demean[, iv2]),]

total <-
  plot_twovariable(
    demean_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin=-10, ymax=10, xmin=-40, xmax=40,
    xlab ,ylab,
    ggtitle = "all stimulus intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#BBBBBB"),
    alpha = .8, fit_lm = TRUE, lm_method ="lm", identity_line = FALSE
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for NPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )

```

### 7-4. [correct] NPSgmc \~ EXPECTcmc \* cue \* stim {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

# plot parameters
###################
iv1 = "EXPECT_cmc"
iv2 = "NPS_gmc"
subject = "sub"
xlab = "Expectation rating \n(CMC; cluster group mean-centered)"
ylab = paste(signature_key, "\n(grand mean-centered")
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
yminval=-20; ymaxval=20; xminval=-90; xmaxval=90;
###################

# low stimulus intensity
demean_low = demean_dropna[demean_dropna$stimintensity == "low", ]
low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=yminval, ymax=ymaxval, xmin=xminval, xmax=xmaxval,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimintensity == "med", ]
med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=yminval, ymax=ymaxval, xmin=xminval, xmax=xmaxval,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimintensity == "high", ]
high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=yminval, ymax=ymaxval, xmin=xminval, xmax=xmaxval,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```

- <https://stats.stackexchange.com/questions/365466/significance-of-slope-different-than-zero-in-triple-interaction-with-factors>
- <https://stats.stackexchange.com/questions/586748/calculating-trends-with-emtrends-for-three-way-interaction-model-results-in-sa>
- emtrends(model.npsexpectdemean, var = 'EXPECT_demean', lmer.df = "asymptotic")

### 7-5. ICC

```{r include=FALSE}
compute_icc <- function(lmer_object){
  var_dat <- lmer_object %>% VarCorr %>% as.data.frame
  icc <- var_dat$vcov[1]/(var_dat$vcov[1]+var_dat$vcov[2])
  return(icc)
}
```

```{r}
compute_icc(model.npsexpectdemean)
```

> The ICC of the dependent variable is .30 and thus very close to the value that we wanted to simulate. It means that about 30% of the variance in this variable is explainable by interindividual differences (i.e., person-related characteristics). This also means that a larger part of the variance is potentially explainable by situational characteristics (e.g., by other variables measured on level 1).

```{r}
emtrends(model.npsexpectdemean, var = 'EXPECT_demean', lmer.df = "asymptotic")
```

### eta squared {.unlisted .unnumbered}

```{r echo=FALSE, warning=TRUE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.npsexpectdemean, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

### Cohen's d {.unlisted .unnumbered}

```{r echo=FALSE, warning=TRUE}
kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.npsexpectdemean, demean_dropna, type = "lme4"), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

### 7-6 simple slopes when STIM == 'high', EXPECT_demean slope difference between high vs. low cue {.unlisted .unnumbered}

```{r}
interactions::sim_slopes(model=model.npsexpectdemean, pred=EXPECT_demean, modx=CUE_high_gt_low, mod2 =STIM_linear, mod2.values = 0.5, centered = 'all', data = demean_dropna)

```

#### emtrneds {.unlisted .unnumbered}

```{r}
emt.t <- emtrends(model.npsexpectdemean, ~ STIM_linear | CUE_high_gt_low,
         var = "EXPECT_demean",
         # nuisance = c("EXPECT_cmc"),
         at = list(STIM_linear=c(0.5, 0, -0.5)),
         lmer.df = "asymp")
pairs(emt.t, simple = "each")
# contrast(emt.t, "revpairwise")
```

```{r eval=FALSE, include=FALSE}
library(reghelper)
simple_slopes(model.npsexpectdemean,
        levels=list(STIM_linear=c(0.5, 'sstest'),
        CUE_high_gt_low=c(0.5,-0.5, 'sstest')))  # test at specific levels
```

## 8. NPS and session effects

```{r include=FALSE}
# code session
# contrast code 1 linear
demean_dropna$SES_linear[demean_dropna$ses == "ses-01"] <- -0.5
demean_dropna$SES_linear[demean_dropna$ses == "ses-03"] <- 0
demean_dropna$SES_linear[demean_dropna$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
demean_dropna$SES_quadratic[demean_dropna$ses == "ses-01"] <- -0.33
demean_dropna$SES_quadratic[demean_dropna$ses == "ses-03"] <- 0.66
demean_dropna$SES_quadratic[demean_dropna$ses == "ses-04"] <- -0.33

```

#### 8-1. [correct] NPS \~ EXPECT_demean \* CUE \* STIM + CMC (Session as covariate) {.unlisted .unnumbered}

```{r echo=TRUE, message=TRUE, warning=TRUE, paged.print=FALSE}

model.npsexpectdemean.sescontrol <- lmer(NPS_gmc ~
                          CUE_high_gt_low*STIM_linear*EXPECT_demean +
                          CUE_high_gt_low*STIM_quadratic*EXPECT_demean +
                          # CUE_high_gt_low*STIM_linear*EXPECT_demean +
                          # CUE_high_gt_low*STIM_quadratic*EXPECT_demean +
                          EXPECT_cmc +
                          ses +
                          (CUE_high_gt_low|sub), data = demean_dropna
                    )
# CUE_high_gt_low+STIM+EXPECT_demean
sjPlot::tab_model(model.npsexpectdemean.sescontrol,
                  title = "Multilevel-modeling: \nlmer(NPSpos ~ CUE * STIM * EXPECT_demean + SES + (CUE + EXPECT| sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

#### 8-2. [correct] NPS \~ EXPECT_demean \* CUE \* STIM \* SES + CMC (Session as interaction) {.unlisted .unnumbered}

```{r echo=TRUE, message=TRUE, warning=TRUE, paged.print=FALSE}

model.npsexpectdemean.ses <- lmer(NPS_gmc ~
                          CUE_high_gt_low*STIM_linear*EXPECT_demean*SES_linear +
                          CUE_high_gt_low*STIM_quadratic*EXPECT_demean*SES_linear +
                          CUE_high_gt_low*STIM_linear*EXPECT_demean*SES_quadratic +
                          CUE_high_gt_low*STIM_quadratic*EXPECT_demean*SES_quadratic +
                          EXPECT_cmc +
                          (CUE_high_gt_low|sub) + (1|ses), data = demean_dropna
                    )
# CUE_high_gt_low+STIM+EXPECT_demean
sjPlot::tab_model(model.npsexpectdemean.ses,
                  title = "Multilevel-modeling: \nlmer(NPS_gmc ~ CUE * STIM * EXPECT_demean * SES + EXPECT_cmc + (CUE| sub) + (1|ses), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

## 9. plotly 3 factors

```{r echo=FALSE}
# paindf <- data_screen[data_screen$runtype == "runtype-pain",]
remove_sub_list = c("sub-0009") # "sub-0117", "sub-0081", "sub-0060", "sub-0063", "sub-0074", "sub-0085", "sub-0098", "sub-0118")
df_merge_drop <- subset(df_merge, !(sub %in% remove_sub_list))
subset_ses <-  df_merge_drop[df_merge_drop$task == 'pain',]
p.demean <- subset_ses %>%
  group_by(sub) %>%
  mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
  mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
  mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
  mutate(OUTCOME_demean = event04_actual_angle - avg_outcome) %>%
  mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
  mutate(EXPECT_demean = event02_expect_angle - avg_expect) %>%
  group_by(sub, ses) %>%
  mutate(NPSpos = as.numeric(NPSpos)) %>%
  mutate(avg_NPS = mean(NPSpos, na.rm = TRUE)) %>%
  mutate(NPS_demean = NPSpos - avg_NPS) %>%
  ungroup %>%
  mutate(OUTCOME_cmc = avg_outcome - mean(avg_outcome)) %>%
  mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) %>%
  mutate(NPS_cmc = avg_NPS - mean(avg_NPS))

plotly_subjectwise <- meanSummary(
        p.demean,
        c("sub","ses",  "cuetype", "stimintensity", "EXPECT_demean"), c("NPSpos")
    )
```

```{r echo=FALSE}
library(plotly)
# lmer(NPSpos ~ CUE_high_gt_low*STIM_linear*event02_expect_angle + CUE_high_gt_low*STIM_quadratic*event02_expect_angle + (CUE_high_gt_low|sub), data = data_screen)
ses1 = p.demean[p.demean$ses == "ses-01",]
x <- seq_len(nrow(volcano)) + 100
y <- seq_len(ncol(volcano)) + 500
fig <- plot_ly(ses1, x = ~cuetype, y = ~EXPECT_demean, z = ~NPSpos) %>% #colors = c('#BF382A','yellow', '#0C4B8E'))
  # group_by(STIM) %>%
  group_by(STIM_linear) %>%
  # add_markers(color = ~STIM_linear) %>%
  # group_by(cuetype) %>%
  add_lines(color = ~STIM_linear)

fig <- fig %>% layout(scene = list
                      (
                        xaxis = list(title = 'Cue'),
                        zaxis = list(title = 'NPSpos'),
                        yaxis = list(title = 'Expectation rating')
                        ))

fig
```

```{r}
library(plotly)
ses1.Lh = p.demean[p.demean$ses == "ses-01" & p.demean$STIM == "low" & p.demean$cue_name == "high",]
ses1.Lph <- plot_ly(ses1.Lh,x = ~EXPECT_demean, y = ~NPSpos)
ses1.Mh = p.demean[p.demean$ses == "ses-01" & p.demean$STIM == "med" & p.demean$cue_name == "high",]
ses1.Mph <- plot_ly(ses1.Mh,x = ~EXPECT_demean, y = ~NPSpos)
ses1.Hh = p.demean[p.demean$ses == "ses-01" & p.demean$STIM == "high" & p.demean$cue_name == "high",]
ses1.Hph <- plot_ly(ses1.Hh,x = ~EXPECT_demean, y = ~NPSpos )

ses1.Ll = p.demean[p.demean$ses == "ses-01" & p.demean$STIM == "low" & p.demean$cue_name == "low",]
ses1.Lpl <- plot_ly(ses1.Ll,x = ~EXPECT_demean, y = ~NPSpos)
ses1.Ml = p.demean[p.demean$ses == "ses-01" & p.demean$STIM == "med" & p.demean$cue_name == "low",]
ses1.Mpl <- plot_ly(ses1.Ml,x = ~EXPECT_demean, y = ~NPSpos)
ses1.Hl = p.demean[p.demean$ses == "ses-01" & p.demean$STIM == "high"& p.demean$cue_name == "low",]
ses1.Hpl <- plot_ly(ses1.Hl,x = ~EXPECT_demean, y = ~NPSpos )

subplot(
  add_histogram2d(ses1.Lph, zsmooth = "best") %>%
    colorbar() %>%
    layout(xaxis = list(title = "low_stim high_cue")),
  add_histogram2d(ses1.Mph, zsmooth = "best") %>%
    colorbar() %>%
    layout(xaxis = list(title = "med_stim high_cue")),
  add_histogram2d(ses1.Hph, zsmooth = "best") %>%
    colorbar() %>%
    layout(xaxis = list(title = "high_stim high_cue")),

  add_histogram2d(ses1.Lpl, zsmooth = "best") %>%
    colorbar() %>%
    layout(xaxis = list(title = "low_stim")),
  add_histogram2d(ses1.Mpl, zsmooth = "best") %>%
    colorbar() %>%
    layout(xaxis = list(title = "med_stim")),
  add_histogram2d(ses1.Hpl, zsmooth = "best") %>%
    colorbar() %>%
    layout(xaxis = list(title = "high_stim")),
  shareY = TRUE, titleX = TRUE
)
```

```{r}
# save tsv
test = ses1[, c("sub", "cuetype", "stimintensity", "EXPECT_demean", "NPSpos")]

write.table(test, file=file.path(analysis_dir, "model40test.tsv"), quote=FALSE, sep='\t', row.names = FALSE)

```

#### 3x3 plots EXPECT_demean {.unlisted .unnumbered}

```{r echo=FALSE}
iv1 = "EXPECT_demean"; iv2 = "NPS_gmc" # "NPS_demean"
group = "cuetype"; subject = "sub"
xlab = "Expectation rating \n(subjectwise mean-centered)"
ylab = paste(signature_key)
remove_xy <- theme(
  axis.text.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.x = element_blank(),
    axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank(),
  plot.margin = unit(c(0,0.2,0,1), 'lines')
)
yminval = -30; ymaxval = 40; xminval = -70; xmaxval = 70

# low stimulus intensity
demean_low = demean_dropna[demean_dropna$stimintensity == "low" & demean_dropna$ses == "ses-01", ]
ses01low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin = yminval, ymax = ymaxval, xmin = xminval, xmax = xmaxval,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimintensity == "med" & demean_dropna$ses == "ses-01", ]
ses01med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin = yminval, ymax = ymaxval, xmin = xminval, xmax = xmaxval,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimintensity == "high" & demean_dropna$ses == "ses-01", ]
ses01high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin = yminval, ymax = ymaxval, xmin = xminval, xmax = xmaxval,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
# ses 03 ________________________
demean_low = demean_dropna[demean_dropna$stimintensity == "low" & demean_dropna$ses == "ses-03", ]
ses03low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin = yminval, ymax = ymaxval, xmin = xminval, xmax = xmaxval,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimintensity == "med" & demean_dropna$ses == "ses-03", ]
ses03med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin = yminval, ymax = ymaxval, xmin = xminval, xmax = xmaxval,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimintensity == "high" & demean_dropna$ses == "ses-03", ]
ses03high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin = yminval, ymax = ymaxval, xmin = xminval, xmax = xmaxval,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# ses 04 ________________________
demean_low = demean_dropna[demean_dropna$stimintensity == "low" & demean_dropna$ses == "ses-04", ]
ses04low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin = yminval, ymax = ymaxval, xmin = xminval, xmax = xmaxval,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimintensity == "med" & demean_dropna$ses == "ses-04", ]
ses04med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin = yminval, ymax = ymaxval, xmin = xminval, xmax = xmaxval,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimintensity == "high" & demean_dropna$ses == "ses-04", ]
ses04high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin = yminval, ymax = ymaxval, xmin = xminval, xmax = xmaxval,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(ses01low+remove_xy, ses01med+remove_xy, ses01high+remove_xy,
                           ses03low+remove_xy, ses03med+remove_xy, ses03high+remove_xy,
                           ses04low+remove_xy, ses04med+remove_xy, ses04high+remove_xy,
                           ncol = 3, nrow = 3, common.legend = TRUE, legend = "bottom",
                           widths = c(1, 1, 1))

plots_title <- annotate_figure(plots,
                               top =
                                 text_grob(paste(str_to_title(taskname),
                                                 "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"),
                                           color = "black", face = "bold", size = 12),
                               left = text_grob("NPSpos (dot product)", rot = 90, vjust = 1),
                               bottom = text_grob("Expectation rating\n(subjectwise mean-centering)")
                               )
plots_title

```

```{r}

fig.height = 50
fig.width = 10
ggplot(aes(x=EXPECT_demean, y=NPSpos, color = CUE_high_gt_low, shape =), data=demean_dropna) +
  geom_smooth(method='lm', se=F, size=0.75) +
  geom_point(size=0.1) +
    # geom_abline(intercept = 0, slope = 1, color="green",
    #              linetype="dashed", size=0.5) +
  facet_wrap(~ses) +
  theme(legend.position='none') +
  xlim(-50,50) + ylim(-50,50) +
  xlab("raw data from each participant: n-1 lagged outcome angle") +
  ylab("n current expectation rating")

```

#### NPSpos \~ EXPECT_demean \* STIM \* CUE {.unlisted .unnumbered}

```{r echo=FALSE}
iv1 = "EXPECT_demean" #"event02_expect_angle";
iv2 = "NPSpos" # "NPS_demean"
group = "cuetype"; subject = "sub"
xlab = "Expectation rating \n(subjectwise mean-centered)"
ylab = paste(signature_key)
remove_xy <- theme(
  axis.text.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.x = element_blank(),
    axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank(),
  plot.margin = unit(c(0,0.2,0,1), 'lines')
)

remove_x <- theme(
  axis.text.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.x = element_blank(),
  plot.margin = unit(c(0,0.2,0,1), 'lines')
)

remove_y <- theme(
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank(),
  plot.margin = unit(c(0,0.2,0,1), 'lines')
)

xmin_val = -60
xmax_val = 45
ymin_val = -20
ymax_val = 60
# low stimulus intensity
demean_low = demean_dropna[demean_dropna$stimintensity == "low" & demean_dropna$ses == "ses-01", ]
ses01low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimintensity == "med" & demean_dropna$ses == "ses-01", ]
ses01med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimintensity == "high" & demean_dropna$ses == "ses-01", ]
ses01high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
# ses 03 ________________________
demean_low = demean_dropna[demean_dropna$stimintensity == "low" & demean_dropna$ses == "ses-03", ]
ses03low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimintensity == "med" & demean_dropna$ses == "ses-03", ]
ses03med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimintensity == "high" & demean_dropna$ses == "ses-03", ]
ses03high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# ses 04 ________________________
demean_low = demean_dropna[demean_dropna$stimintensity == "low" & demean_dropna$ses == "ses-04", ]
ses04low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimintensity == "med" & demean_dropna$ses == "ses-04", ]
ses04med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimintensity == "high" & demean_dropna$ses == "ses-04", ]
ses04high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(ses01low+remove_x, ses01med+remove_xy, ses01high+remove_xy,
                           ses03low+remove_x, ses03med+remove_xy, ses03high+remove_xy,
                           ses04low, ses04med+remove_y, ses04high+remove_y,
                           ncol = 3, nrow = 3, common.legend = TRUE, legend = "bottom",
                           widths = c(1, 1, 1))

plots_title <- annotate_figure(plots,
                               top =
                                 text_grob(paste(str_to_title(taskname),
                                                 "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"),
                                           color = "black", face = "bold", size = 12),
                               left = text_grob("NPSpos (dot product)", rot = 90, vjust = 1),
                               bottom = text_grob("Expectation rating\n(subjectwise mean-centering)")
                               )
plots_title

```

## 9. NPS \~ trial order

```{r}
pvc$run_num = as.numeric(as.factor(pvc$run))
pvc <- pvc %>%
  dplyr::group_by(sub, ses, runtype) %>%
  dplyr::mutate(mean_run = mean(run_num))
# compared to mean_run, is the run_num smaller or larger?
pvc$formerlatter_run <-
  ifelse(pvc$mean_run >= pvc$run_num , "former", "latter")
pvc$ses_run <-
  interaction(pvc$formerlatter_run, pvc$ses, sep = "_")
NPStrialorder = pvc
```

```{r}
NPStrialorder$ses_run <-
  interaction(NPStrialorder$formerlatter_run, NPStrialorder$ses, sep = "_")

NPStrialorder$ses_run_trial <-
  interaction(NPStrialorder$trial,NPStrialorder$formerlatter_run, NPStrialorder$ses, sep = "_")

NPStrialorder$ses_run_num <- as.numeric(as.factor(NPStrialorder$ses_run))
NPStrialorder$ses_run_trial_num <- as.numeric(as.factor(NPStrialorder$ses_run_trial))
```

```{r}
data.frame(table(NPStrialorder$ses_run_trial_num ))
```

## pain {.tabset}

### trial order \* cue {.unlisted .unnumbered}

```{r echo=FALSE}
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    dv <- "NPSpos"
    subject = "ses_run_trial_num"
    trialorder_subjectwise_p2 <- meanSummary(
        NPStrialorder[NPStrialorder$runtype == "runtype-pain",],
        c(  model_iv2, "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)

iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_subjectwise_p2,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "lm",
    data = trialorder_subjectwise_p2,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      color = cue_ordered,
      # linetype = as.factor(stim_ordered)
      )) +
    geom_point(
    data = trialorder_subjectwise_p2,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # linetype = as.factor(stim_ordered),
      color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      colour = cue_ordered,
      # linetype = as.factor(stim_ordered),
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPSpos") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(0,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g  +
  annotate("text", x = 0+2, y = 25, label = "ses-01", size = 2) +
  annotate("text", x = 24+4, y = 25, label = "ses-03", size = 2) +
  annotate("text", x = 48+4, y = 25, label = "ses-04", size = 2) +

  annotate("text", x = 0+8, y = 24, label = "1st run", size = 2) +
  annotate("text", x = 12+8, y = 24, label = "2nd run", size = 2) +
  annotate("text", x = 24+8, y = 24, label = "1st run", size = 2) +
  annotate("text", x = 36+8, y = 24, label = "2nd run", size = 2) +
  annotate("text", x = 48+8, y = 24, label = "1st run", size = 2) +
  annotate("text", x = 60+8, y = 24, label = "2nd run", size = 2)
```

### trial order only {.unlisted .unnumbered}

```{r echo=FALSE}
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    # rating <- "NPSpos"
    dv <- "NPSpos"
    subject = "ses_run_trial_num"
    trialorder_summary <- meanSummary(
        NPStrialorder[NPStrialorder$runtype == "runtype-pain",],
        c( "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)


iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_summary,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_summary,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # color = cue_ordered,
      # linetype = as.factor(stim_ordered)
      )) +
    geom_point(
    data = trialorder_summary,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # linetype = as.factor(stim_ordered),
      # color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_summary,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # colour = cue_ordered,
      # linetype = as.factor(stim_ordered),
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPSpos") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(0,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g
```

```{r}
model.trial = lm(NPSpos ~ trial*cuetype, data = NPStrialorder[NPStrialorder$runtype == "runtype-pain",], )
Anova(model.trial, type = "III")
summary(model.trial)
```

```{r}
model.trial = lm(NPSpos ~ trial*cuetype, data = NPStrialorder[NPStrialorder$runtype == "runtype-pain",], )
Anova(model.trial, type = "III")
summary(model.trial)
```

## pain per session {.tabset}

### trial order \* cue \* ses 01 {.unlisted .unnumbered}

```{r echo=FALSE}
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    dv <- "NPSpos"
    subject = "ses_run_trial_num"
    trialorder_subjectwise_p2 <- meanSummary(
        NPStrialorder[(NPStrialorder$runtype == "runtype-pain") & (NPStrialorder$ses == "ses-01" ),],
        c(  model_iv2, "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)

iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_subjectwise_p2,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered,
      )) +
    geom_point(
    data = trialorder_subjectwise_p2,
    aes(
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered
      ),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  geom_errorbar(
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      colour = cue_ordered,
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPSpos") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(0,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g  +
  annotate("text", x = 0+2, y = 25, label = "ses-01", size = 2) +
  annotate("text", x = 24+4, y = 25, label = "ses-03", size = 2) +
  annotate("text", x = 48+4, y = 25, label = "ses-04", size = 2) +

  annotate("text", x = 0+8, y = 24, label = "1st run", size = 2) +
  annotate("text", x = 12+8, y = 24, label = "2nd run", size = 2) +
  annotate("text", x = 24+8, y = 24, label = "1st run", size = 2) +
  annotate("text", x = 36+8, y = 24, label = "2nd run", size = 2) +
  annotate("text", x = 48+8, y = 24, label = "1st run", size = 2) +
  annotate("text", x = 60+8, y = 24, label = "2nd run", size = 2)
```

### trial order \* cue \* ses-03 {.unlisted .unnumbered}

```{r echo=FALSE}
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    dv <- "NPSpos"
    subject = "ses_run_trial_num"
    trialorder_subjectwise_p2 <- meanSummary(
        NPStrialorder[(NPStrialorder$runtype == "runtype-pain") & (NPStrialorder$ses == "ses-03" ),],
        c(  model_iv2, "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)

iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_subjectwise_p2,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered,
      )) +
    geom_point(
    data = trialorder_subjectwise_p2,
    aes(
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered
      ),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  geom_errorbar(
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      colour = cue_ordered,
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPSpos") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(0,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g  +
  annotate("text", x = 0+2, y = 25, label = "ses-01", size = 2) +
  annotate("text", x = 24+4, y = 25, label = "ses-03", size = 2) +
  annotate("text", x = 48+4, y = 25, label = "ses-04", size = 2) +

  annotate("text", x = 0+8, y = 24, label = "1st run", size = 2) +
  annotate("text", x = 12+8, y = 24, label = "2nd run", size = 2) +
  annotate("text", x = 24+8, y = 24, label = "1st run", size = 2) +
  annotate("text", x = 36+8, y = 24, label = "2nd run", size = 2) +
  annotate("text", x = 48+8, y = 24, label = "1st run", size = 2) +
  annotate("text", x = 60+8, y = 24, label = "2nd run", size = 2)
```

### trial order \* cue \* ses-04 {.unlisted .unnumbered}

```{r echo=FALSE}
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    dv <- "NPSpos"
    subject = "ses_run_trial_num"
    trialorder_subjectwise_p2 <- meanSummary(
        NPStrialorder[(NPStrialorder$runtype == "runtype-pain") & (NPStrialorder$ses == "ses-04" ),],
        c(  model_iv2, "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)

iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_subjectwise_p2,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered,
      )) +
    geom_point(
    data = trialorder_subjectwise_p2,
    aes(
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered
      ),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  geom_errorbar(
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      colour = cue_ordered,
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPSpos") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(0,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g  +
  annotate("text", x = 0+2, y = 25, label = "ses-01", size = 2) +
  annotate("text", x = 24+4, y = 25, label = "ses-03", size = 2) +
  annotate("text", x = 48+4, y = 25, label = "ses-04", size = 2) +

  annotate("text", x = 0+8, y = 24, label = "1st run", size = 2) +
  annotate("text", x = 12+8, y = 24, label = "2nd run", size = 2) +
  annotate("text", x = 24+8, y = 24, label = "1st run", size = 2) +
  annotate("text", x = 36+8, y = 24, label = "2nd run", size = 2) +
  annotate("text", x = 48+8, y = 24, label = "1st run", size = 2) +
  annotate("text", x = 60+8, y = 24, label = "2nd run", size = 2)
```

## vicarious {.tabset}

### trial order \* cue {.unlisted .unnumbered}

```{r echo=FALSE}
taskname = "vicarious"
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    dv <- "NPSpos"
    subject = "ses_run_trial_num"
    trialorder_subjectwise_p2 <- meanSummary(
        NPStrialorder[NPStrialorder$runtype == "runtype-vicarious",],
        c(  model_iv2, "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)


iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_subjectwise_p2,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_subjectwise_p2,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      color = cue_ordered,
      # linetype = as.factor(stim_ordered)
      )) +
    geom_point(
    data = trialorder_subjectwise_p2,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # linetype = as.factor(stim_ordered),
      color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      colour = cue_ordered,
      # linetype = as.factor(stim_ordered),
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPSpos") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(-5,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g
```

### trial order only {.unlisted .unnumbered}

```{r echo=FALSE}
taskname = "vicarious"
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    # rating <- "NPSpos"
    dv <- "NPSpos"
    subject = "ses_run_trial_num"
    trialorder_summary <- meanSummary(
        NPStrialorder[NPStrialorder$runtype == "runtype-vicarious",],
        c( "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)


iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_summary,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_summary,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # color = cue_ordered,
      # linetype = as.factor(stim_ordered)
      )) +
    geom_point(
    data = trialorder_summary,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # linetype = as.factor(stim_ordered),
      # color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_summary,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # colour = cue_ordered,
      # linetype = as.factor(stim_ordered),
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPSpos") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(-5,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g
```

## cognitive {.tabset}

### trial order \* cue {.unlisted .unnumbered}

```{r echo=FALSE}
taskname = "cognitive"
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    dv <- "NPSpos"
    subject = "ses_run_trial_num"
    trialorder_subjectwise_p2 <- meanSummary(
        NPStrialorder[NPStrialorder$runtype == "runtype-cognitive",],
        c(  model_iv2, "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)


iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_subjectwise_p2,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_subjectwise_p2,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      color = cue_ordered,
      # linetype = as.factor(stim_ordered)
      )) +
    geom_point(
    data = trialorder_subjectwise_p2,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # linetype = as.factor(stim_ordered),
      color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      colour = cue_ordered,
      # linetype = as.factor(stim_ordered),
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPSpos") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(-5,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g
```

### trial order only {.unlisted .unnumbered}

```{r echo=FALSE}
taskname = "cognitive"
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    # rating <- "NPSpos"
    dv <- "NPSpos"
    subject = "ses_run_trial_num"
    trialorder_summary <- meanSummary(
        NPStrialorder[NPStrialorder$runtype == "runtype-cognitive",],
        c( "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)


iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_summary,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_summary,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # color = cue_ordered,
      # linetype = as.factor(stim_ordered)
      )) +
    geom_point(
    data = trialorder_summary,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # linetype = as.factor(stim_ordered),
      # color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_summary,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # colour = cue_ordered,
      # linetype = as.factor(stim_ordered),
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPSpos") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(-5,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g
```
