# [fMRI] FIR ~ task {#ch50_fir_glasser}

---
title: "50_iv-6cond_dv-firglasserSPM_ttl2_rINS"
output: html_document
date: "2023-08-14"
---


TODO
* load tsv
* concatenate 
* per time column, calculate mean and variance
* plot

```{r libraries, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(psych)
library(reshape)
library(plyr)
library(dplyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(ggpubr)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
main_dir = dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, "scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

## parameters {TODO: ignore}
```{r}

# parameters
main_dir <- dirname(dirname(getwd()))
ROI <- "rINS"
datadir <- file.path(main_dir, 'analysis/fmri/nilearn/glm/fir')
analysis_folder  = paste0("model50_iv-6cond_dv-firglasserSPM_ttl2_", ROI)
analysis_dir <-
  file.path(main_dir,
            "analysis",
            "mixedeffect",
            analysis_folder,
            as.character(Sys.Date())) # nolint
dir.create(analysis_dir,
           showWarnings = FALSE,
           recursive = TRUE)
save_dir <- analysis_dir
```

```{r}

plot_timeseries_onefactor <-  function(df, iv1,  mean, error, xlab, ylab, ggtitle, color) {
    
n_points <- 100  # Number of points for interpolation
    g <- ggplot(
      data = df,
      aes(
        x = .data[[iv1]],
        y = .data[[mean]],
        group = 1,
        color = color
      ),
      cex.lab = 1.5,
      cex.axis = 2,
      cex.main = 1.5,
      cex.sub = 1.5
    ) +

      geom_errorbar(aes(
        ymin = (.data[[mean]] - .data[[error]]),
        ymax = (.data[[mean]] + .data[[error]]),
        color = color
      ), width = .1, alpha=0.8) +

      geom_line() +
      geom_point(color=color) +
      ggtitle(ggtitle) +
      xlab(xlab) +
      ylab(ylab) +

      theme_classic() +
      
      theme(aspect.ratio = .6) +
      expand_limits(x = 3.25) +

      scale_color_manual("",
                         values =  color) +
            # scale_fill_manual("",
                         # values =  color) +
      theme(
        legend.position = c(.99, .99),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      theme(legend.key = element_rect(fill = "white", colour = "white")) +
      theme_bw()
    
    return(g)
  }
```

## load dataframe
```{r}
# ------------------------------------------------------------------------------
#                       epoch stim, high stim vs low stim
# ------------------------------------------------------------------------------
datadir = file.path(main_dir, "analysis/fmri/spm/fir/ttl2par")
taskname = 'pain'
exclude <- "sub-0001"
filename <- paste0("sub-*",  "*roi-", ROI, "_tr-42.csv")
  common_path <- Sys.glob(file.path(datadir, "sub-*",  filename
  ))
  filter_path <- common_path[!str_detect(common_path, pattern = exclude)]

df <- do.call("rbind.fill", lapply(filter_path, FUN = function(files) {
    read.table(files, header = TRUE, sep = ",")
    }))
```

## taskwise stim effect
```{r}
run_types <- c("pain", "vicarious", "cognitive")
  plot_list <- list()
  TR_length <- 42
for (run_type in run_types) {
  print(run_type)
  filtered_df <- df[!(df$condition == "rating" | df$condition == "cue" | df$runtype != run_type), ]

  parsed_df <- filtered_df %>%
    separate(condition, into = c("cue", "stim"), sep = "_", remove = FALSE)
  # --------------------- subset regions based on ROI ----------------------------
  df_long <- pivot_longer(parsed_df, cols = starts_with("tr"), names_to = "tr_num", values_to = "tr_value")

  # ----------------------------- clean factor -----------------------------------
  df_long$tr_ordered <- factor(
          df_long$tr_num,
          levels = c(paste0("tr", 1:TR_length))
      )
  df_long$stim_ordered <- factor(
          df_long$stim,
          levels = c("stimH", "stimM", "stimL")
      )

  # --------------------------- summary statistics -------------------------------
  subjectwise <- meanSummary(df_long,
                                        c("sub","tr_ordered", "stim_ordered"), "tr_value")
  groupwise <- summarySEwithin(
    data = subjectwise,
    measurevar = "mean_per_sub",
    withinvars = c( "stim_ordered", "tr_ordered"),
    idvar = "sub"
  )
  groupwise$task <- run_type
  # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

  # ... Rest of your data processing code ...
  
  # subset <- groupwise[groupwise$runtype == run_type, ]
  # TODO: count number of participants and add number
  LINEIV1 = "tr_ordered"
  LINEIV2 = "stim_ordered"
  MEAN = "mean_per_sub_norm_mean"
  ERROR = "se"
  dv_keyword = "actual"
  sorted_indices <- order(groupwise$tr_ordered)
  groupwise_sorted <- groupwise[sorted_indices, ]
  p1 <- plot_timeseries_bar(groupwise_sorted, 
                            LINEIV1, LINEIV2, MEAN, ERROR,  
                            xlab = "TRs", 
                            ylab = paste0(ROI, " activation (A.U.)"), 
                            ggtitle = paste0(run_type, " (N = ", length(unique(subjectwise$sub)),") time series, Epoch - stimulus"),
                            color = c("#5f0f40","#ae2012", "#fcbf49"))
  time_points <- seq(1, 0.46 * TR_length, 0.46)
  #p1 <- p1 + scale_x_discrete(labels = setNames(time_points, colnames(df_long)[7:(7 + TR_length)])) + theme_classic()
  
  plot_list[[run_type]] <- p1 + theme_classic()
}
  
  # --------------------------- plot three tasks -------------------------------
library(gridExtra)
plot_list <- lapply(plot_list, function(plot) {
  plot + theme(plot.margin = margin(5, 5, 5, 5))  # Adjust plot margins if needed
})
combined_plot <- ggpubr::ggarrange(plot_list[["pain"]],plot_list[["vicarious"]],plot_list[["cognitive"]],
                  common.legend = TRUE,legend = "bottom", ncol = 3, nrow = 1, 
                  widths = c(3, 3, 3), heights = c(.5,.5,.5), align = "v")
combined_plot
ggsave(file.path(save_dir, "taskwise_epoch-stim_desc-highcueGTlowcue.png"), combined_plot, width = 12, height = 4)
```






### PCA subjectwise
```{r}
# install.packages("ggplot2")    # Install ggplot2 if you haven't already
# install.packages("FactoMineR") # Install FactoMineR if you haven't already
library(ggplot2)
library(FactoMineR)
run_types = c("pain")
for (run_type in run_types) {
  print(run_type)
  filtered_df <- df[!(df$condition == "rating" | df$condition == "cue" | df$runtype != run_type), ]

  parsed_df <- filtered_df %>%
    separate(condition, into = c("cue", "stim"), sep = "_", remove = FALSE)
  # --------------------- subset regions based on ROI ----------------------------
  df_long <- pivot_longer(parsed_df, cols = starts_with("tr"), names_to = "tr_num", values_to = "tr_value")

  # ----------------------------- clean factor -----------------------------------
  df_long$tr_ordered <- factor(
          df_long$tr_num,
          levels = c(paste0("tr", 1:TR_length))
      )
  df_long$stim_ordered <- factor(
          df_long$stim,
          levels = c("stimH", "stimM", "stimL")
      )

  # --------------------------- summary statistics -------------------------------
  subjectwise <- meanSummary(df_long,
                                        c("sub","tr_ordered", "stim_ordered"), "tr_value")

# Assuming your original dataframe is named 'df'

# Convert the dataframe to wide format
df_wide <- pivot_wider(subjectwise, 
                       id_cols = c("tr_ordered", "stim_ordered"), 
                       names_from = c("sub"), 
                       values_from = "mean_per_sub")

# df_wide <- pivot_wider(subjectwise, 
#                        id_cols = c("sub", "ROIindex","stim_ordered"), 
#                        names_from = "tr_ordered", 
#                        values_from = "mean_per_sub")
stim_high.df <- df_wide[df_wide$stim_ordered == "stimH",]
stim_med.df <- df_wide[df_wide$stim_ordered == "stimM",]
stim_low.df <- df_wide[df_wide$stim_ordered == "stimL",]
# selected_columns <- subset(stim_high.df, select = 2:(ncol(stim_high.df) - 1))
meanhighdf <- data.frame(subset(stim_high.df, select = 3:(ncol(stim_high.df) - 1)))
high.pca_result <- prcomp(meanhighdf)
high.pca_scores <- as.data.frame(high.pca_result$x)
# Access the proportion of variance explained by each principal component
high.variance_explained <- high.pca_result$sdev^2 / sum(high.pca_result$sdev^2)
plot(high.variance_explained)
# Access the standard deviations of each principal component
high.stdev <- high.pca_result$sdev

meanmeddf <- data.frame(subset(stim_med.df, select = 3:(ncol(stim_med.df) - 1)))
med.pca <- prcomp(meanmeddf)
med.pca_scores <- as.data.frame(med.pca$x)

meanlowdf <- data.frame(subset(stim_low.df, select = 3:(ncol(stim_low.df) - 1)))
low.pca <- prcomp(meanlowdf)
low.pca_scores <- as.data.frame(low.pca$x)
library(plotly)  # You can use plotly to create an interactive 3D plot
# plot_ly(high.pca_scores, x = ~PC1, y = ~PC2, z = ~PC3, type = "scatter3d", mode = "markers")
# plot_ly(low.pca_scores, x = ~PC1, y = ~PC2, z = ~PC3, type = "scatter3d", mode = "markers")
combined_pca_scores <- rbind(high.pca_scores, med.pca_scores, low.pca_scores)

# Add a new column to indicate the stim_ordered category (high_stim or low_stim)
combined_pca_scores$stim_ordered <- c(rep("high_stim", nrow(high.pca_scores)), 
                                      rep("med_stim", nrow(med.pca_scores)), 
                                      rep("low_stim", nrow(low.pca_scores)))

# Create the 3D PCA plot
plot_ly(combined_pca_scores, x = ~PC1, y = ~PC2, z = ~PC3, type = "scatter3d", mode = "markers",
        color = ~stim_ordered)
# data_matrix <- groupwise[groupwise$stim_ordered == "high_stim",c("tr_ordered", "mean_per_sub_norm_mean")]
# sorted_indices <- order(data_matrix$tr_ordered)
# df_ordered <- data_matrix[sorted_indices, ]
# pca_result <- PCA(data_matrix$mean_per_sub_norm_mean)
# datapoints <- df$datapoints
}
```
```{r}
plot_ly(combined_pca_scores, x = ~PC1, y = ~PC2, z = ~PC3, type = "scatter3d", mode = "markers",
        color = ~stim_ordered)
```


### PCA groupwise
```{r}
# install.packages("ggplot2")    # Install ggplot2 if you haven't already
# install.packages("FactoMineR") # Install FactoMineR if you haven't already
library(ggplot2)
library(FactoMineR)



# Assuming your original dataframe is named 'df'

# Convert the dataframe to wide format
df_wide.group <- pivot_wider(subjectwise,
                       id_cols = c("tr_ordered", "stim_ordered"),
                       names_from = "sub",
                       values_from = "mean_per_sub")
# ------
# data_matrix <- groupwise[groupwise$stim_ordered == "high_stim",c("tr_ordered", "mean_per_sub_norm_mean")]
# sorted_indices <- order(data_matrix$tr_ordered)
# df_ordered <- data_matrix[sorted_indices, ]
# datapoints <- df_ordered$mean_per_sub_norm_mean
# data_df <- data.frame(Dim1 = datapoints, Dim2 = datapoints, Dim3 = datapoints)
# pca <- prcomp(data_df)
# pca_scores <- as.data.frame(pca$x)
# plot_ly(pca_scores, x = ~PC1, y = ~PC2, z = ~PC3, type = "scatter3d", mode = "markers")
# -------
stim_high.df <- df_wide[df_wide$stim_ordered == "stimH",]
stim_low.df <- df_wide[df_wide$stim_ordered == "stimL",]
# selected_columns <- subset(stim_high.df, select = 2:(ncol(stim_high.df) - 1))
meanhighdf <- data.frame(subset(stim_high.df, select = 3:(ncol(stim_high.df) - 1)))
high.pca <- prcomp(meanhighdf)
high.pca_scores <- as.data.frame(high.pca$x)

meanlowdf <- data.frame(subset(stim_low.df, select = 3:(ncol(stim_low.df) - 1)))
low.pca <- prcomp(meanlowdf)
low.pca_scores <- as.data.frame(low.pca$x)
library(plotly)  # You can use plotly to create an interactive 3D plot
# plot_ly(high.pca_scores, x = ~PC1, y = ~PC2, z = ~PC3, type = "scatter3d", mode = "markers")
# plot_ly(low.pca_scores, x = ~PC1, y = ~PC2, z = ~PC3, type = "scatter3d", mode = "markers")
combined_pca_scores <- rbind(high.pca_scores, low.pca_scores)

# Add a new column to indicate the stim_ordered category (high_stim or low_stim)
combined_pca_scores$stim_ordered <- c(rep("high_stim", nrow(high.pca_scores)), rep("low_stim", nrow(low.pca_scores)))

# Create the 3D PCA plot
plot_ly(combined_pca_scores, x = ~PC1, y = ~PC2, z = ~PC3, type = "scatter3d", mode = "markers",
        color = ~stim_ordered)
# data_matrix <- groupwise[groupwise$stim_ordered == "high_stim",c("tr_ordered", "mean_per_sub_norm_mean")]
# sorted_indices <- order(data_matrix$tr_ordered)
# df_ordered <- data_matrix[sorted_indices, ]
# pca_result <- PCA(data_matrix$mean_per_sub_norm_mean)
# datapoints <- df$datapoints

# Assuming you have a dataframe named 'data' containing the 20 data points, 'x' and 'y' values, and corresponding standard deviations 'sd'

# Load the ggplot2 library
# install.packages("ggplot2")
library(ggplot2)

# Create the plot
# y = "mean_per_sub_mean"z
# combined_pca <- combined_pca_scores %>%
  # mutate(group_index = group_indices(., stim_ordered))

combined_pca <- combined_pca_scores %>%
  group_by(stim_ordered) %>%
  mutate(group_index = row_number())
ggplot(combined_pca, aes(x=group_index,y=PC1, group = stim_ordered, colour=stim_ordered)) +
  stat_smooth(method="loess", span=0.25, se=TRUE, aes(color=stim_ordered), alpha=0.3) +
  theme_bw()


```


```{r}
# Assuming you have a dataframe named 'data' containing the 20 data points, 'x' and 'y' values, and corresponding standard deviations 'sd'

# Load the ggplot2 library
# install.packages("ggplot2")
library(ggplot2)

# Create the plot
# y = "mean_per_sub_mean"z
ggplot(groupwise, aes(x=tr_ordered,y=mean_per_sub_mean, group = stim_ordered, colour=stim_ordered)) +
  stat_smooth(method="loess", span=0.25, se=TRUE, aes(color=stim_ordered), alpha=0.3) +
  theme_bw()

```
```{r}
# ggplot(data=groupwise, aes(x=tr_ordered, y=mean_per_sub_mean, ymin=se, ymax=se, fill=stim_ordered, linetype=stim_ordered)) + 
#  geom_line() + 
#  geom_ribbon(alpha=0.5)  
# Assuming you have a dataframe named 'data' containing the 20 mean data points and corresponding standard errors
# 'x' represents the x-values (e.g., time points)
# 'mean_y' represents the mean y-values
# 'se_y' represents the standard errors of the mean y-values

# Load the ggplot2 library
# install.packages("ggplot2")
library(ggplot2)
# groupwise$x <- as.numeric(groupwise$x)
# 
# # Sort the dataframe by the 'x' variable (if it's not already sorted)
# data <- data[order(data$x), ]

# Create the plot
# Create the plot with custom span and smoothing method
ggplot(groupwise, aes(x=tr_ordered,y=mean_per_sub_mean)) +
  geom_line() +                                   # Plot the smooth line for the mean
  geom_ribbon(aes(ymin = mean_per_sub_mean - se, ymax = mean_per_sub_mean + se), alpha = 0.3) + # Add the ribbon for standard error
  geom_smooth(method = "loess", span = 0.1, se = FALSE) +       # Add the loess smoothing curve
  labs(x = "X-axis Label", y = "Y-axis Label", title = "Smooth Line with Standard Error Ribbon") +
  theme_minimal()

```



## DEP: epoch: stim, high cue vs low cue

```{r}
# filtered_df <- subset(df, condition != "rating")
filtered_df <- df[!(df$condition == "rating" | df$condition == "cue"), ]

parsed_df <- filtered_df %>%
  separate(condition, into = c("cue", "stim"), sep = "_", remove = FALSE)

TR_length <- 42
# --------------------- subset regions based on ROI ----------------------------
df_long <- pivot_longer(parsed_df, cols = starts_with("tr"), names_to = "tr_num", values_to = "tr_value")

# ----------------------------- clean factor -----------------------------------
df_long$tr_ordered <- factor(
        df_long$tr_num,
        levels = c(paste0("tr", 1:TR_length))
    )
df_long$cue_ordered <- factor(
        df_long$cue,
        levels = c("cueH","cueL")
    )

# --------------------------- summary statistics -------------------------------
subjectwise <- meanSummary(df_long,
                                      c("sub", "tr_ordered", "cue_ordered"), "tr_value")
groupwise <- summarySEwithin(
  data = subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c("cue_ordered", "tr_ordered"),
  idvar = "sub"
)
groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

# --------------------------------- plot ---------------------------------------
LINEIV1 = "tr_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "se"
dv_keyword = "actual"
sorted_indices <- order(groupwise$tr_ordered)
groupwise_sorted <- groupwise[sorted_indices, ]
p1 = plot_timeseries_bar(groupwise, 
               LINEIV1, LINEIV2, MEAN, ERROR,  xlab = "Runs" , ylab= "Epoch: stimulus, High cue vs. Low cue", ggtitle="time_series", color=c("red", "blue"))
time_points <- seq(1, 0.46 * TR_length, 0.46)
p1 + scale_x_discrete(labels = setNames(time_points, colnames(df_long)[7:7+TR_length]))+ theme_classic()

```

## taskwise cue effect
```{r}
run_types <- c("pain", "vicarious", "cognitive")
  plot_list <- list()
  TR_length <- 42
for (run_type in run_types) {
  filtered_df <- df[!(df$condition == "rating" | df$condition == "cue" | df$runtype != run_type), ]

  parsed_df <- filtered_df %>%
    separate(condition, into = c("cue", "stim"), sep = "_", remove = FALSE)
  # --------------------- subset regions based on ROI ----------------------------
  df_long <- pivot_longer(parsed_df, cols = starts_with("tr"), names_to = "tr_num", values_to = "tr_value")

  # ----------------------------- clean factor -----------------------------------
  df_long$tr_ordered <- factor(
          df_long$tr_num,
          levels = c(paste0("tr", 1:TR_length))
      )
df_long$cue_ordered <- factor(
        df_long$cue,
        levels = c("cueH","cueL")
    )

  # --------------------------- summary statistics -------------------------------
  subjectwise <- meanSummary(df_long,
                                        c("sub","tr_ordered", "cue_ordered"), "tr_value")
  groupwise <- summarySEwithin(
    data = subjectwise,
    measurevar = "mean_per_sub",
    withinvars = c( "cue_ordered", "tr_ordered"),
    idvar = "sub"
  )
  groupwise$task <- run_type
  # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

  # ... Rest of your data processing code ...
  
  # subset <- groupwise[groupwise$runtype == run_type, ]
  LINEIV1 = "tr_ordered"
  LINEIV2 = "cue_ordered"
  MEAN = "mean_per_sub_norm_mean"
  ERROR = "se"
  dv_keyword = "actual"
  sorted_indices <- order(groupwise$tr_ordered)
  groupwise_sorted <- groupwise[sorted_indices, ]
  p1 <- plot_timeseries_bar(groupwise_sorted, 
                            LINEIV1, LINEIV2, MEAN, ERROR,  
                            xlab = "TRs", 
                            ylab = paste0(ROI, " activation (A.U.)"), 
                            ggtitle = paste0(run_type, " time series, Epoch - stimulus"), 
                            color =c("red", "blue"))
  time_points <- seq(1, 0.46 * TR_length, 0.46)
  #p1 <- p1 + scale_x_discrete(labels = setNames(time_points, colnames(df_long)[7:(7 + TR_length)])) + theme_classic()
  
  plot_list[[run_type]] <- p1 + theme_classic()
}
  
  # --------------------------- plot three tasks -------------------------------
library(gridExtra)
plot_list <- lapply(plot_list, function(plot) {
  plot + theme(plot.margin = margin(5, 5, 5, 5))  # Adjust plot margins if needed
})
combined_plot <- ggpubr::ggarrange(plot_list[["pain"]],plot_list[["vicarious"]],plot_list[["cognitive"]],
                  common.legend = TRUE,legend = "bottom", ncol = 3, nrow = 1, 
                  widths = c(3, 3, 3), heights = c(.5,.5,.5), align = "v")
combined_plot
ggsave(file.path(save_dir, "taskwise_epoch-stim_desc-highcueGTlowcue.png"), combined_plot, width = 12, height = 4)
```

## epoch: stim, rating
```{r eval=FALSE, include=FALSE}
# ------------------------------------------------------------------------------
#                       epoch stim, high cue vs low cue
# ------------------------------------------------------------------------------
# --------------------- subset regions based on ROI ----------------------------


parsed_df <- df[(df$condition == "rating"), ]
TR_length <- 42
df_rating <- pivot_longer(parsed_df, cols = starts_with("tr"), names_to = "tr_num", values_to = "tr_value")

# ----------------------------- clean factor -----------------------------------
df_rating$tr_ordered <- factor(
        df_rating$tr_num,
        levels = c(paste0("tr", 1:TR_length))
    )

# --------------------------- summary statistics -------------------------------
subjectwise <- meanSummary(df_rating,
                                      c("sub", "tr_ordered"), "tr_value")
groupwise <- summarySEwithin(
  data = subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c( "tr_ordered"),
  idvar = "sub"
)
groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402



# Assuming your data frame is named "time_series_data"

# Create the ggplot
gg <- ggplot(groupwise, aes(x = tr_ordered, y = mean_per_sub_norm_mean, group = 1)) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(ymin = mean_per_sub_norm_mean - se, ymax = mean_per_sub_norm_mean + se), width = 0.2) +
  labs(x = "Time", y = "Amplitude", title = "Time Series Data with Error Bars")
gg <- gg + theme_classic() +       theme(legend.key = element_rect(fill = "white", colour = "white")) +
      theme_bw() 
# Print the ggplot
print(gg)

# --------------------------------- plot ---------------------------------------
LINEIV1 = "tr_ordered"
# LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "se"
dv_keyword = "actual"
sorted_indices <- order(groupwise$tr_ordered)
groupwise_sorted <- groupwise[sorted_indices, ]
p2 = plot_timeseries_onefactor(groupwise_sorted, 
               LINEIV1,MEAN, ERROR,  xlab = "Runs" , ylab= "Epoch: stimulus, High cue vs. Low cue", ggtitle="time_series", color="red")
time_points <- seq(1, 0.46 * TR_length, 0.46)
p2 + scale_x_discrete(labels = setNames(time_points, colnames(df_long)[7:7+TR_length]))+ theme_classic()
p2 + theme_classic()
```



## epoch: 6 cond
```{r}
# ------------------------------------------------------------------------------
#                       epoch stim, high cue vs low cue
# ------------------------------------------------------------------------------
# --------------------- subset regions based on ROI ----------------------------

# ----------------------------- clean factor -----------------------------------
df_long$tr_ordered <- factor(
        df_long$tr_num,
        levels = c(paste0("tr", 1:TR_length))
    )
df_long$cue_ordered <- factor(
        df_long$cue,
        levels = c("cueH", "cueL")
    )
df_long$stim_ordered <- factor(
        df_long$stim,
        levels = c("stimH", "stimM", "stimL")
    )

df_long$sixcond <- factor(
        df_long$condition,
        levels = c("cueH_stimH", "cueL_stimH", 
                   "cueH_stimM", "cueL_stimM",
                   "cueH_stimL", "cueL_stimL")
) 
# --------------------------- summary statistics -------------------------------
subjectwise <- meanSummary(df_long,
                                      c("sub", "tr_ordered", "sixcond"), "tr_value")
groupwise <- summarySEwithin(
  data = subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c("sixcond", "tr_ordered"),
  idvar = "sub"
)
groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

# --------------------------------- plot ---------------------------------------
LINEIV1 = "tr_ordered"
LINEIV2 = "sixcond"
MEAN = "mean_per_sub_norm_mean"
ERROR = "se"
dv_keyword = "actual"
sorted_indices <- order(groupwise$tr_ordered)
groupwise_sorted <- groupwise[sorted_indices, ]
p3H = plot_timeseries_bar(groupwise, 
               LINEIV1, LINEIV2, MEAN, ERROR,  xlab = "Runs" , ylab= "Epoch: stimulus, High cue vs. Low cue", ggtitle=paste0("High intensity - Low cue vs. High cue (N = ", unique(groupwise$N), ")" ), color=c("red","#5f0f40","gray", "gray", "gray", "gray"))
time_points <- seq(1, 0.46 * TR_length, 0.46)
p3H + scale_x_discrete(labels = setNames(time_points, colnames(df_long)[7:7+TR_length]))+ theme_classic()
p3H + theme_classic()
```

```{r}
p3M = plot_timeseries_bar(groupwise, 
               LINEIV1, LINEIV2, MEAN, ERROR,  xlab = "Runs" , ylab= "Epoch: stimulus, High cue vs. Low cue", ggtitle=paste0("Medium intensity - Low cue vs. High cue (N = ", unique(groupwise$N), ")"), color=c("#d6d6d6","#d6d6d6","#bc3908", "#f6aa1c", "gray", "gray"))
time_points <- seq(1, 0.46 * TR_length, 0.46)
p3M + scale_x_discrete(labels = setNames(time_points, colnames(df_long)[7:7+TR_length]))+ theme_classic()
p3M + theme_classic()
```

```{r}
p3L = plot_timeseries_bar(groupwise, 
               LINEIV1, LINEIV2, MEAN, ERROR,  xlab = "Runs" , ylab= "Epoch: stimulus, High cue vs. Low cue", ggtitle=paste0("Low intensity - Low cue vs. High cue (N = ", unique(groupwise$N), ")"), color=c("gray","gray","gray", "gray", "#2541b2", "#00a6fb"))
time_points <- seq(1, 0.46 * TR_length, 0.46)
p3L + scale_x_discrete(labels = setNames(time_points, colnames(df_long)[7:7+TR_length]))+ theme_classic()
p3L + theme_classic()
```



## taskwise 6 cond effect

```{r}
# ------------------------------------------------------------------------------
#                       epoch stim, high cue vs low cue
# ------------------------------------------------------------------------------
# --------------------- subset regions based on ROI ----------------------------
run_types <- c("pain", "vicarious", "cognitive")
  
  TR_length <- 42
for (run_type in run_types) {
  filtered_df <- df[!(df$condition == "rating" | df$condition == "cue" | df$runtype != run_type), ]
plot_list <- list()

  parsed_df <- filtered_df %>%
    separate(condition, into = c("cue", "stim"), sep = "_", remove = FALSE)
  # --------------------- subset regions based on ROI ----------------------------
  df_long <- pivot_longer(parsed_df, cols = starts_with("tr"), names_to = "tr_num", values_to = "tr_value")

# ----------------------------- clean factor -----------------------------------
df_long$tr_ordered <- factor(
        df_long$tr_num,
        levels = c(paste0("tr", 1:TR_length))
    )
df_long$cue_ordered <- factor(
        df_long$cue,
        levels = c("cueH", "cueL")
    )
df_long$stim_ordered <- factor(
        df_long$stim,
        levels = c("stimH", "stimM", "stimL")
    )

df_long$sixcond <- factor(
        df_long$condition,
        levels = c("cueH_stimH", "cueL_stimH", 
                   "cueH_stimM", "cueL_stimM",
                   "cueH_stimL", "cueL_stimL")
) 
# --------------------------- summary statistics -------------------------------
subjectwise <- meanSummary(df_long,
                                      c("sub", "tr_ordered", "sixcond"), "tr_value")
groupwise <- summarySEwithin(
  data = subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c("sixcond", "tr_ordered"),
  idvar = "sub"
)
groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

# --------------------------------- plot ---------------------------------------
LINEIV1 = "tr_ordered"
LINEIV2 = "sixcond"
MEAN = "mean_per_sub_norm_mean"
ERROR = "se"
dv_keyword = "actual"
sorted_indices <- order(groupwise$tr_ordered)
groupwise_sorted <- groupwise[sorted_indices, ]
p3H = plot_timeseries_bar(groupwise, 
               LINEIV1, LINEIV2, MEAN, ERROR,  xlab = "Runs" , ylab= "Epoch: stimulus, High cue vs. Low cue", ggtitle=paste0("High intensity - Low cue vs. High cue (N = ", unique(groupwise$N), ")" ), color=c("red","#5f0f40","gray", "gray", "gray", "gray"))
time_points <- seq(1, 0.46 * TR_length, 0.46)
# p3H + scale_x_discrete(labels = setNames(time_points, colnames(df_long)[7:7+TR_length]))+ theme_classic()
p3H + theme_classic()
plot_list[["H"]] <- p3H + theme_classic()

p3M = plot_timeseries_bar(groupwise, 
               LINEIV1, LINEIV2, MEAN, ERROR,  xlab = "Runs" , ylab= "Epoch: stimulus, High cue vs. Low cue", ggtitle=paste0("Medium intensity - Low cue vs. High cue (N = ", unique(groupwise$N), ")"), color=c("#d6d6d6","#d6d6d6","#bc3908", "#f6aa1c", "gray", "gray"))
time_points <- seq(1, 0.46 * TR_length, 0.46)
# p3M + scale_x_discrete(labels = setNames(time_points, colnames(df_long)[7:7+TR_length]))+ theme_classic()
plot_list[["M"]] <- p3M + theme_classic()

p3L = plot_timeseries_bar(groupwise, 
               LINEIV1, LINEIV2, MEAN, ERROR,  xlab = "Runs" , ylab= "Epoch: stimulus, High cue vs. Low cue", ggtitle=paste0("Low intensity - Low cue vs. High cue (N = ", unique(groupwise$N), ")"), color=c("gray","gray","gray", "gray", "#2541b2", "#00a6fb"))
time_points <- seq(1, 0.46 * TR_length, 0.46)
# p3L + scale_x_discrete(labels = setNames(time_points, colnames(df_long)[7:7+TR_length]))+ theme_classic()
plot_list[["L"]] <- p3L + theme_classic()


  # --------------------------- plot three tasks -------------------------------
library(gridExtra)
plot_list <- lapply(plot_list, function(plot) {
  plot + theme(plot.margin = margin(5, 5, 5, 5))  # Adjust plot margins if needed
})
combined_plot <- ggpubr::ggarrange(plot_list[["H"]],plot_list[["M"]],plot_list[["L"]],
                  common.legend = FALSE,legend = "bottom", ncol = 3, nrow = 1, 
                  widths = c(3, 3, 3), heights = c(.5,.5,.5), align = "v")
combined_plot
ggsave(file.path(save_dir, paste0("taskwise-",run_type, "_epoch-stim_desc-stimcuecomparison.png")), combined_plot, width = 12, height = 4)
}
```





