

# load NPS


```{r include=FALSE}
library(car)
library(psych)
library(reshape)
# library(PupillometryR)
library(dplyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(plyr)
library(ggpubr)
library(r2mlm)
library(effectsize)
library(devtools)
# options(es.use_symbols = TRUE) # get nice symbols when printing! (On Windows, requires R >= 4.2.0)
library(EMAtools)
library(emmeans)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(DT)
library(raincloudplots)
devtools::source_url("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(r2mlm)
main_dir <- dirname(dirname(getwd()))
print(main_dir)
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```


# load beahvarioa
# load bad json
# drop based on NPS and bad json
```{r}
main_dir = "/Users/h/Documents/projects_local/cue_expectancy"
```

## datawrangle :: load NPS
```{r}
# load NPS dot product
NPSdf <- read.csv(file.path(main_dir, 'analysis/fmri/nilearn/deriv01_signature/rampupdown/signature-NPSpos_sub-all_runtype-pvc_event-stimulus.tsv' ))


NPSsplit <- NPSdf %>%
  # 1) Extract the components from the singletrial_fname column (sub,ses, run etc)
  extract(col = singletrial_fname, into = c("sub", "ses", "run", "runtype", "event", "trial", "cuetype", "stimintensity"),
          regex = "(sub-\\w+)_+(ses-\\w+)_+(run-\\w+)_+(runtype-\\w+)_+(event-\\w+)_+(trial-\\w+)_+(cuetype-\\w+)_+(stimintensity-\\w+).nii.gz") %>%
  # 2) Extract numbers and keywords as specified
  mutate(
    sub = as.integer(str_extract(sub, "\\d+")),
    ses = as.integer(str_extract(ses, "\\d+")),
    run = as.integer(str_extract(run, "\\d+")),
    trail = as.integer(str_extract(trial, "\\d+")) + 1,
    cue = case_when(
      str_detect(cuetype, "low") ~ "low_cue",
      str_detect(cuetype, "high") ~ "high_cue"
    ), 
    task = str_replace(runtype, "runtype-", ""), 
    stim = case_when(
      stimintensity == "stimintensity-low" ~ "low_stim",
      stimintensity == "stimintensity-med" ~ "med_stim",
      stimintensity == "stimintensity-high" ~ "high_stim",
      TRUE ~ stimintensity  # Retain original value if neither "low" nor "high"
    )
  ) %>%
  # 3) Select and rename the necessary columns
  select(
    sub,
    ses,
    run,
    task,
    event,
    trial,
    cue,
    stim,
    NPSpos
  )
# Let's assume 'df' is your data frame and 'trial' is the column with trial identifiers
NPSsplit$trial_char <- NPSsplit$trial
NPSsplit$trial <- as.numeric(sub("trial-", "", NPSsplit$trial_char)) + 1

```


### datawrangle :: remove bad runs
```{r}
library(jsonlite)
jsonfname <- "/Users/h/Documents/projects_local/cue_expectancy/scripts/bad_runs.json"


bad_runs <- fromJSON(jsonfname, simplifyDataFrame = FALSE)

# Initialize an empty data frame to store bad run entries
bad_runs_df <- data.frame(sub = integer(), ses = integer(), run = integer(), stringsAsFactors = FALSE)

# Parse the JSON content
for (sub_id in names(bad_runs)) {
  sub_num <- as.integer(substring(sub_id, 5))  # Extract the numeric part of the subject ID
  
  # Iterate over sessions and their runs for each subject
  for (ses_run_str in bad_runs[[sub_id]]) {
    ses_num <- as.integer(substring(strsplit(ses_run_str, "_")[[1]][1], 5))  # Extract session number
    run_num <- as.integer(substring(strsplit(ses_run_str, "_")[[1]][2], 5))  # Extract run number
    
    # Append to the bad_runs_df data frame
    bad_runs_df <- rbind(bad_runs_df, data.frame(sub = sub_num, ses = ses_num, run = run_num))
  }
}

# drop rows in merge_df if they overlap with bad_runs_df 
clean_merge_df <- NPSsplit %>%
  anti_join(bad_runs_df, by = c("sub", "ses", "run"))
# clean_merge_df <- merge_df %>%
#   anti_join(NPSsplit, by = c("sub", "ses", "run"))

```
# datawrangle :: load beahvarioal
```{r}

datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
taskname = '*'
subject_varkey <- "src_subject_id"
iv <- "param_stimulus_type"; 
iv_keyword <- "stim"; 
dv <- "event04_actual_angle"; dv_keyword <- "outcome"
exclude <- "sub-0001"
#sub-0074|sub-0085|sub-0118|sub-0117|sub-0103|sub-0063|sub-0002|sub-0003|sub-0004|sub-0005|sub-0007|sub-0008|sub-0013|sub-0016|sub-0017|sub-0019|sub-0020|sub-0021|sub-0025|sub-0075|sub-0009|sub-0117|sub-0119|sub-0081|sub-0060

p.df <- load_task_social_df(datadir, taskname = "pain", subject_varkey, iv, dv, exclude)
p.df <- p.df %>%
group_by(src_subject_id, session_id, param_run_num) %>%
mutate(trial_index_runwise = row_number()) %>%
ungroup() 
names(p.df)[names(p.df) == "src_subject_id"] <- "sub"
names(p.df)[names(p.df) == "session_id"] <- "ses"
names(p.df)[names(p.df) == "param_run_num"] <- "run"
names(p.df)[names(p.df) == "param_task_name"] <- "task"
names(p.df)[names(p.df) == "param_cue_type"] <- "cue"
names(p.df)[names(p.df) == "param_stimulus_type"] <- "stim"
names(p.df)[names(p.df) == "trial_index_runwise"] <- "trial"
names(p.df)[names(p.df) == "event02_expect_angle"] <- "RATING_expectation"
names(p.df)[names(p.df) == "event04_actual_angle"] <- "RATING_outcome"
```


# datawrangle :: merge NPS and behavioral
```{r}
library(dplyr)
# Assuming your dataframe is called df

merge_df <- inner_join(NPSsplit, p.df, by = c("sub", "ses", "run","cue",
"task", "stim","trial"))
```

## load fear of pain
```{r}
fop <- read.csv('/Users/h/Downloads/IndividualizedSpatia_DATA_2023-11-11_1303.csv')

# select rows that start with sub-@
fop.sub <- fop[grepl("^sub-", fop$record_id), ]

# convert rows to indices
fop.sub$sub <- as.integer(sub("sub-", "", fop.sub$record_id))
# drop row: sub-0062
fop.sub <- fop.sub[fop.sub$sub != "sub-0062 (2) (pre-ses)", ]


# calculate fop total score
columns_to_sum <- paste0("fop", 1:30)
fop.sub$composite_score <- rowSums(fop.sub[, columns_to_sum], na.rm = TRUE)

fop.comp <- fop.sub[, c("sub", "composite_score")]

# merge sub and fop total score
nps.beh.fop <- inner_join(merge_df, fop.comp, by = c("sub"))
```
# merge and save
```{r}

clean_df <- nps.beh.fop[, c("sub", "ses", "run", "NPSpos", "cue",
"stim", "RATING_expectation", "RATING_outcome", "composite_score")]

clean_df_na <- clean_df[!is.na(clean_df$RATING_expectation),]
clean_df <- clean_df_na[!is.na(clean_df_na$RATING_expectation),]
clean_df$stimintensity <- clean_df$stim
clean_df$stim[clean_df$stimintensity == "low_stim"] <- -0.5
clean_df$stim[clean_df$stimintensity == "med_stim"] <- 0
clean_df$stim[clean_df$stimintensity == "high_stim"] <- 0.5

write.csv(clean_df , '/Users/h/Desktop/cleanmerge_NPS.csv')
```

## datawrangle :: check number of trials
```{r}
frequency_per_sub <- table(clean_df$sub)
frequency_per_sub_df <- as.data.frame(frequency_per_sub)
# Step 1: Identify subjects with less than 10 occurrences
subjects_to_remove <- frequency_per_sub_df %>%
  filter(Freq < 10) %>%
  select(Var1)
subjects_to_remove$Var1 <- as.integer(as.character(subjects_to_remove$Var1))

# Step 2: Remove these subjects from the main data frame
filtered_main_df <- clean_df %>%
  anti_join(subjects_to_remove, by = c("sub" = "Var1"))
write.csv(filtered_main_df , '/Users/h/Desktop/cleanmerge_NPS.csv')
```

## datawrangle :: between vs within
```{r}
p.demean <- filtered_main_df %>%
group_by(sub) %>%
mutate(RATING_outcome = as.numeric(RATING_outcome)) %>%
mutate(RATING_expectation = as.numeric(RATING_expectation)) %>%
mutate(avg_outcome = mean(RATING_outcome, na.rm = TRUE)) %>%
mutate(OUTCOME_demean = RATING_outcome - avg_outcome) %>%
mutate(avg_expect = mean(RATING_expectation, na.rm = TRUE)) %>%
mutate(EXPECT_demean = RATING_expectation - avg_expect)

p.demean <- p.demean %>%
group_by(sub) %>%
mutate(NPSpos = as.numeric(NPSpos)) %>%
mutate(avg_NPS = mean(NPSpos, na.rm = TRUE)) %>%
mutate(NPS_demean = NPSpos - avg_NPS) %>%
  ungroup %>%
mutate(OUTCOME_cmc = avg_outcome - mean(avg_outcome)) %>%
mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) %>%
mutate(NPS_cmc = avg_NPS - mean(avg_NPS)) 
write.csv(p.demean , '/Users/h/Desktop/pain_withinbetween.csv')
```


# ggplot NPS and Outcome
```{r}
library(ggplot2)

min_value <- -40
max_value <- 40
p.demean$sub <- factor(p.demean$sub)
plot.PE_NPS <- ggplot(p.demean, aes(x = NPSpos, y = RATING_outcome)) + 
  geom_point(aes(colour = sub), size = .1) +  # Points colored by subject
  geom_smooth(aes(colour = sub), method = 'lm', formula = y ~ x, se = FALSE, size = .3, linetype = "dashed") +  # Subject-wise regression lines
  geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = .5, color = "black") +  # Group regression line
  ylim(0, 180) +  # Set y-axis limits
  theme_classic2()  # Use a theme with a white background
plot.PE_NPS
```

```{r}
library(ggplot2)

min_value <- -40
max_value <- 40
p.demean$sub <- factor(p.demean$sub)
plot.PE_NPS <- ggplot(p.demean, aes(x = NPS_demean, y = RATING_outcome)) + 
  geom_point(aes(colour = sub), size = .1) +  # Points colored by subject
  geom_smooth(aes(colour = sub), method = 'lm', formula = y ~ x, se = FALSE, size = .3, linetype = "dashed") +  # Subject-wise regression lines
  geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = .5, color = "black") +  # Group regression line
  ylim(0, 180) +  # Set y-axis limits
  theme_classic2()  # Use a theme with a white background
plot.PE_NPS
```
```{r}
library(ggplot2)

min_value <- -40
max_value <- 40
p.demean$sub <- factor(p.demean$sub)
plot.PE_NPS <- ggplot(p.demean, aes(x = RATING_expectation, y = NPSpos)) + 
  geom_point(aes(colour = sub), size = .1) +  # Points colored by subject
  geom_smooth(aes(colour = sub), method = 'lm', formula = y ~ x, se = FALSE, size = .3, linetype = "dashed") +  # Subject-wise regression lines
  geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = .5, color = "black") +  # Group regression line
  ylim(-40, 40) +  # Set y-axis limits
  theme_classic2()  # Use a theme with a white background
plot.PE_NPS
```

```{r}
ggplot(p.demean, aes(x=NPS_cmc, y=OUTCOME_cmc)) + 
  geom_point() + 
  theme_minimal() + 
  labs(x = "NPS cmc", y = "Outcome cmc", title = "Scatter plot of NPS cmc vs. Outcome cmc")

```

## 6. OUTCOME ~ NPS
### Q. Do higher NPS values indicate higher outcome ratings? (Pain task only) {.unlisted .unnumbered}

> Yes, Higher NPS values are associated with higher outcome ratings. The linear relationship between NPS value and outcome ratings are stronger for conditions where cue level is congruent with stimulus intensity levels. In other words, NPS-outcome rating relationship is stringent in the low cue-low intensity group, as is the case for high cue-ghigh intensity group. 

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
p.sig<- clean_df
# plot parameters
iv2 = "RATING_outcome"
iv1 = "NPSpos"
subject = "sub"
ylab = "Outcome rating"
xlab = "NPSpos" #signature_key
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"

df_dropna <- p.sig[!is.na(p.sig[, iv1]) & !is.na(p.sig[, iv2]),]
subjectwise_2dv <- meanSummary_2dv(df_dropna,
                                   c(subject),
                                   iv1, iv2)
subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
g <- ggplot(data = subjectwise_naomit_2dv,
            aes(x = .data[["DV1_mean_per_sub"]],
                y = .data[["DV2_mean_per_sub"]],)) +
  geom_point(size = 2,
             alpha = alpha) +

  theme(aspect.ratio = 1) +
  #scale_color_manual(values = color_scheme) +
  scale_shape_manual(values = c(16, 17)) +
  xlab(xlab) +
  ylab(ylab) +
  xlim(-10, 30) +
  ylim(0, 180) +
  ggtitle(ggtitle) +
  theme(
    axis.line = element_line(colour = "grey50"),
    panel.background = element_blank(),
    plot.subtitle = ggtext::element_textbox_simple(size = 11)
  ) +
  geom_ribbon(
    stat = "smooth",
    method = lm_method,
    se = TRUE,
    alpha = 0.1,
    aes(color = NULL)
  ) +
  geom_line(
    stat = "smooth",
    method = lm_method,
    alpha = 0.8,
    linewidth = 1.5
  )
g
```
> NPS_demean is the within subject data, removing each subject's mean NPS response. Centering around the person’s mean (also known as centering within clusters = CWC)NPS_cmc is the subject's mean NPS response.
> 

```{r}
NPS.between_within <- lmer(RATING_outcome~ NPS_demean + NPS_cmc + (1|sub), data = p.demean)
summary(NPS.between_within)
```

```{r}
p.demean$NPS_within <- p.demean$NPS_demean
p.demean$NPS_between <- p.demean$NPS_cmc
p.demean$EXPECT_within <- p.demean$EXPECT_demean
p.demean$EXPECT_between <- p.demean$EXPECT_cmc

model.nps <- lmer(NPSpos ~ EXPECT_demean + EXPECT_cmc + (1|sub), data = p.demean)
summary(model.nps)

model.npsmd <- lmer(RATING_outcome ~ NPS_demean + NPS_cmc + EXPECT_demean + EXPECT_cmc + (1|sub), data = p.demean)
summary(model.npsmd)
vif(model.npsmd)
```

```{r}
# NPSpos 
iv1 = "NPSpos"
nbins = 10
p.demean %>%
  dplyr::group_by(.data[["sub"]]) %>%
  select(everything())  %>%
  mutate(NPS_demean = .data[[iv1]] - mean(.data[[iv1]])) %>%
  mutate(
    bin = ggplot2::cut_interval(.data[["NPS_demean"]], n = nbins),
    NPSlevels = as.numeric(cut_interval(.data[["NPS_demean"]], n = nbins))
  )

NPS <- lmer(RATING_outcome~ NPSpos + (NPSlevels|sub), data = p.demean)
summary(NPS)
```
## what is the relationshipe between expect-> NPS and NPS -> pain
Participants with the most positive expectancy effects on NPS also have the most positive NPS-pain relationships (to verify...).
```{r}

model.1 <- lmer(NPSpos ~ RATING_expectation + (RATING_expectation|sub), data = p.demean)
summary(model.1)

model.2 <- lmer(RATING_outcome ~ NPSpos + (NPSpos|sub), data = p.demean)
summary(model.2)

fixEffect1 <- as.data.frame(fixef(model.1))
randEffect1 <- as.data.frame(ranef(model.1))
fixEffect2 <- as.data.frame(fixef(model.2))
randEffect2 <- as.data.frame(ranef(model.2))
modelX <- lm(randEffect1 ~randEffect2)
summary(modelX)
```

