# [physio] scl ~ cue*stim {#scl}
```
title: "model09_iv-cue-stim_dv-scl"
author: "Heejung Jung"
date: '2022-09-17'
```

## overview
TODO:
split data into task (full -> P, v, c subset)
push code to git
create code map
log transform
* SCL: mean signal
* SCR: log transform

## Overview

The purpose of this notebook is to analyze biopac phasic data. 
Data has been preprocessed with neurokit

We load a dataframe that contains the following outcome measures:
'Event_Onset', 'EDA_Peak_Amplitude', 'EDA_SCR', 'SCR_Peak_Amplitude',
'SCR_Peak_Amplitude_Time', 'SCR_RiseTime', 'SCR_RecoveryTime'

We model this as a function of "cue" and "stimulus intensity",
while allowing for random effects from participants. 



```{r load_libraries_51, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(ggpubr)
library(gridExtra)
library(tidyverse)
library(GGally)
library(reshape)
library(boot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(stringr)
library(stats)
library(equatiomatic)
library(sjmisc)
library(sjPlot)
library(sjlabelled)
library(effectsize)
library(gghalves)
library(brms)

library(r2mlm)
main_dir <- dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```



```{r load_data_and_exclude_51}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, "analysis", "physio", "physio01_SCL")
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model91_physio_iv-cue-stim_dv-scl", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```
```{r}
ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"
subject_varkey <- "src_subject_id"
```

```{r}
# parameters _____________________________________ # nolint
# phasic = read.csv("/Volumes/spacetop_projects_social/data/physio/physio02_preproc/group_epochstart-0_epochend-9_physio-phasic.csv")
# tonic = read.csv("/Volumes/spacetop_projects_social/data/physio/physio02_preproc/group_epochstart--1_epochend-8_physio-scl.csv")
  # INPUT:
  # * taskname (e.g. pain, cognitive, vicarious)
  # * subject_varkey (e.g. src_subject_id or subject)
  # A. load data ______________________________________________________________
taskname = "*"
filename <- paste0("*_runtype-", taskname,"_epochstart--1_epochend-20_physio-scl.csv")
  common_path <- Sys.glob(file.path(datadir, "sub-*", "ses-*", filename
  ))
  filter_path <- common_path[!str_detect(common_path, pattern = exclude)]

# scl <- do.call("rbind", lapply(filter_path, FUN = function(files) {
#     read.csv(files)
#     }))

  
scl <- do.call("rbind.fill", lapply(filter_path, FUN = function(files) {
    read.csv(files)
    }))

  is.nan.data.frame <- function(x) {
    do.call(cbind, lapply(x, is.nan))
  }
  scl[is.nan(scl)] <- NA
  scl[, "subject"] <- factor(scl[, subject_varkey])

  # B. plot expect rating NA ___________________________________________________




```

This is the data that we will use

```{r echo=FALSE}
scl <- read.csv("/Users/h/Documents/projects_local/cue_expectancy/data/physio/sub-all_ses-all_run-all_runtype-cognitive_epochstart--3_epochend-20_samplingrate-25_ttlindex-1_physio-scltimecourse.csv")
head(scl)
```


```{r contrast_coding_51}
#contrast code 1 linear
scl$stim_con_linear[scl$param_stimulus_type == "low_stim"] <- -0.5
scl$stim_con_linear[scl$param_stimulus_type == "med_stim"] <- 0
scl$stim_con_linear[scl$param_stimulus_type == "high_stim"] <- 0.5

# contrast code 2 quadratic
scl$stim_con_quad[scl$param_stimulus_type == "low_stim"] <- -0.33
scl$stim_con_quad[scl$param_stimulus_type == "med_stim"] <- 0.66
scl$stim_con_quad[scl$param_stimulus_type == "high_stim"] <- -0.33

# social cue contrast
scl$social_cue[scl$param_cue_type == 'low_cue'] <- -0.5 # social influence task
scl$social_cue[scl$param_cue_type == 'high_cue'] <- 0.5 # no influence task
scl$cue_factor = factor(scl$social_cue)
```

```{r}
# parameters ___________________________________________________________________
scl$subject = factor(scl$src_subject_id)
#subject_varkey <- "subject"
iv <- "cue_factor"
stim_con1 = "stim_con_linear"
stim_con2 = "stim_con_quad"
dv <- "mean_signal" # DON"T USE EDA_Peak_Amplitude (misleading)
iv_keyword <- "cue-stim"
dv_keyword <- "scl_peak"
xlab <- ""
taskname <- "full"
#ylim = c(-1,1)
#tonic_task = 
```

### full model with all tasks
```{r lmer_fullmodel_51, class.source = 'fold-show'}
fullmodel = lmer(mean_signal ~ 1+ cue_factor*stim_con_linear +cue_factor*stim_con_quad + (1 |src_subject_id), data = scl)
summary(fullmodel)
print(summary(fullmodel))
```



```{r plot_results_pain_51}

cooksd <- cooks.distance(fullmodel)
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(scl$subject)))))])
data_screen <- scl[-influential, ]

# reordering for plots _________________________________________________________
scl$cue_name[scl$param_cue_type == "high_cue"] <- "high cue"
scl$cue_name[scl$param_cue_type == "low_cue"] <- "low cue" # no influence task

scl$stim_name[scl$param_stimulus_type == "high_stim"] <- "high" # no influence task
scl$stim_name[scl$param_stimulus_type == "med_stim"] <- "med" # no influence task
scl$stim_name[scl$param_stimulus_type == "low_stim"] <- "low" # no influence task

scl$stim_ordered <- factor(scl$stim_name, levels=c("low", "med", "high"))
scl$cue_ordered <- factor(scl$cue_name, levels=c("low cue", "high cue"))
model_iv1 = "stim_ordered";model_iv2 = "cue_ordered"

# summary statistics for plots _________________________________________________
subjectwise <- meanSummary(scl, c("subject", model_iv1, model_iv2), dv)
try <- na.omit(subjectwise)
groupwise <- summarySEwithin(
        data = try,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(model_iv1, model_iv2), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    
group_mean <- "mean_per_sub_norm_mean"
se <- "se";   
ggtitle <- paste(taskname, dv_keyword);    
title <- paste(taskname, " - RT")
xlab <- "";    
ylab <- "SCL peak amplitude ";    
w = 5; h = 3; 
ylim = c(-3,3)
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
              "_iv-", iv_keyword,"_dv-", dv_keyword,
              "_", as.character(Sys.Date()), ".png",
              sep = ""
        )
    )
plot_rainclouds_twofactor(
        try, groupwise,
        model_iv1, model_iv2, subjectwise_mean, group_mean, se, "subject",
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

```


### PAIN
```{r lmer_fullmodel_pain_51, class.source = 'fold-show'}
pain = lmer(mean_signal ~ 1+ cue_factor + stim_con_linear + stim_con_quad + cue_factor:stim_con_linear + cue_factor:stim_con_quad + (1  |src_subject_id), data = scl[scl$param_task_name == 'pain',])
summary(pain)
```

### VICARIOUS
```{r lmer_fullmodel_vicarious_51, class.source = 'fold-show'}
vicarious = lmer(mean_signal ~ 1+ cue_factor + stim_con_linear + stim_con_quad + cue_factor:stim_con_linear + cue_factor:stim_con_quad + (1  |src_subject_id), data = scl[scl$param_task_name == 'vicarious',])
summary(vicarious)
```

### COGNITIVE
```{r lmer_fullmodel_cognitive_51, class.source = 'fold-show'}
cognitive = lmer(mean_signal ~ 1+ cue_factor + stim_con_linear + stim_con_quad + cue_factor:stim_con_linear + cue_factor:stim_con_quad + (1  |src_subject_id), data = scl[scl$param_task_name == 'cognitive',])
summary(cognitive)
```

### TASKWISE PLOTS
```{r}
combined_se_calc_cooksd = data.frame()
for (taskname in c( "pain", "vicarious", "cognitive")) { #"pain",
    ggtitle <- paste(taskname, " - SCL signal")
    title <- paste(taskname, " - EDA")
    subject <- "subject"
    print(taskname)
    data = scl[scl$param_task_name == taskname,]
    w <- 10
    h <- 6

    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
    # contrast code ________________________________________
    data$stim[data$param_stimulus_type == "low_stim"] <- -0.5 # social influence task
    data$stim[data$param_stimulus_type == "med_stim"] <- 0 # no influence task
    data$stim[data$param_stimulus_type == "high_stim"] <- 0.5 # no influence task

    data$stim_factor <- factor(data$param_stimulus_type)
    data$cue_factor <- factor(data$param_cue_type)
    # contrast code 1 linear
    data$stim_con_linear[data$param_stimulus_type == "low_stim"] <- -0.5
    data$stim_con_linear[data$param_stimulus_type == "med_stim"] <- 0
    data$stim_con_linear[data$param_stimulus_type == "high_stim"] <- 0.5

    # contrast code 2 quadratic
    data$stim_con_quad[data$param_stimulus_type == "low_stim"] <- -0.33
    data$stim_con_quad[data$param_stimulus_type == "med_stim"] <- 0.66
    data$stim_con_quad[data$param_stimulus_type == "high_stim"] <- -0.33

    # social cude contrast
    data$social_cue[data$param_cue_type == "low_cue"] <- -0.5 # social influence task
    data$social_cue[data$param_cue_type == "high_cue"] <- 0.5 # no influence task
    data$cue_factor = factor(data$social_cue)
    data$subject = factor(data$src_subject_id)
    stim_con1 <- "stim_con_linear"
    stim_con2 <- "stim_con_quad"
    iv1 <- "cue_factor"
    dv <- "mean_signal"
    dv_keyword <- "EDA-scl-mean-signal"

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )
    
    cooksd <- lmer_twofactor_cooksd_fix(
        data = data, taskname = taskname, iv = iv1, stim_con1 = stim_con1, stim_con2 = stim_con2, dv = dv,
        subject_keyword = "subject", dv_keyword = dv_keyword, model_savefname = model_savefname, effects = 'random_intercept', print_lmer_output = TRUE
    )
    influential <- as.numeric(names(cooksd)[
        (cooksd > (4 / as.numeric(length(unique(data$src_subject_id)))))
    ])
    data_screen <- data[-influential, ]
    data_screen <- data
    # [ PLOT ] reordering for plots _________________________ # nolint
    data_screen$cue_name[data_screen$param_cue_type == "high_cue"] <- "high cue"
    data_screen$cue_name[data_screen$param_cue_type == "low_cue"] <- "low cue"

    data_screen$stim_name[data_screen$param_stimulus_type == "high_stim"] <- "high"
    data_screen$stim_name[data_screen$param_stimulus_type == "med_stim"] <- "med"
    data_screen$stim_name[data_screen$param_stimulus_type == "low_stim"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data_screen$stim_ordered <- factor(
        data_screen$stim_name,
        levels = c("low", "med", "high")
    )
    data_screen$cue_ordered <- factor(
        data_screen$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data_screen,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402
    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
    # if(any(startsWith(dv_keyword, c("expect", "Expect")))){color = c( "#1B9E77", "#D95F02")}else{color=c( "#4575B4", "#D73027")} # if keyword starts with
    # print("groupwisemean")
    #  [ PLOT ] calculate mean and se  ----------------------------------------------------------------------------
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "subject"
    ggtitle <- paste(taskname, " - Actual Rating (degree) Cooksd removed")
    title <- paste(taskname, " - Actual")
    xlab <- ""
    ylab <- "ratings (degree)"
    ylim <- c(-10,190)
    dv_keyword <- "actual"
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_halfrainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
    g

    
    # ggsave(plot_savefname, width = w, height = h)

    
    

    # save fixed random effects _______________________________
    # randEffect$newcoef <- mapvalues(randEffect$term,
    #     from = c("(Intercept)", "data[, iv]", 
    #              "data[, stim_con1]", "data[, stim_con2]", 
    #              "data[, iv]:data[, stim_con1]", 
    #              "data[, iv]:data[, stim_con2]"),
    #     to = c("rand_intercept", "rand_cue", "rand_stimlin", 
    #            "rand_stimquad", "rand_int_cue_stimlin", "rand_int_cue_stimquad")
    # )
    # 
    # #
    # # # The arguments to spread():
    # # # - data: Data object
    # # # - key: Name of column containing the new column names
    # # # - value: Name of column containing values
    # #
    # # # TODO: add fixed effects
    # #
    # rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
    # wide_rand <- spread(rand_subset, key = newcoef, value = condval)
    # wide_fix <- do.call(
    #     "rbind",
    #     replicate(nrow(wide_rand), as.data.frame(t(as.matrix(fixEffect))),
    #         simplify = FALSE
    #     )
    # )
    # rownames(wide_fix) <- NULL
    # new_wide_fix <- dplyr::rename(wide_fix,
    #     fix_intercept = `(Intercept)`, 
    #     fix_cue = `data[, iv]`,
    #     fix_stimulus_linear = `data[, stim_con1]`,
    #     fix_stimulus_quad = `data[, stim_con2]`, 
    #     fix_int_cue_stimlin = `data[, iv]:data[, stim_con1]`,
    #     fix_int_cue_stimquad = `data[, iv]:data[, stim_con2]`
    # )
    # 
    # total <- cbind(wide_rand, new_wide_fix)
    # total$task <- taskname
    # new_total <- total %>% dplyr::select(task, everything())
    # new_total <- dplyr::rename(total, subj = grp)
    # 
    # plot_savefname <- file.path(analysis_dir, 
    #                             paste("randeffect_task-", taskname, 
    #                                   "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = ""))
    # write.csv(new_total, plot_savefname, row.names = FALSE)
}


```

```{r}
library(ggpubr)
DATA = as.data.frame(groupwise)
color = c( "#4575B4", "#D73027")
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "ci"
dv_keyword = "actual"
    
    g <- ggplot(data = DATA, aes(
        x = stim_ordered,
        y = mean_per_sub_norm_mean,
        group = factor(cue_ordered),
        color = factor(cue_ordered)
    ), cex.lab = 1.5, cex.axis = 2, cex.main = 1.5, cex.sub = 1.5) +
        geom_errorbar(aes(
            ymin = (mean_per_sub_norm_mean - se),
            ymax = (mean_per_sub_norm_mean + se)
        ), width = .1) +
        geom_line() +
        geom_point() +
        # scale_x_continuous(breaks = seq(-3, +3, by = 1)) +
        # scale_y_continuous(breaks = seq(0, 90, by=30), limits=c(0,90)) +
        ggtitle(ggtitle) +
        xlab("Stimulus intensity") +
        ylab("Rating (degrees)") +
        # guides(fill=guide_legend(title="Social Endorsement Position")) +
        scale_color_manual(values = color) +
        theme_classic() +
        theme(legend.position = "none") +
        theme(aspect.ratio = .6)
g

```

```{r}

library(ggpubr)
DATA = as.data.frame(combined_se_calc_cooksd)
color = c( "#4575B4", "#D73027")
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "ci"
dv_keyword = "eda-mean-peak-amplitude"
p1 = plot_lineplot_twofactor_subset(DATA, 'pain', 
               LINEIV1, LINEIV2, MEAN, ERROR, color, ggtitle = 'pain' )
p2 = plot_lineplot_twofactor_subset(DATA,'vicarious', 
               LINEIV1, LINEIV2, MEAN, ERROR, color,ggtitle = 'vicarious')
p3 = plot_lineplot_twofactor_subset(DATA, 'cognitive', 
               LINEIV1, LINEIV2, MEAN, ERROR, color,ggtitle = 'cognitive')
#grid.arrange(p1, p2, p3, ncol=3 , common.legend = TRUE)
ggpubr::ggarrange(p1,p2,p3,ncol = 3, nrow = 1, common.legend = TRUE,legend = "bottom")
plot_filename = file.path(analysis_dir,
                          paste('lineplot_task-all_rating-',dv_keyword,'.png', sep = ""))
ggsave(plot_filename, width = 8, height = 4)
```
