# [fMRI] NPS ~ per trial {#fmri_nps_per_trial}

## What is the purpose of this notebook? {.unlisted .unnumbered}

- Here, I plot NPS dot products as a function of trial order, in order to visualize the progression of nociceptive values across time and session


```{r libraries_nps_stim, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(lme4)
library(optimx)
library(minqa)
library(dfoptim)
library(psych)
library(reshape)
library(dplyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(plyr)
library(ggpubr)
library(r2mlm)
library(effectsize)
library(devtools)
options(es.use_symbols = TRUE) # get nice symbols when printing! (On Windows, requires R >= 4.2.0)
library(EMAtools)
library(emmeans)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(DT)
library(raincloudplots)
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/R_rainclouds.R")
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/summarySE.R")

devtools::source_url("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(r2mlm)
main_dir <- dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R",
                          full.names=TRUE,
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```

## 0. load data and find intersection between behavioral and nps dataframes
```{r}
# load events.tsv
analysis_folder <- "fmri_nps"
beh <- readr::read_tsv(file.path(main_dir, "data/beh/sub-all_task-all_events.tsv"))
# load nps tsv
nps <- read.csv(file.path(main_dir, "analysis/fmri/nilearn/deriv01_signature/rampup_plateau/signature-NPS_sub-all_runtype-pvc_event-stimulus.tsv"), sep = ",")
# intersect
# Assuming df1 and df2 are your data frames and 'key_column' is the name of your key column
df_merge <- inner_join(beh, nps, by = "singletrial_fname")
taskname <- "pain"
```

```{r}
data <-df_merge[df_merge$runtype == "pain" ,]

# contrast code ________________________________________________________________
data$stim <- NA; data$STIM_linear <- NA; data$STIM_quadratic <- NA; 
data$CUE_high_gt_low <- NA;
data$SES_linear <- NA;data$SES_quadratic <- NA
data$stim[data$stimulusintensity == "low_stim"] <-  -0.5 # social influence task
data$stim[data$stimulusintensity == "med_stim"] <- 0 # no influence task
data$stim[data$stimulusintensity == "high_stim"] <-  0.5 # no influence task

data$STIM <- factor(data$stimulusintensity)

# contrast code 1 linear
data$STIM_linear[data$stimulusintensity == "low_stim"] <- -0.5
data$STIM_linear[data$stimulusintensity == "med_stim"] <- 0
data$STIM_linear[data$stimulusintensity == "high_stim"] <- 0.5

# contrast code 2 quadratic
data$STIM_quadratic[data$stimulusintensity == "low_stim"] <- -0.33
data$STIM_quadratic[data$stimulusintensity == "med_stim"] <- 0.66
data$STIM_quadratic[data$stimulusintensity == "high_stim"] <- -0.33

# social cude contrast
data$CUE_high_gt_low[data$cue == "low_cue"] <-  -0.5 # social influence task
data$CUE_high_gt_low[data$cue == "high_cue"] <-  0.5 # no influence task

data$EXPECT <- data$expectrating
data$OUTCOME <- data$outcomerating


data$SES_linear[data$ses == "ses-01"] <- -0.5
data$SES_linear[data$ses == "ses-03"] <- 0
data$SES_linear[data$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
data$SES_quadratic[data$ses == "ses-01"] <- -0.33
data$SES_quadratic[data$ses == "ses-03"] <- 0.66
data$SES_quadratic[data$ses == "ses-04"] <- -0.33

stim_con1 <- "STIM_linear"
stim_con2 <- "STIM_quadratic"
iv1 <- "CUE_high_gt_low"
dv <- "NPS"
dv_keyword <- "NPS"

# filter data __________________________________________________________________
# Make sure that each condition cell has adequate amount of trials
subjects_with_inadequate_data <- data %>%
  group_by(sub, CUE_high_gt_low, SES_linear, STIM_linear) %>%
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 3) %>%
  distinct(sub) %>%
  pull(sub)
df_filter <- data %>%
  filter(!(sub %in% subjects_with_inadequate_data))
```



## 1. NPS ~ trial x cue
```{r echo=FALSE}

df_clean <- df_clean %>%
  group_by(sub) %>% 
  mutate(trial_index_sub = row_number()) %>%
  ungroup()
count_trial <- df_clean %>% count("sub")

# Subset the data frame to include only the listed IDs

data_p2_long = df_clean %>%
  pivot_longer(cols = c( 'NPS'),
               names_to = "rating_type",
               values_to = "rating_value")

    data_p2_long$cue_name[data_p2_long$cue == "high_cue"] <- "high cue"
    data_p2_long$cue_name[data_p2_long$cue == "low_cue"] <- "low cue"

    data_p2_long$stim_name[data_p2_long$stimulusintensity == "high_stim"] <- "high"
    data_p2_long$stim_name[data_p2_long$stimulusintensity == "med_stim"] <- "med"
    data_p2_long$stim_name[data_p2_long$stimulusintensity == "low_stim"] <- "low"

    data_p2_long$stim_ordered <- factor(
        data_p2_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_p2_long$cue_ordered <- factor(
        data_p2_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    dv <- "rating_value"
    subject = "trial_index_sub"
    trialorder_subjectwise_p2 <- meanSummary(
        data_p2_long,
        c( model_iv2,  model_iv1, "trial_index_sub"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
    trialorder_subjectwise_p2 <- subset(trialorder_subjectwise_p2, trial_index_sub < 73)
    trialorder_groupwise_p2 <- summarySEwithin(
        data = trialorder_subjectwise_p2,
        measurevar = "mean_per_sub",
        withinvars = c("cue_ordered", "trial_index_sub" ),
    )
trialorder_subjectwise_p2 <- subset(trialorder_subjectwise_p2, trial_index_sub < 73)
# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index_sub"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_groupwise_p2,
  aes(x = as.numeric(trial_index_sub),
      y = mean_per_sub_norm_mean,
      color = cue_ordered,
      )
  ) +
  geom_smooth(
    method = "lm",
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index_sub),
      y = mean_per_sub_norm_mean,
      color = cue_ordered,
      )) +
    geom_point(
    data = trialorder_groupwise_p2,
    aes(
      x =as.numeric(trial_index_sub),
      y = mean_per_sub_norm_mean,
      color = cue_ordered
      ),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+
  geom_errorbar(
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index_sub),
      y = mean_per_sub_mean,
      colour = cue_ordered,
      ymin = mean_per_sub_norm_mean - se,
      ymax = mean_per_sub_norm_mean + se), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high cue" = "red", #"#009411",
                                "low cue" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPS") +
  labs(title = paste0(taskname, " (N = ", length(unique(data_p2_long$sub)), ")"))+
  theme_classic2() +
theme(aspect.ratio = .7) +
        theme(    axis.text.x = element_text(size = 20),
    axis.text.y = element_text(size = 20),
    axis.title.x = element_text(size = 25),
    axis.title.y = element_text(size = 25),
    axis.title = element_text(size = 40))
g
```


## 2. NPS ~ trial (N > 60) x cue 
```{r echo=FALSE}

count_trial <- df_clean %>% count("sub")
valid_subs <- count_trial %>%
  filter(freq >= 60 & freq <= 72)
# Subset the data frame to include only the listed IDs
df_subset <- df_clean %>%
  filter(sub %in% valid_subs$sub)
data_p2_long = df_subset %>%
  pivot_longer(cols = c( 'NPS'),
               names_to = "rating_type",
               values_to = "rating_value")
    data_p2_long$cue_name[data_p2_long$cue == "high_cue"] <- "high cue"
    data_p2_long$cue_name[data_p2_long$cue == "low_cue"] <- "low cue"

    data_p2_long$stim_name[data_p2_long$stimulusintensity == "high_stim"] <- "high"
    data_p2_long$stim_name[data_p2_long$stimulusintensity == "med_stim"] <- "med"
    data_p2_long$stim_name[data_p2_long$stimulusintensity == "low_stim"] <- "low"

    data_p2_long$stim_ordered <- factor(
        data_p2_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_p2_long$cue_ordered <- factor(
        data_p2_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    dv <- "rating_value"
    subject = "trial_index_sub"
    trialorder_subjectwise_p2 <- meanSummary(
        data_p2_long,
        c( model_iv2,  model_iv1, "trial_index_sub"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
    trialorder_subjectwise_p2 <- subset(trialorder_subjectwise_p2, trial_index_sub < 73)
    trialorder_groupwise_p2 <- summarySEwithin(
        data = trialorder_subjectwise_p2,
        measurevar = "mean_per_sub",
        withinvars = c("cue_ordered", "trial_index_sub" ),
    )
trialorder_subjectwise_p2 <- subset(trialorder_subjectwise_p2, trial_index_sub < 73)
# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index_sub"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_groupwise_p2,
  aes(x = as.numeric(trial_index_sub),
      y = mean_per_sub_norm_mean,
      color = cue_ordered,
      )
  ) +
  geom_smooth(
    method = "lm",
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index_sub),
      y = mean_per_sub_norm_mean,
      color = cue_ordered,
      )) +
    geom_point(
    data = trialorder_groupwise_p2,
    aes(
      x =as.numeric(trial_index_sub),
      y = mean_per_sub_norm_mean,
      color = cue_ordered
      ),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+
  geom_errorbar(
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index_sub),
      y = mean_per_sub_mean,
      colour = cue_ordered,
      ymin = mean_per_sub_norm_mean - se,
      ymax = mean_per_sub_norm_mean + se), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high cue" = "red", #"#009411",
                                "low cue" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPS") +
  labs(title = paste0(taskname, " (N = ", length(unique(data_p2_long$sub)), ")"))+
  theme_classic2() +
theme(aspect.ratio = .7) +
        theme(    axis.text.x = element_text(size = 20),
    axis.text.y = element_text(size = 20),
    axis.title.x = element_text(size = 25),
    axis.title.y = element_text(size = 25),
    axis.title = element_text(size = 40))
g
```

## 3. NPS ~ trial
```{r echo=FALSE}

count_trial <- df_clean %>% count("sub")
valid_subs <- count_trial %>%
  filter(freq >= 60 & freq <= 72)
# Subset the data frame to include only the listed IDs
df_subset <- df_clean %>%
  filter(sub %in% valid_subs$sub)
data_p2_long = df_subset %>%
  pivot_longer(cols = c( 'NPS'),
               names_to = "rating_type",
               values_to = "rating_value")
    data_p2_long$cue_name[data_p2_long$cue == "high_cue"] <- "high cue"
    data_p2_long$cue_name[data_p2_long$cue == "low_cue"] <- "low cue"

    data_p2_long$stim_name[data_p2_long$stimulusintensity == "high_stim"] <- "high"
    data_p2_long$stim_name[data_p2_long$stimulusintensity == "med_stim"] <- "med"
    data_p2_long$stim_name[data_p2_long$stimulusintensity == "low_stim"] <- "low"

    data_p2_long$stim_ordered <- factor(
        data_p2_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_p2_long$cue_ordered <- factor(
        data_p2_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    dv <- "rating_value"
    subject = "trial_index_sub"
    trialorder_subjectwise_p2 <- meanSummary(
        data_p2_long,
        c( model_iv2,  model_iv1, "trial_index_sub"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
    trialorder_subjectwise_p2 <- subset(trialorder_subjectwise_p2, trial_index_sub < 73)
    trialorder_groupwise_p2 <- summarySEwithin(
        data = trialorder_subjectwise_p2,
        measurevar = "mean_per_sub",
        withinvars = c("trial_index_sub" ), #"cue_ordered", 
    )
trialorder_subjectwise_p2 <- subset(trialorder_subjectwise_p2, trial_index_sub < 73)
# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index_sub"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_groupwise_p2,
  aes(x = as.numeric(trial_index_sub),
      y = mean_per_sub_norm_mean,
      #color = cue_ordered,
      )
  ) +
  geom_smooth(
    method = "lm",
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index_sub),
      y = mean_per_sub_norm_mean,
      #color = cue_ordered,
      )) +
    geom_point(
    data = trialorder_groupwise_p2,
    aes(
      x =as.numeric(trial_index_sub),
      y = mean_per_sub_norm_mean,
      #color = cue_ordered
      ),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+
  geom_errorbar(
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index_sub),
      y = mean_per_sub_mean,
     # colour = cue_ordered,
      ymin = mean_per_sub_norm_mean - se,
      ymax = mean_per_sub_norm_mean + se), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high cue" = "red", #"#009411",
                                "low cue" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPS") +
  labs(title = paste0(taskname, " (N = ", length(unique(data_p2_long$sub)), ")"))+
  theme_classic2() +
theme(aspect.ratio = .7) +
        theme(    axis.text.x = element_text(size = 20),
    axis.text.y = element_text(size = 20),
    axis.title.x = element_text(size = 25),
    axis.title.y = element_text(size = 25),
    axis.title = element_text(size = 40))
g
```

## 4. plot NPS as a function of subjects
```{r echo=FALSE}
library(ggforce)

# Plot with pagination using facet_wrap_paginate
g <- ggplot(
  data = df_clean, 
  aes(x = as.numeric(trial_index_sub), 
      y = NPS, 
      group = factor(sub))) + 
  geom_line(size = 0.5) + # Thinner lines for clarity
  geom_point(size = 1.5) + # Smaller points
  scale_shape_manual(values = c(21, 16)) +
  scale_color_manual(values = c("high cue" = "red", 
                                "low cue" = "blue")) + 
  xlab("No. of trials") + 
  ylab("NPS") + 
  labs(title = paste0(taskname, " (N = ", length(unique(df_clean$sub)), ")")) + 
  theme_classic2() + 
  theme(
    axis.text.x = element_text(size = 5), 
    axis.text.y = element_text(size = 5), 
    axis.title.x = element_text(size = 10), 
    axis.title.y = element_text(size = 10), 
    plot.title = element_text(size = 12), 
    strip.text = element_text(size = 6)) +
  ggforce::facet_wrap_paginate(~sub, scales = "free_y", ncol = 10, nrow = 10, page = 1) # Adjust columns, rows, and page

# Increase plot size
options(repr.plot.width = 20, repr.plot.height = 60) # Adjust as needed

g



```
## 5. NPS ~ sub trial cue
```{r echo=FALSE}
library(ggforce)

# Plot with pagination using facet_wrap_paginate
g <- ggplot(
  data = df_clean, 
  aes(x = as.numeric(trial_index_sub), 
      y = NPS, 
      group = factor(sub),
      color = cue
      )) + 
  geom_line(size = 0.5) + # Thinner lines for clarity
  geom_point(size = 1.5) + # Smaller points
  scale_shape_manual(values = c(21, 16)) +
  scale_color_manual(values = c("high_cue" = "red", 
                                "low_cue" = "blue")) + 
  xlab("No. of trials") + 
  ylab("NPS") + 
  labs(title = paste0(taskname, " (N = ", length(unique(df_clean$sub)), ")")) + 
  theme_classic2() + 
  theme(
    axis.text.x = element_text(size = 5), 
    axis.text.y = element_text(size = 5), 
    axis.title.x = element_text(size = 10), 
    axis.title.y = element_text(size = 10), 
    plot.title = element_text(size = 12), 
    strip.text = element_text(size = 6)) +
  ggforce::facet_wrap_paginate(~sub, scales = "free_y", ncol = 10, nrow = 10, page = 1) # Adjust columns, rows, and page

# Increase plot size
options(repr.plot.width = 20, repr.plot.height = 60) # Adjust as needed

g
```

## 6. why do we see outlierlike values
Let's plot each trial and its distribution
```{r}
# Filter data for trials 40 to 72
df_trials_40_72 <- df_subset %>%
  filter(trial_index_sub >= 40 & trial_index_sub <= 72)
# Filter the data for trials 40 to 72

# Plot the density plot for each trial index with faceting
ggplot(df_trials_40_72, aes(x = NPS, fill = cue)) +
  geom_density(alpha = 0.6) +
  facet_wrap(~ trial_index_sub, ncol = 4) + # Create a facet for each trial
  scale_fill_manual(values = c("high_cue" = "red", "low_cue" = "blue")) +
  xlab("NPS") +
  ylab("Density") +
  labs(title = "Density of NPS per Trial (40 to 72)") +
  theme_classic() +
  theme(
    strip.text = element_text(size = 5),
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 5),
    panel.spacing = unit(0.5, "lines"), 
    aspect.ratio = 0.8
  )

```


