# beh :: painpathway ROI ~ cue \* stim {#upgrade_beh-outcome-cueXstim}

## What is the purpose of this notebook? {.unlisted .unnumbered}

We investigate the profile of painpathway ROIs as a function of cue and stimulus intensity

- Main model: `lmer(outcome_rating ~ cue * stim)`
- Main question: do outcome ratings differ as a function of cue type and Stimulus intensity?
- If there is a main effect of cue on outcome ratings, does this cue effect differ depending on task type?
- Is there an interaction between the two factors?
- IV:
- cue (high / low)
- stim (high / med / low)
- DV: outcome rating

```{r libraries_nps_stim, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(lme4)
library(optimx)
library(minqa)
library(dfoptim)
library(tidyverse)
library(psych)
library(reshape)
library(dplyr)

library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(plyr)
library(ggpubr)
library(r2mlm)
library(effectsize)
# library(devtools)
options(es.use_symbols = TRUE) # get nice symbols when printing! (On Windows, requires R >= 4.2.0)
library(EMAtools)
library(emmeans)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(plotly)
library(DT)
library(raincloudplots)
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/R_rainclouds.R")
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/summarySE.R")

devtools::source_url("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(r2mlm)
main_dir <- dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R",
                          full.names=TRUE,
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```

# F. check CANLAB extract ROI

## F-1. load data

```{r}

main_dir <- dirname(dirname(getwd()))
analysis_folder <- "fmri_painpathway"
beh <- readr::read_tsv(file.path(main_dir, "data/beh/sub-all_task-all_events.tsv"))
all_data <- readr::read_tsv(file.path(main_dir, "analysis/fmri/nilearn/deriv01_signature/rampup_plateau_painpathway/roi-painpathway_sub-all_runtype-pvc_event-stimulus.tsv"))

# dv <- "nps"
# base_dir <- "/Volumes/spacetop_projects_cue/analysis/fmri/nilearn/deriv01_signature/rampup_plateau_painpathway"
# # TODO: instead of VPN, need to push to github
# # List all CSV files matching the pattern
# file_paths <- list.files(base_dir, pattern =  "sub-.*roi-painpathway_runtype-pain.*\\.csv$", full.names = TRUE, recursive = TRUE)
# 
# 
# # save results _________________________________________________________________
# analysis_folder <- "fmri_painpathway"
# analysis_dir <-
#   file.path(main_dir,
#             "analysis",
#             "mixedeffect",
#             analysis_folder,
#             as.character(Sys.Date())) # nolint
# dir.create(analysis_dir,
#            showWarnings = FALSE,
#            recursive = TRUE)
# savedir <- analysis_dir
# # Read and stack the CSV files
# all_data <- file_paths %>%
#   map_dfr(~read_csv(.x, show_col_types = FALSE), .id = "file_path")

df_merge <- inner_join(beh, all_data, by = "singletrial_fname")

df_merge <- df_merge %>%
  mutate(singletrial_fname = as.character(singletrial_fname)) %>%
  extract(singletrial_fname, into = c("sub", "ses", "run", "runtype", "event", "trial", "cuetype", "stimintensity"),
          regex = "^(sub-\\d+)_(ses-\\d+)_(run-\\d+)_runtype-(pain|vicarious|cognitive)_event-(cue|stimulus)_trial-(\\d+)_cuetype-(high|low)(?:_stimintensity-(high|med|low))?\\.nii.gz$",
          remove = FALSE)

# Adjust the dataframe to handle NA for missing stimintensity, if tidyr version doesn't support `fill`
df_merge$stimintensity[df_merge$stimintensity == ""] <- NA

data <-df_merge[df_merge$runtype == "pain" ,]

# contrast code ________________________________________________________________
data$stim <- NA; data$STIM_linear <- NA; data$STIM_quadratic <- NA;
data$CUE_high_gt_low <- NA;
data$SES_linear <- NA;data$SES_quadratic <- NA
data$stim[data$stimulusintensity == "low_stim"] <-  -0.5 # social influence task
data$stim[data$stimulusintensity == "med_stim"] <- 0 # no influence task
data$stim[data$stimulusintensity == "high_stim"] <-  0.5 # no influence task

data$STIM <- factor(data$stimulusintensity)

# contrast code 1 linear
data$STIM_linear[data$stimulusintensity == "low_stim"] <- -0.5
data$STIM_linear[data$stimulusintensity == "med_stim"] <- 0
data$STIM_linear[data$stimulusintensity == "high_stim"] <- 0.5

# contrast code 2 quadratic
data$STIM_quadratic[data$stimulusintensity == "low_stim"] <- -0.33
data$STIM_quadratic[data$stimulusintensity == "med_stim"] <- 0.66
data$STIM_quadratic[data$stimulusintensity == "high_stim"] <- -0.33

# social cude contrast
data$CUE_high_gt_low[data$cue == "low_cue"] <-  -0.5 # social influence task
data$CUE_high_gt_low[data$cue == "high_cue"] <-  0.5 # no influence task

data$EXPECT <- data$expectrating
data$OUTCOME <- data$outcomerating


data$SES_linear[data$ses == "ses-01"] <- -0.5
data$SES_linear[data$ses == "ses-03"] <- 0
data$SES_linear[data$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
data$SES_quadratic[data$ses == "ses-01"] <- -0.33
data$SES_quadratic[data$ses == "ses-03"] <- 0.66
data$SES_quadratic[data$ses == "ses-04"] <- -0.33

stim_con1 <- "STIM_linear"
stim_con2 <- "STIM_quadratic"
iv1 <- "CUE_high_gt_low"
dv <- "nps"
dv_keyword <- "NPS"
```
```{r}
#' Plot a Two-Factor Line Plot with Optional Subsetting
#'
#' This function creates a line plot for data with two factors. It allows for optional subsetting of the data based on a specified task name. If the 'taskname' column does not exist or 'taskname' is NULL, the function uses the entire dataset. It utilizes ggplot2 for plotting.
#'
#' @param data A data frame containing the dataset to be plotted.
#' @param taskname A string specifying the task name for subsetting the data, or NULL to use the entire dataset.
#' @param iv1 The name of the first independent variable (factor) for the x-axis.
#' @param iv2 The name of the second independent variable (factor) used for grouping and coloring.
#' @param mean The name of the column containing mean values to be plotted on the y-axis.
#' @param error The name of the column containing error values for error bars.
#' @param color A vector of colors to be used for the different groups represented by `iv2`.
#' @param ggtitle The title of the plot.
#' @param xlab Label for the x-axis. Default is "Stimulus Intensity".
#' @param ylab Label for the y-axis. Default is "Outcome Rating".
#'
#' @return A ggplot object representing the line plot.
#'
#' @import ggplot2
#' @export
#'
#' @examples
#' # Example usage with taskname specified:
#' p1 = plot_lineplot_twofactor_subset(data = mydata, taskname = "task1",
#'               iv1 = "intensity", iv2 = "cue", mean = "mean_score", error = "ci",
#'               color = c("red", "blue"), ggtitle = "My Plot")
#'
#' # Example usage without taskname (using entire dataset):
#' p2 = plot_lineplot_twofactor_subset(data = mydata, taskname = NULL,
#'               iv1 = "intensity", iv2 = "cue", mean = "mean_score", error = "ci",
#'               color = c("red", "blue"), ggtitle = "My Plot")
#' [Example plot](TODO)
plot_lineplot_twofactor_subset <- function(data, taskname, iv1, iv2, mean, error,
                                           color, ggtitle, xlab = NULL, ylab = NULL) {
  
  # Check if 'taskname' column exists in 'data'
  if ("runtype" %in% names(data) && !is.null(taskname)) {
    subset <- data[which(data$runtype == taskname), ]
  } else {
    # If 'taskname' column does not exist or 'taskname' is NULL, use the entire dataframe
    subset <- data
  }
  
  # Use default labels if none are provided
  if (is.null(xlab)) xlab <- "Stimulus intensity"
  if (is.null(ylab)) ylab <- "Outcome rating"
  
  g <- ggplot(data = subset, aes(
    x = .data[[iv1]],
    y = .data[[mean]],
    group = as.factor(.data[[iv2]]),
    color = as.factor(.data[[iv2]])
  ), cex.lab = 1.5, cex.axis = 2, cex.main = 1.5, cex.sub = 1.5) +
    geom_pointrange(aes(
      ymin = (.data[[mean]] - .data[[error]]),
      ymax = (.data[[mean]] + .data[[error]])
    ), 
    size = 1,  # Increased thickness for the error bars
    width = 3  # Slightly wider horizontal caps
    ) +
    geom_line(linewidth=1, aes(linetype = as.factor(.data[[iv2]]) )) + # change back to geom_line() +
    ggtitle(ggtitle) +
    xlab(xlab) +
    ylab(ylab) +
    scale_color_manual(values = color) +
    scale_linetype_manual(values = c("solid", "solid")) +
    theme_classic() +
    # ylim(40, 90)+
    theme(aspect.ratio = 1 ,
          axis.line = element_line(size = 0.2),
          axis.ticks = element_line(size = 0.2), # Thin tick marks
          axis.ticks.length = unit(-3, "pt"),
          legend.position = "none")
  return(g)
}
```
## F-2. Filter data and plot

```{r}
# filter data __________________________________________________________________
# Make sure that each condition cell has adequate amount of trials
# dependent_vars <- c("Thal_VPLM_L","Thal_VPLM_R","Thal_IL","Thal_MD","Hythal","pbn_R","pbn_L","Bstem_PAG","rvm_R","Amy_R"
# ,"Amy_L","dpIns_L","dpIns_R","S2_L","S2_R","mIns_L","mIns_R","aIns_L","aIns_R"      ,
# "aMCC_MPFC","s1_foot_L","s1_foot_R","s1_handplus_L","s1_handplus_R"    )  # Update this with your actual DVs
# newlist <- c("Thal_VPLM (L)", "Thal_VPLM (R)", "Thal_IL","Thal_MD","Hythal","PBN (R)","PBN (L)","Bstem & PAG","RVM (R)","Amy (R)"
# ,"Amy (L)","dpIns (L)","dpIns (R)","SII (L)","SII (R)","mIns (L)","mIns (R)","aIns (L)","aIns (R)"      ,
# "aMCC & MPFC","SI foot (L)","SI foot (R)","SI handplus (L)","SI handplus (R)"    )  # Update this with your actual DVs

dependent_vars <- c("Thal_VPLM","Thal_IL","Thal_MD","Hythal","pbn","Bstem_PAG","rvm"
,"Amy","dpIns","S2","mIns","aIns" ,
"aMCC_MPFC","s1_foot","s1_handplus"   )  # Update this with your actual DVs
newlist <- c("Thal_VPLM","Thal_IL","Thal_MD","Hythal","pbn","Bstem_PAG","rvm"
,"Amy","dpIns","S2","mIns","aIns"      ,
"aMCC_MPFC","s1_foot","s1_handplus"   )  # Update this with your actual DVs
# newlist <- dependent_vars #c()
# Initialize a DataFrame to collect combined results
combined_se_calc_cooksd <- data.frame()
for (i in seq_along(dependent_vars)) {
  dv <- dependent_vars[i]
  dv_title <- newlist[i]
# for (dv in dependent_vars) {
subjects_with_inadequate_data <- data %>%
  group_by(sub, CUE_high_gt_low, STIM_linear) %>% #SES_linear,
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 2) %>%
  distinct(sub) %>%
  pull(sub)
df_filter <- data %>%
  filter(!(sub %in% subjects_with_inadequate_data))

print(sprintf("after filtering out subjects that have less than 2 trials in cell, we have N=%d -> N=%d",length(unique(data$sub)), length(unique(df_filter$sub)) ))

## QC. check NPS distribution __________________________________________________________________

df_filter.NA <- df_filter# %>% filter(!is.na(nps))  # Remove NA values
head(df_filter.NA)


combined_se_calc_cooksd <- data.frame()
taskname = "pain"
ggtitle <- paste(taskname, " - Painpathway")
title <- paste(taskname, " - actual")
subject <- "sub"
w <- 10
h <- 6


analysis_dir <-
  file.path(main_dir,
            "analysis",
            "mixedeffect",
            analysis_folder,
            as.character(Sys.Date())) # nolint
dir.create(analysis_dir,
           showWarnings = FALSE,
           recursive = TRUE)
savedir <- analysis_dir



# df_filter.NA <- df_filter.NA %>%
#     group_by(sub) %>%
#     mutate(NPS_scaled = scale(nps)) %>%
#     ungroup()

# [ PLOT ] reordering for plots _________________________ # nolint
df_filter.NA$cue_name[df_filter.NA$cue == "high_cue"] <-  "high cue"
df_filter.NA$cue_name[df_filter.NA$cue == "low_cue"] <-  "low cue"

df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "high_stim"] <-  "High"
df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "med_stim"] <-  "Med"
df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "low_stim"] <-  "Low"

df_filter.NA$stim_ordered <- factor(df_filter.NA$stim_name, levels = c("Low", "Med", "High"))
df_filter.NA$cue_ordered <- factor(df_filter.NA$cue_name, levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"
# lmer model __________________________________________________________________
model_savefname <- file.path(
  analysis_dir,
  paste(
    "lmer_nps-",dv,"_",as.character(Sys.Date()),".txt",
    sep = ""
  )
)
formula_string <- paste(dv, "~ CUE_high_gt_low * STIM_linear + CUE_high_gt_low * STIM_quadratic + (1|sub)")
model_formula <- as.formula(formula_string)
# Fit the model
sink(model_savefname)
model.npscuestim <- lmer(model_formula, data = df_filter.NA, control = lmerControl(
      optimizer = "bobyqa",
      # optCtrl = list(
      #   method = "nmkb",
      #   maxit = 1e9,
      #   maxfun = 1e9,
      #   maxeval = 1e7,
      #   xtol_abs = 1e-9,
      #   ftol_abs = 1e-9
      # )
    ))

print(summary(model.npscuestim))
sink()
# summary statistics calculate mean and se  ____________________________________
NPSstimcue_subjectwise <- meanSummary(df_filter.NA,
                                      c(subject, model_iv1, model_iv2), dv)
NPSstimcue_groupwise <- summarySEwithin(
  data = NPSstimcue_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
NPSstimcue_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

combined_se_calc_cooksd <-
  rbind(combined_se_calc_cooksd, NPSstimcue_groupwise)
# plot parameters ______________________________________________________________
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
subject <- "sub"
ggtitle <- paste(taskname, " - Pain Pathway Cooksd removed")
title <- paste(taskname, " - Pain Pathway")
xlab <- ""
ylab <- "Pain Pathway (degree)"
# ylim <- c(-1,1)
dv_keyword <- dv #"painpathway"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#0b5fa6", "#0b5fa6")
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), "_cooksd.png",
    sep = ""
  )
)



### Lineplots with only low cue ____________________________________
subsetNPS <- NPSstimcue_groupwise[NPSstimcue_groupwise$cue_ordered == "low cue",]
g <- plot_lineplot_twofactor_subset(subsetNPS, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#0b5fa6", "#0b5fa6"),
                        ggtitle = dv_title,
                        xlab = "Stimulus intensity", ylab = "Mean score")
g + theme(aspect.ratio=.8)


### Lineplots________________________________________________________________________
g <- plot_lineplot_twofactor_subset(NPSstimcue_groupwise, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#0b5fa6","high cue" = "#C5263A"),
                        ggtitle = dv_title, 
                        xlab = "Stimulus intensity", ylab = "Mean score")
g <- g + theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
   geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 3)  # Adjust point size


#   print(arranged_plot)
  plot_filename = file.path(analysis_dir,
  paste('lineplot_task-all_rating-', dv_keyword,dv, '.svg', sep = ""))

print(g)

  ggsave(plot_filename, g, width = 8, height = 4, dpi=300)
}

```

### Session wise plots


1. organize session wiese data frame

```{r}
#### STEP 1: Create df_filter.NA ONCE before the loop (with all ROIs)

# Filter subjects with inadequate data
subjects_with_inadequate_data <- data %>%
  group_by(sub, CUE_high_gt_low, STIM_linear) %>%
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 2) %>%
  distinct(sub) %>%
  pull(sub)

df_filter <- data %>%
  filter(!(sub %in% subjects_with_inadequate_data))

print(sprintf("after filtering out subjects that have less than 2 trials in cell, we have N=%d -> N=%d",
              length(unique(data$sub)), length(unique(df_filter$sub))))

# This is your df_filter.NA for ALL ROIs
df_filter.NA <- df_filter

#### STEP 2: Create session-filtered version with adequate trials per cell
subjects_with_inadequate_data_ses <- df_filter.NA %>%
  group_by(sub, CUE_high_gt_low, STIM_linear, SES_linear) %>%
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 3) %>%
  distinct(sub) %>%
  pull(sub)

df_filter_ses <- df_filter.NA %>%
  filter(!(sub %in% subjects_with_inadequate_data_ses))

print(sprintf("after filtering for session analysis (3+ trials per cell), we have N=%d -> N=%d",
              length(unique(df_filter.NA$sub)), length(unique(df_filter_ses$sub))))

#### STEP 3: Now plot sessionwise Pain Pathway ROIs
library(ggplot2)
library(dplyr)

# Define ROIs
dependent_vars <- c("Thal_VPLM","Thal_IL","Thal_MD","Hythal","pbn","Bstem_PAG","rvm","Amy",
                    "dpIns","S2","mIns","aIns","aMCC_MPFC","s1_foot","s1_handplus")

newlist <- c("Thal_VPLM","Thal_IL","Thal_MD","Hythal","PBN","Bstem & PAG","RVM","Amygdala",
             "dpIns","S2","mIns","aIns","aMCC & MPFC","S1 foot","S1 handplus")

# Loop through all ROIs
for (i in seq_along(dependent_vars)) {
  dv <- dependent_vars[i]
  dv_title <- newlist[i]
  
  print(paste("Plotting", dv_title, "across sessions..."))
  
  # Check if column exists
  if (!dv %in% names(df_filter_ses)) {
    print(paste("WARNING: Column", dv, "not found in df_filter_ses - skipping"))
    next
  }
  
  # 1. Prepare data with session labels
  df_filter_ses$ses_name <- factor(df_filter_ses$ses,
                                    levels = c("ses-01", "ses-03", "ses-04"),
                                    labels = c("Session 1", "Session 2", "Session 3"))
  
  df_filter_ses$cue_name <- NA
  df_filter_ses$cue_name[df_filter_ses$cue == "high_cue"] <- "High cue"
  df_filter_ses$cue_name[df_filter_ses$cue == "low_cue"] <- "Low cue"
  
  df_filter_ses$stim_name <- NA
  df_filter_ses$stim_name[df_filter_ses$stimulusintensity == "high_stim"] <- "High"
  df_filter_ses$stim_name[df_filter_ses$stimulusintensity == "med_stim"] <- "Med"
  df_filter_ses$stim_name[df_filter_ses$stimulusintensity == "low_stim"] <- "Low"
  
  df_filter_ses$stim_ordered <- factor(df_filter_ses$stim_name, 
                                        levels = c("Low", "Med", "High"))
  df_filter_ses$cue_ordered <- factor(df_filter_ses$cue_name, 
                                       levels = c("Low cue", "High cue"))
  
  # 2. Calculate summary statistics for this ROI
  ROI_summary <- df_filter_ses %>%
    group_by(ses_name, stim_ordered, cue_ordered, sub) %>%
    summarise(mean_per_sub = mean(.data[[dv]], na.rm = TRUE), .groups = "drop") %>%
    group_by(ses_name, stim_ordered, cue_ordered) %>%
    summarise(
      mean = mean(mean_per_sub, na.rm = TRUE),
      se = sd(mean_per_sub, na.rm = TRUE) / sqrt(n()),
      .groups = "drop"
    )
  
  # 3. Plot with facets by session
  p <- ggplot(ROI_summary, aes(x = stim_ordered, y = mean, 
                                  color = cue_ordered, group = cue_ordered)) +
    geom_linerange(aes(ymin = mean - se, ymax = mean + se), 
                   linewidth = 0.5) +
    geom_line(linewidth = 1) +
    geom_point(size = 4, shape = 16) +
    facet_wrap(~ ses_name, ncol = 3) +
    scale_color_manual(values = c("Low cue" = "#4274AD", "High cue" = "#C5263A")) +
    labs(
      title = paste(dv_title, "Across Sessions"),
      x = "Stimulus Intensity",
      y = dv_title,
      color = "Cue Type"
    ) +
    theme_classic() +
    theme(
      aspect.ratio = 0.8,
      axis.line = element_line(linewidth = 0.5),
      axis.text = element_text(size = 12),
      axis.title = element_text(size = 14),
      plot.title = element_text(size = 16, hjust = 0.5),
      strip.background = element_blank(),
      strip.text = element_text(size = 14, face = "bold"),
      legend.position = "bottom"
    )
  
  print(p)
  
  # Save
  ggsave(file.path(analysis_dir, paste0("roi-", dv, "_by_session_", Sys.Date(), ".svg")),
         plot = p, width = 10, height = 4, dpi = 300)
}
```

2. plot per session
```{r}
#### plot sessionwise Pain Pathway ROIs [ Update ]
library(ggplot2)
library(dplyr)

# Define ROIs
dependent_vars <- c("Thal_VPLM","Thal_IL","Thal_MD","Hythal","pbn","Bstem_PAG","rvm","Amy",
                    "dpIns","S2","mIns","aIns","aMCC_MPFC","s1_foot","s1_handplus")

newlist <- c("Thal_VPLM","Thal_IL","Thal_MD","Hythal","PBN","Bstem & PAG","RVM","Amygdala",
             "dpIns","S2","mIns","aIns","aMCC & MPFC","S1 foot","S1 handplus")

# Loop through all ROIs
for (i in seq_along(dependent_vars)) {
  dv <- dependent_vars[i]
  dv_title <- newlist[i]
  
  print(paste("Plotting", dv_title, "across sessions..."))
  
  # 1. Prepare data with session labels (INSIDE the loop)
  df_filter_ses$ses_name <- factor(df_filter_ses$ses,
                                    levels = c("ses-01", "ses-03", "ses-04"),
                                    labels = c("Session 1", "Session 2", "Session 3"))
  
  df_filter_ses$cue_name <- NA
  df_filter_ses$cue_name[df_filter_ses$cue == "high_cue"] <- "High cue"
  df_filter_ses$cue_name[df_filter_ses$cue == "low_cue"] <- "Low cue"
  
  df_filter_ses$stim_name <- NA
  df_filter_ses$stim_name[df_filter_ses$stimulusintensity == "high_stim"] <- "High"
  df_filter_ses$stim_name[df_filter_ses$stimulusintensity == "med_stim"] <- "Med"
  df_filter_ses$stim_name[df_filter_ses$stimulusintensity == "low_stim"] <- "Low"
  
  df_filter_ses$stim_ordered <- factor(df_filter_ses$stim_name, 
                                        levels = c("Low", "Med", "High"))
  df_filter_ses$cue_ordered <- factor(df_filter_ses$cue_name, 
                                       levels = c("Low cue", "High cue"))
  
  # 2. Calculate summary statistics for this ROI
  ROI_summary <- df_filter_ses %>%
    group_by(ses_name, stim_ordered, cue_ordered, sub) %>%
    summarise(mean_per_sub = mean(!!sym(dv), na.rm = TRUE), .groups = "drop") %>%
    group_by(ses_name, stim_ordered, cue_ordered) %>%
    summarise(
      mean = mean(mean_per_sub, na.rm = TRUE),
      se = sd(mean_per_sub, na.rm = TRUE) / sqrt(n()),
      .groups = "drop"
    )
  
  # 3. Plot with facets by session
  p <- ggplot(ROI_summary, aes(x = stim_ordered, y = mean, 
                                  color = cue_ordered, group = cue_ordered)) +
    geom_linerange(aes(ymin = mean - se, ymax = mean + se), 
                   linewidth = 0.5) +
    geom_line(linewidth = 1) +
    geom_point(size = 4, shape = 16) +
    facet_wrap(~ ses_name, ncol = 3) +
    scale_color_manual(values = c("Low cue" = "#4274AD", "High cue" = "#C5263A")) +
    labs(
      title = paste(dv_title, "Across Sessions"),
      x = "Stimulus Intensity",
      y = dv_title,
      color = "Cue Type"
    ) +
    theme_classic() +
    theme(
      aspect.ratio = 0.8,
      axis.line = element_line(linewidth = 0.5),
      axis.text = element_text(size = 12),
      axis.title = element_text(size = 14),
      plot.title = element_text(size = 16, hjust = 0.5),
      strip.background = element_blank(),
      strip.text = element_text(size = 14, face = "bold"),
      legend.position = "bottom"
    )
  
  print(p)
  
  # Save
  ggsave(file.path(analysis_dir, paste0(dv, "_by_session_", Sys.Date(), ".svg")),
         plot = p, width = 10, height = 4, dpi = 300)
}
```



```{r}
library(ggplot2)
library(dplyr)
library(lme4)
library(ggeffects)

# Assuming 'data' is your dataset already loaded
dependent_vars <- c("Thal_VPLM","Thal_IL","Thal_MD","Hythal","pbn_R","pbn_L","Bstem_PAG","rvm_R",
                    "Amy_R","Amy_L","dpIns_L","dpIns_R","S2_L","S2_R","mIns_L","mIns_R","aIns_L","aIns_R",
                    "aMCC_MPFC","s1_foot_L","s1_foot_R","s1_handplus_L","s1_handplus_R")

# Filtering data
df_filtered <- data %>%
  group_by(sub, CUE_high_gt_low, STIM_linear) %>%
  filter(n() >= 3) %>%
  ungroup()

# Create a function to generate models and plots
generate_plots <- function(dv) {
  # Construct the model formula dynamically
  formula_string <- paste(dv, "~ CUE_high_gt_low * STIM_linear  + CUE_high_gt_low * STIM_quadratic+ (CUE_high_gt_low + STIM_linear|sub)")
  model <- lmer(as.formula(formula_string), data = df_filtered)

  # Generate predictions for plotting
  preds <- ggpredict(model, terms = c("CUE_high_gt_low", "STIM_linear"))

  # Create the plot
  p <- ggplot(preds, aes(x = x, y = predicted, color = group)) +
    geom_line() +
    geom_point() +
    labs(title = dv, y = "Predicted Value", x = "Stimulus Linear") +
    theme_minimal()

  return(p)
}

# Apply the function across all dependent variables and store plots
plots <- lapply(dependent_vars, generate_plots)

# Combine plots into a single grid
library(gridExtra)
grid.arrange(grobs = plots, ncol = 4)  # Adjust the number of columns as needed

```

```{r}
# filter data __________________________________________________________________
# Make sure that each condition cell has adequate amount of trials
dependent_vars <- c("Thal_VPLM_L","Thal_VPLM_R","Thal_IL","Thal_MD","Hythal","pbn_R","pbn_L","Bstem_PAG","rvm_R","Amy_R"
,"Amy_L","dpIns_L","dpIns_R","S2_L","S2_R","mIns_L","mIns_R","aIns_L","aIns_R"      ,
"aMCC_MPFC","s1_foot_L","s1_foot_R","s1_handplus_L","s1_handplus_R"    )  # Update this with your actual DVs
newlist <- c("Thal_VPLM (L)", "Thal_VPLM (R)", "Thal_IL","Thal_MD","Hythal","PBN (R)","PBN (L)","Bstem & PAG","RVM (R)","Amy (R)"
,"Amy (L)","dpIns (L)","dpIns (R)","SII (L)","SII (R)","mIns (L)","mIns (R)","aIns (L)","aIns (R)"      ,
"aMCC & MPFC","SI foot (L)","SI foot (R)","SI handplus (L)","SI handplus (R)"    )  # Update this with your actual DVs


# newlist <- dependent_vars #c()
# Initialize a DataFrame to collect combined results
combined_se_calc_cooksd <- data.frame()
for (i in seq_along(dependent_vars)) {
  dv <- dependent_vars[i]
  dv_title <- newlist[i]
# for (dv in dependent_vars) {
subjects_with_inadequate_data <- data %>%
  group_by(sub, CUE_high_gt_low, STIM_linear) %>% #SES_linear,
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 2) %>%
  distinct(sub) %>%
  pull(sub)
df_filter <- data %>%
  filter(!(sub %in% subjects_with_inadequate_data))

print(sprintf("after filtering out subjects that have less than 2 trials in cell, we have N=%d -> N=%d",length(unique(data$sub)), length(unique(df_filter$sub)) ))

## QC. check NPS distribution __________________________________________________________________

df_filter.NA <- df_filter# %>% filter(!is.na(nps))  # Remove NA values
head(df_filter.NA)


combined_se_calc_cooksd <- data.frame()
taskname = "pain"
ggtitle <- paste(taskname, " - NPS (degree)")
title <- paste(taskname, " - actual")
subject <- "sub"
w <- 10
h <- 6


analysis_dir <-
  file.path(main_dir,
            "analysis",
            "mixedeffect",
            analysis_folder,
            as.character(Sys.Date())) # nolint
dir.create(analysis_dir,
           showWarnings = FALSE,
           recursive = TRUE)
savedir <- analysis_dir



# df_filter.NA <- df_filter.NA %>%
#     group_by(sub) %>%
#     mutate(NPS_scaled = scale(nps)) %>%
#     ungroup()

# [ PLOT ] reordering for plots _________________________ # nolint
df_filter.NA$cue_name[df_filter.NA$cue == "high_cue"] <-  "high cue"
df_filter.NA$cue_name[df_filter.NA$cue == "low_cue"] <-  "low cue"

df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "high_stim"] <-  "High"
df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "med_stim"] <-  "Med"
df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "low_stim"] <-  "Low"

df_filter.NA$stim_ordered <- factor(df_filter.NA$stim_name, levels = c("Low", "Med", "High"))
df_filter.NA$cue_ordered <- factor(df_filter.NA$cue_name, levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"
# lmer model __________________________________________________________________
model_savefname <- file.path(
  analysis_dir,
  paste(
    "lmer_nps-",dv,"_",as.character(Sys.Date()),".txt",
    sep = ""
  )
)
formula_string <- paste(dv, "~ CUE_high_gt_low * STIM_linear + CUE_high_gt_low * STIM_quadratic + (CUE_high_gt_low + STIM_linear|sub)")
model_formula <- as.formula(formula_string)
# Fit the model
sink(model_savefname)
model.npscuestim <- lmer(model_formula, data = df_filter.NA, control = lmerControl(
      optimizer = "optimx",
      optCtrl = list(
        method = "nmkb",
        maxit = 1e9,
        maxfun = 1e9,
        maxeval = 1e7,
        xtol_abs = 1e-9,
        ftol_abs = 1e-9
      )
    ))

print(summary(model.npscuestim))
sink()
# summary statistics calculate mean and se  ____________________________________
NPSstimcue_subjectwise <- meanSummary(df_filter.NA,
                                      c(subject, model_iv1, model_iv2), dv)
NPSstimcue_groupwise <- summarySEwithin(
  data = NPSstimcue_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
NPSstimcue_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

combined_se_calc_cooksd <-
  rbind(combined_se_calc_cooksd, NPSstimcue_groupwise)
# plot parameters ______________________________________________________________
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
subject <- "sub"
ggtitle <- paste(taskname, " - NPS Cooksd removed")
title <- paste(taskname, " - NPS")
xlab <- ""
ylab <- "NPS (degree)"
ylim <- c(-1,1)
dv_keyword <- "NPS"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#0b5fa6", "#0b5fa6")
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), "_cooksd.png",
    sep = ""
  )
)



### Lineplots with only low cue ____________________________________
subsetNPS <- NPSstimcue_groupwise[NPSstimcue_groupwise$cue_ordered == "low cue",]
g <- cueR::plot_lineplot_twofactor_subset(subsetNPS, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#4274AD", "#4274AD"),
                        ggtitle = dv_title,
                        xlab = "Stimulus intensity", ylab = "Average BOLD")
g + theme(aspect.ratio=.8)


### Lineplots________________________________________________________________________
g <- cueR::plot_lineplot_twofactor_subset(NPSstimcue_groupwise, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#4274AD","high cue" = "#C5263A"),
                        ggtitle = dv_title,
                        xlab = "Stimulus intensity", ylab = "Average BOLD")
g <- g + theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
   geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 3)  # Adjust point size


#   print(arranged_plot)
  plot_filename = file.path(analysis_dir,
  paste('lineplot_task-all_rating-', dv_keyword,dv, '.svg', sep = ""))

print(g)

  ggsave(paste0("/Users/h/Documents/projects_local/cue_expectancy/resources/plots_dissertation/ch4/painpathway_cue_",dv,".svg"), g, width = 4, height = 4, dpi=300)
}
```
