# [fMRI] NPS ~ pvc {#nps_task}

## What is the purpose of this notebook? {.unlisted .unnumbered}

- Here, I model NPS dot products as a function of cue, stimulus intensity and expectation ratings.
- One of the findings is that low cues lead to higher NPS dotproducts in the high intensity group, and that this effect becomes non-significant across sessions.
- 03/23/2023: For now, I'm grabbing participants that have complete data, i.e. 18 runs, all three sessions.

```{r libraries_nps_stim, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(psych)
library(reshape)
library(dplyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(plyr)
library(ggpubr)
library(r2mlm)
library(effectsize)
library(devtools)
options(es.use_symbols = TRUE) # get nice symbols when printing! (On Windows, requires R >= 4.2.0)
library(EMAtools)
library(emmeans)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(DT)
library(raincloudplots)
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/R_rainclouds.R")
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/summarySE.R")

devtools::source_url("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(r2mlm)
main_dir <- dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R",
                          full.names=TRUE,
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```


```{r}
# load events.tsv
analysis_folder <- "fmri_nps"
beh <- readr::read_tsv(file.path(main_dir, "data/beh/sub-all_task-all_events.tsv"))
# load nps tsv
nps <- read.csv(file.path(main_dir, "analysis/fmri/nilearn/deriv01_signature/rampup_plateau/signature-NPS_sub-all_runtype-pvc_event-stimulus.tsv"), sep = ",")
# intersect
# Assuming df1 and df2 are your data frames and 'key_column' is the name of your key column
df_merge <- inner_join(beh, nps, by = "singletrial_fname")

```





```{r function::summary_for_plots_pvc, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
summary_for_plots_PVC <- function(df, groupwise_measurevar, subject_keyword, model_iv1, model_iv2, dv) {
    #  [ PLOT ] calculate mean and se  _________________________
    subjectwise <- meanSummary(
        df,
        c(subject_keyword, model_iv1, model_iv2), dv
    )
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = groupwise_measurevar,
        withinvars = c(model_iv1, model_iv2), idvar = subject_keyword
    )

    return(list(subjectwise,groupwise))
}
```

```{r function::simple_contrasts_singletrial, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
simple_contrasts_singletrial <- function(df) {
# [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
df$STIM <- factor(df$stimulusintensity)

# contrast code 1 linear
df$STIM_linear[df$stimulusintensity == "low"] <-  -0.5
df$STIM_linear[df$stimulusintensity == "med"] <-  0
df$STIM_linear[df$stimulusintensity == "high"] <-  0.5

# contrast code 2 quadratic
df$STIM_quadratic[df$stimulusintensity == "low"] <-  -0.33
df$STIM_quadratic[df$stimulusintensity == "med"] <-  0.66
df$STIM_quadratic[df$stimulusintensity == "high"] <-  -0.33

# cue contrast
df$CUE_high_gt_low[df$cue == "low"] <-  -0.5 # social influence task
df$CUE_high_gt_low[df$cue == "high"] <-  0.5 # no influence task

df$stim_ordered <- factor(
        df$stimulusintensity,
        levels = c("low", "med", "high")
    )

df$cue_name[df$cuetype == "low"] <- "low"
df$cue_name[df$cuetype == "high"] <- "high"

df$cue_ordered <- factor(
        df$cue_name,
        levels = c("low", "high")
    )
return(df)
}
```

```{r function::NPS_lineplot_34, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
two_factor_lineplot <-
  function(df, iv1, iv2, mean, error, xlab, ylab) {
    g <- ggplot(
      data = df,
      aes(
        x = .data[[iv1]],
        y = .data[[mean]],
        group = factor(.data[[iv2]]),
        color = factor(.data[[iv2]])
      ),
      cex.lab = 1.5,
      cex.axis = 2,
      cex.main = 1.5,
      cex.sub = 1.5
    ) +
      geom_errorbar(aes(
        ymin = (.data[[mean]] - .data[[error]]),
        ymax = (.data[[mean]] + .data[[error]])
      ), width = .1) +
      geom_line() +
      geom_point() +
      ggtitle(ggtitle) +
      xlab(xlab) +
      ylab(ylab) +
      #scale_color_manual(values = color) +
      theme_classic() +

      theme(aspect.ratio = .6) +
      expand_limits(x = 3.25) +
      #guides(fill = "none") +
      #guides(color = TRUE) +
      #guides(fill = guide_legend(title = "title")) +
      #scale_fill_manual(values = color) +
      scale_color_manual("",
                         values =  c(
                           "pain" = "#941100",
                           "vicarious" = "#008F51",
                           "cognitive" = "#011891"
                         )) +
      theme(
        legend.position = c(.99, .99),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      theme(legend.key = element_rect(fill = "white", colour = "white")) +
      theme_bw()

    return(g)
  }
```

## 1. NPS ~ 3 task x 3 stimulus intensity

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Step 1: Common parameters
# step 1: load data
for (signature_key in c("NPS")) {
     #c("NPS", "NPS", "NPSneg", "VPS", #"VPSnooccip", "ThermalPain", "MechPain", "GeneralAversive", "AversiveVisual"
                      #  "ZhouVPS", "PINES",  "GSR", "GeuterPaincPDM")) {
  dv_keyword = signature_key
  signature_name = signature_key
  # step 1: common parameters _______
  main_dir <- dirname(dirname(getwd()))

  analysis_folder  = paste0("model35_iv-task-stim_dv-", signature_key)

  sig_name <-
    Sys.glob(file.path(
      main_dir,
      "analysis/fmri/nilearn/signature_extract",
      paste0(
        "signature-",
        signature_key,
        "_sub-all_runtype-pvc_event-stimulus.tsv"
      )
    )) # nolint
  print(sig_name)
  analysis_dir <-
    file.path(main_dir,
              "analysis",
              "mixedeffect",
              analysis_folder,
              as.character(Sys.Date())) # nolint
  dir.create(analysis_dir,
             showWarnings = FALSE,
             recursive = TRUE)
  savedir <- analysis_dir

  # step 2: load data
  df = read.csv(sig_name)
  sig_df = df %>% separate(
    singletrial_fname,
    sep = "_",
    c(
      "sub",
      "ses",
      "run",
      "runtype",
      "event",
      "trial",
      "cuetype",
      "stimulusintensity"
    )
  )
  sig_df = sig_df %>% separate(
    stimulusintensity,
    into = c(NA, "stimulusintensity"),
    extra = "drop",
    fill = "left"
  )
  pvc <- simple_contrasts_singletrial(sig_df)
  pvc$task[pvc$runtype == "pain"] <- "pain"
  pvc$task[pvc$runtype == "vicarious"] <- "vicarious"
  pvc$task[pvc$runtype == "cognitive"] <- "cognitive"
  pvc$task <- factor(pvc$task)


  # step 3: parameters

  taskname = "all"
  plot_keyword = "stimulusintensity"
  ggtitle_phrase =  "(3 tasks x 3 stimulus intensity)"

  pvc$task = factor(pvc$task)
  plot_keys <- list(
    sub_mean = "mean_per_sub",
    group_mean = "mean_per_sub_norm_mean",
    legend_keyword = "stimulus intensity",
    se = "se",
    subject = "sub",
    ggtitle = paste0(
      str_to_title(signature_key),
      " dot product: ",
      str_to_title(taskname),
      ' ',
      ggtitle_phrase,
      " (N = ",
      length(unique(pvc$sub)),
      ")"
    ),
    title = paste0(
      str_to_title(signature_key),
      " - ",
      str_to_title(plot_keyword)
    ),
    xlab = "",
    ylab = paste(signature_key, " (dot product)"),
    ylim = c(-250, 500)
  )

  # step 4: within between summary
  groupwise <- data.frame()
  subjectwise <- data.frame()
  summary <- summary_for_plots_PVC(
    df = pvc,
    # taskname = taskname,
    groupwise_measurevar = plot_keys$sub_mean,
    # "mean_per_sub",
    subject_keyword = plot_keys$subject,
    # "sub",
    model_iv1 =  "task",
    model_iv2 =  "stim_ordered",
    dv = signature_key #"NPS"
  )
  subjectwise <<- as.data.frame(summary[[1]])
  groupwise <<- as.data.frame(summary[[2]])
  if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
    plot_keys$color <- c("#1B9E77", "#D95F02", "#D95F02")
  } else {
    plot_keys$color <- c("#4575B4", "#FFA500", "#D73027")
  }

  # step 5: plot

  iv2 = "stim_ordered"
  iv1 = "task"
  taskname = "all"
  if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
    color <- c("#1B9E77", "#D95F02", "#D95F02")
  } else {
    color <- c("#4575B4", "#FFA500", "#D73027")
  }
  subject_mean <- "mean_per_sub"
  sub_mean = subject_mean
  group_mean <- "mean_per_sub_norm_mean"
  se <- "se"
  ylim <- c(-25, 26)
  subject <- "sub"
  ggtitle_phrase <-  "(3 tasks x 3 stimulus intensity)"
  ggtitle <-
    paste0(
      str_to_title(signature_name),
      " dot product: ",
      str_to_title(taskname),
      ' ',
      ggtitle_phrase,
      " (N = ",
      length(unique(pvc$sub)),
      ")"
    )

  title <-
    paste0(str_to_title(dv_keyword),
           " - ",
           str_to_title(plot_keys$legend_keyword))
  xlab <- ""
  plot_keyword = "stimulusintensity"
  ylab <- paste(signature_name, " (dot product)")
  plot2_savefname <- file.path(
    analysis_dir,
    paste(
      "signature_task-",
      taskname,
      "_event-",
      plot_keyword,
      "_dv-",
      signature_key,
      "_",
      as.character(Sys.Date()),
      ".png",
      sep = ""
    )
  )
  p <- plot_halfrainclouds_twofactor(
    subjectwise,
    groupwise,
    iv1,
    iv2,
    subject_mean,
    group_mean,
    se,
    subject,
    ggtitle,
    title,
    xlab,
    ylab,
    taskname,
    ylim,
    w = 10,
    h = 6,
    dv_keyword,
    color,
    plot2_savefname
  )
p
}
```

```{r echo=FALSE}
p
```



#### Contrast weight table {.unlisted .unnumbered}

```{r echo=FALSE}
tab <- matrix(c(0, .5, -.5,
                .66, -.34, -.34), ncol=3, byrow=TRUE)
colnames(tab) <- c('pain','vicarious','cognitive')
rownames(tab) <- c('task_V_gt_C','task_P_gt_VC')
kableExtra::kable_styling(
  knitr::kable(
    tab, caption = "Contrast weights", "html"),
  "striped", position = "left", font_size = 15)
```

## 2. NPS ~ paintask: 2 cue x 3 stimulus_intensity

### Q. Within pain task, Does stimulus intenisty level and cue level significantly predict NPS dotproducts? {.unlisted .unnumbered}



# 03/10/2024
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
combined_se_calc_cooksd <- data.frame()
combined_psig <- data.frame()
taskname = "pain"
ggtitle <- paste(taskname, " - NPS (degree)")
title <- paste(taskname, " - actual")
subject <- "sub"
w <- 10
h <- 6
p.sig <- df_merge[df_merge$runtype == "pain" ,]
data <- p.sig


analysis_dir <-
  file.path(main_dir,
            "analysis",
            "mixedeffect",
            analysis_folder,
            as.character(Sys.Date())) # nolint
dir.create(analysis_dir,
           showWarnings = FALSE,
           recursive = TRUE)
savedir <- analysis_dir
combined_psig <-
  rbind(combined_psig, p.sig)

# contrast code ________________________________________________________________
data$stim[data$stimulusintensity == "low_stim"] <-  -0.5 # social influence task
data$stim[data$stimulusintensity == "med_stim"] <- 0 # no influence task
data$stim[data$stimulusintensity == "high_stim"] <-  0.5 # no influence task

data$STIM <- factor(data$stimulusintensity)

# contrast code 1 linear
data$STIM_linear[data$stimulusintensity == "low_stim"] <- -0.5
data$STIM_linear[data$stimulusintensity == "med_stim"] <- 0
data$STIM_linear[data$stimulusintensity == "high_stim"] <- 0.5

# contrast code 2 quadratic
data$STIM_quadratic[data$stimulusintensity == "low_stim"] <- -0.33
data$STIM_quadratic[data$stimulusintensity == "med_stim"] <- 0.66
data$STIM_quadratic[data$stimulusintensity == "high_stim"] <- -0.33

# social cude contrast
data$CUE_high_gt_low[data$cue == "low_cue"] <-  -0.5 # social influence task
data$CUE_high_gt_low[data$cue == "high_cue"] <-  0.5 # no influence task


data$EXPECT <- data$expectrating
data$OUTCOME <- data$outcomerating

data$SES_linear[data$ses == "ses-01"] <- -0.5
data$SES_linear[data$ses == "ses-03"] <- 0
data$SES_linear[data$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
data$SES_quadratic[data$ses == "ses-01"] <- -0.33
data$SES_quadratic[data$ses == "ses-03"] <- 0.66
data$SES_quadratic[data$ses == "ses-04"] <- -0.33

stim_con1 <- "STIM_linear"
stim_con2 <- "STIM_quadratic"
iv1 <- "CUE_high_gt_low"
dv <- "NPS"
dv_keyword <- "NPS"

# filter data __________________________________________________________________
# Make sure that each condition cell has adequate amount of trials
subjects_with_inadequate_data <- data %>%
  group_by(sub, CUE_high_gt_low, SES_linear, STIM_linear) %>%
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 3) %>%
  distinct(sub) %>%
  pull(sub)
df_filter <- data %>%
  filter(!(subject %in% subjects_with_inadequate_data))
# lmer model __________________________________________________________________
model_savefname <- file.path(
  analysis_dir,
  paste(
    "lmer_task-",taskname,"_rating-",dv_keyword,"_",as.character(Sys.Date()),"_cooksd.txt",
    sep = ""
  )
)


# [ PLOT ] reordering for plots _________________________ # nolint
df_filter$cue_name[df_filter$cue == "high_cue"] <-
  "high cue"
df_filter$cue_name[df_filter$cue == "low_cue"] <-
  "low cue"

df_filter$stim_name[df_filter$stimulusintensity == "high_stim"] <-
  "high"
df_filter$stim_name[df_filter$stimulusintensity == "med_stim"] <-
  "med"
df_filter$stim_name[df_filter$stimulusintensity == "low_stim"] <-
  "low"

# DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

df_filter$stim_ordered <- factor(df_filter$stim_name,
                                   levels = c("low", "med", "high"))
df_filter$cue_ordered <- factor(df_filter$cue_name,
                                  levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"

#  [ PLOT ] calculate mean and se  _________________________
NPSstimcue_subjectwise <- meanSummary(df_filter,
                                      c(subject, model_iv1, model_iv2), dv)
NPSstimcue_groupwise <- summarySEwithin(
  data = NPSstimcue_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
NPSstimcue_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

combined_se_calc_cooksd <-
  rbind(combined_se_calc_cooksd, NPSstimcue_groupwise)
# calculate mean and se
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
subject <- "sub"
ggtitle <- paste(taskname, " - NPS Cooksd removed")
title <- paste(taskname, " - NPS")
xlab <- ""
ylab <- "NPS (degree)"
ylim <- c(-10, 60)
dv_keyword <- "NPS"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#4575B4", "#D73027")
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), "_cooksd.png",
    sep = ""
  )
)
g <- plot_halfrainclouds_twofactor(
  NPSstimcue_subjectwise,
  NPSstimcue_groupwise,
  model_iv1,
  model_iv2,
  sub_mean,
  group_mean,
  se,
  subject,
  ggtitle,
  title,
  xlab,
  ylab,
  taskname,
  ylim,
  w,
  h,
  dv_keyword,
  color,
  plot_savefname
)
g
```

### Lineplots with only low cue {.unlisted .unnumbered}

```{r echo=FALSE, warning=FALSE}
subsetNPS <- NPSstimcue_groupwise[NPSstimcue_groupwise$cue_ordered == "low cue",]
g <- plot_lineplot_twofactor_subset(subsetNPS, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#5D5C5C", "#D73027"), ggtitle = "Within pain task: NPS dotproducts as a function of stimulus intensity level and cue",
                        xlab = "Stimulus intensity", ylab = "NPS (dot product)")
g + theme(aspect.ratio=.8)
```

### Lineplots {.unlisted .unnumbered}

```{r echo=FALSE, warning=FALSE}
g <- plot_lineplot_twofactor_subset(NPSstimcue_groupwise, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#5D5C5C","high cue" = "#D73027"), ggtitle = "Within pain task: NPS dotproducts as a function of stimulus intensity level and cue",
                        xlab = "Stimulus intensity", ylab = "NPS (dot product)")
g + theme(aspect.ratio=.8)
```

### Lineplots {.unlisted .unnumbered}

```{r echo=FALSE, warning=FALSE}
g <- plot_lineplot_twofactor(NPSstimcue_groupwise,
                        iv2 = "stim_ordered", iv1 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("high" = "red",
                                  "med" = "orange",
                                  "low" = "yellow"),
                        ggtitle = "Within pain task: NPS dotproducts as a function of stimulus intensity level and cue",
                        xlab = "Stimulus intensity", ylab = "NPS (dot product)")
g + theme(aspect.ratio=.8)
```

## Linear model results (NPS ~ paintask: 2 cue x 3 stimulus_intensity)

lmer
```{r echo=TRUE, message=FALSE, warning=TRUE, paged.print=FALSE}

model.npscuestim <- lmer(NPS ~
                          CUE_high_gt_low*STIM_linear +CUE_high_gt_low * STIM_quadratic +
                          (CUE_high_gt_low+STIM|sub), data = df_filter
                    )
sjPlot::tab_model(model.npscuestim,
                  title = "Multilevel-modeling: \nlmer(NPS ~ CUE * STIM + (CUE + STIM | sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

```{r}

library(parallel)
ncores <- detectCores()
diff_optims <- allFit(model.npscuestim, maxfun = 1e5, parallel = 'multicore', ncpus = ncores)
# diff_optims <- allFit(model.full, maxfun = 1e5)
diff_optims_OK <- diff_optims[sapply(diff_optims, is, "merMod")]
lapply(diff_optims_OK, function(x) x@optinfo$conv$lme4$messages)
```

## model converge

```{r}
library(optimx)
model.npscuestim <- lmer(NPS ~
                          CUE_high_gt_low*STIM_linear +CUE_high_gt_low * STIM_quadratic +
                          (CUE_high_gt_low+STIM|sub), data = df_filter,
                         control = lmerControl(optimizer = "nlminbwrap",
                                               # optCtrl = list(method="nlminb",
                                                              # maxit = 1e9,
                                                              # maxfun = 1e9,
                                                              # maxeval = 1e7,
                                                              # xtol_abs = 1e-9,
                                                              # ftol_abs = 1e-9)
                         )
)

```

```
lmer(NPS ~
                          CUE_high_gt_low*STIM_linear +CUE_high_gt_low * STIM_quadratic +
                          (CUE_high_gt_low+STIM|sub), data = data
                    )
```

```{r echo=FALSE}
summary(model.npscuestim)
```

#### Linear model eta-squared {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.npscuestim, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
#parameters::model_parameters(model.npscuestim)
```

#### Linear model Cohen's d: NPS stimulus_intensity d = 1.16, cue d = 0.45 {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}

kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.npscuestim, data, type = "lme4"),
    "html"), "striped", position = "left", font_size = 12)
```

## 3. NPS ~ SES _ CUE _ STIM

### Q. Is the cue effect on NPS different across sessions? {.unlisted .unnumbered}

> Quick answer: Yes, the cue effect in session 1 (for high intensity group) is significantly different; whereas this different becomes non significant in session 4.
> To unpack, a participant was informed to experience a low stimulus intensity, when in fact they were delivered a high intensity stimulus. This violation presumably leads to a higher NPS response, given that they were delivered a much painful stimulus than expected. The fact that the cue effect is almost non significant during the last session indicates that the cue effects are not just an anchoring effect.

```{r}

# code session
# contrast code 1 linear
df_filter$SES_linear[df_filter$ses == "ses-01"] <- -0.5
df_filter$SES_linear[df_filter$ses == "ses-03"] <- 0
df_filter$SES_linear[df_filter$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
df_filter$SES_quadratic[df_filter$ses == "ses-01"] <- -0.33
df_filter$SES_quadratic[df_filter$ses == "ses-03"] <- 0.66
df_filter$SES_quadratic[df_filter$ses == "ses-04"] <- -0.33

model.npsses <- lmer(NPS ~
                          CUE_high_gt_low*STIM_linear*SES_linear +
                          CUE_high_gt_low*STIM_quadratic*SES_linear +
                          CUE_high_gt_low*STIM_linear*SES_quadratic +
                          CUE_high_gt_low*STIM_quadratic*SES_quadratic +
                          (1|sub), data = df_filter
                    )
# CUE_high_gt_low+STIM+EXPECT_demean
sjPlot::tab_model(model.npsses,
                  title = "Multilevel-modeling: \nlmer(NPS ~ CUE * STIM * SES + (1| sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

#### eta squared {.unlisted .unnumbered}

```{r echo=FALSE, warning=TRUE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.npsses, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

#### Cohen's d {.unlisted .unnumbered}

```{r echo=FALSE, warning=TRUE}
kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.npsses, df_filter, type = "lme4"), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

#### Session wise plots {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

combined_se_calc_cooksd <- data.frame()
for (sesname in c("ses-01", "ses-03", "ses-04")) {
taskname = "pain"
    ggtitle <- paste(taskname, " - actual judgment (degree)")
    title <- paste(taskname, " - actual")
    subject <- "sub"
    w <- 10
    h <- 6
s1.sig <- df_merge[df_merge$runtype == "pain" & df_merge$ses == sesname,]
data <- s1.sig
    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
data$stim[data$stimulusintensity == "low_stim"] <- -0.5 # social influence task
data$stim[data$stimulusintensity == "med_stim"] <- 0 # no influence task
data$stim[data$stimulusintensity == "high_stim"] <- 0.5 # no influence task

data$STIM <- factor(data$stimulusintensity)

# contrast code 1 linear
data$STIM_linear[data$stimulusintensity == "low_stim"] <- -0.5
data$STIM_linear[data$stimulusintensity == "med_stim"] <- 0
data$STIM_linear[data$stimulusintensity == "high_stim"] <- 0.5

# contrast code 2 quadratic
data$STIM_quadratic[data$stimulusintensity == "low_stim"] <- -0.33
data$STIM_quadratic[data$stimulusintensity == "med_stim"] <- 0.66
data$STIM_quadratic[data$stimulusintensity == "high_stim"] <- -0.33

# social cude contrast
data$CUE_high_gt_low[data$cue == "low_cue"] <- -0.5 # social influence task
data$CUE_high_gt_low[data$cue == "high_cue"] <- 0.5 # no influence task


stim_con1 <- "STIM_linear"
stim_con2 <- "STIM_quadratic"
iv1 <- "CUE_high_gt_low"
dv <- "NPS"

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )


    # [ PLOT ] reordering for plots _________________________ # nolint
    data$cue_name[data$cue == "high_cue"] <- "high cue"
    data$cue_name[data$cue == "low_cue"] <- "low cue"

    data$stim_name[data$stimulusintensity == "high_stim"] <- "high"
    data$stim_name[data$stimulusintensity == "med_stim"] <- "med"
    data$stim_name[data$stimulusintensity == "low_stim"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data$stim_ordered <- factor(
        data$stim_name,
        levels = c("low", "med", "high")
    )
    data$cue_ordered <- factor(
        data$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    actual_groupwise$ses <- sesname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
   # calculate mean and se
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(str_to_title(taskname), " - NPS Cooksd removed ", sesname )
    title <- paste(str_to_title(taskname), " - cue level")
    xlab <- ""
    ylab <- "NPS (degree)"
    ylim <- c(-10,60)
    dv_keyword <- "NPS"
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_halfrainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
print(g)
}
```

#### session wise line plots {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE}
# lineplot per session

DATA = as.data.frame(combined_se_calc_cooksd)
color = c("#4C77ED", "#ED220D")
model_iv1 <- "stim_ordered"
model_iv2 <- "ses_ordered"
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "se"
dv_keyword = "actual"
p1 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-01",],
               LINEIV1, LINEIV2, MEAN, ERROR, color, ggtitle = 'ses-01',
               ylab = "NPS (dot products)" )
p2 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-03",],
               LINEIV1, LINEIV2, MEAN, ERROR, color, ggtitle = 'ses-03',
               ylab = "NPS (dot products)")
p3 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-04",],
               LINEIV1, LINEIV2, MEAN, ERROR, color,ggtitle = 'ses-04',
               ylab = "NPS (dot products)")

ggpubr::ggarrange(p1,p2,p3,ncol = 3, nrow = 1, common.legend = TRUE,legend = "bottom")
 
plot_filename = file.path(analysis_dir,
                          paste('lineplot_task-all_rating-',dv_keyword,'.png', sep = ""))
ggsave(plot_filename, width = 8, height = 4)
```

---

## 4. [INCORRECT] no cmc NPS ~ CUE _ STIM _ EXPECT

- 2 cue _ 3 stimulus_intensity _ expectation_rating

```{r echo=TRUE, warning=TRUE}

data$EXPECT <- data$expectrating
model.nps3factor <- lmer(NPS ~
                          CUE_high_gt_low*STIM_linear*EXPECT +
                           CUE_high_gt_low*STIM_quadratic*EXPECT +
                          (CUE_high_gt_low  |sub), data = data_screen
                    )
sjPlot::tab_model(model.nps3factor,
                  title = "Multilevel-modeling: \nlmer(NPS ~ CUE * STIM * EXPECTATION + (CUE + STIM + EXPECT | sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

#### eta squared {.unlisted .unnumbered}

```{r echo=FALSE, warning=TRUE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.nps3factor, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

#### Cohen's d {.unlisted .unnumbered}

```{r echo=FALSE, warning=TRUE}
kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.nps3factor, data_screen, type = "lme4"), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

---

## 6. OUTCOME ~ NPS

### Q. Do higher NPS values indicate higher outcome ratings? (Pain task only) {.unlisted .unnumbered}

> Yes, Higher NPS values are associated with higher outcome ratings. The linear relationship between NPS value and outcome ratings are stronger for conditions where cue level is congruent with stimulus intensity levels. In other words, NPS-outcome rating relationship is stringent in the low cue-low intensity group, as is the case for high cue-ghigh intensity group.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# plot parameters
iv2 = "event04_actual_angle"
iv1 = "NPS"
subject = "sub"
ylab = "Outcome rating"
xlab = "NPS" #signature_key
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
p.sig <- df_merge[df_merge$runtype == "runtype-pain",]
df_dropna <- p.sig[!is.na(p.sig[, iv1]) & !is.na(p.sig[, iv2]),]
subjectwise_2dv <- meanSummary_2continuous(df_dropna,
                                   c(subject),
                                   iv1, iv2)
subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
g <- ggplot(data = subjectwise_naomit_2dv,
            aes(x = .data[["DV1_mean_per_sub"]],
                y = .data[["DV2_mean_per_sub"]],)) +
  geom_point(size = 2,
             alpha = alpha) +

  theme(aspect.ratio = 1) +
  #scale_color_manual(values = color_scheme) +
  scale_shape_manual(values = c(16, 17)) +
  xlab(xlab) +
  ylab(ylab) +
  xlim(-10, 30) +
  ylim(0, 180) +
  ggtitle(ggtitle) +
  theme(
    axis.line = element_line(colour = "grey50"),
    panel.background = element_blank(),
    plot.subtitle = ggtext::element_textbox_simple(size = 11)
  ) +
  geom_ribbon(
    stat = "smooth",
    method = lm_method,
    se = TRUE,
    alpha = 0.1,
    aes(color = NULL)
  ) +
  geom_line(
    stat = "smooth",
    method = lm_method,
    alpha = 0.8,
    linewidth = 1.5
  )
g
```

### 6-1. outcome_rating \* cue

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
p.sig <- df_merge[df_merge$runtype == "runtype-pain",]
iv2 = "event04_actual_angle"; iv1 = "NPS"
df_dropna <-
  p.sig[!is.na(p.sig$event04_actual_angle) & !is.na(p.sig$NPS),]
total <-
  plot_twovariable(
    df_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin=0, ymax=180, xmin=-10, xmax=30,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "all stimulus intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#BBBBBB"),
    alpha = .8, fit_lm = TRUE, lm_method ="lm", identity_line = FALSE
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for NPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )
```

### 6-2. outcome_rating _ stimulus_intensity _ cue

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv2 = "event04_actual_angle"; iv1 = "NPS"
group = "cuetype"; subject = "sub"
# low stimulus intensity
df_low = df_dropna[df_dropna$stimulusintensity == "low", ]
low <-
  plot_twovariable(
    df_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=0, ymax=180, xmin=-10, xmax=30,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
df_med = df_dropna[df_dropna$stimulusintensity == "med", ]
med <-
  plot_twovariable(
    df_med, iv1, iv2,
    group = group, subject = subject,
    ymin=0, ymax=180, xmin=-10, xmax=30,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
df_high = df_dropna[df_dropna$stimulusintensity == "high", ]
high <-
  plot_twovariable(
    df_high, iv1, iv2,
    group = group, subject = subject,
    ymin=0, ymax=180, xmin=-10, xmax=30,
    ylab = "Outcome rating", xlab = signature_key,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```

### 6-3. demeaned outcome rating \* cue

```{r echo=FALSE}
remove_sub_list = c("sub-0009")
#, "sub-0117", "sub-0081", "sub-0060", "sub-0063", "sub-0074", "sub-0080", "sub-0085", "sub-0098", "sub-0118", "sub-0129")
df_merge_drop <- subset(df_merge, !(sub %in% remove_sub_list))
freq <- count(df_merge, "sub")
subset_ses <-  df_merge_drop[df_merge_drop$task == 'pain',]
p.demean <- subset_ses %>%
group_by(sub) %>%
mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
mutate(expectrating = as.numeric(event02_expect_angle)) %>%
mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
mutate(OUTCOME_demean = event04_actual_angle - avg_outcome) %>%
mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
mutate(EXPECT_demean = event02_expect_angle - avg_expect)

p.demean <- p.demean %>%
group_by(sub, ses) %>%
mutate(NPS = as.numeric(NPS)) %>%
mutate(avg_NPS = mean(NPS, na.rm = TRUE)) %>%
mutate(NPS_demean = NPS - avg_NPS) %>%
  ungroup %>%
mutate(OUTCOME_cmc = avg_outcome - mean(avg_outcome)) %>%
mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) %>%
mutate(NPS_cmc = avg_NPS - mean(avg_NPS))
# plot parameters
iv1 = "NPS"
iv2 = "OUTCOME_demean"

subject = "sub"
ylab = "Outcome rating \n(subjectwise mean-centered)"
xlab = signature_key
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
# p.sig <- df_merge[df_merge$runtype == "runtype-pain", ]
demean_dropna <- p.demean[!is.na(p.demean[, iv1]) & !is.na(p.demean[, iv2]),]
demean_dropna$EXPECT <- demean_dropna$event02_expect_angle
total <-
  plot_twovariable(
    demean_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin=-25, ymax=25, xmin=-10, xmax=30,
    ylab,  xlab = paste(signature_key), #, "\n(subjectwise mean-centered)"),
    ggtitle = "all stimulus intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#BBBBBB"),
    alpha = .8, fit_lm = TRUE, lm_method ="lm", identity_line = FALSE
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for NPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )

```

### 6-4. demeaned outcome rating ~ demeaned NPS

```{r echo=FALSE}
remove_sub_list = c("sub-0009")
#, "sub-0117", "sub-0081", "sub-0060", "sub-0063", "sub-0074", "sub-0080", "sub-0085", "sub-0098", "sub-0118", "sub-0129")
df_merge_drop <- subset(df_merge, !(sub %in% remove_sub_list))
freq <- count(df_merge, "sub")
subset_ses <-  df_merge_drop[df_merge_drop$task == 'pain',]
p.demean <- subset_ses %>%
group_by(sub) %>%
mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
mutate(OUTCOME_demean = event04_actual_angle - avg_outcome) %>%
mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
mutate(EXPECT_demean = event02_expect_angle - avg_expect)

p.demean <- p.demean %>%
group_by(sub, ses) %>%
mutate(NPS = as.numeric(NPS)) %>%
mutate(avg_NPS = mean(NPS, na.rm = TRUE)) %>%
mutate(NPS_demean = NPS - avg_NPS) %>%
  ungroup %>%
mutate(OUTCOME_cmc = avg_outcome - mean(avg_outcome)) %>%
mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) %>%
mutate(NPS_cmc = avg_NPS - mean(avg_NPS))
# plot parameters
iv1 = "NPS_demean"
iv2 = "OUTCOME_demean"

subject = "sub"
ylab = "Outcome rating \n(subjectwise mean-centered)"
xlab = paste(signature_key, "\n(subjectwise mean-centered)")
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
# p.sig <- df_merge[df_merge$runtype == "runtype-pain", ]
demean_dropna <- p.demean[!is.na(p.demean[, iv1]) & !is.na(p.demean[, iv2]),]
demean_dropna$EXPECT <- demean_dropna$event02_expect_angle
total <-
  plot_twovariable(
    demean_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin=-25, ymax=25, xmin=-5, xmax=5,
    ylab,  xlab = paste(signature_key), #, "\n(subjectwise mean-centered)"),
    ggtitle = "all stimulus intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#BBBBBB"),
    alpha = .8, fit_lm = TRUE, lm_method ="lm", identity_line = FALSE
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for NPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )

```

### facet wrap

```{r echo=FALSE}

ggplot(demean_dropna, aes(x = NPS,
                       y = OUTCOME_demean,
                       col=cuetype,
                       shape = sub), alpha = .3, size = .3, color = 'gray') +
  geom_point(size = .1) +
  # geom_line(aes(col=cuetype)) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1, alpha = .3) +
  theme_classic() + theme(legend.position = "none")
```

```{r}
iv1 = "NPS"
iv2 = "OUTCOME_demean"
subject = "sub"
ggplot(aes(x=iv1, y=iv2, group = "sub"), data=demean_dropna) +
  geom_smooth(method='lm', se=F, size=0.75) +
  geom_point(size=0.1) +
  facet_wrap(~sub) +
  theme(legend.position='none') +
  xlab("relDuration")
```

### 6-4. demeaned_outcome_rating _ stimulus_intensity _ cue

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv2 = "OUTCOME_demean"; iv1 = "NPS" # "NPS"
ylab = "Outcome rating \n(subjectwise mean-centered)"
xlab =  paste(signature_key)
group = "cuetype"; subject = "sub"
# low stimulus intensity
demean_low = demean_dropna[demean_dropna$stimulusintensity == "low", ]
low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=-50, ymax=50, xmin=-10, xmax=30,
    ylab = ylab, xlab =  xlab,
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimulusintensity == "med", ]
med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=-50, ymax=50, xmin=-10, xmax=30,
    ylab = ylab, xlab =  xlab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimulusintensity == "high", ]
high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=-50, ymax=50, xmin=-10, xmax=30,
    ylab = ylab, xlab =  xlab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```

#### Is 6-4 this statistically significant? (without CMC subjectwise mean) {.unlisted .unnumbered}

```{r echo=TRUE, message=FALSE, warning=TRUE, paged.print=FALSE}
# organize variable names
# NPS_demean vs. NPS
model.npsoutcome <- lmer(OUTCOME_demean ~ CUE_high_gt_low*STIM_linear*NPS + CUE_high_gt_low*STIM_quadratic*NPS + (CUE_high_gt_low+STIM+NPS|sub), data = demean_dropna)
sjPlot::tab_model(model.npsoutcome,
                  title = "Multilevel-modeling: \nlmer(OUTCOME_demean ~ CUE * STIM * NPS + (CUE * STIM *NPS | sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

### 6-5. OUTCOMEdemean ~ NPSdemean

```{r echo=FALSE}
remove_sub_list = c("sub-0009")
#, "sub-0117", "sub-0081", "sub-0060", "sub-0063", "sub-0074", "sub-0080", "sub-0085", "sub-0098", "sub-0118", "sub-0129")
df_merge_drop <- subset(df_merge, !(sub %in% remove_sub_list))
freq <- count(df_merge, "sub")
subset_ses <-  df_merge_drop[df_merge_drop$task == 'pain',]
p.demean <- subset_ses %>%
group_by(sub) %>%
mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
mutate(OUTCOME_demean = event04_actual_angle - avg_outcome) %>%
mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
mutate(EXPECT_demean = event02_expect_angle - avg_expect)

p.demean <- p.demean %>%
group_by(sub, ses) %>%
mutate(NPS = as.numeric(NPS)) %>%
mutate(avg_NPS = mean(NPS, na.rm = TRUE)) %>%
mutate(NPS_demean = NPS - avg_NPS) %>%
  ungroup %>%
mutate(OUTCOME_cmc = avg_outcome - mean(avg_outcome)) %>%
mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) %>%
mutate(NPS_cmc = avg_NPS - mean(avg_NPS))
# plot parameters
iv1 = "NPS_demean"
iv2 = "OUTCOME_demean"

subject = "sub"
ylab = "Outcome rating \n(subjectwise mean-centered)"
xlab = paste(signature_key, "\n(subjectwise mean-centered)")
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
# p.sig <- df_merge[df_merge$runtype == "runtype-pain", ]
demean_dropna <- p.demean[!is.na(p.demean[, iv1]) & !is.na(p.demean[, iv2]),]
demean_dropna$EXPECT <- demean_dropna$event02_expect_angle
total <-
  plot_twovariable(
    demean_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin=-25, ymax=25, xmin=-5, xmax=5,
    ylab,  xlab = xlab, #, "\n(subjectwise mean-centered)"),
    ggtitle = "all stimulus intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#BBBBBB"),
    alpha = .8, fit_lm = TRUE, lm_method ="lm", identity_line = FALSE
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for NPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )

```

### 6-6. demeaned_outcome_rating ~ stimulus_intensity _ cue _ NPS demean

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv2 ="event04_actual_angle" #"OUTCOME_demean";
iv1 = "NPS_demean" # "NPS"
ylab = "Outcome rating" # \n(subjectwise mean-centered)"
xlab =  "NPS \n(subjectwise mean-centered)"
group = "cuetype"; subject = "sub"
# low stimulus intensity
yminval=0; ymaxval=180; xminval=-25; xmaxval=25;
ymin=yminval; ymax=ymaxval; xmin=xminval; xmax=xmaxval;

demean_low = demean_dropna[demean_dropna$stimulusintensity == "low", ]
low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=yminval, ymax=ymaxval, xmin=xminval, xmax=xmaxval,
    ylab = ylab, xlab =  xlab,
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimulusintensity == "med", ]
med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=yminval, ymax=ymaxval, xmin=xminval, xmax=xmaxval,
    ylab = ylab, xlab =  xlab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimulusintensity == "high", ]
high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=yminval, ymax=ymaxval, xmin=xminval, xmax=xmaxval,
    ylab = ylab, xlab =  xlab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```

---

## 7. NPS ~ expectation_rating

### Q. What is the relationship betweeen expectation ratings & NPS? (Pain task only) {.unlisted .unnumbered}

Do we see a linear effect between expectation rating and NPS dot products? Also, does this effect differ as a function of cue and stimulus intensity ratings, as is the case for behavioral ratings?

> Quick answer: Yes, expectation ratings predict NPS dotproducts; Also, there tends to be a different relationship depending on cues, just by looking at the figures, although this needs to be tested statistically.

### 7-1. [ correct ] NPS ~ demeaned_expect \* cue {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
remove_sub_list = c("sub-0009") # "sub-0117", "sub-0081", "sub-0060", "sub-0063", "sub-0074", "sub-0085", "sub-0098", "sub-0118")
df_merge_drop <- subset(df_merge, !(sub %in% remove_sub_list))
subset_ses <-  df_merge_drop[df_merge_drop$task == 'pain',]
p.demean <- subset_ses %>%
  group_by(sub) %>%
  mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
  mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
  mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
  mutate(OUTCOME_demean = event04_actual_angle - avg_outcome) %>%
  mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
  mutate(EXPECT_demean = event02_expect_angle - avg_expect) %>%
  group_by(sub, ses) %>%
  mutate(NPS = as.numeric(NPS)) %>%
  mutate(avg_NPS = mean(NPS, na.rm = TRUE)) %>%
  mutate(NPS_demean = NPS - avg_NPS) %>%
  ungroup %>%
  mutate(OUTCOME_cmc = avg_outcome - mean(avg_outcome)) %>%
  mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) %>%
  mutate(NPS_cmc = avg_NPS - mean(avg_NPS))

# plot parameters

iv1 = "EXPECT_demean"
iv2 = "NPS" # NPS_demean
subject = "sub"
xlab = "Expectation rating \n(subjectwise mean-centered)"
ylab = paste(signature_key) #, " \n(mean-centered)")
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
demean_dropna <- p.demean[!is.na(p.demean[, iv1]) & !is.na(p.demean[, iv2]),]

total <-
  plot_twovariable(
    demean_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin=-10, ymax=10, xmin=-40, xmax=40,
    xlab ,ylab,
    ggtitle = "all stimulus intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#BBBBBB"),
    alpha = .8, fit_lm = TRUE, lm_method ="lm", identity_line = FALSE
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for NPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )

```

```{r}
# plot parameters

iv1 = "EXPECT_demean"
iv2 = "NPS_demean" # NPS_demean
subject = "sub"
xlab = "Expectation rating \n(subjectwise mean-centered)"
ylab = paste(signature_key,  "\n(mean-centered)")
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
demean_dropna <- p.demean[!is.na(p.demean[, iv1]) & !is.na(p.demean[, iv2]),]

total <-
  plot_twovariable(
    demean_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin=-10, ymax=10, xmin=-40, xmax=40,
    xlab ,ylab,
    ggtitle = "all stimulus intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#BBBBBB"),
    alpha = .8, fit_lm = TRUE, lm_method ="lm", identity_line = FALSE
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for NPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )

```

```{r echo=FALSE}
ggplot(demean_dropna, aes(x = event02_expect_angle,
                       y = event04_actual_angle,
                       col = cuetype,
                       shape = sub), size = .3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .3) +
  theme_classic() + theme(legend.position = "none")
```

```{r echo=FALSE}
ggplot(demean_dropna, aes(x = event02_expect_angle,
                       y = event04_actual_angle,
                       col = stim_ordered,
                       shape = sub), size = .3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  theme_classic() + theme(legend.position = "none")
```

```{r echo=FALSE}
ggplot(demean_dropna, aes(x = EXPECT_demean,
                       y = OUTCOME_demean,
                       col = stim_ordered,
                       shape = sub), size = .3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1, alpha = .2) +
  theme_classic() + theme(legend.position = "none")
```

```{r echo=FALSE}
ggplot(demean_dropna[demean_dropna$stimulusintensity == 'low',],
       aes(x = NPS_demean,
                       y = OUTCOME_demean,
                       col = cuetype,
                       shape = sub), size = .3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1, alpha = .2) +
  theme_classic() + theme(legend.position = "none")

ggplot(demean_dropna[demean_dropna$stimulusintensity == 'high',],
       aes(x = NPS_demean,
                       y = OUTCOME_demean,
                       col = cuetype,
                       shape = sub), size = 3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1, alpha = .2) +
  theme_classic() + theme(legend.position = "none")
```

```{r echo=FALSE}
ggplot(demean_dropna, aes(x = event02_expect_angle,
                       y = NPS,
                       col = cuetype,
                       shape = sub), size = .3, color = 'gray') +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .3) +
  theme_classic() + theme(legend.position = "none")
```

```{r echo=FALSE}
ggplot(demean_dropna, aes(x = STIM_linear,
                       y = NPS,
                       col = cuetype,
                       shape = sub), size = .3, color = c('red', 'gray')) +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  theme_classic() + theme(legend.position = "none")
```

```{r echo=FALSE}
ggplot(demean_dropna, aes(x = NPS_demean,
                       y = OUTCOME_demean,
                       col = cuetype,
                       shape = sub), size = .3, col = c('red', 'gray')) +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  theme_classic() + theme(legend.position = "none")

```

```{r echo=FALSE}
ggplot(demean_dropna[demean_dropna$stimulusintensity == "low", ], aes(x = NPS_demean,
                       y = OUTCOME_demean,
                       col = cuetype,
                       shape = sub), size = .3, col = c('red', 'gray')) +
  geom_point(size = .1) +
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  theme_classic() + theme(legend.position = "none")

```

### 7-1-2. NPS ~ EXPECT \* cue {.unlisted .unnumbered} + CMC

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
# plot parameters

iv1 = "event02_expect_angle"
iv2 = "NPS" # NPS_demean
subject = "sub"
xlab = "Expectation rating"
ylab = paste(signature_key) #, " \n(mean-centered)")
ggtitle = "All stimulus intensity"
alpha = 0.8
lm_method = "lm"
demean_dropna <- p.demean[!is.na(p.demean[, iv1]) & !is.na(p.demean[, iv2]),]

total <-
  plot_twovariable(
    demean_dropna, iv1, iv2,
    group = "cuetype", subject = "sub",
    ymin=-5, ymax=10, xmin=0, xmax=180,
    xlab ,ylab,
    ggtitle = "all stimulus intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#BBBBBB"),
    alpha = .8, fit_lm = TRUE, lm_method ="lm", identity_line = FALSE
  )
total + labs(title =paste0("task-",taskname, "- What is the pattern for NPS pos dotproduct and expect ratings? \nHow is does this pattern differ depending on high vs low cues?\n\n")
          )

```

### 7-2. [ correct ] NPS ~ demeaned_expect _ cue _ stim {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv1 = "EXPECT_demean"; iv2 = "NPS" # "NPS_demean"
group = "cuetype"; subject = "sub"
xlab = "Expectation rating \n(subjectwise mean-centered)"
ylab = paste(signature_key)
# low stimulus intensity
demean_low = demean_dropna[demean_dropna$stimulusintensity == "low", ]
low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimulusintensity == "med", ]
med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimulusintensity == "high", ]
high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```

### 7-3. NPS_demean ~ demeaned_expect _ cue _ stim {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
iv1 = "EXPECT_demean"; iv2 = "NPS_demean" # "NPS_demean"
group = "cuetype"; subject = "sub"
xlab = "Expectation rating \n(subjectwise mean-centered)"
ylab = paste(signature_key, "\n(subjectwise mean-centered)")
# low stimulus intensity
demean_low = demean_dropna[demean_dropna$stimulusintensity == "low", ]
low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimulusintensity == "med", ]
med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimulusintensity == "high", ]
high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(low, med, high, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots, top = text_grob(paste(str_to_title(taskname), "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"), color = "black", face = "bold", size = 12))
plots_title
```

### 7-3. [ correct ] NPS ~ EXPECTdemean x CUE x STIM + CMC {.unlisted .unnumbered}

                    )

- https://stats.stackexchange.com/questions/365466/significance-of-slope-different-than-zero-in-triple-interaction-with-factors
- https://stats.stackexchange.com/questions/586748/calculating-trends-with-emtrends-for-three-way-interaction-model-results-in-sa
- emtrends(model.npsexpectdemean, var = 'EXPECT_demean', lmer.df = "asymptotic")

CUE*SES*EXPECT

```{r echo=TRUE, message=FALSE, warning=TRUE, paged.print=FALSE}
model.npsexpectdemean <- lmer(NPS ~
                          CUE_high_gt_low*EXPECT_demean*STIM_linear*factor(ses)  +
                            CUE_high_gt_low*EXPECT_demean*STIM_quadratic*factor(ses) +  EXPECT_cmc +
                          (1|sub), data = demean_dropna
                    )
# model.npsexpectdemean <- lmer(NPS ~
#                           CUE_high_gt_low*EXPECT_demean*STIM*factor(ses)  +
#                             +  EXPECT_cmc +
#                           (1|sub), data = demean_dropna
#                     )
Anova(model.npsexpectdemean)
# CUE_high_gt_low+STIM+EXPECT_demean
sjPlot::tab_model(model.npsexpectdemean,
                  title = "Multilevel-modeling: \nlmer(NPS ~ CUE * STIM * EXPECT_demean + (1| sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

```{r}
compute_icc <- function(lmer_object){
  var_dat <- lmer_object %>% VarCorr %>% as.data.frame
  icc <- var_dat$vcov[1]/(var_dat$vcov[1]+var_dat$vcov[2])
  return(icc)
}
```

### ICC

```{r}
compute_icc(model.npsexpectdemean)
```

> The ICC of the dependent variable is .30 and thus very close to the value that we wanted to simulate. It means that about 30% of the variance in this variable is explainable by interindividual differences (i.e., person-related characteristics). This also means that a larger part of the variance is potentially explainable by situational characteristics (e.g., by other variables measured on level 1).

```{r}
emtrends(model.npsexpectdemean, var = 'EXPECT_demean', lmer.df = "asymptotic")
```

#### eta squared {.unlisted .unnumbered}

```{r echo=FALSE, warning=TRUE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.npsexpectdemean, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

#### Cohen's d {.unlisted .unnumbered}

```{r echo=FALSE, warning=TRUE}
kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.npsexpectdemean, demean_dropna, type = "lme4"), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

## 7-3 simple slopes when STIM == 'high', EXPECT_demean slope difference between high vs. low cue {.unlisted .unnumbered}

```{r}
interactions::sim_slopes(model=model.npsexpectdemean, pred=EXPECT_demean, modx=CUE_high_gt_low, mod2 =STIM_linear, mod2.values = 0.5, centered = 'all', data = demean_dropna)

```

#### emtrneds {.unlisted .unnumbered}

```{r}
emt.t <- emtrends(model.npsexpectdemean, ~ STIM_linear | CUE_high_gt_low,
         var = "EXPECT_demean",
         # nuisance = c("EXPECT_cmc"),
         at = list(STIM_linear=c(0.5, 0, -0.5)),
         lmer.df = "asymp")
pairs(emt.t, simple = "each")
# contrast(emt.t, "revpairwise")
```

```{r eval=FALSE, include=FALSE}
library(reghelper)
simple_slopes(model.npsexpectdemean,
        levels=list(STIM_linear=c(0.5, 'sstest'),
        CUE_high_gt_low=c(0.5,-0.5, 'sstest')))  # test at specific levels
```

## 8. NPS and session effects

```{r}
# code session
# contrast code 1 linear
demean_dropna$SES_linear[demean_dropna$ses == "ses-01"] <- -0.5
demean_dropna$SES_linear[demean_dropna$ses == "ses-03"] <- 0
demean_dropna$SES_linear[demean_dropna$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
demean_dropna$SES_quadratic[demean_dropna$ses == "ses-01"] <- -0.33
demean_dropna$SES_quadratic[demean_dropna$ses == "ses-03"] <- 0.66
demean_dropna$SES_quadratic[demean_dropna$ses == "ses-04"] <- -0.33

```

#### 8-1. [ correct ] NPS ~ EXPECT_demean _ CUE _ STIM + CMC (Session as covariate)

```{r echo=TRUE, message=TRUE, warning=TRUE, paged.print=FALSE}

model.npsexpectdemean.sescontrol <- lmer(NPS ~
                          CUE_high_gt_low*STIM_linear*EXPECT_demean +
                          CUE_high_gt_low*STIM_quadratic*EXPECT_demean +
                          # CUE_high_gt_low*STIM_linear*EXPECT_demean +
                          # CUE_high_gt_low*STIM_quadratic*EXPECT_demean +
                          EXPECT_cmc +
                          ses +
                          (CUE_high_gt_low|sub), data = demean_dropna
                    )
# CUE_high_gt_low+STIM+EXPECT_demean
sjPlot::tab_model(model.npsexpectdemean.sescontrol,
                  title = "Multilevel-modeling: \nlmer(NPS ~ CUE * STIM * EXPECT_demean + SES + (CUE + EXPECT| sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

#### 8-2. [ correct ] NPS ~ EXPECT_demean _ CUE _ STIM \* SES + CMC (Session as interaction)

```{r echo=TRUE, message=TRUE, warning=TRUE, paged.print=FALSE}

model.npsexpectdemean.ses <- lmer(NPS ~
                          CUE_high_gt_low*STIM_linear*EXPECT_demean*SES_linear +
                          CUE_high_gt_low*STIM_quadratic*EXPECT_demean*SES_linear +
                          CUE_high_gt_low*STIM_linear*EXPECT_demean*SES_quadratic +
                          CUE_high_gt_low*STIM_quadratic*EXPECT_demean*SES_quadratic +
                          EXPECT_cmc +
                          (CUE_high_gt_low|sub) + (1|ses), data = demean_dropna
                    )
# CUE_high_gt_low+STIM+EXPECT_demean
sjPlot::tab_model(model.npsexpectdemean.ses,
                  title = "Multilevel-modeling: \nlmer(NPS ~ CUE * STIM * EXPECT_demean * SES + (CUE + EXPECT| sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

## 9. plotly 3 factors

```{r echo=FALSE}
# paindf <- data_screen[data_screen$runtype == "runtype-pain",]
remove_sub_list = c("sub-0009") # "sub-0117", "sub-0081", "sub-0060", "sub-0063", "sub-0074", "sub-0085", "sub-0098", "sub-0118")
df_merge_drop <- subset(df_merge, !(sub %in% remove_sub_list))
subset_ses <-  df_merge_drop[df_merge_drop$task == 'pain',]
p.demean <- subset_ses %>%
  group_by(sub) %>%
  mutate(event04_actual_angle = as.numeric(event04_actual_angle)) %>%
  mutate(event02_expect_angle = as.numeric(event02_expect_angle)) %>%
  mutate(avg_outcome = mean(event04_actual_angle, na.rm = TRUE)) %>%
  mutate(OUTCOME_demean = event04_actual_angle - avg_outcome) %>%
  mutate(avg_expect = mean(event02_expect_angle, na.rm = TRUE)) %>%
  mutate(EXPECT_demean = event02_expect_angle - avg_expect) %>%
  group_by(sub, ses) %>%
  mutate(NPS = as.numeric(NPS)) %>%
  mutate(avg_NPS = mean(NPS, na.rm = TRUE)) %>%
  mutate(NPS_demean = NPS - avg_NPS) %>%
  ungroup %>%
  mutate(OUTCOME_cmc = avg_outcome - mean(avg_outcome)) %>%
  mutate(EXPECT_cmc = avg_expect - mean(avg_expect)) %>%
  mutate(NPS_cmc = avg_NPS - mean(avg_NPS))

plotly_subjectwise <- meanSummary(
        p.demean,
        c("sub","ses",  "cuetype", "stimulusintensity", "EXPECT_demean"), c("NPS")
    )
```

```{r}
library(plotly)
# lmer(NPS ~ CUE_high_gt_low*STIM_linear*event02_expect_angle + CUE_high_gt_low*STIM_quadratic*event02_expect_angle + (CUE_high_gt_low|sub), data = data_screen)
ses1 = p.demean[p.demean$ses == "ses-01",]
x <- seq_len(nrow(volcano)) + 100
y <- seq_len(ncol(volcano)) + 500
fig <- plot_ly(ses1, x = ~cuetype, y = ~EXPECT_demean, z = ~NPS) %>% #colors = c('#BF382A','yellow', '#0C4B8E'))
  # group_by(STIM) %>%
  group_by(STIM_linear) %>%
  # add_markers(color = ~STIM_linear) %>%
  # group_by(cuetype) %>%
  add_lines(color = ~STIM_linear)

fig <- fig %>% layout(scene = list
                      (
                        xaxis = list(title = 'Cue'),
                        zaxis = list(title = 'NPS'),
                        yaxis = list(title = 'Expectation rating')
                        ))

fig
```

```{r}
library(plotly)
ses1.Lh = p.demean[p.demean$ses == "ses-01" & p.demean$STIM == "low" & p.demean$cue_name == "high",]
ses1.Lph <- plot_ly(ses1.Lh,x = ~EXPECT_demean, y = ~NPS)
ses1.Mh = p.demean[p.demean$ses == "ses-01" & p.demean$STIM == "med" & p.demean$cue_name == "high",]
ses1.Mph <- plot_ly(ses1.Mh,x = ~EXPECT_demean, y = ~NPS)
ses1.Hh = p.demean[p.demean$ses == "ses-01" & p.demean$STIM == "high" & p.demean$cue_name == "high",]
ses1.Hph <- plot_ly(ses1.Hh,x = ~EXPECT_demean, y = ~NPS )

ses1.Ll = p.demean[p.demean$ses == "ses-01" & p.demean$STIM == "low" & p.demean$cue_name == "low",]
ses1.Lpl <- plot_ly(ses1.Ll,x = ~EXPECT_demean, y = ~NPS)
ses1.Ml = p.demean[p.demean$ses == "ses-01" & p.demean$STIM == "med" & p.demean$cue_name == "low",]
ses1.Mpl <- plot_ly(ses1.Ml,x = ~EXPECT_demean, y = ~NPS)
ses1.Hl = p.demean[p.demean$ses == "ses-01" & p.demean$STIM == "high"& p.demean$cue_name == "low",]
ses1.Hpl <- plot_ly(ses1.Hl,x = ~EXPECT_demean, y = ~NPS )

subplot(
  add_histogram2d(ses1.Lph, zsmooth = "best") %>%
    colorbar() %>%
    layout(xaxis = list(title = "low_stim high_cue")),
  add_histogram2d(ses1.Mph, zsmooth = "best") %>%
    colorbar() %>%
    layout(xaxis = list(title = "med_stim high_cue")),
  add_histogram2d(ses1.Hph, zsmooth = "best") %>%
    colorbar() %>%
    layout(xaxis = list(title = "high_stim high_cue")),

  add_histogram2d(ses1.Lpl, zsmooth = "best") %>%
    colorbar() %>%
    layout(xaxis = list(title = "low_stim")),
  add_histogram2d(ses1.Mpl, zsmooth = "best") %>%
    colorbar() %>%
    layout(xaxis = list(title = "med_stim")),
  add_histogram2d(ses1.Hpl, zsmooth = "best") %>%
    colorbar() %>%
    layout(xaxis = list(title = "high_stim")),
  shareY = TRUE, titleX = TRUE
)
```

```{r}
# save tsv
test = ses1[, c("sub", "cuetype", "stimulusintensity", "EXPECT_demean", "NPS")]

write.table(test, file=file.path(analysis_dir, "test.tsv"), quote=FALSE, sep='\t', row.names = FALSE)
```

#### 3x3 plots EXPECT_demean

```{r}
iv1 = "EXPECT_demean"; iv2 = "NPS" # "NPS_demean"
group = "cuetype"; subject = "sub"
xlab = "Expectation rating \n(subjectwise mean-centered)"
ylab = paste(signature_key)
remove_xy <- theme(
  axis.text.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.x = element_blank(),
    axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank(),
  plot.margin = unit(c(0,0.2,0,1), 'lines')
)

# low stimulus intensity
demean_low = demean_dropna[demean_dropna$stimulusintensity == "low" & demean_dropna$ses == "ses-01", ]
ses01low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimulusintensity == "med" & demean_dropna$ses == "ses-01", ]
ses01med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimulusintensity == "high" & demean_dropna$ses == "ses-01", ]
ses01high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
# ses 03 ________________________
demean_low = demean_dropna[demean_dropna$stimulusintensity == "low" & demean_dropna$ses == "ses-03", ]
ses03low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimulusintensity == "med" & demean_dropna$ses == "ses-03", ]
ses03med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimulusintensity == "high" & demean_dropna$ses == "ses-03", ]
ses03high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# ses 04 ________________________
demean_low = demean_dropna[demean_dropna$stimulusintensity == "low" & demean_dropna$ses == "ses-04", ]
ses04low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimulusintensity == "med" & demean_dropna$ses == "ses-04", ]
ses04med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimulusintensity == "high" & demean_dropna$ses == "ses-04", ]
ses04high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=-20, ymax=20, xmin=-50, xmax=50,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(ses01low+remove_xy, ses01med+remove_xy, ses01high+remove_xy,
                           ses03low+remove_xy, ses03med+remove_xy, ses03high+remove_xy,
                           ses04low+remove_xy, ses04med+remove_xy, ses04high+remove_xy,
                           ncol = 3, nrow = 3, common.legend = TRUE, legend = "bottom",
                           widths = c(1, 1, 1))

plots_title <- annotate_figure(plots,
                               top =
                                 text_grob(paste(str_to_title(taskname),
                                                 "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"),
                                           color = "black", face = "bold", size = 12),
                               left = text_grob("NPS (dot product)", rot = 90, vjust = 1),
                               bottom = text_grob("Expectation rating\n(subjectwise mean-centering)")
                               )
plots_title

```

```{r}

fig.height = 50
fig.width = 10
ggplot(aes(x=EXPECT_demean, y=NPS, color = CUE_high_gt_low, shape =), data=demean_dropna) +
  geom_smooth(method='lm', se=F, size=0.75) +
  geom_point(size=0.1) +
    # geom_abline(intercept = 0, slope = 1, color="green",
    #              linetype="dashed", size=0.5) +
  facet_wrap(~ses) +
  theme(legend.position='none') +
  xlim(-50,50) + ylim(-50,50) +
  xlab("raw data from each participant: n-1 lagged outcome angle") +
  ylab("n current expectation rating")

```

#### NPS ~ EXPECT_demean _ STIM _ CUE

```{r}
iv1 = "EXPECT_demean" #"event02_expect_angle";
iv2 = "NPS" # "NPS_demean"
group = "cuetype"; subject = "sub"
xlab = "Expectation rating \n(subjectwise mean-centered)"
ylab = paste(signature_key)
remove_xy <- theme(
  axis.text.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.x = element_blank(),
    axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank(),
  plot.margin = unit(c(0,0.2,0,1), 'lines')
)

remove_x <- theme(
  axis.text.x = element_blank(),
  axis.ticks.x = element_blank(),
  axis.title.x = element_blank(),
  plot.margin = unit(c(0,0.2,0,1), 'lines')
)

remove_y <- theme(
  axis.text.y = element_blank(),
  axis.ticks.y = element_blank(),
  axis.title.y = element_blank(),
  plot.margin = unit(c(0,0.2,0,1), 'lines')
)

xmin_val = -60
xmax_val = 45
ymin_val = -20
ymax_val = 60
# low stimulus intensity
demean_low = demean_dropna[demean_dropna$stimulusintensity == "low" & demean_dropna$ses == "ses-01", ]
ses01low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimulusintensity == "med" & demean_dropna$ses == "ses-01", ]
ses01med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimulusintensity == "high" & demean_dropna$ses == "ses-01", ]
ses01high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
# ses 03 ________________________
demean_low = demean_dropna[demean_dropna$stimulusintensity == "low" & demean_dropna$ses == "ses-03", ]
ses03low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimulusintensity == "med" & demean_dropna$ses == "ses-03", ]
ses03med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimulusintensity == "high" & demean_dropna$ses == "ses-03", ]
ses03high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# ses 04 ________________________
demean_low = demean_dropna[demean_dropna$stimulusintensity == "low" & demean_dropna$ses == "ses-04", ]
ses04low <-
  plot_twovariable(
    demean_low, iv1 , iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    #, " \n(mean-centered)"),
    ggtitle = "Low intensity",
    color_scheme = c("cuetype-high" ="#FF8800","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# med stimulus intensity
demean_med = demean_dropna[demean_dropna$stimulusintensity == "med" & demean_dropna$ses == "ses-04", ]
ses04med <-
  plot_twovariable(
    demean_med, iv1, iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    ggtitle = "Medium intensity",
    color_scheme = c("cuetype-high" ="#DB6000","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )

# high stimulus intensity
demean_high = demean_dropna[demean_dropna$stimulusintensity == "high" & demean_dropna$ses == "ses-04", ]
ses04high <-
  plot_twovariable(
    demean_high, iv1, iv2,
    group = group, subject = subject,
    ymin=ymin_val, ymax=ymax_val, xmin=xmin_val, xmax=xmax_val,
    xlab = xlab, ylab = ylab,
    ggtitle = "High intensity",
    color_scheme = c("cuetype-high" ="#941100","cuetype-low" =  "#5D5C5C"),
    alpha = .5, fit_lm = TRUE, lm_method = "lm", identity_line = FALSE
  )
plots <- ggpubr::ggarrange(ses01low+remove_x, ses01med+remove_xy, ses01high+remove_xy,
                           ses03low+remove_x, ses03med+remove_xy, ses03high+remove_xy,
                           ses04low, ses04med+remove_y, ses04high+remove_y,
                           ncol = 3, nrow = 3, common.legend = TRUE, legend = "bottom",
                           widths = c(1, 1, 1))

plots_title <- annotate_figure(plots,
                               top =
                                 text_grob(paste(str_to_title(taskname),
                                                 "\n NPS/Outcome linear relationship does not differ as a function of stimulus intensity and cue"),
                                           color = "black", face = "bold", size = 12),
                               left = text_grob("NPS (dot product)", rot = 90, vjust = 1),
                               bottom = text_grob("Expectation rating\n(subjectwise mean-centering)")
                               )
plots_title

```

## 9. NPS ~ trial order

```{r}
pvc$run_num = as.numeric(as.factor(pvc$run))
pvc <- pvc %>%
  dplyr::group_by(sub, ses, runtype) %>%
  dplyr::mutate(mean_run = mean(run_num))
# compared to mean_run, is the run_num smaller or larger?
pvc$formerlatter_run <-
  ifelse(pvc$mean_run >= pvc$run_num , "former", "latter")
pvc$ses_run <-
  interaction(pvc$formerlatter_run, pvc$ses, sep = "_")
NPStrialorder = pvc
```

```{r}
NPStrialorder$ses_run <-
  interaction(NPStrialorder$formerlatter_run, NPStrialorder$ses, sep = "_")

NPStrialorder$ses_run_trial <-
  interaction(NPStrialorder$trial,NPStrialorder$formerlatter_run, NPStrialorder$ses, sep = "_")

NPStrialorder$ses_run_num <- as.numeric(as.factor(NPStrialorder$ses_run))
NPStrialorder$ses_run_trial_num <- as.numeric(as.factor(NPStrialorder$ses_run_trial))
```

```{r}
data.frame(table(NPStrialorder$ses_run_trial_num ))
```

### trial order \* cue

```{r}
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    dv <- "NPS"
    subject = "ses_run_trial_num"
    trialorder_subjectwise_p2 <- meanSummary(
        NPStrialorder[NPStrialorder$runtype == "runtype-pain",],
        c(  model_iv2, "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
trialorder_subjectwise_p2


iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_subjectwise_p2,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_subjectwise_p2,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      color = cue_ordered,
      # linetype = as.factor(stim_ordered)
      )) +
    geom_point(
    data = trialorder_subjectwise_p2,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # linetype = as.factor(stim_ordered),
      color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      colour = cue_ordered,
      # linetype = as.factor(stim_ordered),
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPS") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(0,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g
```

### trial order only

```{r}
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    # rating <- "NPS"
    dv <- "NPS"
    subject = "ses_run_trial_num"
    trialorder_summary <- meanSummary(
        NPStrialorder[NPStrialorder$runtype == "runtype-pain",],
        c( "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
trialorder_subjectwise_p2


iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_summary,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_summary,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # color = cue_ordered,
      # linetype = as.factor(stim_ordered)
      )) +
    geom_point(
    data = trialorder_summary,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # linetype = as.factor(stim_ordered),
      # color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_summary,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # colour = cue_ordered,
      # linetype = as.factor(stim_ordered),
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPS") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(0,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g
```

```{r}
model.trial = lm(NPS ~ trial*cuetype, data = NPStrialorder[NPStrialorder$runtype == "runtype-pain",], )
Anova(model.trial, type = "III")
summary(model.trial)
```

## vicarious

### trial order \* cue

```{r}
taskname = "vicarious"
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    dv <- "NPS"
    subject = "ses_run_trial_num"
    trialorder_subjectwise_p2 <- meanSummary(
        NPStrialorder[NPStrialorder$runtype == "runtype-vicarious",],
        c(  model_iv2, "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
trialorder_subjectwise_p2


iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_subjectwise_p2,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_subjectwise_p2,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      color = cue_ordered,
      # linetype = as.factor(stim_ordered)
      )) +
    geom_point(
    data = trialorder_subjectwise_p2,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # linetype = as.factor(stim_ordered),
      color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      colour = cue_ordered,
      # linetype = as.factor(stim_ordered),
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPS") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(-5,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g
```

### trial order only

```{r}
taskname = "vicarious"
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    # rating <- "NPS"
    dv <- "NPS"
    subject = "ses_run_trial_num"
    trialorder_summary <- meanSummary(
        NPStrialorder[NPStrialorder$runtype == "runtype-vicarious",],
        c( "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
trialorder_subjectwise_p2


iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_summary,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_summary,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # color = cue_ordered,
      # linetype = as.factor(stim_ordered)
      )) +
    geom_point(
    data = trialorder_summary,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # linetype = as.factor(stim_ordered),
      # color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_summary,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # colour = cue_ordered,
      # linetype = as.factor(stim_ordered),
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPS") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(-5,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g
```

## cognitive

### trial order \* cue

```{r}
taskname = "cognitive"
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    dv <- "NPS"
    subject = "ses_run_trial_num"
    trialorder_subjectwise_p2 <- meanSummary(
        NPStrialorder[NPStrialorder$runtype == "runtype-cognitive",],
        c(  model_iv2, "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
trialorder_subjectwise_p2


iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_subjectwise_p2,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_subjectwise_p2,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      color = cue_ordered,
      # linetype = as.factor(stim_ordered)
      )) +
    geom_point(
    data = trialorder_subjectwise_p2,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # linetype = as.factor(stim_ordered),
      color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_subjectwise_p2,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      colour = cue_ordered,
      # linetype = as.factor(stim_ordered),
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPS") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(-5,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g
```

### trial order only

```{r}
taskname = "cognitive"
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    # rating <- "NPS"
    dv <- "NPS"
    subject = "ses_run_trial_num"
    trialorder_summary <- meanSummary(
        NPStrialorder[NPStrialorder$runtype == "runtype-cognitive",],
        c( "ses_run_trial_num"), dv
    )
    trialorder_subjectwise_p2 <- replace(trialorder_subjectwise_p2, is.na(trialorder_subjectwise_p2), 0)
trialorder_subjectwise_p2


iv1 = "ses_run_trial_num"
iv2 = "cue_ordered"
data =
g <- ggplot(
  data = trialorder_summary,
  aes(x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # color = cue_ordered,
      # group = rating_type
      # linetype = as.factor(stim_ordered)
      )
  ) +
  geom_smooth(
    method = "loess",
    data = trialorder_summary,
    aes(
      # shape = as.character(rating_type),
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # color = cue_ordered,
      # linetype = as.factor(stim_ordered)
      )) +
    geom_point(
    data = trialorder_summary,
    aes(
      # shape = as.character(rating_type),
      x =as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # linetype = as.factor(stim_ordered),
      # color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 2.5
    ) +
  scale_shape_manual(values=c(21, 16))+

  # scale_x_continuous(breaks = seq(0, 72, by = 5)) +
  geom_errorbar(
    data = trialorder_summary,
    aes(
      x = as.numeric(ses_run_trial_num),
      y = mean_per_sub,
      # group = rating_type,
      # colour = cue_ordered,
      # linetype = as.factor(stim_ordered),
      ymin = mean_per_sub - sd/sqrt(length(unique(NPStrialorder$sub))),
      ymax = mean_per_sub + sd/sqrt(length(unique(NPStrialorder$sub)))), width = .1, size = 0.2
    ) +
  scale_color_manual(values = c("high" = "red", #"#009411",
                                "low" = "blue" #5D5C5C"
                                )) +
  xlab("No. of trials") +
  ylab("NPS") +
  labs(title = paste(taskname, "(N = ", length(unique(NPStrialorder$sub)), ")"))+
  ylim(-5,25) +
  theme_classic2() +
theme(aspect.ratio = .7) + geom_vline(xintercept = c(12,24,36,48,60), linetype="dotted",
                color = "blue", size=.1)
g
```
