# PLS ::  PLS scores ~  cue * stim {#pls}

## What is the purpose of this notebook? {.unlisted .unnumbered}

Here, we want to... {{ INSERT }} 

* Main model: `plsscores ~ cue stim` 
* Main question: With PLS, did we predict the observed scores well? 
* {{ HYPOTHESES/EXPECTED expect }}
* 
* IV: 
  - {{ FACTOR NAME }} ( {{ LEVELS}} )
* DV: {{ DV }}


### TODO: 
```
INSERT HERE
```

### References : Once note book is complete, add at the bottom of Rmd
```
INSERT HERE
```

### load libraries {.unlisted .unnumbered}
```{r message=FALSE, warning=FALSE, include=FALSE}
library(car)
library(psych)
library(cueR)
```


### display distribution of data
Let's look at the distribution of the data. X axis: Y axis: 
```{r paged.print=TRUE}
expect.fname = "/Users/h/Documents/projects_local/cue_expectancy/analysis/fmri/nilearn/pls/pls_model-expectrating.tsv"
outcome.fname = "/Users/h/Documents/projects_local/cue_expectancy/analysis/fmri/nilearn/pls/pls_model-outcomerating.tsv"

expect_df = read.csv(expect.fname, sep = '\t')
outcome_df = read.csv(outcome.fname, sep = '\t')
```


```{r}
for (taskname in c("pain")) {
  combined_data <- data.frame()
subject <- "sub"
model_iv1 <- "cuetype"
model_iv2 <- "stimulusintensity"
model_iv2 <- "runtype"
dv <- paste0(taskname,"_expect")
expect.subjectwise <- meanSummary(expect_df,
                                      c(subject, model_iv1, "runtype"), dv)
expect.groupwise <- summarySEwithin(
  data = expect.subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
expect.groupwise$data <- "observed"
dv <- paste0("pred_", taskname, "_expect")
pls.expect.subjectwise <- meanSummary(expect_df,
                                      c(subject, model_iv1, "runtype"),dv )
pls.expect.groupwisewise <- summarySEwithin(
  data = pls.expect.subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
pls.expect.groupwisewise$data <- "plsmodel"

library(ggplot2)

# Assuming pls.expect.groupwisewise and expect.groupwise are already loaded and prepared as described

# Combine the data for ease of plotting (optional, depending on your needs)
combined_data <- data.frame(
  mean_per_sub_norm_mean_x = expect.groupwise$mean_per_sub_norm_mean,  # x-axis
  mean_per_sub_norm_mean_y = pls.expect.groupwisewise$mean_per_sub_norm_mean,  # y-axis
  se_x = expect.groupwise$se,
  se_y = pls.expect.groupwisewise$se,
  cuetype = expect.groupwise$cuetype,
  runtype = expect.groupwise$runtype
)

# Plotting
g <- ggplot(combined_data, aes(x = mean_per_sub_norm_mean_x, y = mean_per_sub_norm_mean_y, color = runtype)) +
  geom_point(size=3) +
  geom_errorbarh(aes(xmin = mean_per_sub_norm_mean_x - se_x, xmax = mean_per_sub_norm_mean_x + se_x)) +
  geom_errorbar(aes(ymin = mean_per_sub_norm_mean_y - se_y, ymax = mean_per_sub_norm_mean_y + se_y)) +
  theme_minimal() +
  labs(x = "Expect Groupwise mean_per_sub_norm_mean", 
       y = "PLS Expect Groupwise mean_per_sub_norm_mean", 
       title = "Comparison of Groupwise means") +
  scale_color_manual(values = c("pain" = "red","vicarious" = "green",  "cognitive" = "blue")) +
  ylim(0,180) +
  xlim(0,180)
print(g)
}
```


```{r}
library(ggplot2)

# Define a list of keyword pairs
keyword_pairs <- list(
  c("observed" = "pain", "predicted" = "pain"),
  c("observed" = "vic", "predicted" = "vicarious"),
  c("observed" = "cog", "predicted" = "cognitive")
)

combined_data <- data.frame()

for (pair in keyword_pairs) {
  observed_keyword <- names(pair)[1]
  predicted_keyword <- names(pair)[2]
  taskname_observed <- pair[[1]]
  taskname_predicted <- pair[[2]]
  
  subject <- "sub"
  model_iv1 <- "cuetype"
  model_iv2 <- "runtype" # Correctly assign model_iv2 to "runtype"
  dv_observed <- paste0(taskname_observed, "_expect")
  dv_predicted <- paste0("pred_", taskname_predicted, "_expect")
  
  # Process observed data
  expect.subjectwise <- meanSummary(expect_df, c(subject, model_iv1, model_iv2), dv_observed)
  expect.groupwise <- summarySEwithin(data = expect.subjectwise, measurevar = "mean_per_sub", withinvars = c(model_iv1, model_iv2), idvar = subject)
  expect.groupwise$data <- observed_keyword
  
  # Process predicted data
  pls.expect.subjectwise <- meanSummary(expect_df, c(subject, model_iv1, model_iv2), dv_predicted)
  pls.expect.groupwisewise <- summarySEwithin(data = pls.expect.subjectwise, measurevar = "mean_per_sub", withinvars = c(model_iv1, model_iv2), idvar = subject)
  pls.expect.groupwisewise$data <- predicted_keyword
  
  # Assuming pls.expect.groupwisewise and expect.groupwise are already loaded and prepared as described
  # Combine the data for ease of plotting
  temp_combined_data <- data.frame(
    mean_per_sub_norm_mean_x = expect.groupwise$mean_per_sub_norm_mean,  # x-axis
    mean_per_sub_norm_mean_y = pls.expect.groupwisewise$mean_per_sub_norm_mean,  # y-axis
    se_x = expect.groupwise$se,
    se_y = pls.expect.groupwisewise$se,
    cuetype = expect.groupwise$cuetype,
    runtype = expect.groupwise$runtype
  )
  
  combined_data <- rbind(combined_data, temp_combined_data)
}

# Plotting
g <- ggplot(combined_data, aes(x = mean_per_sub_norm_mean_x, y = mean_per_sub_norm_mean_y, color = runtype)) +
  geom_point(size=3) +
  geom_errorbarh(aes(xmin = mean_per_sub_norm_mean_x - se_x, xmax = mean_per_sub_norm_mean_x + se_x)) +
  geom_errorbar(aes(ymin = mean_per_sub_norm_mean_y - se_y, ymax = mean_per_sub_norm_mean_y + se_y)) +
  theme_minimal() +
  labs(x = "Expect Groupwise mean_per_sub_norm_mean", 
       y = "PLS Expect Groupwise mean_per_sub_norm_mean", 
       title = "Comparison of Groupwise means") +
  scale_color_manual(values = c("pain" = "red","vicarious" = "green",  "cognitive" = "blue")) +
  ylim(0,180) +
  xlim(0,180)
print(g)

```
```{r}
library(ggplot2)
library(ggplot2)

# Define a list of keyword pairs
keyword_pairs <- list(
  c("observed" = "pain", "predicted" = "pain"),
  c("observed" = "vic", "predicted" = "vicarious"),
  c("observed" = "cog", "predicted" = "cognitive")
)

combined_data <- data.frame()
plot_list <- list()

for (pair in keyword_pairs) {
  observed_keyword <- names(pair)[1]
  predicted_keyword <- names(pair)[2]
  taskname_observed <- pair[[1]]
  taskname_predicted <- pair[[2]]
  
  subject <- "sub"
  model_iv1 <- "stimulusintensity"
  model_iv2 <- "runtype" # Correctly assign model_iv2 to "runtype"
  dv_observed <- paste0(taskname_observed, "_expect")
  dv_predicted <- paste0("pred_", taskname_predicted, "_expect")
  
  # Process observed data
  expect.subjectwise <- meanSummary(expect_df, c(subject, model_iv1, model_iv2), dv_observed)
  expect.groupwise <- summarySEwithin(data = expect.subjectwise, measurevar = "mean_per_sub", withinvars = c(model_iv1, model_iv2), idvar = subject)
  expect.groupwise$data <- observed_keyword
  
  # Process predicted data
  pls.expect.subjectwise <- meanSummary(expect_df, c(subject, model_iv1, model_iv2), dv_predicted)
  pls.expect.groupwisewise <- summarySEwithin(data = pls.expect.subjectwise, measurevar = "mean_per_sub", withinvars = c(model_iv1, model_iv2), idvar = subject)
  pls.expect.groupwisewise$data <- predicted_keyword
  
  # Assuming pls.expect.groupwisewise and expect.groupwise are already loaded and prepared as described
  # Combine the data for ease of plotting
  temp_combined_data <- data.frame(
    mean_per_sub_norm_mean_x = expect.groupwise$mean_per_sub_norm_mean,  # x-axis
    mean_per_sub_norm_mean_y = pls.expect.groupwisewise$mean_per_sub_norm_mean,  # y-axis
    se_x = expect.groupwise$se,
    se_y = pls.expect.groupwisewise$se,
    stimulusintensity = expect.groupwise$stimulusintensity,
    runtype = expect.groupwise$runtype
  )
  
  # combined_data <- rbind(combined_data, temp_combined_data)


# Plotting
g <- ggplot(temp_combined_data, aes(x = mean_per_sub_norm_mean_x, y = mean_per_sub_norm_mean_y, color = runtype)) +
  geom_point(size=1) +
  geom_errorbarh(aes(xmin = mean_per_sub_norm_mean_x - se_x, xmax = mean_per_sub_norm_mean_x + se_x)) +
  geom_errorbar(aes(ymin = mean_per_sub_norm_mean_y - se_y, ymax = mean_per_sub_norm_mean_y + se_y)) +
  theme_minimal() +
  labs(x = "Expect Groupwise mean_per_sub_norm_mean", 
       y = "PLS Expect Groupwise mean_per_sub_norm_mean", 
       title = "Comparison of Groupwise means") +
  scale_color_manual(values = c("pain" = "red","vicarious" = "green",  "cognitive" = "blue")) +
  ylim(0,75) +
  xlim(0,75)


 plot_list[[length(plot_list) + 1]] <- g
}

combined_plot <- ggarrange(plotlist = plot_list, nrow = 2, ncol = 2)

# Print the combined plot
combined_plot

```


```{r}
library(ggplot2)
library(dplyr)

# Assuming sub_means is your data frame already prepared with the necessary columns

# Define the custom color palette
custom_palette <- c(
  pain = '#941100',
  cognitive = '#011891',
  vicarious = '#008F51',
  general = 'purple'
)

# Set up the plotting grid
expect_pairs <- list(
  c('pred_pain_expect', 'pain_expect'),
  c('pred_vicarious_expect', 'vic_expect'),
  c('pred_cognitive_expect', 'cog_expect'),
  c('pred_general_expect', 'gen_expect')
)
# sub_means <- expect_df %>%
#   group_by(sub, stimulusintensity, runtype) %>%
#   dplyr::summarise(across(c(pred_pain_expect, pain_expect,
#                      pred_vicarious_expect, vic_expect,
#                      pred_cognitive_expect, cog_expect,
#                      pred_general_expect, gen_expect), mean, na.rm = TRUE),
#             .groups = 'drop')
sub_means <- expect_df %>%
  group_by(sub, stimulusintensity, runtype) %>%
  summarise(across(c("pred_pain_expect", "pain_expect",
                     "pred_vicarious_expect", "vic_expect",
                     "pred_cognitive_expect", "cog_expect",
                     "pred_general_expect", "gen_expect"),
            list(mean = ~mean(.x, na.rm = TRUE), 
                 se = ~sd(.x, na.rm = TRUE) / sqrt(n()))),
            .groups = 'drop')

# Assuming 'stimulusintensity' has values that need to be ordered as 'low_stim', 'med_stim', 'high_stim'
sub_means$stimulusintensity <- factor(sub_means$stimulusintensity,
                                      levels = c('low_stim', 'med_stim', 'high_stim'),
                                      ordered = TRUE)
# Creating plots for each pair
plot_list <- lapply(1:length(expect_pairs), function(i) {
  pred_expect <- expect_pairs[[i]][1]
  actual_expect <- expect_pairs[[i]][2]
  
  # Calculate means and standard errors for plotting; adjust this as per your actual data's needs
  grouped_means <- sub_means %>%
    group_by(stimulusintensity, runtype) %>%
    summarise_at(vars(pred_expect, actual_expect), list(mean = mean, se = sd/sqrt(n())))
  
  p <- ggplot(grouped_means, aes_string(x = paste0(actual_expect, "_mean"), y = paste0(pred_expect, "_mean"), color = "runtype")) +
    geom_point(size = 3) +
    geom_errorbar(aes_string(ymin = paste0(pred_expect, "_mean") - paste0(pred_expect, "_se"), ymax = paste0(pred_expect, "_mean") + paste0(pred_expect, "_se")), width = 0.2) +
    geom_errorbarh(aes_string(xmin = paste0(actual_expect, "_mean") - paste0(actual_expect, "_se"), xmax = paste0(actual_expect, "_mean") + paste0(actual_expect, "_se")), height = 0.2) +
    scale_color_manual(values = custom_palette) +
    labs(title = strsplit(pred_expect, "_")[[1]][2], x = 'Actual expect Rating', y = 'Predicted expect Rating') +
    theme_minimal() +
    theme(legend.position = "right")
  
  # Adjust legend for the last two plots
  if(i %in% c(3, 4)) {
    p <- p + theme(legend.position = "bottom")
  } else {
    p <- p + theme(legend.position = "none")
  }
  
  return(p)
})

# Arrange plots in a 2x2 grid
library(gridExtra)
grid.arrange(grobs = plot_list, ncol = 2)

```


> Summary: 

### plot {.unlisted .unnumbered}
We'll plot Y as a function of A and B
X axis: 
Y axis:
Each data point indicates ... 
```{r fig.height=10, fig.width=10}

```
> Conclusion:


:::: {.infobox}
Include the actual content here. here are my thoughts
::::

:::: {.refbox}
Include the actual content here. here are my thoughts
::::

