---
title: "ch4_painprocessing"
output: html_document
date: "2025-07-17"
---

```{r libraries_SIIPS_stim, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(cueR)
library(lme4)
library(optimx)
library(minqa)
library(dfoptim)
library(tidyverse)
library(psych)
library(reshape)
library(dplyr)
# library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(plyr)
library(ggpubr)
library(r2mlm)
library(effectsize)
# library(devtools)
options(es.use_symbols = TRUE) # get nice symbols when printing! (On Windows, requires R >= 4.2.0)
library(EMAtools)
library(emmeans)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(plotly)
library(DT)
library(scico)
library(raincloudplots)
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/R_rainclouds.R")
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/summarySE.R")
library(broom)
library(MuMIn)
# devtools::source_url("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(r2mlm)
main_dir <- dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R",
                          full.names=TRUE,
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```

```{r}
dirname(dirname(getwd()))
```

### Prepare dataframe

```{r}
analysis_folder <- "fmri_nps_canlab"

beh <- readr::read_tsv(file.path(main_dir, "analysis/fmri/nilearn/singletrial_rampupplateau/beh/sub-all_task-all_events.tsv"))
dv <- "nps"
base_dir <- file.path(main_dir, "analysis/fmri/nilearn/deriv01_signature/rampup_plateau_canlab")
all_nps <- read.csv(file.path(base_dir, "signature-NPS_sub-all_runtype-pvc_event-stimulus.csv"))
all_siips <-  read.csv(file.path(base_dir, "signature-SIIPS_sub-all_runtype-pain_event-stimulus.csv"))

############# NOTE: run once; concatenate all csv files ########################
# file_paths <- list.files(base_dir, pattern =  "sub-.*_signature-NPSroi_.*\\.csv$", full.names = TRUE, recursive = TRUE)
# all_nps <- file_paths %>%
#   map_dfr(~read_csv(.x, show_col_types = FALSE), .id = "file_path")
#
# file_paths <- list.files(base_dir, pattern =  "sub-.*_roi-SIIPS.*\\.csv$", full.names = TRUE, recursive = TRUE)
# all_siips <- file_paths %>%
#   map_dfr(~read_csv(.x, show_col_types = FALSE), .id = "file_path")
################################################################################

df_merge <- inner_join(beh, all_nps, by = "singletrial_fname")
df_merge <- df_merge %>%
  mutate(singletrial_fname = as.character(singletrial_fname)) %>%
  extract(singletrial_fname, into = c("sub", "ses", "run", "runtype", "event", "trial", "cuetype", "stimintensity"),
          regex = "^(sub-\\d+)_(ses-\\d+)_(run-\\d+)_runtype-(pain|vicarious|cognitive)_event-(cue|stimulus)_trial-(\\d+)_cuetype-(high|low)(?:_stimintensity-(high|med|low))?\\.nii.gz$",
          remove = FALSE)

# Adjust the dataframe to handle NA for missing stimintensity, if tidyr version doesn't support `fill`
df_merge$stimintensity[df_merge$stimintensity == ""] <- NA

data <-df_merge[df_merge$runtype == "pain" ,]

# contrast code ________________________________________________________________
data$stim <- NA; data$STIM_linear <- NA; data$STIM_quadratic <- NA;
data$CUE_high_gt_low <- NA;
data$SES_linear <- NA;data$SES_quadratic <- NA
data$stim[data$stimulusintensity == "low_stim"] <-  -0.5 # social influence task
data$stim[data$stimulusintensity == "med_stim"] <- 0 # no influence task
data$stim[data$stimulusintensity == "high_stim"] <-  0.5 # no influence task

data$STIM <- factor(data$stimulusintensity)

# contrast code 1 linear
data$STIM_linear[data$stimulusintensity == "low_stim"] <- -0.5
data$STIM_linear[data$stimulusintensity == "med_stim"] <- 0
data$STIM_linear[data$stimulusintensity == "high_stim"] <- 0.5

# contrast code 2 quadratic
data$STIM_quadratic[data$stimulusintensity == "low_stim"] <- -0.33
data$STIM_quadratic[data$stimulusintensity == "med_stim"] <- 0.66
data$STIM_quadratic[data$stimulusintensity == "high_stim"] <- -0.33

# social cude contrast
data$CUE_high_gt_low[data$cue == "low_cue"] <-  -0.5 # social influence task
data$CUE_high_gt_low[data$cue == "high_cue"] <-  0.5 # no influence task

data$EXPECT <- data$expectrating
data$OUTCOME <- data$outcomerating


data$SES_linear[data$ses == "ses-01"] <- -0.5
data$SES_linear[data$ses == "ses-03"] <- 0
data$SES_linear[data$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
data$SES_quadratic[data$ses == "ses-01"] <- -0.33
data$SES_quadratic[data$ses == "ses-03"] <- 0.66
data$SES_quadratic[data$ses == "ses-04"] <- -0.33

stim_con1 <- "STIM_linear"
stim_con2 <- "STIM_quadratic"
iv1 <- "CUE_high_gt_low"
dv <- "nps"
dv_keyword <- "NPS"
```

```{r}
# load dataframes ______________________________________________________________

# SIIPS <- siips %>%
#   select(-X)
# NPS <- nps %>%
#   select(-X)
beh <- readr::read_tsv(file.path(main_dir, "analysis/fmri/nilearn/singletrial_rampupplateau/beh/sub-all_task-all_events.tsv"))
# base_dir <- "/Volumes/spacetop_projects_cue/analysis/fmri/nilearn/deriv01_signature/rampup_plateau_canlab"
NPS <- read.csv(file.path(main_dir, "analysis/fmri/nilearn/deriv01_signature/rampup_plateau_canlab/signature-NPS_sub-all_runtype-pvc_event-stimulus.csv"))
SIIPS <-  read.csv(file.path(main_dir, "analysis/fmri/nilearn/deriv01_signature/rampup_plateau_canlab/signature-SIIPS_sub-all_runtype-pain_event-stimulus.csv"))

# merge the three dataframes ___________________________________________________
df_merge1 <- inner_join(beh, NPS, by = "singletrial_fname")
dfmerge <- inner_join(df_merge1, SIIPS, by = "singletrial_fname")
# df_merge <- inner_join(beh, all_nps, by = "singletrial_fname")


dfmerge <- dfmerge %>%
  mutate(singletrial_fname = as.character(singletrial_fname)) %>%
  extract(singletrial_fname, into = c("sub", "ses", "run", "runtype", "event", "trial", "cuetype", "stimintensity"),
          regex = "^(sub-\\d+)_(ses-\\d+)_(run-\\d+)_runtype-(pain|vicarious|cognitive)_event-(cue|stimulus)_trial-(\\d+)_cuetype-(high|low)(?:_stimintensity-(high|med|low))?\\.nii.gz$",
          remove = FALSE)

dfmerge$NPS <- dfmerge$nps
# create folder to save data ___________________________________________________
analysis_dir <- "/Users/h/Documents/projects_local/cue_expectancy/resources/plots_dissertation/ch4"
dir.create(analysis_dir,
           showWarnings = FALSE,
           recursive = TRUE)
savedir <- analysis_dir
lowcuehex <-  "#4274AD" # "#575a5e"
highcuehex <-  "#C5263A" #"#FEAE00"
```

```{r}
data <-dfmerge[dfmerge$runtype == "pain" ,]

# contrast code ________________________________________________________________
data$stim <- NA; data$STIM_linear <- NA; data$STIM_quadratic <- NA;
data$CUE_high_gt_low <- NA;
data$SES_linear <- NA;data$SES_quadratic <- NA
data$stim[data$stimulusintensity == "low_stim"] <-  -0.5 # social influence task
data$stim[data$stimulusintensity == "med_stim"] <- 0 # no influence task
data$stim[data$stimulusintensity == "high_stim"] <-  0.5 # no influence task

data$STIM <- factor(data$stimulusintensity)
data$SUB <- factor(data$sub)

# undo string format
data$outcomerating_impute[data$outcomerating_impute == "n/a"] <- NA
data$outcomerating_impute <- as.numeric(data$outcomerating_impute)

data$expectrating_impute[data$expectrating_impute == "n/a"] <- NA
data$expectrating_impute <- as.numeric(data$expectrating_impute)

# contrast code 1 linear
data$STIM_linear[data$stimulusintensity == "low_stim"] <- -0.5
data$STIM_linear[data$stimulusintensity == "med_stim"] <- 0
data$STIM_linear[data$stimulusintensity == "high_stim"] <- 0.5

# contrast code 2 quadratic
data$STIM_quadratic[data$stimulusintensity == "low_stim"] <- -0.33
data$STIM_quadratic[data$stimulusintensity == "med_stim"] <- 0.66
data$STIM_quadratic[data$stimulusintensity == "high_stim"] <- -0.33

# social cude contrast
data$CUE_high_gt_low[data$cue == "low_cue"] <-  -0.5 # social influence task
data$CUE_high_gt_low[data$cue == "high_cue"] <-  0.5 # no influence task

data$EXPECT <- data$expectrating
data$OUTCOME <- data$outcomerating


data$SES_linear[data$ses == "ses-01"] <- -0.5
data$SES_linear[data$ses == "ses-03"] <- 0
data$SES_linear[data$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
data$SES_quadratic[data$ses == "ses-01"] <- -0.33
data$SES_quadratic[data$ses == "ses-03"] <- 0.66
data$SES_quadratic[data$ses == "ses-04"] <- -0.33

stim_con1 <- "STIM_linear"
stim_con2 <- "STIM_quadratic"
iv1 <- "CUE_high_gt_low"

subjects_with_inadequate_data <- data %>%
  group_by(sub, CUE_high_gt_low, STIM_linear) %>% #SES_linear,
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 3) %>%
  distinct(sub) %>%
  pull(sub)
df_filter <- data %>%
  filter(!(sub %in% subjects_with_inadequate_data))

print(sprintf("after filtering out subjects that have less than 3 trials in cell, we have N=%d -> N=%d",length(unique(data$sub)), length(unique(df_filter$sub)) ))
```

## 1 Beh

### Beh linear analysis

```{r}
model.beh <- lmer(outcomerating_impute ~ CUE_high_gt_low*STIM_linear +
       CUE_high_gt_low*STIM_quadratic + (CUE_high_gt_low+STIM_linear|sub), data = df_filter)
summary(model.beh)
sjPlot::tab_model(model.beh,
                  title = "Multilevel-modeling: \nlmer(Outcome ~ CUE * STIM + (CUE + STIM | sub), data = pain)",
                  CSS = list(css.table = '+font-size: 12;'))
equatiomatic::extract_eq(model.beh)
```

### Beh lineplot

```{r}
dv <- "outcomerating_impute"
taskname <- "pain"
subject <- "sub"
# Plot 1: reordering variables for plots _______________________________________
df_filter$cue_name <- NA; df_filter$stim_name <- NA
df_filter$cue_name[df_filter$cue == "high_cue"] <-  "high cue"
df_filter$cue_name[df_filter$cue == "low_cue"] <-
  "low cue"

df_filter$stim_name[df_filter$stimulusintensity == "high_stim"] <-  "High"
df_filter$stim_name[df_filter$stimulusintensity == "med_stim"] <-  "Med"
df_filter$stim_name[df_filter$stimulusintensity == "low_stim"] <-  "Low"
# DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))
df_filter$stim_ordered <- factor(df_filter$stim_name, levels = c("Low", "Med", "High"))
df_filter$cue_ordered <- factor(df_filter$cue_name, levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"

# Plot 2: summary statistics  __________________________________________________
stimcue_subjectwise <- meanSummary(df_filter,
                                      c(subject, model_iv1, model_iv2), dv)
stimcue_groupwise <- summarySEwithin(
  data = stimcue_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
stimcue_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

# Plot 3: plot parameters  _____________________________________________________
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
ggtitle <- paste(taskname, " - beh Cooksd removed")
title <- paste(taskname, " - beh")
xlab <- ""
ylab <- "Outcome rating"
ylim <- c(-10, 60)
dv_keyword <- "outcomerating"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c(lowcuehex, highcuehex)
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), ".png",
    sep = ""
  )
)
subset <- stimcue_groupwise[stimcue_groupwise$cue_ordered == "low cue",]
g <- plot_lineplot_twofactor(subset,
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = lowcuehex), ggtitle = "Within pain task: Outcome rating",
                        xlab = "Stimulus intensity", ylab = "Outcome rating")
g <- g + theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
  # geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 2) + # Adjust point size
   ylim(42, 87)
ggsave(file.path(analysis_dir, paste0("beh_maineffect", as.character(Sys.Date()), "_lowcue.svg")), plot=g, w=4, h=4, dpi=300)


k <- cueR::plot_lineplot_twofactor_subset(stimcue_groupwise,
                                    taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = lowcuehex,"high cue" = highcuehex),
                        ggtitle = paste0("Beh N =", length(unique(stimcue_subjectwise$sub))),
                        xlab = "Stimulus intensity", ylab = "Outcome rating")
k<- k+ theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
  # geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 2) + # Adjust point size
 ylim(42, 87)
k
ggsave(file.path(analysis_dir, paste0("beh_maineffect", as.character(Sys.Date()), ".svg")), plot=k, w=4, h=4, dpi=300)
```

## 2 NPS (df_filter)

### NPS linear analysis

```{r}
model.NPS <- lmer(NPS ~ CUE_high_gt_low*STIM_linear +
       CUE_high_gt_low*STIM_quadratic + (CUE_high_gt_low+STIM_linear|sub), data = df_filter)
summary(model.NPS)
sjPlot::tab_model(model.NPS,
                  title = "Multilevel-modeling: \nlmer(NPS ~ CUE * STIM + (CUE + STIM | sub), data = pain)",
                  CSS = list(css.table = '+font-size: 12;'))
equatiomatic::extract_eq(model.NPS)
sink("/Users/h/Desktop/NPS_output.txt")  # Redirects output to 'my_output.txt'
summary(model.NPS)
sink(NULL)  #
```

### lineplot

```{r}
dv <- "NPS"
taskname <- "pain"
subject <- "sub"

# Plot 1: reordering variables for plots _______________________________________
df_filter$cue_name[df_filter$cue == "high_cue"] <-  "high cue"
df_filter$cue_name[df_filter$cue == "low_cue"] <-
  "low cue"

df_filter$stim_name[df_filter$stimulusintensity == "high_stim"] <-  "High"
df_filter$stim_name[df_filter$stimulusintensity == "med_stim"] <-  "Med"
df_filter$stim_name[df_filter$stimulusintensity == "low_stim"] <-  "Low"
# DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))
df_filter$stim_ordered <- factor(df_filter$stim_name, levels = c("Low", "Med", "High"))
df_filter$cue_ordered <- factor(df_filter$cue_name, levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"

# Plot 2: summary statistics  __________________________________________________
NPSstimcue_subjectwise <- meanSummary(df_filter,
                                      c(subject, model_iv1, model_iv2), dv)
NPSstimcue_groupwise <- summarySEwithin(
  data = NPSstimcue_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
NPSstimcue_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

# Plot 3: plot parameters  _____________________________________________________
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
ggtitle <- paste(taskname, " - beh Cooksd removed")
title <- paste(taskname, " - beh")
xlab <- ""
ylab <- "NPS"
ylim <- c(-10, 60)
dv_keyword <- "nps"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c(lowcuehex, highcuehex)
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), ".png",
    sep = ""
  )
)
NPSsubset <- NPSstimcue_groupwise[NPSstimcue_groupwise$cue_ordered == "low cue",]
g <- plot_lineplot_twofactor(NPSsubset,
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = lowcuehex), ggtitle = paste0("NPS N =", length(unique(NPSstimcue_subjectwise$sub))),
                        xlab = "Stimulus intensity", ylab = "NPS")
g <- g + theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
  # geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 2) + # Adjust point size
   ylim( 3,6)
ggsave(file.path(analysis_dir, paste0("NPS_maineffect", as.character(Sys.Date()), "_lowcue.svg")), plot=g, w=4, h=4, dpi=300)


k <- cueR::plot_lineplot_twofactor_subset(NPSstimcue_groupwise, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = lowcuehex,"high cue" = highcuehex),
                        ggtitle = paste0("NPS N =", length(unique(NPSstimcue_subjectwise$sub))),
                        xlab = "Stimulus intensity", ylab = "NPS")
k<- k+ theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
  # geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 2) + # Adjust point size
  ylim( 4,6)
k
ggsave(file.path(analysis_dir, paste0("NPS_maineffect", as.character(Sys.Date()), ".svg")), plot=k, w=4, h=4, dpi=300)
```

### NPS pos (df_filter)

```{r}
dv <- "npspos"
taskname <- "pain"
subject <- "sub"
# Plot 1: reordering variables for plots _______________________________________
df_filter$cue_name[df_filter$cue == "high_cue"] <-  "high cue"
df_filter$cue_name[df_filter$cue == "low_cue"] <-
  "low cue"

df_filter$stim_name[df_filter$stimulusintensity == "high_stim"] <-  "High"
df_filter$stim_name[df_filter$stimulusintensity == "med_stim"] <-  "Med"
df_filter$stim_name[df_filter$stimulusintensity == "low_stim"] <-  "Low"
# DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))
df_filter$stim_ordered <- factor(df_filter$stim_name, levels = c("Low", "Med", "High"))
df_filter$cue_ordered <- factor(df_filter$cue_name, levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"

# Plot 2: summary statistics  __________________________________________________
NPSstimcue_subjectwise <- meanSummary(df_filter,
                                      c(subject, model_iv1, model_iv2), dv)
NPSstimcue_groupwise <- summarySEwithin(
  data = NPSstimcue_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
NPSstimcue_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

# Plot 3: plot parameters  _____________________________________________________
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
ggtitle <- paste(taskname, " - beh Cooksd removed")
title <- paste(taskname, " - beh")
xlab <- ""
ylab <- "NPSpos"
ylim <- c(-10, 60)
dv_keyword <- "nps"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c(lowcuehex, highcuehex)
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), ".png",
    sep = ""
  )
)
NPSsubset <- NPSstimcue_groupwise[NPSstimcue_groupwise$cue_ordered == "low cue",]
g <- plot_lineplot_twofactor(NPSsubset,
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = lowcuehex), ggtitle = paste0("NPS N =", length(unique(NPSstimcue_subjectwise$sub))),
                        xlab = "Stimulus intensity", ylab = "NPS")
g <- g + theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
  # geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 2) + # Adjust point size
   ylim( 3,6)
ggsave(file.path(analysis_dir, paste0("NPSpos_maineffect", as.character(Sys.Date()), "_lowcue.svg")), plot=g, w=4, h=4, dpi=300)


k <- cueR::plot_lineplot_twofactor_subset(NPSstimcue_groupwise,taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = lowcuehex,"high cue" = highcuehex),
                        ggtitle = paste0("NPS (pos) N =", length(unique(NPSstimcue_subjectwise$sub))),
                        xlab = "Stimulus intensity", ylab = "NPS")
k<- k+ theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
  # geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 2)
k
ggsave(file.path(analysis_dir, paste0("NPSpos_maineffect", as.character(Sys.Date()), ".svg")), plot=k, w=4, h=4, dpi=300)
```

### NPS neg

```{r}
dv <- "npsneg"
taskname <- "pain"
subject <- "sub"
# Plot 1: reordering variables for plots _______________________________________
df_filter$cue_name[df_filter$cue == "high_cue"] <-  "high cue"
df_filter$cue_name[df_filter$cue == "low_cue"] <-
  "low cue"

df_filter$stim_name[df_filter$stimulusintensity == "high_stim"] <-  "High"
df_filter$stim_name[df_filter$stimulusintensity == "med_stim"] <-  "Med"
df_filter$stim_name[df_filter$stimulusintensity == "low_stim"] <-  "Low"
# DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))
df_filter$stim_ordered <- factor(df_filter$stim_name, levels = c("Low", "Med", "High"))
df_filter$cue_ordered <- factor(df_filter$cue_name, levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"

# Plot 2: summary statistics  __________________________________________________
NPSstimcue_subjectwise <- meanSummary(df_filter,
                                      c(subject, model_iv1, model_iv2), dv)
NPSstimcue_groupwise <- summarySEwithin(
  data = NPSstimcue_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
NPSstimcue_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

# Plot 3: plot parameters  _____________________________________________________
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
ggtitle <- paste(taskname, " - beh Cooksd removed")
title <- paste(taskname, " - beh")
xlab <- ""
ylab <- "NPSneg"
ylim <- c(-10, 60)
dv_keyword <- "nps"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c(lowcuehex, highcuehex)
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), ".png",
    sep = ""
  )
)
NPSsubset <- NPSstimcue_groupwise[NPSstimcue_groupwise$cue_ordered == "low cue",]
g <- plot_lineplot_twofactor(NPSsubset,
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = lowcuehex), ggtitle = paste0("NPS N =", length(unique(NPSstimcue_subjectwise$sub))),
                        xlab = "Stimulus intensity", ylab = "NPSneg")
g <- g + theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
  # geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 2) + # Adjust point size
   ylim( 3,6)
ggsave(file.path(analysis_dir, paste0("NPSneg_maineffect", as.character(Sys.Date()), "_lowcue.svg")), plot=g, w=4, h=4, dpi=300)


k <- cueR::plot_lineplot_twofactor_subset(NPSstimcue_groupwise, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = lowcuehex,"high cue" = highcuehex),
                        ggtitle = paste0("NPSneg N =", length(unique(NPSstimcue_subjectwise$sub))),
                        xlab = "Stimulus intensity", ylab = "NPSneg")
k<- k+ theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
  # geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 2)
k
ggsave(file.path(analysis_dir, paste0("NPSneg_maineffect", as.character(Sys.Date()), ".svg")), plot=k, w=4, h=4, dpi=300)
```

## 3 PE (PEmerge)

```{r}
PEdf <- read.csv("/Users/h/Documents/projects_local/cue_expectancy/data/RL/modelfit_072024/table_pain.csv")


clean_filename <- function(filename) {
  # Remove _cue that follows cuetype-
  filename <- gsub("(cuetype-[^_]+)_cue", "\\1", filename)
  # Remove _stim_stim that follows stimintensity-
  filename <- gsub("(stimintensity-[^_]+)_stim_stim", "\\1", filename)
  return(filename)
}

# Apply the function to the singletrial_fname column
PEdf$singletrial_fname <- sapply(PEdf$singletrial_fname, clean_filename)
PEmerge<- inner_join(df_filter, PEdf, by = "singletrial_fname")
#
# PEmerge <- merge(dfmerge, PEdf, by = c("src_subject_id", "session_id", "param_run_num", "trial_index"))
print(PEmerge)

PE.model <- lmer(nps ~ PE_mdl2 + (1 | sub), data=PEmerge, control = lmerControl(optimizer = "nmkbw"))
summary(PE.model)
sjPlot::tab_model(PE.model,
                  title = "Multilevel-modeling: \nlmer(NPS ~ PE + (PE | sub), data = pain)",
                  CSS = list(css.table = '+font-size: 12;'))
equatiomatic::extract_eq(PE.model)
sink("/Users/h/Desktop/PEnps_output.txt")  # Redirects output to 'my_output.txt'
summary(PE.model)
sink(NULL)  #

library(ggplot2)

min_value <- -40
max_value <- 40
PEmerge$sub <- factor(PEmerge$sub)
plot.PE_NPS <- ggplot(PEmerge, aes(x = PE_mdl2, y = NPS)) +
  geom_point(aes(colour = sub), size = .1) +  # Points colored by subject
  geom_smooth(aes(colour = sub), method = 'lm', formula = y ~ x, se = FALSE, size = .3, linetype = "dashed") +  # Subject-wise regression lines
  geom_smooth(method = 'lm', formula = y ~ x, se = FALSE, size = .5, color = "black") +  # Group regression line
  # ylim(min_value, max_value) +  # Set y-axis limits
  # xlim(min_value, max_value)
  theme_classic2()  +# Use a theme with a white background
xlab("PE") +
   theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 24, ), # Axis titles
          axis.text = element_text(size = 18), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5),# Plot title
         legend.position = "none"
          )
plot.PE_NPS
ggsave("/Users/h/Documents/projects_local/cue_expectancy/resources/plots_dissertation/ch4/ch4_NPSPE.png",plot.PE_NPS, w=5, h=4, dpi=300)

```

Q. How correlated are the outcome ratings and NPS values??
TODO: can we indicate correlation based on significance

## Correlation plot

```{r}
library(corrplot)
# PEmerge$cuetype_numeric <- as.numeric(as.factor(PEmerge$cue))
PEmerge$cue_coded <- ifelse(PEmerge$cue == "high_cue", 1, -1)
vars_to_center <- c("outcomerating_impute", "expectrating_impute", "PE_mdl2", "beh_PE", "nps", "npspos", "npsneg", "cue_coded")
centered_vars <- as.data.frame(scale(PEmerge[, vars_to_center], center = TRUE, scale = FALSE))

centered_vars$beh_PE <- PEmerge$outcomerating_impute - PEmerge$expectrating_impute
# subset <- PEmerge[, c( "outcomerating_impute", "expectrating_impute", "PE_mdl2","beh_PE", "nps", "npspos",  "npsneg", "cuetype_numeric") ]
cor_matrix <- cor(centered_vars, use = "pairwise.complete.obs")
corrplot(cor_matrix, method = "circle")

# Correlation between cuetype and model-based PE
# correlation_model <- cor_matrix["cuetype_numeric", "PE_mdl2"]
# print(correlation_model)
# 
# # Correlation between cuetype and behavioral PE
# correlation_behavioral <- cor_matrix["cuetype_numeric", "beh_PE"]
# print(correlation_behavioral)
```

### Tor suggestion lmer with PE

> What to do when model fit is singular
> https://stackoverflow.com/questions/54597496/how-to-cope-with-a-singular-fit-in-a-linear-mixed-model-lme4
> Singular. it means 
* one or more random effect variances are near zero, 
* and the model is overfitting or overparameterized (can't estimate all the random slopes reliably).
> suggestion. Simplify the random effect structure

Q. Why would i have a singular random effets structure?
A1. when you have too many variables you're fitting. You include too many random slopes relative to the amount of data
A2. the predictors are highly collinear (PE is similar to cue)

NPS pos is predicted by cue and stim
Once PE comes into the picture, matrix is singular
```{r message=TRUE, warning=TRUE}
summary(NPSPE)
```

```{r echo=TRUE}
#
# model.NPS <- lmer(NPS ~ CUE_high_gt_low*STIM_linear +
#        CUE_high_gt_low*STIM_quadratic + (CUE_high_gt_low+STIM_linear|sub), data = df_filter)

NPSPE <- lmer(NPS ~ CUE_high_gt_low + STIM_linear +
       STIM_quadratic  + scale(PE_mdl2) + (1  | sub),
     data = PEmerge)
     # control=lmerControl(isSingular(NPSPE, tol = 1e-4)))
     # check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4)))
summary(NPSPE)
sjPlot::tab_model(NPSPE,
                  title = "model 2: \nlmer(NPS ~ cue + stim + PE + (cue + stim | sub), data = pain)",
                  CSS = list(css.table = '+font-size: 12;'))
equatiomatic::extract_eq(NPSPE)

library(sjPlot)

# Plot marginal effect (partial slope) for PE
library(ggplot2)

# Plot fitted values by subject
PEmerge$predicted_NPS <- predict(NPSPE)

library(dplyr)

PEmerge_sorted <- PEmerge %>%
  arrange(sub, PE_mdl2)

ggplot(PEmerge_sorted, aes(x = PE_mdl2, y = predicted_NPS, color = sub)) +
  geom_line(aes(group = sub), alpha = 0.4) +
  labs(title = "Subject-specific predicted slopes for Prediction Error",
       x = "Prediction Error (PE_mdl2)",
       y = "Predicted NPS") +
  theme_minimal(base_size = 14) +
  theme(legend.position = "none")

library(ggeffects)
library(ggplot2)

# Get predicted values for PE across its range
pe_pred <- ggpredict(NPSPE, terms = "CUE_high_gt_low")

# Plot
ggplot(pe_pred, aes(x = x, y = predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = 0.2) +
  labs(title = "Partial Effect of Prediction Error on NPS",
       x = "Prediction Error (PE_mdl2)",
       y = "Predicted NPS") +
  theme_minimal(base_size = 14)

plot_model(NPSPE, type = "eff", terms = c( "STIM_linear","PE_mdl2"))

```

## 06/26/2025
After slack discussion

One more note for now.  Putting cue and PE into the same linear model, as you did for SIIPS (finding pos effects of both), requires some nuance to interpret and i'm not sure we want to go that route.
This is because cue is a main driver of PEs: high cue -> high predicted pain -> more negative aversive PEs/positive appetitive PEs.  If you partial that out and then look at effects of PE, you're looking at effects of worse-than-expected pain independent of cue. That's interesting but driven by trial-to-trial fluctuations independent of cue, which are probably smaller effects than the cue effects.
Overall, SIIPS activity is not consistent with aversive PEs, because it assimilates to cued values, rather than the opposite. Aversive PEs would show contrast from cued values like NPSpos does.
A model comparison way to approach this could be the following:
Test separate models with {cue}, {stim}, {pe}, {cue + stim}, and {cue + stim + pe} predictors. pe is a derived variable caused by negative effects of cue and positive effects of stim.
Save residual variances for each subject for each model. Transform these to residual std by taking square root
Perform sign tests on pairs of these residual std values (or paired t-tests, if approx normally dstributed) across models.  lower variance means a better model.
A brain variable that codes for aversive PEs will show (a) pe < cue only and pe < stim only in terms of error, (b) negative effects of cue and positive effects of stim in {cue, stim} model, and possibly (c) {cue, stim, pe} < {cue, stim} in residual error. If (c) holds, the trial-to-trial PE predicts the outcome above and beyond the average cue and stim effects.  Also, if error for {pe alone} = error for {cue, stim} it means the trial-to-trial PE model captures the joint effects of cue and stim (ingredients of PE) adequately.

```{r}
############### STEP 01. model each factor
NPSpos ~  cue 
NPSpos ~ stim 
NPSpos ~ PE 
NPSpos ~ cue + stim 
NPSpos ~ cue + stim + PE 

############### STEP 02. residual values
residual_values 

############### STEP 03. signed tests

############### STEP 04. interpretation
```


## 4 NPS nociceptive ROI (df_filter.NA)

```{r}
# STEP 0. filter data __________________________________________________________
# Make sure that each condition cell has adequate amount of trials
dependent_vars <- c("nps","npspos","npsneg",
                    "pos_nps_vermis","pos_nps_rIns","pos_nps_rV1","pos_nps_rThal",
                    "pos_nps_lIns","pos_nps_rdpIns","pos_nps_rS2_Op","pos_nps_dACC",
                    "neg_nps_rLOC","neg_nps_lLOC","neg_nps_rpLOC","neg_nps_pgACC","neg_nps_lSTS","neg_nps_rIPL","neg_nps_PCC"  )
newlist <- c("NPS","NPS positive weights","NPS negative weights",
                    "Vermis","rIns","rV1","rThal",
                    "lIns","rdpIns","rS2 & Op","dACC",
                    "neg_nps_rLOC","neg_nps_lLOC","neg_nps_rpLOC","neg_nps_pgACC","neg_nps_lSTS","neg_nps_rIPL","neg_nps_PCC"  )

# Initialize a DataFrame to collect combined results
combined_se_calc_cooksd <- data.frame()
for (i in seq_along(dependent_vars)) {

  dv <- dependent_vars[i]
  dv_title <- newlist[i]
  print(paste("_______",i, dv, "_______"))

subjects_with_inadequate_data <- data %>%
  group_by(sub, CUE_high_gt_low, STIM_linear) %>% #SES_linear,
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 3) %>%
  distinct(sub) %>%
  pull(sub)
df_filter <- data %>%
  filter(!(sub %in% subjects_with_inadequate_data))

print(sprintf("after filtering out subjects that have less than 3 trials in cell, we have N=%d -> N=%d",length(unique(data$sub)), length(unique(df_filter$sub)) ))

## QC. check NPS distribution __________________________________________________

df_filter.NA <- df_filter %>% filter(!is.na(nps))  # Remove NA values
head(df_filter.NA)


combined_se_calc_cooksd <- data.frame()
taskname = "pain"
ggtitle <- paste(taskname, " - NPS (degree)")
title <- paste(taskname, " - actual")
subject <- "sub"
w <- 10
h <- 6


analysis_dir <-
  file.path(main_dir,
            "analysis",
            "mixedeffect",
            analysis_folder,
            as.character(Sys.Date())) # nolint
dir.create(analysis_dir,
           showWarnings = FALSE,
           recursive = TRUE)
savedir <- analysis_dir

df_filter.NA <- df_filter.NA %>%
    group_by(sub) %>%
    mutate(NPS_scaled = scale(nps)) %>%
    ungroup()

# 1. rename reordering for plots ______________________________________________
df_filter.NA$cue_name <- NA; df_filter.NA$stim_name <- NA
df_filter.NA$cue_name[df_filter.NA$cue == "high_cue"] <-  "high cue"
df_filter.NA$cue_name[df_filter.NA$cue == "low_cue"] <-  "low cue"

df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "high_stim"] <-  "High"
df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "med_stim"] <-  "Med"
df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "low_stim"] <-  "Low"

df_filter.NA$stim_ordered <- factor(df_filter.NA$stim_name, levels = c("Low", "Med", "High"))
df_filter.NA$cue_ordered <- factor(df_filter.NA$cue_name, levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"


# 2. lmer model ________________________________________________________________
model_savefname <- file.path(
  analysis_dir,
  paste(
    "lmer_nps-",dv,"_",as.character(Sys.Date()),".txt",
    sep = ""
  )
)
formula_string <- paste(dv, "~ CUE_high_gt_low * STIM_linear + CUE_high_gt_low * STIM_quadratic + (CUE_high_gt_low + STIM_linear | sub)")
model_formula <- as.formula(formula_string)
# Fit the model
sink(model_savefname)
# This control parameter which ignores the singular warning allows for a zero estimate.
# preoceed with caution. # Read: https://stackoverflow.com/questions/54597496/how-to-cope-with-a-singular-fit-in-a-linear-mixed-model-lme4
model.npscuestim <- lmer(model_formula, data = df_filter.NA,
                         control=lmerControl(check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4)))
                         # control = lmerControl(optimizer = "nmkbw"))
print(summary(model.npscuestim))
sink()

# Check why convergence is negative ____________________________________________
aa <- lme4::allFit(model.npscuestim)
opt.summary <- glance(aa) |> select(optimizer, AIC, NLL_rel) |> arrange(NLL_rel)
print(opt.summary)


# R2 ___________________________________________________________________________
r_squared <- MuMIn::r.squaredGLMM(model.npscuestim)
R2m = r_squared[1] # Marginal R-squared
R2c = r_squared[2]  # Conditional R-squared



# summary statistics calculate mean and se  ____________________________________
NPSstimcue_subjectwise <- meanSummary(df_filter.NA,
                                      c(subject, model_iv1, model_iv2), dv)
NPSstimcue_groupwise <- summarySEwithin(
  data = NPSstimcue_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
NPSstimcue_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

combined_se_calc_cooksd <-
  rbind(combined_se_calc_cooksd, NPSstimcue_groupwise)

# plot parameters ______________________________________________________________
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
subject <- "sub"
ggtitle <- paste(taskname, " - NPS Cooksd removed")
title <- paste(taskname, " - NPS")
xlab <- ""
ylab <- "NPS (degree)"
ylim <- c(-1,1)
dv_keyword <- "NPS"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#4274AD", "#C5263A")
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), "_cooksd.png",
    sep = ""
  )
)



### Lineplots with only low cue ____________________________________
subsetNPS <- NPSstimcue_groupwise[NPSstimcue_groupwise$cue_ordered == "low cue",]
g <- cueR::plot_lineplot_twofactor_subset(subsetNPS, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#4274AD", "#D73027"),
                        ggtitle = dv_title,
                        xlab = "Stimulus intensity", ylab = "Mean score")
g + theme(aspect.ratio=.8)


### Lineplots________________________________________________________________________
g <- cueR::plot_lineplot_twofactor_subset(NPSstimcue_groupwise, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#4274AD","high cue" = "#C5263A"),
                        ggtitle = dv_title,
                        xlab = "Stimulus intensity", ylab = "Mean score")
g <- g + theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
  # geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 2)  # Adjust point size


#   print(arranged_plot)
  plot_filename = file.path(analysis_dir,
  paste('lineplot_task-all_rating-', dv_keyword,dv, '.svg', sep = ""))

print(g)

  ggsave(plot_filename, g, width = 8, height = 4, dpi=300)
}
```

## 5 SIIPS (df_filter.NA)

### SIIPS linear analysis

```{r}


model.SIIPS <- lmer(SIIPS ~ CUE_high_gt_low*STIM_linear +
       CUE_high_gt_low*STIM_quadratic + (CUE_high_gt_low*STIM_linear|sub),
       data = df_filter.NA,
       control=lmerControl(check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4)))
summary(model.SIIPS)
sjPlot::tab_model(model.SIIPS,
                  title = "Multilevel-modeling: \nlmer(SIIPS ~ CUE * STIM + (CUE + STIM | sub), data = pain)",
                  CSS = list(css.table = '+font-size: 12;'))

sink("/Users/h/Desktop/SIIPS_output.txt")  # Redirects output to 'my_output.txt'
summary(model.SIIPS)
equatiomatic::extract_eq(model.SIIPS)
sink(NULL)  #
```

```{r}
dv <- "SIIPS"
taskname <- "pain"
subject <- "sub"
df_filter$stim_name <- NA; df_filter$cue_name <- NA
# Plot 1: reordering variables for plots _______________________________________
df_filter$cue_name[df_filter$cue == "high_cue"] <-  "high cue"
df_filter$cue_name[df_filter$cue == "low_cue"] <-  "low cue"

df_filter$stim_name[df_filter$stimulusintensity == "high_stim"] <-  "High"
df_filter$stim_name[df_filter$stimulusintensity == "med_stim"] <-  "Med"
df_filter$stim_name[df_filter$stimulusintensity == "low_stim"] <-  "Low"

df_filter$stim_ordered <- factor(df_filter$stim_name, levels = c("Low", "Med", "High"))
df_filter$cue_ordered <- factor(df_filter$cue_name, levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"

# Plot 2: summary statistics  __________________________________________________
SIIPS_subjectwise <- meanSummary(df_filter,
                                      c(subject, model_iv1, model_iv2), dv)
SIIPS_groupwise <- summarySEwithin(
  data = SIIPS_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
SIIPS_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

# Plot 3: plot parameters  _____________________________________________________
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
ggtitle <- paste(taskname, " - beh Cooksd removed")
title <- paste(taskname, " - beh")
xlab <- ""
ylab <- "SIIPS"
ylim <- c(-10, 60)
dv_keyword <- "siips"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c(lowcuehex, highcuehex)
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), ".png",
    sep = ""
  )
)
SIIPSsubset <- SIIPS_groupwise[SIIPS_groupwise$cue_ordered == "low cue",]
g <- plot_lineplot_twofactor(SIIPSsubset,
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = lowcuehex), ggtitle = paste0("NPS N =", length(unique(SIIPS_subjectwise$sub))),
                        xlab = "Stimulus intensity", ylab = "SIIPS")
g <- g + theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
  # geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 2) + # Adjust point size
   ylim(465, 650)
ggsave(file.path(analysis_dir, paste0("SIIPS_maineffect", as.character(Sys.Date()), "_lowcue.svg")), plot=g, w=4, h=4, dpi=300)

k <- cueR::plot_lineplot_twofactor_subset(SIIPS_groupwise, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = lowcuehex,"high cue" = highcuehex),
                        ggtitle = paste0("SIIPS N =", length(unique(SIIPS_subjectwise$sub))),
                        xlab = "Stimulus intensity", ylab = "SIIPS")
k<- k+ theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
  # geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 2) + # Adjust point size
 ylim(465, 650)
k
ggsave(file.path(analysis_dir, paste0("SIIPS_maineffect", as.character(Sys.Date()), ".svg")), plot=k, w=4, h=4, dpi=300)
```

## 5-3 SIIPS and PE (PEmerge)

```{r}

SIIPSPE <- lmer(SIIPS ~ CUE_high_gt_low + STIM_linear + PE_mdl2 + (CUE_high_gt_low + STIM_linear   |sub),
     data = PEmerge,
     control=lmerControl(check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4)))
summary(SIIPSPE)
vif(SIIPSPE)
```

## Session wise filter

```{r}
subjects_with_inadequate_data <- data %>%
  group_by(sub, CUE_high_gt_low, STIM_linear, SES_linear) %>% #SES_linear,
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 4) %>%
  distinct(sub) %>%
  pull(sub)
df_filter_ses <- data %>%
  filter(!(sub %in% subjects_with_inadequate_data))

print(sprintf("after filtering out subjects that have less than 3 trials in cell, we have N=%d -> N=%d",length(unique(data$sub)), length(unique(df_filter_ses$sub)) ))
```

## 4 Sessionwise Beh

```{r}
model.behses <- lmer(outcomerating_impute ~
                          CUE_high_gt_low*STIM_linear*SES_linear +
                          CUE_high_gt_low*STIM_quadratic*SES_linear +
                          CUE_high_gt_low*STIM_linear*SES_quadratic +
                          CUE_high_gt_low*STIM_quadratic*SES_quadratic +
                          (CUE_high_gt_low + STIM_linear + SES_linear |
         sub), data = df_filter_ses,
         control=lmerControl(check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4)))
         # control = lmerControl(optimizer = "nmkbw"
                               # ))
summary(model.behses)
sjPlot::tab_model(model.behses,
                  title = "Multilevel-modeling: \nlmer(BEH ~ CUE * STIM *SES + (CUE + STIM + SES | sub), data = pain)",
                  CSS = list(css.table = '+font-size: 12;'))
equatiomatic::extract_eq(model.behses)

# Check why convergence is negative ____________________________________________
abeh <- lme4::allFit(model.behses)
opt.summary <- glance(abeh) |> select(optimizer, AIC, NLL_rel) |> arrange(NLL_rel)
print(opt.summary)
```

## 5 Sessionwise NPS

```{r}
model.NPSses <- lmer(NPS ~
                          CUE_high_gt_low*STIM_linear*SES_linear +
                          CUE_high_gt_low*STIM_quadratic*SES_linear +
                          CUE_high_gt_low*STIM_linear*SES_quadratic +
                          CUE_high_gt_low*STIM_quadratic*SES_quadratic +
                          (CUE_high_gt_low + STIM_linear +SES_linear |
         sub), data = df_filter_ses,
    control = lmerControl(
      optimizer = "optimx",
      optCtrl = list(
        method = "nmkb",
        maxit = 1e9,
        maxfun = 1e9,
        maxeval = 1e7,
        xtol_abs = 1e-9,
        ftol_abs = 1e-9
      )
    )
  )
summary(model.NPSses)
sjPlot::tab_model(model.NPSses,
                  title = "Multilevel-modeling: \nlmer(NPS ~ CUE * STIM * SES+ (CUE + STIM + SES| sub), data = pain)",
                  CSS = list(css.table = '+font-size: 12;'))
equatiomatic::extract_eq(model.NPSses)
```

```{r}
optimx_options <- c("L-BFGS-B", "nlminb", "nlm", "bobyqa", "nmkb", "hjkb")
for(i in 1:length(optimx_options)){
  print(paste0("Testing optimx: ", optimx_options[i]))
  model_flex <-   lmer(
    NPS ~
      CUE_high_gt_low * STIM_linear * SES_linear +
      CUE_high_gt_low * STIM_quadratic * SES_linear +
      CUE_high_gt_low * STIM_linear * SES_quadratic +
      CUE_high_gt_low * STIM_quadratic * SES_quadratic +
      (CUE_high_gt_low + SES_linear + SES_quadratic + STIM_linear + STIM_quadratic |
         sub),
    data = df_filter_ses,
    control = lmerControl(
      optimizer = "optimx",
      optCtrl = list(
        method = optimx_options[i],
        maxit = 1e9,
        maxfun = 1e9,
        maxeval = 1e7,
        xtol_abs = 1e-9,
        ftol_abs = 1e-9
      )
    )
  )

  if(is.null(model_flex@optinfo$conv$lme4$messages)){
    print(paste0("One of the optimx options, ", optimx_options[i],", worked!"))
    print(model_flex)
    break
  }
}
```

## 6 Sessionwise SIIPS

> random slopes of cue effects were colinear with random intercepts with a correlation of 1, therefore estimating the idnvidual difference baseline and dindividual difference of cue effects were impossible

```{r}
with(df_filter_ses, table(CUE_high_gt_low, STIM_linear, SES_linear))
```

```{r}
library(glmmTMB)
model.SIIPSses <- lmer(SIIPS ~
                          CUE_high_gt_low*STIM_linear*SES_linear +
                          CUE_high_gt_low*STIM_quadratic*SES_linear +
                          CUE_high_gt_low*STIM_linear*SES_quadratic +
                          CUE_high_gt_low*STIM_quadratic*SES_quadratic +
                          (1+ CUE_high_gt_low + STIM_quadratic + SES_linear|sub),
         data = df_filter_ses,
                  control = lmerControl(optimizer = "nmkbw"
                               ))


summary(model.SIIPSses)
sjPlot::tab_model(model.SIIPSses,
                  title = "Multilevel-modeling: \nlmer(SIIPS ~ CUE * STIM * SES+ (CUE + STIM *SES | sub), data = pain)",
                  CSS = list(css.table = '+font-size: 12;'))
equatiomatic::extract_eq(model.SIIPSses)
```

> Session is inversly colinear with stimulus intensity, which makes the random slopes impossible to estimate

```{r}


library(ggplot2); theme_set(theme_bw())
library(ggalt)
(ggplot(df_filter_ses, aes(STIM_linear,SIIPS,SES_linear,colour=CUE_high_gt_low))
    +geom_point()
    +geom_encircle(aes(group=sub))
    +theme(legend.position="none")
    + scale_y_log10()
)
```

### linear estimator

```{r}
optimx_options <- c("L-BFGS-B", "nlminb", "nlm", "bobyqa", "nmkb", "hjkb")
for(i in 1:length(optimx_options)){
  print(paste0("Testing optimx: ", optimx_options[i]))
  model_flex <-   lmer(
    SIIPS ~
      CUE_high_gt_low * STIM_linear * SES_linear +
      CUE_high_gt_low * STIM_quadratic * SES_linear +
      CUE_high_gt_low * STIM_linear * SES_quadratic +
      CUE_high_gt_low * STIM_quadratic * SES_quadratic +
      (1+ CUE_high_gt_low + STIM_quadratic + SES_linear  |
         sub),
    data = df_filter_ses,
    control = lmerControl(
      optimizer = "optimx",
      optCtrl = list(
        method = optimx_options[i],
        maxit = 1e9,
        maxfun = 1e9,
        maxeval = 1e3,
        xtol_abs = 1e-3,
        ftol_abs = 1e-3
      )
    )
  )

  if(is.null(model_flex@optinfo$conv$lme4$messages)){
    print(paste0("One of the optimx options, ", optimx_options[i],", worked!"))
    print(model_flex)
    break
  }
}
```

```{r}
# non linear options
algoptions <- c("NLOPT_LN_PRAXIS", "NLOPT_GN_CRS2_LM",
"NLOPT_LN_COBYLA", "NLOPT_LN_NEWUOA",
"NLOPT_LN_NEWUOA_BOUND", "NLOPT_LN_NELDERMEAD",
"NLOPT_LN_SBPLX", "NLOPT_LN_BOBYQA")

for(i in 1:length(algoptions)){
  print(paste0("Testing nloptwrap: ", algoptions[i]))
  model_flex <- lmer(    SIIPS ~
      CUE_high_gt_low * STIM_linear * SES_linear +
      CUE_high_gt_low * STIM_quadratic * SES_linear +
      CUE_high_gt_low * STIM_linear * SES_quadratic +
      CUE_high_gt_low * STIM_quadratic * SES_quadratic +
      ( 1 +CUE_high_gt_low + STIM_quadratic + SES_linear  |
         sub),
                     data = df_filter_ses, REML=FALSE,
                     control = lmerControl(optimizer = "nloptwrap",
                                           optCtrl = list(algorithm = algoptions[i],
                                                          maxit = 1e9,
                                                          maxfun = 1e9,
                                                          maxeval = 1e9,
                                                          xtol_abs = 1e-2,
                                                          ftol_abs = 1e-2)))
  if(is.null(model_flex@optinfo$conv$lme4$messages)){
    print(paste0("One of the nloptwrap options, ", algoptions[i],", worked!"))
    print(model_flex)
    break
  }
}
```

```{r}
  model.glmm <- glmmTMB::glmmTMB(    SIIPS ~
      CUE_high_gt_low * STIM_linear * SES_linear +
      CUE_high_gt_low * STIM_quadratic * SES_linear +
      CUE_high_gt_low * STIM_linear * SES_quadratic +
      CUE_high_gt_low * STIM_quadratic * SES_quadratic +
      ( CUE_high_gt_low + SES_linear  + STIM_linear  |         sub),
                     data = df_filter_ses)
summary(model.glmm)
```

```{r}
dv <- "SIIPS"
taskname <- "pain"
subject <- "sub"
# Plot 1: reordering variables for plots _______________________________________
df_filter$cue_name[df_filter$cue == "high_cue"] <-  "high cue"
df_filter$cue_name[df_filter$cue == "low_cue"] <-  "low cue"

df_filter$stim_name[df_filter$stimulusintensity == "high_stim"] <-  "High"
df_filter$stim_name[df_filter$stimulusintensity == "med_stim"] <-  "Med"
df_filter$stim_name[df_filter$stimulusintensity == "low_stim"] <-  "Low"
df_filter$stim_ordered <- factor(df_filter$stim_name, levels = c("Low", "Med", "High"))
df_filter$cue_ordered <- factor(df_filter$cue_name, levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"

# Plot 2: summary statistics  __________________________________________________
SIIPS_subjectwise <- meanSummary(df_filter,
                                      c(subject, model_iv1, model_iv2, "ses"), dv)
SIIPS_groupwise <- summarySEwithin(
  data = SIIPS_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2, "ses"),
  idvar = subject
)
SIIPS_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

# Plot 3: plot parameters  _____________________________________________________
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
ggtitle <- paste(taskname, " - beh Cooksd removed")
title <- paste(taskname, " - beh")
xlab <- ""
ylab <- "SIIPS"
ylim <- c(-10, 60)
dv_keyword <- "siips"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c(lowcuehex, highcuehex)
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), ".png",
    sep = ""
  )
)
```
