# beh :: outcome ~ cue \* stim {#upgrade_beh-outcome-cueXstim}

## What is the purpose of this notebook? {.unlisted .unnumbered}

Here, I plot the outcome ratings as a function of cue and Stimulus intensity.

- Main model: `lmer(outcome_rating ~ cue * stim)`
- Main question: do outcome ratings differ as a function of cue type and Stimulus intensity?
- If there is a main effect of cue on outcome ratings, does this cue effect differ depending on task type?
- Is there an interaction between the two factors?
- IV:
- cue (high / low)
- stim (high / med / low)
- DV: outcome rating

```{r load_libraries_4, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(psych)
library(car)
library(lme4)
library(lmerTest)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(rmarkdown)
library(stringr)
library(ICC)
library(gghalves)

library(ggpubr)
library(cueR)
main_dir = dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, "scripts/step02_R/utils"),
                        pattern="*.R",
                        full.names=TRUE,
                        ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

```{r parameters_4, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
main_dir = dirname(dirname(getwd()))
print(main_dir)

## common dir for saving plots and model outputs
analysis_dir <- file.path(
  main_dir, "analysis",
  "mixedeffect", "book_iv-cue-stim_dv-outcome", as.character(Sys.Date()))
dir.create(analysis_dir, recursive = TRUE, showWarnings = FALSE)
```

## Cue contrasts

`lmer(Outcome ~ Cue_contrast)`

- IV: Stim X Cue_contrast
- DV: Outcome rating


## load data {.unlisted .unnumbered}
```{r}
df <- readr::read_tsv(file.path(main_dir, "data/beh/sub-all_task-all_events.tsv"))
df.na <- df %>%
  filter(!is.na(outcomerating))
trial_per_condition <- 3
```

## 1. Cue X stim (cue effect)
```{r}
model_summaries <- data.frame()
combined_se_calc_cooksd <- data.frame()
# filter with cue x stim trial combination _____________________________________
for (taskname in c("pain", "vicarious", "cognitive")) {
  # taskname <- "pain"
  # subset dataset per loop based on task name
  df.task <- df.na[df.na$runtype == taskname,]
  df.task_clean <- df.task[complete.cases(df.task$outcomerating), ]
  subjects_with_inadequate_data <- df.task_clean %>%
    group_by(sub,  cue, stimulusintensity) %>% 
    dplyr::summarise(count = n(), .groups = 'drop') %>%
    filter(count < trial_per_condition) %>%
    distinct(sub) %>%
    pull(sub)
  df_filter <- df.task_clean %>%
    filter(!(sub %in% subjects_with_inadequate_data))

print(sprintf("INFO :: After filtering out subjects that have less than %d trials in cell, we have N=%d -> N=%d",trial_per_condition, length(unique(df$sub)), length(unique(df_filter$sub)) ))

beh <- df_filter

subject_varkey <- "sub"
iv <- "cue"; iv_keyword <- "cue"
dv <- "outcomerating"
dv_keyword <- "outcome"
subject <- "sub"
xlab <- ""
ylab <- "Outcome rating"
# exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
w <- 10
h <- 6





# 3. calculate difference scores and summarize _____________________________
beh$run_number <- as.integer(str_extract(beh$run, "\\d+"))

beh$run_order[beh$run_number > 3] <- "a"
beh$run_order[beh$run_number <= 3] <- "b"
sub_diff <- subset(beh, select = c(
    "sub", "ses", "run",
    "runtype", "cue",
    "stimulusintensity", dv
))
subjectwise <- meanSummary(sub_diff, c(
    "sub", "ses", "run",
    "runtype", "cue",
    "stimulusintensity"
), dv)
mean_outcome <- subjectwise[1:(length(subjectwise) - 1)]
wide <- mean_outcome %>%
    spread(cue, mean_per_sub)
wide$diff <- wide$high_cue - wide$low_cue
wide$stim_name[wide$stimulusintensity == "high_stim"] <- "high"
wide$stim_name[wide$stimulusintensity == "med_stim"] <- "med"
wide$stim_name[wide$stimulusintensity == "low_stim"] <- "low"
wide$stim_ordered <- factor(wide$stim_name,
    levels = c("low", "med", "high")
)



# for (taskname in c("pain", "vicarious", "cognitive")) {
# 4. summary stats _____________________________________________________________
subjectwise_diff <- meanSummary(wide, c("sub", "stim_ordered"), "diff")
subjectwise_diff$stim_ordered <- factor(subjectwise_diff$stim_ordered,
    levels = c("low", "med", "high")
)
groupwise_diff <- summarySEwithin(
    data = subjectwise_diff,
    measurevar = "mean_per_sub", # variable created from above
    withinvars = c("stim_ordered"), # iv
    idvar = "sub"
)

# 4. plot results
# 4-1. parameters __________________________________________________________
subjectwise <- subjectwise_diff

groupwise <- groupwise_diff
groupwise$task <- taskname
combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, groupwise)
iv <- "stim_ordered"
subject_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
p1.se <- "se"
dv_keyword = "cuecontrast"
subject <- "sub"
p1.xlab <- ""
p1.ylab <- "Cue effect"
ylim <- c()
ylim <- c(-75,75)
p1.ggtitle <- paste(taskname, " - outcome judgment (degree)")
p1.title <- paste(taskname, " - outcome")
p1.save_fname <- file.path(
    analysis_dir,
    paste("raincloud_task-", taskname, "_rating-",
        dv_keyword, "-cuecontrast_", as.character(Sys.Date()), ".png",
        sep = ""
    )
)
if (any(startsWith(taskname, c("pain", "Pain")))) { # red
    color <- c("#B7021E", "#B7021E", "#B7021E")
} else if (any(startsWith(taskname, c("vicarious", "Vicarious")))) { # green
    color <- c("#22834A", "#22834A", "#22834A")
} else if (any(startsWith(taskname, c("cognitive", "Cognitive")))) { # blue
    color <- c("#0237C9", "#0237C9", "#0237C9")
}

# 4-2. plot rain cloud plots _______________________________________________
g <- plot_halfrainclouds_onefactor(
    subjectwise, groupwise, iv, subject_mean, group_mean, p1.se,
    subject, p1.ggtitle, p1.title, p1.xlab, p1.ylab, taskname, ylim,
    w, h, dv_keyword, color, p1.save_fname
)
g <- g + geom_hline(yintercept = 0, size = 0.5, linetype = "dashed") + 
    theme(aspect.ratio=.8,
          text = element_text(size = 14), # Default text size for the plot
          axis.title = element_text(size = 18, ), # Axis titles
          axis.text = element_text(size = 14), # Axis text (x and y)
          plot.title = element_text(size = 18, hjust = 0.5) # Plot title
          ) 
print(g)
ggsave(p1.save_fname, plot = g)

# 4-3.  plot geom range ____________________________________________________
p2.se <- "sd" # se, sd, ci
p2.xlab <- "Stimulus intensity"
p2.ylab <- "Cue effect"
p2.ggtitle <- paste(taskname, " - cue effect per Stimulus intensity", sep = "")
w <- 5
h <- 5
p2.save_fname <- file.path(
    analysis_dir,
    paste("cueeffect_task-", taskname, "_rating-", dv_keyword, "_",
        as.character(Sys.Date()), ".png",
        sep = ""
    )
)
r <- plot_geompointrange_onefactor(
    subjectwise, groupwise, iv,
    subject_mean, group_mean, p2.se,
    p2.xlab, p2.ylab, color, p2.ggtitle, w, h, p2.save_fname
)
r <- r + geom_hline(yintercept = 0, size = 1, linetype = "dashed") +
  theme(aspect.ratio=.8,
          text = element_text(size = 14), # Default text size for the plot
          axis.title = element_text(size = 18, ), # Axis titles
          axis.text = element_text(size = 14), # Axis text (x and y)
          plot.title = element_text(size = 18, hjust = 0.5) # Plot title
          ) 
  
print(r)
ggsave(p2.save_fname, plot = r)
}

```











### Cue X Stim (2x3) lmer & Raincloud plots

- IV: Cue x stim
- DV: Outcome rating

```{r echo=FALSE, message=FALSE, warning=FALSE}
combined_se_calc_cooksd <- data.frame()
model_summaries <- list()

for (taskname in c("pain", "vicarious", "cognitive")) {


# 1. data parameters ___________________________________________________________
dv_keyword <- "outcomerating"
xlab <- ""
ylab <- "judgment (degree)"
w <- 10
h <- 6
subject <- "sub"

  # subset dataset per loop based on task name
  df.task <- df.na[df.na$runtype == taskname,]
  df.task_clean <- df.task[complete.cases(df.task$outcomerating), ] # drops rows with NA values
  subjects_with_inadequate_data <- df.task_clean %>%
    group_by(sub,  cue, stimulusintensity) %>% 
    dplyr::summarise(count = n(), .groups = 'drop') %>%
    filter(count < trial_per_condition) %>%
    distinct(sub) %>%
    pull(sub)
  df_filter <- df.task_clean %>%
    filter(!(sub %in% subjects_with_inadequate_data))

print(sprintf("INFO :: After filtering out subjects that have less than %d trials in cell, we have N=%d -> N=%d",trial_per_condition, length(unique(df$sub)), length(unique(df_filter$sub)) ))


beh <- df_filter

# 2. contrasts codes _______________________________________________________
beh$stim[beh$stimulusintensity == "low_stim"] <- -0.5
beh$stim[beh$stimulusintensity == "med_stim"] <- 0
beh$stim[beh$stimulusintensity == "high_stim"] <- 0.5

beh$stim_factor <- factor(beh$stimulusintensity)

# ___ 2-1. contrast code 1 linear __________________________________________
beh$STIM_linear[beh$stimulusintensity == "low_stim"] <- -0.5
beh$STIM_linear[beh$stimulusintensity == "med_stim"] <- 0
beh$STIM_linear[beh$stimulusintensity == "high_stim"] <- 0.5

# ___ 2-2. contrast code 2 quadratic _______________________________________
beh$STIM_quadratic[beh$stimulusintensity == "low_stim"] <- -0.33
beh$STIM_quadratic[beh$stimulusintensity == "med_stim"] <- 0.66
beh$STIM_quadratic[beh$stimulusintensity == "high_stim"] <- -0.33

# ___ 2-3. social cude contrast ____________________________________________
beh$CUE_high_gt_low[beh$cue == "low_cue"] <- -0.5
beh$CUE_high_gt_low[beh$cue == "high_cue"] <- 0.5

stim_con1 <- "STIM_linear"
stim_con2 <- "STIM_quadratic"
iv1 <- "CUE_high_gt_low"
dv <- "outcomerating"


# 3. mixed models __________________________________________________________
fullmodel <-
  lmer(
    outcomerating ~ CUE_high_gt_low * STIM_linear + 
      CUE_high_gt_low * STIM_quadratic + 
      (CUE_high_gt_low + STIM_linear| sub),
    data = beh,
    control = lmerControl(
      optimizer = "nloptwrap",
      optCtrl = list(
        algorithm = "NLOPT_LN_BOBYQA",
        maxfun = 1e9,
        maxeval = 1e7,
        xtol_abs = 1e-9,
        ftol_abs = 1e-9
      )
    )
  )
model_summary <- summary(fullmodel)
model_summaries[[taskname]] <- summary(fullmodel)
print(paste0("-------------", taskname, "-------------"))
print(model_summary)

# lmer _________________________________________________________________________

model_summary <- capture.output(summary(fullmodel))

model_savefname <- file.path(
  analysis_dir,
  paste("lmer_task-", taskname, "_cue_on_rating-", dv_keyword, "_",
      as.character(Sys.Date()), ".txt",
      sep = ""
  )
)
write(model_summary, file = model_savefname)
# save equation
write(capture.output(equatiomatic::extract_eq(fullmodel)), file.path(
  analysis_dir,"linear_model_equation.txt"))
  
  
# 4. prep for plots ________________________________________________________
beh$cue_name[beh$cue == "high_cue"] <- "high cue"
beh$cue_name[beh$cue == "low_cue"] <- "low cue"

beh$stim_name[beh$stimulusintensity == "high_stim"] <- "high"
beh$stim_name[beh$stimulusintensity == "med_stim"] <- "med"
beh$stim_name[beh$stimulusintensity == "low_stim"] <- "low"

beh$stim_ordered <- factor(
    beh$stim_name,
    levels = c("low", "med", "high")
)
beh$cue_ordered <- factor(
    beh$cue_name,
    levels = c("low cue", "high cue")
)
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"


# 5. summary statistics ____________________________________________________
outcome_subjectwise <- meanSummary(
    beh,
    c(subject, model_iv1, model_iv2), dv
)
outcome_groupwise <- summarySEwithin(
    data = outcome_subjectwise,
    measurevar = "mean_per_sub",
    withinvars = c(model_iv1, model_iv2), idvar = subject
)
outcome_groupwise$task <- taskname
combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, outcome_groupwise)


# 6. plot related parameters _______________________________________________
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
subject <- "sub"
ggtitle <- paste0(tools::toTitleCase(taskname), " - Outcome Rating (degree)")
title <- paste0(tools::toTitleCase(taskname), " - Outcome")
xlab <- "Stimulus intensity"
ylab <- "Outcome ratings"
ylim <- c(-10,190)
dv_keyword <- "Outcome"

# color differently depending on keyword
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
    color <- c("#1B9E77", "#D95F02")
} else {
    color <- c("#4575B4", "#D73027")
}
plot_savefname <- file.path(
    analysis_dir,
    paste("raincloud_task-", taskname,
        "_rating-", dv_keyword,
        "_", as.character(Sys.Date()), "_cooksd.png",
        sep = ""
    )
)
# 7. ggplot ________________________________________________________________
g <-
  plot_cueexpectancy_twofactor(
    outcome_subjectwise, outcome_groupwise, model_iv1, model_iv2,
    sub_mean, group_mean, se, subject, ggtitle, title,
    xlab, ylab, taskname, ylim,
    w, h, dv_keyword, color, plot_savefname,
    x_hline_position = 3.5,
    x_hline_linetype = "dashed",
    x_hline_nudge_x = 0.1,
    x_hline_textsize = 3,
    legend_factor_levels = c("High cue", "Low cue"),
    legend_factor_colors = c("#D73027", "#4575B4"),
    legend_geom_point_size = 4,
    legend_position = c(-0.1, 0.9),
    legend_widths = c(4, 1)
  )
print(g)
ggsave(plot_savefname, width = w, height = h)
}
print(model_summaries[["pain"]]) #singular
print(model_summaries[["vicarious"]])
print(model_summaries[["cognitive"]]) # singular


```

### Cue X Stim Lineplot {.unlisted .unnumbered}

Instead of the rain cloud plots, here, I plot the lines and confidence interval
for each cue x stim combination. Plotted per task.

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

DATA = as.data.frame(combined_se_calc_cooksd)
color = c( "#4575B4", "#D73027")
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "ci"
dv_keyword = "outcome"
p1 = plot_lineplot_twofactor_subset(DATA, 'pain',
             LINEIV1, LINEIV2, MEAN, ERROR, color, ggtitle = tools::toTitleCase('pain') )
p2 = plot_lineplot_twofactor_subset(DATA,'vicarious',
             LINEIV1, LINEIV2, MEAN, ERROR, color,ggtitle = tools::toTitleCase("vicarious"))
p3 = plot_lineplot_twofactor_subset(DATA, 'cognitive',
             LINEIV1, LINEIV2, MEAN, ERROR, color,ggtitle = tools::toTitleCase('cognitive'))

ggpubr::ggarrange(p1,p2,p3,ncol = 3, nrow = 1, common.legend = TRUE,legend = "bottom")
# plot_filename = file.path(analysis_dir,                        paste('lineplot_task-all_rating-',dv_keyword,'.png', sep = ""))
# ggsave(plot_filename, width = 8, height = 4)
```


### Cue X Stim lmer

```{r}
fullmodel <-
  lmer(
    outcomerating ~ CUE_high_gt_low * STIM_linear + 
      CUE_high_gt_low * STIM_quadratic + 
      (CUE_high_gt_low * STIM_quadratic| sub),
    data = beh
   
  )
```


```{r}
# optimizer
library(parallel)
ncores <- detectCores()
# diff_optims <- allFit(fullmodel, maxfun = 1e5, parallel = 'multicore', ncpus = ncores)
diff_optims <- allFit(fullmodel, maxfun = 1e9)
diff_optims_OK <- diff_optims[sapply(diff_optims, is, "merMod")]
lapply(diff_optims_OK, function(x) x@optinfo$conv$lme4$messages)
```

```{r}
diff_optims <- allFit(fullmodel, maxfun = 1e5)

optimx_options <- c("L-BFGS-B", "nlminb", "nlm", "bobyqa", "nmkb", "hjkb")
for(i in 1:length(optimx_options)){
  print(paste0("Testing optimx: ", optimx_options[i]))
  model_full <-   lmer(
  outcomerating ~ CUE_high_gt_low * STIM_linear + CUE_high_gt_low * STIM_quadratic + (
    CUE_high_gt_low + STIM_quadratic  |
      sub
  ), data = beh,
  control = lmerControl(
    optimizer = "optimx",
    optCtrl = list(
      method = optimx_options[i],
      maxit = 1e9,
      maxfun = 1e9,
      maxeval = 1e7,
      xtol_abs = 1e-9,
      ftol_abs = 1e-9
    )
  ))
                        # control = lmerControl(optimizer = "nloptwrap",
                        #                    optCtrl = list(algorithm = "NLOPT_LN_BOBYQA",
                        #                                   maxfun = 1e9,
                        #                                   maxeval = 1e7,
                        #                                   xtol_abs = 1e-9,
                        #                                   ftol_abs = 1e-9))
  if(is.null(model_full@optinfo$conv$lme4$messages)){
    print(paste0("One of the optimx options, ", optimx_options[i],", worked!"))
    print(model_full)
    break
  }
}
```

```{r}
ggplot(beh, aes(x = sub, y = outcomerating, fill = sub)) +
  geom_boxplot() + 
  geom_jitter(width = .1, alpha = 0, size = 1)
```


## 2. Cue x stim x ses lineplot 
### filter with including session
```{r}
subjects_with_inadequate_ses <- df.na %>%
  group_by(sub, cue, stimulusintensity, ses) %>% 
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 5) %>%
  distinct(sub) %>%
  pull(sub)
df_filter_ses <- df %>%
  filter(!(sub %in% subjects_with_inadequate_ses))

print(sprintf("after filtering out subjects that have less than 3 trials in cell, we have N=%d -> N=%d",length(unique(df$sub)), length(unique(df_filter_ses$sub)) ))
```

```{r}

# taskname <- "pain"
ggtitle <- paste(taskname, " - outcome judgment (degree)")
title <- paste(taskname, " - outcome")
subject <- "subject"

beh <- df_filter_ses
  # 2. contrasts codes _______________________________________________________


# 2. contrasts codes _______________________________________________________
beh$stim[beh$stimulusintensity == "low_stim"] <- -0.5
beh$stim[beh$stimulusintensity == "med_stim"] <- 0
beh$stim[beh$stimulusintensity == "high_stim"] <- 0.5

beh$stim_factor <- factor(beh$stimulusintensity)

# ___ 2-1. contrast code 1 linear __________________________________________
beh$STIM_linear[beh$stimulusintensity == "low_stim"] <- -0.5
beh$STIM_linear[beh$stimulusintensity == "med_stim"] <- 0
beh$STIM_linear[beh$stimulusintensity == "high_stim"] <- 0.5

# ___ 2-2. contrast code 2 quadratic _______________________________________
beh$STIM_quadratic[beh$stimulusintensity == "low_stim"] <- -0.33
beh$STIM_quadratic[beh$stimulusintensity == "med_stim"] <- 0.66
beh$STIM_quadratic[beh$stimulusintensity == "high_stim"] <- -0.33

# ___ 2-3. social cude contrast ____________________________________________
beh$CUE_high_gt_low[beh$cue == "low_cue"] <- -0.5
beh$CUE_high_gt_low[beh$cue == "high_cue"] <- 0.5
# contrast code 1 linear
beh$SES_linear[beh$ses == "ses-01"] <- -0.5
beh$SES_linear[beh$ses == "ses-03"] <- 0
beh$SES_linear[beh$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
beh$SES_quadratic[beh$ses == "ses-01"] <- -0.33
beh$SES_quadratic[beh$ses == "ses-03"] <- 0.64
beh$SES_quadratic[beh$ses == "ses-04"] <- -0.33

beh$CUE_high_gt_low[beh$cue == "high_cue"] <- 0.5
beh$CUE_high_gt_low[beh$cue == "low_cue"] <- -0.5

model.ses <- lmer(outcomerating ~
                        CUE_high_gt_low*STIM_linear*SES_linear +
                        CUE_high_gt_low*STIM_quadratic*SES_linear +
                        CUE_high_gt_low*STIM_linear*SES_quadratic +
                        CUE_high_gt_low*STIM_quadratic*SES_quadratic +
                        (1|sub), data = beh
                  )
# CUE_high_gt_low+STIM+EXPECT_demean
sjPlot::tab_model(model.ses,
                title = "Multilevel-modeling: \nlmer(beta ~ CUE * STIM * SES + (1| sub), data = pvc)",
                CSS = list(css.table = '+font-size: 12;'))

combined_se_calc_cooksd <- data.frame()

for (taskname in c("pain", "vicarious", "cognitive")) {
for (sesname in c("ses-01", "ses-03", "ses-04")) {

  ggtitle <- paste(taskname, " - Outcome rating")
  title <- paste(taskname, " -  Outcome rating")
  subject <- "sub"
  w <- 10
  h <- 6
data.ses <- beh[ beh$ses == sesname & beh$runtype == taskname,]

data.ses <- data.ses %>% filter(!is.na(outcomerating))


  stim_con1 <- "STIM_linear"
  stim_con2 <- "STIM_quadratic"
  iv1 <- "CUE_high_gt_low"
  dv <- "outcomerating"

  # [ MODEL ] _________________________________________________ # nolint
  model_savefname <- file.path(
      analysis_dir,
      paste("lmer_task-", taskname,
          "_rating-", dv_keyword,
          "_", as.character(Sys.Date()), "_cooksd.txt",
          sep = ""
      )
  )

  # [ PLOT ] reordering for plots _________________________ # nolint
  data.ses$cue_name <- NA
  data.ses$cue_name[data.ses$cue == "high_cue"] <- "high cue"
  data.ses$cue_name[data.ses$cue == "low_cue"] <- "low cue"
  #
  data.ses$stim_name[data.ses$stimulusintensity == "high_stim"] <- "high"
  data.ses$stim_name[data.ses$stimulusintensity == "med_stim"] <- "med"
  data.ses$stim_name[data.ses$stimulusintensity == "low_stim"] <- "low"


  data.ses$stim_ordered <- factor(
      data.ses$stim_name,
      levels = c("low", "med", "high")
  )
  data.ses$cue_ordered <- factor(
      data.ses$cue_name,
      levels = c("low cue", "high cue")
  )
  model_iv1 <- "stim_ordered"
  model_iv2 <- "cue_ordered"
subject <- "sub"
  #  [ PLOT ] calculate mean and se  _________________________
  actual_subjectwise <- meanSummary(
      data.ses,
      c(subject, model_iv1, model_iv2), dv
  )
  actual_groupwise <- summarySEwithin(
      data = actual_subjectwise,
      measurevar = "mean_per_sub",
      withinvars = c(model_iv1, model_iv2), idvar = subject
  )
  actual_groupwise$task <- taskname
  actual_groupwise$ses <- sesname
  # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

  combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
 # calculate mean and se
  sub_mean <- "mean_per_sub"
  group_mean <- "mean_per_sub_norm_mean"
  se <- "se"

  ggtitle <- paste(str_to_title(taskname), " - Outcome ", sesname )
  title <- paste(str_to_title(taskname), " - cue level")
  xlab <- "Stimulus intensity"
  ylab <- "Outcome rating (a.u.)"
  ylim <- c(-10,60)
  dv_keyword <- "outcome"
  if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
      color <- c("#1B9E77", "#D95F02")
  } else {
      color <- c("#4575B4", "#D73027")
  } # if keyword starts with
  plot_savefname <- file.path(
      analysis_dir,
      paste("raincloud_task-", taskname,
          "_rating-", dv_keyword,
          "_", as.character(Sys.Date()), "_cooksd.png",
          sep = ""
      )
  )
  g <- plot_halfrainclouds_twofactor(
      actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
      sub_mean, group_mean, se, subject,
      ggtitle, title, xlab, ylab, taskname,ylim,
      w, h, dv_keyword, color, plot_savefname
  )
print(g)
}
}
```



#### session wise line plots {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE}
# lineplot per session

ses.summarystat <- as.data.frame(combined_se_calc_cooksd)
for (taskname in c("pain", "vicarious", "cognitive")) {
  DATA <- ses.summarystat[ses.summarystat$task == taskname,]
  color <- c("#4C77ED", "#ED220D")
  model_iv1 <- "stim_ordered"
  model_iv2 <- "ses_ordered"
  LINEIV1 <- "stim_ordered"
  LINEIV2 <- "cue_ordered"
  MEAN = "mean_per_sub_norm_mean"
  ERROR = "se"
  dv_keyword = "outcomerating"
  p1 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-01" , ],
                               LINEIV1, LINEIV2, MEAN, ERROR, color, 
                               ggtitle = 'ses-01', ylab = "Outcome rating")
  p2 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-03", ],
                               LINEIV1, LINEIV2, MEAN, ERROR, color,
                               ggtitle = 'ses-03', ylab = "Outcome rating")
  p3 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-04", ],
                               LINEIV1, LINEIV2, MEAN,ERROR, color,
                               ggtitle = 'ses-04', ylab = "Outcome rating")
  arranged_plot <- ggpubr::ggarrange(
    p1, p2, p3, ncol = 3, nrow = 1, common.legend = TRUE, legend = "bottom"
  )
  print(arranged_plot)
  # plot_filename = file.path(analysis_dir,
                            # paste('lineplot_task-all_rating-', dv_keyword, '.png', sep = ""))
  # ggsave(plot_filename, arranged_plot, width = 8, height = 4)
}
```


## 3. Individual differences in cue effects

```{r}
combined_cueeffect <- data.frame()

for (taskname in c("pain", "vicarious", "cognitive")) {
subject <- "sub"
dv <- diff
df <- wide[wide$runtype == taskname, ]

# 5. summary statistics ____________________________________________________
avg_within_run <- df %>%
  group_by(sub, ses, run) %>%
  summarise(avg_diff_per_run = mean(diff, na.rm = TRUE)) %>%
  ungroup()

# Average across sessions for each subject
outcome_subjectwise <- avg_within_run %>%
  group_by(sub) %>%
  summarise(avg_diff_per_sub = mean(avg_diff_per_run, na.rm = TRUE)) %>%
  ungroup()

outcome_subjectwise$task <- taskname
combined_cueeffect <- rbind(combined_cueeffect, outcome_subjectwise)
}

# wide form ____________________________________________________________________

wide_df <- combined_cueeffect %>%
  pivot_wider(names_from = task, values_from = avg_diff_per_sub)


# plot cue effects _____________________________________________________________
pv <- plot_ggplot_correlation(data = wide_df, x = 'Vicarious', y = 'Pain', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 45, label_position = 45)
vc <- plot_ggplot_correlation(data = wide_df, x = 'Cognitive', y = 'Vicarious', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 45, label_position = 45)
cp <- plot_ggplot_correlation(data = wide_df, x = 'Pain', y = 'Cognitive', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 45, label_position = 45)


# 4. combine plots and add title _______________________________________________
plots <- ggpubr::ggarrange(pv, vc, cp, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots,top = text_grob("individual differences\n - cue effects from expectation ratings", color = "black", face = "bold", size = 10 ))
save_plotname <- file.path(
  analysis_dir,
  paste("randeffect_scatterplot_task-all_",
      as.character(Sys.Date()), ".png",
      sep = ""
  )
)
plots
ggsave(save_plotname, width = 10, height = 3)
```

## individual differences random effects (DEP)
```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

# 1. stack random effects from each task- .csv ____________________________________
dfP = read.csv(file.path(analysis_dir, paste('randeffect_task-pain_',as.character(Sys.Date()),'_outlier-cooksd.csv',  sep='') ))
dfV = read.csv(file.path(analysis_dir, paste('randeffect_task-vicarious_',as.character(Sys.Date()),'_outlier-cooksd.csv',  sep='') ))
dfC = read.csv(file.path(analysis_dir, paste('randeffect_task-cognitive_',as.character(Sys.Date()),'_outlier-cooksd.csv',  sep='') ))

pvc <- merge_recurse(list(dfP,dfV,dfC))

save_fname = file.path(analysis_dir, paste('randeffect_task-all_',as.character(Sys.Date()),'_outlier-cooksd.csv',  sep='') )
write.csv(pvc, save_fname, row.names = FALSE)


# 2. stack _____________________________________________________________________
pvc_rand_cue_subset <- subset(pvc, select = c(task, subj, CUE_high_gt_low))
pvc_rand_cue <- spread(pvc_rand_cue_subset, key = task, value = CUE_high_gt_low)


# 3. plot individually _________________________________________________________
pv <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'vicarious', y = 'pain', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 20, label_position = 18)
vc <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'cognitive', y = 'vicarious', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 20, label_position = 18)
cp <- plot_ggplot_correlation(data = pvc_rand_cue, x = 'pain', y = 'cognitive', p_acc = 0.001, r_acc = 0.01, limit_min = -20, limit_max = 20, label_position = 18)


# 4. combine plots and add title _______________________________________________
plots <- ggpubr::ggarrange(pv, vc, cp, ncol = 3, nrow = 1, common.legend = FALSE, legend = "bottom")
plots_title <- annotate_figure(plots,top = text_grob("individual differences\n - cue effects from expectation ratings", color = "black", face = "bold", size = 10 ))
save_plotname <- file.path(
  analysis_dir,
  paste("randeffect_scatterplot_task-all_",
      as.character(Sys.Date()), ".png",
      sep = ""
  )
)
plots
ggsave(save_plotname, width = 10, height = 3)
```



## Clinical trials

## cue contrast average across intensity

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

## common dir for saving plots and model outputs
analysis_dir <- file.path(
  main_dir, "analysis",
  "mixedeffect", "model04_iv-cuecontrast_dv-outcome", as.character(Sys.Date()))
dir.create(analysis_dir, recursive = TRUE, showWarnings = FALSE)

for (taskname in c("pain", "vicarious", "cognitive")) {
  subject_varkey <- "sub"
  iv <- "param_cue_type"; iv_keyword <- "cue"
  dv <- "event04_actual_angle"
  dv_keyword <- "outcome"
  subject <- "subject"
  xlab <- ""
  ylab <- "ratings (degree)"
  exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
  w <- 10
  h <- 6
  model_savefname <- file.path(
      analysis_dir,
      paste("lmer_task-", taskname, "_cue_on_rating-", dv_keyword, "_",
          as.character(Sys.Date()), ".txt",
          sep = ""
      )
  )
  # ___ 1) load data _______________________________________________________________ # nolint
  data <- df_load_beh(datadir, taskname, subject_varkey, iv, dv, exclude)
  unique(data$sub)
  data$subject <- factor(data$sub)



  # ___ 3) calculate difference scores and summarize _______________________________ 
  # TODO: within param_run_num
  data$run_order <- NA
  data$run_order[data$param_run_num > 3] <- "a"
  data$run_order[data$param_run_num <= 3] <- "b"
  sub_diff <- subset(data, select = c(
      "subject", "session_id", "run_order",
      "param_task_name", "param_cue_type",
     # "param_stimulus_type",
      dv
  ))
  subjectwise <- meanSummary(sub_diff, c(
      "subject", "session_id", "run_order",
      "param_task_name", "param_cue_type"
      #"param_stimulus_type"
  ), dv)
  mean_outcome <- subjectwise[1:(length(subjectwise) - 1)]
  wide <- mean_outcome %>%
      spread(param_cue_type, mean_per_sub)
  wide$diff <- wide$high_cue - wide$low_cue
  subjectwise_diff <- meanSummary(wide, c("subject"), "diff")
  groupwise_diff <- summarySE(
      data = subjectwise_diff,
      measurevar = "mean_per_sub" # variable created from above
  )
  print(taskname)
  print(groupwise_diff$mean_per_sub_mean)
  print(groupwise_diff$se)


  subjectwise_NDA_high <- meanSummary(wide, c("subject"), "high_cue")
  subjectwise_NDA_low <- meanSummary(wide, c("subject"), "low_cue")
  subjectwise_NDA_low<- na.omit(subjectwise_NDA_low)
  subjectwise_NDA_high<- na.omit(subjectwise_NDA_high)
  groupwise_NDA_high <- summarySE(
      data = subjectwise_NDA_high,
      measurevar = "mean_per_sub" # variable created from above
  )
 groupwise_NDA_low <- summarySE(
      data = subjectwise_NDA_low,
      measurevar = "mean_per_sub" # variable created from above
  )

  print("high vs. low cue")
  print(c("low", groupwise_NDA_low$mean_per_sub_mean, groupwise_NDA_low$se))
  print(c("high", groupwise_NDA_high$mean_per_sub_mean, groupwise_NDA_high$se))


}
```
```{r}
head(data)
```

Question:
If a model fails to converge, what are your steps for checking issues?
Is there a diagnostic plot that would inform me?
I'd like to know what your workflow is

Question: 
If the inclusion of a parameter doesn't make a difference
determined by the anova function
is it safe to remove?
The experiment has these structures and we know that some other dependent variables changed across time, 
so it would be best to include just so that we have starts and compare. 

Question:
what if the levels are somewhat correlated within factors

```{r eval=FALSE, fig.height=10, fig.width=7, include=FALSE}
ggplot(data, aes(y = event04_actual_angle, x = param_cue_type)) +
geom_point() +
xlab("Cue") +
ylab("Outcome rating") +
theme_classic(base_size = 15) +
stat_smooth(method = "lm", formula = 'y ~ x', se=F,fullrange = T) +
facet_wrap(~sub)
```

## LMER
```{r eval=FALSE, include=FALSE}
# 1. remove trials less than 10, per participant _______________________________
data_filtered <- data %>%
group_by(sub) %>%
filter(n() >= 12) %>%
ungroup()  # Remove the grouping specification

# 2. glmmTMB ___________________________________________________________________

# model.cuestim <- glmmTMB::glmmTMB(event04_actual_angle ~ param_cue_type * param_stimulus_type + ( param_cue_type + param_stimulus_type | sub), data = data_filtered)
# summary_model <- summary(model.full)
# anova(model.cuestim, model.cuestimses)
# 3. ICC _______________________________________________________________________
# # Extracting variance components
# random_effect_variance <- summary_model$varcor$cond$sub[1,1] # Adjust index based on your model structure
# residual_variance <- summary_model$sigma^2
# # Calculating ICC
# icc <- random_effect_variance / (random_effect_variance + residual_variance) # 0.38



# model.cuestimexpect <- glmmTMB::glmmTMB(event04_actual_angle ~ param_cue_type * param_stimulus_type * event02_expect_angle +session_id+ ( 0 + param_cue_type * param_stimulus_type * event02_expect_angle| sub) + (1|session_id), data = data_filtered)
# summary(model.cuestimexpect)

model.cuestimses <- glmmTMB::glmmTMB(event04_actual_angle ~ param_cue_type * param_stimulus_type + session_id + ( param_cue_type + param_stimulus_type | sub), data = data_filtered)
summary(model.cuestimses)
summary_cuestimses <- summary(model.cuestimses)
# from vignette ________________________________________________________________
print(paste(">> model Converged?", model.cuestimses$sdr$pdHess ))
(vc.toep <- VarCorr(model.cuestimses))
vc1 <- vc.toep$cond[[1]] ## first term of var-cov for RE of conditional model
summary(diag(vc1))
summary(vc1[row(vc1)!=col(vc1)])
# Compound symmetry
VarCorr(model.cuestimses)
# 3. ICC _______________________________________________________________________
# Extracting variance components
random_effect_variance <- summary_cuestimses$varcor$cond$sub[1,1] # Adjust index based on your model structure
residual_variance <- summary_cuestimses$sigma^2
# Calculating ICC
icc <- random_effect_variance / (random_effect_variance + residual_variance) # 0.38



```

> ICC is 0.38 for a model with cue and stim. 


## cue contrast average across expectation

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}

## common dir for saving plots and model outputs
analysis_dir <- file.path(
  main_dir, "analysis",
  "mixedeffect", "model05_iv-cuecontrast_dv-outcome", as.character(Sys.Date()))
dir.create(analysis_dir, recursive = TRUE, showWarnings = FALSE)

for (taskname in c("pain", "vicarious", "cognitive")) {
  subject_varkey <- "sub"
  iv <- "param_cue_type"; iv_keyword <- "cue"
  dv <- "event02_expect_angle"
  dv_keyword <- "expect"
  subject <- "subject"
  xlab <- ""
  ylab <- "ratings (degree)"
  exclude <- "sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999"
  w <- 10
  h <- 6
  model_savefname <- file.path(
      analysis_dir,
      paste("lmer_task-", taskname, "_cue_on_rating-", dv_keyword, "_",
          as.character(Sys.Date()), ".txt",
          sep = ""
      )
  )
  # ___ 1) load data _______________________________________________________________ # nolint
  data <- df_load_beh(datadir, taskname, subject_varkey, iv, dv, exclude)
  unique(data$sub)
  data$subject <- factor(data$sub)

  # ___ 2) mixed effects model _____________________________________________________ # nolint
  cooksd <- lmer_onefactor_cooksd(
      df = data, taskname, iv, dv, subject_keyword = subject, dv_keyword, model_savefname, print_lmer_output=FALSE
  )
  influential <- as.numeric(names(cooksd)[
      (cooksd > (4 / as.numeric(length(unique(data$subject)))))
  ])
  data_screen <- data[-influential, ]

  # ___ 3) calculate difference scores and summarize _______________________________ # nolint
  # TODO: within param_run_num
  data$run_order[data$param_run_num > 3] <- "a"
  data$run_order[data$param_run_num <= 3] <- "b"
  sub_diff <- subset(data, select = c(
      "subject", "session_id", "run_order",
      "param_task_name", "param_cue_type",
     # "param_stimulus_type",
      dv
  ))
  subjectwise <- meanSummary(sub_diff, c(
      "subject", "session_id", "run_order",
      "param_task_name", "param_cue_type"
      #"param_stimulus_type"
  ), dv)
  mean_outcome <- subjectwise[1:(length(subjectwise) - 1)]
  wide <- mean_outcome %>%
      spread(param_cue_type, mean_per_sub)
  wide$diff <- wide$high_cue - wide$low_cue

  subjectwise_diff <- meanSummary(wide, c("subject"), "diff")
  # subjectwise_diff$stim_ordered <- factor(subjectwise_diff$stim_ordered,
  #     # levels = c("low", "med", "high")
  # )
  subjectwise_diff<- na.omit(subjectwise_diff)
  groupwise_diff <- summarySE(
      data = subjectwise_diff,
      measurevar = "mean_per_sub" # variable created from above
      # withinvars = c("stim_ordered"), # iv
      # idvar = "subject"
  )

  subjectwise_NDA_high <- meanSummary(wide, c("subject"), "high_cue")
  subjectwise_NDA_low <- meanSummary(wide, c("subject"), "low_cue")
  subjectwise_NDA_low<- na.omit(subjectwise_NDA_low)
  subjectwise_NDA_high<- na.omit(subjectwise_NDA_high)
  groupwise_NDA_high <- summarySE(
      data = subjectwise_NDA_high,
      measurevar = "mean_per_sub" # variable created from above
  )
 groupwise_NDA_low <- summarySE(
      data = subjectwise_NDA_low,
      measurevar = "mean_per_sub" # variable created from above
  )
  print(taskname)
  print(groupwise_diff$mean_per_sub_mean)
  print(groupwise_diff$se)
  print("high vs. low cue")
  print(c("low", groupwise_NDA_low$mean_per_sub_mean, groupwise_NDA_low$se))
  print(c("high", groupwise_NDA_high$mean_per_sub_mean, groupwise_NDA_high$se))


}
```

:::: {.refbox}

- https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

::::
