---
title: "book_fMRI_iv_stim_dv-NPS_PE.Rmd"
author: "Heejung Jung"
date: "`r Sys.Date()`"
output: html_document
---

# TODO: 10/10/24 fix the squiggly lines

# [fMRI] NPS \~ PE controlling for partialling out Stimulus effects {#nps_pe_stim}

## What is the purpose of this notebook? {.unlisted .unnumbered}

-   We're curious whether the Neurologic pain signature (NPS) can be explained by prediction errors (PE), after removing for stimulus effects

```{r libraries_nps_stim, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(psych)
library(lme4)
library(dplyr)
library(scico)
devtools::source_url("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(r2mlm)
main_dir <- dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R",
                          full.names=TRUE,
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```

## 0. load data and find intersection between behavioral and nps dataframes

```{r}
# load behavioral, PE data, and NPS data  ______________________________________
analysis_folder <- "fmri_npspebeh"
beh <- readr::read_tsv(file.path(main_dir, "data/beh/sub-all_task-all_events.tsv"))
nps <- read.csv(file.path(main_dir, "analysis/fmri/nilearn/deriv01_signature/rampup_plateau/signature-NPS_sub-all_runtype-pvc_event-stimulus.tsv"), sep = ",")
pe <- read.csv(file.path(main_dir, "data/RL/July2024_Heejung_fMRI_paper/table_pain.csv"), sep = ",")


# reconstruct column based on metadata _________________________________________
pe$singletrial_fname <- sprintf(
  "sub-%04d_%s_run-%02d_runtype-%s_event-stimulus_trial-%03d_cuetype-%s_stimintensity-%s.nii.gz", 
  pe$src_subject_id, 
  pe$ses, 
  pe$param_run_num, 
  pe$runtype, 
  pe$trial_index -1,
  gsub("_cue", "", pe$param_cue_type),       # Remove "_cue" from param_cue_type
  gsub("_stim", "", pe$param_stimulus_type)  # Remove "_stim" from param_stimulus_type
)


# merge dataframes and prevent duplicate columns _______________________________
dfmerge <- beh %>%
  inner_join(nps, by = "singletrial_fname") %>%
  inner_join(pe %>% select(-c(ses, runtype, trial_index, expectrating, expectlabel, outcomerating, outcomelabel)), by = "singletrial_fname")
```

```{r}
# fit lmer 
# NPS ~ stimeffect
# remove first trial index
# get resid
# resid ~ PE?

# 0. filter data
data <-dfmerge[dfmerge$runtype == "pain" ,]

# contrast code ________________________________________________________________
data$stim <- NA; data$STIM_linear <- NA; data$STIM_quadratic <- NA; 
data$CUE_high_gt_low <- NA;
data$SES_linear <- NA;data$SES_quadratic <- NA
data$stim[data$stimulusintensity == "low_stim"] <-  -0.5 # social influence task
data$stim[data$stimulusintensity == "med_stim"] <- 0 # no influence task
data$stim[data$stimulusintensity == "high_stim"] <-  0.5 # no influence task

data$STIM <- factor(data$stimulusintensity)

# contrast code 1 linear
data$STIM_linear[data$stimulusintensity == "low_stim"] <- -0.5
data$STIM_linear[data$stimulusintensity == "med_stim"] <- 0
data$STIM_linear[data$stimulusintensity == "high_stim"] <- 0.5

# contrast code 2 quadratic
data$STIM_quadratic[data$stimulusintensity == "low_stim"] <- -0.33
data$STIM_quadratic[data$stimulusintensity == "med_stim"] <- 0.66
data$STIM_quadratic[data$stimulusintensity == "high_stim"] <- -0.33

# social cude contrast
data$CUE_high_gt_low[data$cue == "low_cue"] <-  -0.5 # social influence task
data$CUE_high_gt_low[data$cue == "high_cue"] <-  0.5 # no influence task

data$EXPECT <- data$expectrating
data$OUTCOME <- data$outcomerating


data$SES_linear[data$ses == "ses-01"] <- -0.5
data$SES_linear[data$ses == "ses-03"] <- 0
data$SES_linear[data$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
data$SES_quadratic[data$ses == "ses-01"] <- -0.33
data$SES_quadratic[data$ses == "ses-03"] <- 0.66
data$SES_quadratic[data$ses == "ses-04"] <- -0.33

stim_con1 <- "STIM_linear"
stim_con2 <- "STIM_quadratic"
iv1 <- "CUE_high_gt_low"
dv <- "NPS"
dv_keyword <- "NPS"


# filter data only if there are three trials per cue x stim cell
subjects_with_inadequate_data <- data %>%
  group_by(sub, CUE_high_gt_low, STIM_linear) %>% #SES_linear, 
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 3) %>%
  distinct(sub) %>%
  pull(sub)
df_filter <- data %>%
  filter(!(sub %in% subjects_with_inadequate_data))


# filter data - remove first trials
df_filter.no1 <- df_filter[df_filter$trial_index != 1, ]

df_clean.no1 <- df_filter.no1 %>%
  group_by(sub) %>%
  mutate(trial_index_sub = row_number()) %>%
  ungroup()

# lmer :: NPS, fit with PE _______________________________________
model.npspe <- lmer(NPS ~ PE_mdl2 + (PE_mdl2|sub), data = df_clean.no1)
cat(strrep("-", 50),"\nmodel: NPS ~ PE + (PE|sub)\n",strrep("-", 50),"\n")
summary(model.npspe)


# lmer :: fit NPS with stim ____________________________________________________
model.npsstimresid <- lmer(NPS ~ STIM_linear + STIM_quadratic + (STIM_linear|sub), data = df_clean.no1)
cat(strrep("-", 50),"\nmodel: NPS ~ stim + (stim|sub)\n",strrep("-", 50),"\n")
summary(model.npsstimresid)

# residuals, after accounting for stimulus effects!
df_clean.no1 <- df_clean.no1 %>%
  mutate(NPSresid = resid(model.npsstimresid))

# lmer :: stim residual NPS, fit with PE _______________________________________
model.residnpspe <- lmer(NPSresid ~ PE_mdl2 + (PE_mdl2|sub), data = df_clean.no1)
cat(strrep("-", 50),"\nmodel: NPS residuals ~ PE + (PE|sub)\n",strrep("-", 50),"\n")
summary(model.residnpspe)

```

## plot NPS as a function of PE
## plot residual values per subject
```{r}

df_clean.no1 <- df_clean.no1 %>%
  arrange(sub, trial_index_sub, PE_mdl2) %>%
  mutate(fit1.m = predict(model.npspe, re.form = NA),
         fit1.c = predict(model.npspe, re.form = NULL),
         resid1 = resid(model.npspe))
n_subjects <- length(unique(df_clean.no1$sub))
batlow_colors <- scico(n_subjects, palette = "batlow")

df_clean.no1 %>%
  ggplot(aes(x = PE_mdl2, y = fit1.m + resid1)) +
  scale_color_manual(values = batlow_colors) +
  geom_point(pch = 16, aes(col = sub, group = sub), size = .25, alpha = .5) + 
  geom_line(aes(y = fit1.c, color = sub, group = sub), size = .5, alpha = .75) +  # Group lines by subject
  geom_line(aes(y = fit1.m), col = 1, size = 1.5, alpha = .9) +  # Group-level fit
  theme_classic2() +
  labs(
    title = "Scatter Plot with Individual and Group-Level Slopes",
    x = "PE_mdl2",
    y = "Fitted Values"
  ) 
# +
# coord_cartesian(ylim = c(-20, 20)) 



```

## plot NPSresidualstim as a function of PE values per subject
```{r}


summary(model.residnpspe)$varcor
df_clean.no1 <- df_clean.no1 %>%
  arrange(sub, trial_index_sub, PE_mdl2) %>%
  mutate(fit2.m = predict(model.residnpspe, re.form = NA),
         fit2.c = predict(model.residnpspe, re.form = NULL),
         resid2 = resid(model.residnpspe))

df_clean.no1 %>%
  ggplot(aes(x = PE_mdl2, y = fit2.m + resid2)) +
  geom_point(pch = 16, aes(col = sub, group = sub), size = .25) + 
  geom_line(aes(y = fit2.c, color = sub, group = sub), size = .5) +  # Group lines by subject
  #geom_line(aes(y = fit2.m), col = 1, size = 1) +  # Group-level fit
  theme_minimal() +
  labs(
    title = "Scatter Plot with Individual and Group-Level Slopes",
    x = "PE_mdl2",
    y = "Fitted Values"
  ) +
coord_cartesian(ylim = c(-20, 20))


```


