# [fMRI] NPSneg ~ session {#NPSneg_ses}

## What is the purpose of this notebook? {.unlisted .unnumbered}

- Here, I model NPSneg dot products as a function of cue, stimulus intensity and expectation ratings.
- One of the findings is that low cues lead to higher NPSneg dotproducts in the high intensity group, and that this effect becomes non-significant across sessions.

```{r libraries_NPSneg_stim, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(lme4)
library(optimx)
library(minqa)
library(dfoptim)
library(tidyverse)
library(psych)
library(reshape)
library(plyr)
library(dplyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)

library(ggpubr)
library(r2mlm)
library(effectsize)
library(devtools)
options(es.use_symbols = TRUE) # get nice symbols when printing! (On Windows, requires R >= 4.2.0)
library(EMAtools)
library(emmeans)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(plotly)
library(DT)
library(raincloudplots)

# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/R_rainclouds.R")
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/summarySE.R")

devtools::source_url("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(r2mlm)
main_dir <- dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R",
                          full.names=TRUE,
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```

############################################# {.unlisted .unnumbered}

## 0. load data and find intersection between behavioral and NPSneg dataframes

############################################# {.unlisted .unnumbered}

```{r}
# load events.tsv
analysis_folder <- "fmri_NPSneg"
beh <- readr::read_tsv(file.path(main_dir, "data/beh/sub-all_task-all_events.tsv"))
# load NPSneg tsvv/Volumes/spacetop_projects_cue/analysis/fmri/nilearn/deriv01_signature/rampup_plateau/signature-NPSnegpos_sub-all_runtype-pvc_event-stimulus.tsv
NPSneg <- read.csv(file.path("/Volumes/spacetop_projects_cue/analysis/fmri/nilearn/deriv01_signature/rampup_plateau/signature-NPSneg_sub-all_runtype-pvc_event-stimulus.tsv"))

# intersect
# Assuming df1 and df2 are your data frames and 'key_column' is the name of your key column
df_merge <- inner_join(beh, NPSneg, by = "singletrial_fname")
```

```{r}
data <-df_merge[df_merge$runtype == "pain" ,]

# contrast code ________________________________________________________________
data$stim <- NA; data$STIM_linear <- NA; data$STIM_quadratic <- NA;
data$CUE_high_gt_low <- NA;
data$SES_linear <- NA;data$SES_quadratic <- NA
data$stim[data$stimulusintensity == "low_stim"] <-  -0.5 # social influence task
data$stim[data$stimulusintensity == "med_stim"] <- 0 # no influence task
data$stim[data$stimulusintensity == "high_stim"] <-  0.5 # no influence task

data$STIM <- factor(data$stimulusintensity)

# contrast code 1 linear
data$STIM_linear[data$stimulusintensity == "low_stim"] <- -0.5
data$STIM_linear[data$stimulusintensity == "med_stim"] <- 0
data$STIM_linear[data$stimulusintensity == "high_stim"] <- 0.5

# contrast code 2 quadratic
data$STIM_quadratic[data$stimulusintensity == "low_stim"] <- -0.33
data$STIM_quadratic[data$stimulusintensity == "med_stim"] <- 0.66
data$STIM_quadratic[data$stimulusintensity == "high_stim"] <- -0.33

# social cude contrast
data$CUE_high_gt_low[data$cue == "low_cue"] <-  -0.5 # social influence task
data$CUE_high_gt_low[data$cue == "high_cue"] <-  0.5 # no influence task

data$EXPECT <- data$expectrating
data$OUTCOME <- data$outcomerating


data$SES_linear[data$ses == "ses-01"] <- -0.5
data$SES_linear[data$ses == "ses-03"] <- 0
data$SES_linear[data$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
data$SES_quadratic[data$ses == "ses-01"] <- -0.33
data$SES_quadratic[data$ses == "ses-03"] <- 0.66
data$SES_quadratic[data$ses == "ses-04"] <- -0.33

stim_con1 <- "STIM_linear"
stim_con2 <- "STIM_quadratic"
iv1 <- "CUE_high_gt_low"
dv <- "NPSneg"
dv_keyword <- "NPSneg"

# filter data __________________________________________________________________
# Make sure that each condition cell has adequate amount of trials

subjects_with_inadequate_data <- data %>%
  group_by(sub, CUE_high_gt_low, STIM_linear) %>% #SES_linear,
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 3) %>%
  distinct(sub) %>%
  pull(sub)
df_filter <- data %>%
  filter(!(sub %in% subjects_with_inadequate_data))

print(sprintf("after filtering out subjects that have less than 3 trials in cell, we have N=%d -> N=%d",length(unique(data$sub)), length(unique(df_filter$sub)) ))
```

### QC. check NPSneg distribution

```{r}
df_filter.NA <- df_filter %>% filter(!is.na(NPSneg))  # Remove NA values
head(df_filter.NA)
# Sort the data by median "outcome" in ascending order
sorted_data <- df_filter.NA %>%
  group_by(sub) %>%
  dplyr::summarize(median_NPSneg = median(NPSneg, na.rm = TRUE)) %>%
  arrange(median_NPSneg) %>%
  select(sub)

# Reorder the "subject" factor based on the sorted order
df_filter.NA$sub <- factor(df_filter.NA$sub, levels = sorted_data$sub)

# Create the ggplot
g <- ggplot(df_filter.NA, aes(x = sub, y = NPSneg, fill = sub)) +
  geom_boxplot(outlier.shape = NA, width = 1.2, position = position_dodge(2)) +
  geom_jitter(width = .1, alpha = 0, size = 1) +
  labs(x = "Subject", y = "NPSneg") +
  theme_classic() +
  theme(legend.position = "none") +
  scale_x_discrete(breaks = NULL)

# Convert ggplot object to a plotly object with hover information
g_plotly <- ggplotly(ggplot_largetext(g), tooltip = c("x", "y"))
g_plotly
```

```{r function::summary_for_plots_pvc, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
summary_for_plots_PVC <- function(df, groupwise_measurevar, subject_keyword, model_iv1, model_iv2, dv) {
    #  [ PLOT ] calculate mean and se  _________________________
    subjectwise <- meanSummary(
        df,
        c(subject_keyword, model_iv1, model_iv2), dv
    )
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = groupwise_measurevar,
        withinvars = c(model_iv1, model_iv2), idvar = subject_keyword
    )

    return(list(subjectwise,groupwise))
}
```

```{r function::simple_contrasts_singletrial, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
simple_contrasts_singletrial <- function(df) {
# [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
df$STIM <- factor(df$stimulusintensity)

# contrast code 1 linear
df$STIM_linear[df$stimulusintensity == "low"] <-  -0.5
df$STIM_linear[df$stimulusintensity == "med"] <-  0
df$STIM_linear[df$stimulusintensity == "high"] <-  0.5

# contrast code 2 quadratic
df$STIM_quadratic[df$stimulusintensity == "low"] <-  -0.33
df$STIM_quadratic[df$stimulusintensity == "med"] <-  0.66
df$STIM_quadratic[df$stimulusintensity == "high"] <-  -0.33

# cue contrast
df$CUE_high_gt_low[df$cue == "low"] <-  -0.5 # social influence task
df$CUE_high_gt_low[df$cue == "high"] <-  0.5 # no influence task

df$stim_ordered <- factor(
        df$stimulusintensity,
        levels = c("low", "med", "high")
    )

df$cue_name[df$cuetype == "low"] <- "low"
df$cue_name[df$cuetype == "high"] <- "high"

df$cue_ordered <- factor(
        df$cue_name,
        levels = c("low", "high")
    )
return(df)
}
```

```{r function::NPSneg_lineplot_34, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
two_factor_lineplot <-
  function(df, iv1, iv2, mean, error, xlab, ylab) {
    g <- ggplot(
      data = df,
      aes(
        x = .data[[iv1]],
        y = .data[[mean]],
        group = factor(.data[[iv2]]),
        color = factor(.data[[iv2]])
      ),
      cex.lab = 1.5,
      cex.axis = 2,
      cex.main = 1.5,
      cex.sub = 1.5
    ) +
      geom_errorbar(aes(
        ymin = (.data[[mean]] - .data[[error]]),
        ymax = (.data[[mean]] + .data[[error]])
      ), width = .1) +
      geom_line() +
      geom_point() +
      ggtitle(ggtitle) +
      xlab(xlab) +
      ylab(ylab) +
      #scale_color_manual(values = color) +
      theme_classic() +

      theme(aspect.ratio = .6) +
      expand_limits(x = 3.25) +
      #guides(fill = "none") +
      #guides(color = TRUE) +
      #guides(fill = guide_legend(title = "title")) +
      #scale_fill_manual(values = color) +
      scale_color_manual("",
                         values =  c(
                           "pain" = "#941100",
                           "vicarious" = "#008F51",
                           "cognitive" = "#011891"
                         )) +
      theme(
        legend.position = c(.99, .99),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      theme(legend.key = element_rect(fill = "white", colour = "white")) +
      theme_bw()

    return(g)
  }
```

### Contrast weight table {.unlisted .unnumbered}

```{r echo=FALSE}
tab <- matrix(c(0, .5, -.5,
                .66, -.34, -.34), ncol=3, byrow=TRUE)
colnames(tab) <- c('pain','vicarious','cognitive')
rownames(tab) <- c('task_V_gt_C','task_P_gt_VC')
kableExtra::kable_styling(
  knitr::kable(
    tab, caption = "Contrast weights", "html"),
  "striped", position = "left", font_size = 15)
```

############################################# {.unlisted .unnumbered}

## 2. NPSneg ~ paintask: 2 cue x 3 stimulus_intensity

############################################# {.unlisted .unnumbered}

### Q. Within pain task, Does stimulus intenisty level and cue level significantly predict NPSneg dotproducts? {.unlisted .unnumbered}

# 03/10/2024

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
combined_se_calc_cooksd <- data.frame()
# combined_psig <- data.frame()
taskname = "pain"
dv_keyword <- "NPSneg"
ggtitle <- paste(taskname, " - NPSneg (degree)")
title <- paste(taskname, " - NPS dot product values")
subject <- "sub"
w <- 10
h <- 6
# p.sig <- df_merge[df_merge$runtype == "pain" ,]

analysis_dir <-
  file.path(main_dir,
            "analysis",
            "mixedeffect",
            analysis_folder,
            as.character(Sys.Date())) # nolint
dir.create(analysis_dir,
           showWarnings = FALSE,
           recursive = TRUE)
savedir <- analysis_dir
# combined_psig <-
#   rbind(combined_psig, p.sig)


# lmer model __________________________________________________________________
model_savefname <- file.path(
  analysis_dir,
  paste(
    "lmer_task-",taskname,"_rating-",dv_keyword,"_",as.character(Sys.Date()),"_cooksd.txt",
    sep = ""
  )
)


# [ PLOT ] reordering for plots _________________________ # nolint
df_filter$cue_name[df_filter$cue == "high_cue"] <-
  "high cue"
df_filter$cue_name[df_filter$cue == "low_cue"] <-
  "low cue"

df_filter$stim_name[df_filter$stimulusintensity == "high_stim"] <-
  "high"
df_filter$stim_name[df_filter$stimulusintensity == "med_stim"] <-
  "med"
df_filter$stim_name[df_filter$stimulusintensity == "low_stim"] <-
  "low"

# DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

df_filter$stim_ordered <- factor(df_filter$stim_name,
                                   levels = c("low", "med", "high"))
df_filter$cue_ordered <- factor(df_filter$cue_name,
                                  levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"

#  [ PLOT ] calculate mean and se  _________________________
NPSnegstimcue_subjectwise <- meanSummary(df_filter,
                                      c(subject, model_iv1, model_iv2), dv)
NPSnegstimcue_groupwise <- summarySEwithin(
  data = NPSnegstimcue_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
NPSnegstimcue_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

combined_se_calc_cooksd <-
  rbind(combined_se_calc_cooksd, NPSnegstimcue_groupwise)
# calculate mean and se
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
subject <- "sub"
ggtitle <- paste(taskname, " - NPSneg")
title <- paste(taskname, " - NPSneg")
xlab <- ""
ylab <- "NPSneg (degree)"
ylim <- c(-10, 60)
dv_keyword <- "NPSneg"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#4274AD", "#C5263A")
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), ".png",
    sep = ""
  )
)
g <- plot_halfrainclouds_twofactor(
  NPSnegstimcue_subjectwise,
  NPSnegstimcue_groupwise,
  model_iv1,
  model_iv2,
  sub_mean,
  group_mean,
  se,
  subject,
  ggtitle,
  title,
  xlab,
  ylab,
  taskname,
  ylim,
  w,
  h,
  dv_keyword,
  color,
  plot_savefname
)
g
```

### Lineplots with only low cue {.unlisted .unnumbered}

```{r echo=FALSE, warning=FALSE}
subsetNPSneg <- NPSnegstimcue_groupwise[NPSnegstimcue_groupwise$cue_ordered == "low cue",]
g <- plot_lineplot_twofactor_subset(subsetNPSneg, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#5D5C5C", "#D73027"), ggtitle = "Within pain task: NPSneg dotproducts as a function of stimulus intensity level and cue",
                        xlab = "Stimulus intensity", ylab = "NPSneg (dot product)")
g + theme(aspect.ratio=.8)
```

### Lineplots {.unlisted .unnumbered}

```{r echo=FALSE, warning=FALSE}
g <- plot_lineplot_twofactor_subset(NPSnegstimcue_groupwise, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#5D5C5C","high cue" = "#D73027"), ggtitle = "Within pain task: NPSneg dotproducts as a function of stimulus intensity level and cue",
                        xlab = "Stimulus intensity", ylab = "NPSneg (dot product)")
g + theme(aspect.ratio=.8)
```

### Lineplots tilt axis {.unlisted .unnumbered}

```{r echo=FALSE, warning=FALSE}
g <- plot_lineplot_twofactor(NPSnegstimcue_groupwise,
                        iv2 = "stim_ordered", iv1 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("high" = "red",
                                  "med" = "orange",
                                  "low" = "yellow"),
                        ggtitle = "Within pain task: NPSneg dotproducts as a function of stimulus intensity level and cue",
                        xlab = "Stimulus intensity", ylab = "NPSneg (dot product)")
g + theme(aspect.ratio=.8)
```

## Table lmer. Linear model results (NPSneg ~ paintask: 2 cue x 3 stimulus_intensity)

> modeling random slopes of cue and stimulus intensity, we find a signfiicant effect of cue and stimulus effect on NPS negative weights (bcue = 0.03, p < .05, bstimlinear = -0.14, p < .001) Model used optimizer Nelder Mead.

```{r echo=TRUE, message=FALSE, warning=TRUE, paged.print=FALSE}

model.NPSnegcuestim <- lmer(NPSneg ~
                          CUE_high_gt_low*STIM_linear +
                            CUE_high_gt_low * STIM_quadratic +
                          (CUE_high_gt_low+STIM_linear|sub), data = df_filter,
                          control = lmerControl(optimizer = "Nelder_Mead")
                    )
sjPlot::tab_model(model.NPSnegcuestim,
                  title = "Multilevel-modeling: \nlmer(NPSneg ~ CUE * STIM + (CUE + STIM | sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

### optimizers

```{r}

library(parallel)
ncores <- detectCores()
diff_optims <- allFit(model.NPSnegcuestim, maxfun = 1e5, parallel = 'multicore', ncpus = ncores)
# diff_optims <- allFit(model.full, maxfun = 1e5)
diff_optims_OK <- diff_optims[sapply(diff_optims, is, "merMod")]
lapply(diff_optims_OK, function(x) x@optinfo$conv$lme4$messages)
```

```{r}
diff_optims <- allFit(model.NPSnegcuestim, maxfun = 1e5)
```

### model converge [OK: optimizer nmkbw]

```{r}
library(optimx)
model.NPSnegcuestim <- lmer(NPSneg ~
                          CUE_high_gt_low*STIM_linear +
                          CUE_high_gt_low*STIM_quadratic +
                          (CUE_high_gt_low + STIM_linear|sub), data = df_filter,
                                    control=lmerControl(optimizer="nmkbw"
                                 ))
                         # control = lmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 1e5)))

summary(model.NPSnegcuestim)
```

```
lmer(NPSneg ~
                          CUE_high_gt_low*STIM_linear +CUE_high_gt_low * STIM_quadratic +
                          (CUE_high_gt_low+STIM|sub), data = data
                    )
```

#### Linear model eta-squared {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.NPSnegcuestim, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
#parameters::model_parameters(model.NPSnegcuestim)
```

#### Linear model Cohen's d: {.unlisted .unnumbered}

> - NPSneg cue d = 0.21

- NPSneg stimulus_intensity d = -1.42

```{r echo=FALSE, message=FALSE, warning=TRUE, paged.print=FALSE}

kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.NPSnegcuestim, data, type = "lme4"),
    "html"), "striped", position = "left", font_size = 12)
```

############################################# {.unlisted .unnumbered}

## 3. NPSneg ~ SES _ CUE _ STIM

############################################# {.unlisted .unnumbered}

### Q. Is the cue effect on NPSneg different across sessions? {.unlisted .unnumbered}

> Quick answer: Yes, the cue effect in session 1 (for high intensity group) is significantly different; whereas this different becomes non significant in session 4.
> To unpack, a participant was informed to experience a low stimulus intensity, when in fact they were delivered a high intensity stimulus. This violation presumably leads to a higher NPSneg response, given that they were delivered a much painful stimulus than expected. The fact that the cue effect is almost non significant during the last session indicates that the cue effects are not just an anchoring effect.

### filter per sub/cue/stim/ses at least 3 trials per combination {.unlisted .unnumbered}

```{r}
subjects_with_inadequate_data <- data %>%
  group_by(sub, CUE_high_gt_low, STIM_linear, SES_linear) %>%
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 3) %>%
  distinct(sub) %>%
  pull(sub)
df_filter_ses <- data %>%
  filter(!(sub %in% subjects_with_inadequate_data))

print(sprintf("after filtering out subjects that have less than 3 trials in cell, we have N=%d -> N=%d",length(unique(data$sub)), length(unique(df_filter_ses$sub)) ))
```

### Table lmer. NPS ~ SES

> Modeling random slopes of cue, ses, stimulus intensity, we find signficant cue effects (b = 0.04, p < .05), stimulus effects (b = -0.13, p < .001) and session effects (b = -0.04, p < .05). However, the session wise interaction was marginally signficant; cue x ses (quadratic): b = 0.062, se = 0.034, t(4570) = 1.784, p = 0.075 stimlinear x sesquadratic b = 0.078, se = 0.043, t(4484) = 1.827, p = 0.067.

b se
CUE_high_gt_low:SES_quadratic 6.200e-02 3.475e-02
STIM_linear:SES_quadratic 7.809e-02 4.275e-02
df t p
CUE_high_gt_low:SES_quadratic 4.570e+03 1.784 0.0745
STIM_linear:SES_quadratic 4.484e+03 1.827 0.0678

Using NLOPT_LN_NELDERMEAD nloptwrap optimizer

```{r}
model.NPSnegses <- lmer(
  NPSneg ~
    CUE_high_gt_low * STIM_linear * SES_linear +
    CUE_high_gt_low * STIM_quadratic * SES_linear +
    CUE_high_gt_low * STIM_linear * SES_quadratic +
    CUE_high_gt_low * STIM_quadratic * SES_quadratic +
    (CUE_high_gt_low + SES_quadratic + STIM_linear |
       sub),
  data = df_filter_ses,
  control = lmerControl(
    optimizer = "nloptwrap",
    optCtrl = list(
      algorithm = "NLOPT_LN_NELDERMEAD",
      maxfun = 1e9,
      maxeval = 1e7,
      xtol_abs = 1e-9,
      ftol_abs = 1e-9
    )
  )
)

summary(model.NPSnegses)
# CUE_high_gt_low+STIM+EXPECT_demean
sjPlot::tab_model(model.NPSnegses,
                  title = "Multilevel-modeling: \nlmer(NPSneg ~ CUE * STIM * SES + (CUE + SES + STIM| sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
```

```{r}
library(parallel)
ncores <- detectCores()
diff_optims <- allFit(model.NPSnegses, maxfun = 1e5, parallel = 'multicore', ncpus = ncores)
# diff_optims <- allFit(model.full, maxfun = 1e5)
diff_optims_OK <- diff_optims[sapply(diff_optims, is, "merMod")]
lapply(diff_optims_OK, function(x) x@optinfo$conv$lme4$messages)
```

### model converge [OK: optimizer nmkbw]

### convergence

```{r}
optimx_options <- c("L-BFGS-B", "nlminb", "nlm", "bobyqa", "nmkb", "hjkb")
for(i in 1:length(optimx_options)){
  print(paste0("Testing optimx: ", optimx_options[i]))
  model_flex <-   lmer(
    NPSneg ~
      CUE_high_gt_low * STIM_linear * SES_linear +
      CUE_high_gt_low * STIM_quadratic * SES_linear +
      CUE_high_gt_low * STIM_linear * SES_quadratic +
      CUE_high_gt_low * STIM_quadratic * SES_quadratic +
      (CUE_high_gt_low + SES_linear + STIM_linear |
         sub),
    data = df_filter_ses,
    control = lmerControl(
      optimizer = "optimx",
      optCtrl = list(
        method = optimx_options[i],
        maxit = 1e9,
        maxfun = 1e9,
        maxeval = 1e7,
        xtol_abs = 1e-9,
        ftol_abs = 1e-9
      )
    )
  )
        # control = lmerControl(optimizer = "nloptwrap",
        #                    optCtrl = list(algorithm = "NLOPT_LN_BOBYQA",
        #                                   maxfun = 1e9,
        #                                   maxeval = 1e7,
        #                                   xtol_abs = 1e-9,
        #                                   ftol_abs = 1e-9))
  if(is.null(model_flex@optinfo$conv$lme4$messages)){
    print(paste0("One of the optimx options, ", optimx_options[i],", worked!"))
    print(model_flex)
    break
  }
}
```

#### eta squared {.unlisted .unnumbered}

```{r echo=FALSE, warning=TRUE}
kableExtra::kable_styling(
  knitr::kable(
    eta_squared(model.NPSnegses, partial = TRUE), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

#### Cohen's d {.unlisted .unnumbered}

> cue: stim: -1.39

```{r echo=FALSE, warning=TRUE}
kableExtra::kable_styling(
  knitr::kable(
    lme.dscore(model.NPSnegses, df_filter, type = "lme4"), # MODIFY
    "html"), "striped", position = "left", font_size = 12)
```

#### Session wise plots {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

combined_se_calc_cooksd <- data.frame()
for (sesname in c("ses-01", "ses-03", "ses-04")) {
taskname = "pain"
    ggtitle <- paste(taskname, " - actual judgment (degree)")
    title <- paste(taskname, " - actual")
    subject <- "sub"
    w <- 10
    h <- 6
s1.sig <- df_filter_ses[df_filter_ses$runtype == "pain" & df_filter_ses$ses == sesname,]
data <- s1.sig


stim_con1 <- "STIM_linear"
stim_con2 <- "STIM_quadratic"
iv1 <- "CUE_high_gt_low"
dv <- "NPSneg"

    # [ MODEL ] _______________________________________________________________
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )


    # [ PLOT ] reordering for plots _________________________ # nolint
    data$cue_name[data$cue == "high_cue"] <- "high cue"
    data$cue_name[data$cue == "low_cue"] <- "low cue"

    data$stim_name[data$stimulusintensity == "high_stim"] <- "high"
    data$stim_name[data$stimulusintensity == "med_stim"] <- "med"
    data$stim_name[data$stimulusintensity == "low_stim"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data$stim_ordered <- factor(
        data$stim_name,
        levels = c("low", "med", "high")
    )
    data$cue_ordered <- factor(
        data$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    actual_groupwise$ses <- sesname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
   # calculate mean and se
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(str_to_title(taskname), " - NPSneg Cooksd removed ", sesname )
    title <- paste(str_to_title(taskname), " - cue level")
    xlab <- ""
    ylab <- "NPSneg (degree)"
    ylim <- c(-10,60)
    dv_keyword <- "NPSneg"
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4274AD", "#C5263A")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_halfrainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
print(g)
}
```

#### session wise line plots {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE}
# lineplot per session

DATA = as.data.frame(combined_se_calc_cooksd)
color = c("#4C77ED", "#ED220D")
model_iv1 <- "stim_ordered"
model_iv2 <- "ses_ordered"
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "se"
dv_keyword = "actual"
p1 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-01",],
               LINEIV1, LINEIV2, MEAN, ERROR, color, ggtitle = 'ses-01',
               ylab = "NPSneg (dot products)" )
p2 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-03",],
               LINEIV1, LINEIV2, MEAN, ERROR, color, ggtitle = 'ses-03',
               ylab = "NPSneg (dot products)")
p3 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-04",],
               LINEIV1, LINEIV2, MEAN, ERROR, color,ggtitle = 'ses-04',
               ylab = "NPSneg (dot products)")

ggpubr::ggarrange(p1,p2,p3,ncol = 3, nrow = 1, common.legend = TRUE,legend = "bottom")

plot_filename = file.path(analysis_dir,
                          paste('lineplot_task-all_rating-',dv_keyword,'.png', sep = ""))
ggsave(plot_filename, width = 8, height = 4)
```

---
