# [physio] SCL singletrial {#glm_SCL}

In this notebook, we model SCR reponses trial-by-trial. Using canonical SCR functions,
we extract beta coefficients, which allow us to explore the relationship between skin conductance and
SIIPS, NPS, PE, and outcome ratings.

```{r message=TRUE, warning=TRUE, include=FALSE}
library(car)
library(psych)
library(reshape)
library(plyr); library(dplyr)
# library(tidyselect)
library(tidyr)
library(stringr)
library(lme4)
library(lmerTest)
library(gghalves)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
main_dir = dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, "scripts/step02_R/utils"),
                          pattern="*.R",
                          full.names=TRUE,
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

```{r function::simple_contrasts_singletrial, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
simple_contrasts_singletrial <- function(df) {
# [ CONTRASTS ]  ________________________________________________________________________________ # nolint
# contrast code ________________________________________
df$cue_factor <- factor(df$cue)

# # contrast code 1 linear
df$STIM_linear[df$stim == "low"] <-  -0.5
df$STIM_linear[df$stim == "med"] <-  0
df$STIM_linear[df$stim == "high"] <-  0.5
#
# # contrast code 2 quadratic
df$STIM_quadratic[df$stim == "low"] <-  -0.33
df$STIM_quadratic[df$stim == "med"] <-  0.66
df$STIM_quadratic[df$stim == "high"] <-  -0.33

df$stim_name <- df$stim

# cue contrast
df$cue_con[df$cue == "low"] <- -0.5
df$cue_con[df$cue == "high"] <- 0.5

# df$cue_name[df$cue == "intercept"] <- "intercept"
df$cue_name <- df$cue


df$stim_ordered <- factor(
        df$stim_name,
        levels = c("low", "med", "high")
    )

df$cue_ordered <- factor(
        df$cue_name,
        levels = c("low", "high")
    )

return(df)
}
```

```{r}
main_dir
```

## How was this dataframe generated?

via [https://github.com/jungheejung/spacetop_biopac/tree/main/scripts/p03_glm](https://github.com/jungheejung/spacetop_biopac/tree/main/scripts/p03_glm/glm_singletrial)

```{r}

taskname <- "pain"
# 1. load data _________________________________________________________________
beta <- read.table(file = file.path(paste0(main_dir, "/analysis/physio/nobaseline/glm_singletrial/glm-singletrial_task-", taskname, "_scr.tsv")), sep = '\t', header = TRUE)
```

## 1. stim x cue effect

```{r}
# 2. summarize data frame ______________________________________________________
# beta_con <- beta %>%
#   gather(key = "stim_cue", value = "beta", starts_with("high_stim"), starts_with("med_stim"), starts_with("low_stim")) %>%
#   separate(stim_cue, into = c("stim", "cue"), sep = "\\.")
beta$stim <- beta$stimtype
beta$cue <- beta$cuetype
beta_con <- simple_contrasts_singletrial(beta)

```

```{r}
subjects_with_inadequate_data <- beta_con %>%
  group_by(sub, cue_factor, STIM_linear) %>%
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 1) %>%
  distinct(sub) %>%
  pull(sub)
df_filter <- beta_con %>%
  filter(!(sub %in% subjects_with_inadequate_data))

print(sprintf("after filtering out subjects that have less than 3 trials in cell, we have N=%d -> N=%d",length(unique(beta_con$sub)), length(unique(df_filter$sub)) ))
```

```{r}
# 3. linear model ______________________________________________________________
model.factorial <- lmer(beta ~ STIM_linear*cue_factor + STIM_quadratic*cue_factor + (cue_factor |sub), data = beta_con)

sjPlot::tab_model(model.factorial,
              title = paste0(tools::toTitleCase(taskname), ": \nlmer(SCR beta ~ Stim * Cue + (Cue + Stim | sub), data = beta)"),
              CSS = list(css.table = '+font-size: 12;'))
summary(model.factorial)
```

```{r}

# 4. plot parameters _____________________________________________________________
subject <- "sub"
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"
dv <- "beta"
dv_keyword <- "sclbeta"
taskname <- "pain"
# model_iv2 <- "cue_ordered"
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "book_scrsingletrial")
beta_con$taskname <- taskname



# 5. summary stats _____________________________________________________________
SCLstim_subjectwise <- meanSummary(beta_con,
                                      c(subject, model_iv1, model_iv2), dv)
SCLstim_groupwise <- summarySEwithin(
  data = SCLstim_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
SCLstim_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

# 6. more plot parameters ______________________________________________________
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
subject <- "sub"
ggtitle <- paste(taskname, " - ", dv)
title <- paste(taskname, " - ", dv)
xlab <- ""
ylab <- "SCL beta coefficients (A.U.)"
ylim <- c(-10, 60)

if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#4274AD", "#C5263A")
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), "_cooksd.png",
    sep = ""
  )
)
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c( "blue",  "red")
} else {
  color <- c( "blue", "red")
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_qc-", dv_keyword, "_", as.character(Sys.Date()), "_cooksd.png",
    sep = ""
  )
)

# 7. raincloudplots ____________________________________________________________
# TODO:
# * change the range of the figure
# * change the x-axis
# * drop the NA conditions
# * change theme
# * adjust the box plots

ylim <- c(-1, 4.5)
# taskname = "pain"
w <- 10; h <- 5
g <- plot_halfrainclouds_twofactor(
  SCLstim_subjectwise,
  SCLstim_groupwise,
  model_iv1, model_iv2,
  sub_mean,
  group_mean,
  se,
  subject,
  ggtitle,
  title,
  xlab,
  ylab,
  taskname,
  ylim,
  w,
  h,
  dv_keyword,
  color,
  plot_savefname
)
g <- g + theme_bw() + theme_classic()
print(g)
SCLstim_groupwise$task = taskname

k <- plot_lineplot_twofactor(SCLstim_groupwise,
                             # taskname="pain",
                        iv1="stim_ordered",
                        iv2="cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c( "high" = "red",
                                  "low" = "#4C77ED"),
                        ggtitle = title,
                        xlab = "Stimulus intensity", ylab = "SCR")
# k <- k + theme(aspect.ratio=.8) +   geom_line(size = 1) + # Adjust line thickness
#   geom_point(size = 3)  # Adjust point size
k <- k + theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
  # geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 2)  # Adjust point size

ggsave(file.path(analysis_dir, paste0("SCR_maineffect", as.character(Sys.Date()), ".svg")), width = 8, height = 4, dpi=300)

print(k)
```

## 2. across sessions?

```{r}


# contrast code 1 linear
beta_con$SES_linear[beta_con$ses == "ses-01"] <- -0.5
beta_con$SES_linear[beta_con$ses == "ses-03"] <- 0
beta_con$SES_linear[beta_con$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
beta_con$SES_quadratic[beta_con$ses == "ses-01"] <- -0.33
beta_con$SES_quadratic[beta_con$ses == "ses-03"] <- 0.66
beta_con$SES_quadratic[beta_con$ses == "ses-04"] <- -0.33

beta_con$cue_con[beta_con$cue == "high_cue"] <- 0.5
beta_con$cue_con[beta_con$cue == "low_cue"] <- -0.5

model.betases <- lmer(beta ~
                          cue_con*STIM_linear*SES_linear +
                          cue_con*STIM_quadratic*SES_linear +
                          cue_con*STIM_linear*SES_quadratic +
                          cue_con*STIM_quadratic*SES_quadratic +
                          (cue_con + STIM_linear + SES_linear|sub), data = beta_con
                    )
# cue_con+STIM+EXPECT_demean
sjPlot::tab_model(model.betases,
                  title = "Multilevel-modeling: \nlmer(beta ~ CUE * STIM * SES + (1| sub), data = pvc)",
                  CSS = list(css.table = '+font-size: 12;'))
summary(model.betases)
equatiomatic::extract_eq(model.betases)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

combined_se_calc_cooksd <- data.frame()
for (sesname in c("ses-01", "ses-03", "ses-04")) {

    ggtitle <- paste(taskname, " - SCR betas")
    title <- paste(taskname, " - SCR betas")
    subject <- "sub"
    w <- 10
    h <- 6
  data <- beta_con[ beta_con$ses == sesname,]


    stim_con1 <- "STIM_linear"
    stim_con2 <- "STIM_quadratic"
    iv1 <- "cue_con"
    dv <- "beta"

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )

    # [ PLOT ] reordering for plots _________________________ # nolint
    data$cue_name <- NA
    data$cue_name[data$cue == "high"] <- "high cue"
    data$cue_name[data$cue == "low"] <- "low cue"
    #
    # data$stim_name[data$stim == "high_stim"] <- "High"
    # data$stim_name[data$stim == "med_stim"] <- "Med"
    # data$stim_name[data$stim == "low_stim"] <- "Low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data$stim_ordered <- factor(
        data$stim_name,
        levels = c("low", "med", "high")
    )
    data$cue_ordered <- factor(
        data$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    actual_groupwise$ses <- sesname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
   # calculate mean and se
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(str_to_title(taskname), " - SCR ", sesname )
    title <- paste(str_to_title(taskname), " - cue level")
    xlab <- ""
    ylab <- "SCR (a.u.)"
    ylim <- c(-1,5)
    dv_keyword <- "SCR"
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4274AD", "#C5263A")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_halfrainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
print(g)
}
```

#### session wise line plots {.unlisted .unnumbered}

```{r echo=FALSE, message=FALSE, warning=FALSE}
# lineplot per session

DATA = as.data.frame(combined_se_calc_cooksd)
color = c("#4C77ED", "#ED220D")
model_iv1 <- "stim_ordered"
model_iv2 <- "ses_ordered"
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "se"
dv_keyword = "actual"
p1 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-01",],
               LINEIV1, LINEIV2, MEAN, ERROR, color, ggtitle = 'ses-01',
               ylab = "SCR (A.U.)" )
p2 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-03",],
               LINEIV1, LINEIV2, MEAN, ERROR, color, ggtitle = 'ses-03',
               ylab = "SCR (A.U.)")
p3 = plot_lineplot_twofactor(DATA[DATA$ses == "ses-04",],
               LINEIV1, LINEIV2, MEAN, ERROR, color,ggtitle = 'ses-04',
               ylab = "SCR (A.U.)")

ggpubr::ggarrange(p1,p2,p3,ncol = 3, nrow = 1, common.legend = TRUE,legend = "bottom")
plot_filename = file.path(analysis_dir,
                          paste('lineplot_task-all_rating-',dv_keyword,'.png', sep = ""))
ggsave(plot_filename, width = 8, height = 4)
```

```{r}
  DATA = as.data.frame(combined_se_calc_cooksd)
  color <- c("#4C77ED", "#ED220D")
  model_iv1 <- "stim_ordered"
  model_iv2 <- "ses_ordered"
  LINEIV1 <- "stim_ordered"
  LINEIV2 <- "cue_ordered"
  MEAN <- "mean_per_sub_norm_mean"
  ERROR <- "se"
  dv_keyword <- "SCR"
  line_thickness <- 0.2
  ylim <- c(1.3, 2.4)
  p1 <- plot_lineplot_twofactor_subset(DATA[DATA$ses == "ses-01" , ], taskname,
                               LINEIV1, LINEIV2, MEAN, ERROR, color,
                               ggtitle = 'Visit 1', ylab = "SCR",
                               ylim=ylim)
  p1 <- p1 + theme(
  aspect.ratio = 1, # Adjust this as needed
  axis.line = element_line(size = line_thickness)
)
  p2 = plot_lineplot_twofactor_subset(DATA[DATA$ses == "ses-03", ], taskname,
                               LINEIV1, LINEIV2, MEAN, ERROR, color,
                               ggtitle = 'Visit 2', ylab = "SCR",
                               ylim=ylim)
    p2 <- p2 + theme(
  aspect.ratio = 1, # Adjust this as needed
  axis.line = element_line(size = line_thickness)
)
  p3 = plot_lineplot_twofactor_subset(DATA[DATA$ses == "ses-04", ], taskname,
                               LINEIV1, LINEIV2, MEAN,ERROR, color,
                               ggtitle = 'Visit 3', ylab = "SCR",
                               ylim=ylim)
    p3 <- p3 + theme(
  aspect.ratio = 1, # Adjust this as needed
  axis.line = element_line(size = line_thickness)
)
  arranged_plot <- ggpubr::ggarrange(
    p1, p2, p3, ncol = 3, nrow = 1, common.legend = TRUE, legend = "bottom"
  )
  print(arranged_plot)
  plot_filename = file.path(analysis_dir,
  paste('lineplot_task-all_rating-', dv_keyword,taskname, '.svg', sep = ""))
  ggsave(plot_filename, arranged_plot, width = 8, height = 4, dpi=300)
```

## 3. Singletrial SCR and PE

### merge dataframe

```{r}
analysis_folder <- "physio_singletrial"
pe <- read.csv(file.path(main_dir, "data/RL/July2024_Heejung_fMRI_paper/table_pain.csv"), sep = ",")
pe$singletrial_fname <- sprintf(
  "sub-%04d_%s_run-%02d_runtype-%s_event-stimulus_trial-%03d_cuetype-%s_stimintensity-%s.nii.gz",
  pe$src_subject_id,
  pe$ses,
  pe$param_run_num,
  pe$runtype,
  pe$trial_index -1,
  gsub("_cue", "", pe$param_cue_type),       # Remove "_cue" from param_cue_type
  gsub("_stim", "", pe$param_stimulus_type)  # Remove "_stim" from param_stimulus_type
)

beta_con$trialind <- as.numeric(gsub("trial-", "", beta_con$singletrial_index))
beta_con$singletrial_fname <- sprintf(
  "%s_%s_%s_runtype-%s_event-stimulus_trial-%03d_cuetype-%s_stimintensity-%s.nii.gz",
  beta_con$sub,
  beta_con$ses,
  beta_con$run,
  beta_con$runtype,
  beta_con$trialind -1,
  beta_con$cuetype,
  beta_con$stimtype
)

# intersect ____________________________________________________________________
df_merge <- inner_join(beta_con, pe, by = "singletrial_fname")
df_merge <- df_merge %>%
  select(-ends_with(".x"), -ends_with(".y"))
taskname <- "pain"

# model lmer SCR beta & PE _____________________________________________________
model.scrpe <- lmer(beta ~ PE_mdl2 + (PE_mdl2 |sub), data = df_merge)

sjPlot::tab_model(model.scrpe,
              title = paste0(tools::toTitleCase(taskname), ": \nlmer(SCR beta ~ PE + (PE | sub), data = beta)"),
              CSS = list(css.table = '+font-size: 12;'))
summary(model.scrpe)
```

## 4. Singletrial SCR and NPS

```{r}
nps <- read.csv(file.path(main_dir, "analysis/fmri/nilearn/deriv01_signature/rampup_plateau/signature-NPS_sub-all_runtype-pvc_event-stimulus.tsv"), sep = ",")
# intersect
# Assuming df1 and df2 are your data frames and 'key_column' is the name of your key column
df.scrnpspe <- inner_join(df_merge, nps, by = "singletrial_fname")

model.scrpe <- lmer(beta ~ NPS + (NPS |sub), data = df.scrnpspe)

sjPlot::tab_model(model.scrpe,
              title = paste0(tools::toTitleCase(taskname), ": \nlmer(SCR beta ~ NPS + (NPS | sub), data = beta)"),
              CSS = list(css.table = '+font-size: 12;'))
summary(model.scrpe)
```

## 5. Singletrial SCR and SIIPS

```{r}
SIIPS <- read.csv(file.path("/Volumes/spacetop_projects_cue/analysis/fmri/nilearn/deriv01_signature/rampup_plateau/signature-SIIPS_sub-all_runtype-pvc_event-stimulus.tsv"), sep = ",")
# intersect

df.scr <- inner_join(df.scrnpspe, SIIPS, by = "singletrial_fname")

model.scr_SIIPS <- lmer(beta ~ SIIPS + (SIIPS |sub), data = df.scr)

sjPlot::tab_model(model.scr_SIIPS,
              title = paste0(tools::toTitleCase(taskname), ": \nlmer(SCR beta ~ SIIPS + (SIIPS | sub), data = beta)"),
              CSS = list(css.table = '+font-size: 12;'))
summary(model.scr_SIIPS)
```

## 6. Singletrial SCR and NPS + SIIPS

```{r}
model.scr_signature <- lmer(beta ~ SIIPS + NPS + (SIIPS + NPS |sub), data = df.scr)

sjPlot::tab_model(model.scr_signature,
              title = paste0(tools::toTitleCase(taskname), ": \nlmer(SCR beta ~ SIIPS + NPS + (SIIPS + NPS  | sub), data = beta)"),
              CSS = list(css.table = '+font-size: 12;'))
summary(model.scr_signature)
```

## 7-1. Singletrial SCR and SIIPS resid, correlate with PE?

> After modeling SCR with SIIPS, the residuals do not correlate with PE

```{r}
# residuals, after accounting for stimulus effects!
df.scr <- df.scr %>%
  mutate(SIIPSresid = resid(model.scr_SIIPS))
# df_clean.no1$NPSresid <- residuals(model.npsstimresid)
model.residSIIPSpe <- lmer(SIIPSresid ~ PE_mdl2 + (PE_mdl2|sub), data = df.scr)
summary(model.residSIIPSpe)
```

## 7-2. Singletrial SCR and SIIPS resid, correlate with NPS?

> After modeling SCR with SIIPS, the residuals do not correlate with PE

```{r}
# residuals, after accounting for stimulus effects!
df.scr <- df.scr %>%
  mutate(SIIPSresid = resid(model.scr_SIIPS))
# df_clean.no1$NPSresid <- residuals(model.npsstimresid)
model.residSIIPSnps <- lmer(SIIPSresid ~ NPS + (NPS|sub), data = df.scr)
summary(model.residSIIPSnps)
```
