# PLS ::  PLS scores ~  cue * stim {#pls}

## What is the purpose of this notebook? {.unlisted .unnumbered}

Here, we want to... {{ INSERT }} 

* Main model: `plsscores ~ cue stim` 
* Main question: With PLS, did we predict the observed scores well? 
* {{ HYPOTHESES/EXPECTED OUTCOME }}
* 
* IV: 
  - {{ FACTOR NAME }} ( {{ LEVELS}} )
* DV: {{ DV }}


### TODO: 
```
INSERT HERE
```

### References : Once note book is complete, add at the bottom of Rmd
```
INSERT HERE
```

### load libraries {.unlisted .unnumbered}
```{r message=FALSE, warning=FALSE, include=FALSE}
library(car)
library(psych)
library(cueR)
```


### display distribution of data
Let's look at the distribution of the data. X axis: Y axis: 
```{r paged.print=TRUE}
expect.fname = "/Users/h/Documents/projects_local/cue_expectancy/analysis/fmri/nilearn/pls/pls_model-expectrating.tsv"
outcome.fname = "/Users/h/Documents/projects_local/cue_expectancy/analysis/fmri/nilearn/pls/pls_model-outcometrating.tsv"

expect_df = read.csv(expect.fname, sep = '\t')
outcome_df = read.csv(outcome.fname, sep = '\t')
```
```{r}
subject <- "sub"
model_iv1 <- "cuetype"
model_iv2 <- "stimulusintensity"
dv <- "expectrating"
expect.subjectwise <- meanSummary(expect_df,
                                      c(subject, model_iv1), dv)
expect.groupwise <- summarySEwithin(
  data = expect.subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1),
  idvar = subject
)

dv <- "pred_pain_expect"
pls.expect.subjectwise <- meanSummary(expect_df,
                                      c(subject, model_iv1), dv)
pls.expect.subjectwise <- summarySEwithin(
  data = expect.subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1),
  idvar = subject
)
# outcome.subjectwise <- meanSummary(outcome_df,
#                                       c(subject, model_iv2), dv)
# outcome.groupwise <- summarySEwithin(
#   data = outcome.subjectwise,
#   measurevar = "mean_per_sub",
#   withinvars = c(model_iv2),
#   idvar = subject
# )
```

> Summary: 

### plot {.unlisted .unnumbered}
We'll plot Y as a function of A and B
X axis: 
Y axis:
Each data point indicates ... 
```{r fig.height=10, fig.width=10}

```
> Conclusion:


:::: {.infobox}
Include the actual content here. here are my thoughts
::::

:::: {.refbox}
Include the actual content here. here are my thoughts
::::

