# beh :: painpathway ROI ~ cue \* stim {#upgrade_beh-outcome-cueXstim}

## What is the purpose of this notebook? {.unlisted .unnumbered}

We investigate the profile of painpathway ROIs as a function of cue and stimulus intensity

- Main model: `lmer(pain_pathway_beta ~ cue * stim)`
- Main question: do pain pathway ROI betas differ as a function of cue type and Stimulus intensity?
- If there is a main effect of cue on ROIs, does this cue effect differ depending on task type?
- Is there an interaction between the two factors?
- IV:
- cue (high / low)
- stim (high / med / low)
- DV: pain pathway average betas

```{r libraries_nps_stim, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(lme4)
library(optimx)
library(minqa)
library(dfoptim)
library(tidyverse)
library(psych)
library(reshape)
library(dplyr)

library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(plyr)
library(ggpubr)
library(r2mlm)
library(effectsize)
# library(devtools)
options(es.use_symbols = TRUE) # get nice symbols when printing! (On Windows, requires R >= 4.2.0)
library(EMAtools)
library(emmeans)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(plotly)
library(DT)
library(raincloudplots)
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/R_rainclouds.R")
# devtools::source_url("https://raw.githubusercontent.com/RainCloudPlots/RainCloudPlots/master/tutorial_R/summarySE.R")

devtools::source_url("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(r2mlm)
main_dir <- dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R",
                          full.names=TRUE,
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```

# F. check CANLAB extract ROI

## F-1. load data

```{r}

main_dir <- dirname(dirname(getwd()))
analysis_folder <- "fmri_painpathway"
beh <- readr::read_tsv(file.path(main_dir, "data/beh/sub-all_task-all_events.tsv"))
dv <- "nps"
base_dir <- file.path(main_dir, '/analysis/fmri/nilearn/deriv01_signature/rampup_plateau_painpathway')
#"/Volumes/spacetop_projects_cue/analysis/fmri/nilearn/deriv01_signature/rampup_plateau_painpathway"
# TODO: instead of VPN, need to push to github
# List all CSV files matching the pattern
file_paths <- list.files(base_dir, pattern =  "sub-.*roi-painpathway_runtype-pain.*\\.csv$", full.names = TRUE, recursive = TRUE)


# save results _________________________________________________________________
analysis_folder <- "fmri_painpathway"
analysis_dir <-
  file.path(main_dir,
            "analysis",
            "mixedeffect",
            analysis_folder,
            as.character(Sys.Date())) # nolint
dir.create(analysis_dir,
           showWarnings = FALSE,
           recursive = TRUE)
savedir <- analysis_dir
# Read and stack the CSV files
all_data <- file_paths %>%
  map_dfr(~read_csv(.x, show_col_types = FALSE), .id = "file_path")

df_merge <- inner_join(beh, all_data, by = "singletrial_fname")

df_merge <- df_merge %>%
  mutate(singletrial_fname = as.character(singletrial_fname)) %>%
  extract(singletrial_fname, into = c("sub", "ses", "run", "runtype", "event", "trial", "cuetype", "stimintensity"),
          regex = "^(sub-\\d+)_(ses-\\d+)_(run-\\d+)_runtype-(pain|vicarious|cognitive)_event-(cue|stimulus)_trial-(\\d+)_cuetype-(high|low)(?:_stimintensity-(high|med|low))?\\.nii.gz$",
          remove = FALSE)

# Adjust the dataframe to handle NA for missing stimintensity, if tidyr version doesn't support `fill`
df_merge$stimintensity[df_merge$stimintensity == ""] <- NA

data <-df_merge[df_merge$runtype == "pain" ,]

# contrast code ________________________________________________________________
data$stim <- NA; data$STIM_linear <- NA; data$STIM_quadratic <- NA;
data$CUE_high_gt_low <- NA;
data$SES_linear <- NA;data$SES_quadratic <- NA
data$stim[data$stimulusintensity == "low_stim"] <-  -0.5 # social influence task
data$stim[data$stimulusintensity == "med_stim"] <- 0 # no influence task
data$stim[data$stimulusintensity == "high_stim"] <-  0.5 # no influence task

data$STIM <- factor(data$stimulusintensity)

# contrast code 1 linear
data$STIM_linear[data$stimulusintensity == "low_stim"] <- -0.5
data$STIM_linear[data$stimulusintensity == "med_stim"] <- 0
data$STIM_linear[data$stimulusintensity == "high_stim"] <- 0.5

# contrast code 2 quadratic
data$STIM_quadratic[data$stimulusintensity == "low_stim"] <- -0.33
data$STIM_quadratic[data$stimulusintensity == "med_stim"] <- 0.66
data$STIM_quadratic[data$stimulusintensity == "high_stim"] <- -0.33

# social cude contrast
data$CUE_high_gt_low[data$cue == "low_cue"] <-  -0.5 # social influence task
data$CUE_high_gt_low[data$cue == "high_cue"] <-  0.5 # no influence task

data$EXPECT <- data$expectrating
data$OUTCOME <- data$outcomerating


data$SES_linear[data$ses == "ses-01"] <- -0.5
data$SES_linear[data$ses == "ses-03"] <- 0
data$SES_linear[data$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
data$SES_quadratic[data$ses == "ses-01"] <- -0.33
data$SES_quadratic[data$ses == "ses-03"] <- 0.66
data$SES_quadratic[data$ses == "ses-04"] <- -0.33

stim_con1 <- "STIM_linear"
stim_con2 <- "STIM_quadratic"
iv1 <- "CUE_high_gt_low"
dv <- "nps"
dv_keyword <- "NPS"
```

## F-2. Filter data and plot

```{r}
# filter data __________________________________________________________________
# Make sure that each condition cell has adequate amount of trials
dependent_vars <- c("Thal_VPLM_L","Thal_VPLM_R","Thal_IL","Thal_MD","Hythal","pbn_R","pbn_L","Bstem_PAG","rvm_R","Amy_R"
,"Amy_L","dpIns_L","dpIns_R","S2_L","S2_R","mIns_L","mIns_R","aIns_L","aIns_R"      ,
"aMCC_MPFC","s1_foot_L","s1_foot_R","s1_handplus_L","s1_handplus_R"    )  # Update this with your actual DVs
newlist <- c("Thal_VPLM (L)", "Thal_VPLM (R)", "Thal_IL","Thal_MD","Hythal","PBN (R)","PBN (L)","Bstem & PAG","RVM (R)","Amy (R)"
,"Amy (L)","dpIns (L)","dpIns (R)","SII (L)","SII (R)","mIns (L)","mIns (R)","aIns (L)","aIns (R)"      ,
"aMCC & MPFC","SI foot (L)","SI foot (R)","SI handplus (L)","SI handplus (R)"    )  # Update this with your actual DVs


# newlist <- dependent_vars #c()
# Initialize a DataFrame to collect combined results
combined_se_calc_cooksd <- data.frame()
for (i in seq_along(dependent_vars)) {
  dv <- dependent_vars[i]
  dv_title <- newlist[i]
# for (dv in dependent_vars) {
subjects_with_inadequate_data <- data %>%
  group_by(sub, CUE_high_gt_low, STIM_linear) %>% #SES_linear,
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 2) %>%
  distinct(sub) %>%
  pull(sub)
df_filter <- data %>%
  filter(!(sub %in% subjects_with_inadequate_data))

print(sprintf("after filtering out subjects that have less than 2 trials in cell, we have N=%d -> N=%d",length(unique(data$sub)), length(unique(df_filter$sub)) ))

## QC. check NPS distribution __________________________________________________________________

df_filter.NA <- df_filter# %>% filter(!is.na(nps))  # Remove NA values
head(df_filter.NA)


combined_se_calc_cooksd <- data.frame()
taskname = "pain"
ggtitle <- paste(taskname, " - NPS (degree)")
title <- paste(taskname, " - actual")
subject <- "sub"
w <- 10
h <- 6


analysis_dir <-
  file.path(main_dir,
            "analysis",
            "mixedeffect",
            analysis_folder,
            as.character(Sys.Date())) # nolint
dir.create(analysis_dir,
           showWarnings = FALSE,
           recursive = TRUE)
savedir <- analysis_dir



# df_filter.NA <- df_filter.NA %>%
#     group_by(sub) %>%
#     mutate(NPS_scaled = scale(nps)) %>%
#     ungroup()

# [ PLOT ] reordering for plots _________________________ # nolint
df_filter.NA$cue_name[df_filter.NA$cue == "high_cue"] <-  "high cue"
df_filter.NA$cue_name[df_filter.NA$cue == "low_cue"] <-  "low cue"

df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "high_stim"] <-  "High"
df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "med_stim"] <-  "Med"
df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "low_stim"] <-  "Low"

df_filter.NA$stim_ordered <- factor(df_filter.NA$stim_name, levels = c("Low", "Med", "High"))
df_filter.NA$cue_ordered <- factor(df_filter.NA$cue_name, levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"
# lmer model __________________________________________________________________
model_savefname <- file.path(
  analysis_dir,
  paste(
    "lmer_nps-",dv,"_",as.character(Sys.Date()),".txt",
    sep = ""
  )
)
formula_string <- paste(dv, "~ CUE_high_gt_low * STIM_linear + CUE_high_gt_low * STIM_quadratic + (1|sub)")
model_formula <- as.formula(formula_string)
# Fit the model
sink(model_savefname)
model.npscuestim <- lmer(model_formula, data = df_filter.NA)
# , control = lmerControl(
#       optimizer = "optimx",
#       optCtrl = list(
#         method = "nmkb",
#         maxit = 1e9,
#         maxfun = 1e9,
#         maxeval = 1e7,
#         xtol_abs = 1e-9,
#         ftol_abs = 1e-9
#       )
#     ))

print(summary(model.npscuestim))
sink()
# summary statistics calculate mean and se  ____________________________________
NPSstimcue_subjectwise <- meanSummary(df_filter.NA,
                                      c(subject, model_iv1, model_iv2), dv)
NPSstimcue_groupwise <- summarySEwithin(
  data = NPSstimcue_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
NPSstimcue_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

combined_se_calc_cooksd <-
  rbind(combined_se_calc_cooksd, NPSstimcue_groupwise)
# plot parameters ______________________________________________________________
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
subject <- "sub"
ggtitle <- paste(taskname, " - NPS Cooksd removed")
title <- paste(taskname, " - NPS")
xlab <- ""
ylab <- "NPS (degree)"
ylim <- c(-1,1)
dv_keyword <- "NPS"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#0b5fa6", "#0b5fa6")
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), "_cooksd.png",
    sep = ""
  )
)



### Lineplots with only low cue ____________________________________
subsetNPS <- NPSstimcue_groupwise[NPSstimcue_groupwise$cue_ordered == "low cue",]
g <- plot_lineplot_twofactor_subset(subsetNPS, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#0b5fa6", "#0b5fa6"),
                        ggtitle = dv_title,
                        xlab = "Stimulus intensity", ylab = "Mean score")
g + theme(aspect.ratio=.8)


### Lineplots________________________________________________________________________
g <- plot_lineplot_twofactor_subset(NPSstimcue_groupwise, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#0b5fa6","high cue" = "#C5263A"),
                        ggtitle = dv_title, ylim=c(0, 0.55),
                        xlab = "Stimulus intensity", ylab = "Mean score")
g <- g + theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
   geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 3)  # Adjust point size


#   print(arranged_plot)
  plot_filename = file.path(analysis_dir,
  paste('lineplot_task-all_rating-', dv_keyword,dv, '.svg', sep = ""))

print(g)

  # ggsave(plot_filename, g, width = 8, height = 4, dpi=300)
}

```

```{r}
library(ggplot2)
library(dplyr)
library(lme4)
library(ggeffects)

# Assuming 'data' is your dataset already loaded
dependent_vars <- c("Thal_VPLM_L","Thal_IL","Thal_MD","Hythal","pbn_R","pbn_L","Bstem_PAG","rvm_R",
                    "Amy_R","Amy_L","dpIns_L","dpIns_R","S2_L","S2_R","mIns_L","mIns_R","aIns_L","aIns_R",
                    "aMCC_MPFC","s1_foot_L","s1_foot_R","s1_handplus_L","s1_handplus_R")

# Filtering data
df_filtered <- data %>%
  group_by(sub, CUE_high_gt_low, STIM_linear) %>%
  filter(n() >= 3) %>%
  ungroup()

# Create a function to generate models and plots
generate_plots <- function(dv) {
  # Construct the model formula dynamically
  formula_string <- paste(dv, "~ CUE_high_gt_low * STIM_linear  + CUE_high_gt_low * STIM_quadratic+ (CUE_high_gt_low + STIM_linear|sub)")
  model <- lmer(as.formula(formula_string), data = df_filtered)

  # Generate predictions for plotting
  preds <- ggpredict(model, terms = c("CUE_high_gt_low", "STIM_linear"))

  # Create the plot
  p <- ggplot(preds, aes(x = x, y = predicted, color = group)) +
    geom_line() +
    geom_point() +
    labs(title = dv, y = "Predicted Value", x = "Stimulus Linear") +
    theme_minimal()

  return(p)
}

# Apply the function across all dependent variables and store plots
plots <- lapply(dependent_vars, generate_plots)

# Combine plots into a single grid
library(gridExtra)
grid.arrange(grobs = plots, ncol = 4)  # Adjust the number of columns as needed

```

```{r}
# filter data __________________________________________________________________
# Make sure that each condition cell has adequate amount of trials
dependent_vars <- c("Thal_VPLM_L","Thal_VPLM_R","Thal_IL","Thal_MD","Hythal","pbn_R","pbn_L","Bstem_PAG","rvm_R","Amy_R"
,"Amy_L","dpIns_L","dpIns_R","S2_L","S2_R","mIns_L","mIns_R","aIns_L","aIns_R"      ,
"aMCC_MPFC","s1_foot_L","s1_foot_R","s1_handplus_L","s1_handplus_R"    )  # Update this with your actual DVs
newlist <- c("Thal_VPLM (L)", "Thal_VPLM (R)", "Thal_IL","Thal_MD","Hythal","PBN (R)","PBN (L)","Bstem & PAG","RVM (R)","Amy (R)"
,"Amy (L)","dpIns (L)","dpIns (R)","SII (L)","SII (R)","mIns (L)","mIns (R)","aIns (L)","aIns (R)"      ,
"aMCC & MPFC","SI foot (L)","SI foot (R)","SI handplus (L)","SI handplus (R)"    )  # Update this with your actual DVs


# newlist <- dependent_vars #c()
# Initialize a DataFrame to collect combined results
combined_se_calc_cooksd <- data.frame()
for (i in seq_along(dependent_vars)) {
  dv <- dependent_vars[i]
  dv_title <- newlist[i]
# for (dv in dependent_vars) {
subjects_with_inadequate_data <- data %>%
  group_by(sub, CUE_high_gt_low, STIM_linear) %>% #SES_linear,
  dplyr::summarise(count = n(), .groups = 'drop') %>%
  filter(count < 2) %>%
  distinct(sub) %>%
  pull(sub)
df_filter <- data %>%
  filter(!(sub %in% subjects_with_inadequate_data))

print(sprintf("after filtering out subjects that have less than 2 trials in cell, we have N=%d -> N=%d",length(unique(data$sub)), length(unique(df_filter$sub)) ))

## QC. check NPS distribution __________________________________________________________________

df_filter.NA <- df_filter# %>% filter(!is.na(nps))  # Remove NA values
head(df_filter.NA)


combined_se_calc_cooksd <- data.frame()
taskname = "pain"
ggtitle <- paste(taskname, " - NPS (degree)")
title <- paste(taskname, " - actual")
subject <- "sub"
w <- 10
h <- 6


analysis_dir <-
  file.path(main_dir,
            "analysis",
            "mixedeffect",
            analysis_folder,
            as.character(Sys.Date())) # nolint
dir.create(analysis_dir,
           showWarnings = FALSE,
           recursive = TRUE)
savedir <- analysis_dir



# df_filter.NA <- df_filter.NA %>%
#     group_by(sub) %>%
#     mutate(NPS_scaled = scale(nps)) %>%
#     ungroup()

# [ PLOT ] reordering for plots _________________________ # nolint
df_filter.NA$cue_name[df_filter.NA$cue == "high_cue"] <-  "high cue"
df_filter.NA$cue_name[df_filter.NA$cue == "low_cue"] <-  "low cue"

df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "high_stim"] <-  "High"
df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "med_stim"] <-  "Med"
df_filter.NA$stim_name[df_filter.NA$stimulusintensity == "low_stim"] <-  "Low"

df_filter.NA$stim_ordered <- factor(df_filter.NA$stim_name, levels = c("Low", "Med", "High"))
df_filter.NA$cue_ordered <- factor(df_filter.NA$cue_name, levels = c("low cue", "high cue"))
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"
# lmer model __________________________________________________________________
model_savefname <- file.path(
  analysis_dir,
  paste(
    "lmer_nps-",dv,"_",as.character(Sys.Date()),".txt",
    sep = ""
  )
)
formula_string <- paste(dv, "~ CUE_high_gt_low * STIM_linear + CUE_high_gt_low * STIM_quadratic + (CUE_high_gt_low + STIM_linear|sub)")
model_formula <- as.formula(formula_string)
# Fit the model
sink(model_savefname)
model.npscuestim <- lmer(model_formula, data = df_filter.NA, control = lmerControl(
      optimizer = "optimx",
      optCtrl = list(
        method = "nmkb",
        maxit = 1e9,
        maxfun = 1e9,
        maxeval = 1e7,
        xtol_abs = 1e-9,
        ftol_abs = 1e-9
      )
    ))

print(summary(model.npscuestim))
sink()
# summary statistics calculate mean and se  ____________________________________
NPSstimcue_subjectwise <- meanSummary(df_filter.NA,
                                      c(subject, model_iv1, model_iv2), dv)
NPSstimcue_groupwise <- summarySEwithin(
  data = NPSstimcue_subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv1, model_iv2),
  idvar = subject
)
NPSstimcue_groupwise$task <- taskname
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

combined_se_calc_cooksd <-
  rbind(combined_se_calc_cooksd, NPSstimcue_groupwise)
# plot parameters ______________________________________________________________
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
subject <- "sub"
ggtitle <- paste(taskname, " - NPS Cooksd removed")
title <- paste(taskname, " - NPS")
xlab <- ""
ylab <- "NPS (degree)"
ylim <- c(-1,1)
dv_keyword <- "NPS"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#0b5fa6", "#0b5fa6")
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_task-", taskname, "_rating-", dv_keyword, "_", as.character(Sys.Date()), "_cooksd.png",
    sep = ""
  )
)



### Lineplots with only low cue ____________________________________
subsetNPS <- NPSstimcue_groupwise[NPSstimcue_groupwise$cue_ordered == "low cue",]
g <- cueR::plot_lineplot_twofactor_subset(subsetNPS, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#4274AD", "#4274AD"),
                        ggtitle = dv_title,
                        xlab = "Stimulus intensity", ylab = "Average BOLD")
g + theme(aspect.ratio=.8)


### Lineplots________________________________________________________________________
g <- cueR::plot_lineplot_twofactor_subset(NPSstimcue_groupwise, taskname = "pain",
                        iv1 = "stim_ordered", iv2 = "cue_ordered",
                        mean = "mean_per_sub_norm_mean", error = "se",
                        color = c("low cue" = "#4274AD","high cue" = "#C5263A"),
                        ggtitle = dv_title,
                        xlab = "Stimulus intensity", ylab = "Average BOLD")
g <- g + theme(aspect.ratio=1,
          text = element_text(size = 18), # Default text size for the plot
          axis.title = element_text(size = 22, ), # Axis titles
          axis.text = element_text(size = 15), # Axis text (x and y)
          plot.title = element_text(size = 24, hjust = 0.5) # Plot title
          ) +
   geom_line(size = 1) + # Adjust line thickness
  geom_point(size = 3)  # Adjust point size


#   print(arranged_plot)
  plot_filename = file.path(analysis_dir,
  paste('lineplot_task-all_rating-', dv_keyword,dv, '.svg', sep = ""))

print(g)

  ggsave(paste0("/Users/h/Documents/projects_local/cue_expectancy/resources/plots_dissertation/ch4/painpathway_cue_",dv,".svg"), g, width = 4, height = 4, dpi=300)
}
```
