# Atlas :: Parcel Beta ~ Cue X Stim X Ses {#KEYWORD}

## What is the purpose of this notebook? {.unlisted .unnumbered}

Here, we want to extract the beta coefficients from the Canlab 2023 atlas.
I use the finegrained parcels from canlab 2023.
Code: `scripts/step10_nilearn/parcel_canlab2023/parcel_singletrial.m`
Data structure is filename, 525 columns of parcels
Row indicate each single trial.

- Main model: `lmer( Parcel ~ cue * stim * ses)`
- Main question: Does brain activation differ as a function of cue, stim, ses?
- Pain related parcels will show the reverse cue effect
- cognitive evaluative regions will show a pattern that reflects the behavioral rating effect
-
- IV:
  - Cue ( high / low cue )
  - Stim ( high / med / low intensity )
- DV: Canlab 2023 parcels

### TODO:

```
convert data into long format for the 525 parcels
also, cluster them into subregions
```

### References : Once note book is complete, add at the bottom of Rmd

```
INSERT HERE
```

### load libraries {.unlisted .unnumbered}

```{r message=FALSE, warning=FALSE, include=FALSE}
library(car)
library(psych)
library(reshape)
library(plyr); library(dplyr)
library(tidyselect)
# library(tidyr)
library(stringr)
library(lme4)
library(lmerTest)
library(gghalves)
library(cueR)
```

### display distribution of data

Let's look at the distribution of the data. X axis: Y axis:

```{r paged.print=TRUE}
# main_dir = dirname(dirname(getwd()))
# # 1. load data _________________________________________________________________
taskname <- "pain"
main_dir <- dirname(dirname(getwd()))
data_dir <- file.path(main_dir, "analysis/fmri/nilearn/deriv02_parcel-canlab2023/singletrial_rampupdown")
analysis_dir <- '/Users/h/Desktop/TMP'
dir.create(analysis_dir, recursive = TRUE, showWarnings = FALSE)
pattern <- "extractdata_.*_atlas-canlab2023\\.tsv$"
file_paths <- list.files(data_dir, pattern = pattern, full.names = TRUE)
all_data <- lapply(file_paths, read.table, sep = '\t', header = TRUE) %>% bind_rows()

atlaslabels <- read.csv(file.path(data_dir, "label_atlas-canlab2023_parcel-525.csv"))

# split metadata _________________________________________________________________
# Assuming all_data has already been expanded with the separate() function
all_data <- all_data %>%
  separate(col = filename,
           into = c("sub", "ses", "run", "runtype", "event", "trial", "cuetype", "stimintensity"),
           sep = "_",
           remove = FALSE,
           convert = FALSE) %>%
  mutate(across(c(sub, ses, run, runtype, event, trial, cuetype, stimintensity),
                ~sub(".*-", "", .))) %>%
  mutate(stimintensity = gsub("\\.nii\\.gz", "", stimintensity))

# Remove the 'stimintensity-' prefix from the stimintensity column
all_data$stimintensity <- gsub("stimintensity-", "", all_data$stimintensity)

# Print the modified data frame to check the results
print(head(all_data))


# 3. create contrasts _________________________________________________________________

df <- cueR::simple_contrast_singletrial(all_data)
df$cue_ordered <- factor(
        df$cuetype,
        levels = c("low", "high")
    )
# contrast code 1 linear
df$SES_linear[df$ses == "ses-01"] <- -0.5
df$SES_linear[df$ses == "ses-03"] <- 0
df$SES_linear[df$ses == "ses-04"] <- 0.5

# contrast code 2 quadratic
df$SES_quadratic[df$ses == "ses-01"] <- -0.33
df$SES_quadratic[df$ses == "ses-03"] <- 0.66
df$SES_quadratic[df$ses == "ses-04"] <- -0.33

head(df)

```

## lmer

```{r}
# 3. linear model ______________________________________________________________
model.factorial <- lmer(region_extraction21 ~ STIM_linear*CUE_high_gt_low + STIM_quadratic*CUE_high_gt_low* + (1|sub), data = df)
# summary(model.factorial)
sjPlot::tab_model(model.factorial,
              title = paste0(tools::toTitleCase(taskname), ": \nlmer(Canlab2023 R21 ~ Stim * Cue + (1 | sub), data = df)"),
              CSS = list(css.table = '+font-size: 12;'))
```

## lmer session wise

```{r}

model.betases <- lmer(region_extraction21 ~
                          CUE_high_gt_low*STIM_linear*SES_linear +
                          CUE_high_gt_low*STIM_quadratic*SES_linear +
                          CUE_high_gt_low*STIM_linear*SES_quadratic +
                          CUE_high_gt_low*STIM_quadratic*SES_quadratic +
                          (1|sub), data = df
                    )
# CUE_high_gt_low+STIM+EXPECT_demean
sjPlot::tab_model(model.betases,
                  title = "Multilevel-modeling: \nlmer(beta ~ CUE * STIM * SES + (1| sub), data = df)",
                  CSS = list(css.table = '+font-size: 12;'))
```

## plot parameters

```{r}
model_iv1 <- "stim_ordered"
model_iv2 <- "cue_ordered"
dv <- "region_extraction21"
dv_keyword <- "region_21"
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "se"
color = c("#4C77ED", "#ED220D")
```

## session wise plots

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

combined_se_calc_cooksd <- data.frame()
for (sesname in c("ses-01", "ses-03", "ses-04")) {

    ggtitle <- paste(taskname, " - atlas extraction")
    title <- paste(taskname, " - atlas extraction")
    subject <- "sub"
    w <- 10
    h <- 6
  data <- df[ df$ses == sesname,]


    # stim_con1 <- "STIM_linear"
    # stim_con2 <- "STIM_quadratic"
    # iv1 <- "CUE_high_gt_low"
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    dv <- "region_extraction21"
    dv_keyword <- "region_21"

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )

    # [ PLOT ] reordering for plots _________________________ # nolint
    # data$cue_name <- NA
    # data$cue_name[data$cuetype == "cuetype-high"] <- "high cue"
    # data$cue_name[data$cuetype == "cuetype-low"] <- "low cue"
    #
    # data$stim_name[data$stimintensity == "high"] <- "high"
    # data$stim_name[data$stimintensity == "med"] <- "med"
    # data$stim_name[data$stimintensity == "low"] <- "low"
    #
    # # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))
    #
    # data$stim_ordered <- factor(
    #     data$stim_name,
    #     levels = c("low", "med", "high")
    # )
    # data$cue_ordered <- factor(
    #     data$cue_name,
    #     levels = c("low cue", "high cue")
    # )
    # model_iv1 <- "stim_ordered"
    # model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    actual_groupwise$ses <- sesname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
   # calculate mean and se
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(str_to_title(taskname), " - SCR ", sesname )
    title <- paste(str_to_title(taskname), " - cue level")
    xlab <- ""
    ylab <- "beta (a.u.)"
    ylim <- c(-10,60)

    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4274AD", "#C5263A")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
#     g <- cueR::plot_halfrainclouds_twofactor(
#         actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
#         sub_mean, group_mean, se, subject,
#         ggtitle, title, xlab, ylab, taskname,ylim,
#         w, h, dv_keyword, color, plot_savefname
#     )
# print(g)
}

```

## session wise lineplot: somatomotor

```{r echo=FALSE, message=FALSE, warning=FALSE}
# 1. select ROI based on keyword __________________________________________________
keyword <- "somatomotor"
subset_atlaslabels <- atlaslabels[grep(keyword, atlaslabels$Label3), ]
roi_nums <- row.names(subset_atlaslabels)

# Assuming 'keyword' and 'subset_atlaslabels' are defined as before
roi_nums <- row.names(subset_atlaslabels)  # Pre-computed ROI numbers
data <- df
data$ses <- as.factor(data$ses)
for (roi_num in roi_nums) {
    dv <- paste0("region_extraction", roi_num)

    # Ensure 'dv' exists in 'data' to avoid errors
    if (!dv %in% names(data)) {
        next  # Skip this iteration if 'dv' doesn't exist
    }

    actual_subjectwise <- meanSummary(data, c("sub", model_iv1, model_iv2, "ses"), dv)
    actual_groupwise <- summarySEwithin(data = actual_subjectwise, measurevar = "mean_per_sub", withinvars = c(model_iv1, model_iv2, "ses"), idvar = "sub")

    DATA <- as.data.frame(actual_groupwise)
    DATA$taskname <- taskname

    plots <- lapply(unique(DATA$ses), function(ses) {
        cueR::plot_lineplot_twofactor_subset(DATA[DATA$ses == ses,], taskname = taskname,
                                             LINEIV1, LINEIV2, MEAN, ERROR, color,
                                             ggtitle = paste0(roi_num, atlaslabels$Label2[as.numeric(roi_num)], atlaslabels$Label3[as.numeric(roi_num)], ses),
                                             ylab = paste0("Region ", roi_num, " (.a.u.)"))
    })

    g <- ggpubr::ggarrange(plotlist = plots, ncol = 3, nrow = 1, common.legend = TRUE, legend = "bottom")
    print(g)
}

```

## session wise lineplot: insula

```{r}
# 1. select ROI based on keyword __________________________________________________
keyword <- "insula"
subset_atlaslabels <- atlaslabels[grep(keyword, atlaslabels$Label3), ]
roi_nums <- row.names(subset_atlaslabels)

# Assuming 'keyword' and 'subset_atlaslabels' are defined as before
roi_nums <- row.names(subset_atlaslabels)  # Pre-computed ROI numbers
data <- df
data$ses <- as.factor(data$ses)
for (roi_num in roi_nums) {
    dv <- paste0("region_extraction", roi_num)

    # Ensure 'dv' exists in 'data' to avoid errors
    if (!dv %in% names(data)) {
        next  # Skip this iteration if 'dv' doesn't exist
    }

    actual_subjectwise <- meanSummary(data, c("sub", model_iv1, model_iv2, "ses"), dv)
    actual_groupwise <- summarySEwithin(data = actual_subjectwise, measurevar = "mean_per_sub", withinvars = c(model_iv1, model_iv2, "ses"), idvar = "sub")

    DATA <- as.data.frame(actual_groupwise)
    DATA$taskname <- taskname

    plots <- lapply(unique(DATA$ses), function(ses) {
        cueR::plot_lineplot_twofactor_subset(DATA[DATA$ses == ses,], taskname = taskname,
                                             LINEIV1, LINEIV2, MEAN, ERROR, color,
                                             ggtitle = paste0(roi_num, atlaslabels$Label2[as.numeric(roi_num)], atlaslabels$Label3[as.numeric(roi_num)], ses),
                                             ylab = paste0("Region ", roi_num, " (.a.u.)"))
    })

    g <- ggpubr::ggarrange(plotlist = plots, ncol = 3, nrow = 1, common.legend = TRUE, legend = "bottom")
    print(g)
}

```

## session wise lineplot: thalamus

## session wise lineplot: mPFC

```{r}
# 1. select ROI based on keyword __________________________________________________
keyword <- "mPFC"
subset_atlaslabels <- atlaslabels[grep(keyword, atlaslabels$Label3), ]
roi_nums <- row.names(subset_atlaslabels)

# Assuming 'keyword' and 'subset_atlaslabels' are defined as before
roi_nums <- row.names(subset_atlaslabels)  # Pre-computed ROI numbers
data <- df
data$ses <- as.factor(data$ses)
for (roi_num in roi_nums) {
    dv <- paste0("region_extraction", roi_num)

    # Ensure 'dv' exists in 'data' to avoid errors
    if (!dv %in% names(data)) {
        next  # Skip this iteration if 'dv' doesn't exist
    }

    actual_subjectwise <- meanSummary(data, c("sub", model_iv1, model_iv2, "ses"), dv)
    actual_groupwise <- summarySEwithin(data = actual_subjectwise, measurevar = "mean_per_sub", withinvars = c(model_iv1, model_iv2, "ses"), idvar = "sub")

    DATA <- as.data.frame(actual_groupwise)
    DATA$taskname <- taskname

    plots <- lapply(unique(DATA$ses), function(ses) {
        cueR::plot_lineplot_twofactor_subset(DATA[DATA$ses == ses,], taskname = taskname,
                                             LINEIV1, LINEIV2, MEAN, ERROR, color,
                                             ggtitle = paste0(roi_num, atlaslabels$Label2[as.numeric(roi_num)], atlaslabels$Label3[as.numeric(roi_num)], ses),
                                             ylab = paste0("Region ", roi_num, " (.a.u.)"))
    })

    g <- ggpubr::ggarrange(plotlist = plots, ncol = 3, nrow = 1, common.legend = TRUE, legend = "bottom")
    print(g)
}
```

## positive effects?

```{r}
# 1. select ROI based on keyword __________________________________________________
keyword <- "Ctx_a24"
subset_atlaslabels <- atlaslabels[grep(keyword, atlaslabels$Label1), ]
roi_nums <- row.names(subset_atlaslabels)

# Assuming 'keyword' and 'subset_atlaslabels' are defined as before
roi_nums <- row.names(subset_atlaslabels)  # Pre-computed ROI numbers
data <- df
data$ses <- as.factor(data$ses)
for (roi_num in roi_nums) {
    dv <- paste0("region_extraction", roi_num)

    # Ensure 'dv' exists in 'data' to avoid errors
    if (!dv %in% names(data)) {
        next  # Skip this iteration if 'dv' doesn't exist
    }

    actual_subjectwise <- meanSummary(data, c("sub", model_iv1, model_iv2, "ses"), dv)
    actual_groupwise <- summarySEwithin(data = actual_subjectwise, measurevar = "mean_per_sub", withinvars = c(model_iv1, model_iv2, "ses"), idvar = "sub")

    DATA <- as.data.frame(actual_groupwise)
    DATA$taskname <- taskname

    plots <- lapply(unique(DATA$ses), function(ses) {
        cueR::plot_lineplot_twofactor_subset(DATA[DATA$ses == ses,], taskname = taskname,
                                             LINEIV1, LINEIV2, MEAN, ERROR, color,
                                             ggtitle = paste0(roi_num, atlaslabels$Label2[as.numeric(roi_num)], atlaslabels$Label3[as.numeric(roi_num)], ses),
                                             ylab = paste0("Region ", roi_num, " (.a.u.)"))
    })

    g <- ggpubr::ggarrange(plotlist = plots, ncol = 3, nrow = 1, common.legend = TRUE, legend = "bottom")
    print(g)
}
```

```{r}
# 1. select ROI based on keyword __________________________________________________
keyword <- "Ctx_25"
subset_atlaslabels <- atlaslabels[grep(keyword, atlaslabels$Label1), ]
roi_nums <- row.names(subset_atlaslabels)

# Assuming 'keyword' and 'subset_atlaslabels' are defined as before
roi_nums <- row.names(subset_atlaslabels)  # Pre-computed ROI numbers
data <- df
data$ses <- as.factor(data$ses)
for (roi_num in roi_nums) {
    dv <- paste0("region_extraction", roi_num)

    # Ensure 'dv' exists in 'data' to avoid errors
    if (!dv %in% names(data)) {
        next  # Skip this iteration if 'dv' doesn't exist
    }

    actual_subjectwise <- meanSummary(data, c("sub", model_iv1, model_iv2, "ses"), dv)
    actual_groupwise <- summarySEwithin(data = actual_subjectwise, measurevar = "mean_per_sub", withinvars = c(model_iv1, model_iv2, "ses"), idvar = "sub")

    DATA <- as.data.frame(actual_groupwise)
    DATA$taskname <- taskname

    plots <- lapply(unique(DATA$ses), function(ses) {
        cueR::plot_lineplot_twofactor_subset(DATA[DATA$ses == ses,], taskname = taskname,
                                             LINEIV1, LINEIV2, MEAN, ERROR, color,
                                             ggtitle = paste0(roi_num, atlaslabels$Label2[as.numeric(roi_num)], atlaslabels$Label3[as.numeric(roi_num)], ses),
                                             ylab = paste0("Region ", roi_num, " (.a.u.)"))
    })

    g <- ggpubr::ggarrange(plotlist = plots, ncol = 3, nrow = 1, common.legend = TRUE, legend = "bottom")
    print(g)
}
```

## session wise lineplot: TPJ

> Summary:

### plot {.unlisted .unnumbered}

We'll plot Y as a function of A and B
X axis:
Y axis:
Each data point indicates ...

```{r fig.height=10, fig.width=10}

```

> Conclusion:

:::: {.infobox}
Include the actual content here. here are my thoughts
::::

:::: {.refbox}
Include the actual content here. here are my thoughts
::::
