# QC :: fdmean {#QCfdmean}

---

title: "fdmean"
output: html_document
date: "2023-07-18"

---

## Does FD differ as a function of task (pain/vicarious/cognitive)?

> Framewise displacement does differ as a function. comparing Pain vs. non-pain tasks, the FD means are significantly differ.
> However, as we can see, this effect is driven by a handful of participants

## Method: where do the FEmean values come from?

They are from mriqc. The analysis to compile all the framewise displacement values live here: [ INSERT LINK ]

```{r warning=FALSE, include=FALSE}
library(car)
library(psych)
library(reshape)
library(dplyr)
library(plyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(gghalves)
library(cueR)
```

```{r echo=FALSE}
main_dir = dirname(dirname(getwd()))

# 1. load in the dataframe _____________________________________________________
fdmeandf <- read.table(file = file.path(main_dir, "resources/qcreports/fdmean_run_type.tsv"), sep = '\t', header = TRUE)



# 2. create contrasts for pain vs non-pain runs ________________________________
fdmeandf$PAIN_NOPAIN[fdmeandf$run_type == "pain"] <- 0.5
fdmeandf$PAIN_NOPAIN[fdmeandf$run_type == "vicarious"] <- -0.5
fdmeandf$PAIN_NOPAIN[fdmeandf$run_type == "cognitive"] <- -0.5
df <- fdmeandf %>% drop_na(PAIN_NOPAIN)



# 3. linear model ______________________________________________________________
df$sub_factor <- factor(df$sub)
model.fdmean <- lmer(fd_mean ~ PAIN_NOPAIN + (PAIN_NOPAIN|sub_factor), data=df)
summary(model.fdmean)



# 4. generate summary stats for each subject ___________________________________
df$run_name[df$run_type == "pain"] <- "pain"
df$run_name[df$run_type == "vicarious"] <- "non-pain"
df$run_name[df$run_type == "cognitive"] <- "non-pain"

df$pain_ordered <- factor(
        df$run_name,
        levels = c("non-pain", "pain")
    )

subject <- "sub_factor"
model_iv <- "pain_ordered"
dv <- "fd_mean"
subjectwise <- meanSummary(df,c(subject, model_iv), dv)

groupwise <- summarySEwithin(
  data=subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv),
  idvar = subject
)



# 5. plot parameters ___________________________________________________________
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model98_fdmean", as.character(Sys.Date()))
sub_mean <- "mean_per_sub"
group_mean <- "mean_per_sub_norm_mean"
se <- "se"
subject <- "sub_factor"
ggtitle <- paste( dv)
title <- paste( dv)
xlab <- ""
ylab <- "FD mean (mm)"
dv_keyword <- "fdmean"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
  color <- c("#1B9E77", "#D95F02")
} else {
  color <- c("#4274AD", "#C5263A")
} # if keyword starts with
plot_savefname <- file.path(
  analysis_dir,
  paste(
    "raincloud_qc-", dv_keyword, "_", as.character(Sys.Date()), "_cooksd.png",
    sep = ""
  )
)



# 6. raincloud plot ____________________________________________________________
ylim <- c(0,.6)
taskname = "all"
w <- 10; h <- 5
g <- plot_halfrainclouds_onefactor(
  subjectwise,
  groupwise,
  model_iv,
  sub_mean,
  group_mean,
  se,
  subject,
  ggtitle,
  title,
  xlab,
  ylab,
  taskname,
  ylim,
  w,
  h,
  dv_keyword,
  color,
  plot_savefname
)
g <- g + theme_bw() + theme_classic()
print(g)



# 7. lineplot __________________________________________________________________
k <- cueR::plot_lineplot_onefactor(groupwise,
                        iv = "pain_ordered",
                        mean = "mean_per_sub_norm_mean",
                        error = "se",
                        color = c("pain" = "red",
                                  "non-pain" = "gray"),
                        xlab = "tasktype",
                        ylab = "FD mean (mm)",
                        ggtitle="fdmean pain vs nonpain")
                                  # "med" = "orange",
print(k)
```
