# RL simulation Jepma PE {#ch21_jepmaPE}


## Overview
The purpose of this markdown is to benchmark the plots from Jepma et al. (2018). 
Here, we plot the expectancy ratings and the actual ratings, with the high and low cues -- in one panel. 

### Some thoughts, TODOs {.unlisted .unnumbered}
* plot 2. some runs were repeated or omitted for the subjects that have more than 72 trials. I need to identify that list and work on the behavioral data. 
* I need to check whether the counterbalancing was done correctly. 


```{r message=FALSE, warning=FALSE, include=FALSE}
library(psych)
library(car)
# library(lmSupport)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(bbmle)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(stats)
library(ggpubr)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lme4)
library(effectsize)
library(brms)
library(devtools)
library(gghalves)
library(visibly) # 
library(plotly) #plot
library(scico) # plot


library(r2mlm)
main_dir <- dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```

## Function : plot binned rating function
```{r}
plot_binned_rating_pe <- function(df, taskname, iv1, iv2, group, xlab = "expectation ratings",
                               ylab = "outcome ratings", levels = 10, participant, ylim) {
    library(ggplot2)
    library(dplyr)
main_dir <- dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, 'scripts', 'step02_R', 'utils'),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
    # IV1 <- enquo(iv1)
    # IV2 <- enquo(iv2)

    if (any(startsWith(taskname, c("pain", "Expect")))) {
        color_palette <- c("#941100", "#000000")
    } else if (any(startsWith(taskname, c("vicarious")))) {
        color_palette <- c("#008F51", "#000000")
    } else if (any(startsWith(taskname, c("cognitive")))) {
        color_palette <- c("#011891", "#000000")
    }

    df_dropna <- df[!is.na(df[, iv1]) & !is.na(df[, iv2]), ]
    # step01 :: If a participant has less than 5 trials, then drop participant
    k <- df_dropna %>%
        dplyr::group_by(.data[[participant]]) %>%
        filter(n() >= 5) %>%
        ungroup()

    # step02 :: demean and discretize data
    df_discrete <- k %>%
        dplyr::group_by(.data[[participant]]) %>%
        select(everything())  %>%
        mutate(
            iv2_demean = .data[[iv2]] - mean(.data[[iv2]]),
            iv1_demean = .data[[iv1]] - mean(.data[[iv1]])
        ) %>%
        mutate(
            bin = ggplot2::cut_interval(.data[["iv1_demean"]], n = levels),
            expectlevels = as.numeric(ggplot2::cut_interval(.data[["iv1_demean"]], n = levels))
        )

    # discrete_df <- df_discrete[df_discrete$param_task_name == taskname, ]
    discrete_df <- df_discrete #[df_discrete$param_task_name == taskname, ]
    discrete_df$expectlevels_newlev <- discrete_df$expectlevels - (levels/2)

    subjectwise_bin_demean_cue <- meanSummary(discrete_df, c(
        "subject",  "expectlevels", group
    ), "iv2_demean")
    subjectwise_bin_demean_naomit <- na.omit(subjectwise_bin_demean_cue)
    groupwise_bin_demean <- summarySEwithin(
        data = subjectwise_bin_demean_naomit,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("expectlevels", group), # iv
        idvar = "subject"
    )
    subjectwise_bin_demean_naomit$expectlevels_newlev <- as.numeric(subjectwise_bin_demean_naomit$expectlevels) - (levels/2)
    groupwise_bin_demean$expectlevels_newlev <- as.numeric(groupwise_bin_demean$expectlevels) - (levels/2)
    discrete_df$expectlevels_newlev <- as.factor(discrete_df$expectlevels_newlev)
    g <-
        plot_errorbar(
            subjectwise_bin_demean_naomit,
            groupwise_bin_demean,
            iv = "expectlevels_newlev",
            sub_iv = "expectlevels",
            group_by = group,
            subjectwise_mean = "mean_per_sub",
            group_mean = "mean_per_sub_norm_mean",
            se = "se",
            subject = "subject",
            ggtitle = paste0("Do we see a sigmoidal pattern in the pain task?\ntask-", taskname, ": expectation predict outcome ratings"),
            title = "levels of expectation ratings",
            xlab = xlab,
            ylab = ylab,
            taskname = taskname,
            ylim = ylim,
            w = 3,
            h = 5,
            dv_keyword = "sigmoidal",
            color = color_palette,
            level_num = levels,
            save_fname = "~/Download/TEST.png"
        )
    return(g)
}

```


```{r}
plot_errorbar <- function(subjectwise, groupwise, iv, sub_iv, group_by,
                          subjectwise_mean, group_mean, se, subject,
                          ggtitle, title, xlab, ylab, taskname, ylim,
                          w, h, dv_keyword, color, level_num, save_fname) {
    library(ggplot2)

    g <- ggplot(
        data = subjectwise,
        aes(
            y = .data[[subjectwise_mean]],
            x = factor(.data[[iv]]),
            fill = factor(.data[[group_by]])
        )
    ) +
        coord_cartesian(ylim = ylim, expand = TRUE) +
        geom_point(
            aes(
                x = as.numeric(as.factor(.data[[iv]])) - (level_num / 2) - 0.1,
                y = .data[[subjectwise_mean]],
                color = factor(.data[[group_by]])
            ),
            position = position_jitter(width = .1),
            size = 1,
            alpha = 0.3,
        ) +
        geom_errorbar(
            data = groupwise,
            aes(
                x = as.numeric(.data[[iv]]) + .1,
                y = as.numeric(.data[[group_mean]]),
                group = .data[[group_by]],
                color = factor(.data[[group_by]]),
                ymin = .data[[group_mean]] - .data[[se]],
                ymax = .data[[group_mean]] + .data[[se]]
            ),
            position = position_dodge(width = 0.3), width = 0.3, # position = 'dodge',#nolint
            alpha = 1, lwd = .7
        ) +
        geom_line(
            data = groupwise,
            aes(
                group = .data[[group_by]],
                y = as.numeric(.data[[group_mean]]),
                x = as.numeric(.data[[iv]]) + .1,
                color = factor(.data[[group_by]]),
            ),
            position = position_dodge(width = 0.2),
            linetype = "solid", alpha = 1
        ) +
        # legend stuff ________________________________________________________ # nolint
        guides(fill = guide_legend(title = title)) +
        scale_fill_manual(values = color) +
        scale_color_manual(values = color) +
        ggtitle(ggtitle) +
        xlab(xlab) +
        ylab(ylab) +
        #theme_bw() +
        theme(
            axis.line = element_line(colour = "grey50"),
            panel.background = element_blank(),
            #plot.subtitle = ggtext::element_textbox_simple(size = 11)
        )
    ggsave(save_fname, width = w, height = h)
    return(g)
}

```



## load behavioral daata
```{r}
df = read.csv(file.path(main_dir, 'resources', 'references', 'cue_behavioraldata.csv'))
```

```{r}
colnames(df)
```

```{r}
# PE :: prediction error ______________________________________________________
df$PE =   df$RATING_outcome - df$RATING_expectation
# Lag expectation rating ______________________________________________________
# per run/ses/sub
data_a3lag <- df %>%
  group_by(sub,ses,run) %>% 
  mutate(prev_trial.RATING_expectation = lag(RATING_expectation, n = 1, default = NA)) %>% 
  mutate(next_trial.RATING_expectation = lead(RATING_expectation, n = 1, default = NA)) %>%
  mutate(ave.RATING_expectation = mean(RATING_expectation, na.rm = TRUE))
data_a3lag <- data_a3lag[!is.na(data_a3lag$ave.RATING_expectation),]
taskname = 'pain'
data_a3lag$next_trial.RATING_expect_fill = coalesce(data_a3lag$next_trial.RATING_expectation, data_a3lag$ave.RATING_expectation) 
data_a3lag$prev_trial.RATING_expect_fill = coalesce(data_a3lag$prev_trial.RATING_expectation, data_a3lag$ave.RATING_expectation) 

data_a3lag <- data_a3lag[data_a3lag$task == 'pain',]
# EXPECTUPDATE :: expectation (N) - expectation (N-1) ________________________
df_jepma <- data_a3lag %>%
  # group_by(sub,ses,run) %>%
  mutate(EXPECTUPDATE_NEXT =  next_trial.RATING_expect_fill-RATING_expectation )  %>%
  mutate(EXPECTUPDATE_PREV =  RATING_expectation- prev_trial.RATING_expect_fill)  %>%
  mutate(EXPECTUPDATE_PREV_JEPMA =  (RATING_expectation - prev_trial.RATING_expect_fill)/((PE)+1)) %>%
  mutate(EXPECTUPDATE_NEXT_JEPMA =  (next_trial.RATING_expect_fill - RATING_expectation)/((PE)+1))
# EXPECTUPDATE_NEXT_JEPMA: Jepma (2018)
```

```{r}
df_jepma$PE_type[df_jepma$PE >  0] <- "aversive" # outcome > expect
df_jepma$PE_type[df_jepma$PE <= 0] <- "appetitive" # outcome < expect
df_jepma$PE_con[df_jepma$PE <=  0] <- -1
df_jepma$PE_con[df_jepma$PE > 0] <-  1
df_jepma$cue_con[df_jepma$IV_cuelevel == "low_cue"] <- -1
df_jepma$cue_con[df_jepma$IV_cuelevel == "high_cue"] <- 1
df_jepma <- df_jepma[!is.na(df_jepma$RATING_expectation),]

write.csv(df_jepma, '/Users/h/Desktop/cuerating_0505.csv')
```

## JEPMA 
```{r}
# summary statistics ____________________________________________________________
subject = "sub"
model_iv1 = "PE_type"
model_iv2 =  "IV_cuelevel"

dv <- "EXPECTUPDATE_NEXT_JEPMA" #"PE"
    subjectwise <- meanSummary(
        df_jepma,
        c(subject, model_iv1, model_iv2), dv
    )
    groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    #  calculate mean and se  ----------------------------------------------------------------------------
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "sub"
    ggtitle <- paste(taskname, "Confirmation bias in expectation updating")
    legend_title <- "cue levels"
    title <- paste(taskname, " - Actual")
    xlab <- ""
    ylab <- "Learning Rate"
    ylim <- c(-250,250)
    dv_keyword <- "learning rate"
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c( "#D73027", "#4575B4")
    } # if keyword starts with]
    analysis_dir = '/Users/h/Desktop'
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )

plot_halfrainclouds_twofactor(subjectwise, groupwise,
                                      model_iv1, model_iv2, sub_mean, group_mean, se, subject,
                                      ggtitle, legend_title, xlab, ylab, task_name, ylim,
                                      w, h, dv_keyword, color, save_fname)

plot_lineplot_twofactor(groupwise, model_iv1, model_iv2, "mean_per_sub_norm_mean", error = "se",
                      color = c( high_cue = "#D73027", low_cue = "#4575B4"), 
                      ggtitle, 
                      xlab= "Stimulus intensity", 
                      ylab = "Learning rate") 
```


```{r}
plot_lineplot_twofactor(groupwise, model_iv1, model_iv2, "mean_per_sub_norm_mean", error = "se",
                      color = c( high_cue = "#D73027", low_cue = "#4575B4"), 
                      ggtitle, 
                      xlab= "Stimulus intensity", 
                      ylab = "Learning rate") 
```

```
library(plyr)
subjectwise_cuetype = meanSummary_2dv(DATA=df_jepma,
        GROUP = c("sub", "trialindex", "IV_cuelevel"), DV1 = "PE", DV2 = "EXPECTUPDATE")
plot_twovariable(subjectwise_cuetype, iv1 = "DV1_mean_per_sub", iv2 = "DV2_mean_per_sub", group = "IV_cuelevel", subject = "sub", xmin=-50, xmax=50, ymin=-50,ymax=50,
xlab="PE", ylab="Expectation update", ggtitle="", color_scheme=c( high_cue = "#D73027", low_cue = "#4575B4"), alpha=.8, fit_lm=TRUE, lm_method = "lm", identity_line=TRUE, size=NULL)

```
```{r}
subjectwise_cuetype_groupby = meanSummary_2dv(DATA=df_jepma,
        GROUP = c("sub", "IV_cuelevel"), DV1 = "PE", DV2 = "EXPECTUPDATE_NEXT")
plot_twovariable(df_jepma, iv1 = "PE", iv2 = "EXPECTUPDATE_NEXT", group = "IV_cuelevel", subject = "sub", xmin=-50, xmax=50, ymin=-50,ymax=50,
xlab="PE", ylab="Expectation update", ggtitle="", color_scheme=c( high_cue = "#D73027", low_cue = "#4575B4"), alpha=.8, fit_lm=TRUE, lm_method = "lm", identity_line=TRUE, size=NULL)

```

```{r}

model.l <- lmer(EXPECTUPDATE_NEXT ~ 1+ PE*IV_cuelevel + (1+ IV_cuelevel|sub), data = df_jepma, 
                control=lmerControl(check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4)))
summary(model.l)
library(sjPlot)
plot_model(model.l, type = "pred", terms = c("PE", "IV_cuelevel"))
```




# ```{r}
# subjectwise_cuetype_groupby = meanSummary_2dv(DATA=df_jepma,
#         GROUP = c("sub", "IV_cuelevel"), DV1 = "PE", DV2 = "EXPECTUPDATE_PREV_JEPMA")
# plot_twovariable(df_jepma, iv1 = "PE", iv2 = "EXPECTUPDATE_PREV_JEPMA", group = "IV_cuelevel", subject = "sub", xmin=-50, xmax=50, ymin=-50,ymax=50,
# xlab="PE", ylab="Expectation update", ggtitle="", color_scheme=c( high_cue = "#D73027", low_cue = "#4575B4"), alpha=.8, fit_lm=TRUE, lm_method = "lm", identity_line=TRUE, size=NULL)
# 
# ```

# use sjplot
```{r}

model.l <- lmer(EXPECTUPDATE_NEXT_JEPMA ~ 1+ PE*IV_cuelevel + (1+ IV_cuelevel|sub), data = df_jepma, 
                control=lmerControl(check.conv.singular = .makeCC(action = "ignore",  tol = 1e-4)))
summary(model.l)
```
```{r}
library(sjPlot)
plot_model(model.l, type = "pred", terms = c("PE", "IV_cuelevel"))
```

# %% TODO
* plot each paritcipant subject wise plot for PE and expect_prev_jepma
```{r}
ggplot(df_jepma[df_jepma$sub == 14, ], aes(x = PE, y = EXPECTUPDATE_NEXT, color = IV_cuelevel)) +
  geom_point() +
  facet_wrap(~ sub, ncol = 1) +  # Adjust ncol to your desired number of columns
  labs(x = "PE", y = "Learning Rate") +
  theme_minimal()
```

```{r}
ggplot(df_jepma, aes(x = PE, y = EXPECTUPDATE_NEXT, color = IV_cuelevel)) +
  geom_point() +
  facet_wrap(~ sub, ncol = 20) +  # Adjust ncol to your desired number of columns
  labs(x = "PE", y = "Learning Rate") +
  theme_minimal()

```


```{r}
# subjectwise_cuetype_groupby = meanSummary_2dv(DATA=df_jepma,
#         GROUP = c("sub", "IV_cuelevel"), DV1 = "PE", DV2 = "EXPECTUPDATE_JEPMA")
# plot_twovariable(df_jepma, iv1 = "PE", iv2 = "EXPECTUPDATE", group = "IV_cuelevel", subject = "sub", xmin=-50, xmax=50, ymin=-50,ymax=50,
# xlab="PE", ylab="Expectation update", ggtitle="", color_scheme=c( high_cue = "#D73027", low_cue = "#4575B4"), alpha=.8, fit_lm=TRUE, lm_method = "lm", identity_line=TRUE, size=NULL)

```

## TODO: plot in bins
## Check bin process {.unlisted .unnumbered}

### Let's demean the ratings for one participant  {.unlisted .unnumbered}
1. bin ratings
Do the bins do their jobs?
plot one run
then check the min, max and see if the quantization is done properly.
YES, it is
```{r eval=FALSE, include=FALSE}
# per subject, session, run
df_bin = df_jepma
min(df_bin$PE)
max(df_bin$PE)
range(df_bin$PE)
cut_interval(range(df_bin$PE), n = 10)
hist(df_bin$PE)
df_bin$bin = cut_interval(df_bin$PE, n = 10)
df_bin$bin_num = as.numeric(cut_interval(df_bin$PE, n = 10))
```


* confirm that df discrete has 10 levels per participant
* the number of counts per frequency can differ 
```{r}
k <-df_bin %>% group_by(sub) %>% filter(n()>= 5) %>% ungroup()

df_discrete = k %>%
  group_by(sub) %>%
  mutate(bin = cut_interval(PE, n = 10),
         outcomelevels = as.numeric(cut_interval(PE, n = 10)))

res <- df_discrete %>% 
  group_by(sub,outcomelevels) %>% 
  tally()

dset1 <- head(res)
knitr::kable(dset1, format = "html")
```


### subjectwise plot {.unlisted .unnumbered}
What is the pattern of expectation rating and outcome rating, per participant? 
Do we see a linear effect? We should also plot the data as a sigmoidal fit
```{r echo=FALSE}
# df <- load_task_social_df(datadir,taskname = taskname,subject_varkey = subject_varkey,iv = iv,exclude = exclude  )
iv2 = "EXPECTUPDATE_NEXT"; levels = 10
iv1 = "PE"; 
df_dropna <- df_jepma[!is.na(df_jepma[, iv1]) & !is.na(df_jepma[, iv2]), ]
k <-df_dropna %>% group_by(sub) %>% filter(n()>= 5) %>% ungroup()

df_discrete <- k %>%
  dplyr::group_by(.data[["sub"]]) %>%
  select(everything())  %>%
  mutate(Expectupdate_demean = .data[[iv2]] - mean(.data[[iv2]]),
         PE_demean = .data[[iv1]] - mean(.data[[iv1]])) %>%
  mutate(
    bin = ggplot2::cut_interval(.data[["PE_demean"]], n = levels),
    pelevels = as.numeric(cut_interval(.data[["PE_demean"]], n = levels))
  )

swp <- ggplot(
  df_discrete,
  aes(y = Expectupdate_demean,
      x = pelevels,
      colour = subject),
  size = .01,
  color = 'gray'
) +
  geom_point(position = position_jitter(width = .1),size = .1, alpha = .3) +
  # geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  geom_smooth(method = 'rlm', se = F, linewidth = .1, alpha = .5) +
  theme(axis.line = element_line(colour = "grey50"), 
      panel.background = element_blank(),
      plot.subtitle = ggtext::element_textbox_simple(size= 11))

# ADD description
swp +  labs(title =paste0("task-",taskname, "- Subjectwise pattern for outcome and expect ratings? \n\n"),
        subtitle = "participants indeed have a linear relationship betwen ")
```


### Non-demeaned subjectwise plot {.unlisted .unnumbered}
What is the pattern of expectation rating and outcome rating, per participant? 
Do we see a linear effect? We should also plot the data as a sigmoidal fit
```{r echo=FALSE}
# df <- load_task_social_df(datadir,taskname = taskname,subject_varkey = subject_varkey,iv = iv,exclude = exclude  )
iv2 = "EXPECTUPDATE_NEXT"; levels = 10
iv1 = "PE"; 
df_dropna <- df_jepma[!is.na(df_jepma[, iv1]) & !is.na(df_jepma[, iv2]), ]
k <-df_dropna %>% group_by(sub) %>% filter(n()>= 5) %>% ungroup()

df_discrete <- k %>%
  dplyr::group_by(.data[["sub"]]) %>%
  select(everything())  %>%
  # mutate(Expectupdate_demean = .data[[iv2]] - mean(.data[[iv2]]),
         # PE_demean = .data[[iv1]] - mean(.data[[iv1]])) %>%
  mutate(
    bin = ggplot2::cut_interval(.data[[iv1]], n = levels),
    pelevels = as.numeric(cut_interval(.data[[iv1]], n = levels))
  )

swp <- ggplot(
  df_discrete,
  aes(y = EXPECTUPDATE_NEXT,
      x = pelevels,
      colour = subject),
  size = .01,
  color = 'gray'
) +
  geom_point(position = position_jitter(width = .1),size = .1, alpha = .3) +
  # geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .1) +
  geom_smooth(method = 'rlm', se = F, linewidth = .1, alpha = .5) +
  theme(axis.line = element_line(colour = "grey50"), 
      panel.background = element_blank(),
      plot.subtitle = ggtext::element_textbox_simple(size= 11))

# ADD description
swp +  labs(title =paste0("task-",taskname, "- Subjectwise pattern for outcome and expect ratings? \n\n"),
        subtitle = "participants indeed have a linear relationship betwen ")
```

## Demeaned cue
```{r}
# df <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
taskname = 'pain'
plot_binned_rating_pe(df_dropna, taskname, iv1 = "PE", iv2 = "EXPECTUPDATE_NEXT", group = "IV_cuelevel", xlab = "PE",
                               ylab = "Expectation Update", levels = 10, participant="sub", ylim = c(-20, 20)) 

iv2 = "EXPECTUPDATE_NEXT"; levels = 10
iv1 = "PE"; 
group = "IV_cuelevel"
df_dropna <- df_jepma[!is.na(df_jepma[, iv1]) & !is.na(df_jepma[, iv2]), ]
k <-df_dropna %>% group_by(sub) %>% filter(n()>= 5) %>% ungroup()

    # step02 :: demean and discretize data
    df_discrete <- k %>%
        dplyr::group_by(.data[["sub"]]) %>%
        select(everything())  %>%
        mutate(
            iv2_demean = .data[[iv2]] - mean(.data[[iv2]]),
            PE_demean = .data[["PE"]] - mean(.data[["PE"]])
        ) %>%
        mutate(
            bin = ggplot2::cut_interval(.data[["PE_demean"]], n = levels),
            expectlevels = as.numeric(ggplot2::cut_interval(.data[["PE_demean"]], n = levels))
        )


    discrete_df <- df_discrete #[df_discrete$param_task_name == taskname, ]
    discrete_df$expectlevels_newlev <- discrete_df$expectlevels - (levels/2)

    subjectwise_bin_demean_cue <- meanSummary(discrete_df, c(
        "sub",  "expectlevels", group
    ), "iv2_demean")
    subjectwise_bin_demean_naomit <- na.omit(subjectwise_bin_demean_cue)
    groupwise_bin_demean <- summarySEwithin(
        data = subjectwise_bin_demean_naomit,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("expectlevels", "IV_cuelevel"), # iv
        idvar = "subject"
    )
    subjectwise_bin_demean_naomit$expectlevels_newlev <- as.numeric(subjectwise_bin_demean_naomit$expectlevels) - (levels/2)
    groupwise_bin_demean$expectlevels_newlev <- as.numeric(groupwise_bin_demean$expectlevels) - (levels/2)
    discrete_df$expectlevels_newlev <- as.factor(discrete_df$expectlevels_newlev)
    g <-
        plot_errorbar(
            subjectwise_bin_demean_naomit,
            groupwise_bin_demean,
            iv = "expectlevels_newlev",
            sub_iv = "expectlevels",
            group_by = "IV_cuelevel",
            subjectwise_mean = "mean_per_sub",
            group_mean = "mean_per_sub_norm_mean",
            se = "se",
            subject = "subject",
            ggtitle = paste0("Do we see a sigmoidal pattern in the pain task?\ntask-", taskname, ": expectation predict outcome ratings"),
            title = "levels of expectation ratings",
            xlab = xlab,
            ylab = ylab,
            taskname = taskname,
            ylim = c(-70, 70),
            w = 3,
            h = 5,
            dv_keyword = "sigmoidal",
            color = c("red", "blue"),
            level_num = levels,
            save_fname = "~/Download/TEST.png"
        )
g

```
## Non-Demeaned cue
```{r}
# df <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
taskname = 'pain'
plot_binned_rating_pe(df_dropna, taskname, iv1 = "PE", iv2 = "EXPECTUPDATE_NEXT", group = "IV_cuelevel", xlab = "PE",
                               ylab = "Expectation Update", levels = 10, participant="sub", ylim = c(-100, 100)) 

iv2 = "EXPECTUPDATE_NEXT"; levels = 10
iv1 = "PE"; 
group = "IV_cuelevel"
df_dropna <- df_jepma[!is.na(df_jepma[, iv1]) & !is.na(df_jepma[, iv2]), ]
k <-df_dropna %>% group_by(sub) %>% filter(n()>= 5) %>% ungroup()

    # step02 :: demean and discretize data
    df_discrete <- k %>%
        dplyr::group_by(.data[["sub"]]) %>%
        select(everything())  %>%
        # mutate(
            # iv2_demean = .data[[iv2]] - mean(.data[[iv2]]),
            # PE_demean = .data[["PE"]] - mean(.data[["PE"]])
        # ) %>%
        mutate(
            bin = ggplot2::cut_interval(.data[[iv1]], n = levels),
            expectlevels = as.numeric(ggplot2::cut_interval(.data[[iv1]], n = levels))
        )


    discrete_df <- df_discrete 
    discrete_df$expectlevels_newlev <- discrete_df$expectlevels - (levels/2)

    subjectwise_bin_demean_cue <- meanSummary(discrete_df, c(
        "sub",  "expectlevels", group
    ), iv2)
    subjectwise_bin_demean_naomit <- na.omit(subjectwise_bin_demean_cue)
    groupwise_bin_demean <- summarySEwithin(
        data = subjectwise_bin_demean_naomit,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c("expectlevels", "IV_cuelevel"), # iv
        idvar = "subject"
    )
    subjectwise_bin_demean_naomit$expectlevels_newlev <- as.numeric(subjectwise_bin_demean_naomit$expectlevels) - (levels/2)
    groupwise_bin_demean$expectlevels_newlev <- as.numeric(groupwise_bin_demean$expectlevels) - (levels/2)
    discrete_df$expectlevels_newlev <- as.factor(discrete_df$expectlevels_newlev)
    g <-
        plot_errorbar(
            subjectwise_bin_demean_naomit,
            groupwise_bin_demean,
            iv = "expectlevels_newlev",
            sub_iv = "expectlevels",
            group_by = "IV_cuelevel",
            subjectwise_mean = "mean_per_sub",
            group_mean = "mean_per_sub_norm_mean",
            se = "se",
            subject = "subject",
            ggtitle = paste0("Do we see a sigmoidal pattern in the pain task?\ntask-", taskname, ": expectation predict outcome ratings"),
            title = "levels of expectation ratings",
            xlab = xlab,
            ylab = ylab,
            taskname = taskname,
            ylim = ylim,
            w = 3,
            h = 5,
            dv_keyword = "sigmoidal",
            color = c("red", "blue"),
            level_num = levels,
            save_fname = "~/Download/TEST.png"
        )
g

```


```{r}
plot_errorbar <- function(subjectwise, groupwise, iv, sub_iv, group_by,
                          subjectwise_mean, group_mean, se, subject,
                          ggtitle, title, xlab, ylab, taskname, ylim,
                          w, h, dv_keyword, color, level_num, save_fname) {
    library(ggplot2)

    g <- ggplot(
        data = subjectwise,
        aes(
            y = .data[[subjectwise_mean]],
            x = factor(.data[[iv]]),
            fill = factor(.data[[group_by]])
        )
    ) +
        coord_cartesian(ylim = ylim, expand = TRUE) +
        geom_point(
            aes(
                x = as.numeric(as.factor(.data[[iv]])) - (level_num / 2) - 0.1,
                y = .data[[subjectwise_mean]],
                color = factor(.data[[group_by]])
            ),
            position = position_jitter(width = .1),
            size = 1,
            alpha = 0.3,
        ) +
        geom_errorbar(
            data = groupwise,
            aes(
                x = as.numeric(.data[[iv]]) + .1,
                y = as.numeric(.data[[group_mean]]),
                group = .data[[group_by]],
                color = factor(.data[[group_by]]),
                ymin = .data[[group_mean]] - .data[[se]],
                ymax = .data[[group_mean]] + .data[[se]]
            ),
            position = position_dodge(width = 0.3), width = 0.3, # position = 'dodge',#nolint
            alpha = 1, lwd = .7
        ) +
        geom_line(
            data = groupwise,
            aes(
                group = .data[[group_by]],
                y = as.numeric(.data[[group_mean]]),
                x = as.numeric(.data[[iv]]) + .1,
                color = factor(.data[[group_by]]),
            ),
            position = position_dodge(width = 0.2),
            linetype = "solid", alpha = 1
        ) +
        # legend stuff ________________________________________________________ # nolint
        guides(fill = guide_legend(title = title)) +
        scale_fill_manual(values = color) +
        scale_color_manual(values = color) +
        ggtitle(ggtitle) +
        xlab(xlab) +
        ylab(ylab) +
        #theme_bw() +
        theme(
            axis.line = element_line(colour = "grey50"),
            panel.background = element_blank(),
            #plot.subtitle = ggtext::element_textbox_simple(size = 11)
        )
    ggsave(save_fname, width = w, height = h)
    return(g)
```


