# fMRI :: FIR ~ task TTL2 {#scltimeseries_tt2}

The purpose of this notebook is to plot the BOLD timeseries from SPM FIR model.
TODO

- load tsv
- concatenate
- per time column, calculate mean and variance
- plot

## references

https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402

```{r libraries_52, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(car)
library(psych)
library(reshape)
library(plyr)
library(dplyr)
library(tidyselect)
library(tidyr)
library(stringr)
library(lmerTest)
library(ggplot2)
library(gghalves)
library(ggpubr)
library(plotly)
library(FactoMineR)
library(grid)
library(cueR)
```

```{r}

plot_timeseries_onefactor <-
  function(df, iv1, mean, error, xlab, ylab, ggtitle, color) {
    n_points <- 100 # Number of points for interpolation

    g <- ggplot(
      data = df,
      aes(
        x = .data[[iv1]],
        y = .data[[mean]],
        group = .data[[iv1]],
        color = .data[[iv1]]
      ),
      cex.lab = 1.5,
      cex.axis = 2,
      cex.main = 1.5,
      cex.sub = 1.5
    ) +
      geom_errorbar(
        aes(
        ymin = (.data[[mean]] - .data[[error]]),
        ymax = (.data[[mean]] + .data[[error]])
      ),
      width = .001,

      alpha = 0.1) +
      geom_line() +
      geom_point() +
      ggtitle(ggtitle) +
      xlab(xlab) +
      ylab(ylab) +
      theme_classic() +
      theme(aspect.ratio = .6) +
      expand_limits(x = 3.25) +
      scale_color_manual("",
                         values = color) +

      theme_bw()

    return(g)
  }
```

```{r}
plot_timeseries_bar_SANDBOX <-
  function(df, iv1, iv2, mean, error, xlab, ylab, ggtitle, color) {
    n_points <- 100 # Number of points for interpolation

    ## Removing "tr" from the column values
    df[[iv1]] <- as.numeric(sub("tr", "", df[[iv1]]))

    g <- ggplot(
      data = df,
      aes(
        x = .data[[iv1]],
        y = .data[[mean]],
        group = factor(.data[[iv2]]),
        color = factor(.data[[iv2]])
      ),
      cex.lab = 1.5,
      cex.axis = 2,
      cex.main = 1.5,
      cex.sub = 1.5
    ) +
      geom_errorbar(aes(
        ymin = (.data[[mean]] - .data[[error]]),
        ymax = (.data[[mean]] + .data[[error]]),
        #fill =  factor(.data[[iv2]])
      ),
      width = .001,
      alpha = 0.1) +
      #geom_line() +
      geom_point() +
      ggtitle(ggtitle) +
      xlab(xlab) +
      ylab(ylab) +
      theme_classic() +
      expand_limits(x = 3.25) +
      scale_color_manual("",
                         values = color) +
      scale_fill_manual("",
                        values = color) +
      theme(
        aspect.ratio = .6,
        text = element_text(size = 20),
        axis.title.x = element_text(size = 24),
        axis.title.y = element_text(size = 24),
        legend.position = c(.99, .99),
        legend.justification = c("right", "top"),
        legend.box.just = "right",
        legend.margin = margin(6, 6, 6, 6)
      ) +
      theme(legend.key = element_rect(fill = "white", color = "white")) +
      theme_bw()

    return(g)
  }
```

### parameters {.unlisted .unnumbered}

```{r message=FALSE, warning=FALSE}
main_dir <- dirname(dirname(getwd()))
datadir <- file.path(main_dir, "analysis/fmri/nilearn/glm/fir")
analysis_folder <- paste0("model52_iv-6cond_dv-firglasserSPM_ttl1")
analysis_dir <-
  file.path(main_dir,
            "analysis",
            "mixedeffect",
            analysis_folder,
            as.character(Sys.Date()))
dir.create(analysis_dir,
           showWarnings = FALSE,
           recursive = TRUE)
save_dir <- analysis_dir
```




## load data
```{r}

run_type <- "pain"

df.scl <- read.csv(paste0("/Users/h/Documents/projects_local/cue_expectancy/analysis/physio/physio01_SCL/sub-all_ses-all_run-all_runtype-", run_type,"_epochstart--3_epochend-20_samplingrate-25_ttlindex-2_physio-scltimecourse.csv"))
# fname example sub-0015_ses-01_run-06_runtype-vicarious_epochstart--3_epochend-20_baselinecorrect-True_samplingrate-25_ttlindex-1_physio-scltimecourse
column_mapping <- c("src_subject_id" = "sub", 
                    "session_id" = "ses", 
                    "param_run_num" = "run", 
                    "param_task_name" = "runtype",
                    "param_cue_type" = "cue", 
                    "param_stimulus_type" = "stimintensity", 
                    "event04_actual_angle" = "OUTCOME", 
                    "event02_expect_angle" = "EXPECT")
df.scl <- cueR::df_rename_columns(df.scl, column_mapping)
```


## downsample data!
```{r}
# downsample data to contain averaged columns at a 5Hz sampling rate
time_columns <- grep("time_", names(df.scl), value = TRUE)
downsampled_df <- df.scl  # Start with the original dataframe
# Loop through each set of five columns, calculate the mean, and store in new columns
for (i in seq(1, length(time_columns), by = 5)) {
    selected_columns <- time_columns[i:min(i+4, length(time_columns))]
    mean_column_name <- paste0("downsample_", (i-1)/5)
    downsampled_df[[mean_column_name]] <- rowMeans(df.scl[, selected_columns], na.rm = TRUE)
}



# Select only the new averaged columns along with any other non-time columns
non_time_columns <- setdiff(names(df.scl), time_columns)
new_time_columns <- grep("downsample_", names(downsampled_df), value = TRUE)
downsampled_df <- downsampled_df[, c(non_time_columns, new_time_columns)]



# convert to long ______________________________________________________________
df_long <-
  pivot_longer(
    downsampled_df,
    cols = starts_with("downsample"),
    names_to = "tr_num",
    values_to = "tr_value"
  )
```




## SCR 1) Cue X Stim effect 

```{r echo=FALSE, fig.width=10, fig.height=3}
# order variables ______________________________________________________________
TR_length <- 5 * 23-1

df_long$tr_ordered <- factor(df_long$tr_num,
                         levels = c(paste0("downsample_", 0:TR_length)))
df_long$cue_ordered <- factor(df_long$cue,
                           levels = c("high_cue", "low_cue"))
df_long$stim_ordered <- factor(df_long$stimintensity,
                           levels = c("high_stim", "med_stim", "low_stim"))
df_long$condition <- paste0(df_long$cue, "_", df_long$stimintensity)

df_long$sixcond <- factor(
  df_long$condition,
  levels = c(
    "high_cue_high_stim",
    "low_cue_high_stim",
    "high_cue_med_stim",
    "low_cue_med_stim",
    "high_cue_low_stim",
    "low_cue_low_stim"
  )
)



# summary statistic _____________________________________________________________
subjectwise <- meanSummary(df_long,
                           c("sub", "tr_ordered", "sixcond"), "tr_value")
groupwise <- summarySEwithin(
  data = subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c("sixcond", "tr_ordered"),
  idvar = "sub"
)
groupwise$task <- taskname


# plot parameters _____________________________________________________________
plot_list_per_roi <- list()
    groupwise$tr_numeric <- as.numeric(str_replace(groupwise$tr_ordered, "downsample_", "")) + 1
    groupwise$tr_sequence <-  groupwise$tr_numeric 
    LINEIV1 <- "tr_sequence"
    LINEIV2 <- "sixcond"
    MEAN <- "mean_per_sub_norm_mean"
    ERROR <- "se"
    dv_keyword <- "actual"
    sorted_indices <- order(groupwise$tr_ordered)
    groupwise_sorted <- groupwise[sorted_indices,]
    XLAB <- "TRs"
    YLAB <- "Stimulus Epoch High vs. Low cue"
    HIGHSTIM_COLOR <- c(
     "high_cue_high_stim" = "red",
      "low_cue_high_stim" = "#5f0f40",
      "high_cue_med_stim" = "NA",
      "low_cue_med_stim" = "NA",
      "high_cue_low_stim" = "NA",
      "low_cue_low_stim" = "NA"
    )
    MEDSTIM_COLOR <- c(
      "high_cue_high_stim" = "NA",
      "low_cue_high_stim" = "NA",
      "high_cue_med_stim" = "#bc3908",
      "low_cue_med_stim" = "#f6aa1c",
      "high_cue_low_stim" = "NA",
      "low_cue_low_stim" = "NA"
    )
    LOWSTIM_COLOR <- c(
      "high_cue_high_stim" = "NA",
      "low_cue_high_stim" = "NA",
      "high_cue_med_stim" = "NA",
      "low_cue_med_stim" = "NA",
      "high_cue_low_stim" = "#2541b2",
      "low_cue_low_stim" = "#00a6fb"
    )

    AXIS_FONTSIZE <- 10
    COMMONAXIS_FONTSIZE <- 15
    TITLE_FONTSIZE <- 20
    figure_width <- 10  # Adjust this to your actual figure width
    figure_height <- 10  # Adjust this to your actual figure height
    GEOMPOINT_SIZE <- .5 #calculate_point_size(figure_width, figure_height)

    # ----------------------------------------------------------------------------
    #                             plot intensity per task
    # ----------------------------------------------------------------------------
    p3H <- plot_timeseries_bar(
      groupwise,
      LINEIV1,
      LINEIV2,
      MEAN,
      ERROR,
      XLAB,
      YLAB,
      ggtitle = paste0(tools::toTitleCase(run_type), "\n High intensity (N = ", unique(groupwise$N), ")"),
      color_mapping = HIGHSTIM_COLOR,
      show_legend = FALSE,
      geompoint_size = GEOMPOINT_SIZE
    )

    # create tickmarks for every five second ________________________________________
    m <- (20 - (-3)) / (114 - 0)
    b <- -3 - m * 1
    # Function to calculate index for a given time
    get_index <- function(time) {
      round((time - b) / m)
    }
    labels_to_show <- c(-3, 0, 5, 10, 15, 20) # Desired timepoints
    breaks_to_show <- sapply(times, get_index) # Calculate corresponding indices


    # It's important to ensure that both 'breaks_to_show' and 'labels_to_show' have the same length
    # If the lengths differ, we need to adjust them so they match
    if (length(breaks_to_show) != length(labels_to_show)) {
      # Assuming you want to keep all the breaks and just adjust the labels
      labels_to_show <- labels_to_show[seq_along(breaks_to_show)]
    }

    # High intensity
    plot_list[["H"]] <- p3H +
      scale_x_continuous(
        breaks = breaks_to_show,
        # Set breaks at every 10th point
        labels = labels_to_show,
        # Use the calculated labels
        limits = range(groupwise$tr_sequence)  # Set the limits based on the sequence
      ) +
      theme_classic()

    # Medium intensity
    p3M <- plot_timeseries_bar(
      groupwise,
      LINEIV1,
      LINEIV2,
      MEAN,
      ERROR,
      XLAB,
      YLAB,
      ggtitle = paste0(
        tools::toTitleCase(run_type),
        "\n Medium intensity (N = ",
        unique(groupwise$N),
        ")"
      ),
      color_mapping = MEDSTIM_COLOR,
      show_legend = FALSE,
      geompoint_size = GEOMPOINT_SIZE
    )
    plot_list[["M"]] <- p3M +
      scale_x_continuous(
        breaks = breaks_to_show,        # Set breaks at every 10th point
        labels = labels_to_show,        # Use the calculated labels
        limits = range(groupwise$tr_sequence)  # Set the limits based on the sequence
      ) +
      theme_classic()

    # Low intensity
    p3L <- plot_timeseries_bar(
      groupwise,
      LINEIV1,
      LINEIV2,
      MEAN,
      ERROR,
      XLAB,
      YLAB,
      ggtitle = paste0(tools::toTitleCase(run_type), "\n Low intensity (N = ", unique(groupwise$N), ")"),
      color_mapping = LOWSTIM_COLOR,
      show_legend = FALSE,
      geompoint_size = GEOMPOINT_SIZE
    )
    plot_list[["L"]] <- p3L +
      scale_x_continuous(
        breaks = breaks_to_show,
        # Set breaks at every 10th point
        labels = labels_to_show,
        # Use the calculated labels
        limits = range(groupwise$tr_sequence)  # Set the limits based on the sequence
      ) +
      theme_classic()

# ----------------------------------------------------------------------------
    #                   combine three tasks in one panel per ROI
    # ----------------------------------------------------------------------------

    library(gridExtra)
    plot_list <- lapply(plot_list, function(plot) {
      plot +
        theme(
          plot.margin = margin(5, 5, 5, 5),          # Adjust plot margins if needed
          axis.title.y = element_blank(),          # Remove y-axis title
          axis.title.x = element_blank(),
          axis.text.y = element_text(size = AXIS_FONTSIZE),          # Increase y-axis text size
          axis.text.x = element_text(size = AXIS_FONTSIZE, angle = 30)
        )
    })
    combined_plot_per_run <-
      ggpubr::ggarrange(
        plot_list[["H"]],
        plot_list[["M"]],
        plot_list[["L"]],
        common.legend = FALSE,
        legend = "none",
        ncol = 3,
        nrow = 1,
        widths = c(3, 3, 3),
        heights = c(.5, .5, .5),
        align = "v"
      )

    # Add the combined plot for this run type to the list for the current ROI
    plot_list_per_roi[[run_type]] <- combined_plot_per_run


  # end of run loop

  # ----------------------------------------------------------------------------
  #                  add commom legend
  # ----------------------------------------------------------------------------
  legend_data <- data.frame(
    sixcond = factor(
      c(
        "cueH_stimH",
        "cueL_stimH",
        "cueH_stimM",
        "cueL_stimM",
        "cueH_stimL",
        "cueL_stimL"
      )
    ,
    levels = c(
      "cueH_stimH",
      "cueL_stimH",
      "cueH_stimM",
      "cueL_stimM",
      "cueH_stimL",
      "cueL_stimL"
    )
  ),
    color = c("red", "#5f0f40", "#bc3908", "#f6aa1c", "#2541b2", "#00a6fb"),
    stringsAsFactors = FALSE
  )

  legend_plot <-
    ggplot(legend_data, aes(x = sixcond, y = 1, color = sixcond)) +
    geom_point() +
    scale_color_manual(values = legend_data$color) +
    theme_void() +
    theme(legend.position = "bottom") +
    guides(color = guide_legend(title = "Condition"))

  legend_grob <-
    ggplotGrob(legend_plot)$grobs[[which(sapply(ggplotGrob(legend_plot)$grobs, function(x)
      x$name) == "guide-box")]]
  heights <- c(rep(1, length(run_types)), 2)
  # ----------------------------------------------------------------------------
  #                  common axes for the 9 panels
  # ----------------------------------------------------------------------------
  y_axis_label <-
    textGrob(
      "SCR BOLD \n(high > low cue; stimulus epoch)",
      rot = 90,
      gp = gpar(fontsize = COMMONAXIS_FONTSIZE)
    )
    x_axis_label <-
    textGrob(
      "SCR timecourse (s; 25 hz)",
      rot = 0,
      gp = gpar(fontsize = COMMONAXIS_FONTSIZE)
    )
  num_rows <- length(plot_list_per_roi) + 1  # +1 for the legend
  # ----------------------------------------------------------------------------
  #                  combined plots across 3 tasks
  # ----------------------------------------------------------------------------
  roi_combined_plot <-
    do.call(grid.arrange, c(plot_list_per_roi, ncol = 1))
roi <- "pain"
  final_plot <- grid.arrange(
    y_axis_label,
    arrangeGrob(
      roi_combined_plot,
     x_axis_label,
      legend_grob,

      ncol = 1,
      heights = c(11,.5, 1)
    ),
    ncol = 2,
    widths = c(1, 10),    # Relative widths for the label, plots, and legend,
    top = textGrob(sprintf("%s Time series per task", roi), gp = gpar(
      fontsize = TITLE_FONTSIZE, fontface = "bold"
    ))  # title parameter
  )
  grid.draw(final_plot)


  # # ----------------------------------------------------------------------------
  # #                 save all plots
  # # ----------------------------------------------------------------------------
  # ggsave(file.path(
  #   save_dir,
  #   paste0("roi-",
  #          roi ,
  #          "_epoch-stim_desc-stimcuecomparison.png")
  # ),
  # all_plots[[roi]],
  # width = 12,
  # height = 20)

```



## SCR 2) cue effect

> There is a significant SCR effect of cue. High cues lead to greater SCR response during the pain stimulus phase

```{r}
# 1. order variables ______________________________________________________________
TR_length <- 5 * 23-1

df_long$tr_ordered <- factor(df_long$tr_num,
                         levels = c(paste0("downsample_", 0:TR_length)))
df_long$cue_ordered <- factor(df_long$cue,
                           levels = c("high_cue", "low_cue"))
# df_long$stim_ordered <- factor(df_long$stimintensity,
#                            levels = c("high_stim", "med_stim", "low_stim"))
df_long$condition <- paste0(df_long$cue, "_", df_long$stimintensity)



# 2. summary statistic _____________________________________________________________
cuesubjectwise <- meanSummary(df_long,
                           c("sub", "tr_ordered", "cue_ordered"), "tr_value")
cuegroupwise <- summarySEwithin(
  data = cuesubjectwise,
  measurevar = "mean_per_sub",
  withinvars = c("cue_ordered", "tr_ordered"),
  idvar = "sub"
)
cuegroupwise$task <- taskname



# 3. plot parameters _____________________________________________________________
plot_list_per_roi <- list()
cuegroupwise$tr_numeric <- as.numeric(str_replace(cuegroupwise$tr_ordered, "downsample_", "")) + 1
cuegroupwise$tr_sequence <-  cuegroupwise$tr_numeric 
LINEIV1 <- "tr_sequence"
LINEIV2 <- "cue_ordered"
MEAN <- "mean_per_sub_norm_mean"
ERROR <- "se"
dv_keyword <- "actual"
sorted_indices <- order(cuegroupwise$tr_ordered)
groupwise_sorted <- cuegroupwise[sorted_indices,]
XLAB <- "TRs"
YLAB <- "Stimulus Epoch High vs. Low cue"

AXIS_FONTSIZE <- 10
COMMONAXIS_FONTSIZE <- 15
TITLE_FONTSIZE <- 20
figure_width <- 10  # Adjust this to your actual figure width
figure_height <- 10  # Adjust this to your actual figure height
GEOMPOINT_SIZE <- .1 #calculate_point_size(figure_width, figure_height)



# 4. plot _________________________________________________________________________
p1 <- plot_timeseries_bar(
  groupwise_sorted,
  LINEIV1,
  LINEIV2,
  MEAN,
  ERROR,
  xlab = "TRs",
  ylab = paste0("SCR (A.U.)"),
  ggtitle = paste0(run_type, " time series, Epoch - stimulus"),
  color = c("#D73027", "#4575B4")
)
p1 <- p1 + theme_classic()



# 5. create tickmarks for every five second ________________________________________
m <- (20 - (-3)) / (114 - 0)
b <- -3 - m * 1
get_index <- function(time) {
  round((time - b) / m) # Function to calculate index for a given time
}
labels_to_show <- c(-3, 0, 5, 10, 15, 20) # Desired timepoints
breaks_to_show <- sapply(times, get_index) # Calculate corresponding indices
# It's important to ensure that both 'breaks_to_show' and 'labels_to_show' have the same length
# If the lengths differ, we need to adjust them so they match
if (length(breaks_to_show) != length(labels_to_show)) {
  # Assuming you want to keep all the breaks and just adjust the labels
  labels_to_show <- labels_to_show[seq_along(breaks_to_show)]
}

# 6. layer in tick marks ________________________________________
p1 <- p1 +
  scale_x_continuous(
    breaks = breaks_to_show,
    labels = labels_to_show,
    limits = range(groupwise$tr_sequence)  # Set the limits based on the sequence
  ) +
  theme_classic()
ggplot_largetext(p1)
```


## SCR 3) stim effect


> There is a significant SCR effect of intensity. High intensity indeed leads to greater SCR response during the pain stimulus phase

```{r}
# 1. order variables ______________________________________________________________
TR_length <- 5 * 23-1

df_long$tr_ordered <- factor(df_long$tr_num,
                         levels = c(paste0("downsample_", 0:TR_length)))
# df_long$cue_ordered <- factor(df_long$cue,
#                            levels = c("high_cue", "low_cue"))
df_long$stim_ordered <- factor(df_long$stimintensity,
                           levels = c("high_stim", "med_stim", "low_stim"))
df_long$condition <- paste0(df_long$cue, "_", df_long$stimintensity)



# 2. summary statistic _____________________________________________________________
stimsubjectwise <- meanSummary(df_long,
                           c("sub", "tr_ordered", "stim_ordered"), "tr_value")
stimgroupwise <- summarySEwithin(
  data = stimsubjectwise,
  measurevar = "mean_per_sub",
  withinvars = c("stim_ordered", "tr_ordered"),
  idvar = "sub"
)
stimgroupwise$task <- taskname



# 3. plot parameters _____________________________________________________________
plot_list_per_roi <- list()
stimgroupwise$tr_numeric <- as.numeric(str_replace(stimgroupwise$tr_ordered, "downsample_", "")) + 1
stimgroupwise$tr_sequence <-  stimgroupwise$tr_numeric 
LINEIV1 <- "tr_sequence"
LINEIV2 <- "stim_ordered"
MEAN <- "mean_per_sub_norm_mean"
ERROR <- "se"
dv_keyword <- "actual"
sorted_indices <- order(stimgroupwise$tr_ordered)
groupwise_sorted <- stimgroupwise[sorted_indices,]
XLAB <- "Time series (s)"
YLAB <- "Stimulus Epoch High vs. Low stim"

AXIS_FONTSIZE <- 10
COMMONAXIS_FONTSIZE <- 15
TITLE_FONTSIZE <- 20
figure_width <- 10  # Adjust this to your actual figure width
figure_height <- 10  # Adjust this to your actual figure height
GEOMPOINT_SIZE <- .1 #calculate_point_size(figure_width, figure_height)



# 4. plot _________________________________________________________________________
p1 <- plot_timeseries_bar(
  groupwise_sorted,
  LINEIV1,
  LINEIV2,
  MEAN,
  ERROR,
  xlab = "TRs",
  ylab = paste0("SCR (A.U.)"),
  ggtitle = paste0(run_type, " time series, Epoch - stimulus"),
  color =  c("#5f0f40", "#ae2012", "#fcbf49")
)
p1 <- p1 + theme_classic()



# 5. create tickmarks for every five second ________________________________________
m <- (20 - (-3)) / (114 - 0)
b <- -3 - m * 1
get_index <- function(time) {
  round((time - b) / m) # Function to calculate index for a given time
}
labels_to_show <- c(-3, 0, 5, 10, 15, 20) # Desired timepoints
breaks_to_show <- sapply(times, get_index) # Calculate corresponding indices
# It's important to ensure that both 'breaks_to_show' and 'labels_to_show' have the same length
# If the lengths differ, we need to adjust them so they match
if (length(breaks_to_show) != length(labels_to_show)) {
  # Assuming you want to keep all the breaks and just adjust the labels
  labels_to_show <- labels_to_show[seq_along(breaks_to_show)]
}

# 6. layer in tick marks ________________________________________
p1 <- p1 +
  scale_x_continuous(
    breaks = breaks_to_show,
    labels = labels_to_show,
    limits = range(groupwise$tr_sequence)  # Set the limits based on the sequence
  ) +
  theme_classic()
ggplot_largetext(p1)
```



## SCR 4) stim effect across tasks for loop
```{r echo=FALSE, fig.width=9}
run_types <- c("pain", "vicarious", "cognitive")
plot_list <- list()
TR_length <- 42



for (run_type in run_types) {
  
  # 1. load data _______________________________________________________________
  df.scl <- read.csv(paste0("/Users/h/Documents/projects_local/cue_expectancy/analysis/physio/physio01_SCL/sub-all_ses-all_run-all_runtype-",run_type,"_epochstart--3_epochend-20_samplingrate-25_ttlindex-1_physio-scltimecourse.csv"))

  column_mapping <- c("src_subject_id" = "sub", 
                      "session_id" = "ses", 
                      "param_run_num" = "run", 
                      "param_task_name" = "runtype",
                      "param_cue_type" = "cue", 
                      "param_stimulus_type" = "stimintensity", 
                      "event04_actual_angle" = "OUTCOME", 
                      "event02_expect_angle" = "EXPECT")
  df.scl <- cueR::df_rename_columns(df.scl, column_mapping)
  
  
  
  # 2. downsample data ____________________________________________________________
  # ___ 1) to contain averaged columns at a 5Hz sampling rate 
  time_columns <- grep("time_", names(df.scl), value = TRUE)
  downsampled_df <- df.scl  # Start with the original dataframe
  # ___ 2) Loop through each set of five columns, calculate the mean, and store in new columns
  for (i in seq(1, length(time_columns), by = 5)) {
      selected_columns <- time_columns[i:min(i+4, length(time_columns))]
      mean_column_name <- paste0("downsample_", (i-1)/5)
      downsampled_df[[mean_column_name]] <- rowMeans(df.scl[, selected_columns], na.rm = TRUE)
  }
  # ___ 3) Select only the new averaged columns along with any other non-time columns
  non_time_columns <- setdiff(names(df.scl), time_columns)
  new_time_columns <- grep("downsample_", names(downsampled_df), value = TRUE)
  downsampled_df <- downsampled_df[, c(non_time_columns, new_time_columns)]
  
  
  
  # 3. convert to long ______________________________________________________________
  df_long <-
    pivot_longer(
      downsampled_df,
      cols = starts_with("downsample"),
      names_to = "tr_num",
      values_to = "tr_value"
    )
  
  # 4. order variables ______________________________________________________________
  TR_length <- 5 * 23-1
  
  df_long$tr_ordered <- factor(df_long$tr_num,
                           levels = c(paste0("downsample_", 0:TR_length)))
  # df_long$cue_ordered <- factor(df_long$cue,
  #                            levels = c("high_cue", "low_cue"))
  df_long$stim_ordered <- factor(df_long$stimintensity,
                             levels = c("high_stim", "med_stim", "low_stim"))
  df_long$condition <- paste0(df_long$cue, "_", df_long$stimintensity)
  
  
  
  # 5. summary statistic _____________________________________________________________
  stimsubjectwise <- meanSummary(df_long,
                             c("sub", "tr_ordered", "stim_ordered"), "tr_value")
  stimgroupwise <- summarySEwithin(
    data = stimsubjectwise,
    measurevar = "mean_per_sub",
    withinvars = c("stim_ordered", "tr_ordered"),
    idvar = "sub"
  )
  stimgroupwise$task <- taskname
  
  
  
  # 6. plot parameters _____________________________________________________________
  plot_list_per_roi <- list()
  stimgroupwise$tr_numeric <- as.numeric(str_replace(stimgroupwise$tr_ordered, "downsample_", "")) + 1
  stimgroupwise$tr_sequence <-  stimgroupwise$tr_numeric 
  LINEIV1 <- "tr_sequence"
  LINEIV2 <- "stim_ordered"
  MEAN <- "mean_per_sub_norm_mean"
  ERROR <- "se"
  dv_keyword <- "actual"
  sorted_indices <- order(stimgroupwise$tr_ordered)
  groupwise_sorted <- stimgroupwise[sorted_indices,]
  XLAB <- "Time series (s)"
  YLAB <- "Stimulus Epoch High vs. Low stim"
  
  AXIS_FONTSIZE <- 10
  COMMONAXIS_FONTSIZE <- 15
  TITLE_FONTSIZE <- 20
  figure_width <- 10  # Adjust this to your actual figure width
  figure_height <- 10  # Adjust this to your actual figure height
  GEOMPOINT_SIZE <- .1 #calculate_point_size(figure_width, figure_height)
  
  
  
  # 7. plot _________________________________________________________________________
  p1 <- plot_timeseries_bar(
    groupwise_sorted,
    LINEIV1,
    LINEIV2,
    MEAN,
    ERROR,
    xlab = "TRs",
    ylab = paste0("SCR (A.U.)"),
    ggtitle = paste0(run_type, " time series, Epoch - stimulus"),
    color =  c("#5f0f40", "#ae2012", "#fcbf49")
  )
  p1 <- p1 + theme_classic()
  
  
  
  # 8. create tickmarks for every five second ________________________________________
  m <- (20 - (-3)) / (114 - 0)
  b <- -3 - m * 1
  get_index <- function(time) {
    round((time - b) / m) # Function to calculate index for a given time
  }
  labels_to_show <- c(-3, 0, 5, 10, 15, 20) # Desired timepoints
  breaks_to_show <- sapply(times, get_index) # Calculate corresponding indices
  # It's important to ensure that both 'breaks_to_show' and 'labels_to_show' have the same length
  # If the lengths differ, we need to adjust them so they match
  if (length(breaks_to_show) != length(labels_to_show)) {
    # Assuming you want to keep all the breaks and just adjust the labels
    labels_to_show <- labels_to_show[seq_along(breaks_to_show)]
  }
  
  # 9. layer in tick marks ________________________________________
  p1 <- p1 +
    scale_x_continuous(
      breaks = breaks_to_show,
      labels = labels_to_show,
      limits = range(groupwise$tr_sequence)  # Set the limits based on the sequence
    ) +
    theme_classic()
  # ggplot_largetext(p1)
  plot_list[[run_type]] <- ggplot_largetext(p1) + theme_classic()
}

# combine and plot ______________________________________________________________
  library(gridExtra)
  plot_list <- lapply(plot_list, function(plot) {
    plot + theme(plot.margin = margin(5, 5, 5, 5)) # Adjust plot margins if needed
  })
  combined_plot <- ggpubr::ggarrange(
    plot_list[["pain"]],
    plot_list[["vicarious"]],
    plot_list[["cognitive"]],
    common.legend = TRUE,
    legend = "bottom",
    ncol = 3,
    nrow = 1,
    widths = c(3, 3, 3),
    heights = c(.5, .5, .5),
    align = "v"
  )
  print(combined_plot)
```



