# {{ MODULE }} ::  {{ DV }} ~  {{ IV }} {#KEYWORD}

## What is the purpose of this notebook? {.unlisted .unnumbered}

Here, we want to... {{ INSERT }} 

* Main model: `lmer( {{ INSERT YOUR MODEL }})` 
* Main question: {{ INSERT YOUR QUESTION }}? 
* {{ HYPOTHESES/EXPECTED OUTCOME }}
* 
* IV: 
  - {{ FACTOR NAME }} ( {{ LEVELS}} )
* DV: {{ DV }}


### TODO: 
```
INSERT HERE
```

### References : Once note book is complete, add at the bottom of Rmd
```
INSERT HERE
```

### load libraries {.unlisted .unnumbered}
```{r message=FALSE, warning=FALSE, include=FALSE}

```


### display distribution of data
Let's look at the distribution of the data. X axis: Y axis: 
```{r paged.print=TRUE}

```
> Summary: 

### plot {.unlisted .unnumbered}
We'll plot Y as a function of A and B
X axis: 
Y axis:
Each data point indicates ... 
```{r fig.height=10, fig.width=10}

```
> Conclusion:


:::: {.infobox}
Include the actual content here. here are my thoughts
::::

:::: {.refbox}
Include the actual content here. here are my thoughts
::::

