---
title: "c04_NPS_painrating"
author: "Heejung Jung"
date: "2/22/2022"
output: html_document
---

---
title: "c03_NPS_ICC"
author: "Heejung Jung"
date: "2/22/2022"
output: html_document
---

* load csv file in 
* calculate summary of dataframe
* average NPS rating per temperature
* average NPS rating per session
* calculate ICC "two-way random effects"

```{r}
library(psych)
library(car)
library(lmSupport)
library(lme4)
library(lmerTest)
library(plyr)
#library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(ggpubr)
library(irr)
library(ICC)
source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
```

# Functions _____________________________________________________________________


### FUNCTION: normdatawithin
```{r}
normDataWithin <- function(data=NULL, idvar, measurevar, betweenvars=NULL,
                           na.rm=FALSE, .drop=TRUE) {
  ## Norms the data within specified groups in a data frame; it normalizes each
## subject (identified by idvar) so that they have the same mean, within each group
## specified by betweenvars.
##   data: a data frame.
##   idvar: the name of a column that identifies each subject (or matched subjects)
##   measurevar: the name of a column that contains the variable to be summariezed
##   betweenvars: a vector containing names of columns that are between-subjects variables
##   na.rm: a boolean that indicates whether to ignore NA's
    library(plyr)

    # Measure var on left, idvar + between vars on right of formula.
    data.subjMean <- ddply(data, c(idvar, betweenvars), .drop=.drop,
     .fun = function(xx, col, na.rm) {
        c(subjMean = mean(xx[,col], na.rm=na.rm))
      },
      measurevar,
      na.rm
    )

    # Put the subject means with original data
    data <- merge(data, data.subjMean)

    # Get the normalized data in a new column
    measureNormedVar <- paste(measurevar, "_norm", sep="")
    data[,measureNormedVar] <- data[,measurevar] - data[,"subjMean"] +
                               mean(data[,measurevar], na.rm=na.rm)

    # Remove this subject mean column
    data$subjMean <- NULL

    return(data)
}
```

### FUNCTION: summarySEwithin
```{r}
summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=NULL,
                            idvar=NULL, na.rm=FALSE, conf.interval=.95, .drop=TRUE) {

  ## Summarizes data, handling within-subjects variables by removing inter-subject variability.
## It will still work if there are no within-S variables.
## Gives count, un-normed mean, normed mean (with same between-group mean),
##   standard deviation, standard error of the mean, and confidence interval.
## If there are within-subject variables, calculate adjusted values using method from Morey (2008).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   betweenvars: a vector containing names of columns that are between-subjects variables
##   withinvars: a vector containing names of columns that are within-subjects variables
##   idvar: the name of a column that identifies each subject (or matched subjects)
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
  # Ensure that the betweenvars and withinvars are factors
  factorvars <- vapply(data[, c(betweenvars, withinvars), drop=FALSE],
    FUN=is.factor, FUN.VALUE=logical(1))

  if (!all(factorvars)) {
    nonfactorvars <- names(factorvars)[!factorvars]
    message("Automatically converting the following non-factors to factors: ",
            paste(nonfactorvars, collapse = ", "))
    data[nonfactorvars] <- lapply(data[nonfactorvars], factor)
  }

  # Get the means from the un-normed data
  datac <- summarySE(data, measurevar, groupvars=c(betweenvars, withinvars),
                     na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Drop all the unused columns (these will be calculated with normed data)
  datac$sd <- NULL
  datac$se <- NULL
  datac$ci <- NULL

  # Norm each subject's data
  ndata <- normDataWithin(data, idvar, measurevar, betweenvars, na.rm, .drop=.drop)

  # This is the name of the new column
  measurevar_n <- paste(measurevar, "_norm", sep="")

  # Collapse the normed data - now we can treat between and within vars the same
  ndatac <- summarySE(ndata, measurevar_n, groupvars=c(betweenvars, withinvars),
                      na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Apply correction from Morey (2008) to the standard error and confidence interval
  #  Get the product of the number of conditions of within-S variables
  nWithinGroups    <- prod(vapply(ndatac[,withinvars, drop=FALSE], FUN=nlevels,
                           FUN.VALUE=numeric(1)))
  correctionFactor <- sqrt( nWithinGroups / (nWithinGroups-1) )

  # Apply the correction factor
  ndatac$sd <- ndatac$sd * correctionFactor
  ndatac$se <- ndatac$se * correctionFactor
  ndatac$ci <- ndatac$ci * correctionFactor

  # Combine the un-normed means with the normed results
  df = merge(datac, ndatac)
  return(df)
  
}
```

### FUNCTION: meanSummary
```{r}
meanSummary <- function(DATA, GROUP, DV){
  z <- ddply(DATA, GROUP, .fun = function(xx){
                         c(mean_per_sub = mean(xx[,DV],na.rm=TRUE),
                         sd = sd(xx[,DV],na.rm=TRUE) ) })
  return(z)
  }
```

### FUNCTION: plot_expect_rainclouds
```{r}
# data within_average
# DV = mean_per_sub
# IV = param_cue_type
plot_expect_rainclouds = function(within_average, group_level_condition_average, 
                                  fill_IV, SUB_MEAN, GROUP_MEAN, SE, SUBJECT,
                                  GGTITLE, TITLE, XLAB, YLAB,task_name, w, h, DV_KEYWORD,COLOR, SAVE_FNAME) {
g <- ggplot(data = within_average, 
            aes(y = .data[[SUB_MEAN]], x = factor(.data[[fill_IV]]), fill =  factor(.data[[fill_IV]]))) +
  geom_flat_violin(aes(fill =  factor(.data[[fill_IV]])), position = position_nudge(x = .1, y = 0), 
                   adjust = 1.5, trim = FALSE, alpha = .3, colour = NA) +
  geom_line(data = within_average,
           aes(group = .data[[SUBJECT]], y = .data[[SUB_MEAN]], x = as.numeric( .data[[fill_IV]] )-.15, 
               fill =  factor(.data[[fill_IV]])), linetype = "solid", color = "grey", alpha = .3) +
  geom_point(aes(x = as.numeric( .data[[fill_IV]])-.15, y = .data[[SUB_MEAN]], color = factor(.data[[fill_IV]])),
             position = position_jitter(width = .05), size = 1, alpha = 0.8, shape = 20) +
  geom_boxplot(aes(x =  .data[[fill_IV]], y = .data[[SUB_MEAN]], fill =  .data[[fill_IV]]), width = .1,
               outlier.shape = NA, alpha = 0.8, width = .1, colour = "black") +
  geom_errorbar(data = group_level_condition_average, 
                aes(x = as.numeric( .data[[fill_IV]])+.1, y = as.numeric(.data[[GROUP_MEAN]]), 
                   colour =  factor(.data[[fill_IV]]), 
                   ymin =  .data[[GROUP_MEAN]] - .data[[SE]], 
                   ymax =  .data[[GROUP_MEAN]] + .data[[SE]]), width = .05) +

  # legend stuff __________________________________________________________________________________
  expand_limits(x = 2.8) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  guides(fill=guide_legend(title=TITLE))+
  scale_fill_manual(values = COLOR)+
  scale_color_manual(values = COLOR)+

  ggtitle(GGTITLE) +
  # coord_flip() + #vertical vs horizontal
  xlab(XLAB) +
  ylab(YLAB) +
  theme_bw() 
ggsave(SAVE_FNAME, width = w, height = h)
return(g)

}
```
### FUNCTION: plot_actual_rainclouds
```{r}
plot_actual_rainclouds = function(subjectwise, groupwise, 
                                  IV1, IV2, SUB_MEAN, GROUP_MEAN, SE, SUBJECT, GGTITLE, TITLE, XLAB,YLAB,task_name, w, h, DV_KEYWORD,COLOR,SAVE_FNAME) {

g <- ggplot(data = subjectwise, aes(y = .data[[SUB_MEAN]], x = .data[[IV1]], fill = .data[[IV2]])) +
  geom_flat_violin(aes(fill = .data[[IV2]]), position = position_nudge(x = .1, y = 0), adjust = 1.5,
                   trim = FALSE, alpha = .3, colour = NA) +
  geom_line(data = subjectwise, aes(group = .data[[SUBJECT]], y = .data[[SUB_MEAN]], x = as.numeric(.data[[IV1]])-.15, fill = .data[[IV2]]), linetype = 3, color = "grey") +
  #geom_point(aes(group = subject, x = as.numeric(IV1)-.15, y = mean_per_sub, color = IV2),
 #            position = position_jitter(width = .05), size = 1, alpha = 0.8, shape = 20) +
  geom_point(data = subjectwise, aes(x = as.numeric(.data[[IV1]])-.15, 
                                     y = .data[[SUB_MEAN]], color =.data[[IV2]]),
             position = position_jitter(width = .05), size = 1, alpha = 0.8, shape = 20) +
  geom_boxplot(data = subjectwise, aes(x = .data[[IV1]], y = .data[[SUB_MEAN]], fill = .data[[IV2]]),width = .1,
               outlier.shape = NA, alpha = 0.8, width = .1, colour = "black") +

  # use summary stats __________________________________________________________________________________

  geom_errorbar(data = groupwise, aes(x = as.numeric(.data[[IV1]])+.1, y = .data[[GROUP_MEAN]],
                              group = .data[[IV2]], colour = .data[[IV2]], 
                              ymin = .data[[GROUP_MEAN]] - .data[[SE]], 
                              ymax = .data[[GROUP_MEAN]] + .data[[SE]]), width = .05) +

  # legend stuff __________________________________________________________________________________
  expand_limits(x = 3.25) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  guides(fill=guide_legend(title="social cues"))+
  #scale_color_brewer(palette = "Dark2") +
  #scale_fill_brewer(palette = "Dark2") +
  scale_fill_manual(values = COLOR)+
  scale_color_manual(values = COLOR)+
  ggtitle(GGTITLE) +
  # coord_flip() + #vertical vs horizontal
  xlab("Stimulus intensity levels") +
  ylab("Degrees of actual ratings") +
  theme_bw() 

g
#w = 5
#h = 3

ggsave(SAVE_FNAME, width = w, height = h)

}
```


```{r}
run_cue_lmer = function(DATA,TASKNAME, IV, DV, SUBJECT, DV_KEYWORD, MODEL_SAVE){
  model.cue = lmer( DATA[,DV] ~ DATA[,IV] + (DATA[,IV] | DATA[,SUBJECT]) )
  print(paste("model: ", str_to_title(DV_KEYWORD), " ratings - ", TASKNAME))
  print(summary(model.cue))
  sink(MODEL_SAVE)
  print(summary(model.cue))
  sink()
  cooksd <- cooks.distance(model.cue)
  return(cooksd)
  }
```

# load csv file in 
```{r}
main_dir = '/Volumes/spacetop_projects_social'
filename = '/Volumes/spacetop_projects_social/analysis/mixedeffect/nps/ttlonset_nps-dotproduct_2022-02-21.csv'
df = read.csv(filename)
```

# plot NPS pain rating per temperature
```{r}
DATA = subset(df, task == 'pain-plateau')
DATA =  DATA %>%
  group_by(sub_num) %>%
  mutate_at(vars(actual_rating), list(scaled = scale))

```


# 1. average NPS rating per temperature 
# rescale NPS and pain rating
# fit a linear model (pain_rating ~ NPS) and grab the beta coefficients
# plot beta
```{r}
# DATA = subset(df, task == 'pain-plateau')
main_dir = '/Users/h/Dropbox/projects_dropbox/social_influence_analysis/'
for (TASKNAME in c("pain-early", "pain-late", "pain-post", "pain-plateau")){
DATA = subset(df, task == TASKNAME)
DATA =  DATA %>%
  group_by(sub_num) %>%
  mutate_at(vars(actual_rating), list(scaled = scale))
# run_cue_lmer( DATA,"NPS pain rating", "scaled", "nps", "sub_num", "NPS response", MODEL_SAVE)
DATA$demean_ACTUAL = DATA$actual_rating -mean(DATA$actual_rating)
DATA$demean_EXPECT = DATA$expect_rating -mean(DATA$expect_rating)
model.npspain = lmer(  nps_corr~demean_ACTUAL + (demean_ACTUAL | sub_num) , DATA)
summary(model.npspain)
model.npspainexpect = lmer( nps_corr~demean_EXPECT + (demean_EXPECT | sub_num) , DATA)
fixEffect_expect <<-as.data.frame(fixef(model.npspainexpect))
randEffect_expect <<-as.data.frame(ranef(model.npspainexpect))
rand_subset = subset(randEffect_expect, select  = -c(grpvar, term, condsd))
# wide_rand = spread(rand_subset, key = grp, value = condval)
rand_subset$task = TASKNAME
wide_fix = do.call("rbind", replicate(nrow(rand_subset), as.data.frame(t(as.matrix(fixEffect_expect))), simplify = FALSE))
rownames(wide_fix)<-NULL

summary(model.npspainexpect)

# TODO:
# plot random effect slope and NPS average rating
a = ggplot(data = DATA, aes(x = actual_rating, y = nps)) +
  geom_point(color = 'black') +
  stat_smooth(method = 'lm') +
  theme_classic()

e = ggplot(data = DATA, aes(x = expect_rating, y = nps)) +
  geom_point(color = 'red') +
  stat_smooth(method = 'lm') + 
  theme_classic()
ggpubr::ggarrange(a,e,ncol =2, nrow = 1, common.legend = FALSE,legend = "bottom")
plot_filename = file.path(main_dir, 'analysis','mixedeffect','nps', paste('socialinfluence_task-',TASKNAME,'_',DV_KEYWORD,'_icc','_', as.character(Sys.Date()),'.png', sep = ""))
ggsave(plot_filename, width = 10, height = 3)
}

```
```{r}
ggplot(data = DATA, aes(x = actual_rating, y = nps)) +
  geom_point(color = 'black') +
  stat_smooth(method = 'lm') +
  theme_classic()

ggplot(data = DATA, aes(x = expect_rating, y = nps)) +
  geom_point(color = 'red') +
  stat_smooth(method = 'lm') + 
  theme_classic()

```
```{r}
ggplot(data = DATA, aes(x = expect_rating, y = nps)) +
  geom_point(color = 'red') +
  stat_smooth(method = 'lm')

```


# 
```{r}
DATA = subset(df, task == 'pain-plateau')
SUBJECT = "sub_num"
IV1 = "actual_rating"
IV2 = "stim_type"
DV = "nps"
DATA$sub_num = factor(DATA$sub_num)
# DATA$task <- factor(DATA$task, levels = c("pain-early", "pain-late", "pain-post", "pain-plateau", "pain"))
subjectwise_npstemp = meanSummary(DATA, c(SUBJECT, IV1,IV2), DV)
groupwise_npstemp = summarySEwithin(data=subjectwise_npstemp, 
                  measurevar = "mean_per_sub", # variable created from above
                    withinvars = c(IV1,IV2), # IV
                    idvar = "sub_num")
groupwise_npstempdrp <- na.omit(groupwise_npstemp)
```

```{r}
temp_nps = subset(subjectwise_temp,select = c("sub_num", "stim_type", "mean_per_sub"))
temp_nps_wide = reshape(temp_nps, idvar = "sub_num", timevar = "stim_type", direction = "wide")
```
```{r}
ICC(temp_nps_wide[,c("mean_per_sub.high_stim", "mean_per_sub.low_stim")])
c50_icc = icc(
  temp_nps_wide[,c("mean_per_sub.high_stim", "mean_per_sub.low_stim")], model = "twoway", 
  type = "agreement", unit = "single"
  )
c50_icc

ICC(temp_nps_wide[,c("mean_per_sub.high_stim", "mean_per_sub.med_stim")])
c49_icc = icc(
  temp_nps_wide[,c("mean_per_sub.high_stim", "mean_per_sub.med_stim")], model = "twoway", 
  type = "agreement", unit = "single"
  )
c49_icc

ICC(temp_nps_wide[,c("mean_per_sub.med_stim", "mean_per_sub.low_stim")])
c48_icc = icc(
  temp_nps_wide[,c("mean_per_sub.med_stim", "mean_per_sub.low_stim")], model = "twoway", 
  type = "agreement", unit = "single"
  )
c48_icc
```
```{r}
ggplot(data = temp_nps_wide, aes(x = mean_per_sub.high_stim, y = mean_per_sub.low_stim)) +
  geom_point(color = 'red') +
  stat_smooth(method = 'lm')

ggplot(data = temp_nps_wide, aes(x = mean_per_sub.high_stim, y = mean_per_sub.med_stim)) +
  geom_point(color = 'red') +
  stat_smooth(method = 'lm')

ggplot(data = temp_nps_wide, aes(x = mean_per_sub.med_stim, y = mean_per_sub.low_stim)) +
  geom_point(color = 'red') +
  stat_smooth(method = 'lm')
```


# 2. ICC per session
```{r}
DATA = subset(df, task == 'pain-plateau')
SUBJECT = "sub_num"
IV = "ses_num"
DV = "nps"
DATA$sub_num = factor(DATA$sub_num)
# DATA$task <- factor(DATA$task, levels = c("pain-early", "pain-late", "pain-post", "pain-plateau", "pain"))
subjectwise_ses = meanSummary(DATA, c(SUBJECT, IV), DV)
groupwise_ses = summarySEwithin(data=subjectwise_ses, 
                  measurevar = "mean_per_sub", # variable created from above
                    withinvars = c(IV), # IV
                    idvar = "sub_num")
groupwise_drop_ses <- na.omit(groupwise_ses)
```
```{r}
ses_nps = subset(subjectwise_ses,select = c("sub_num", "ses_num", "mean_per_sub"))
ses_nps_wide = reshape(ses_nps, idvar = "sub_num", timevar = "ses_num", direction = "wide")
```
```{r}
ICC(ses_nps_wide[,c("mean_per_sub.4", "mean_per_sub.1")])
ses4_1_icc = icc(
  ses_nps_wide[,c("mean_per_sub.4", "mean_per_sub.1")], model = "twoway", 
  type = "agreement", unit = "single"
  )
ses4_1_icc

ICC(ses_nps_wide[,c("mean_per_sub.4", "mean_per_sub.3")])
ses4_3_icc = icc(
  ses_nps_wide[,c("mean_per_sub.4", "mean_per_sub.3")], model = "twoway", 
  type = "agreement", unit = "single"
  )
ses4_3_icc

ICC(ses_nps_wide[,c("mean_per_sub.3", "mean_per_sub.1")])
ses3_1_icc = icc(
  ses_nps_wide[,c("mean_per_sub.3", "mean_per_sub.1")], model = "twoway", 
  type = "agreement", unit = "single"
  )
ses3_1_icc
```
```{r}
ggplot(data = ses_nps_wide, aes(x = mean_per_sub.4, y = mean_per_sub.1)) +
  geom_point(color = 'red') +
  stat_smooth(method = 'lm')

ggplot(data = ses_nps_wide, aes(x = mean_per_sub.4, y = mean_per_sub.3)) +
  geom_point(color = 'red') +
  stat_smooth(method = 'lm')

ggplot(data = ses_nps_wide, aes(x = mean_per_sub.3, y = mean_per_sub.1)) +
  geom_point(color = 'red') +
  stat_smooth(method = 'lm')
```



```{r}
c = subset(temp_nps_wide, stim_type == "high_stim")
c50_icc = icc(
  c50[,-1], model = "twoway", 
  type = "agreement", unit = "average"
  )
c50_icc
```

# ICC for temp
```{r}
DATA = subset(df, task == 'pain-plateau' & stim_type == "high_stim")
TDATA <- DATA %>%
        group_by(sub_num) %>%
        mutate(index = seq_along(sub_num))
temp_nps = subset(TDATA,select = c("sub_num", "index", "nps"))

temp_nps_wide = temp_nps %>% 
  group_by(index) %>% 
  spread(sub_num,nps)

c50_icc = icc(
  temp_nps_wide[,-1], model = "twoway", 
  type = "agreement", unit = "single"
  )
c50_icc
ICC(temp_nps_wide[,-1])
```

# average NPS rating per session
```{r}
DATA = subset(df, task == 'pain-plateau')
SUBJECT = "sub_num"
IV1 = "stim_type"
IV2 = "ses_num"
DV = "nps"
DATA$sub_num = factor(DATA$sub_num)
# DATA$task <- factor(DATA$task, levels = c("pain-early", "pain-late", "pain-post", "pain-plateau", "pain"))
subjectwise_temp_ses = meanSummary(DATA, c(SUBJECT, IV1, IV2), DV)
groupwise_temp_ses = summarySEwithin(data=subjectwise_temp_ses, 
                  measurevar = "mean_per_sub", # variable created from above
                    withinvars = c(IV1, IV2), # IV
                    idvar = "sub_num")
groupwise_drop_temp_ses <- na.omit(groupwise_temp_ses)
```

* calculate ICC "two-way random effects"