---
title: "model05_iv-cue-stim_dv-RT"
author: "Heejung Jung"
date: '06/27/2022'
output:
  html_document:
    toc: true
    theme: united
    code_folding: hide
editor_options: 
  markdown: 
    wrap: 72
---



""" 
This Rmarkdown tests the cue effect (high vs. low) on Reaction time and performance in the cognitive, mental-rotation tasks. We also test for stimulus intensity effects.
"""

# model 05 iv-cue dv-RT summary
* left = diff, right = same
* model 1: Does RT differ as a function of cue type and stimulut intensity?
* model 1-1: Does RT differ as a function of cue, ONLY for the correct trials?
* model 1-2: Does RT differ as a function of cue, ONLY for the incorrect trials?
* model 2: would log-transforming help? Do we see a cue effect on the log-transformmed RTs?

#TODO: 06/28/2022   
* change variable names and two factor code accordingly

load library
```{r load libraries, message=TRUE, warning=TRUE, include=FALSE, paged.print=TRUE, results='hide'}
library(psych)
library(car)
library(lmSupport)
library(lme4)
library(lmerTest)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(ggpubr)
#library(extraoperators)
#library(JWileymisc)
#library(multilevelTools)
#library(Hmisc)
#library(Rmisc)
#library(dplyr)
# library(PupillometryR)
source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

library(r2mlm)
main_dir = dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, "scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```


```{r main directory}
main_dir = dirname(dirname(getwd()))
print(main_dir)
```

# Prepare data and preprocess
## 1) load data
```{r load data}
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "cognitive"
ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001"
data <- load_task_social_df(datadir, taskname = taskname, 
                            subject_varkey = subject_varkey, 
                            iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
```

## 2) plot RT distribution per participant
- the purpose is to identify whether RTs are distributed from 0-5 sec or not
- From this, we can also identify the quality of the data and determine if we need to scrub or remove participants. 
```{r plot RT distribution, echo=TRUE}
ggplot(data,aes(x=event03_RT, group = subject)) +
  geom_histogram(color="darkblue", fill="lightblue", binwidth=0.25, bins = 20) + 
  facet_wrap(~subject, ncol = 10) + 
  theme(axis.text=element_text(size=5),text=element_text(size=6))
```

* Some participants may not have responded within time limit.
* The button may not have registered the correct onset
* I may have to remove the RTs with 5 sec. 

---

## 3) exclude participants with RT of 5 seconds
```{r}
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "cognitive"

ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"

# load data _____________________________________
data <- datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset

analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model05_iv-cue-stim_dv-RT", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)

data$event03_response_samediff <- mapvalues(data$event03_stimulusC_response,
                                                from = c(1, 2),
                                                to = c("diff", "same"))

data$event03_correct <- ifelse(data$event03_C_stim_match == data$event03_response_samediff, 1, ifelse(data$event03_C_stim_match != data$event03_response_samediff, 0, "NA"))
```

# model 1: 
* IV: cue (high vs. low)
* DV: RT of the incorrect trials
* contrast code two factors -- stimulus intensity and cue type
* plotting all trials (including correct and incorrect trials)
```{r model 1 contrast coding}
# contrast code 1 linear _____________________________________
data$stim_con_linear[data$param_stimulus_type == "low_stim"] <- -0.5
data$stim_con_linear[data$param_stimulus_type == "med_stim"] <- 0
data$stim_con_linear[data$param_stimulus_type == "high_stim"] <- 0.5

# contrast code 2 quadratic _____________________________________
data$stim_con_quad[data$param_stimulus_type == "low_stim"] <- -0.33
data$stim_con_quad[data$param_stimulus_type == "med_stim"] <- 0.66
data$stim_con_quad[data$param_stimulus_type == "high_stim"] <- -0.33

# social cue contrast _____________________________________
# data$social_cue[data$param_cue_type == "low_cue"] <- -0.5 # social influence task
# data$social_cue[data$param_cue_type == "high_cue"] <- 0.5 # no influence task
# data$cue_factor = factor(data$social_cue)

data$social_cue[data$param_cue_type == 'low_cue'] <- -0.5 # social influence task
data$social_cue[data$param_cue_type == 'high_cue'] <- 0.5 # no influence task
data$cue_factor = factor(data$param_cue_type)

# factorize group variable _____________________________________
data$subject = factor(data$src_subject_id)
```

```{r model 1 cue effect on RT}

# parameters ___________________________________________________________________
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
stim_con1 = "stim_con_linear"
stim_con2 = "stim_con_quad"
dv <- "event03_RT"
iv_keyword <- "cue-stim"
dv_keyword <- "RT"
xlab <- ""
taskname <- "cognitive"
ylim = c(0,5)
    
# lmer filename ________________________________________________________________
model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname, "_iv-", iv_keyword,
            "_dv-", dv_keyword,
            "_", as.character(Sys.Date()), ".txt",
            sep = ""
        )
    )

# removing NA values ___________________________________________________________
data_clean = data[!is.na(data$event03_RT),]
data_clean$subject = factor(data_clean$src_subject_id)

# lmer model ___________________________________________________________________
cooksd <- lmer_twofactor_cooksd_fix(data = data_clean,
                                     taskname = "cognitive",
                                     iv = "cue_factor",
                                     stim_con1 = "stim_con_linear",
                                     stim_con2 = "stim_con_quad",
                                     dv = "event03_RT",
                                     subject = "subject",
                                     dv_keyword = "RT",
                                     model_savefname = model_savefname,
                                     effects = "random_intercept")
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data_clean$subject)))))])
data_screen <- data_clean[-influential, ]

# reordering for plots _________________________________________________________
data_clean$cue_name[data_clean$param_cue_type == "high_cue"] <- "high cue"
data_clean$cue_name[data_clean$param_cue_type == "low_cue"] <- "low cue" # no influence task

data_clean$stim_name[data_clean$param_stimulus_type == "high_stim"] <- "high" # no influence task
data_clean$stim_name[data_clean$param_stimulus_type == "med_stim"] <- "med" # no influence task
data_clean$stim_name[data_clean$param_stimulus_type == "low_stim"] <- "low" # no influence task

data_clean$stim_ordered <- factor(data_clean$stim_name, levels=c("low", "med", "high"))
data_clean$cue_ordered <- factor(data_clean$cue_name, levels=c("low cue", "high cue"))
model_iv1 = "stim_ordered";model_iv2 = "cue_ordered"

# summary statistics for plots _________________________________________________
subjectwise <- meanSummary(data_clean, c(subject, model_iv1, model_iv2), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(model_iv1, model_iv2), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    group_mean <- "mean_per_sub_norm_mean"
se <- "se";    subject <- "subject"
ggtitle <- paste(taskname, " - Reaction Time (s)");    title <- paste(taskname, " - RT")
xlab <- "";    ylab <- "Reaction Time (s)";    
w = 5; h = 3; dv_keyword <- "RT"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
              "_iv-", iv_keyword,"_dv-", dv_keyword,
            "_", as.character(Sys.Date()), ".png",
            sep = ""
        )
    )
plot_rainclouds_twofactor(
        subjectwise, groupwise,
        model_iv1, model_iv2, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

# save random effects for individual difference analysis _______________________
randEffect$newcoef <- mapvalues(randEffect$term,
    from = c("(Intercept)"),
    to = c("rand_intercept")
)
rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = `(Intercept)`,
    fix_cue = `cue_factorlow_cue`,
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, 
          "_iv-", iv_keyword,"_dv-", dv_keyword,
        "_",as.character(Sys.Date()), "_outlier-cooksd.csv",
        sep = ""
    )
)
write.csv(new_total, rand_savefname, row.names = FALSE)
```
## Model 1 Interim summary
* Research question: Does RT differ as a function of high vs. low cue?
* Conclusion: No. RT does not differ as a function of cue
* Next step: It's interesting that there is no cue effect on RT, while the cue effect on ratings are robust. We see if this effect is potentially present in only certain type of trials, namely the correct vs. incorrect trials of the mental rotation task


# model 1-1
* IV: 
    * cue (high vs. low)
    * stimulus intensity (high vs. medium vs. low)
* DV: RT of the correct trials
* Subsetting trials (identical to model 1, except for subsetting correct trials)
```{r model 1-1 correct trials only}
# parameters ___________________________________________________________________
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT-correct"
xlab <- ""
taskname <- "cognitive"
ylim = c(0,5)
    
# lmer filename ________________________________________________________________
model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,"_iv-", iv_keyword,
            "_dv-", dv_keyword,
            "_", as.character(Sys.Date()), ".txt",
            sep = ""
        )
    )

# removing NA values ___________________________________________________________

data_clean = data[!is.na(data$event03_correct),]
data_c = data[data_clean$event03_correct == 1,]
data_c$subject = factor(data_c$src_subject_id)

# lmer model ___________________________________________________________________
# cooksd <- lmer_twofactor_cooksd_fix(data = data_clean,
#                                      taskname = "cognitive",
#                                      iv = "cue",
#                                      stim_con1 = "stim_con_linear",
#                                      stim_con2 = "stim_con_quad",
#                                      dv = "event03_RT",
#                                      subject = "src_subject_id",
#                                      dv_keyword = "RT",
#                                      model_savefname = model_savefname,
#                                      effects = "random_intercept")
# influential <- as.numeric(names(cooksd)[
#     (cooksd > (4 / as.numeric(length(unique(data_c$subject)))))])
# data_screen <- data_c[-influential, ]


# lmer model ___________________________________________________________________
model_onefactor_correct <- lmer(event03_RT ~ cue_factor*stim_con_linear + cue_factor*stim_con_quad + (1 | src_subject_id), data = data_c)
fixEffect <- as.data.frame(fixef(model_onefactor_correct))
randEffect <- as.data.frame(ranef(model_onefactor_correct))
cooksd <- cooks.distance(model_onefactor_correct)
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data_c$subject)))))])
data_screen <- data_c[-influential, ]
equatiomatic::extract_eq(model_onefactor_correct)



# summary statistics for plots _________________________________________________
subjectwise <- meanSummary(data_screen, c(subject, iv), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(iv), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    group_mean <- "mean_per_sub_norm_mean"
se <- "se";    subject <- "subject"
ggtitle <- paste(taskname, dv_keyword);    title <- paste(taskname, " - RT")
xlab <- "";    ylab <- "Reaction Time (s)";    
w = 5; h = 3; 
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_iv-", iv_keyword,"_dv-", dv_keyword,
            "_", as.character(Sys.Date()), ".png",
            sep = ""
        )
    )
plot_rainclouds_onefactor(
        subjectwise, groupwise,
        iv, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

# save random effects for individual difference analysis _______________________
randEffect$newcoef <- mapvalues(randEffect$term,
    from = c("(Intercept)"),
    to = c("rand_intercept")
)
rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)

rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = `(Intercept)`,
    fix_cue = `cue_factorlow_cue`,
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, 
          "_iv-", iv_keyword,"_dv-", dv_keyword,
        "_", as.character(Sys.Date()), "_outlier-cooksd.csv",
        sep = ""
    )
)
write.csv(new_total, rand_savefname, row.names = FALSE)
```
## Model 1-1 Interim summary (correct trials)
* Research question: Only using correct trials, does RT differ as a function of high vs. low cue? 
* Conclusion: No. Even within the subset of correct trials, RT does not differ as a function of cue.
* Next step: Is there a cue effect on RT, only for the incorrect trials? Perhaps the cue had an effect on one's expectation, and the mismatch of thee cues led to incorrect performance, reflected in the RTs


# model 1-2: 
* IV: cue (high vs. low)
* DV: RT of the incorrect trials
* Subsetting trials (identical to model 1, except for subsetting incorrect trials)
```{r model 1-2 incorrect trials only}
# parameters ___________________________________________________________________
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT-incorrect"
xlab <- ""
taskname <- "cognitive"
ylim = c(0,5)
    
# lmer filename ________________________________________________________________
model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,"_iv-", iv_keyword,
            "_dv-", dv_keyword,
            "_", as.character(Sys.Date()), ".txt",
            sep = ""
        )
    )

# removing NA values ___________________________________________________________

data_clean = data[!is.na(data$event03_correct),]
data_i = data[data_clean$event03_correct == 0,]
data_i$subject = factor(data_i$src_subject_id)

# lmer model ___________________________________________________________________
model_onefactor_incorrect <- lmer(event03_RT ~ cue_factor*stim_con_linear + cue_factor*stim_con_quad + (1 | src_subject_id), data = data_i)
fixEffect <- as.data.frame(fixef(model_onefactor_incorrect))
randEffect <- as.data.frame(ranef(model_onefactor_incorrect))
cooksd <- cooks.distance(model_onefactor_incorrect)
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data_i$subject)))))])
data_screen_i <- data_i[-influential, ]
equatiomatic::extract_eq(model_onefactor_incorrect)

# summary statistics for plots _________________________________________________
subjectwise <- meanSummary(data_screen_i, c(subject, iv), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(iv), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    group_mean <- "mean_per_sub_norm_mean"
se <- "se";    subject <- "subject"
ggtitle <- paste(taskname, dv_keyword);    title <- paste(taskname, " - RT")
xlab <- "";    ylab <- "Reaction Time (s)";    
w = 5; h = 3; 
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_iv-", iv_keyword,"_dv-", dv_keyword,
            "_", as.character(Sys.Date()), ".png",
            sep = ""
        )
    )
plot_rainclouds_onefactor(
        subjectwise, groupwise,
        iv, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

# save random effects for individual difference analysis _______________________
randEffect$newcoef <- mapvalues(randEffect$term,
    from = c("(Intercept)"),
    to = c("rand_intercept")
)

rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = `(Intercept)`,
    fix_cue = `cue_factorlow_cue`,
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_iv-", iv_keyword,"_dv-", dv_keyword,
            "_",as.character(Sys.Date()), "_outlier-cooksd.csv",
        sep = ""
    )
)
write.csv(new_total, rand_savefname, row.names = FALSE)
```
## Model 1-2 Interim summary (incorrect trials)
* Research question: Only using incorrect trials, does RT differ as a function of high vs. low cue? 
* Conclusion: No. Even within the subset of incorrect trials, RT does not differ as a function of cue
* Next step: Reaction times are data points that are non-normal; mostly a skewed distribution. In order to deal with this skewness, we log-transform the data and investigate the same question, whether the cues have a signficant effect on reaction times. 


# model 2: Log transformation
* IV: cue (high vs. low)
* DV: log-transformmed RT

```{r model 2 cue effect on log-RT, message=TRUE, warning=TRUE, paged.print=FALSE}
# parameters ___________________________________________________________________
subject_varkey <- "src_subject_id"
iv <- "cue_factor"
dv <- "log_RT"
dv_keyword <- "RT-log"
xlab <- ""
taskname <- "cognitive"
ylim = c(0,5)
    
# lmer filename ________________________________________________________________
model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,"_iv-", iv_keyword,
            "_dv-", dv_keyword, as.character(Sys.Date()), ".txt",
            sep = ""
        )
    )

# removing NA values ___________________________________________________________
data_clean = data[!is.na(data$event03_correct),]
data_clean$log_RT = log(data_clean$event03_RT)
data_clean$subject = factor(data_clean$src_subject_id)

# lmer model ___________________________________________________________________
model_onefactor_log <- lmer(log_RT ~ cue_factor + (1 | subject), data = data_clean)
summary(model_onefactor_log)

fixEffect <- as.data.frame(fixef(model_onefactor_log))
randEffect <- as.data.frame(ranef(model_onefactor_log))
cooksd <- cooks.distance(model_onefactor_log)
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data_clean$subject)))))])
data_screen_log <- data_clean[-influential, ]
equatiomatic::extract_eq(model_onefactor_log)

# summary statistics for plots _________________________________________________
subjectwise <- meanSummary(data_screen_log, c(subject, iv), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(iv), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    group_mean <- "mean_per_sub_norm_mean"
se <- "se";   
ggtitle <- paste(taskname, dv_keyword);    title <- paste(taskname, " - RT")
xlab <- "";    ylab <- "Reaction Time (s)";    
w = 5; h = 3; 
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_iv-", iv_keyword,"_dv-", dv_keyword,"_",
            as.character(Sys.Date()), ".png",
            sep = ""
        )
    )
plot_rainclouds_onefactor(
        subjectwise, groupwise,
        iv, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

# save random effects for individual difference analysis _______________________
fixEffect <- as.data.frame(fixef(model_onefactor_log))
randEffect <- as.data.frame(ranef(model_onefactor_log))
randEffect$newcoef <- mapvalues(randEffect$term,
    from = c("(Intercept)"),
    to = c("rand_intercept")
)

rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = `(Intercept)`,
    fix_cue = `cue_factorlow_cue`,
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname,"_iv-", iv_keyword,"_dv-", dv_keyword,
        "_outlier-cooksd_", as.character(Sys.Date()), ".csv",
        sep = ""
    )
)


write.csv(new_total, rand_savefname, row.names = FALSE)
```
* Research question: Does log transformming help? After log-transformming RT, does RT differ as a function of high vs. low cue? 
* conclusion 2: No, log transformmed or not, there is no significant cue effect on RT

# Conclusion across model 1 and 2
* There is no substansive evidence that suggeest cue effects on reaction time. In other words, the time to respond to a rotated figure does not differ as a function of high or low cue. 
