---
title: "model09_iv-cue-stim_dv-phasic"
author: "Heejung Jung"
date: '2022-09-17'
output:
  html_document:
    toc: true
    theme: united
    code_folding: hide
editor_options: 
  markdown: 
    wrap: 72
---

TODO:
split data into task (full -> P, v, c subset)
push code to git
create code map
# Overview

The purpose of this notebook is to analyze biopac phasic data. 
Data has been preprocessed with neurokit

We load a dataframe that contains the following outcome measures:
'Event_Onset', 'EDA_Peak_Amplitude', 'EDA_SCR', 'SCR_Peak_Amplitude',
'SCR_Peak_Amplitude_Time', 'SCR_RiseTime', 'SCR_RecoveryTime'

We model this as a function of "cue" and "stimulus intensity",
while allowing for random effects from participants. 

------------------------------------------------------------------------

# Why use multilevel models?

-   content copied from
    <http://www.bristol.ac.uk/cmm/learning/multilevel-models/what-why.html>

> There are a number of reasons for using multilevel models:
>
> 1.  Correct inferences: Traditional multiple regression techniques
>     treat the units of analysis as independent observations. One
>     consequence of failing to recognise hierarchical structures is
>     that standard errors of regression coefficients will be
>     underestimated, leading to an overstatement of statistical
>     significance. Standard errors for the coefficients of higher-level
>     predictor variables will be the most affected by ignoring
>     grouping.
>
> 2.  Substantive interest in group effects: In many situations a key
>     research question concerns the extent of grouping in individual
>     outcomes, and the identification of 'outlying' groups. In
>     evaluations of school performance, for example, interest centres
>     on obtaining 'value-added' school effects on pupil attainment.
>     Such effects correspond to school-level residuals in a multilevel
>     model which adjusts for prior attainment.
>
> 3.  Estimating group effects simultaneously with the effects of
>     group-level predictors: An alternative way to allow for group
>     effects is to include dummy variables for groups in a traditional
>     (ordinary least squares) regression model. Such a model is called
>     an analysis of variance or fixed effects model. In many cases
>     there will be predictors defined at the group level, eg type of
>     school (mixed vs. single sex). In a fixed effects model, the
>     effects of group-level predictors are confounded with the effects
>     of the group dummies, ie it is not possible to separate out
>     effects due to observed and unobserved group characteristics. In a
>     multilevel (random effects) model, the effects of both types of
>     variable can be estimated.
>
> 4.  Inference to a population of groups: In a multilevel model the
>     groups in the sample are treated as a random sample from a
>     population of groups. Using a fixed effects model, inferences
>     cannot be made beyond the groups in the sample.

------------------------------------------------------------------------

load libraries

```{r load libraries, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
library(lmSupport)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(stats)
library(ggpubr)
library(equatiomatic)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lme4)
library(effectsize)
library(brms)
#library(Hmisc)
#library(Rmisc)
## library(extraoperators)
##library(JWileymisc)
##library(multilevelTools)
# library(PupillometryR)
source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

library(r2mlm)
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

# Terminology

factor

:   In experimental designs, factor is the equivalent of independent
    variable. In R, one can factorize a categorical variable by using
    the `factor` function. Thereby we interchangeably use the term
    factor in lieu of independent variable.

    From this, the term `factorial design` originates.

level

:   within each independent variable, a researcher may determine
    different levels. Since the purpose of linear models is to compare
    at least one condition to another, a factor contains more than one
    level.

group variable

:   Unit of analysis. In most fMRI experiments that collect individual
    data, the group variable would be the individual participant.
    However, in other research questions, the group variable could
    easily be more than one individual. For instance, a dyad of
    participants that carry out conversations, multiple patients that
    see an identical doctor, a classroom full of individuals, or voting
    districts could serve as a grouping variable, depending on the
    research question.

-   <div>

        factor:
        group

    </div>

# Model versions {.tabset}

## Summary of models

### Method 1: repeated measures and `one-sample t-tests`

-   Data Matrix: Wide form
    -   row (83 subject)
    -   column (6 conditions: highCue x highStim, highCue x medStim,
        highCue x lowStim, lowCue x highStim,lowCue x medStim, lowCue x
        lowStim)
-   Model: Use "lm". One-sample t-test
-   Effect size (cohen's d): mean / sd (intersubject slope) \> use
    degrees of freedom.

### 
load data and combine participant data
```{r}
analysis_dir
```


```{r load data and exclude}
main_dir = dirname(dirname(getwd()))
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model09_iv-cue-stim_dv-phasic", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```
```{r}
# parameters _____________________________________ # nolint
phasic = read.csv("/Volumes/spacetop_projects_social/data/physio/02_preproc-physio/group_epochstart-0_epochend-9_physio-phasic.csv")
```

This is the data that we will use

```{r echo=FALSE}
head(phasic)
```


## Method 3 multilevel modeling

### Method 3 multilevel modeling

-   Data Matrix: Long form
    -   Row (5412: 83 subject \* 2 cue \* 3 stimulus intensity \* 12 trials)
    -   Columns (4: subject, session, task type, run_num, cue type, stimulus intensity type,
        EDA metrics)
-   Model: Use "lmer" multilevel-modeling
    -   grouping variable: subjects (i.e. src_subject_id)
    -   fixed effects - cue (2 levels, contrast-coded [high, low: 1,
        -1]) - stim_linear (3 levels, [low, med, high: -1, 0, 1]) -
        stim_quadratic (3 levels, [low, med, high: -1, 2, -1])
    -   random effects - cue - stim_linear - cue\*stim_linear
    -   NOTE: due to convergence failure, cue\*stim_quadratic term was
        removed
-   Effect size (cohen's d): beta_coefficient/ sqrt(sum of all random
    variance)

contrast-coding for multi-level modeling (code-hidden)

```{r model 3 contrast coding}
#contrast code 1 linear
phasic$stim_con_linear[phasic$param_stimulus_type == "low_stim"] <- -0.5
phasic$stim_con_linear[phasic$param_stimulus_type == "med_stim"] <- 0
phasic$stim_con_linear[phasic$param_stimulus_type == "high_stim"] <- 0.5

# contrast code 2 quadratic
phasic$stim_con_quad[phasic$param_stimulus_type == "low_stim"] <- -0.33
phasic$stim_con_quad[phasic$param_stimulus_type == "med_stim"] <- 0.66
phasic$stim_con_quad[phasic$param_stimulus_type == "high_stim"] <- -0.33

# social cue contrast
phasic$social_cue[phasic$param_cue_type == 'low_cue'] <- -0.5 # social influence task
phasic$social_cue[phasic$param_cue_type == 'high_cue'] <- 0.5 # no influence task
phasic$cue_factor = factor(phasic$social_cue)
```

```{r}
# parameters ___________________________________________________________________
phasic$subject = factor(phasic$src_subject_id)
subject_varkey <- "subject"
iv <- "cue_factor"
stim_con1 = "stim_con_linear"
stim_con2 = "stim_con_quad"
dv <- "EDA_Peak_Amplitude"
iv_keyword <- "cue-stim"
dv_keyword <- "eda_peak"
xlab <- ""
taskname <- "full"
#ylim = c(-1,1)
#phasic_task = 
```

multi-level modeling using **lmer**

```{r lmer fullmodel, class.source = 'fold-show'}
fullmodel = lmer(EDA_Peak_Amplitude ~ 1+ cue_factor + stim_con_linear + stim_con_quad + cue_factor:stim_con_linear + cue_factor:stim_con_quad + (1  |subject), data = phasic)

# output of model
summary(fullmodel)

```



```{r plot results}
cooksd <- cooks.distance(fullmodel)
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(phasic$subject)))))])
data_screen <- phasic[-influential, ]

# reordering for plots _________________________________________________________
phasic$cue_name[phasic$param_cue_type == "high_cue"] <- "high cue"
phasic$cue_name[phasic$param_cue_type == "low_cue"] <- "low cue" # no influence task

phasic$stim_name[phasic$param_stimulus_type == "high_stim"] <- "high" # no influence task
phasic$stim_name[phasic$param_stimulus_type == "med_stim"] <- "med" # no influence task
phasic$stim_name[phasic$param_stimulus_type == "low_stim"] <- "low" # no influence task

phasic$stim_ordered <- factor(phasic$stim_name, levels=c("low", "med", "high"))
phasic$cue_ordered <- factor(phasic$cue_name, levels=c("low cue", "high cue"))
model_iv1 = "stim_ordered";model_iv2 = "cue_ordered"

# summary statistics for plots _________________________________________________
subjectwise <- meanSummary(phasic, c(subject, model_iv1, model_iv2), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(model_iv1, model_iv2), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    
group_mean <- "mean_per_sub_norm_mean"
se <- "se";   
ggtitle <- paste(taskname, dv_keyword);    
title <- paste(taskname, " - RT")
xlab <- "";    
ylab <- "EDA peak amplitude ";    
w = 5; h = 3; 
ylim = c(-1,3)
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
              "_iv-", iv_keyword,"_dv-", dv_keyword,
              "_", as.character(Sys.Date()), ".png",
              sep = ""
        )
    )
plot_rainclouds_twofactor(
        subjectwise, groupwise,
        model_iv1, model_iv2, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

```
### TASKWISE
```{r}
for (taskname in c( "vicarious", "cognitive")) {#"pain"
    ggtitle <- paste(taskname, " - EDA phasic signal")
    title <- paste(taskname, " - EDA")
    subject <- "subject"
    #data <- phasic
    
    data = phasic[phasic$param_task_name == taskname,]
    w <- 10
    h <- 6

    # [ CONTRASTS ]  ________________________________________________________________________________ # nolint
    # contrast code ________________________________________
    data$stim[data$param_stimulus_type == "low_stim"] <- -0.5 # social influence task
    data$stim[data$param_stimulus_type == "med_stim"] <- 0 # no influence task
    data$stim[data$param_stimulus_type == "high_stim"] <- 0.5 # no influence task

    data$stim_factor <- factor(data$param_stimulus_type)

    # contrast code 1 linear
    data$stim_con_linear[data$param_stimulus_type == "low_stim"] <- -0.5
    data$stim_con_linear[data$param_stimulus_type == "med_stim"] <- 0
    data$stim_con_linear[data$param_stimulus_type == "high_stim"] <- 0.5

    # contrast code 2 quadratic
    data$stim_con_quad[data$param_stimulus_type == "low_stim"] <- -0.33
    data$stim_con_quad[data$param_stimulus_type == "med_stim"] <- 0.66
    data$stim_con_quad[data$param_stimulus_type == "high_stim"] <- -0.33

    # social cude contrast
    data$social_cue[data$param_cue_type == "low_cue"] <- -0.5 # social influence task
    data$social_cue[data$param_cue_type == "high_cue"] <- 0.5 # no influence task


    stim_con1 <- "stim_con_linear"
    stim_con2 <- "stim_con_quad"
    iv1 <- "cue_factor"
    dv <- "EDA_Peak_Amplitude"
    dv_keyword <- "EDA-phasic-peak-amplitude"

    # [ MODEL ] _________________________________________________ # nolint
    model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.txt",
            sep = ""
        )
    )
    cooksd <- lmer_two_factor_cooksd(
        data, taskname, iv1, stim_con1, stim_con2, dv,
        subject, dv_keyword, model_savefname
    )
    influential <- as.numeric(names(cooksd)[
        (cooksd > (4 / as.numeric(length(unique(data$src_subject_id)))))
    ])
    data_screen <- data[-influential, ]
    # [ PLOT ] reordering for plots _________________________ # nolint
    data_screen$cue_name[data_screen$param_cue_type == "high_cue"] <- "high cue"
    data_screen$cue_name[data_screen$param_cue_type == "low_cue"] <- "low cue"

    data_screen$stim_name[data_screen$param_stimulus_type == "high_stim"] <- "high"
    data_screen$stim_name[data_screen$param_stimulus_type == "med_stim"] <- "med"
    data_screen$stim_name[data_screen$param_stimulus_type == "low_stim"] <- "low"

    # DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

    data_screen$stim_ordered <- factor(
        data_screen$stim_name,
        levels = c("low", "med", "high")
    )
    data_screen$cue_ordered <- factor(
        data_screen$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"

    #  [ PLOT ] calculate mean and se  _________________________
    actual_subjectwise <- meanSummary(
        data_screen,
        c(subject, model_iv1, model_iv2), dv
    )
    actual_groupwise <- summarySEwithin(
        data = actual_subjectwise,
        measurevar = "mean_per_sub",
        withinvars = c(model_iv1, model_iv2), idvar = subject
    )
    actual_groupwise$task <- taskname
    # https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402
    combined_se_calc_cooksd <- rbind(combined_se_calc_cooksd, actual_groupwise)
    # if(any(startsWith(dv_keyword, c("expect", "Expect")))){color = c( "#1B9E77", "#D95F02")}else{color=c( "#4575B4", "#D73027")} # if keyword starts with
    # print("groupwisemean")
    #  [ PLOT ] calculate mean and se  ----------------------------------------------------------------------------
    sub_mean <- "mean_per_sub"
    group_mean <- "mean_per_sub_norm_mean"
    se <- "se"
    subject <- "subject"
    ggtitle <- paste(taskname, " - Actual Rating (degree) Cooksd removed")
    title <- paste(taskname, " - Actual")
    xlab <- ""
    ylab <- "ratings (degree)"
    ylim <- c(-10,190)
    dv_keyword <- "actual"
    if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    } # if keyword starts with
    plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), "_cooksd.png",
            sep = ""
        )
    )
    g <- plot_rainclouds_twofactor(
        actual_subjectwise, actual_groupwise, model_iv1, model_iv2,
        sub_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, taskname,ylim,
        w, h, dv_keyword, color, plot_savefname
    )
    g
    # g <- g + 
    #   geom_hline(yintercept = 0, size = 0.1, linetype = "dashed") + 
    #   geom_label(x = 3.5, y = 0, label = c("no sensation"), hjust = 0, nudge_x = 0.1, size = 3) +
    #   geom_hline(yintercept = 3, size = 0.1, linetype = "dashed") + 
    #   geom_label(x = 3.5, y = 3, label = c("barely detectable"), hjust = 0, nudge_x = 0.1, size = 3) +
    #   geom_hline(yintercept = 10, size = 0.1, linetype = "dashed") + 
    #   geom_label(x = 3.5, y = 10, label = c("weak"), hjust = 0, nudge_x = 0.1, size = 3) +
    #   geom_hline(yintercept = 30, size = 0.1, linetype = "dashed") + 
    #   geom_label(x = 3.5, y = 30, label = c("moderate"), hjust = 0, nudge_x = 0.1, size = 3) +
    #   geom_hline(yintercept = 65, size = 0.1, linetype = "dashed") + 
    #   geom_label(x = 3.5, y = 65, label = c("strong"), hjust = 0, nudge_x = 0.1, size = 3) +
    #   geom_hline(yintercept = 95, size = 0.1, linetype = "dashed") + 
    #   geom_label(x = 3.5, y = 95, label = c("very strong"), hjust = 0, nudge_x = 0.1, size = 3) +
    #   geom_hline(yintercept = 180, size = 0.1, linetype = "dashed") + 
    #   geom_label(x = 3.5, y = 180, label = c("strongest imaginable"), hjust = 0, nudge_x = 0.1, size = 3) +
    #   coord_cartesian(clip = 'off')+
    #   theme_classic() + 
    #   theme(legend.position = "none") 
    # 
    
    # ggsave(plot_savefname, width = w, height = h)

    
    

    # save fixed random effects _______________________________
    # randEffect$newcoef <- mapvalues(randEffect$term,
    #     from = c("(Intercept)", "data[, iv]", 
    #              "data[, stim_con1]", "data[, stim_con2]", 
    #              "data[, iv]:data[, stim_con1]", 
    #              "data[, iv]:data[, stim_con2]"),
    #     to = c("rand_intercept", "rand_cue", "rand_stimlin", 
    #            "rand_stimquad", "rand_int_cue_stimlin", "rand_int_cue_stimquad")
    # )
    # 
    # #
    # # # The arguments to spread():
    # # # - data: Data object
    # # # - key: Name of column containing the new column names
    # # # - value: Name of column containing values
    # #
    # # # TODO: add fixed effects
    # #
    # rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
    # wide_rand <- spread(rand_subset, key = newcoef, value = condval)
    # wide_fix <- do.call(
    #     "rbind",
    #     replicate(nrow(wide_rand), as.data.frame(t(as.matrix(fixEffect))),
    #         simplify = FALSE
    #     )
    # )
    # rownames(wide_fix) <- NULL
    # new_wide_fix <- dplyr::rename(wide_fix,
    #     fix_intercept = `(Intercept)`, 
    #     fix_cue = `data[, iv]`,
    #     fix_stimulus_linear = `data[, stim_con1]`,
    #     fix_stimulus_quad = `data[, stim_con2]`, 
    #     fix_int_cue_stimlin = `data[, iv]:data[, stim_con1]`,
    #     fix_int_cue_stimquad = `data[, iv]:data[, stim_con2]`
    # )
    # 
    # total <- cbind(wide_rand, new_wide_fix)
    # total$task <- taskname
    # new_total <- total %>% dplyr::select(task, everything())
    # new_total <- dplyr::rename(total, subj = grp)
    # 
    # plot_savefname <- file.path(analysis_dir, 
    #                             paste("randeffect_task-", taskname, 
    #                                   "_", as.character(Sys.Date()), "_outlier-cooksd.csv", sep = ""))
    # write.csv(new_total, plot_savefname, row.names = FALSE)
}


```

```{r}
library(ggpubr)
DATA = as.data.frame(groupwise)
color = c( "#4575B4", "#D73027")
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "ci"
dv_keyword = "actual"
    
    g <- ggplot(data = DATA, aes(
        x = stim_ordered,
        y = mean_per_sub_norm_mean,
        group = factor(cue_ordered),
        color = factor(cue_ordered)
    ), cex.lab = 1.5, cex.axis = 2, cex.main = 1.5, cex.sub = 1.5) +
        geom_errorbar(aes(
            ymin = (mean_per_sub_norm_mean - se),
            ymax = (mean_per_sub_norm_mean + se)
        ), width = .1) +
        geom_line() +
        geom_point() +
        # scale_x_continuous(breaks = seq(-3, +3, by = 1)) +
        # scale_y_continuous(breaks = seq(0, 90, by=30), limits=c(0,90)) +
        ggtitle(ggtitle) +
        xlab("Stimulus intensity") +
        ylab("Rating (degrees)") +
        # guides(fill=guide_legend(title="Social Endorsement Position")) +
        scale_color_manual(values = color) +
        theme_classic() +
        theme(legend.position = "none") +
        theme(aspect.ratio = .6)
g
# 
# p1 = plot_lineplot_twofactor(DATA, 'pain', 
#                LINEIV1, LINEIV2, MEAN, ERROR, color, ggtitle = 'pain' )
# p2 = plot_lineplot_twofactor(DATA,'vicarious', 
#                LINEIV1, LINEIV2, MEAN, ERROR, color,ggtitle = 'vicarious')
# p3 = plot_lineplot_twofactor(DATA, 'cognitive', 
#                LINEIV1, LINEIV2, MEAN, ERROR, color,ggtitle = 'cognitive')
# #grid.arrange(p1, p2, p3, ncol=3 , common.legend = TRUE)
# ggpubr::ggarrange(p1,p2,p3,ncol = 3, nrow = 1, common.legend = TRUE,legend = "bottom")
# plot_filename = file.path(analysis_dir,
#                           paste('lineplot_task-all_rating-',dv_keyword,'.png', sep = ""))
# ggsave(plot_filename, width = 8, height = 4)
```

```{r}

library(ggpubr)
DATA = as.data.frame(combined_se_calc_cooksd)
color = c( "#4575B4", "#D73027")
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "ci"
dv_keyword = "eda-mean-peak-amplitude"
p1 = plot_lineplot_twofactor(DATA, 'pain', 
               LINEIV1, LINEIV2, MEAN, ERROR, color, ggtitle = 'pain' )
p2 = plot_lineplot_twofactor(DATA,'vicarious', 
               LINEIV1, LINEIV2, MEAN, ERROR, color,ggtitle = 'vicarious')
p3 = plot_lineplot_twofactor(DATA, 'cognitive', 
               LINEIV1, LINEIV2, MEAN, ERROR, color,ggtitle = 'cognitive')
#grid.arrange(p1, p2, p3, ncol=3 , common.legend = TRUE)
ggpubr::ggarrange(p1,p2,p3,ncol = 3, nrow = 1, common.legend = TRUE,legend = "bottom")
plot_filename = file.path(analysis_dir,
                          paste('lineplot_task-all_rating-',dv_keyword,'.png', sep = ""))
ggsave(plot_filename, width = 8, height = 4)
```
```


# ______ modify accordingly - brute copy pasted
```{r}
fixef(Method3_fullmodel)
```

```{r}
sd_raw_pre_t <- filter(phasic, cue_factor ==  "0.5") %>% summarise(s = sd(tradeoff)) %>% pull()  # treatment baseline SD
sd_raw_pre_c <- filter(phasic, cue_factor == "-0.5") %>% summarise(s = sd(tradeoff)) %>% pull()  # control baseline SD

sd_raw_pre_t
sd_raw_pre_c

# pooled PRE based on addition of two group conditions
sd_raw_pre_p <- sqrt((sd_raw_pre_c^2 + sd_raw_pre_t^2) / 2)
sd_raw_pre_p
```

## Method 3 - Effect size estimates

d = estimate for fixed effect / (sqrt of sum of variances of random
effects)

```{r, class.source = 'fold-show'}
#https://www.journalofcognition.org/articles/10.5334/joc.10/
cat(paste("effectsize of lmer cue effect:", 
          0.0658 / sqrt(sum(0.0000,0.6077,1.1785,4.0424,0.8779))))

#0.0658 / sqrt(sum(0.1519,0.6078,2.0258,4.0428,0.8779))
#0.07/sqrt(sum(0.88,0.15,0.61,2.35,4.04,-1.00,0.37,-0.61))

#cohen_f = 0.02540844**2 / (2*2)
#cohen_f
```


## Method 3 plotting

```{r}
library(sjPlot)

tab_model(fullmodel, p.val = "kr", show.df = TRUE)
plot_model(fullmodel, vline.color = "red")

# sort coefficients based on sizee
# plot_model(Method3_fullmodel, sort.est = TRUE)

# sjp.lmer(Method3_fullmodel, y.offset = .4)

plot_model(fullmodel, type = "re")
library(equatiomatic)
equatiomatic::extract_eq(fullmodel)
```

--

## Conclusion: Method 1 vs Method 3 {.unnumbered}

-   TODO: find a way to plot the results side-by-side

```{r}
#sjPlot::sjt.lmer(Method3_fullmodel)
```

### **Comparison between Method 1 and Method 3**

While the coefficients vary from model to model, the t and p values are
identical. Please note that the multilevel modeling does not include the
quadratic stimulus x cue interaction term int he random slopes. Thereby
the t values do differ in this case. TODO: expand and clean \* update
the beta coefficients

#### 1) Statistics of Cue effect

-   **Method 1 onesample-t version**: *b* = -0.1974, *se* = 0.3597,
    *t*(82) = -0.549, *p* = .585

<!-- -->

-   **Method 3 lmer version**: *b* = 0.06580, *se* = 0.11989, *t*(81.99)
    = 0.549, *p* = .5846

#### 4) Interaction effect

-   **Method 1 onesample-t version:** *b* = 0.7858, *se* = 0.3017,
    *t*(82) = 2.605, *p* = 0.0109

-   **Method 3 lmer version**: *b* = -0.78582, *se* = 0.30170,
    *t*(81.99944) = -2.605, *p* = .0109

### In otherwords, the results are identical.

------------------------------------------------------------------------

# References

-   multilevel modelling ::
    <http://www.bristol.ac.uk/cmm/learning/multilevel-models/what-why.html>
-   multilevel modelling :: df
    <https://bbolker.github.io/mixedmodels-misc/glmmFAQ.html#why-doesnt-lme4-display-denominator-degrees-of-freedomp-values-what-other-options-do-i-have>
-   multilevel modelling :: <https://m-clark.github.io/>
-   [Fixed vs random effects models for fMRI meta
    analysis](https://biblio.ugent.be/publication/5775681/file/5775705.pdf)
-   <https://rpsychologist.com/d3/ci/>
-   power analysis :: <https://jakewestfall.shinyapps.io/crossedpower/>
-   power analysis in lmm glmm ::
    <https://lkumle.github.io/power_notebooks/>
-   sjPlot :: <https://github.com/strengejacke/sjPlot/issues/311>
-   sjPlot :: <https://strengejacke.wordpress.com/2017/10/23/one-function-to-rule-them-all-visualization-of-regression-models-in-rstats-w-sjplot/>

# Other links

-   Markdown formatting ::
    <https://bookdown.org/yihui/rmarkdown-cookbook/embed-rmd.html>
-   CANlab glmfit_multilevel ::
    <https://github.com/canlab/CanlabCore/blob/master/CanlabCore/Statistics_tools/glmfit_multilevel.m>
-   lmer results formatting ::
    <http://www.strengejacke.de/sjPlot/articles/sjtlmer.html>
-   lmer results formatting ::
    <https://stats.stackexchange.com/questions/173335/two-regression-outputs-side-by-side-in-r>
-   lmer and formulas :: <https://rpubs.com/rslbliss/r_mlm_ws>
-   repeated measures using aov in R ::
    <https://stackoverflow.com/questions/5694664/repeated-measures-within-subjects-anova-in-r>
-   Matthew McCurdy anova using afex in R
    <https://ademos.people.uic.edu/Chapter21.html>
-   error term in repeated measures R ::
    <https://stats.stackexchange.com/questions/247582/repeated-measures-anova-in-r-errorsubject-vs-errorsubject-day>
-   effect sizes in anova R ::
    <https://cran.r-project.org/web/packages/effectsize/vignettes/anovaES.html>
