---
title: "model08_iv-cue-trial_dv-expect-actual"
author: "Heejung Jung"
date: '2022-09-13'
output: 
  html_document:
    toc: true
    theme: united
    code_folding: hide
editor_options: 
  markdown: 
    wrap: 72
---

# Overview 
The purpose of this markdown is to benchmark the plots from Jepma et al. (2018). 
Here, we plot the expectancy ratings and the actual ratings, with the high and low cues -- in one panel. 

# Some thoughts, TODOs
* plot 2. some runs were repeated or omitted for the subjects that have more than 72 trials. I need to identify that list and work on the behavioral data. 
* I need to check whether the counterbalancing was done correctly. 
* 

# TODO: 
plot 2
TODO: there's something to account for - some runs were repeated or omitted
for the subjects that have more than 72 trials, 
I need to identify that list and word on the behavioral data

library
```{r load libraries, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
# library(lmSupport)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(stats)
library(ggpubr)
library(equatiomatic)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lme4)
library(effectsize)
library(brms)
#library(Hmisc)
#library(Rmisc)
## library(extraoperators)
##library(JWileymisc)
##library(multilevelTools)
# library(PupillometryR)
source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

library(r2mlm)
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

load data and combine participant data

```{r load data and exclude}
main_dir = dirname(dirname(getwd()))
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "cognitive"

ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"

# load data _____________________________________
data <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
# data['event03_RT'], data.event03_RT - pandas
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model08_iv-cue-trial_dv-expect-actual", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```


# plot 1 - one run, average across participants
```{r transform data to longform}

# subject # run # param_cue # param_stim # rating_type # rating_value
#tidyr::pivot(data, key = "rating_value", value = c('event02_expect_angle', 'event04_actual_angle'))
# TODO: need to add tirla numbers

#data$trial = lapply(c("src_subject_id", "session_id", "param_run_num"), factor)
data_trial= data %>%
  arrange(src_subject_id, session_id, param_run_num) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = rep_len(1:12, length.out = n()))
```

```{r}
data_long = data_trial %>% 
  pivot_longer(cols = c('event02_expect_angle', 'event04_actual_angle'),
               names_to = "rating_type", 
               values_to = "rating_value")
```

```{r plot data}
# PLOT
    data_long$cue_name[data_long$param_cue_type == "high_cue"] <- "high cue"
    data_long$cue_name[data_long$param_cue_type == "low_cue"] <- "low cue"

    data_long$stim_name[data_long$param_stimulus_type == "high_stim"] <- "high"
    data_long$stim_name[data_long$param_stimulus_type == "med_stim"] <- "med"
    data_long$stim_name[data_long$param_stimulus_type == "low_stim"] <- "low"
    
    data_long$stim_ordered <- factor(
        data_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_long$cue_ordered <- factor(
        data_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    rating <- "rating_type"
    dv <- "rating_value"
    
    trialorder_subjectwise <- meanSummary(
        data_long,
        c(subject, model_iv2, rating, "trial_index"), dv
    )
    subjectwise_naomit <- na.omit(trialorder_subjectwise) 
    trialorder_groupwise <- summarySEwithin(
        data = subjectwise_naomit,
        measurevar = "mean_per_sub",
        withinvars = c("cue_ordered", "rating_type",  "trial_index"), idvar = subject
    )
```

```{r}
trialorder_subjectwise$rating_type_key <- mapvalues(trialorder_subjectwise$rating_type,
                                                from = c("event02_expect_angle", "event04_actual_angle"),
                                                to = c("expect", "actual"))
trialorder_groupwise$rating_type_key <- mapvalues(trialorder_groupwise$rating_type,
                                                from = c("event02_expect_angle", "event04_actual_angle"),
                                                to = c("expect", "actual"))
actual_trialorder_groupwise <- trialorder_groupwise[which(trialorder_groupwise$rating_type_key == "actual"),]
expect_trialorder_groupwise <-trialorder_groupwise[which(trialorder_groupwise$rating_type_key == "expect"),]
actual_trialorder_subjectwise <- trialorder_subjectwise[which(trialorder_subjectwise$rating_type_key == "actual"),]
expect_trialorder_subjectwise <-trialorder_subjectwise[which(trialorder_subjectwise$rating_type_key == "expect"),]
```

ggplot

```{r}
# * dataset: trialorder_groupwise
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"
data = 
g <- ggplot(
  data = trialorder_groupwise,
  aes(x = trial_index,
      y = mean_per_sub_norm_mean, 
      color = cue_ordered,
      group = rating_type_key
      )
  ) +
    geom_point(
    data = trialorder_groupwise,
    aes(
      shape = as.character(rating_type_key),
      x =trial_index,
      y = mean_per_sub_norm_mean,
      group = rating_type_key,
      #color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 3
    ) +
  scale_shape_manual(values=c(16, 21))+

  # geom_point(
  #   data = trialorder_subjectwise,
  #   aes(
  #     x = as.numeric(trial_index) - .15,
  #     y = mean_per_sub,
  #     color = cue_ordered
  #     ),
  #   position = position_jitter(width = .05),
  #   size = 1, alpha = 0.8, shape = 20
  #   ) +
  geom_errorbar(
    data = trialorder_groupwise,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      group = rating_type_key,
      colour = cue_ordered,
      ymin = mean_per_sub_norm_mean - se,
      ymax = mean_per_sub_norm_mean + se
      ), width = .01, size = 0.5
    ) +
  scale_color_manual(values = c("high cue" = "red", 
                                "low cue" = "blue")) +
    xlab("no. of trials") +
  ylab("rating") +
  ylim(0,100) +
  theme_bw() 
g 
```

# plot 2 - average across participant, but spread all 6 runs in one x axis
load data and combine participant data

```{r p2 :: load data and exclude}
main_dir = dirname(dirname(getwd()))
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "cognitive"

ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"

# load data _____________________________________
data <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
```
### p2 :: check number of trials per participant

```{r p2 check number of trials per participant}
data_p2= data %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
```
### p2 :: identify erroneous participant
```{r p2 identify erroneous participant}
# participants who have more than 72 trials will be flagged
# excluded for now
# TODO: resolve subject 98
count_trial <- data_p2 %>% count("src_subject_id") 
count_trial[count_trial$freq > 72,]
```

### p2 :: convert to long form
```{r p2 convert to long form}
data_p2 <- data_p2[data_p2$src_subject_id != 98, ]
data_p2_long = data_p2 %>% 
  pivot_longer(cols = c('event02_expect_angle', 'event04_actual_angle'),
               names_to = "rating_type", 
               values_to = "rating_value")
```

### p2 :: plot data
I'm plotting all of the trials per participant. In this case, there is no trialwise variability, because we're plotting all 72 trials. 
Averaging across participants will be the only source of variability, reflected in the error bars
```{r p2 plot data}
# PLOT
  # I'm plotting
    data_p2_long$cue_name[data_p2_long$param_cue_type == "high_cue"] <- "high cue"
    data_p2_long$cue_name[data_p2_long$param_cue_type == "low_cue"] <- "low cue"

    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "high_stim"] <- "high"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "med_stim"] <- "med"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "low_stim"] <- "low"
    
    data_p2_long$stim_ordered <- factor(
        data_p2_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_p2_long$cue_ordered <- factor(
        data_p2_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    rating <- "rating_type"
    dv <- "rating_value"
    
    trialorder_groupwise_p2 <- meanSummary(
        data_p2_long,
        c( model_iv2, rating, "trial_index"), dv
    )
    # subjectwise_naomit_p2 <- na.omit(trialorder_subjectwise_p2) 
    # trialorder_groupwise_p2 <- summarySEwithin(
    #     data = subjectwise_naomit_p2, trial_index, 
    #     measurevar = "mean_per_sub",
    #     withinvars = c("cue_ordered", "rating_type", "trial_index"), idvar = subject
    # )
```



```{r}
trialorder_groupwise_p2$rating_type_key <- mapvalues(trialorder_groupwise_p2$rating_type,
                                                from = c("event02_expect_angle", "event04_actual_angle"),
                                                to = c("expect", "actual"))
# trialorder_groupwise_p2$rating_type_key <- mapvalues(trialorder_groupwise_p2$rating_type,
#                                                 from = c("event02_expect_angle", "event04_actual_angle"),
#                                                 to = c("expect", "actual"))
# actual_trialorder_groupwise <- trialorder_groupwise_p2[which(trialorder_groupwise_p2$rating_type_key == "actual"),]
# expect_trialorder_groupwise <-trialorder_groupwise_p2[which(trialorder_groupwise_p2$rating_type_key == "expect"),]
# actual_trialorder_subjectwise <- trialorder_subjectwise_p2[which(trialorder_subjectwise_p2$rating_type_key == "actual"),]
# expect_trialorder_subjectwise <-trialorder_subjectwise_p2[which(trialorder_subjectwise_p2$rating_type_key == "expect"),]
```

ggplot



```{r}
# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"
data = 
g <- ggplot(
  data = trialorder_groupwise_p2,
  aes(x = trial_index,
      y = mean_per_sub, 
      color = cue_ordered,
      group = rating_type_key
      )
  ) +
    geom_point(
    data = trialorder_groupwise_p2,
    aes(
      shape = as.character(rating_type_key),
      x =trial_index,
      y = mean_per_sub,
      group = rating_type_key,
      #color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 3
    ) +
  scale_shape_manual(values=c(16, 21))+

  geom_errorbar(
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub,
      group = rating_type_key,
      colour = cue_ordered,
      ymin = mean_per_sub - sd/sqrt(length(unique(data_p2_long$src_subject_id))),
      ymax = mean_per_sub + sd/sqrt(length(unique(data_p2_long$src_subject_id)))
      ), width = .1, size = 0.5
    ) +
  scale_color_manual(values = c("high cue" = "red", 
                                "low cue" = "blue")) +
  xlab("no. of trials") +
  ylab("rating") +
  ylim(0,100) +
  theme_bw() 
g 
```