---
title: "model05_iv-cue-stim_dv-RT"
author: "Heejung Jung"
date: "06/27/2022"
output: html_document
---
""" 
This Rmarkdown tests the cue effect (high vs. low) on Reaction time and performance in the cognitive, mental-rotation tasks. We also test for stimulus intensity effects.
"""

# model 05 iv-cue dv-RT
* left = diff, right = same
* model 1: Does RT differ as a function of cue type and stimulut intensity?
* model 1-1: Does RT differ as a function of cue, ONLY for the correct trials?
* model 1-2: Does RT differ as a function of cue, ONLY for the incorrect trials?
* model 2: would log-transforming help? Do we see a cue effect on the log-transformmed RTs?

#TODO: 06/28/2022
* change variable names and two factor code accordingly

```{r load libraries, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
library(lmSupport)
library(lme4)
library(lmerTest)
library(plyr)
#library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
#library(Hmisc)
#library(Rmisc)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
## library(extraoperators)
##library(JWileymisc)
##library(multilevelTools)
library(ggpubr)
# library(PupillometryR)
source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

library(r2mlm)
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```


# parameters
```{r main directory, include=FALSE}
main_dir = dirname(dirname(getwd()))
print(main_dir)
```

## 1) plot RT data
```{r load data, echo=TRUE}
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "cognitive"
ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001"
data <- load_task_social_df(taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
```

# plot RT distribution per participant
- the purpose is to identify whether RTs are distributed from 0-5 sec or not
```{r plot RT distribution, echo=TRUE}
ggplot(data,aes(x=event03_RT, group = subject)) +
  geom_histogram(color="darkblue", fill="lightblue", binwidth=0.25, bins = 20) + 
  facet_wrap(~subject, ncol = 10) + 
  theme(axis.text=element_text(size=5),text=element_text(size=6))
```

* some participants may not have responded within time limit
* the button may not have registered the correct onset
* I may have to remove the RTs with 5 sec. 

---

# exclude participants with RT of 5 seconds
```{r}
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "cognitive"

ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"

# load data _____________________________________
data <- load_task_social_df(taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset

analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model05_iv-cue-stim_dv-RT", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)

data$event03_response_samediff <- mapvalues(data$event03_stimulusC_response,
                                                from = c(1, 2),
                                                to = c("diff", "same"))

data$event03_correct <- ifelse(data$event03_C_stim_match == data$event03_response_samediff, 1, ifelse(data$event03_C_stim_match != data$event03_response_samediff, 0, "NA"))
```

# model 1: 
* plotting all of the code
* Does RT differ as a function of high vs. low cue?
* conclusion: No. RT does not differ as a function of cue
```{r model 1 contrast coding}
#contrast code 1 linear
data$stim_con_linear[data$param_stimulus_type == "low_stim"] <- -0.5
data$stim_con_linear[data$param_stimulus_type == "med_stim"] <- 0
data$stim_con_linear[data$param_stimulus_type == "high_stim"] <- 0.5

# contrast code 2 quadratic
data$stim_con_quad[data$param_stimulus_type == "low_stim"] <- -0.33
data$stim_con_quad[data$param_stimulus_type == "med_stim"] <- 0.66
data$stim_con_quad[data$param_stimulus_type == "high_stim"] <- -0.33

# social cue contrast
data$social_cue[data$param_cue_type == 'low_cue'] <- -0.5 # social influence task
data$social_cue[data$param_cue_type == 'high_cue'] <- 0.5 # no influence task
data$cue_factor = factor(data$param_cue_type)
```

```{r model 1 cue effect on RT, echo=TRUE}
# parameters ________________________________
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
stim_con1 = "stim_con_linear"
stim_con2 = "stim_con_quad"
dv <- "event03_RT"
iv_keyword <- "cue-stim"
dv_keyword <- "RT"
xlab <- ""
taskname <- "cognitive"
ylim = c(0,5)
    
# lmer filename ________________________________
model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname, "_iv-", iv_keyword,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), ".txt",
            sep = ""
        )
    )

# removing NA values ________________________________
data_clean = data[!is.na(data$event03_RT),]
#data_clean <- data_clean[complete.cases(data), ]
data_clean$subject = factor(data_clean$src_subject_id)
# lmer model ________________________________
cooksd <- lmer_two_factor_cooksd_fix(data = data_clean,
                                     taskname = "cognitive",
                                     iv = "cue_factor",
                                     stim_con1 = "stim_con_linear",
                                     stim_con2 = "stim_con_quad",
                                     dv = "event03_RT",
                                     subject = "src_subject_id",
                                     dv_keyword = "RT",
                                     model_savefname = model_savefname,
                                     effects = "random_intercept")
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data_clean$subject)))))])
data_screen <- data_clean[-influential, ]

# reordering for plots ----------------------------------------------------------------------------
data_clean$cue_name[data_clean$param_cue_type == "high_cue"] <- "high cue"
data_clean$cue_name[data_clean$param_cue_type == "low_cue"] <- "low cue" # no influence task

data_clean$stim_name[data_clean$param_stimulus_type == "high_stim"] <- "high" # no influence task
data_clean$stim_name[data_clean$param_stimulus_type == "med_stim"] <- "med" # no influence task
data_clean$stim_name[data_clean$param_stimulus_type == "low_stim"] <- "low" # no influence task

data_clean$stim_ordered <- factor(data_clean$stim_name, levels=c("low", "med", "high"))
data_clean$cue_ordered <- factor(data_clean$cue_name, levels=c("low cue", "high cue"))
model_iv1 = "stim_ordered";model_iv2 = "cue_ordered"

# summary statistics for plots ________________________________
subjectwise <- meanSummary(data_clean, c(subject, model_iv1, model_iv2), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(model_iv1, model_iv2), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    group_mean <- "mean_per_sub_norm_mean"
se <- "se";    subject <- "subject"
ggtitle <- paste(taskname, " - Reaction Time (s)");    title <- paste(taskname, " - RT")
xlab <- "";    ylab <- "Reaction Time (s)";    
w = 5; h = 3; dv_keyword <- "RT"
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,"_iv-", iv_keyword,
            "_dv-", dv_keyword,
            "_", as.character(Sys.Date()), ".png",
            sep = ""
        )
    )
plot_rainclouds_twofactor(
        subjectwise, groupwise,
        model_iv1, model_iv2, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

# random effects ________________________________
# randEffect <- as.data.frame(ranef(model_onefactor))
# fixEffect <- as.data.frame(fixef(model_onefactor))
randEffect$newcoef <- mapvalues(randEffect$term,
    from = c("(Intercept)", 
             "param_cue_typelow_cue"
             ),
    to = c("rand_intercept", "rand_cue")
)

rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = `(Intercept)`,
    fix_cue = `param_cue_typelow_cue`,
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",
        as.character(Sys.Date()), "_outlier-cooksd.csv",
        sep = ""
    )
)
write.csv(new_total, rand_savefname, row.names = FALSE)
```


# model 1-1
* omitting code (identical to model 1, except for subsetting correct trials)
* Only using correct trials, does RT differ as a function of high vs. low cue? 
* conclusion 1-1: No. Even within the subset of correct trials, RT does not differ as a function of cue
```{r model 1-1 correct trials only, echo=FALSE}
# parameters ________________________________
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT-correct"
xlab <- ""
taskname <- "cognitive"
ylim = c(0,5)
    
# lmer filename ________________________________
model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), ".txt",
            sep = ""
        )
    )

# removing NA values ________________________________

data_clean = data[!is.na(data$event03_correct),]
data_c = data[data_clean$event03_correct == 1,]
data_c$subject = factor(data_c$src_subject_id)

# lmer model ________________________________
cooksd <- lmer_two_factor_cooksd_fix(data = data_clean,
                                     taskname = "cognitive",
                                     iv = "cue_factor",
                                     stim_con1 = "stim_con_linear",
                                     stim_con2 = "stim_con_quad",
                                     dv = "event03_RT",
                                     subject = "src_subject_id",
                                     dv_keyword = "RT",
                                     model_savefname = model_savefname,
                                     effects = "random_intercept")
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data_c$subject)))))])
data_screen <- data_c[-influential, ]

# summary statistics for plots ________________________________
subjectwise <- meanSummary(data_screen, c(subject, iv), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(iv), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    group_mean <- "mean_per_sub_norm_mean"
se <- "se";    subject <- "subject"
ggtitle <- paste(taskname, dv_keyword);    title <- paste(taskname, " - RT")
xlab <- "";    ylab <- "Reaction Time (s)";    
w = 5; h = 3; 
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_dv-", dv_keyword,
            "_", as.character(Sys.Date()), ".png",
            sep = ""
        )
    )
plot_rainclouds_onefactor(
        subjectwise, groupwise,
        iv, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

# random effects ________________________________
fixEffect_correct <- as.data.frame(fixef(model_onefactor_correct))
randEffect_correct <- as.data.frame(ranef(model_onefactor_correct))
randEffect_correct$newcoef <- mapvalues(randEffect_correct$term,
    from = c("(Intercept)", 
             "param_cue_typelow_cue"
             ),
    to = c("rand_intercept", "rand_cue")
)

rand_subset <- subset(randEffect_correct, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = `(Intercept)`,
    fix_cue = `param_cue_typelow_cue`,
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",dv_keyword,
            "_",
        as.character(Sys.Date()), "_outlier-cooksd.csv",
        sep = ""
    )
)
write.csv(new_total, rand_savefname, row.names = FALSE)
```



# model 1-2: 
* omitting code (identical to model 1, except for subsetting incorrect trials)
* Only using incorrect trials, does RT differ as a function of high vs. low cue? 
* conclusion 1-2: no. Even within the subset of incorrect trials, RT does not differ as a function of cue
```{r model 1-2 incorrect trials only, echo=FALSE}
# parameters ________________________________
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT-incorrect"
xlab <- ""
taskname <- "cognitive"
ylim = c(0,5)
    
# lmer filename ________________________________
model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "_", as.character(Sys.Date()), ".txt",
            sep = ""
        )
    )

# removing NA values ________________________________

data_clean = data[!is.na(data$event03_correct),]
data_i = data[data_clean$event03_correct == 0,]
data_i$subject = factor(data_i$src_subject_id)

# lmer model ________________________________
cooksd <- lmer_two_factor_cooksd_fix(data = data_clean,
                                     taskname = "cognitive",
                                     iv = "cue_factor",
                                     stim_con1 = "stim_con_linear",
                                     stim_con2 = "stim_con_quad",
                                     dv = "event03_RT",
                                     subject = "src_subject_id",
                                     dv_keyword = "RT",
                                     model_savefname = model_savefname,
                                     effects = "random_intercept")
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data_i$subject)))))])
data_screen <- data_i[-influential, ]

# summary statistics for plots ________________________________
subjectwise <- meanSummary(data_screen, c(subject, iv), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(iv), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    group_mean <- "mean_per_sub_norm_mean"
se <- "se";    subject <- "subject"
ggtitle <- paste(taskname, dv_keyword);    title <- paste(taskname, " - RT")
xlab <- "";    ylab <- "Reaction Time (s)";    
w = 5; h = 3; 
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_dv-", dv_keyword,
            "_", as.character(Sys.Date()), ".png",
            sep = ""
        )
    )
plot_rainclouds_onefactor(
        subjectwise, groupwise,
        iv, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

# random effects ________________________________
fixEffect_incorrect <- as.data.frame(fixef(model_onefactor_incorrect))
randEffect_incorrect <- as.data.frame(ranef(model_onefactor_incorrect))
randEffect_incorrect$newcoef <- mapvalues(randEffect_incorrect$term,
    from = c("(Intercept)", 
             "param_cue_typelow_cue"
             ),
    to = c("rand_intercept", "rand_cue")
)

rand_subset <- subset(randEffect_incorrect, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = `(Intercept)`,
    fix_cue = `param_cue_typelow_cue`,
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",dv_keyword,
            "_",
        as.character(Sys.Date()), "_outlier-cooksd.csv",
        sep = ""
    )
)
write.csv(new_total, rand_savefname, row.names = FALSE)
```

# model 2: 
* omitting code (identical to model 1, except for log-transformming RT)
* Does log transformming help? After log-transformming RT, does RT differ as a function of high vs. low cue? 
* conclusion 2: No, log transformmed or not, there is no significant cue effect on RT
```{r model 2 cue effect on log-RT, echo=FALSE}
# parameters ________________________________
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "log_RT"
dv_keyword <- "RT-log"
xlab <- ""
taskname <- "cognitive"
ylim = c(0,5)
    
# lmer filename ________________________________
model_savefname <- file.path(
        analysis_dir,
        paste("lmer_task-", taskname,
            "_rating-", dv_keyword,
            "-log_", as.character(Sys.Date()), ".txt",
            sep = ""
        )
    )

# removing NA values ________________________________
data_clean = data[!is.na(data$event03_correct),]
data_clean$log_RT = log(data_clean$event03_RT)
data_clean$subject = factor(data_clean$src_subject_id)

# lmer model ________________________________
sink(model_savefname)
model_onefactor_log <- lmer(log_RT ~ param_cue_type + (1 | subject), data = data_clean)
summary(model_onefactor_log)
sink()


fixEffect <- as.data.frame(fixef(model_onefactor_log))
randEffect <- as.data.frame(ranef(model_onefactor_log))
cooksd <- cooks.distance(model_onefactor_log)
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(data_clean$subject)))))])
data_screen_log <- data_clean[-influential, ]

# summary statistics for plots ________________________________
subjectwise <- meanSummary(data_screen_log, c(subject, iv), dv)
groupwise <- summarySEwithin(
        data = subjectwise,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(iv), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";    group_mean <- "mean_per_sub_norm_mean"
se <- "se";   
ggtitle <- paste(taskname, dv_keyword);    title <- paste(taskname, " - RT")
xlab <- "";    ylab <- "Reaction Time (s)";    
w = 5; h = 3; 
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4575B4", "#D73027")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
            "_dv-", dv_keyword,
            "-log_", as.character(Sys.Date()), ".png",
            sep = ""
        )
    )
plot_rainclouds_onefactor(
        subjectwise, groupwise,
        iv, subjectwise_mean, group_mean, se, subject,
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

# random effects ________________________________
fixEffect <- as.data.frame(fixef(model_onefactor_log))
randEffect <- as.data.frame(ranef(model_onefactor_log))
randEffect$newcoef <- mapvalues(randEffect$term,
    from = c("(Intercept)", 
             "param_cue_typelow_cue"
             ),
    to = c("rand_intercept", "rand_cue")
)

rand_subset <- subset(randEffect, select = -c(grpvar, term, condsd))
wide_rand <- spread(rand_subset, key = newcoef, value = condval)

wide_fix <- do.call(
    "rbind",
    replicate(nrow(wide_rand),
        as.data.frame(t(as.matrix(fixEffect))),
        simplify = FALSE
    )
)
rownames(wide_fix) <- NULL
new_wide_fix <- dplyr::rename(wide_fix,
    fix_intercept = `(Intercept)`,
    fix_cue = `param_cue_typelow_cue`,
)

total <- cbind(wide_rand, new_wide_fix)
total$task <- taskname
new_total <- total %>% dplyr::select(task, everything())
new_total <- dplyr::rename(total, subj = grp)

rand_savefname <- file.path(
    analysis_dir,
    paste("randeffect_task-", taskname, "_",
        as.character(Sys.Date()), "_outlier-cooksd.csv",
        sep = ""
    )
)
write.csv(new_total, rand_savefname, row.names = FALSE)
```

