---
title: "model08_iv-cue-trial_dv-expect-actual"
author: "Heejung Jung"
date: '2022-09-13'
updated: '2023-01-18'
output: 
  html_document:
    toc: true
    theme: united
    code_folding: hide
editor_options: 
  markdown: 
    wrap: 72
---

# Overview 
The purpose of this markdown is to benchmark the plots from Jepma et al. (2018). 
Here, we plot the expectancy ratings and the actual ratings, with the high and low cues -- in one panel. 

# Some thoughts, TODOs
* plot 2. some runs were repeated or omitted for the subjects that have more than 72 trials. I need to identify that list and work on the behavioral data. 
* I need to check whether the counterbalancing was done correctly. 

# Additional analyse 01/18/2023
* see if current expectation ratings predict outcome ratings
* see if prior stimulus experience (N-1) predicts current expectation ratings
* see if current expectation ratings are explained as a function of prior outcome rating and current expectation rating

library
```{r load_libraries_8, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
# library(lmSupport)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(stats)
library(ggpubr)
library(equatiomatic)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lme4)
library(effectsize)
library(brms)
library(devtools)
library(visibly) # 
library(plotly) #plot
library(scico) # plot
source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
# source("https://gist.github.com/benmarwick/2a1bb0133ff568cbe28d/geom_flat_violin.R")

library(r2mlm)
file.sources = list.files(c("/Users/h/Dropbox/projects_dropbox/social_influence_analysis/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

load data and combine participant data

```{r load data and exclude}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "pain"

ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"

# load data _____________________________________
data <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
data$event03_RT <- data$event03_stimulusC_reseponseonset - data$event03_stimulus_displayonset
# data['event03_RT'], data.event03_RT - pandas
analysis_dir <- file.path(main_dir, "analysis", "mixedeffect", "model08_iv-cue-trial_dv-expect-actual", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```

```{r}
summary(data)
```
```{r}
# data(data, package = 'visibly')

myvars <- names(data) %in% 
  c( "event02_expect_angle", "event02_expect_RT", "event04_actual_angle", "event04_actual_RT", "event01_cue_onset")
newdata <- data[myvars]
# numdata  <- unlist(lapply(data, is.numeric), use.names = FALSE) 
data_naomit <- na.omit(newdata)
cor_matrix = cor(data_naomit)
corr_heat(cor_matrix)
```
```{r}

ISIvars <- names(data) %in% 
  c( "ISI01_duration", "ISI02_duration", "ISI03_duration")
ISIdata <- data[ISIvars]
# numdata  <- unlist(lapply(data, is.numeric), use.names = FALSE) 
ISIdata_naomit <- na.omit(ISIdata)
ISIcor_matrix = cor(ISIdata_naomit)
corr_heat(ISIcor_matrix)
```

```{r}
car::vif(lm(event04_actual_angle ~  event02_expect_angle + event02_expect_RT + event04_actual_RT, dat = data_naomit))

```


# plot 1 - one run, average across participants
```{r transform data to longform}

# subject # run # param_cue # param_stim # rating_type # rating_value
#tidyr::pivot(data, key = "rating_value", value = c('event02_expect_angle', 'event04_actual_angle'))
# TODO: need to add tirla numbers

#data$trial = lapply(c("src_subject_id", "session_id", "param_run_num"), factor)
data_trial= data %>%
  arrange(src_subject_id, session_id, param_run_num) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = rep_len(1:12, length.out = n()))
```

```{r}
data_long = data_trial %>% 
  pivot_longer(cols = c('event02_expect_angle', 'event04_actual_angle'),
               names_to = "rating_type", 
               values_to = "rating_value")
```

```{r plot data - ignore warning - just about creating a new column}
# # PLOT
    data_long$cue_name[data_long$param_cue_type == "high_cue"] <- "high cue"
    data_long$cue_name[data_long$param_cue_type == "low_cue"] <- "low cue"

    data_long$stim_name[data_long$param_stimulus_type == "high_stim"] <- "high"
    data_long$stim_name[data_long$param_stimulus_type == "med_stim"] <- "med"
    data_long$stim_name[data_long$param_stimulus_type == "low_stim"] <- "low"

    data_long$stim_ordered <- factor(
        data_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_long$cue_ordered <- factor(
        data_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    rating <- "rating_type"
    dv <- "rating_value"
    trialorder_subjectwise <- meanSummary(
        data_long,
        c(subject, model_iv2, rating, "trial_index"), dv
    )
    
    subjectwise_naomit <- na.omit(trialorder_subjectwise)
    
    trialorder_groupwise <- summarySEwithin(
        data = subjectwise_naomit,
        measurevar = "mean_per_sub",
        withinvars = c("cue_ordered", "rating_type",  "trial_index"), idvar = subject
    )
```

```{r}
trialorder_subjectwise$rating_type_key <- mapvalues(trialorder_subjectwise$rating_type,
                                                from = c("event02_expect_angle", "event04_actual_angle"),
                                                to = c("expect", "actual"))
trialorder_groupwise$rating_type_key <- mapvalues(trialorder_groupwise$rating_type,
                                                from = c("event02_expect_angle", "event04_actual_angle"),
                                                to = c("expect", "actual"))
actual_trialorder_groupwise <- trialorder_groupwise[which(trialorder_groupwise$rating_type_key == "actual"),]
expect_trialorder_groupwise <-trialorder_groupwise[which(trialorder_groupwise$rating_type_key == "expect"),]
actual_trialorder_subjectwise <- trialorder_subjectwise[which(trialorder_subjectwise$rating_type_key == "actual"),]
expect_trialorder_subjectwise <-trialorder_subjectwise[which(trialorder_subjectwise$rating_type_key == "expect"),]
```

ggplot

```{r}
# * dataset: trialorder_groupwise
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"
data = 
g <- ggplot(
  data = trialorder_groupwise,
  aes(x = trial_index,
      y = mean_per_sub_norm_mean, 
      color = cue_ordered,
      group = rating_type_key
      )
  ) +
    geom_point(
    data = trialorder_groupwise,
    aes(
      shape = as.character(rating_type_key),
      x =trial_index,
      y = mean_per_sub_norm_mean,
      group = rating_type_key,
      #color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 3
    ) +
  scale_shape_manual(values=c(16, 21))+

  # geom_point(
  #   data = trialorder_subjectwise,
  #   aes(
  #     x = as.numeric(trial_index) - .15,
  #     y = mean_per_sub,
  #     color = cue_ordered
  #     ),
  #   position = position_jitter(width = .05),
  #   size = 1, alpha = 0.8, shape = 20
  #   ) +
  geom_errorbar(
    data = trialorder_groupwise,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub_norm_mean,
      group = rating_type_key,
      colour = cue_ordered,
      ymin = mean_per_sub_norm_mean - se,
      ymax = mean_per_sub_norm_mean + se
      ), width = .01, size = 0.5
    ) +
  scale_color_manual(values = c("high cue" = "red", 
                                "low cue" = "blue")) +
    xlab("no. of trials") +
  ylab("rating") +
  ylim(0,100) +
  theme_bw() 
g 
```

# plot 2 - average across participant, but spread all 6 runs in one x axis
load data and combine participant data

```{r p2 :: load data and exclude}
main_dir = dirname(dirname(getwd()))
datadir = file.path(main_dir, 'data', 'beh', 'beh02_preproc')
# parameters _____________________________________ # nolint
subject_varkey <- "src_subject_id"
iv <- "param_cue_type"
dv <- "event03_RT"
dv_keyword <- "RT"
xlab <- ""
taskname <- "pain"

ylab <- "ratings (degree)"
subject <- "subject"
exclude <- "sub-0999|sub-0001|sub-0002|sub-0003|sub-0004|sub-0005|sub-0006|sub-0007|sub-0008|sub-0009|sub-0010|sub-0011"

# load data _____________________________________
data <- load_task_social_df(datadir, taskname = taskname, subject_varkey = subject_varkey, iv = iv, exclude = exclude)
```
### p2 :: check number of trials per participant

```{r p2 check number of trials per participant}
data_p2= data %>%
  arrange(src_subject_id ) %>%
  group_by(src_subject_id) %>%
  mutate(trial_index = row_number())
```
### p2 :: identify erroneous participant
```{r p2 identify erroneous participant}
# participants who have more than 72 trials will be flagged
# excluded for now
# TODO: resolve subject 98
count_trial <- data_p2 %>% count("src_subject_id") 
count_trial[count_trial$freq > 72,]
```

### p2 :: convert to long form
```{r p2 convert to long form}
data_p2 <- data_p2[data_p2$src_subject_id != 98, ]
data_p2_long = data_p2 %>% 
  pivot_longer(cols = c('event02_expect_angle', 'event04_actual_angle'),
               names_to = "rating_type", 
               values_to = "rating_value")
```

### p2 :: plot data
I'm plotting all of the trials per participant. In this case, there is no trialwise variability, because we're plotting all 72 trials. 
Averaging across participants will be the only source of variability, reflected in the error bars
```{r p2 plot data}
# PLOT
  # I'm plotting
    data_p2_long$cue_name[data_p2_long$param_cue_type == "high_cue"] <- "high cue"
    data_p2_long$cue_name[data_p2_long$param_cue_type == "low_cue"] <- "low cue"

    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "high_stim"] <- "high"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "med_stim"] <- "med"
    data_p2_long$stim_name[data_p2_long$param_stimulus_type == "low_stim"] <- "low"
    
    data_p2_long$stim_ordered <- factor(
        data_p2_long$stim_name,
        levels = c("low", "med", "high")
    )
    data_p2_long$cue_ordered <- factor(
        data_p2_long$cue_name,
        levels = c("low cue", "high cue")
    )
    model_iv1 <- "stim_ordered"
    model_iv2 <- "cue_ordered"
    rating <- "rating_type"
    dv <- "rating_value"
    
    trialorder_subjectwise_p2 <- meanSummary(
        data_p2_long,
        c( model_iv2, rating, "trial_index"), dv
    )
    
    subjectwise_naomit_p2 <- na.omit(trialorder_subjectwise_p2)
    trialorder_groupwise_p2 <- summarySEwithin(
        data = subjectwise_naomit_p2, 
        measurevar = "mean_per_sub",
        withinvars = c("cue_ordered", "rating_type", "trial_index"), idvar = subject
    )
```



```{r}
trialorder_groupwise_p2$rating_type_key <- mapvalues(trialorder_groupwise_p2$rating_type,
                                                from = c("event02_expect_angle", "event04_actual_angle"),
                                                to = c("expect", "actual"))
# trialorder_groupwise_p2$rating_type_key <- mapvalues(trialorder_groupwise_p2$rating_type,
#                                                 from = c("event02_expect_angle", "event04_actual_angle"),
#                                                 to = c("expect", "actual"))
# actual_trialorder_groupwise <- trialorder_groupwise_p2[which(trialorder_groupwise_p2$rating_type_key == "actual"),]
# expect_trialorder_groupwise <-trialorder_groupwise_p2[which(trialorder_groupwise_p2$rating_type_key == "expect"),]
# actual_trialorder_subjectwise <- trialorder_subjectwise_p2[which(trialorder_subjectwise_p2$rating_type_key == "actual"),]
# expect_trialorder_subjectwise <-trialorder_subjectwise_p2[which(trialorder_subjectwise_p2$rating_type_key == "expect"),]
```

ggplot



```{r}
# * dataset: trialorder_groupwise_p2
# * x-axis: trial_index (sorted)
# * y-axis: rating
# * group: cue_ordered, rating_type
# * DV: mean_per_sub_norm_mean
# * error bar: se

iv1 = "trial_index"
iv2 = "cue_ordered"
data = 
g <- ggplot(
  data = trialorder_groupwise_p2,
  aes(x = trial_index,
      y = mean_per_sub_mean, 
      color = cue_ordered,
      group = rating_type_key
      )
  ) +
    geom_point(
    data = trialorder_groupwise_p2,
    aes(
      shape = as.character(rating_type_key),
      x =trial_index,
      y = mean_per_sub_mean,
      group = rating_type_key,
      #color = cue_ordered
      ),
    #position = position_jitter(width = .05),
    size = 3
    ) +
  scale_shape_manual(values=c(16, 21))+

  geom_errorbar(
    data = trialorder_groupwise_p2,
    aes(
      x = as.numeric(trial_index),
      y = mean_per_sub_mean,
      group = rating_type_key,
      colour = cue_ordered,
      ymin = mean_per_sub_mean - sd/sqrt(length(unique(data_p2_long$src_subject_id))),
      ymax = mean_per_sub_mean + sd/sqrt(length(unique(data_p2_long$src_subject_id)))
      ), width = .1, size = 0.5
    ) +
  scale_color_manual(values = c("high cue" = "red", 
                                "low cue" = "blue")) +
  xlab("no. of trials") +
  ylab("rating") +
  labs(title = paste(taskname, "- What is the pattern for actual and expect ratings?\nHow is does this pattern differ depending on high vs low cues?"),
        subtitle = "1) As a sanity check, high cues leads to higher outcome ratings, compared to lower outcome ratings. 2) Within high cues, expectations ratings are higher than outcome ratings -- i.e. compensating for the high expectations 3) Within low cues, expectation ratings are lower than outcome ratings -- i.e. compenstation for more painful than expected experience, thus restuling in higher outcome ratings 4) the difference between expectation and outcome rating is smaller in the low cue condition than the high cue condition. ")+
  ylim(0,100) +
  theme_bw() 
g
```


# additional analysis
# Additional analyse 01/18/2023
* see if current expectation ratings predict outcome ratings
* see if prior stimulus experience (N-1) predicts current expectation ratings
* see if current expectation ratings are explained as a function of prior outcome rating and current expectation rating

when loading the dataset, I need to add in trial index per dataframe.
Then, for the shift the rating? 
```{r}
data_a3 <- data_p2 %>% 
  group_by(src_subject_id, session_id, param_run_num) %>% 
  mutate(trial_index = row_number(param_run_num))

data_a3lag <- 
    data_a3 %>%
    group_by(src_subject_id, session_id, param_run_num) %>%
    mutate(lag.04outcomeangle = dplyr::lag(event04_actual_angle, n = 1, default = NA))
data_a3lag_omit <- data_a3lag[complete.cases(data_a3lag$lag.04outcomeangle),]
```


```{r}
    trialorder_subjectwise_lagoutcome <- meanSummary(
        data_a3lag_omit,
        c("src_subject_id", "session_id", "param_run_num"), "lag.04outcomeangle" )
    trialorder_subjectwise_lagoutcome <- meanSummary(
        data_a3lag_omit,
        c("src_subject_id", "session_id", "param_run_num"), "lag.04outcomeangle" )

    # subjectwise_naomit <- na.omit(trialorder_subjectwise)
    # trialorder_groupwise <- summarySEwithin(
    #     data = subjectwise_naomit,
    #     measurevar = "mean_per_sub",
    #     withinvars = c("cue_ordered", "rating_type",  "trial_index"), idvar = subject
    # )
```
```{r}
model.lagoutcome = lmer(event02_expect_angle ~ lag.04outcomeangle + (1 | src_subject_id) + (1|session_id) , data = data_a3lag_omit)
summary(model.lagoutcome)
```

```{r}
meanSummary_2dv <- function(DATA, GROUP, DV1, DV2) {
    z <- ddply(DATA, GROUP, .fun = function(xx) {
        c(
            DV1_mean_per_sub = mean(xx[, DV1], na.rm = TRUE),
            DV1_sd = sd(xx[, DV1], na.rm = TRUE),
            DV2_mean_per_sub = mean(xx[, DV2], na.rm = TRUE),
            DV2_sd = sd(xx[, DV1], na.rm = TRUE)
        )
    })
    return(z)
}
```

```{r}
subjectwise_2dv = meanSummary_2dv(data_a3lag_omit,
        c("src_subject_id", "trial_index"), 
        "lag.04outcomeangle", "event02_expect_angle")
```

```{r}
subjectwise_naomit_2dv <- na.omit(subjectwise_2dv)
```

```{r}
sp <- ggplot(data=subjectwise_naomit_2dv, 
             aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", size=0.5) +
  theme(aspect.ratio=1) +
  xlab("n-1 outcome rating") +
  ylab("n expectation rating")
sp
# plot(subjectwise_naomit_2dv$DV1_mean_per_sub, subjectwise_naomit_2dv$DV2_mean_per_sub) + lines(x = c(0,200), y = c(0,200))
```


```{r}
    trialorder_groupwise <- summarySEwithin(
        data = subjectwise_naomit_2dv,
        measurevar = "DV1_mean_per_sub",
        # betweenvars = "src_subject_id",
        withinvars = factor( "trial_index"),
         idvar = "src_subject_id"
    )
```


```{r}
    trialorder_groupwise <- summarySEwithin(
        data = subset(subjectwise_naomit_2dv, select = -c(src_subject_id)),
        measurevar = "DV1_mean_per_sub",
        # betweenvars = "src_subject_id",
        withinvars = as.factor( "trial_index")
         #idvar = "trial_index"
    )
```
```{r}
data_a3lag_omit$src_subject_id <- as.factor(data_a3lag_omit$src_subject_id)

lag.raw <- ggplot(aes(x=lag.04outcomeangle, y=event02_expect_angle), data=data_a3lag_omit) +
  geom_smooth(method='lm', se=F, size=0.75) +
  geom_point(size=0.1) + 
    geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", size=0.5) +
  facet_wrap(~src_subject_id) + 
  theme(legend.position='none') + 
  xlim(0,180) + ylim(0,180) +
  xlab("raw data from each participant: n-1 lagged outcome angle") + 
  ylab("n current expectation rating")
lag.raw +
  labs(title = paste(taskname, "- Is there a linear relationship between current expectation ratings and the previous outcome ratings?"),
       subtitle = "Plotting the raw data - with all of the datapoints ignoring run differences", 
       caption = "Blue = fitted linear slope per participant; Green: 1:1 slope")
```

```{r}
subjectwise_naomit_2dv$src_subject_id <- as.factor(subjectwise_naomit_2dv$src_subject_id)

lag.avg <- ggplot(aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub), data=subjectwise_naomit_2dv) +
  geom_smooth(method='lm', se=F, size=0.75) +
  geom_point(size=0.1) + 
    geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", size=0.5) +
  facet_wrap(~src_subject_id) + 
  theme(legend.position='none') + 
  xlim(0,180) + ylim(0,180) +
  xlab("raw data from each participant: n-1 lagged outcome angle") + 
  ylab("n current expectation rating") 

lag.avg +
  labs(title = paste(taskname, "- Is there a linear relationship between current expectation ratings and the previous outcome ratings?"),
       subtitle = "Observation notes: 1) The relationship is more of an attenuated one, where the higher outcome ratings lead to a slightly lower expectation rating, and a low outcome leads to a higher expectation rating, when considering a 1:1 relationship. This pattern could be explained by regression to the mean type mechanism, where participants are accounting for the fact that their previous experience was extreme on either ends and that this current trial will be under/over estimated. It probably will make sense to also see the relationship between current expectation ratings influencing current outcome ratings. ", 
       caption = "Blue = fitted linear slope per participant; Green: 1:1 slope")

```

```{r}
# https://gist.github.com/even4void/5074855
```

```{r}
ggplot(data_a3lag_omit, aes(y = event02_expect_angle, 
                       x = lag.04outcomeangle, 
                       colour = subject), size = .3, color = 'gray') + 
  geom_point(size = .1) + 
  geom_smooth(method = 'lm', formula= y ~ x, se = FALSE, size = .3) +
  theme_bw()
```

```{r DEP}
# data_a3lag_omit$subject = as.factor(data_a3lag_omit$src_subject_id)
# model.lagoutcome = lmer(event02_expect_angle ~ lag.04outcomeangle + (1 |subject), data = data_a3lag_omit)
# # unique(as.numeric(row.names(ranef(model.lagoutcome)$src_subject_id)))
# 
# data_a3lag %>%
#   modelr::add_predictions(model.lagoutcome, var = 'event02_expect_angle') %>%
#   dplyr::group_by(subject) %>%
#   # group_by(src_subject_id) %>%
#   plot_ly %>%
#   add_lines(
#     x =  ~ lag.04outcomeangle,
#     y =  ~ mixed,
#     opacity = .2,
#     color = '#00aaff',
#     size = .5,
#     name = 'Mixed\nModel'
#   ) %>%
#   layout(yaxis = list(title = 'event02_expect_angle')) %>%
#   theme_plotly()
```
# Additional analysis
01/23/2023

```{r}
model.lag_cue = lmer(event02_expect_angle ~ lag.04outcomeangle*param_cue_type + (1 | src_subject_id) + (1|session_id) , data = data_a3lag_omit)
summary(model.lag_cue)
```
```{r}
meanSummary_2dv <- function(DATA, GROUP, DV1, DV2) {
    z <- ddply(DATA, GROUP, .fun = function(xx) {
        c(
            DV1_mean_per_sub = mean(xx[, DV1], na.rm = TRUE),
            DV1_sd = sd(xx[, DV1], na.rm = TRUE),
            DV2_mean_per_sub = mean(xx[, DV2], na.rm = TRUE),
            DV2_sd = sd(xx[, DV1], na.rm = TRUE)
        )
    })
    return(z)
}
```

```{r}
subjectwise_cuetype = meanSummary_2dv(data_a3lag_omit,
        c("src_subject_id", "trial_index", "param_cue_type"), 
        "lag.04outcomeangle", "event02_expect_angle")
```

```{r}
# subjectwise_cuetype_2dv <- na.omit(subjectwise_cuetype)
```

```{r}
subjectwise_cuetype$param_cue_type <- as.factor(subjectwise_cuetype$param_cue_type)
sp <- ggplot(data=subjectwise_cuetype, 
             aes(x=DV1_mean_per_sub, y=DV2_mean_per_sub,
             color = param_cue_type)) + 
  geom_point() +
  geom_abline(intercept = 0, slope = 1, color="green", 
                 linetype="dashed", size=0.5) +
  geom_smooth(method = 'lm') +
  theme(aspect.ratio=1) +
  xlab("n-1 outcome rating") +
  ylab("n expectation rating")
sp +
    labs(title = paste(taskname, "- Does the linear relationship between current expectation ratings and the previous outcome ratings differ as a function of cue?"),
       subtitle = "Plotting the raw data - with all of the datapoints averaged across runs per 12 trials", 
       caption = "high cue vs low cue. The slope is significant, theree is not interaction; Green: 1:1 slope")
# plot(subjectwise_naomit_2dv$DV1_mean_per_sub, subjectwise_naomit_2dv$DV2_mean_per_sub) + lines(x = c(0,200), y = c(0,200))
```
