---
title: "model09_iv-temp_dv-scl"
author: "Heejung Jung"
date: "2022-12-07"
output:
  html_document:
    toc: true
    theme: united
    code_folding: hide
editor_options:
  markdown:
    wrap: 72
---

TODO:
split data into task (full -> P, v, c subset)
push code to git
create code map
log transform

- SCL: mean signal
- SCR: log transform

# Overview

The purpose of this notebook is to analyze biopac phasic data.
Data has been preprocessed with neurokit

We load a dataframe that contains the following outcome measures:
'Event_Onset', 'EDA_Peak_Amplitude', 'EDA_SCR', 'SCR_Peak_Amplitude',
'SCR_Peak_Amplitude_Time', 'SCR_RiseTime', 'SCR_RecoveryTime'

We model this as a function of "cue" and "stimulus intensity",
while allowing for random effects from participants.

---

# Why use multilevel models?

- content copied from
  <http://www.bristol.ac.uk/cmm/learning/multilevel-models/what-why.html>

> There are a number of reasons for using multilevel models:
>
> 1.  Correct inferences: Traditional multiple regression techniques
>     treat the units of analysis as independent observations. One
>     consequence of failing to recognise hierarchical structures is
>     that standard errors of regression coefficients will be
>     underestimated, leading to an overstatement of statistical
>     significance. Standard errors for the coefficients of higher-level
>     predictor variables will be the most affected by ignoring
>     grouping.
>
> 2.  Substantive interest in group effects: In many situations a key
>     research question concerns the extent of grouping in individual
>     outcomes, and the identification of 'outlying' groups. In
>     evaluations of school performance, for example, interest centres
>     on obtaining 'value-added' school effects on pupil attainment.
>     Such effects correspond to school-level residuals in a multilevel
>     model which adjusts for prior attainment.
>
> 3.  Estimating group effects simultaneously with the effects of
>     group-level predictors: An alternative way to allow for group
>     effects is to include dummy variables for groups in a traditional
>     (ordinary least squares) regression model. Such a model is called
>     an analysis of variance or fixed effects model. In many cases
>     there will be predictors defined at the group level, eg type of
>     school (mixed vs. single sex). In a fixed effects model, the
>     effects of group-level predictors are confounded with the effects
>     of the group dummies, ie it is not possible to separate out
>     effects due to observed and unobserved group characteristics. In a
>     multilevel (random effects) model, the effects of both types of
>     variable can be estimated.
>
> 4.  Inference to a population of groups: In a multilevel model the
>     groups in the sample are treated as a random sample from a
>     population of groups. Using a fixed effects model, inferences
>     cannot be made beyond the groups in the sample.

---

load libraries

```{r load libraries, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
library(psych)
library(car)
library(lme4)
library(lmerTest)
library(dplyr)
library(plyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
library(stats)
library(ggpubr)
library(equatiomatic)
library(sjPlot)
library(sjmisc)
library(sjlabelled)
library(lme4)
library(effectsize)
library(brms)
#library(Hmisc)
#library(Rmisc)
## library(extraoperators)
##library(JWileymisc)
##library(multilevelTools)
# library(PupillometryR)
# source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
# source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
# source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
# source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
# source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

library(r2mlm)
main_dir = dirname(dirname(getwd()))
file.sources = list.files(file.path(main_dir, "scripts/step02_R/utils"),
                         pattern="*.R",
                          full.names=TRUE,
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)
```

# Terminology

factor

: In experimental designs, factor is the equivalent of independent
variable. In R, one can factorize a categorical variable by using
the `factor` function. Thereby we interchangeably use the term
factor in lieu of independent variable.

    From this, the term `factorial design` originates.

level

: within each independent variable, a researcher may determine
different levels. Since the purpose of linear models is to compare
at least one condition to another, a factor contains more than one
level.

group variable

: Unit of analysis. In most fMRI experiments that collect individual
data, the group variable would be the individual participant.
However, in other research questions, the group variable could
easily be more than one individual. For instance, a dyad of
participants that carry out conversations, multiple patients that
see an identical doctor, a classroom full of individuals, or voting
districts could serve as a grouping variable, depending on the
research question.

- <div>

      factor:
      group

  </div>

# Model versions {.tabset}

## Summary of models

### Method 1: repeated measures and `one-sample t-tests`

- Data Matrix: Wide form
  - row (83 subject)
  - column (6 conditions: highCue x highStim, highCue x medStim,
    highCue x lowStim, lowCue x highStim,lowCue x medStim, lowCue x
    lowStim)
- Model: Use "lm". One-sample t-test
- Effect size (cohen's d): mean / sd (intersubject slope) \> use
  degrees of freedom.

###

load data and combine participant data

```{r load data and exclude}
main_dir = dirname(dirname(getwd()))
analysis_dir <- file.path(main_dir, "analysis", "physio", "physio01_SCL", as.character(Sys.Date()))
dir.create(analysis_dir, showWarnings = FALSE, recursive = TRUE)
```

```{r}
analysis_dir
```

```{r}
# parameters _____________________________________ # nolint
main_dir = dirname(dirname(getwd()))
tonic = read.csv(file.path(main_dir, "analysis/physio/physio01_SCL/sub-all_ses-all_run-all_runtype-pain_epochstart--1_epochend-15_samplingrate-25_ttlindex-2_physio-scltimecourse.csv"))
```

This is the data that we will use

```{r echo=FALSE}
head(tonic)
```

## Method 3 multilevel modeling

### Method 3 multilevel modeling

- Data Matrix: Long form
  - Row (5412: 83 subject \* 2 cue \* 3 stimulus intensity \* 12 trials)
  - Columns (4: subject, session, task type, run_num, cue type, stimulus intensity type,
    EDA metrics)
- Model: Use "lmer" multilevel-modeling
  - grouping variable: subjects (i.e. src_subject_id)
  - fixed effects - cue (2 levels, contrast-coded [high, low: 1,
    -1]) - stim_linear (3 levels, [low, med, high: -1, 0, 1]) -
    stim_quadratic (3 levels, [low, med, high: -1, 2, -1])
  - random effects - cue - stim_linear - cue\*stim_linear
  - NOTE: due to convergence failure, cue\*stim_quadratic term was
    removed
- Effect size (cohen's d): beta_coefficient/ sqrt(sum of all random
  variance)

contrast-coding for multi-level modeling (code-hidden)

```{r model 3 contrast coding}
#contrast code 1 linear
tonic$stim_con_linear[tonic$param_stimulus_type == "low_stim"] <- -0.5
tonic$stim_con_linear[tonic$param_stimulus_type == "med_stim"] <- 0
tonic$stim_con_linear[tonic$param_stimulus_type == "high_stim"] <- 0.5

# contrast code 2 quadratic
tonic$stim_con_quad[tonic$param_stimulus_type == "low_stim"] <- -0.33
tonic$stim_con_quad[tonic$param_stimulus_type == "med_stim"] <- 0.66
tonic$stim_con_quad[tonic$param_stimulus_type == "high_stim"] <- -0.33

# social cue contrast
tonic$social_cue[tonic$param_cue_type == 'low_cue'] <- -0.5 # social influence task
tonic$social_cue[tonic$param_cue_type == 'high_cue'] <- 0.5 # no influence task
tonic$cue_factor = factor(tonic$social_cue)
```

```{r}
# parameters ___________________________________________________________________
tonic$subject = factor(tonic$src_subject_id)
subject_varkey <- "subject"
iv <- "cue_factor"
stim_con1 = "stim_con_linear"
stim_con2 = "stim_con_quad"
dv <- "mean_signal" # DON"T USE EDA_Peak_Amplitude (misleading)
iv_keyword <- "cue-stim"
dv_keyword <- "scl_peak"
xlab <- ""
taskname <- "full"
#ylim = c(-1,1)
#tonic_task =
```

multi-level modeling using **lmer**

```{r lmer fullmodel, class.source = 'fold-show'}
fullmodel = lmer(mean_signal ~ 1+ cue_factor + stim_con_linear + stim_con_quad + cue_factor:stim_con_linear + cue_factor:stim_con_quad + (1  |subject), data = tonic)

# output of model
summary(fullmodel)

```

```{r plot results}

cooksd <- cooks.distance(fullmodel)
influential <- as.numeric(names(cooksd)[
    (cooksd > (4 / as.numeric(length(unique(tonic$subject)))))])
data_screen <- tonic[-influential, ]

# reordering for plots _________________________________________________________
tonic$cue_name[tonic$param_cue_type == "high_cue"] <- "high cue"
tonic$cue_name[tonic$param_cue_type == "low_cue"] <- "low cue" # no influence task

tonic$stim_name[tonic$param_stimulus_type == "high_stim"] <- "high" # no influence task
tonic$stim_name[tonic$param_stimulus_type == "med_stim"] <- "med" # no influence task
tonic$stim_name[tonic$param_stimulus_type == "low_stim"] <- "low" # no influence task

tonic$stim_ordered <- factor(tonic$stim_name, levels=c("low", "med", "high"))
tonic$cue_ordered <- factor(tonic$cue_name, levels=c("low cue", "high cue"))
model_iv1 = "stim_ordered";model_iv2 = "cue_ordered"

# summary statistics for plots _________________________________________________
subjectwise <- meanSummary(tonic, c("subject", model_iv1, model_iv2), dv)
try <- na.omit(subjectwise)
groupwise <- summarySEwithin(
        data = try,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(model_iv1, model_iv2), # iv
        idvar = "subject"
    )

subjectwise_mean <- "mean_per_sub";
group_mean <- "mean_per_sub_norm_mean"
se <- "se";
ggtitle <- paste(taskname, dv_keyword);
title <- paste(taskname, " - RT")
xlab <- "";
ylab <- "SCL peak amplitude ";
w = 5; h = 3;
ylim = c(-1,3)
if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#1B9E77", "#D95F02")
    } else {
        color <- c("#4274AD", "#C5263A")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
              "_iv-", iv_keyword,"_dv-", dv_keyword,
              "_", as.character(Sys.Date()), ".png",
              sep = ""
        )
    )
plot_rainclouds_twofactor(
        try, groupwise,
        model_iv1, model_iv2, subjectwise_mean, group_mean, se, "subject",
        ggtitle, title, xlab, ylab, task_name, ylim,
        w, h, dv_keyword, color, plot_savefname
    )

```

# Temperature predicting rating

```{r temperature fullmodel, class.source = 'fold-show'}
temp_pain = lmer(event02_expect_angle ~ 1+ stim_con_linear + stim_con_quad + (1  |subject), data = tonic)

# output of model
summary(temp_pain)

```

```{r}
key = 'actual'
if (any(startsWith(key, c("expect", "Expect")))) {
        dv = 'event02_expect_angle'
        dv_keyword = 'expect_rating'
        ylab <- "expect rating ";
    } else {
        dv = 'event04_actual_angle'
        dv_keyword = 'actual_rating'
        ylab <- "actual rating ";
    }
# dv = 'event02_expect_angle'
iv_keyword = 'temp'
# dv_keyword = 'expect_rating'
task_name = 'pain'
subjectwise_mean <- "mean_per_sub";
group_mean <- "mean_per_sub_norm_mean"
se <- "se";
ggtitle <- paste(task_name, dv_keyword);
title <- paste(task_name, " - temperature")
xlab <- "";
# ylab <- "expect rating ";
w = 5; h = 3;
ylim = c(-1,180)


cooksd_temp <- cooks.distance(temp_pain)
influential_temp <- as.numeric(names(cooksd_temp)[
    (cooksd > (4 / as.numeric(length(unique(tonic$subject)))))])
data_screen_temp <- tonic[-influential_temp, ]

# reordering for plots _________________________________________________________

tonic$stim_name[tonic$param_stimulus_type == "high_stim"] <- "high" # no influence task
tonic$stim_name[tonic$param_stimulus_type == "med_stim"] <- "med" # no influence task
tonic$stim_name[tonic$param_stimulus_type == "low_stim"] <- "low" # no influence task

tonic$stim_ordered <- factor(tonic$stim_name, levels=c("low", "med", "high"))
#tonic$cue_ordered <- factor(tonic$cue_name, levels=c("low cue", "high cue"))
model_iv1 = "stim_ordered"; #model_iv2 = "cue_ordered"

# summary statistics for plots _________________________________________________
subjectwise_temp <- meanSummary(tonic, c("subject", model_iv1), dv)
try <- na.omit(subjectwise_temp)
groupwise_temp <- summarySEwithin(
        data = try,
        measurevar = "mean_per_sub", # variable created from above
        withinvars = c(model_iv1), # iv
        idvar = "subject"
    )

if (any(startsWith(dv_keyword, c("expect", "Expect")))) {
        color <- c("#7678ed", "#f7b801", "#f18701")
    } else {
        color <- c("#4575B4",  "#D95F02", "#D73027")
    }
plot_savefname <- file.path(
        analysis_dir,
        paste("raincloud_task-", taskname,
              "_iv-", iv_keyword,"_dv-", dv_keyword,
              "_", as.character(Sys.Date()), ".png",
              sep = ""
        )
    )
plot_rainclouds_onefactor(
        subjectwise = try, groupwise = groupwise_temp,
        iv = model_iv1, subjectwise_mean = subjectwise_mean, group_mean = group_mean,
        se = se, subject = "subject",
        ggtitle = ggtitle, title = title, xlab = xlab, ylab = ylab, taskname = task_name, ylim = ylim,
        w = w, h = h, dv_keyword = dv_keyword, color, plot_savefname
    )

```
