---
title: "PVC_dartmouth_TorSuggestion"
author: "Heejung Jung"
date: "4/6/2021"
output: html_document
---
# load libraries
```{r}
library(psych)
library(car)
library(lmSupport)
library(lme4)
library(lmerTest)
library(plyr)

library(tidyr)
library(stringr)
library(ggplot2)
#library(Hmisc)

#library(Rmisc)
library(png)
library(knitr)
library(TMB)
#library(sjPlot)
#library(ggpubr)
library(gridExtra)
#library(merTools)
#library(sjstats) #to get ICC
#library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
## library(extraoperators)
##library(JWileymisc)
##library(multilevelTools)
library(ggpubr)
library(dplyr)
# library(PupillometryR)
source('http://psych.colorado.edu/~jclab/R/mcSummaryLm.R')
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(r2mlm)
```


# parameters

```{r}
main_dir = dirname(dirname(getwd()))
```
# 0. function

## a) summary table
http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/#Helper%20functions

### Function normdatawithin
```{r}
normDataWithin <- function(data=NULL, idvar, measurevar, betweenvars=NULL,
                           na.rm=FALSE, .drop=TRUE) {
  ## Norms the data within specified groups in a data frame; it normalizes each
## subject (identified by idvar) so that they have the same mean, within each group
## specified by betweenvars.
##   data: a data frame.
##   idvar: the name of a column that identifies each subject (or matched subjects)
##   measurevar: the name of a column that contains the variable to be summariezed
##   betweenvars: a vector containing names of columns that are between-subjects variables
##   na.rm: a boolean that indicates whether to ignore NA's
    library(plyr)

    # Measure var on left, idvar + between vars on right of formula.
    data.subjMean <- ddply(data, c(idvar, betweenvars), .drop=.drop,
     .fun = function(xx, col, na.rm) {
        c(subjMean = mean(xx[,col], na.rm=na.rm))
      },
      measurevar,
      na.rm
    )

    # Put the subject means with original data
    data <- merge(data, data.subjMean)

    # Get the normalized data in a new column
    measureNormedVar <- paste(measurevar, "_norm", sep="")
    data[,measureNormedVar] <- data[,measurevar] - data[,"subjMean"] +
                               mean(data[,measurevar], na.rm=na.rm)

    # Remove this subject mean column
    data$subjMean <- NULL

    return(data)
}
```

### FUNCTION: summarySEwithin
```{r}
summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=NULL,
                            idvar=NULL, na.rm=FALSE, conf.interval=.95, .drop=TRUE) {

  ## Summarizes data, handling within-subjects variables by removing inter-subject variability.
## It will still work if there are no within-S variables.
## Gives count, un-normed mean, normed mean (with same between-group mean),
##   standard deviation, standard error of the mean, and confidence interval.
## If there are within-subject variables, calculate adjusted values using method from Morey (2008).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   betweenvars: a vector containing names of columns that are between-subjects variables
##   withinvars: a vector containing names of columns that are within-subjects variables
##   idvar: the name of a column that identifies each subject (or matched subjects)
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
  # Ensure that the betweenvars and withinvars are factors
  factorvars <- vapply(data[, c(betweenvars, withinvars), drop=FALSE],
    FUN=is.factor, FUN.VALUE=logical(1))

  if (!all(factorvars)) {
    nonfactorvars <- names(factorvars)[!factorvars]
    message("Automatically converting the following non-factors to factors: ",
            paste(nonfactorvars, collapse = ", "))
    data[nonfactorvars] <- lapply(data[nonfactorvars], factor)
  }

  # Get the means from the un-normed data
  datac <- summarySE(data, measurevar, groupvars=c(betweenvars, withinvars),
                     na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Drop all the unused columns (these will be calculated with normed data)
  datac$sd <- NULL
  datac$se <- NULL
  datac$ci <- NULL

  # Norm each subject's data
  ndata <- normDataWithin(data, idvar, measurevar, betweenvars, na.rm, .drop=.drop)

  # This is the name of the new column
  measurevar_n <- paste(measurevar, "_norm", sep="")

  # Collapse the normed data - now we can treat between and within vars the same
  ndatac <- summarySE(ndata, measurevar_n, groupvars=c(betweenvars, withinvars),
                      na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Apply correction from Morey (2008) to the standard error and confidence interval
  #  Get the product of the number of conditions of within-S variables
  nWithinGroups    <- prod(vapply(ndatac[,withinvars, drop=FALSE], FUN=nlevels,
                           FUN.VALUE=numeric(1)))
  correctionFactor <- sqrt( nWithinGroups / (nWithinGroups-1) )

  # Apply the correction factor
  ndatac$sd <- ndatac$sd * correctionFactor
  ndatac$se <- ndatac$se * correctionFactor
  ndatac$ci <- ndatac$ci * correctionFactor

  # Combine the un-normed means with the normed results
  df = merge(datac, ndatac)
  return(df)
  
}
```

### FUNCTION: summarySE
```{r}
# summarySE function
summarySE <- function(data = NULL, measurevar, groupvars = NULL, na.rm = FALSE,
                      conf.interval = .95, .drop = TRUE) {
  library(plyr)

  # New version of length which can handle NA's: if na.rm==T, don't count them
  length2 <- function(x, na.rm = FALSE) {
    if (na.rm) {
      sum(!is.na(x))
    } else {
      length(x)
    }
  }

  # This does the summary. For each group's data frame, return a vector with
  # N, mean, median, and sd

  datac <- plyr::ddply(data, groupvars, .drop=.drop,
                   .fun = function(xx, col) {
                       c(N      = length2(xx[[col]], na.rm=na.rm),
                         mean   = mean(xx[[col]], na.rm=na.rm),
                         median = median(xx[[col]], na.rm=na.rm),
                         sd      = sd(xx[[col]], na.rm=na.rm)
                       )
                   },
                   measurevar
  )

  # Rename the "mean" and "median" columns
 datac <- plyr::rename(datac, c("mean" = paste(measurevar, "_mean", sep = "")))
 datac <- plyr::rename(datac, c("median" = paste(measurevar, "_median", sep = "")))

 datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean

  # Confidence interval multiplier for standard error
  # Calculate t-statistic for confidence interval:
  # e.g., if conf.interval is .95, use .975 (above/below), and use df=N-1
  ciMult <- qt(conf.interval / 2 + .5, datac$N - 1)
  datac$ci <- datac$se * ciMult

  return(datac)
}
```

### FUNCTION: meanSummary
```{r}
meanSummary <- function(DATA, GROUP, DV){
  z <- ddply(DATA, GROUP, .fun = function(xx){
                         c(mean_per_sub = mean(xx[,DV],na.rm=TRUE),
                         sd = sd(xx[,DV],na.rm=TRUE) ) })
  return(z)
  }
```


## FUNCTION: expect_df load data
```{r}
expect_df = function(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE ) {
  
  # INPUT:
  # * TASKNAME (e.g. pain, cognitive, vicarious)
  # * SUBJECT_VARKEY (e.g. src_subject_id or subject)
  # A. load data ______________________________________________________________
  FILENAME = paste('*_task-social_*-' ,TASKNAME, '_beh.csv', sep = "")
  common_path = Sys.glob(file.path(main_dir,'data', 'dartmouth', 'd02_preprocessed',
                                   'sub-*','ses-*',FILENAME))
  filter_path = common_path[!str_detect(common_path,pattern="sub-0001")]
  
  DF <- do.call("rbind",lapply(filter_path,FUN=function(files){ read.csv(files)}))
  is.nan.data.frame <- function(x)
    do.call(cbind, lapply(x, is.nan))
  DF[is.nan(DF)] <- NA
  # subjects as factor
  print("subject")
  DF[,"subject"] = factor(DF[,SUBJECT_VARKEY])
  # print("line323")
  # B. plot expect rating NA ___________________________________________________
  DF_expect_NA = aggregate(DF[,DV], list(DF$subject),function(x) sum(is.na(x)))
  TITLE = paste(TASKNAME, " task - Expectation ratings", sep = "" )
  ggplot(DF_expect_NA, aes(x = Group.1, y = x))+ 
    geom_bar(stat = "identity", position = "identity") +
    xlab("subject ID") + 
    ylab("freq. of NA") + 
    ggtitle(TITLE) +
    theme_bw()
  
  # C. run model ___________________________________________________
  
  DF_remove_NA = DF[!is.na(  DF[DV]  ),]
  return(DF_remove_NA)
  return(as.data.frame(DF_remove_NA))
}

```

## FUNCTION: run_cue_lmer 
```{r}
run_cue_lmer = function(DATA,TASKNAME, IV, DV, SUBJECT, DV_KEYWORD){
  model.cue = lmer( DATA[,DV] ~ DATA[,IV] + (DATA[,IV] | DATA[,SUBJECT]))
  print("--------------------------")
  print(paste("model: ", str_to_title(DV_KEYWORD), " ratings - ", TASKNAME))
  print(paste("IV: ", str_to_title(IV),"DV: ", str_to_title(DV) ))
  print(paste("Random effects: ", str_to_title(SUBJECT)))
  print("--------------------------")
  print(summary(model.cue))
  
  model_filename = file.path(main_dir, 'analysis', 'archive', 'wideform', 
                   paste('lmer_task-' ,TASKNAME, '_rating-', DV_KEYWORD,'_torsuggest-wideform.txt', sep = ""))
  sink(model_filename)
  print("--------------------------")
  print(paste("model: ", str_to_title(DV_KEYWORD), " ratings - ", TASKNAME))
  print(paste("IV: ", str_to_title(IV),"DV: ", str_to_title(DV) ))
  print(paste("Random effects: ", str_to_title(SUBJECT)))
  print("--------------------------")
  print(summary(model.cue))
  sink()
  }
```

## FUNCTION: run_full_lmer
```{r}
run_full_lmer = function(DATA,TASKNAME, IV,CON1, CON2, DV, SUBJECT, DV_KEYWORD){
  
  
  model.full = lmer( DATA[,DV] ~ DATA[,IV]* DATA[,CON1] +
                       DATA[,IV]* DATA[,CON2]+ 
                       (DATA[,IV]* DATA[,CON1] +  DATA[,IV]* DATA[,CON2] | DATA[,SUBJECT])
                     )
  print("--------------------------")
  print(paste("model: ", str_to_title(DV_KEYWORD), " ratings - ", TASKNAME))
  print(paste("IV: ", str_to_title(IV),"CONTRASTS",str_to_title(CON1),str_to_title(CON2), "DV: ", str_to_title(DV) ))
  print(paste("Random effects: ", str_to_title(SUBJECT)))
  print("--------------------------")
  print(summary(model.full))
  
  model_filename = file.path(main_dir, 'analysis', 'semicircle_degree', 
                   paste('lmer_task-' ,TASKNAME, '_rating-', DV_KEYWORD,'_torsuggest.txt', sep = ""))
  sink(model_filename)
  print("--------------------------")
  print(paste("model: ", str_to_title(DV_KEYWORD), " ratings - ", TASKNAME))
  print(paste("IV: ", str_to_title(IV),"CONTRASTS",str_to_title(CON1),str_to_title(CON2), "DV: ", str_to_title(DV) ))
  print(paste("Random effects: ", str_to_title(SUBJECT)))
  print("--------------------------")
  print(summary(model.full))
  sink()
  }
```

# ______________
# 1. EXPECT
# ______________


## expect contrast
```{r}
# stimulus intensity
DF$stim[DF$event03_stimulus_type == "low_stim"] <- -0.5 # social influence task
DF$stim[DF$event03_stimulus_type == "med_stim"] <- 0 # no influence task
DF$stim[DF$event03_stimulus_type == "high_stim"] <- 0.5 # no influence task

DF$stim_factor = factor(DF$event03_stimulus_type)

#contrast code 1 linear
DF$stim_con_linear[DF$event03_stimulus_type == "low_stim"] <- -0.5
DF$stim_con_linear[DF$event03_stimulus_type == "med_stim"] <- 0
DF$stim_con_linear[DF$event03_stimulus_type == "high_stim"] <- 0.5

# contrast code 2 quadratic
DF$stim_con_quad[DF$event03_stimulus_type == "low_stim"] <- -0.33
DF$stim_con_quad[DF$event03_stimulus_type == "med_stim"] <- 0.66
DF$stim_con_quad[DF$event03_stimulus_type == "high_stim"] <- -0.33

# social cude contrast
DF$social_cue[DF$param_cue_type == 'low_cue'] <- -0.5 # social influence task
DF$social_cue[DF$param_cue_type == 'high_cue'] <- 0.5 # no influence task
DF$cue_factor = factor(DF$param_cue_type)
```

```
IV: cue
DV: expectation rating
```
```{r}
# parameters
TASKNAME = 'vicarious'
SUBJECT_VARKEY = "src_subject_id"
IV = "param_cue_type"
DV = "event02_expect_angle"
DV_KEYWORD = "expect"
XLAB = ""; YLAB = "ratings (degree)"; 
if(any(startsWith(DV_KEYWORD, c("expect", "Expect")))){COLOR = c( "#1B9E77", "#D95F02")}else{COLOR=c( "#4575B4", "#D73027")} # if 
GGTITLE = paste(TASKNAME, " - Expectation Rating (degree)")
TITLE = paste(TASKNAME, " - Expect")
SUBJECT = "subject"
EXCLUDE = ""

DATA = expect_df(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE )

DATA$cue[DATA$param_cue_type == 'high_cue'] <- "high cue" 
DATA$cue[DATA$param_cue_type == 'low_cue'] <- "low cue" # no influence task

DATA$stim[DATA$param_stimulus_type == 'high_stim'] <- "high" # no influence task
DATA$stim[DATA$param_stimulus_type == 'med_stim'] <- "med" # no influence task
DATA$stim[DATA$param_stimulus_type == 'low_stim'] <- "low" # no influence task

DATA$stim <- factor(DATA$stim, levels=c("low", "med", "high"))
DATA$cue <- factor(DATA$cue, levels=c( "low cue", "high cue"))
df_d = meanSummary(DATA, c(SUBJECT, "stim", "cue"), DV)


run_cue_lmer(DATA,TASKNAME, IV, DV, SUBJECT, DV_KEYWORD)

# IV = "param_cue_type"
# DV = "event02_expect_angle"

# plot ver 1
df_d = meanSummary(DATA, c(SUBJECT, "cue"), DV)
df_a = summarySEwithin(data=df_d,
                  measurevar = "mean_per_sub", # variable created from above
                    withinvars = c("cue"), # IV
                    idvar = "subject")

p1 <- ggplot(data = df_a, aes(x = cue, y = mean_per_sub_norm_mean, fill = cue)) +
  geom_bar(stat = "identity", width = .5) +
  geom_errorbar(data = df_a, aes(ymin = mean_per_sub_norm_mean-ci, ymax = mean_per_sub_norm_mean+ci, width = .05))+
  geom_point(data = df_d, aes(y = mean_per_sub, x = cue), alpha = 0.4, width = .1, 
             position = position_jitter(.1),
             size = 2) +
  guides(fill=FALSE) +
  ylab("score mean") +
  # theme_cowplot()+
  ggtitle(GGTITLE)
p1

# plot ver 2 - con
WIDE_EXPECT = meanSummary(DATA, c(SUBJECT, IV), DV)

WIDE_EXPECT_D = DATA_EXPECT %>%
  select(subject, param_cue_type, mean_per_sub ) %>%
  spread( param_cue_type, mean_per_sub )
WIDE_EXPECT_D$high_vs_low_cue = WIDE_EXPECT_D$high_cue - WIDE_EXPECT_D$low_cue

WIDE_EXPECT_A = summarySE(data=WIDE_EXPECT_D,
                  measurevar = "high_vs_low_cue") # variable created from above
                # withinvars = c("subject")) # IV
                   # idvar = "subject")

# summarySE <- function(data = NULL, measurevar, groupvars = NULL, na.rm = FALSE,
                      # conf.interval = .95, .drop = TRUE) 

expect.effect.size = mean(WIDE_EXPECT$high_vs_low_cue)/sd(WIDE_EXPECT$high_vs_low_cue) # 2.61

res <- t.test(WIDE_EXPECT_D$high_vs_low_cue, mu = 0)
print(res)

# data:  WIDE_EXPECT_D$high_vs_low_cue
# t = 7.8302, df = 8, p-value = 5.095e-05
# alternative hypothesis: true mean is not equal to 0
# 95 percent confidence interval:
#  23.24188 42.64609
# sample estimates:
# mean of x 
#  32.94398 


# raincloud plots
g <- ggplot(data = df_d, aes(y = mean_per_sub, x = cue, fill = cue)) +
  geom_flat_violin(aes(fill = cue), position = position_nudge(x = .1, y = 0), adjust = 1.5,
                   trim = FALSE, alpha = .5, colour = NA) +
  geom_line(data = df_d, aes(group = subject, y = mean_per_sub, x = as.numeric(cue)-.15, fill = cue), linetype = 3, color = "grey") +
  #geom_point(aes(group = subject, x = as.numeric(levels_ordered)-.15, y = mean_per_sub, color = social_name),
 #            position = position_jitter(width = .05), size = 1, alpha = 0.8, shape = 20) +
  geom_point(aes(x = as.numeric(cue)-.15, y = mean_per_sub, color = cue),
             position = position_jitter(width = .05), size = 1, alpha = 0.8, shape = 20) +
  geom_boxplot(aes(x = cue, y = mean_per_sub, fill = cue),width = .1,
               outlier.shape = NA, alpha = 0.8, width = .1, colour = "black") +
  
  # use summary stats __________________________________________________________________________________
#  geom_line(data = a, aes(x = as.numeric(levels_ordered)+.1, y = mean_degree_per_sub_norm,
#                           group = social_name, colour = social_name), linetype = 3) +
  
  # geom_point(data = a, aes(x = as.numeric(levels_ordered)+.1, y = mean_degree_per_sub_norm,
                           # group = social_name, colour = social_name), shape = 18) +
  geom_errorbar(data = df_a, aes(x = as.numeric(cue)+.1, y = mean_per_sub_norm_mean,
                             colour = cue, 
                              ymin = mean_per_sub_norm_mean-se, 
                              ymax = mean_per_sub_norm_mean+se), width = .05) +

  # legend stuff __________________________________________________________________________________
  expand_limits(x = 2.8) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  guides(fill=guide_legend(title="social cues"))+
  # scale_color_brewer(palette = "PiYG") +
  # scale_fill_brewer(palette = "PiYG") +
  scale_fill_manual(values =COLOR) +#c( "#4575B4", "#D73027"))+
  scale_color_manual(values = COLOR)+ #c( "#4575B4","#D73027"))+
  ggtitle(GGTITLE) +
  # coord_flip() + #vertical vs horizontal
  
  xlab("Stimulus intensity levels") +
  ylab("Degrees of expected ratings") +
  theme_bw() 

g


```

# cue effect onesample t
## 1) tidyverse - wide form
## 2) calculate high vs low cue "event02_expect_angle" "event04_actual_angle"
```{r}
# widen
IV = "param_cue_type"
DV = "event02_expect_angle"
DATA_EXPECT = meanSummary(DATA, c(SUBJECT, IV), DV)

WIDE_EXPECT = DATA_EXPECT %>% 
  select(subject, param_cue_type, mean_per_sub ) %>%
  spread( param_cue_type, mean_per_sub )


df_d = meanSummary(DATA, c(SUBJECT, IV), DV)
df_a = summarySEwithin(data=df_d, 
                  measurevar = "mean_per_sub", # variable created from above
                    withinvars = c(IV), # IV
                    idvar = "subject")
```


```{r}
WIDE_EXPECT$high_vs_low_cue = WIDE_EXPECT$high_cue - WIDE_EXPECT$low_cue
expect.effect.size = mean(WIDE_EXPECT$high_vs_low_cue)/sd(WIDE_EXPECT$high_vs_low_cue) # 2.61
EXPECT_CON_D = meanSummary(WIDE_EXPECT, c( IV), high_vs_low_cue)
EXPECT_CON_A = summarySEwithin(data=EXPECT_CON_D, 
                  measurevar = "mean_per_sub", # variable created from above
                   # withinvars = c(IV), # IV
                    idvar = "subject")
```

# barplot ver 1
```{r}

p1 <- ggplot(data = df_a, aes(x = param_cue_type, y = mean_per_sub_norm_mean, fill = param_cue_type)) +
  geom_bar(stat = "identity", width = .5) +
  geom_errorbar(data = df_a, aes(ymin = mean_per_sub_norm_mean-ci, ymax = mean_per_sub_norm_mean+ci, width = .05))+
  geom_point(data = df_d, aes(y = mean_per_sub, x = param_cue_type), alpha = 0.4, width = .1, 
             position = position_jitter(.1),
             size = 2) +
  guides(fill=FALSE) +
  ylab("score mean") +
  theme_cowplot()+
  ggtitle(GGTITLE)
p1
```

# barplot ver 2
```{r}
# WIDE_EXPECT %>% get_summary_stats(high_vs_low_cue, type = "mean_sd")
# res <- t.test(WIDE_EXPECT$high_vs_low_cue, mu = 0)
cue_onet.test <- lmer(high_vs_low_cue ~ 1, mu = 0)
cue_onet.test
# Printing the results
# res 
```

```{r}

p2 <- ggplot(data = df_a, aes(x = param_cue_type, y = mean_per_sub_norm_mean, fill = param_cue_type)) +
  geom_bar(stat = "identity", width = .5) +
  geom_errorbar(data = df_a, aes(ymin = mean_per_sub_norm_mean-ci, ymax = mean_per_sub_norm_mean+ci, width = .05))+
  geom_point(data = df_d, aes(y = mean_per_sub, x = param_cue_type), alpha = 0.4, width = .1, 
             position = position_jitter(.1),
             size = 2) +
  guides(fill=FALSE) +
  ylab("score mean") +
  theme_cowplot()+
  ggtitle(GGTITLE)
p2
```

```{r}
df_d = meanSummary(DATA, c(SUBJECT, IV), DV)
df_a = summarySEwithin(data=df_d, 
                  measurevar = "mean_per_sub", # variable created from above
                    withinvars = c(IV), # IV
                    idvar = "subject")

if(any(startsWith(DV_KEYWORD, c("expect", "Expect")))){COLOR = c( "#1B9E77", "#D95F02")}else{COLOR=c( "#4575B4", "#D73027")} # if keyword starts with
GGTITLE = paste(TASKNAME, " - Expectation Rating (degree)")
TITLE = paste(TASKNAME, " - Expect")
plot_expect_rainclouds(df_d, df_a, GGTITLE, TITLE, XLAB, YLAB, TASKNAME, 5, 3, DV_KEYWORD,COLOR)
```


# ----------------
# full factorial
# ----------------


```{r}

# parameters __________________________________________________________________
TASKNAME = 'cognitive'
SUBJECT_VARKEY = "src_subject_id"
IV1 = "param_cue_type"
IV2 = "param_stimulus_type"
DV = "event04_actual_angle"
DV_KEYWORD = "actual"
XLAB = ""; YLAB = "ratings (degree)"; 

GGTITLE = paste(TASKNAME, " - Actual Rating (degree)")
TITLE = paste(TASKNAME, " - Actual")
SUBJECT = "subject"
EXCLUDE = ""
if(any(startsWith(DV_KEYWORD, c("expect", "Expect")))){COLOR = c( "#1B9E77", "#D95F02")}else{COLOR=c(  "#D73027", "#4575B4")}
# 1. load data
ACTUAL_DATA = expect_df(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE )

# contrasts __________________________________________________________________

#contrast code 1 linear
ACTUAL_DATA$stim_con_linear[ACTUAL_DATA$event03_stimulus_type == "low_stim"] <- -0.5
ACTUAL_DATA$stim_con_linear[ACTUAL_DATA$event03_stimulus_type == "med_stim"] <- 0
ACTUAL_DATA$stim_con_linear[ACTUAL_DATA$event03_stimulus_type == "high_stim"] <- 0.5
# 
# # contrast code 2 quadratic
ACTUAL_DATA$stim_con_quad[ACTUAL_DATA$event03_stimulus_type == "low_stim"] <- -0.33
ACTUAL_DATA$stim_con_quad[ACTUAL_DATA$event03_stimulus_type == "med_stim"] <- 0.66
ACTUAL_DATA$stim_con_quad[ACTUAL_DATA$event03_stimulus_type == "high_stim"] <- -0.33

# social cude contrast
ACTUAL_DATA$social_cue[ACTUAL_DATA$param_cue_type == 'low_cue'] <- -0.5 # social influence task
ACTUAL_DATA$social_cue[ACTUAL_DATA$param_cue_type == 'high_cue'] <- 0.5 # no influence task

#ACTUAL_DATA$stim_factor = factor(ACTUAL_DATA$event03_stimulus_type)
#ACTUAL_DATA$cue_factor = factor(ACTUAL_DATA$param_cue_type)

# 2. lmer model __________________________________________________________________
#run_full_lmer(ACTUAL_DATA, TASKNAME, "social_cue","stim_con_linear","stim_con_quad" , DV, SUBJECT, DV_KEYWORD)
model.full= lmer(ACTUAL_DATA[,DV] ~ ACTUAL_DATA[,"social_cue"]*ACTUAL_DATA[,"stim_con_linear"] + ACTUAL_DATA[,"social_cue"]*ACTUAL_DATA[,"stim_con_quad"] +
       (ACTUAL_DATA[,"social_cue"]*ACTUAL_DATA[,"stim_con_linear"] + ACTUAL_DATA[,"social_cue"]*ACTUAL_DATA[,"stim_con_quad"]|ACTUAL_DATA[,SUBJECT]) )

print(summary(model.full))
model_filename = file.path(main_dir, 'analysis', 'semicircle_degree', 
                   paste('lmer_task-' ,TASKNAME, '_rating-', DV_KEYWORD,'_torsuggest.txt', sep = ""))
sink(model_filename)
print("--------------------------")
print(paste("model: ", str_to_title(DV_KEYWORD), " ratings - ", TASKNAME))
print(paste("IV: ", str_to_title(IV)))
print(paste("CONTRASTS",str_to_title("stim_con_linear"),str_to_title("stim_con_linear"))) 
print(paste("D V: ", str_to_title(DV) ))
print(paste("Random effects: ", str_to_title(SUBJECT)))
print("--------------------------")
print(summary(model.full))
sink()
# 3. summary table
#df_d = meanSummary(DATA, c(SUBJECT, IV1, IV2), DV)


# 4. re-label __________________________________________________________________

ACTUAL_DATA$stim[ACTUAL_DATA$param_stimulus_type == 'high_stim'] <- "high" # no influence task
ACTUAL_DATA$stim[ACTUAL_DATA$param_stimulus_type == 'med_stim'] <- "med" # no influence task
ACTUAL_DATA$stim[ACTUAL_DATA$param_stimulus_type == 'low_stim'] <- "low" # no influence task

ACTUAL_DATA$cue[ACTUAL_DATA$event01_cue_type == "high_cue"] <- "high" 
ACTUAL_DATA$cue[ACTUAL_DATA$event01_cue_type == "low_cue"] <- "low" # no influence task


ACTUAL_DATA$stim <- factor(ACTUAL_DATA$stim, levels=c("low", "med", "high"))
ACTUAL_DATA$cue <- factor(ACTUAL_DATA$cue, levels=c("high", "low"))
df_d = meanSummary(ACTUAL_DATA, c(SUBJECT, "stim", "cue"), DV)
df_a = summarySEwithin(data=df_d,
                  measurevar = "mean_per_sub", # variable created from above
                    withinvars = c( "stim", "cue"), # IV
                    idvar = "subject")
df_a$stim <- factor(df_a$stim, levels=c("low", "med", "high"))
df_a$cue <- factor(df_a$cue, levels=c("high", "low"))
# 4. raincloud plot _______________________________________________________
# 
  #within subjet line
  #geom_line(data = df_d, aes(group = subject, y = mean_per_sub, x = as.numeric(stim)-.15, fill = cue), linetype = 3, color = "grey") +
  # between subject line
k <- ggplot(data = df_d, aes(y = mean_per_sub, x = stim, fill = cue)) +
  geom_flat_violin(aes(fill = cue), position = position_nudge(x = .1, y = 0), adjust = 1.5,
                   trim = FALSE, alpha = .7, colour = NA) +
  geom_line(data = df_a, aes(x = as.numeric(stim)+.1, y = mean_per_sub_norm_mean, group = cue, colour = cue),  linetype = 2) +
  geom_point(aes(x = as.numeric(stim)-.15, y = mean_per_sub, color = cue),
             position = position_jitter(width = .05), size = 1, alpha = 0.8, shape = 20) +
  geom_boxplot(aes(x = stim, y = mean_per_sub, fill = cue),width = .1,
               outlier.shape = NA, alpha = 0.8, width = .1, colour = "black") +
  # use summary stats __________________________________________________________________________________
  geom_errorbar(data = df_a, aes(x = as.numeric(stim)+.1, y = mean_per_sub_norm_mean,
                              group = cue, colour = cue, 
                              ymin = mean_per_sub_norm_mean-se, 
                              ymax = mean_per_sub_norm_mean+se), width = .05) +
  # legend stuff __________________________________________________________________________________
  expand_limits(x = 3.25) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  guides(fill=guide_legend(title="social cues"))+
  scale_fill_manual(values = COLOR)+
  scale_color_manual(values = COLOR)+
  ggtitle(GGTITLE) +
  xlab("Stimulus intensity levels") +
  ylab("Degrees of actual ratings") +
  theme_bw() 
k


#__________________________________________________________________________________
# plot ver 2 - contrasts
#__________________________________________________________________________________
WIDE_EXPECT = meanSummary(ACTUAL_DATA, c(SUBJECT, IV1, IV2), DV)

WIDE_EXPECT_D = WIDE_EXPECT %>%
  select(subject, param_cue_type,param_stimulus_type, mean_per_sub ) %>%
  spread( c(param_cue_type), mean_per_sub )

WIDE_EXPECT_D$high_vs_low_cue = WIDE_EXPECT_D$high_cue - WIDE_EXPECT_D$low_cue

WIDE_EXPECT_A = summarySEwithin(data=WIDE_EXPECT_D,
                measurevar = "high_vs_low_cue", # variable created from above
                 withinvars = c("param_stimulus_type"), # IV
                   idvar = "subject")

WIDE_EXPECT_D$param_stimulus_type <- factor(WIDE_EXPECT_D$param_stimulus_type, levels=c("low_stim", "med_stim", "high_stim"))
WIDE_EXPECT_A$param_stimulus_type <- factor(WIDE_EXPECT_A$param_stimulus_type, levels=c("low_stim", "med_stim", "high_stim"))

expect.effect.size = mean(WIDE_EXPECT$high_vs_low_cue)/sd(WIDE_EXPECT$high_vs_low_cue) # 2.61


p2 <- ggplot(data = WIDE_EXPECT_A, aes(x = param_stimulus_type,y = high_vs_low_cue_mean, fill =param_stimulus_type )) +
  geom_bar(stat = "identity", width = .5) +
  geom_errorbar(data = WIDE_EXPECT_A, aes(ymin = high_vs_low_cue_mean-ci, ymax = high_vs_low_cue_mean+ci, width = .05))+
  geom_point(data = WIDE_EXPECT_D, aes(y = high_vs_low_cue), alpha = 0.4, width = .1,
             position = position_jitter(.1),
             size = 2) +
  guides(fill=FALSE) +
  ylab("semi-circle rating (High > low cue)") +
  theme_cowplot()+
  ggtitle(GGTITLE)
p2
```


