---
title: "socialinfluence_dartmouth_CBB"
author: "Heejung Jung"
date: "4/5/2021"
output: html_document
---


# load libraries
```{r}
library(psych)
library(car)
library(lmSupport)
library(lme4)
library(lmerTest)
library(plyr)
#library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
#library(Hmisc)
#library(Rmisc)
library(png)
library(knitr)
library(TMB)
library(sjPlot)
library(ggpubr)
library(gridExtra)
library(merTools)
library(sjstats) #to get ICC
library(broom)
library(tidyverse)
library(GGally)
library(RCurl)
library(rstanarm)
library(reshape)
library(boot)
library(afex)
library(cowplot)
library(readr)
library(lavaan)
library(rmarkdown)
library(readr)
library(caTools)
library(bitops)
library(stringr)
## library(extraoperators)
##library(JWileymisc)
##library(multilevelTools)
library(ggpubr)
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")
library(r2mlm)
```

# parameters

```{r}
main_dir = dirname(dirname(getwd()))
```
# 0. _____________________________________ function _____________________________________

## a) summary table
http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)/#Helper%20functions

### FUNCTION normdatawithin
```{r}
normDataWithin <- function(data=NULL, idvar, measurevar, betweenvars=NULL,
                           na.rm=FALSE, .drop=TRUE) {
  ## Norms the data within specified groups in a data frame; it normalizes each
## subject (identified by idvar) so that they have the same mean, within each group
## specified by betweenvars.
##   data: a data frame.
##   idvar: the name of a column that identifies each subject (or matched subjects)
##   measurevar: the name of a column that contains the variable to be summariezed
##   betweenvars: a vector containing names of columns that are between-subjects variables
##   na.rm: a boolean that indicates whether to ignore NA's
    library(plyr)

    # Measure var on left, idvar + between vars on right of formula.
    data.subjMean <- ddply(data, c(idvar, betweenvars), .drop=.drop,
     .fun = function(xx, col, na.rm) {
        c(subjMean = mean(xx[,col], na.rm=na.rm))
      },
      measurevar,
      na.rm
    )

    # Put the subject means with original data
    data <- merge(data, data.subjMean)

    # Get the normalized data in a new column
    measureNormedVar <- paste(measurevar, "_norm", sep="")
    data[,measureNormedVar] <- data[,measurevar] - data[,"subjMean"] +
                               mean(data[,measurevar], na.rm=na.rm)

    # Remove this subject mean column
    data$subjMean <- NULL

    return(data)
}
```

### FUNCTION: summarySEwithin
```{r}
summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=NULL,
                            idvar=NULL, na.rm=FALSE, conf.interval=.95, .drop=TRUE) {

  ## Summarizes data, handling within-subjects variables by removing inter-subject variability.
## It will still work if there are no within-S variables.
## Gives count, un-normed mean, normed mean (with same between-group mean),
##   standard deviation, standard error of the mean, and confidence interval.
## If there are within-subject variables, calculate adjusted values using method from Morey (2008).
##   data: a data frame.
##   measurevar: the name of a column that contains the variable to be summariezed
##   betweenvars: a vector containing names of columns that are between-subjects variables
##   withinvars: a vector containing names of columns that are within-subjects variables
##   idvar: the name of a column that identifies each subject (or matched subjects)
##   na.rm: a boolean that indicates whether to ignore NA's
##   conf.interval: the percent range of the confidence interval (default is 95%)
  # Ensure that the betweenvars and withinvars are factors
  factorvars <- vapply(data[, c(betweenvars, withinvars), drop=FALSE],
    FUN=is.factor, FUN.VALUE=logical(1))

  if (!all(factorvars)) {
    nonfactorvars <- names(factorvars)[!factorvars]
    message("Automatically converting the following non-factors to factors: ",
            paste(nonfactorvars, collapse = ", "))
    data[nonfactorvars] <- lapply(data[nonfactorvars], factor)
  }

  # Get the means from the un-normed data
  datac <- summarySE(data, measurevar, groupvars=c(betweenvars, withinvars),
                     na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Drop all the unused columns (these will be calculated with normed data)
  datac$sd <- NULL
  datac$se <- NULL
  datac$ci <- NULL

  # Norm each subject's data
  ndata <- normDataWithin(data, idvar, measurevar, betweenvars, na.rm, .drop=.drop)

  # This is the name of the new column
  measurevar_n <- paste(measurevar, "_norm", sep="")

  # Collapse the normed data - now we can treat between and within vars the same
  ndatac <- summarySE(ndata, measurevar_n, groupvars=c(betweenvars, withinvars),
                      na.rm=na.rm, conf.interval=conf.interval, .drop=.drop)

  # Apply correction from Morey (2008) to the standard error and confidence interval
  #  Get the product of the number of conditions of within-S variables
  nWithinGroups    <- prod(vapply(ndatac[,withinvars, drop=FALSE], FUN=nlevels,
                           FUN.VALUE=numeric(1)))
  correctionFactor <- sqrt( nWithinGroups / (nWithinGroups-1) )

  # Apply the correction factor
  ndatac$sd <- ndatac$sd * correctionFactor
  ndatac$se <- ndatac$se * correctionFactor
  ndatac$ci <- ndatac$ci * correctionFactor

  # Combine the un-normed means with the normed results
  df = merge(datac, ndatac)
  return(df)
  
}
```

### FUNCTION: meanSummary
```{r}
meanSummary <- function(DATA, GROUP, DV){
  z <- ddply(DATA, GROUP, .fun = function(xx){
                         c(mean_per_sub = mean(xx[,DV],na.rm=TRUE),
                         sd = sd(xx[,DV],na.rm=TRUE) ) })
  return(z)
  }
```


### FUNCTION: expect_df load data
```{r}
expect_df = function(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE ) {
  # INPUT:
  # * TASKNAME (e.g. pain, cognitive, vicarious)
  # * SUBJECT_VARKEY (e.g. src_subject_id or subject)
  # A. load data ______________________________________________________________
  FILENAME = paste('*_task-social_*-' ,TASKNAME, '_beh.csv', sep = "")
  common_path = Sys.glob(file.path(main_dir,'data', 'dartmouth', 'd02_preprocessed',
                                   'sub-*','ses-*',FILENAME))
  filter_path = common_path[!str_detect(common_path,pattern="sub-0001|sub-0003|sub-0004|sub-0005|sub-0025|sub-0999")]
  
  DF <- do.call("rbind",lapply(filter_path,FUN=function(files){ read.csv(files)}))
  is.nan.data.frame <- function(x)
    do.call(cbind, lapply(x, is.nan))
  DF[is.nan(DF)] <- NA
  # subjects as factor
  #print("subject")
  DF[,"subject"] = factor(DF[,SUBJECT_VARKEY])
  # print("line323")
  # B. plot expect rating NA ___________________________________________________
  DF_expect_NA = aggregate(DF[,DV], list(DF$subject),function(x) sum(is.na(x)))
  #TITLE = paste(TASKNAME, " task - Expectation ratings", sep = "" )
  # ggplot(DF_expect_NA, aes(x = Group.1, y = x))+ 
  #   geom_bar(stat = "identity", position = "identity") +
  #   xlab("subject ID") + 
  #   ylab("freq. of NA") + 
  #   ggtitle(TITLE) +
  #   theme_bw()
  #print(213)
  # C. run model ___________________________________________________
  
  DF_remove_NA = DF[!is.na(  DF[DV]  ),]
  #return(DF_remove_NA)
  #print(218)
  # cog_dataset[!is.na(cog_dataset["event02_expect_angle"]),]
    # c1. contrastcode
  # stimulus intensity
  # DF_remove_NA$stim[DF_remove_NA$event03_stimulus_type == "low_stim"] <- -0.5 # social influence task
  # DF_remove_NA$stim[DF_remove_NA$event03_stimulus_type == "med_stim"] <- 0 # no influence task
  # DF_remove_NA$stim[DF_remove_NA$event03_stimulus_type == "high_stim"] <- 0.5 # no influence task
  # 
  # DF_remove_NA$stim_factor = factor(DF_remove_NA$event03_stimulus_type)
  # 
  # #contrast code 1 linear
  # DF_remove_NA$stim_con_linear[DF_remove_NA$event03_stimulus_type == "low_stim"] <- -0.5
  # DF_remove_NA$stim_con_linear[DF_remove_NA$event03_stimulus_type == "med_stim"] <- 0
  # DF_remove_NA$stim_con_linear[DF_remove_NA$event03_stimulus_type == "high_stim"] <- 0.5
  # 
  # # contrast code 2 quadratic
  # DF_remove_NA$stim_con_quad[DF_remove_NA$event03_stimulus_type == "low_stim"] <- -0.33
  # DF_remove_NA$stim_con_quad[DF_remove_NA$event03_stimulus_type == "med_stim"] <- 0.66
  # DF_remove_NA$stim_con_quad[DF_remove_NA$event03_stimulus_type == "high_stim"] <- -0.33
  # 
  # # social cude contrast
  # DF_remove_NA$social_cue[DF_remove_NA[,IV] == 'low_cue'] <- -0.5 # social influence task
  # DF_remove_NA$social_cue[DF_remove_NA[,IV] == 'high_cue'] <- 0.5 # no influence task
  # DF_remove_NA$cue_factor = factor(DF_remove_NA[,IV])
  DATA <<- as.data.frame(DF_remove_NA)
}
```

### FUNCTION: run_cue_lmer 
```{r}
run_cue_lmer = function(DATA,TASKNAME, IV, DV, SUBJECT, DV_KEYWORD, MODEL_SAVE){
  model.cue = lmer( DATA[,DV] ~ DATA[,IV] + (DATA[,IV] | DATA[,SUBJECT]) + (DATA[,IV] | DATA$session_id))
  print(paste("model: ", str_to_title(DV_KEYWORD), " ratings - ", TASKNAME))
  print(summary(model.cue))
  sink(MODEL_SAVE)
  print(summary(model.cue))
  sink()
  cooksd <- cooks.distance(model.cue)
  return(cooksd)
  }
```



### FUNCTION: run_cue_stim_lmer
```{r}
run_cue_stim_lmer = function(DATA,TASKNAME, IV, STIMC1,STIMC2, DV, SUBJECT, DV_KEYWORD, SAVE_FNAME){
  model.full = lmer( DATA[,DV] ~ DATA[,IV]*DATA[,STIMC1] + DATA[,IV]*DATA[,STIMC2] + 
                    (DATA[,IV]*DATA[,STIMC1] + DATA[,IV]*DATA[,STIMC2] | DATA[,SUBJECT])) 
                    # + 
                    # (DATA[,IV]*DATA[,STIMC1] + DATA[,IV]*DATA[,STIMC2] | DATA$session_id))
  sink(SAVE_FNAME)
  print(paste("model: ", str_to_title(DV_KEYWORD), " ratings - ", TASKNAME))
  print(summary(model.full))
  sink()
  print(summary(model.full))
  fixEffect <<- as.data.frame(fixef(model.full))
  randEffect <<-as.data.frame(ranef(model.full))
  cooksd <- cooks.distance(model.full)
  return(cooksd)
  #View(as.data.frame(fixEffect))
  #View(as.data.frame(randEffect$src_subject_id))
  # A <<- coef(model.full)$src_subject_id
  # B <<- coef(summary(model.full))[ , "Estimate"]
  # return(list(A, B))
  # model_filename = file.path(main_dir, 'analysis', 'semicircle_degree', 
  #                            paste('lmer_task-' ,TASKNAME, '_rating-', DV_KEYWORD,'.txt', sep = ""))

  }
```

## b) plot
### b-1) plot cue effect
```{r}
FIX_plot_expect_rainclouds = function(within_average, group_level_condition_average,  
                                      GGTITLE, TITLE, XLAB, YLAB, IV, task_name, w, h, COLOR) {

g <- ggplot(data = within_average, aes(y = mean_per_sub, x = within_average[,IV], fill = within_average[,IV])) +
  geom_flat_violin(aes(fill = IV), position = position_nudge(x = .1, y = 0), adjust = 1.5,
                   trim = FALSE, alpha = .5, colour = NA) +
  geom_line(data = within_average, aes(group = subject, y = mean_per_sub, x = as.numeric(within_average[,IV])-.15, fill = within_average[,IV]), linetype = "solid", color = "grey", alpha = .3) +
  geom_point(aes(x = as.numeric(within_average[,IV])-.15, y = mean_per_sub, color = within_average[,IV]),
             position = position_jitter(width = .05), size = 1, alpha = 0.8, shape = 20) +
  geom_boxplot(aes(x = within_average[,IV], y = mean_per_sub, fill = within_average[,IV]),width = .1,
               outlier.shape = NA, alpha = 0.8, width = .1, colour = "black") +
  geom_errorbar(data = group_level_condition_average, aes(x = as.numeric(group_level_condition_average[,IV])+.1, y = mean_per_sub_norm_mean,
                             colour = group_level_condition_average[,IV], 
                              ymin = mean_per_sub_norm_mean-se, 
                              ymax = mean_per_sub_norm_mean+se), width = .05) +

  # legend stuff __________________________________________________________________________________
  expand_limits(x = 2.8) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  guides(fill=guide_legend(title=TITLE))+
  scale_fill_manual(values = COLOR)+
  scale_color_manual(values = COLOR)+

  ggtitle(GGTITLE) +
  # coord_flip() + #vertical vs horizontal
  xlab(XLAB) +
  ylab(YLAB) +
  theme_bw() 
# plot_filename = file.path(main_dir, 'analysis', paste('paingenbias_task-' ,task_name, '_onlyresponse.png', sep = ""))
# ggsave(plot_filename, width = w, height = h)
g

}
```


### FUNCTION: plot_expect_rainclouds
```{r}
# data within_average
# DV = mean_per_sub
# IV = param_cue_type
plot_expect_rainclouds = function(within_average, group_level_condition_average, 
                                  fill_IV, SUB_MEAN, GROUP_MEAN, SE, SUBJECT,
                                  GGTITLE, TITLE, XLAB, YLAB,task_name, w, h, DV_KEYWORD,COLOR, SAVE_FNAME) {
g <- ggplot(data = within_average, 
            aes(y = .data[[SUB_MEAN]], x = factor(.data[[fill_IV]]), fill =  factor(.data[[fill_IV]]))) +
  coord_cartesian(ylim = c(-10,120), expand = TRUE) +
  geom_flat_violin(aes(fill =  factor(.data[[fill_IV]])), position = position_nudge(x = .1, y = 0), 
                   adjust = 1.5, trim = FALSE, alpha = .3, colour = NA) +
  geom_line(data = within_average,
           aes(group = .data[[SUBJECT]], y = .data[[SUB_MEAN]], x = as.numeric( .data[[fill_IV]] )-.15, 
               fill =  factor(.data[[fill_IV]])), linetype = "solid", color = "grey", alpha = .3) +
  geom_point(aes(x = as.numeric( .data[[fill_IV]])-.15, y = .data[[SUB_MEAN]], color = factor(.data[[fill_IV]])),
             position = position_jitter(width = .05), size = 1, alpha = 0.8, shape = 20) +
  geom_boxplot(aes(x =  .data[[fill_IV]], y = .data[[SUB_MEAN]], fill =  .data[[fill_IV]]), width = .1,
               outlier.shape = NA, alpha = 0.8, width = .1, colour = "black") +
  geom_errorbar(data = group_level_condition_average, 
                aes(x = as.numeric( .data[[fill_IV]])+.1, y = as.numeric(.data[[GROUP_MEAN]]), 
                   colour =  factor(.data[[fill_IV]]), 
                   ymin =  .data[[GROUP_MEAN]] - .data[[SE]], 
                   ymax =  .data[[GROUP_MEAN]] + .data[[SE]]), width = .05) +

  # legend stuff __________________________________________________________________________________
  expand_limits(x = 2.8) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  guides(fill=guide_legend(title=TITLE))+
  scale_fill_manual(values = COLOR)+
  scale_color_manual(values = COLOR)+
  ggtitle(GGTITLE) +
  # coord_flip() + #vertical vs horizontal
  xlab(XLAB) +
  ylab(YLAB) +
  theme_bw() 
# \n
return(g)

}
```

### FUNCTION: plot_actual_rainclouds
```{r}
plot_actual_rainclouds = function(subjectwise, groupwise, 
                                  IV1, IV2, SUB_MEAN, GROUP_MEAN, SE, SUBJECT, GGTITLE, TITLE, XLAB,YLAB,task_name, w, h, DV_KEYWORD,COLOR,SAVE_FNAME) {

g <- ggplot(data = subjectwise, aes(y = .data[[SUB_MEAN]], x = .data[[IV1]], fill = .data[[IV2]])) +
  geom_flat_violin(aes(fill = .data[[IV2]]), position = position_nudge(x = .1, y = 0), adjust = 1.5,
                   trim = FALSE, alpha = .3, colour = NA) +
  geom_line(data = subjectwise, aes(group = .data[[SUBJECT]], y = .data[[SUB_MEAN]], x = as.numeric(.data[[IV1]])-.15, fill = .data[[IV2]]), linetype = 3, color = "grey") +
  #geom_point(aes(group = subject, x = as.numeric(IV1)-.15, y = mean_per_sub, color = IV2),
 #            position = position_jitter(width = .05), size = 1, alpha = 0.8, shape = 20) +
  geom_point(data = subjectwise, aes(x = as.numeric(.data[[IV1]])-.15, 
                                     y = .data[[SUB_MEAN]], color =.data[[IV2]]),
             position = position_jitter(width = .05), size = 1, alpha = 0.8, shape = 20) +
  geom_boxplot(data = subjectwise, aes(x = .data[[IV1]], y = .data[[SUB_MEAN]], fill = .data[[IV2]]),width = .1,
               outlier.shape = NA, alpha = 0.8, width = .1, colour = "black") +

  # use summary stats __________________________________________________________________________________

  geom_errorbar(data = groupwise, aes(x = as.numeric(.data[[IV1]])+.1, y = .data[[GROUP_MEAN]],
                              group = .data[[IV2]], colour = .data[[IV2]], 
                              ymin = .data[[GROUP_MEAN]] - .data[[SE]], 
                              ymax = .data[[GROUP_MEAN]] + .data[[SE]]), width = .05) +

  # legend stuff __________________________________________________________________________________
  expand_limits(x = 3.25) +
  guides(fill = FALSE) +
  guides(color = FALSE) +
  guides(fill=guide_legend(title="social cues"))+
  #scale_color_brewer(palette = "Dark2") +
  #scale_fill_brewer(palette = "Dark2") +
  scale_fill_manual(values = COLOR)+
  scale_color_manual(values = COLOR)+
  ggtitle(GGTITLE) +
  # coord_flip() + #vertical vs horizontal
  xlab("Stimulus intensity levels") +
  ylab("Degrees of actual ratings") +
  theme_bw() 

g
#w = 5
#h = 3

ggsave(SAVE_FNAME, width = w, height = h)

}
```

combined expect_df / run_cue_lmer / meanSummary / plot_expect_rainclouds
```{r}
load_and_plot = function(TASKNAME, SUBJECT_VARKEY, IV, DV,DV_KEYWORD, XLAB,YLAB,GGTITLE, TITLE,SUBJECT,EXCLUDE ) {
  # load data
  DATA = expect_df(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE )
  # run model
  RESULTS = run_cue_lmer(DATA,TASKNAME, IV, DV, SUBJECT, SAVE_FNAME)
  # summarize for plots
  df_d = meanSummary(DATA, c(SUBJECT, IV), DV)
  df_a = summarySEwithin(data=df_d, 
                    measurevar = "mean_per_sub", # variable created from above
                    withinvars = c(IV), # IV
                    idvar = "subject")
  # set color
  if(any(startsWith(DV_KEYWORD, c("expect", "Expect")))){COLOR = c( "#1B9E77", "#D95F02")}else{COLOR=c( "#4575B4", "#D73027")} # if keyword starts with True, color it with orange and green, else, stick with red and blue
  # plot
  GGTITLE = paste(TASKNAME, " - Expectation Rating (degree)")
  TITLE = paste(TASKNAME, " - Expect")
  plot_expect_rainclouds(df_d, df_a, GGTITLE, TITLE, XLAB, YLAB, TASKNAME, 5, 3, DV_KEYWORD,COLOR)
  
  

}
```

## rain cloud theme
```{r}
raincloud_theme = theme(
text = element_text(size = 10),
axis.title.x = element_text(size = 16),
axis.title.y = element_text(size = 16),
axis.text = element_text(size = 14),
axis.text.x = element_text(angle = 45, vjust = 0.5),
legend.title=element_text(size=16),
legend.text=element_text(size=16),
legend.position = "right",
plot.title = element_text(lineheight=.8, face="bold", size = 16),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))
w = 5
h = 3
```



### b-2) plot full factorial


# _____________________________________ 1. expectation rating _____________________________________


```{r 1-1. plot expectation ratings for PVC task }
# parameters
# TASKNAME = 'cognitive'
SUBJECT_VARKEY = "src_subject_id"
IV = "param_cue_type"
DV = "event02_expect_angle"
DV_KEYWORD = "expect"
XLAB = ""; YLAB = "ratings (degree)"; 

GGTITLE = paste(TASKNAME, " - Expectation Rating (degree)")
TITLE = paste(TASKNAME, " - Expect")
SUBJECT = "subject"
EXCLUDE = ""

analysis_dir =file.path(main_dir,'analysis', 'mixedeffect', 'model01_cue_expectrating_02-2022')

for (TASKNAME in c("pain", "vicarious", "cognitive")){

SAVE_FNAME = file.path(analysis_dir, paste('lmer_task-', TASKNAME, '_rating-',DV_KEYWORD,'_', as.character(Sys.Date()),'.txt',sep = ''))
DATA = expect_df(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE )
cooksd = run_cue_lmer(DATA,TASKNAME, IV, DV, SUBJECT, DV_KEYWORD, SAVE_FNAME)
influential <- as.numeric(names(cooksd)[(cooksd > (4/as.numeric(length(unique(DATA$src_subject_id))))    )])
DATA_screen <- DATA[-influential, ]

subjectwise = meanSummary(DATA, c(SUBJECT, IV), DV)
groupwise = summarySEwithin(data=subjectwise, 
                  measurevar = "mean_per_sub", # variable created from above
                    withinvars = c(IV), # IV
                    idvar = "subject")

SUB_MEAN = "mean_per_sub"; GROUP_MEAN = "mean_per_sub_norm_mean"; SE = "se"; SUBJECT = "subject"
GGTITLE = paste(TASKNAME, " - Expectation Rating (degree)"); TITLE = paste(TASKNAME, " - Expect")
XLAB = ""; YLAB = "ratings (degree)"; DV_KEYWORD = "expect"
if(any(startsWith(DV_KEYWORD, c("expect", "Expect")))){COLOR = c( "#1B9E77", "#D95F02")}else{COLOR=c( "#4575B4", "#D73027")} # if keyword starts with
#SAVE_FNAME = file.path(analysis_dir, paste('raincloudplot_task-', TASKNAME,'_rating-',DV_KEYWORD,'.png',sep = ''))

SAVE_FNAME = file.path(main_dir, 'analysis','mixedeffect', 'model01_cue_expectrating_02-2022', paste('raincloudpoint_task-' ,TASKNAME, '_rating-', DV_KEYWORD,'_', as.character(Sys.Date()),'.png', sep = ""))
plot_expect_rainclouds(subjectwise, groupwise, 
                                  IV, SUB_MEAN, GROUP_MEAN, SE, SUBJECT,
                                  GGTITLE, TITLE, XLAB, YLAB,task_name, w, h, DV_KEYWORD,COLOR, SAVE_FNAME) 
#plot_expect_rainclouds(df_d, df_a, GGTITLE, TITLE, XLAB, YLAB, TASKNAME, 5, 3, DV_KEYWORD,COLOR)
}
```



## 1-3. pain

# FULL CODE
```{r}
TASKNAME = 'pain'
```

A. load data
```{r}
FILENAME = paste('*_task-social_*-' ,TASKNAME, '_beh.csv', sep = "")
common_path = Sys.glob(file.path(main_dir,'data', 'dartmouth', 'd02_preprocessed', 'sub-*','ses-*',FILENAME))
filter_path = common_path[!str_detect(common_path,pattern="sub-0001|sub-0003|sub-0004|sub-0005|sub-0025")]

DF <- do.call("rbind",lapply(filter_path,FUN=function(files){ read.csv(files)}))
is.nan.data.frame <- function(x)
  do.call(cbind, lapply(x, is.nan))
DF[is.nan(DF)] <- NA
DF = as.data.frame(DF)
# subjects as factor
DF$subject = factor(DF$src_subject_id)
```

B. plot expect rating NA
```{r}
# DF_countNA = subset(cog_dataset, cog_dataset$event02_expect_RT == "NaN") #| cog_dataset$expect_r < 150)
DF_expect_NA = aggregate(DF$event02_expect_RT, list(DF$subject),function(x) sum(is.na(x)))
TITLE = paste(TASKNAME, " task - Expectation ratings", sep = "" )
ggplot(DF_expect_NA, aes(x = Group.1, y = x))+ 
  geom_bar(stat = "identity", position = "identity") +
  xlab("subject ID") + 
  ylab("freq. of NA") + 
  ggtitle(TITLE) +
  theme_bw() 
```

C. run model
1) contrastcode
```{r}
# stimulus intensity
DF$stim[DF$event03_stimulus_type == "low_stim"] <- -0.5 # social influence task
DF$stim[DF$event03_stimulus_type == "med_stim"] <- 0 # no influence task
DF$stim[DF$event03_stimulus_type == "high_stim"] <- 0.5 # no influence task

DF$stim_factor = factor(DF$event03_stimulus_type)

#contrast code 1 linear
DF$stim_con_linear[DF$event03_stimulus_type == "low_stim"] <- -0.5
DF$stim_con_linear[DF$event03_stimulus_type == "med_stim"] <- 0
DF$stim_con_linear[DF$event03_stimulus_type == "high_stim"] <- 0.5

# contrast code 2 quadratic
DF$stim_con_quad[DF$event03_stimulus_type == "low_stim"] <- -0.33
DF$stim_con_quad[DF$event03_stimulus_type == "med_stim"] <- 0.66
DF$stim_con_quad[DF$event03_stimulus_type == "high_stim"] <- -0.33

# social cude contrast
DF$social_cue[DF$param_cue_type == 'low_cue'] <- -0.5 # social influence task
DF$social_cue[DF$param_cue_type == 'high_cue'] <- 0.5 # no influence task
DF$cue_factor = factor(DF$param_cue_type)
```
2) lmer model 
```{r}
model.DF_expect = lmer(event02_expect_angle ~ param_cue_type + (param_cue_type | subject), data=DF)
summary(model.DF_expect)
```

D. Plot
1) summarize data
```{r}
# IV = "param_cue_type"
# DV = "event02_expect_angle"
# SUBJECT = "subject"
# 
# meanSummary <- function(DF, GROUP, DV){
# z <- ddply(DF, GROUP, .fun = function(xx){
#                          c(mean_per_sub = mean(xx[,DV],na.rm=TRUE),
#                          sd = sd(xx[,DV],na.rm=TRUE) ) })
# return(z)
# }
# df_d = meanSummary(DF, c(SUBJECT, "param_cue_type"), DV)
# 
# 
# myFunction2 <- function(x, y, col){
# z <- ddply(x, y, .fun = function(xx){
#                          c(mean = mean(xx[,col],na.rm=TRUE),
#                          max = max(xx[,col],na.rm=TRUE) ) })
# return(z)
# }
# 
# df_a = summarySEwithin(data=df_d, 
#                     measurevar = "mean_dev_per_sub", # variable created from above
#                     withinvars = c(IV), # IV
#                     idvar = "subject")
```


# 1-RT caltulate RT
#### Cognitive RT data
```{r}
cog_dataset$expect_RT = cog_dataset$event02_expect_responseonset - cog_dataset$event02_expect_displayonset
cog_dataset$actual_RT = cog_dataset$event04_actual_responseonset - cog_dataset$event04_actual_displayonset

```

# ____________________________ 2. actual judgment ____________________________
# ____________________________ 2-1. cue effect ____________________________
```{r 2-1 cue effect on actual judgment}
# parameters
# TASKNAME = 'cognitive'
SUBJECT_VARKEY = "src_subject_id"
IV = "param_cue_type"
DV = "event04_actual_angle"
DV_KEYWORD = "actual"
XLAB = ""; YLAB = "judgment (degree)"; 

GGTITLE = paste(TASKNAME, " - actual judgment (degree)")
TITLE = paste(TASKNAME, " - actual")
SUBJECT = "subject"
EXCLUDE = ""


analysis_dir = file.path(main_dir,'analysis', 'mixedeffect', 'model01_cue_expectrating_02-2022')

w = 10; h = 6

# [ CONTRASTS ]  ----------------------------------------------------------------------------
# DATA = cue_stim_contrast(DATA)
# STIMC1 = "stim_con_linear"
# STIMC2 = "stim_con_quad"

for (TASKNAME in c("pain", "vicarious", "cognitive")){

# [ MODEL ] ----------------------------------------------------------------------------
MODEL_FNAME = file.path(analysis_dir, paste('lmer_task-', TASKNAME, '_cue_on_rating-',DV_KEYWORD,'_', as.character(Sys.Date()),'.txt',sep = ''))
DATA = expect_df(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE )
unique(DATA$src_subject_id)
run_cue_lmer(DATA,TASKNAME, IV, DV, SUBJECT, DV_KEYWORD, MODEL_FNAME)
subjectwise = meanSummary(DATA, c(SUBJECT, IV), DV)
groupwise = summarySEwithin(data=subjectwise, 
                  measurevar = "mean_per_sub", # variable created from above
                    withinvars = c(IV), # IV
                    idvar = "subject")

if(any(startsWith(DV_KEYWORD, c("expect", "Expect")))){COLOR = c( "#1B9E77", "#D95F02")}else{COLOR=c( "#4575B4", "#D73027")} # if keyword starts with
GGTITLE = paste(TASKNAME, " - actual judgment (degree)")
TITLE = paste(TASKNAME, " - actual")
SUB_MEAN = "mean_per_sub"; GROUP_MEAN = "mean_per_sub_norm_mean"; SE = "se"; SUBJECT = "subject";
SAVE_FNAME = file.path(main_dir, 'analysis','mixedeffect', 'model01_cue_expectrating_02-2022', paste('raincloudpoint_task-' ,TASKNAME, '_rating-', DV_KEYWORD,'_', as.character(Sys.Date()),'.png', sep = ""))
plot_expect_rainclouds(subjectwise, groupwise,IV, SUB_MEAN, GROUP_MEAN, SE, SUBJECT,GGTITLE, TITLE, XLAB, YLAB,TASKNAME, w, h, DV_KEYWORD,COLOR, SAVE_FNAME)
}
```

# CUE EFFECT effect on actual -- difference contrast -- stim low med high

```{r 2-1 cue effect on actual judgment - difference}
combined_se_calc_cooksd =  data.frame()

analysis_dir = file.path(main_dir,'analysis', 'mixedeffect', 'model05_cue_actualrating_contrast')
dir.create(analysis_dir, showWarnings = FALSE)

# ------------------------------- B. task for loop ------------------------------- 
for (TASKNAME in c("pain", "vicarious", "cognitive")){
  
  # ------------------------------- A. parameters ------------------------------- 
SUBJECT_VARKEY = "src_subject_id"; IV = "param_stimulus_type"
DV = "event04_actual_angle"; 
DV_KEYWORD = "actual"
XLAB = ""; YLAB = "judgment (degree)"; 
GGTITLE = paste(TASKNAME, " - actual judgment (degree)")
TITLE = paste(TASKNAME, " - actual")
SUBJECT = "subject"
EXCLUDE = ""
w = 500; h = 300
  MODEL_FNAME = file.path(analysis_dir, paste('lmer_task-', TASKNAME, '_cue_on_rating-',DV_KEYWORD,'_',
                                              as.character(Sys.Date()),'_cooksd.txt',sep = ''))
# ___ 1) load data
  DATA = expect_df(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE )
  unique(DATA$src_subject_id)
  DATA$subject = factor(DATA$src_subject_id)
  MODELIV1 = "stim_ordered";MODELIV2 = "cue_ordered"

# ___ 2) mixed effects model
  run_cue_lmer(DATA,TASKNAME, IV, DV, SUBJECT, DV_KEYWORD, MODEL_FNAME)
  cooksd = run_cue_stim_lmer(DATA,TASKNAME, IV1, STIMC1,STIMC2, DV, SUBJECT, DV_KEYWORD, MODEL_FNAME)
influential <- as.numeric(names(cooksd)[(cooksd > (4/as.numeric(length(unique(DATA$src_subject_id))))    )])
DATA_screen <- DATA[-influential, ]

# ___ 3) calculate difference scores and summarize
  sub_diff = subset(DATA, select = c("subject", "session_id",  "param_task_name","param_cue_type", 
                                     "param_stimulus_type", DV))
  subjectwise = meanSummary(sub_diff, c("subject", "session_id",  "param_task_name","param_cue_type", 
                                        "param_stimulus_type"), DV)
  mean_actual = subjectwise[1:(length(subjectwise)-1)]
  wide = mean_actual %>% 
    spread(param_cue_type, mean_per_sub)
  wide$diff = wide$high_cue - wide$low_cue
  wide$stim_name[wide$param_stimulus_type == "high_stim"] <- "high" # no influence task
  wide$stim_name[wide$param_stimulus_type == "med_stim"] <- "med" # no influence task
  wide$stim_name[wide$param_stimulus_type == "low_stim"] <- "low" # no influence task
  wide$stim_ordered <- factor(wide$stim_name, levels=c("low", "med", "high"))
  
  subjectwise_diff = meanSummary(wide, c("subject", "stim_ordered"), "diff")
  groupwise_diff = summarySEwithin(data=subjectwise_diff,
                    measurevar = "mean_per_sub", # variable created from above
                      withinvars = c("stim_ordered"), # IV
                      idvar = "subject")

  IV = "stim_ordered"
# ___ 4) plot
  if(any(startsWith(TASKNAME, c("pain", "Pain")))){
    COLOR=c("#EDE9D0", "#DE9B8A", "#C2170A")
    } else if (any(startsWith(TASKNAME, c("vicarious", "Vicarious")))){
      COLOR = c("#D4FADD", "#5DB97B", "#22834A")
    } else if (any(startsWith(TASKNAME, c("vicarious", "Vicarious")))){
      COLOR = c("#D3C2FF", "#7E79FF", "#0237C9")
  }
  GGTITLE = paste(TASKNAME, " - actual judgment (degree)")
  TITLE = paste(TASKNAME, " - actual")
  SUB_MEAN = "mean_per_sub"; GROUP_MEAN = "mean_per_sub_norm_mean"; SE = "se"; SUBJECT = "subject";
  SAVE_FNAME = file.path(analysis_dir, paste('socialinfluence_task-' ,TASKNAME, '_rating-', 
                                             DV_KEYWORD,'-diff_', as.character(Sys.Date()),'.png', 
                                             sep = ""))
  g = plot_expect_rainclouds(subjectwise_diff,groupwise_diff,IV,SUB_MEAN,GROUP_MEAN,SE, 
                         SUBJECT,GGTITLE,TITLE,XLAB,YLAB,TASKNAME,w,h,DV_KEYWORD,COLOR,SAVE_FNAME)
  ggsave(SAVE_FNAME, plot = g)

}
```

```{r}
d=data.frame(drink=c("coffee","tea","water"), mean=c(3,6,2), lower=c(2.6,5.6,1.8), upper=c(3.5,6.3,2.8))
j = ggplot() +
  geom_jitter(data = subjectwise_diff, 
              mapping = aes(stim_ordered,mean_per_sub),
              position = position_jitter(0.2)) +
  geom_pointrange(data=groupwise_diff, 
                mapping=aes(x = stim_ordered,
                            y = mean_per_sub_norm_mean, 
                            ymin = as.numeric(mean_per_sub_norm_mean - ci), 
                            ymax = as.numeric(mean_per_sub_norm_mean + ci)), 
                position = position_dodge(0.3),
                size=1, color=c("#D3C2FF", "#7E79FF", "#0237C9"),  shape=19) 
j
# p<-ggplot(subjectwise_diff,aes(x=stim_ordered,y=mean_per_sub, colour = factor(stim_ordered))) +
#   geom_hline(yintercept=0,size=0.5,linetype = "dashed")+ 
#   geom_hline(yintercept=0.2,size=0.5,linetype = "dashed")+ 
#   geom_hline(yintercept=0.5,size=0.5,linetype = "dashed") + 
#   geom_hline(yintercept=0.8,size=0.5,linetype = "dashed") + 
#   geom_hline(yintercept=1.2,size=0.5,linetype = "dashed")+ 
#   geom_hline(yintercept=2.0,size=0.5,linetype = "dashed")


```









```{r EXPECT, all three tasks}
# parameters
TASKNAME = 'cognitive'
SUBJECT_VARKEY = "src_subject_id"
IV = "param_cue_type"
DV = "event04_actual_angle"
DV_KEYWORD = "expect"
XLAB = ""; YLAB = "ratings (degree)"; 

GGTITLE = paste(TASKNAME, " - Expectation Rating (degree)")
TITLE = paste(TASKNAME, " - Expect")
SUBJECT = "subject"
EXCLUDE = ""

analysis_dir =file.path(main_dir,'analysis', 'mixedeffect', 'model01_cue_expectrating_sfn')

for (TASKNAME in c("pain", "vicarious", "cognitive")){

SAVE_FNAME = file.path(analysis_dir, paste('lmer_task-', TASKNAME, '_rating-',DV_KEYWORD,'.txt',sep = ''))
DATA = expect_df(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE )
run_cue_lmer(DATA,TASKNAME, IV, DV, SUBJECT, DV_KEYWORD, SAVE_FNAME)
subjectwise = meanSummary(DATA, c(SUBJECT, IV), DV)
groupwise = summarySEwithin(data=subjectwise, 
                  measurevar = "mean_per_sub", # variable created from above
                    withinvars = c(IV), # IV
                    idvar = "subject")

SUB_MEAN = "mean_per_sub"; GROUP_MEAN = "mean_per_sub_norm_mean"; SE = "se"; SUBJECT = "subject"
GGTITLE = paste(TASKNAME, " - Expectation Rating (degree)"); TITLE = paste(TASKNAME, " - Expect")
XLAB = ""; YLAB = "ratings (degree)"; DV_KEYWORD = "expect"
if(any(startsWith(DV_KEYWORD, c("expect", "Expect")))){COLOR = c( "#1B9E77", "#D95F02")}else{COLOR=c( "#4575B4", "#D73027")} # if keyword starts with
SAVE_FNAME = file.path(main_dir, 'analysis','mixedeffect', 'model01_cue_expectrating_sfn', paste('raincloudpoint_task-' ,TASKNAME, '_rating-', DV_KEYWORD,'.png', sep = ""))
plot_expect_rainclouds(subjectwise, groupwise,IV, SUB_MEAN, GROUP_MEAN, SE, SUBJECT,GGTITLE, TITLE, XLAB, YLAB,task_name, w, h, DV_KEYWORD,COLOR, SAVE_FNAME)
}
```




# ____________________________ 2-2. full factorial ____________________________
```{r FUNCTION: cue_stim_contrast}
cue_stim_contrast = function(DATA){
  # [ CONTRASTS ]  ----------------------------------------------------------------------------
DATA$stim[DATA$param_stimulus_type == "low_stim"] <- -0.5 # social influence task
DATA$stim[DATA$param_stimulus_type == "med_stim"] <- 0 # no influence task
DATA$stim[DATA$param_stimulus_type == "high_stim"] <- 0.5 # no influence task

DATA$stim_factor = factor(DATA$param_stimulus_type)

#contrast code 1 linear
DATA$stim_con_linear[DATA$param_stimulus_type == "low_stim"] <- -0.5
DATA$stim_con_linear[DATA$param_stimulus_type == "med_stim"] <- 0
DATA$stim_con_linear[DATA$param_stimulus_type == "high_stim"] <- 0.5

# contrast code 2 quadratic
DATA$stim_con_quad[DATA$param_stimulus_type == "low_stim"] <- -0.33
DATA$stim_con_quad[DATA$param_stimulus_type == "med_stim"] <- 0.66
DATA$stim_con_quad[DATA$param_stimulus_type == "high_stim"] <- -0.33

# social cude contrast
DATA$social_cue[DATA$param_cue_type == 'low_cue'] <- -0.5 # social influence task
DATA$social_cue[DATA$param_cue_type == 'high_cue'] <- 0.5 # no influence task
DATA$cue_factor = factor(DATA$param_cue_type)
return(as.data.frame(DATA))
}
```

# MODEL 2: actual rating = CUE X STIM
```{r}

combined_se_calc =  data.frame()
# 1. [ PARAMETERS ]  ----------------------------------------------------------------------------
# TASKNAME = 'cognitive'
SUBJECT_VARKEY = "src_subject_id"
IV1 = "param_cue_type"
DV = "event04_actual_angle"
DV_KEYWORD = "actual"
XLAB = ""; YLAB = "judgment (degree)"; 

for (TASKNAME in c("pain","vicarious","cognitive")){
GGTITLE = paste(TASKNAME, " - actual judgment (degree)")
TITLE = paste(TASKNAME, " - actual")
SUBJECT = "subject"
EXCLUDE = ""
DATA = expect_df(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE )
analysis_dir = file.path(main_dir,'analysis', 'mixedeffect', 'model03_cue_stim_actualrating_02-2022')

w = 10; h = 6

# [ CONTRASTS ]  ----------------------------------------------------------------------------
DATA = cue_stim_contrast(DATA)
STIMC1 = "stim_con_linear"
STIMC2 = "stim_con_quad"

# [ MODEL ] ----------------------------------------------------------------------------
MODEL_FNAME = file.path(analysis_dir, paste('lmer_task-', TASKNAME, '_rating-',DV_KEYWORD,'_', as.character(Sys.Date()),'.txt',sep = ''))
run_cue_stim_lmer(DATA,TASKNAME, IV1, STIMC1,STIMC2, DV, SUBJECT, DV_KEYWORD, MODEL_FNAME)

# [ PLOT ] reordering for plots ----------------------------------------------------------------------------
DATA$cue_name[DATA$param_cue_type == "high_cue"] <- "high cue"
DATA$cue_name[DATA$param_cue_type == "low_cue"] <- "low cue" # no influence task

DATA$stim_name[DATA$param_stimulus_type == "high_stim"] <- "high" # no influence task
DATA$stim_name[DATA$param_stimulus_type == "med_stim"] <- "med" # no influence task
DATA$stim_name[DATA$param_stimulus_type == "low_stim"] <- "low" # no influence task

# DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

DATA$stim_ordered <- factor(DATA$stim_name, levels=c("low", "med", "high"))
DATA$cue_ordered <- factor(DATA$cue_name, levels=c("low cue", "high cue"))
MODELIV1 = "stim_ordered";MODELIV2 = "cue_ordered"

#  [ PLOT ] calculate mean and se  ----------------------------------------------------------------------------
actual_subjectwise = meanSummary(DATA, c(SUBJECT, MODELIV1, MODELIV2), DV)
actual_groupwise = summarySEwithin(data=actual_subjectwise, measurevar = "mean_per_sub", withinvars = c(MODELIV1, MODELIV2), idvar = SUBJECT)
actual_groupwise$task = TASKNAME
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402
combined_se_calc = rbind(combined_se_calc, actual_groupwise)
#if(any(startsWith(DV_KEYWORD, c("expect", "Expect")))){COLOR = c( "#1B9E77", "#D95F02")}else{COLOR=c( "#4575B4", "#D73027")} # if keyword starts with
#print("groupwisemean")
#  [ PLOT ] calculate mean and se  ----------------------------------------------------------------------------
SUB_MEAN = "mean_per_sub"; GROUP_MEAN = "mean_per_sub_norm_mean"; SE = "se"; SUBJECT = "subject";
GGTITLE = paste(TASKNAME, " - Actual Rating (degree)"); TITLE = paste(TASKNAME, " - Actual");
XLAB = ""; YLAB = "ratings (degree)";
DV_KEYWORD = "actual"
if(any(startsWith(DV_KEYWORD, c("expect", "Expect")))){COLOR = c( "#1B9E77", "#D95F02")}else{COLOR=c( "#4575B4", "#D73027")} # if keyword starts with
SAVE_FNAME = file.path(analysis_dir,paste('socialinfluence_task-' ,TASKNAME, '_rating-', DV_KEYWORD,'_', as.character(Sys.Date()),'.png', sep = ""))
plot_actual_rainclouds(actual_subjectwise, actual_groupwise, MODELIV1, MODELIV2,
                       SUB_MEAN, GROUP_MEAN, SE, SUBJECT,
                       GGTITLE, TITLE, XLAB, YLAB,TASKNAME, w, h, DV_KEYWORD,COLOR, SAVE_FNAME)



# [ FIXED RANDOM EFFECTS ]save fixed random effects    ----------------------------------------------------------------------------
require(plyr)
randEffect$newcoef <- mapvalues(randEffect$term,
          from=c("(Intercept)","DATA[, IV]low_cue","DATA[, STIMC1]", "DATA[, STIMC2]", "DATA[, IV]low_cue:DATA[, STIMC1]", "DATA[, IV]low_cue:DATA[, STIMC2]"),
          to=c("rand_intercept","rand_cue","rand_stimulus_linear", "rand_stimulus_quad", "rand_int_cue_stimlin", "rand_int_cue_stimquad"))

# 
# # The arguments to spread():
# # - data: Data object
# # - key: Name of column containing the new column names
# # - value: Name of column containing values
# 
# # TODO: add fixed effects
# 
rand_subset = subset(randEffect, select  = -c(grpvar, term, condsd))
wide_rand = spread(rand_subset, key = newcoef, value = condval)
# wide_rand$task = TASKNAME
wide_fix = do.call("rbind", replicate(nrow(wide_rand), as.data.frame(t(as.matrix(fixEffect))), simplify = FALSE))
rownames(wide_fix)<-NULL
new_wide_fix = dplyr::rename(wide_fix, fix_intercept = `(Intercept)`,    fix_cue = `DATA[, IV]low_cue`,
              fix_stimulus_linear = `DATA[, STIMC1]`,
     fix_stimulus_quad = `DATA[, STIMC2]`,    fix_int_cue_stimlin = `DATA[, IV]low_cue:DATA[, STIMC1]`,
    fix_int_cue_stimquad = `DATA[, IV]low_cue:DATA[, STIMC2]`  )

total <- cbind(wide_rand,new_wide_fix)
total$task = TASKNAME
new_total <- total %>% dplyr::select(task, everything())
new_total = dplyr::rename(total, subj = grp)

save_fname = file.path(analysis_dir, paste('task-',TASKNAME,'_', as.character(Sys.Date()), '.csv',  sep='') )
write.csv(new_total, save_fname, row.names = FALSE)
}

```

# MODEL 2: actual rating = CUE X STIM REMOVE OUTLIERS 
```{r}

combined_se_calc_cooksd =  data.frame()
# 1. [ PARAMETERS ]  ----------------------------------------------------------------------------
# TASKNAME = 'cognitive'
SUBJECT_VARKEY = "src_subject_id"
IV1 = "param_cue_type"
DV = "event04_actual_angle"
DV_KEYWORD = "actual"
XLAB = ""; YLAB = "judgment (degree)"; 

for (TASKNAME in c("pain","vicarious","cognitive")){
GGTITLE = paste(TASKNAME, " - actual judgment (degree)")
TITLE = paste(TASKNAME, " - actual")
SUBJECT = "subject"
EXCLUDE = ""
DATA = expect_df(TASKNAME, SUBJECT_VARKEY, IV, DV, EXCLUDE )
analysis_dir = file.path(main_dir,'analysis', 'mixedeffect', 'model03_cue_stim_actualrating_02-2022')

w = 10; h = 6

# [ CONTRASTS ]  ----------------------------------------------------------------------------
DATA = cue_stim_contrast(DATA)
STIMC1 = "stim_con_linear"
STIMC2 = "stim_con_quad"

# [ MODEL ] ----------------------------------------------------------------------------
MODEL_FNAME = file.path(analysis_dir, paste('lmer_task-', TASKNAME, '_rating-',DV_KEYWORD,'_', as.character(Sys.Date()),'_cooksd.txt',sep = ''))
cooksd = run_cue_stim_lmer(DATA,TASKNAME, IV1, STIMC1,STIMC2, DV, SUBJECT, DV_KEYWORD, MODEL_FNAME)
influential <- as.numeric(names(cooksd)[(cooksd > (4/as.numeric(length(unique(DATA$src_subject_id))))    )])
DATA_screen <- DATA[-influential, ]
# [ PLOT ] reordering for plots ----------------------------------------------------------------------------
DATA_screen$cue_name[DATA_screen$param_cue_type == "high_cue"] <- "high cue"
DATA_screen$cue_name[DATA_screen$param_cue_type == "low_cue"] <- "low cue" # no influence task

DATA_screen$stim_name[DATA_screen$param_stimulus_type == "high_stim"] <- "high" # no influence task
DATA_screen$stim_name[DATA_screen$param_stimulus_type == "med_stim"] <- "med" # no influence task
DATA_screen$stim_name[DATA_screen$param_stimulus_type == "low_stim"] <- "low" # no influence task

# DATA$levels_ordered <- factor(DATA$param_stimulus_type, levels=c("low", "med", "high"))

DATA_screen$stim_ordered <- factor(DATA_screen$stim_name, levels=c("low", "med", "high"))
DATA_screen$cue_ordered <- factor(DATA_screen$cue_name, levels=c("low cue", "high cue"))
MODELIV1 = "stim_ordered";MODELIV2 = "cue_ordered"

#  [ PLOT ] calculate mean and se  ----------------------------------------------------------------------------
actual_subjectwise = meanSummary(DATA_screen, c(SUBJECT, MODELIV1, MODELIV2), DV)
actual_groupwise = summarySEwithin(data=actual_subjectwise, measurevar = "mean_per_sub", withinvars = c(MODELIV1, MODELIV2), idvar = SUBJECT)
actual_groupwise$task = TASKNAME
# https://stackoverflow.com/questions/29402528/append-data-frames-together-in-a-for-loop/29419402
combined_se_calc_cooksd = rbind(combined_se_calc_cooksd, actual_groupwise)
#if(any(startsWith(DV_KEYWORD, c("expect", "Expect")))){COLOR = c( "#1B9E77", "#D95F02")}else{COLOR=c( "#4575B4", "#D73027")} # if keyword starts with
#print("groupwisemean")
#  [ PLOT ] calculate mean and se  ----------------------------------------------------------------------------
SUB_MEAN = "mean_per_sub"; GROUP_MEAN = "mean_per_sub_norm_mean"; SE = "se"; SUBJECT = "subject";
GGTITLE = paste(TASKNAME, " - Actual Rating (degree) Cooksd removed"); TITLE = paste(TASKNAME, " - Actual");
XLAB = ""; YLAB = "ratings (degree)";
DV_KEYWORD = "actual"
if(any(startsWith(DV_KEYWORD, c("expect", "Expect")))){COLOR = c( "#1B9E77", "#D95F02")}else{COLOR=c( "#4575B4", "#D73027")} # if keyword starts with
SAVE_FNAME = file.path(analysis_dir,paste('socialinfluence_task-' ,TASKNAME, '_rating-', DV_KEYWORD,'_', as.character(Sys.Date()),'_cooksd.png', sep = ""))
plot_actual_rainclouds(actual_subjectwise, actual_groupwise, MODELIV1, MODELIV2,
                       SUB_MEAN, GROUP_MEAN, SE, SUBJECT,
                       GGTITLE, TITLE, XLAB, YLAB,TASKNAME, w, h, DV_KEYWORD,COLOR, SAVE_FNAME)



# [ FIXED RANDOM EFFECTS ]save fixed random effects    ----------------------------------------------------------------------------
#require(plyr)
randEffect$newcoef <- mapvalues(randEffect$term,
          from=c("(Intercept)","DATA[, IV]low_cue","DATA[, STIMC1]", "DATA[, STIMC2]", "DATA[, IV]low_cue:DATA[, STIMC1]", "DATA[, IV]low_cue:DATA[, STIMC2]"),
          to=c("rand_intercept","rand_cue","rand_stimulus_linear", "rand_stimulus_quad", "rand_int_cue_stimlin", "rand_int_cue_stimquad"))

# 
# # The arguments to spread():
# # - data: Data object
# # - key: Name of column containing the new column names
# # - value: Name of column containing values
# 
# # TODO: add fixed effects
# 
rand_subset = subset(randEffect, select  = -c(grpvar, term, condsd))
wide_rand = spread(rand_subset, key = newcoef, value = condval)
# wide_rand$task = TASKNAME
wide_fix = do.call("rbind", replicate(nrow(wide_rand), as.data.frame(t(as.matrix(fixEffect))), simplify = FALSE))
rownames(wide_fix)<-NULL
new_wide_fix = dplyr::rename(wide_fix, fix_intercept = `(Intercept)`,    fix_cue = `DATA[, IV]low_cue`,
              fix_stimulus_linear = `DATA[, STIMC1]`,
     fix_stimulus_quad = `DATA[, STIMC2]`,    fix_int_cue_stimlin = `DATA[, IV]low_cue:DATA[, STIMC1]`,
    fix_int_cue_stimquad = `DATA[, IV]low_cue:DATA[, STIMC2]`  )

total <- cbind(wide_rand,new_wide_fix)
total$task = TASKNAME
new_total <- total %>% dplyr::select(task, everything())
new_total = dplyr::rename(total, subj = grp)

save_fname = file.path(analysis_dir, paste('task-',TASKNAME,'_', as.character(Sys.Date()), '_cooksd.csv',  sep='') )
write.csv(new_total, save_fname, row.names = FALSE)
}

```

# plot using for loop
### FUNCTION: lineplot
```{r}
line_plot <- function(DATA, TASK, IV1, IV2, MEAN, ERROR, COLOR, GGTITLE){
# IV1 = "levels_ordered"
# IV2 = "social_ordered"
# MEAN = mean_per_sub_norm_mean
# ERROR = ci
  SUBSET = DATA[ which(DATA$task == TASK),]

  g = ggplot(data = SUBSET, aes(x = .data[[IV1]], y = .data[[MEAN]], 
                                group = factor(.data[[IV2]]), color = factor(.data[[IV2]])), cex.lab=1.5, cex.axis=2, cex.main=1.5, cex.sub=1.5) + 
  geom_errorbar(aes(ymin = (.data[[MEAN]]-.data[[ERROR]]), ymax = (.data[[MEAN]]+.data[[ERROR]])), width = .1) + 
  geom_line() + 
  geom_point() + 
  #scale_x_continuous(breaks = seq(-3, +3, by = 1)) +
  #scale_y_continuous(breaks = seq(0, 90, by=30), limits=c(0,90)) +
  ggtitle(GGTITLE) +
 # ggtitle(expression(atop(GGTITLE, 
 #                         atop(italic("cue effect on actual experience"), "")))) +
  xlab("Stimulus intensity") + 
  ylab("Rating (degrees)") + 
  #guides(fill=guide_legend(title="Social Endorsement Position")) +
  scale_color_manual(values=COLOR) + 
  theme_classic() + 
  theme(legend.position="none") 
  theme(aspect.ratio=.6)
g
  }
```


```{r}
library(ggpubr)
DATA = as.data.frame(combined_se_calc)
color = c( "#4575B4", "#D73027")
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "ci"
p1 = line_plot(DATA, 'pain', 
               LINEIV1, LINEIV2, MEAN, ERROR, color, GGTITLE = 'pain' )
p2 = line_plot(DATA,'vicarious', 
               LINEIV1, LINEIV2, MEAN, ERROR, color,GGTITLE = 'vicarious')
p3 = line_plot(DATA, 'cognitive', 
               LINEIV1, LINEIV2, MEAN, ERROR, color,GGTITLE = 'cognitive')
#grid.arrange(p1, p2, p3, ncol=3 , common.legend = TRUE)
ggpubr::ggarrange(p1,p2,p3,ncol = 3, nrow = 1, common.legend = TRUE,legend = "bottom")
plot_filename = file.path(main_dir, 'analysis','mixedeffect','model03_cue_stim_actualrating_02-2022', paste('socialinfluence_task-total_rating-',DV_KEYWORD,'_', as.character(Sys.Date()),'.png', sep = ""))
ggsave(plot_filename, width = 7, height = 3)

```


# remove outlier

```{r}
library(ggpubr)
DATA = as.data.frame(combined_se_calc_cooksd)
color = c( "#4575B4", "#D73027")
LINEIV1 = "stim_ordered"
LINEIV2 = "cue_ordered"
MEAN = "mean_per_sub_norm_mean"
ERROR = "ci"
p1 = line_plot(DATA, 'pain', 
               LINEIV1, LINEIV2, MEAN, ERROR, color, GGTITLE = 'pain' )
p2 = line_plot(DATA,'vicarious', 
               LINEIV1, LINEIV2, MEAN, ERROR, color,GGTITLE = 'vicarious')
p3 = line_plot(DATA, 'cognitive', 
               LINEIV1, LINEIV2, MEAN, ERROR, color,GGTITLE = 'cognitive')
#grid.arrange(p1, p2, p3, ncol=3 , common.legend = TRUE)
ggpubr::ggarrange(p1,p2,p3,ncol = 3, nrow = 1, common.legend = TRUE,legend = "bottom")
plot_filename = file.path(main_dir, 'analysis','mixedeffect','model03_cue_stim_actualrating_02-2022', paste('socialinfluence_task-total_rating-',DV_KEYWORD,'_', as.character(Sys.Date()),'cooksd.png', sep = ""))
ggsave(plot_filename, width = 7, height = 3)

```

# concat mixed effect coefficients
```{r}
# stack task- .csv
dfP = read.csv(file.path(analysis_dir, paste('task-pain','_', as.character(Sys.Date()),'.csv',  sep='') ))
dfV = read.csv(file.path(analysis_dir, paste('task-vicarious','_', as.character(Sys.Date()),'.csv',  sep='') ))
dfC = read.csv(file.path(analysis_dir, paste('task-cognitive','_', as.character(Sys.Date()),'.csv',  sep='') ))

PVC <- merge_recurse(list(dfP,dfV,dfC))

save_fname = file.path(analysis_dir, paste('PVC_mixedeffect_coef','_', as.character(Sys.Date()),'2.csv',  sep='') )
write.csv(PVC, save_fname, row.names = FALSE)


```

# plot separately
```{r}
PVC_rand_cue_subset = subset(PVC, select  = c(task, subj, rand_cue))
PVC_rand_cue = spread(PVC_rand_cue_subset, key = task, value = rand_cue)
PV = ggplot(aes(x=vicarious, y=pain), data=PVC_rand_cue, cex.lab=1.5, cex.axis=2, cex.main=1.5, cex.sub=1.5) + geom_point() + theme_classic() +  theme(aspect.ratio=1) + stat_cor(p.accuracy = 0.001, r.accuracy = 0.01, method = "pearson", label.y = 14) + xlim(-15, 15) + ylim(-15, 15)
VC = ggplot(aes(x=cognitive, y=vicarious), data=PVC_rand_cue, cex.lab=1.5, cex.axis=2, cex.main=1.5, cex.sub=1.5) + geom_point() + theme_classic() +  theme(aspect.ratio=1)+ stat_cor(p.accuracy = 0.001, r.accuracy = 0.01, method = "pearson", label.y = 14) + xlim(-15, 15) + ylim(-15, 15)
CP = ggplot(aes(x=pain, y=cognitive), data=PVC_rand_cue, cex.lab=1.5, cex.axis=2, cex.main=1.5, cex.sub=1.5) + geom_point() + theme_classic() +  theme(aspect.ratio=1) + stat_cor(p.accuracy = 0.001, r.accuracy = 0.01, method = "pearson", label.y = 14) + xlim(-15, 15) + ylim(-15, 15)
ggpubr::ggarrange(PV,VC,CP,ncol = 3, nrow = 1, common.legend = FALSE,legend = "bottom")
plot_filename = file.path(main_dir, 'analysis','mixedeffect','model03_cue_stim_actualrating_02-2022', paste('socialinfluence_task-total_rating-',DV_KEYWORD,'_correlation-rand-cue-coef','_', as.character(Sys.Date()),'.png', sep = ""))
ggsave(plot_filename, width = 7, height = 3)

```
# remove outlier
```{r}
# within each task, remove outlier based on cooks' d
```
# concat mixed effect coefficients REMOVE OUTLIER
```{r}
# stack task- .csv
dfP = read.csv(file.path(analysis_dir, paste('task-pain','_', as.character(Sys.Date()),'_cooksd.csv',  sep='') ))
dfV = read.csv(file.path(analysis_dir, paste('task-vicarious','_', as.character(Sys.Date()),'_cooksd.csv',  sep='') ))
dfC = read.csv(file.path(analysis_dir, paste('task-cognitive','_', as.character(Sys.Date()),'_cooksd.csv',  sep='') ))

PVC_cooksd <- merge_recurse(list(dfP,dfV,dfC))

save_fname = file.path(analysis_dir, paste('PVC_mixedeffect_coef','_', as.character(Sys.Date()),'_cooksd.csv',  sep='') )
write.csv(PVC_cooksd, save_fname, row.names = FALSE)


```

# plot separately AFTER REMOVING OUTLIERS
```{r}
PVC_rand_cue_subset = subset(PVC_cooksd, select  = c(task, subj, rand_cue))
# PVC_rand_cue_rmoutlier = PVC_rand_cue_subset_cooksd[PVC_rand_cue_subset_cooksd$sub != 13, ]  
model.rm = lm(PVC_rand_cue_subset$rand_cue ~ 1)

cooksd <- cooks.distance(model.rm)

influential <- as.numeric(names(cooksd)[(cooksd > (4/as.numeric(length(unique(PVC_rand_cue_subset$subj))))    )])
PVC_rand_cue_subset_cooksd <- PVC_rand_cue_subset[-influential, ]


PVC_rand_cue_rm = spread(PVC_rand_cue_subset_cooksd, key = task, value = rand_cue)
PV = ggplot(aes(x=vicarious, y=pain), data=PVC_rand_cue_rm, cex.lab=1.5, cex.axis=2, cex.main=1.5, cex.sub=1.5) + geom_point() + theme_classic() +  theme(aspect.ratio=1) + stat_cor(p.accuracy = 0.001, r.accuracy = 0.01, method = "pearson", label.y = 14) +
 xlim(-15, 15) + ylim(-15, 15)
# stat_cor(aes(color = variable),
#     method = "pearson",
#     label.x = 2, label.y = c(0.0038,0.004))
# + xlim(-15, 15) + ylim(-15, 15)

VC = ggplot(aes(x=cognitive, y=vicarious), data=PVC_rand_cue_rm, cex.lab=1.5, cex.axis=2, cex.main=1.5, cex.sub=1.5) + geom_point() + theme_classic() +  theme(aspect.ratio=1)+ stat_cor(p.accuracy = 0.001, r.accuracy = 0.01, method = "pearson", label.y = 14) + xlim(-15, 15) + ylim(-15, 15)
# + xlim(-15, 15) + ylim(-15, 15)

CP = ggplot(aes(x=pain, y=cognitive), data=PVC_rand_cue_rm, cex.lab=1.5, cex.axis=2, cex.main=1.5, cex.sub=1.5, cex.xlim=c(0,30), cex.ylim=c(0,150)) + geom_point() + theme_classic() +  theme(aspect.ratio=1) + stat_cor(p.accuracy = 0.001, r.accuracy = 0.01, method = "pearson", label.y = 14) + xlim(-15, 15) + ylim(-15, 15)
# + xlim(-15, 15) + ylim(-15, 15)

ggpubr::ggarrange(PV,VC,CP,ncol = 3, nrow = 1, common.legend = FALSE,legend = "bottom")
plot_filename = file.path(main_dir, 'analysis','mixedeffect','model03_cue_stim_actualrating_02-2022', paste('socialinfluence_task-total_rating-',DV_KEYWORD,'_correlation-rand-cue-coef_rmoutlier.png', sep = ""))
ggsave(plot_filename, width = 7, height = 3)

```
# plot separately
```{r}
PVC_rand_cue_subset = subset(PVC, select  = c(task, subj, rand_cue))
PVC_rand_cue = spread(PVC_rand_cue_subset, key = task, value = rand_cue)
PV = ggplot(aes(x=vicarious, y=pain), data=PVC_rand_cue, cex.lab=1.5, cex.axis=2, cex.main=1.5, cex.sub=1.5) + geom_point() + theme_classic() +  theme(aspect.ratio=1) + stat_cor(p.accuracy = 0.001, r.accuracy = 0.01)
VC = ggplot(aes(x=cognitive, y=vicarious), data=PVC_rand_cue, cex.lab=1.5, cex.axis=2, cex.main=1.5, cex.sub=1.5) + geom_point() + theme_classic() +  theme(aspect.ratio=1)+ stat_cor(p.accuracy = 0.001, r.accuracy = 0.01)
CP = ggplot(aes(x=pain, y=cognitive), data=PVC_rand_cue, cex.lab=1.5, cex.axis=2, cex.main=1.5, cex.sub=1.5) + geom_point() + theme_classic() +  theme(aspect.ratio=1) + stat_cor(p.accuracy = 0.001, r.accuracy = 0.01)
ggpubr::ggarrange(PV,VC,CP,ncol = 3, nrow = 1, common.legend = FALSE,legend = "bottom")
plot_filename = file.path(main_dir, 'analysis','mixedeffect','model03_cue_stim_actualrating_02-2022', paste('socialinfluence_task-total_rating-',DV_KEYWORD,'_correlation-rand-cue-coef','_', as.character(Sys.Date()),'.png', sep = ""))
ggsave(plot_filename, width = 7, height = 3)

```

# correlation
```{r}
PVC_rand_cue_subset = subset(PVC, select  = c(task, subj, rand_cue))

PVC_rand_cue = spread(PVC_rand_cue_subset, key = task, value = rand_cue)
PVC_indiff_cue = subset(PVC_rand_cue, select  = -c(subj))
ggpairs(PVC_indiff_cue)


# Make the plot
#my_colors <- brewer.pal(nlevels(as.factor(data$cyl)), "Set2")
scatterplotMatrix(~pain+vicarious+cognitive, data=PVC_indiff_cue , 
      reg.line="" ,
      #smoother="", 
      #col=my_colors , 
      #smoother.args=list(col="grey") , 
      #cex=1.5 , 
      #pch=c(15,16,17) , 
      main="Scatter plot with Three Cylinder Options"
      )
```

```{r}
library(psych)

pairs.panels(PVC_indiff_cue,
             smooth = FALSE,      # If TRUE, draws loess smooths
             scale = FALSE,      # If TRUE, scales the correlation text font
             density = TRUE,     # If TRUE, adds density plots and histograms
             ellipses = FALSE,    # If TRUE, draws ellipses
             method = "pearson", # Correlation method (also "spearman" or "kendall")
             pch = 21,           # pch symbol
             lm = FALSE,         # If TRUE, plots linear fit rather than the LOESS (smoothed) fit
             cor = TRUE,         # If TRUE, reports correlations
             jiggle = FALSE,     # If TRUE, data points are jittered
             factor = 2,         # Jittering factor
             hist.col = 4,       # Histograms color
             stars = TRUE,       # If TRUE, adds significance level with stars
             ci = TRUE)          # If TRUE, adds confidence intervals
```
```{r}
library(psych)

pairs.panels(PVC_indiff_cue,
             smoother = FALSE,      # If TRUE, draws loess smooths
             scale = FALSE,      # If TRUE, scales the correlation text font
             density = TRUE,     # If TRUE, adds density plots and histograms
             ellipses = FALSE,    # If TRUE, draws ellipses
             method = "pearson", # Correlation method (also "spearman" or "kendall")
             pch = 21,           # pch symbol
             lm = TRUE,         # If TRUE, plots linear fit rather than the LOESS (smoothed) fit
             cor = TRUE,         # If TRUE, reports correlations
             jiggle = FALSE,     # If TRUE, data points are jittered
             factor = 2,         # Jittering factor
             hist.col = 4,       # Histograms color
             stars = TRUE,       # If TRUE, adds significance level with stars
             ci = TRUE)          # If TRUE, adds confidence intervals
```

=